### 2014-03-28 intro/intro.Rmd
many updates, including rmd files

ASH based wavelet shrinkage for heteroskedastic models
========================================================

We assume a simple parametric model of the form
$y_i=\mu_i+\epsilon_i$
where $\epsilon_i\sim N(0,\sigma_i^2)$, and both $\mu$ and $\sigma$ are unknown. We use the procedure described in the documentation to estimate both the mean and the variances. Here we present a brief demonstration of the method.

We first look at mean estimation, which is our primary focus. A sample mean function is presented, as well as a couple of different variance functions. Our method is compared against a few other simple methods.

```{r}
spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
n=1024
t=1:n/n
mu.s=spike.f(t)

library(wavethresh)
library(EbayesThresh)
library(caTools)
source(file.path("../Rcode/bayesmooth.R"))
source(file.path("../Rcode/ti_thresh.R"))

mse=function(x,y) mean((x-y)^2)
l2norm=function(x) sum(x^2)
mise=function(x,y,r) 10000*mean(apply(x-rep(1,r)%o%y,1,l2norm)/l2norm(y))
sig.est.func=function(x,n) sqrt(2/(3*(n-2))*sum((1/2*x[1:(n-2)]-x[2:(n-1)]+1/2*x[3:n])^2))

##Default R wavelet method, written into a single function
waveti.u=function (x, filter.number = 10, family = "DaubLeAsymm", min.level = 3, noise.level){
    TT <- length(x)
    thresh <- noise.level * sqrt(2 * log(TT))    
    x.w <- wd(x, filter.number, family, type = "station")
    x.w.t <- threshold(x.w, levels = (min.level):(x.w$nlevels - 1), policy = "manual", value = thresh, type = "hard")
    x.w.t.r <- AvBasis(convert(x.w.t))
    return(x.w.t.r)
}

waveti.ebayes=function (x, filter.number = 10, family = "DaubLeAsymm", min.level = 3, noise.level){
    n=length(x)
    J=log2(n)
    x.w <- wd(x, filter.number, family, type = "station")
    for(j in min.level:(J-1)){
      x.pm = ebayesthresh(accessD(x.w,j),sdev=noise.level)
      x.w = putD(x.w,j,x.pm)
    }
    mu.est=AvBasis(convert(x.w))
    return(mu.est)
}

##mean function
mu.t=(1+mu.s)/5

##signal to noise ratio
rsnr=sqrt(1)

##variance functions
var1=rep(1,n)
var2=(0.0001+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
```

We first look at the case of constant variance
```{r}
##constant variance
sigma.ini=sqrt(var1)
sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

set.seed(327)
X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)

mu.est=apply(X.s,1,bayesmooth)
mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")

mu.est.ti=matrix(0,10,n)
mu.est.ti.ebayes=matrix(0,10,n)
for(i in 1:10){
  sig.est=sig.est.func(X.s[i,],n)
  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
}

##MISEs

##Bayesmooth
mise(t(mu.est),mu.t,10)
##TI thresholding with variance estimated from bayesmooth
mise(t(mu.est.tivar.ash),mu.t,10)
##TI thresholding with variance estimated from running MAD
mise(t(mu.est.tivar.mad),mu.t,10)
##TI thresholding with constant variance (estimated)
mise(mu.est.ti,mu.t,10)
##EBayes with constant variance (estimated)
mise(mu.est.ti.ebayes,mu.t,10)
```

```{r fig.width=12, fig.height=12}

plot(mu.t,type='l')
lines(mu.est[,1],col=2)
lines(mu.est.tivar.mad[,1],col=3)
lines(mu.est.ti[1,],col=4)
lines(mu.est.ti.ebayes[1,],col=6)
```

We then look at the case of non-constant variance
```{r}
##non-constant variance
sigma.ini=sqrt(var2)
sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

set.seed(327)
X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)

mu.est=apply(X.s,1,bayesmooth)
mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")

mu.est.ti=matrix(0,10,n)
mu.est.ti.ebayes=matrix(0,10,n)
for(i in 1:10){
  sig.est=sig.est.func(X.s[i,],n)
  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
}

##MISEs

##Bayesmooth
mise(t(mu.est),mu.t,10)
##TI thresholding with variance estimated from bayesmooth
mise(t(mu.est.tivar.ash),mu.t,10)
##TI thresholding with variance estimated from running MAD
mise(t(mu.est.tivar.mad),mu.t,10)
##TI thresholding with constant variance (estimated)
mise(mu.est.ti,mu.t,10)
##EBayes with constant variance (estimated)
mise(mu.est.ti.ebayes,mu.t,10)

````

```{r fig.width=12, fig.height=12}
plot(mu.t,type='l')
lines(mu.est[,1],col=2)
lines(mu.est.tivar.mad[,1],col=3)
lines(mu.est.ti[1,],col=4)
lines(mu.est.ti.ebayes[1,],col=6)

```

Next we look at variance estimation. Because variance estimation is much harder, we use a larger sample size. Here $n=4096$.

```{r}
n=2^12
t=1:n/n
mu.s=spike.f(t)

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}
dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
mu.dop=dop.f(t)

var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
var3=mu.b
var4=3.4*(2+mu.dop)

sigma.t.1=sqrt(var1)
sigma.t.2=sqrt(var2)
sigma.t.3=sqrt(var3)
sigma.t.4=sqrt(var4)

set.seed(327)
X.s.1=rnorm(n,0,sigma.t.1)
set.seed(327)
X.s.2=rnorm(n,0,sigma.t.2)
set.seed(327)
X.s.3=rnorm(n,0,sigma.t.3)
set.seed(327)
X.s.4=rnorm(n,0,sigma.t.4)

var.est.1=bayesmooth(X.s.1,v.est=TRUE)
var.est.2=bayesmooth(X.s.2,v.est=TRUE)
var.est.3=bayesmooth(X.s.3,v.est=TRUE)
var.est.4=bayesmooth(X.s.4,v.est=TRUE)

mse(var.est.1,sigma.t.1^2)
mse(var.est.2,sigma.t.2^2)
mse(var.est.3,sigma.t.3^2)
mse(var.est.4,sigma.t.4^2)

```

```{r fig.width=12, fig.height=12}
par(mfrow=c(2,2))
plot(sigma.t.1^2,type='l')
lines(var.est.1,col=2)
plot(sigma.t.2^2,type='l')
lines(var.est.2,col=2)
plot(sigma.t.3^2,type='l')
lines(var.est.3,col=2)
plot(sigma.t.4^2,type='l')
lines(var.est.4,col=2)

```

Now we take a look at how this wavelet-based approach handles unevenly spaced data. Wavelet methods are not optimized for unevenly spaced, but still works.

```{r}
n=1024
t=sort(rnorm(1024,0,1))
t=(t-min(t))/(max(t)-min(t))

mu.s=spike.f(t)

##mean function
mu.t=(1+mu.s)/5

##signal to noise ratio
rsnr=sqrt(1)

##variance functions
var1=rep(1,n)
var2=(0.0001+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
```

```

We first look at the case of constant variance
```{r}
##constant variance
sigma.ini=sqrt(var1)
sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

set.seed(327)
X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)

mu.est=apply(X.s,1,bayesmooth)
mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")

mu.est.ti=matrix(0,10,n)
mu.est.ti.ebayes=matrix(0,10,n)
for(i in 1:10){
  sig.est=sig.est.func(X.s[i,],n)
  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
}

##MISEs for the sample points

##Bayesmooth
mise(t(mu.est),mu.t,10)
##TI thresholding with variance estimated from bayesmooth
mise(t(mu.est.tivar.ash),mu.t,10)
##TI thresholding with variance estimated from running MAD
mise(t(mu.est.tivar.mad),mu.t,10)
##TI thresholding with constant variance (estimated)
mise(mu.est.ti,mu.t,10)
##EBayes with constant variance (estimated)
mise(mu.est.ti.ebayes,mu.t,10)

##MISEs for the grid
xgrid=1:n/n
mu.est.inter=matrix(0,10,n)
mu.est.tivar.ash.inter=matrix(0,10,n)
mu.est.tivar.mad.inter=matrix(0,10,n)
mu.est.ti.inter=matrix(0,10,n)
mu.est.ti.ebayes.inter=matrix(0,10,n)
for(i in 1:10){
  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y

}
mu.t.inter=(spike.f(xgrid)+1)/5

mise(mu.est.inter,mu.t.inter,10)
mise(mu.est.tivar.ash.inter,mu.t.inter,10)
mise(mu.est.tivar.mad.inter,mu.t.inter,10)
mise(mu.est.ti.inter,mu.t.inter,10)
mise(mu.est.ti.ebayes.inter,mu.t.inter,10)

```

```{r fig.width=12, fig.height=12}
par(mfrow=c(1,1))
plot(t,mu.t,type='l')
lines(t,mu.est[,1],col=2)
lines(t,mu.est.tivar.mad[,1],col=3)
lines(t,mu.est.ti[1,],col=4)
lines(t,mu.est.ti.ebayes[1,],col=6)
```

We then look at the case of non-constant variance
```{r}
##non-constant variance
sigma.ini=sqrt(var2)
sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

set.seed(327)
X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)

mu.est=apply(X.s,1,bayesmooth)
mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")

mu.est.ti=matrix(0,10,n)
mu.est.ti.ebayes=matrix(0,10,n)
for(i in 1:10){
  sig.est=sig.est.func(X.s[i,],n)
  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
}

##MISEs

##Bayesmooth
mise(t(mu.est),mu.t,10)
##TI thresholding with variance estimated from bayesmooth
mise(t(mu.est.tivar.ash),mu.t,10)
##TI thresholding with variance estimated from running MAD
mise(t(mu.est.tivar.mad),mu.t,10)
##TI thresholding with constant variance (estimated)
mise(mu.est.ti,mu.t,10)
##EBayes with constant variance (estimated)
mise(mu.est.ti.ebayes,mu.t,10)

##MISEs for the grid
xgrid=1:n/n
mu.est.inter=matrix(0,10,n)
mu.est.tivar.ash.inter=matrix(0,10,n)
mu.est.tivar.mad.inter=matrix(0,10,n)
mu.est.ti.inter=matrix(0,10,n)
mu.est.ti.ebayes.inter=matrix(0,10,n)
for(i in 1:10){
  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y

}
mu.t.inter=(spike.f(xgrid)+1)/5

mise(mu.est.inter,mu.t.inter,10)
mise(mu.est.tivar.ash.inter,mu.t.inter,10)
mise(mu.est.tivar.mad.inter,mu.t.inter,10)
mise(mu.est.ti.inter,mu.t.inter,10)
mise(mu.est.ti.ebayes.inter,mu.t.inter,10)

```

```{r fig.width=12, fig.height=12}
par(mfrow=c(1,1))
plot(t,mu.t,type='l')
lines(t,mu.est[,1],col=2)
lines(t,mu.est.tivar.mad[,1],col=3)
lines(t,mu.est.ti[1,],col=4)
lines(t,mu.est.ti.ebayes[1,],col=6)

```

Now we look at some of the simulations in a couple of papers, as well as the datasets used in them. The first one is from Fan and Yao (1998). The simulation is as described in Example 2. To deal with the fact that the sample size is not a sample size of 2, we first reflect the right portion of the data about the right endpoint so that it is a power of 2. To make the data periodic, we then reflect the new data about the right endpoint again. Our results are shown below.

```{r}
mu.mad=0
var.mad=0

for(i in 1:400){
  x=sort(runif(200,-2,2))
  err=rnorm(200)
  sigma.t=0.4*exp(-2*x^2)+0.2
  mu.t=x+2*exp(-16*x^2)
  y=mu.t+sigma.t*err

  xgrid=seq(-1.8,1.8,length.out=101)
  mu.t.inter=xgrid+2*exp(-16*xgrid^2)
  var.t.inter=(0.4*exp(-2*xgrid^2)+0.2)^2

  y.exp=c(y,y[200:145])
  y.data=c(y.exp,y.exp[256:1])

  mu.est=bayesmooth(y.data)
  mu.est=mu.est[1:200]
  var.est=bayesmooth(y.data,v.est=TRUE)
  var.est=var.est[1:200]

  mu.est.inter=approx(x,mu.est,xgrid,'linear')$y
  var.est.inter=approx(x,var.est,xgrid,'linear')$y

  mu.mad[i]=1/101*sum(abs(mu.est.inter-mu.t.inter))
  var.mad[i]=1/101*sum(abs(var.est.inter-var.t.inter))

}

boxplot(var.mad)

plot(x,mu.t,type='l')
lines(x,mu.est[1:200],col=2)

plot(x,sigma.t^2,type='l')
lines(x,var.est[1:200],col=2)

```

We also look at the dataset in Example 1 of Fan and Yao (1998). To take into account replicates, we take the median of the response at the same point The results are shown below.

```{r}
data=read.csv("../gaus_data/treas_bill/treas_bill.csv",header=FALSE)
data=as.numeric(data[,1])

library(tseries)

y=ar(data,FALSE,5)$res
y=y[!is.na(y)]
x=sort(data[5:(length(data)-1)])
y=y[order(data[5:(length(data)-1)])]

plot(x,y)

##average replicate data

x.mod=unique(x)
y.mod=0
for(i in 1:length(x.mod)){
  y.mod[i]=median(y[x==x.mod[i]])
}

y.exp=c(y.mod,y.mod[length(y.mod):(2*length(y.mod)-2^10+1)])
y.final=c(y.exp,y.exp[length(y.exp):1])

y.est=bayesmooth(y.final)
y.est.var=bayesmooth(y.final,v.est=TRUE)

```

```{r fig.width=12, fig.height=12}
par(mfrow=c(2,2))
plot(data,type='l')

plot(x,y)
lines(x.mod,y.est[1:(length(y.mod))],col=2)

plot(x.mod,y.est[1:(length(y.mod))],type='l',ylim=c(-0.3,0.3))

plot(x.mod,sqrt(y.est.var[1:(length(y.mod))]),type='l')
````

We now look at the paper by Delouille et al. (2004). Specifically, we compare with the heavisine function used in section 6, as the actual function is readily available. The results for $n=200$ for both the homoskedastic and teh heteroskedastic cases are given.

```{r}

n=200
mse.hsm.c=0
mse.hsm.n=0
for(i in 1:500){
  xt=sort(rnorm(n,0.5,0.2))
  xt=(xt-min(xt))/(max(xt)-min(xt))

  mu.hsm=4 * sin(4 * pi * xt) - 2*sign(xt - 0.3) - 2*sign(0.72 - xt)

  mu.t=mu.hsm
  var1=rep(1,n)
  var2=(xt<=0.5)+2*(xt>0.5)
  sigma.ini=sqrt(var1)
  rsnr=sqrt(4)
  sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

  y=rnorm(n,mu.t,sigma.t)
  y.exp=c(y,y[200:145])
  y.final=c(y.exp,y.exp[256:1])

  mu.est<-bayesmooth(y.final)
  mu.est=mu.est[1:n]
  mse.hsm.c[i]=mse(mu.est,mu.t)

  sigma.ini=sqrt(var2)
  rsnr=sqrt(4)
  sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

  y=rnorm(n,mu.t,sigma.t)
  y.exp=c(y,y[200:145])
  y.final=c(y.exp,y.exp[256:1])

  mu.est<-bayesmooth(y.final)
  mu.est=mu.est[1:n]
  mse.hsm.n[i]=mse(mu.est,mu.t)

}

sqrt(quantile(mse.hsm.c,seq(0.25,0.75,0.25)))
sqrt(quantile(mse.hsm.n,seq(0.25,0.75,0.25)))

```

We also look at the two datasets in the same paper, which are two commonly seen datasets. We plot the data points and fit, as well as the estimated variances.

```{r}
library(MASS)

x.ini=sort(mcycle$times)
y.ini=mcycle$accel[order(mcycle$times)]

x=unique(x.ini)
y=0
for(i in 1:length(x)){
  y[i]=median(y.ini[x.ini==x[i]])
}

y.exp=c(y,y[length(y):(2*length(y)-128+1)])
y.final=c(y.exp,y.exp[length(y.exp):1])

y.est=bayesmooth(y.final)
y.est=y.est[1:length(y)]
y.var.est=bayesmooth(y.final,v.est=TRUE)
y.var.est=y.var.est[1:length(y)]

```

```{r fig.width=12, fig.height=6}

par(mfrow=c(1,2))

plot(x,y,ylim=c(-150,100))
lines(x,y.est,col=2)
plot(x,y.var.est,type='l')

```

```{r}
library(lattice)

x.ini=sort(ethanol$E)
y.ini=ethanol$NOx[order(ethanol$E)]

x=unique(x.ini)
y=0
for(i in 1:length(x)){
  y[i]=median(y.ini[x.ini==x[i]])
}

y.exp=c(y,y[length(y):(2*length(y)-128+1)])
y.final=c(y.exp,y.exp[length(y.exp):1])

y.est=bayesmooth(y.final)
y.est=y.est[1:length(y)]
y.var.est=bayesmooth(y.final,v.est=TRUE)
y.var.est=y.var.est[1:length(y)]

```

```{r fig.width=12, fig.height=6}

par(mfrow=c(1,2))

plot(x,y,ylim=c(-1,5))
lines(x,y.est,col=2)
plot(x,y.var.est,type='l')

```

### 2014-03-28 intro/multi_signal.Rmd
many updates, including rmd files

##Multiple signals
==========================
We briefly look at a very simple simulation in which there are multiple signals falling into 2 groups, and our goal is to find out the differences between the two groups. We assume that the variances for each signal could be different, but the mean for each group is the same

```{r}
source(file.path("../Rcode/bayesmooth.R"))
source(file.path("../Rcode/multiseq_gaus.R"))
source(file.path("../Rcode/multi_lmm.R"))

n=1024
t=1:n/n

spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
spikem.f=function(x) (0.75*exp(-500*(x-0.23)^2)+2.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+1.5*exp(-16000*(x-0.69)^2)+1*exp(-32000*(x-0.83)^2)+0.8*exp(-12000*(x-0.92)^2))

dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
mu.dop=dop.f(t)
mu.dop=3/(max(mu.dop)-min(mu.dop))*(mu.dop-min(mu.dop))
mu.dop.var=10*dop.f(t)
mu.dop.var=mu.dop.var-min(mu.dop.var)

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}

pos=c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = 2.88/5*c(4, (-5), 3, (-4), 5, (-4.2), 2.1, 4.3, (-3.1), 2.1, (-4.2))
mu.blk = rep(0,n)
for(j in 1:length(pos)){
  mu.blk = mu.blk + (1 + sign(t-pos[j]))*(hgt[j]/2)
}

mu.sp=spike.f(t)
mu.spm=spikem.f(t)

var1=rep(1,n)
var2=(0.0001+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))
var3=(0.00001+2*mu.dop.var)
var4=0.00001+mu.b

sigma.ini.v1=sqrt(var1)
sigma.ini.v2=sqrt(var2)
sigma.ini.v3=sqrt(var3)
sigma.ini.v4=sqrt(var4)

rsnr=sqrt(3)
sigma.0.v1=sigma.ini.v1/mean(sigma.ini.v1)*sd(mu.sp)/rsnr^2
sigma.0.v2=sigma.ini.v2/mean(sigma.ini.v2)*sd(mu.sp)/rsnr^2
sigma.0.v3=sigma.ini.v3/mean(sigma.ini.v3)*sd(mu.sp)/rsnr^2
sigma.0.v4=sigma.ini.v4/mean(sigma.ini.v4)*sd(mu.sp)/rsnr^2

sigma.1.v1=sigma.ini.v1/mean(sigma.ini.v1)*sd(mu.spm)/rsnr^2
sigma.1.v2=sigma.ini.v2/mean(sigma.ini.v2)*sd(mu.spm)/rsnr^2
sigma.1.v3=sigma.ini.v3/mean(sigma.ini.v3)*sd(mu.spm)/rsnr^2
sigma.1.v4=sigma.ini.v4/mean(sigma.ini.v4)*sd(mu.spm)/rsnr^2

set.seed(1112)
X.1=matrix(rnorm(10*n,mu.sp,c(rep(sigma.0.v1,2),rep(sigma.0.v2,4),rep(sigma.0.v3,4))),nrow=10,byrow=TRUE)
set.seed(1112)
X.2=matrix(rnorm(10*n,mu.spm,c(rep(sigma.1.v2,3),rep(sigma.1.v3,2),rep(sigma.1.v4,5))),nrow=10,byrow=TRUE)

X=rbind(X.1,X.2)

g=c(rep(0,10),rep(1,10))

mse=function(x,y) mean((x-y)^2)

system.time(res<-multiseq.gaus(X,g,gridmult=2))

##load in results from the method in Morris (2006)
wfmm.res=read.table("../simulation_g/test_eg_beta.txt")
wfmm.res.quan=read.table("../simulation_g/test_eg_beta_quan.txt")
wfmm.res=data.matrix(wfmm.res)
wfmm.res.quan=data.matrix(wfmm.res.quan)

```

```{r fig.width=12, fig.height=6}
par(mfrow=c(1,2))

plot(mu.sp,type='l',ylim=c(-0.5,3.5),main="1024 points, 10 vs 10 samples, snr=3",ylab="baseline")

lines(res$baseline.mean,col=2)
lines(wfmm.res[1,],col=4)

lines(res$baseline.mean-2*sqrt(res$baseline.var),col=6)
lines(res$baseline.mean+2*sqrt(res$baseline.var),col=6)

lines(wfmm.res.quan[1,1:1024],col=3)
lines(wfmm.res.quan[8,1:1024],col=3)

plot(mu.spm-mu.sp,type='l',ylim=c(-1.2,1.6),main="1024 points, 10 vs 10 samples, snr=3",ylab="effect")

lines(res$effect.mean,col=2)
lines(wfmm.res[2,],col=4)

lines(res$effect.mean-2*sqrt(res$effect.var),col=6)
lines(res$effect.mean+2*sqrt(res$effect.var),col=6)

lines(wfmm.res.quan[1,1025:2048],col=3)
lines(wfmm.res.quan[8,1025:2048],col=3)

```

### 2014-03-28 tests/tests.Rmd
many updates, including rmd files

##Some other attempts

We try dividing the data by the standard deviation so that the new data will be iid. Here we work with the true standard deviation.

```{r}
source(file.path("../Rcode/bayesmooth.R"))
spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))

pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}

n=1024
t=1:n/n

mu.s=spike.f(t)

mu.t=(1+mu.s)/5

rsnr=sqrt(3)

var1=rep(1,n)
var2=(0.0001+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
var3=0.00001+mu.b
sigma.ini=sqrt(var3)
sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2

set.seed(1025)
X.s=rnorm(n,mu.t,sigma.t)

mu.est<-bayesmooth(X.s,sigma=sigma.t)
mu.est.sig=sigma.t*bayesmooth(X.s/sigma.t,sigma=rep(1,n))

mse(mu.est,mu.t)
mse(mu.est.sig,mu.t)
```

```{r fig.width=12, fig.height=12}
plot(mu.t,type='l')
lines(mu.est,col=2)
lines(mu.est.sig,col=4)

```

So dividing the data by its SD does change some of the underlying properties of the original intensity, and does not perform as well as one hopes.

Next we look at better ways to estimate the variance. One way would be to log transform the squared residuals so that they have constant variance. We also try using jash and vash instead of ash. For simplicity, we assume that the true mean is known.

```{r}

spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
n=2^12
t=1:n/n
mu.s=spike.f(t)
pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
mu.b = rep(0,n)
for(j in 1:length(pos)){
  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
}
dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
mu.dop=dop.f(t)
mu.sine=sin(20*t)
var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
var3=mu.b
var4=3.4*(2+mu.dop)
sigma.t.1=sqrt(var1)
sigma.t.2=sqrt(var2)
sigma.t.3=sqrt(var3)
sigma.t.4=sqrt(var4)
mu.t.1=rep(0,n)
mu.t.2=mu.sine

l2norm=function(x) sum(x^2)
mise=function(x,y) l2norm(x-y)/l2norm(y)
mse=function(x,y) mean((x-y)^2)

set.seed(327)
X.11=rnorm(n,mu.t.1,sigma.t.1)
set.seed(327)
X.12=rnorm(n,mu.t.1,sigma.t.2)
set.seed(327)
X.13=rnorm(n,mu.t.1,sigma.t.3)
set.seed(327)
X.14=rnorm(n,mu.t.1,sigma.t.4)
set.seed(327)
X.21=rnorm(n,mu.t.2,sigma.t.1)
set.seed(327)
X.22=rnorm(n,mu.t.2,sigma.t.2)
set.seed(327)
X.23=rnorm(n,mu.t.2,sigma.t.3)
set.seed(327)
X.24=rnorm(n,mu.t.2,sigma.t.4)

source("../simulation_1d_g/wip/bayesmooth_cur.R")
system.time(var.est.cur.11<-bayesmooth.cur(X.11,mu.t.1))
system.time(var.est.cur.12<-bayesmooth.cur(X.12,mu.t.1))
system.time(var.est.cur.13<-bayesmooth.cur(X.13,mu.t.1))
system.time(var.est.cur.14<-bayesmooth.cur(X.14,mu.t.1))
system.time(var.est.cur.21<-bayesmooth.cur(X.21,mu.t.2))
system.time(var.est.cur.22<-bayesmooth.cur(X.22,mu.t.2))
system.time(var.est.cur.23<-bayesmooth.cur(X.23,mu.t.2))
system.time(var.est.cur.24<-bayesmooth.cur(X.24,mu.t.2))

source("../simulation_1d_g/wip/bayesmooth_log.R")
system.time(var.est.log.11<-bayesmooth.log(X.11,mu.t.1,sigma.t.1))
system.time(var.est.log.12<-bayesmooth.log(X.12,mu.t.1,sigma.t.2))
system.time(var.est.log.13<-bayesmooth.log(X.13,mu.t.1,sigma.t.3))
system.time(var.est.log.14<-bayesmooth.log(X.14,mu.t.1,sigma.t.4))
system.time(var.est.log.21<-bayesmooth.log(X.21,mu.t.2,sigma.t.1))
system.time(var.est.log.22<-bayesmooth.log(X.22,mu.t.2,sigma.t.2))
system.time(var.est.log.23<-bayesmooth.log(X.23,mu.t.2,sigma.t.3))
system.time(var.est.log.24<-bayesmooth.log(X.24,mu.t.2,sigma.t.4))

source("../simulation_1d_g/wip/bayesmooth_vash.R")
system.time(var.est.vash.11<-bayesmooth.vash(X.11,mu.t.1))
system.time(var.est.vash.12<-bayesmooth.vash(X.12,mu.t.1))
system.time(var.est.vash.13<-bayesmooth.vash(X.13,mu.t.1))
system.time(var.est.vash.14<-bayesmooth.vash(X.14,mu.t.1))
system.time(var.est.vash.21<-bayesmooth.vash(X.21,mu.t.2))
system.time(var.est.vash.22<-bayesmooth.vash(X.22,mu.t.2))
system.time(var.est.vash.23<-bayesmooth.vash(X.23,mu.t.2))
system.time(var.est.vash.24<-bayesmooth.vash(X.24,mu.t.2))

source("../simulation_1d_g/wip/bayesmooth_jash.R")
system.time(var.est.jash.11<-bayesmooth.jash(X.11,mu.t.1))
system.time(var.est.jash.12<-bayesmooth.jash(X.12,mu.t.1))
system.time(var.est.jash.13<-bayesmooth.jash(X.13,mu.t.1))
system.time(var.est.jash.14<-bayesmooth.jash(X.14,mu.t.1))
system.time(var.est.jash.21<-bayesmooth.jash(X.21,mu.t.2))
system.time(var.est.jash.22<-bayesmooth.jash(X.22,mu.t.2))
system.time(var.est.jash.23<-bayesmooth.jash(X.23,mu.t.2))
system.time(var.est.jash.24<-bayesmooth.jash(X.24,mu.t.2))

matrix(c(mse(var.est.cur.11,sigma.t.1^2),
mse(var.est.cur.12,sigma.t.2^2),
mse(var.est.cur.13,sigma.t.3^2),
mse(var.est.cur.14,sigma.t.4^2),
mse(var.est.log.11,sigma.t.1^2),
mse(var.est.log.12,sigma.t.2^2),
mse(var.est.log.13,sigma.t.3^2),
mse(var.est.log.14,sigma.t.4^2),
mse(var.est.vash.11,sigma.t.1^2),
mse(var.est.vash.12,sigma.t.2^2),
mse(var.est.vash.13,sigma.t.3^2),
mse(var.est.vash.14,sigma.t.4^2),
mse(var.est.jash.11,sigma.t.1^2),
mse(var.est.jash.12,sigma.t.2^2),
mse(var.est.jash.13,sigma.t.3^2),
mse(var.est.jash.14,sigma.t.4^2)),
4,4)

matrix(c(mse(var.est.cur.21,sigma.t.1^2),
mse(var.est.cur.22,sigma.t.2^2),
mse(var.est.cur.23,sigma.t.3^2),
mse(var.est.cur.24,sigma.t.4^2),
mse(var.est.log.21,sigma.t.1^2),
mse(var.est.log.22,sigma.t.2^2),
mse(var.est.log.23,sigma.t.3^2),
mse(var.est.log.24,sigma.t.4^2),
mse(var.est.vash.21,sigma.t.1^2),
mse(var.est.vash.22,sigma.t.2^2),
mse(var.est.vash.23,sigma.t.3^2),
mse(var.est.vash.24,sigma.t.4^2),
mse(var.est.jash.21,sigma.t.1^2),
mse(var.est.jash.22,sigma.t.2^2),
mse(var.est.jash.23,sigma.t.3^2),
mse(var.est.jash.24,sigma.t.4^2)),
4,4)

```

### 2014-03-28 Rcode/bayesmooth_alt1.R

@@ -1,525 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wd_var.R")
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
-      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
[…]

### 2014-03-28 Rcode/bayesmooth_est_var.R

@@ -1,617 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wd_var.R")
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-rshiftx = function(x,sh){
-  L=length(x)
-  if(sh==0){
-     return(x)
-  }else{
-    return(c(x[(L-sh+1):L],x[-((L-sh+1):L)]))
-  }
-}
-lshiftmat = function(x,sh){
-  if(sh==0){
-    return(x)
-  }else{
-    return(cbind(x[,-(1:sh)],x[,1:sh]))
-  }
-}
-rshiftmat = function(x,sh){
-  if(sh==0){
-    return(x)
-  }else{
-    return(cbind(x[,(L-sh+1):L],x[,-((L-sh+1):L)]))
-  }
-}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
[…]

### 2014-03-28 Rcode/bayesmooth_new.R

@@ -1,527 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wd_var.R")
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
-      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
[…]

### 2014-03-28 Rcode/bayesmooth_test_var.R

@@ -1,291 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wd_var.R")
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
-      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
[…]

### 2014-03-28 gaus_data/delouille/mc.R

@@ -30,8 +30,8 @@ y.var.est.alt2=y.var.est.alt2[1:length(y)]
 
 plot(x,y,ylim=c(-150,100))
 lines(x,y.est,col=2)
-lines(x,y.est+2*sqrt(y.var.est),lty=2,col=3)
-lines(x,y.est-2*sqrt(y.var.est),lty=2,col=3)
+plot(x,y.var.est,type='l')
+
 
 
 

### 2014-03-28 gaus_data/treas_bill/analysis.R

@@ -11,6 +11,8 @@ x=sort(data[5:(length(data)-1)])
 y=y[order(data[5:(length(data)-1)])]
 
 plot(x,y)
+
+
 ####
 xmin=min(x)
 xmax=max(x)
@@ -24,25 +26,35 @@ for(i in 1:32){
   y.agg[i]=y[x>=x.seq.l[i]&x<x.seq.u[i]]
 }
 y.agg[1024]=y[x>=x.seq.l[1024]&x<=x.seq.u[1024]]
-####
+
 y.approx=approx(x,y,n=1024,method='constant',rule=2)$y
 x.approx=approx(x,y,n=1024,method='constant',rule=2)$x
 
 lines(x.approx,y.approx,col=2)
+y.est.approx=bayesmooth(y.approx)
+y.est.var.approx=bayesmooth(y.approx,v.est=TRUE)
 
-y.exp=c(y,y[length(y):(2*length(y)-2^11+1)])
+plot(x,y)
+lines(x.approx,y.est.approx,col=2)
+####
+
+x.mod=unique(x)
+y.mod=0
+for(i in 1:length(x.mod)){
+  y.mod[i]=median(y[x==x.mod[i]])
+}
+
+
+y.exp=c(y.mod,y.mod[length(y.mod):(2*length(y.mod)-2^10+1)])
 y.final=c(y.exp,y.exp[length(y.exp):1])
 
 y.est=bayesmooth(y.final)
 y.est.var=bayesmooth(y.final,v.est=TRUE)
 
 plot(x,y)
-lines(x,y.est[1:(length(data)-5)],col=2)
-plot(x,sqrt(y.est.var[1:(length(data)-5)]),type='l')
+lines(x.mod,y.est[1:(length(y.mod))],col=2)
 
-y.est.approx=bayesmooth(y.approx)
-y.est.var.approx=bayesmooth(y.approx,v.est=TRUE)
+plot(x.mod,sqrt(y.est.var[1:(length(y.mod))]),type='l')
 
-plot(x,y)
-lines(x.approx,y.est.approx,col=2)
+
 

### 2014-03-28 simulation_1d_g/method_comp_var_followup.R

@@ -104,111 +104,116 @@ var.est.asha2.dop.v2=matrix(0,100,n)
 var.est.asha2.dop.v3=matrix(0,100,n)
 var.est.asha2.dop.v4=matrix(0,100,n)
 
+
+
 for(i in 1:100){
-var.est.ash.cons.v1[i,]=bayesmooth(sim.m.cons.v1[i,],v.est=TRUE)
-var.est.ash.cons.v2[i,]=bayesmooth(sim.m.cons.v2[i,],v.est=TRUE)
-var.est.ash.cons.v3[i,]=bayesmooth(sim.m.cons.v3[i,],v.est=TRUE)
-var.est.ash.cons.v4[i,]=bayesmooth(sim.m.cons.v4[i,],v.est=TRUE)
+var.est.ash.cons.v1[i,]=bayesmooth(sim.m.cons.v1[i,],v.est=TRUE,weight=0)
+var.est.ash.cons.v2[i,]=bayesmooth(sim.m.cons.v2[i,],v.est=TRUE,weight=0)
+var.est.ash.cons.v3[i,]=bayesmooth(sim.m.cons.v3[i,],v.est=TRUE,weight=0)
+var.est.ash.cons.v4[i,]=bayesmooth(sim.m.cons.v4[i,],v.est=TRUE,weight=0)
 
-var.est.ash.sine.v1[i,]=bayesmooth(sim.m.sine.v1[i,],v.est=TRUE)
-var.est.ash.sine.v2[i,]=bayesmooth(sim.m.sine.v2[i,],v.est=TRUE)
-var.est.ash.sine.v3[i,]=bayesmooth(sim.m.sine.v3[i,],v.est=TRUE)
-var.est.ash.sine.v4[i,]=bayesmooth(sim.m.sine.v4[i,],v.est=TRUE)
+var.est.ash.sine.v1[i,]=bayesmooth(sim.m.sine.v1[i,],v.est=TRUE,weight=0)
+var.est.ash.sine.v2[i,]=bayesmooth(sim.m.sine.v2[i,],v.est=TRUE,weight=0)
+var.est.ash.sine.v3[i,]=bayesmooth(sim.m.sine.v3[i,],v.est=TRUE,weight=0)
+var.est.ash.sine.v4[i,]=bayesmooth(sim.m.sine.v4[i,],v.est=TRUE,weight=0)
 
[…]

### 2014-03-28 simulation_1d_g/tests/gaussian_test.R

@@ -1,13 +1,7 @@
 spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
 n=1024
 t=1:n/n
-mu.s=spike.f(1:n/n)
-#sigma.t=seq(2,10,length.out=n)
-sigma.t=rep(0.17,n)
-
-mu.s0=2
-set.seed(425)
-X.s=rnorm(n,mu.s0*(mu.s),sigma.t)
+mu.s=spike.f(t)
 
 pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
 hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
@@ -59,19 +53,19 @@ mise=function(x,y) 10000*mean(apply(x-rep(1,100)%o%y,1,l2norm)/l2norm(y))
 
 
 
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_alt.R"))
 source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
 source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_test.R"))
 
+source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/ti_thresh.R"))
 
 
 
 
-n=1024
-t=1:n/n
-mu.t=(1+mu.s)/5
+
+
+#mu.t=(1+mu.s)/5
 #mu.t=(1+mu.b)/5
-#mu.t=(1+mu.blk)/5
+mu.t=(1+mu.blk)/5
 #mu.t=(1+mu.ang)/5
 #mu.t=(1+mu.dop)/5
 
@@ -95,21 +89,33 @@ X.s=matrix(rnorm(100*n,mu.t,sigma.t),nrow=100,byrow=TRUE)
 
 ###single
 system.time(mu.est<-bayesmooth(X.s))
+system.time(mu.est.test<-bayesmooth.test(X.s))
 system.time(mu.est.sd<-bayesmooth(X.s/sigma.t,sigma=rep(1,n)))
-system.time(mu.est.alt<-bayesmooth.alt(X.s))
[…]

### 2014-03-28 simulation_1d_g/wip/bayesmooth_jash.R

@@ -1,0 +1,440 @@
+source("../Rcode/wd_var.R")
+source("../Rcode/jash.R")
+
+library(wavethresh)
+require(ashr)
+require(Rcpp)
+require(inline)
+
+
+#interleave two vectors
+interleave=function(x,y){
+  return(as.vector(rbind(x,y)))
+}
+
+
+#shift a vector right and left respectively
+rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
+lshift = function(x){return(c(x[-1],x[1]))}
+
+
+#The following produces both a TItable,
+#and a "parent" table whose pairwise comparisons would be used to create a TI table
+#So, for example, in the ith row, elements 1, 2 would be the parents of the
+#first element in the (i+1)the row of the TI table
+# INPUT: sig, an n vector of Poisson counts at n locations
+# OUTPUT: a list, with elements
+# TItable - the usual TI table
+# parent - the parent values used to make the TI table
+titable=function(sig){
+  n = length(sig)
+  J = log2(n)
+  
+# Create decomposition table of signal, using pairwise sums,
+# keeping just the values that are *not* redundant under the
+# shift-invariant scheme.  This is very similar to TI-tables
+# in Donoho and Coifman's TI-denoising framework.
+  dmat = matrix(0, nrow=J+1, ncol=n)
+  ddmat = matrix(0, nrow=J+1, ncol=n)
+  dmat[1,] = sig
+  ddmat[1,] = sig
+
+  #dmat[1,] = as.matrix(sig)  
+  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
+  
+  for(D in 0:(J-1)){
+    nD = 2^(J-D); 
+    nDo2 = nD/2;
+    twonD = 2*nD;
+    for(l in 0:(2^D-1)){
+      ind = (l*nD+1):((l+1)*nD)
+      #ind2 = (l*twonD+1):((l+1)*twonD)
+      x = dmat[D+1,ind]
+      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
+      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
+      rx = rshift(x);
+      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
[…]

### 2014-03-28 simulation_1d_g/wip/test_jash.R

@@ -1,0 +1,49 @@
+spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
+n=2^12
+t=1:n/n
+mu.s=spike.f(t)
+pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
+hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
+wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
+mu.b = rep(0,n)
+for(j in 1:length(pos)){
+  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
+}
+dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
+mu.dop=dop.f(t)
+#mu.sine=3/4*sin(40*pi*t)
+mu.sine=sin(20*t)
+var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
+var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
+var4=3.4*(2+mu.dop)
+var3=mu.b
+var5=(t-0.5)^2+0.5
+var6=exp(-100*(t-0.5)^2)
+var7=0.5+1.5*mu.s
+sigma.t=sqrt(var1)
+#sigma.t=seq(2,10,length.out=n)
+#sigma.t=rep(2,n)
+l2norm=function(x) sum(x^2)
+mise=function(x,y) l2norm(x-y)/l2norm(y)
+mse=function(x,y) mean((x-y)^2)
+mu.s0=100
+set.seed(1121)
+mu.t=rep(0,n)
+X.s=rnorm(n,0,sigma.t)
+
+source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
[…]

### 2014-03-28 simulation_g/sim.R

@@ -91,7 +91,7 @@ g=c(rep(0,10),rep(1,10))
 
 mse=function(x,y) mean((x-y)^2)
 
-write.table(X,"sim_data.txt",col.names=FALSE,row.names=FALSE)
+write.table(X,"../simulation_g/sim_data.txt",col.names=FALSE,row.names=FALSE)
 
 system.time(res1<-multiseq.gaus(X,g,gridmult=2))
 system.time(res2<-multiseq.gaus(X,g,gridmult=0))

### 2014-04-15 intro/intro.Rmd
some changes

@@
 pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
+hgt = c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
 wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
@@
 
-var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
-var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
-var3=mu.b
-var4=3.4*(2+mu.dop)
+var1.ini=((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
+var1=var1.ini/sqrt(var(var1.ini))
+var2.ini=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))
+var2=var2.ini/sqrt(var(var2.ini))
+var3=mu.b/sqrt(var(mu.b))
+var4=(mu.dop+2)/sqrt(var(mu.dop))
 

### 2014-04-15 tests/tests.Rmd
some changes

@@
 source(file.path("../Rcode/bayesmooth.R"))
+
+l2norm=function(x) sum(x^2)
+mise=function(x,y) l2norm(x-y)/l2norm(y)
+mse=function(x,y) mean((x-y)^2)
+
 spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
 
+n=1024
+t=1:n/n
+
 pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
+hgt = c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
 wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
@@
 }
-
-n=1024
-t=1:n/n
 
@@
 mu.t.2=mu.sine
-
-l2norm=function(x) sum(x^2)
-mise=function(x,y) l2norm(x-y)/l2norm(y)
-mse=function(x,y) mean((x-y)^2)
 

### 2015-04-23 paper/draft_0.tex
small change

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb,amsfonts,fullpage,verbatim,bm,graphicx,enumerate,epstopdf,lscape,enumitem}
\usepackage[titletoc,title]{appendix}
\usepackage[dvipsnames,usenames]{color}
\usepackage[pdftex,pagebackref,colorlinks=true,pdfpagemode=UseNone,urlcolor=blue,linkcolor=blue,citecolor=BrickRed,pdfstartview=FitH,plainpages=true]{hyperref}
\usepackage[top=1.15in,bottom=1.15in,left=1.25in,right=1.25in,letterpaper]{geometry}
\usepackage[font=scriptsize]{caption}

\def\CC{\mathbb{C}}
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}
\def\PP{\mathbb{P}}
\def\EE{\mathbb{E}}
\def\II{\mathbb{I}}

\newcommand{\Ga}{\alpha}
\newcommand{\Gb}{\beta}
\newcommand{\Gg}{\gamma}     \newcommand{\GG}{\Gamma}
\newcommand{\Gd}{\delta}     \newcommand{\GD}{\Delta}
\newcommand{\Ge}{\epsilon}
\newcommand{\Gf}{\phi}       \newcommand{\GF}{\Phi}
\newcommand{\Gh}{\theta}
\newcommand{\Gi}{\iota}
\newcommand{\Gk}{\kappa}
\newcommand{\Gl}{\lambda}    \newcommand{\GL}{\Lambda}
\newcommand{\Go}{\omega}     \newcommand{\GO}{\Omega}
\newcommand{\Gs}{\sigma}     \newcommand{\GS}{\Sigma}
\newcommand{\Gt}{\tau}
\newcommand{\Gz}{\zeta}
\newcommand{\s}{\sigma}
\newcommand{\tr}{\triangle}

\begin{document}

\title{\textbf{Title}}
\date{}
\maketitle

\section{Abstract}
\section{Introduction}
In recent years, the use of various shrinkage and thresholding procedures has become ever more popular in a variety of applications where sparsity is a desirable notion. Here the term ``sparsity'' is loosely defined in the sense that it also includes the case where there are many near-zero (as opposed to exactly zero) terms, as shrinkage procedures often produce. The most prominent usage of such procedures appear in multiresolution denoising analyses such as wavelets, where sparsity in a transformed domain often corresponds to smoothness in the data space [references]. Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are usually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references]. In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its usage in two key areas of univariate wavelet denoising.\bigskip\\
Wavelet estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994). Not only are wavelet methods locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, but they are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001]. While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al. (2001) has shown that various Bayesian shrinkage methods can perform just as well, if not better than, thresholding methods in finite samples where performance is measured by mean squared error (MSE). However, many Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications. Furthermore, it is a nontrivial task to extend the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we will now describe.\bigskip\\
The first problem relates to the frequently encountered Gaussian case. Although the theory for mean estimation with homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], the existing methods for variance estimation with heteroskedastic errors have been far and few between. Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators. More recently Cai \& Wang (2008) also proposed a wavelet thresholding approach using first order differences. The problem of joint mean and variance estimation as described is generally a nontrivial one, and we will demonstrate how we can make use of ASH to tackle this problem.\bigskip\\
The second task is to denoise a Poisson distributed signal. This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest. This problem is particularly interesting in the sense that there are many different ways to perform signal recovery. Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by noting that the variance of a Poisson count is equal to its mean. Kolaczyk (1997, 1999a) derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d. Gaussian case. Multiscale analysis using recursive dyadic partitions within a Bayesian framework has also been developed by Kolaczyk (1999) to make use of a particular form of likelihood factorization. We will discuss the pros and cons of these and some other methods in the simulation section, and further compare them to our method which uses ASH as the main shrinkage procedure in a Bayesian framework similar to that of Kolaczyk (1999b). \bigskip\\
Both these problemss are generally harder to deal with than the classical problem of i.i.d. Gaussian errors, and usually requires some work in extending the ideas from methods aimed at the latter task. Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage. \bigskip\\
\textbf{describe ash}\bigskip\\
The flexibility and computational efficiency of this shrinkage method is immediately obvious. Gaussian mixture priors can effectively approximate any unimodal distribution, allowing us to apply this single shrinkage procedure to the two problems we will be focusing on. At the same time, we can enhance the computational speed of the the entire signal denoising problem via likelihood approximations, which will be discussed in detail in the next section. For an in-depth understanding of the motivations and applications of ASH, see Stephens (??). With the main shrinkage method accounted for, we will now proceed to explore the two aforementiond problems in detail.
\section{Method}
\textbf{Note: the notation should be consistent in the two applications}
\subsection{Gaussian denoising with heteroskedastic errors}
We first consider the application of ASH in the context of the nonparametric regression model with heteroskedastic (and independent) Gaussian errors that are spatially structured. Specifically, consider the model
\begin{eqnarray}\label{eq:1d gaussian model}
Y(t)=\mu(t)+\Ge(t)
\end{eqnarray}
for $t=1,...,T$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve sampled on an equally spaced grid, and $\Ge(t)$ are independent $N(0,\s_t^2)$ noise. To better understand and motivate our method, we first give a brief introduction to classical Bayesian denoising techniques in the wavelet literature.\bigskip\\
In the case of i.i.d Gaussian noise, given an observation vector $\bm{Y}$ of length $T$ (where $T=2^J$ for some positive integer $J$) and an orthogonal $T\times T$ matrix representing the orthonormal wavelet basis chosen, we have that the wavelet coefficients $\bm{d}$ are given by
\begin{eqnarray}
\bm{d}=W\bm{Y}
\end{eqnarray}
where $\mathbb{V}(Y)=\s^2I$. Hence, we can easily see that
\begin{eqnarray}\label{eq:waveletcoef}
\bm{d}\sim N_T(\bm{\Ga},\s^2I)
\end{eqnarray}
where $\bm{\Ga}=W\mathbb{E}(\bm{Y})$. This implies that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods for $\Ga(t)$, $t=1,...,T$, since a diagonal covariance matrix for a multivariate Gaussian random vector implies independence of the components in the vector. As such, a natural and computationally convenient approach is to set independent priors on $\Ga(t)$ as a form of ``shrinkage''. Although we have adopted the priors from ASH in our method, the usual choice for the prior is a ``spike and slab'' prior, ie
\begin{eqnarray}
\Ga_{jk}=\pi_0\Gd_0+(1-\pi_0)N(0,\s_j^2)
\end{eqnarray}
where $\pi_0$ and $\s_j^2$ are hyperparameters. Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,log_2(T)$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$. Given the independent prior and factorized likelihoods for $\bm{\Ga}$, one can then easily obtain the posterior distribution of each $\Ga_{jk}$ since they will also be independent. The posterior mean or median $\hat{\bm{\Ga}}$ is used to estimate the true $\bm{\mu}$ by applying the inverse wavelet transform on $\hat{\bm{\Ga}}$. One could also construct credible bands using the posterior variances.\bigskip\\
This now sets the stage for our method. One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize. If the true variances were known, one could obviously write out the full likelihood and proceed to compute the posterior mean/median using some specified prior. However, this would be computationally cumbersome, and may not be feasible when extended to multiple signals or higher dimensions. A suitable prior might also be difficult to find. As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).\bigskip\\
To describe our approach in more detail, first assume that the true variance function is known, and that the true mean function is given by $\bm{\mu}=(\mu(1),...,\mu(T))$, where $T=2^J$ for some positive integer $J$. Hence
\begin{eqnarray}
\bm{Y}\sim N_T(\bm{\mu},\Lambda)
\end{eqnarray}
where $\Lambda=diag(\Gl(1),...,\Gl(T))$ is a diagonal matrix. Now let $W$ be the matrix associated with the NDWT for the Haar wavelet basis, so that
\begin{eqnarray}
\bm{d}\sim N_T(\bm{\Ga},\tilde{\Lambda})
\end{eqnarray}
where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Lambda}=W\Lambda W^T$. By treating the likelihood for $\bm{\Ga}$ as if it were independent, we can write the likelihood as follows (using the double index mentioned above):
\begin{eqnarray}\label{eq:likelihood}
L(\bm{\Ga}|\bm{d})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(d_{jk}|\Ga_{jk})
\end{eqnarray}
where $P(d_{jk}|\Ga_{jk})=\phi(d_{jk};\Ga_{jk},\tilde{\Lambda}_{(jk,jk)})$. Note that there are $T$ coefficients at each resolution level instead of $2^j$ for resolution $j$ because we are using the non-decimated wavelet transform (NDWT) instead of the standard wavelet transform. Here $\phi$ is the Gaussian density function. Since $\Lambda$ is diagonal, it is easy to see that $\tilde{\Lambda}_{(jk,jk)}=\sum_{i=1}^T \Lambda_{ii}W_{jk,i}^2$. In our method, we use ASH to assign independent priors to $\Ga_{jk}$:
\begin{eqnarray}\label{eq:ashprior}
\Ga_{jk}=\sum_{i=1}^m \pi_i^{(j)} N(0,(\s_i^{(j)})^2)
\end{eqnarray}
with $\sum_i \pi_i^{(j)}=1$, for $0=1,...,J$. Here $\pi_i^{(j)}$ and $\s_i^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level. %ASH also allows us to estimate the $\pi_i$'s via a maximum likelihood approach and fix the $\s_i$'s by using a grid of values. This particular choice of prior specification is extremely flexible, being able to approximate any symmetrical zero-centered distribution, as well as allowing for a relatively easy estimation of the hyperparameters through empirical Bayes. See ASH for more details regarding this choice of prior (?)
Since the prior is a Gaussian mixture and the likelihoods are Gaussian, the posterior is also a Gaussian mixture, with closed form expressions for the posterior mean and variance of $\Ga_{jk}$. Here we use ASH to perform posterior inference. We estimate $\Ga_{00}$ using the corresponding scaling coefficient, which seems intuitively appealing. Finally, we can obtain an estimate of $\mu$ by using the average basis inverse, which is essentially an average of the inverse wavelet transforms for every shift of the data (see Coifman \& Donoho (1995)) since we are using the NDWT. Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, which takes only $T\log(T)$ time.\bigskip\\
While we assumed that the true variances are known for mean estimation, the problem of variance estimation itself is a non-trivial one. Here we make the reasonable assumption that the variance function is also spatially structured, in addition to the mean function. The approach we took is similar in spirit to that of Cai \& Wang (2008), since we make use of wavelet decomposition as well. However, while they use first order differences, we look at the squared residuals. As such, we need a reasonably accurate estimator of the mean function in order to form sensible residuals. At the same time, estimating the mean function in the presence of heteroskedasticity requires that we know the variance function up to some degree of accuracy, and so this process is an iterative one. A natural initial estimate would be the square of first order differences between adjacent points, as discussed in previous variance estimation papers (eg Cai \& Wang (2008)). This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough. Furthermore, since the estimator is approximately $\chi^2$ distributed, it is right skewed and thus overestimates the true variance in general. This results in smoother estimates of the mean function, which is generally acceptable for an initial estimate. Following that, we estimate the mean function by treating the variance estimates as if they were the truth, and re-estimate the variance function using squared residuals. Although this iterative procedure (using squared residuals) could go on for a long time, and convergence is difficult to prove, we found via simulations that two cycles is usually sufficient to produce relatively accurate estimates. Hence, our approach can be described in three steps:
\begin{enumerate}
\item Using squared first order differences as our estimates of the unknown variance function, we estimate the mean function as if the variance function was known (see the above procedure for the case when the variance function is known)
\item Given the estimate of the mean function, take squared residuals and treat those as ``observations'' for the variance function. Next, we project them into wavelet space and apply some form of shrinkage to the wavelet coefficients, before projecting them back into data space to obtain an estimate of the variance function.
\item Repeat steps (1)-(2) once to obtain the final estimates of the mean and variance functions respectively.
\end{enumerate}
In the first step, the initial variance estimates are defined by
\begin{eqnarray}
\hat{\s}_i^2=\frac{1}{2}\left(\sum_{i=1}^T(Y_i-Y_{i-1})^2+\sum_{i=1}^T(Y_i-Y_{i+1})^2\right)
\end{eqnarray}
where $Y_0\equiv Y_T$ and $Y_{T+1}\equiv Y_1$, since wavelet methods typically assume that the function is periodic. Hence, the missing element to complete the description of our method would be the shrinkage of the wavelet coefficients for the variance ``observations'' in step (2) (and similarly in step (3)) above. This is a difficult problem in general, so we simplify the task by using Gaussian approximations to the likelihoods and set independent mixture Gaussian priors. Of course, better likelihoods and priors could be used that reflect the skewness in the distributions of the ``observations'', but we found that a normal approximation works reasonably well (especially for smoother variance functions), and has the key advantage of being easy and fast to implement.\bigskip\\
To describe the shrinkages in steps (2) (and (3)) in more detail, we use
\begin{eqnarray}\label{eq:varobs1}
Z^2(t)=(Y(t)-\hat{\mu}(t))^2
\end{eqnarray}
as our ``observations''. As long as the mean function estimate $\hat{\mu}(t)$ is reasonably accurate, we have that $\mathbb{E}(Z^2(t))\approx\s^2(t)$, so that $Z(t)$ is approximately unbiased for the true variance at point $t$. At this point we essentially have a mean function estimation problem, with variances that are distributed more-or-less as a $\chi^2$ distribution squared. We then approximate this likelihood with a Gaussian likelihood as previously mentioned, and set a Gaussian mixture prior as in ASH. The variance estimation process is then very similar to one for mean estimation as described above, with a few extra details. The full procedure is outlined in Appendix \ref{app:var estimation}. \bigskip\\
\subsection{Poisson denoising}
Next we turn to another popular nonparametric regression problem and demonstrate how we could make use of ASH. Specifically, we assume an underlying signal $\Gl_k$, $k=1,...,n$ with $n=2^J$ for some positive integer $J$. Further assume that each data point $Y_k$, $k=1,...,n$ is realized from a Poisson distribution with mean $\Gl_k$ ie. $Y_k=Pois(\Gl_k)$. Our goal is to recover the true signal $\Gl_k$ as accurately as possible, given $Y_k$. To make our approach easier to understand and relate it to wavelet-based methods, we first summarize the data in a recursive manner (see Kolaczyk (1999) and Nowak (1998) (how to reference technical report?)):
\begin{eqnarray}Y_{Jl}\equiv Y_l\end{eqnarray}
for $l=1,...,n$, and
\begin{eqnarray}Y_{sl}=Y_{s+1,2l}+Y_{s+1,2l+1}\end{eqnarray}
for scale $s=0,...,J-1$ and location $l=0,...,2^s-1$, so that we are looking at the sum of adjacent pairs of ``points'' as we move to coarser resolutions, where a point is already itself a sum of the true data points. Another way to define the $Y's$ is
\begin{eqnarray}Y_{sl}=\sum_{i=l2^{J-s}+1}^{(l+1)2^{J-s}}Y_i\end{eqnarray}
for $s=0,...,J$ and $l=0,...,2^s-1$.
Further define the following:
\begin{eqnarray}\Gl_{Jl}\equiv \Gl_l\end{eqnarray}
for $l=1,...,n$, and
\begin{eqnarray}\Gl_{sl}=\Gl_{s+1,2l}+\Gl_{s+1,2l+1}\end{eqnarray}
for $s=0,...,J-1$ and $l=0,...,2^s-1$. Furthermore, define
\begin{eqnarray}\label{eq:poisson wc}\Ga_{sl}=\log(\Gl_{s+1,2l})-\log(\Gl_{s+1,2l+1})\\\end{eqnarray}
for $s=0,...,J-1$ and $l=0,...,2^s-1$. The ${\Ga}$'s defined this way is extremely similar to the (true) Haar wavelet coefficients, which forms the basis of our approach. Using this recursive representation, we can see that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods, where $\bm{\Ga}$ is the vector of all the $\Ga_{sl}$'s. To be specific, we have
\begin{eqnarray}
L(\bm{\Ga}|\mathbf{Y})&=&P(\mathbf{Y}|\bm{\Ga})\\
&=&P(Y_{0,0}|\Gl_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}P(Y_{j+1,2k}|Y_{j,k},\Ga_{j,k})\\
&=&L(\Gl_{0,0}|Y_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}L(\Ga_{j,k}|Y_{j+1,2k},Y_{j,k})
\end{eqnarray}
where the factorization is due to the recursive definition above. Note that $Y_{00}|\Gl_{00}\sim \textrm{Pois}(\Gl_{00})$. Now for any give $s,l$, $Y_{sl}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable. Hence
\[Y_{s+1,2l}|Y_{sl},\Ga_{sl}\sim \textrm{Bin}({Y_{sl},\frac{1}{1+e^{-\Ga_{sl}}}\equiv\frac{\Gl_{s+1,2l}}{\Gl_{sl}}})\]
Whereas Kolaczyk (1999) sets a conjugate prior (which is a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{s+1,2l}}{\Gl_{sl}}$ and uses a Binomial likelihood, we felt that the two-component mixture prior is too inflexible. As such, we work with the parameters $\Ga_{sl}$ as defined in \eqref{eq:poisson wc} and use ASH to set Gaussian mixture priors to the Gaussian-approximated logit-Binomial (is there such a thing?) likelihoods. Furthermore, these parameters can be more easily connected to wavelet coefficients since they consist of (log) differences rather than ratios. For more details regarding Gaussian approximations to the likelihoods for the $\Ga$'s, see Appendix \ref{app:likelihood approx}. Finally, to reconstruct the signal in the original space using the posterior distribution of the $\Ga$'s (which are in the logit space), we make use of the Delta method. For full details on the reconstruction process as well as the Delta method, see Appendix \ref{app:reconstruction}.
\section{Simulations}
\textbf{Note: after simulation results also describe the method to assess performance of methods that denoise Poisson distributed data without knowing the underlying truth}
\section{Application to real datasets}
In this section we apply the Gaussian denoising technique to two example datasets from different fields, and run the Poisson denoising method on a sequencing dataset. Whereas the application to the sequencing dataset is straightforward, the other two datasets require some pre-processing due to the presence of repeated observations and the fact that the number of sample points is not a power of two. To deal with these complications, we first use the median of the repeated observations at their respective sample points (see eg Delouille et al. (2004)). Next, we mirror the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points. This ensures that the number of data points in the new ``dataset'' is a power of two, and the mean curve would be continuous at the right edge. To further ensure that the input to the Gaussian denoising method is periodic, we then reflect the new dataset about the right edge and use this as the final input. Finally, we extract the first $n$ points from the output of our denoising technique as an estimate of the true mean function. Although the data points are not evenly spaced (in contrast to the requirements of standard wavelet methods), we took the simplest approach and applied the method treating the observations as if they were evenly spaced. This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (see Sardy et al. (1999)). 
\subsection{Motorcycle Acceleration Data}
Here we apply our Gaussian denoising method to a classical dataset from Silverman (1985). The observations are measurements of head acceleration simulated motorcycle accidents in order to test the effectiveness of crash helmets. The response variable here is acceleration in $g$, and the predictor variable is time in milliseconds ($ms$). Note that the observations are not evenly spaced here, and there may be multiple observations at one point. These issues were dealt with as per discussion above. 
\subsection{Three-month Treasury Bill Yields}
The second dataset involves the yields of three-month Treasure Bill from secondary market rates. There are 1735 weekly observations, starting from 5 January 1962 and ending on 31 March 1995. This dataset has been analyzed extensively by others, including Andersen \& Lund (1997), Gallant \& Tauchen (1997) and Fan \& Yao (1998). We preprocess the data following the procedure described in Fan \& Yao (1998):
\subsection{ChIP-Seq Data}
Since the original goal of the Poisson denoising procedure is smoothing next generation sequencing data that is common in the field of genetics, we apply our method to an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute. We specifically looked at reads from ChIP sequencing measuring transcription factor binding in two different cell types, with two samples for each cell type. Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1. Since we are looking mainly at univariate denoising here, we run our method on each sample separately to produce the following plots.
\section{Discussion}
In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have demonstrated its flexibility by utilizing it as part of two wavelet denoising techniques. Both the applications discussed here are not often seen in the wavelet literature because they are typically harder to deal with than the case for i.i.d. Gaussian noise. Nevertheless, they are interesting problems in their own right, as many real world datasets do not satisfy the standard assumptions of having i.i.d. Gaussian noise. In the Gaussian case, our software allows users to easily obtain point estimates for both the mean function and the variance function, the latter of which can be used to provide frequentist confidence intervals for other forms of mean estimation (to the best of our knowledge, there is no readily available software which implements both mean and variance estimation in the wavelet literature). Furthermore, approximate credible intervals are also computed for both the mean and the variance to provide uncertainty estimates. We have also tested our method and found that it is relatively robust to simple forms of autocorrelation between the errors so long as it is not too strong (eg AR? with autocorrelation ?).  In the case of Poisson regression, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods by utilizing ASH as the shrinkage procedure, which allows for more flexibility and accuracy. Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm, due to the fact that we do not have to perform external cycle-spinning. In addition, we have proposed a new procedure to assess the performance of a given method on real datasets under the assumption that they follow a Poisson distribution, without knowing the underlying truth. In both of the applications, one major advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used, whereas the so-called primary resolution level in almost all of the other wavelet-based methods actually affects their performance substantially, depending on the underlying mean and/or variance function. Hence, our fully adaptive procedures allow users to easily apply them to any given dataset.\bigskip\\
We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from standard wavelet literature in terms of pointwise accuracy (MSE in this case). Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussians used indicate that our methods are computationally fast, making them superior to many other Bayesian wavelet techniques. Note that we have not directly compared the computation times of our methods with all the methods listed in the simulation studies, due to the fact that most standard wavelet techniques are part of a package in Matlab whereas our method is coded entirely in R. However, the methods that we did compare against in R indicate that our methods are only slightly slower than the non-Bayesian methods and much faster than the Bayesian ones. On the other hand, since ASH is computationally efficient, we have chosen to sacrifice speed for accuracy in the wavelet transformation stage by using the NDWT (which is $O(n\log n)$), while most standard wavelet methods use the DWT( which is $O(\log n)$). For a more detailed summary of computation times see ??? (maybe?).\bigskip\\
Although we have only focused on one-dimensional univariate denoising here (effectively regression problems with only one covariate), our methods can be extended to various scenarios. Even in one dimension, our methods could be extended to the case with multiple samples, otherwise known as regression analysis of functional data (See Morris ??). Instead of dealing with a vector of observations, we could perform regression analysis on a matrix of observations, each row of which would encapsulate a sample with observations that are temporally or spatially structured. While Morris (2006) proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category. Our work potentially allows for differing variance structures amongst all the samples, thereby imposing even less restrictions on the assumptions behind the regression model. In the simplest case, we could potentially obtain spatially structured differences between the samples by including a single covariate into the regression model that categorizes each sample. We have already developed methods for this scenario for both the Gaussian and the Poisson data discussed in this paper. The Poisson model is extremely useful for discovering regions in sequencing reads where differential expression is present between say, different tissues, as per our sequencing example in the previous section. The Gaussian model could also potentially be used in...(???).\bigskip\\
With some work, our methods could also be extended to higher dimensions which have a wider range of applications. For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in Nowak (1998) (again, reference technical report). However, recent advances in image denoising problems have shown that wavelet transformations might not be the most ideal due to the presence of smooth curves in many images such as photographs. We could thus attempt to use ASH as a shrinkage procedure in other types of transformations such as curvelets, and that could be a potential direction for future work. 
\section{Reference}

\begin{appendices}
\section{}\label{app:var estimation}\bigskip
\textbf{Variance estimation for Gaussian denoising}\bigskip\\
With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$. Note that $\mathbb{E}(\bm{\Gd})\approx(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$. As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
\begin{eqnarray}
L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
\end{eqnarray}
However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions. As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
\begin{eqnarray}
P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
\end{eqnarray}
so that
\begin{eqnarray}\label{eq:gaus approx}
L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
\end{eqnarray}
where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients. Since these variances are unknown, we estimate them from the data and then proceed to treat them as known. More specifically, since $Z(t)\approx N(0,\s^2(t))$, we have that
\begin{eqnarray}
&\mathbb{E}(Z^4(t))\approx 3\s^4\notag\\
\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z^2(t))\approx 2\s^4
\end{eqnarray}
and so we simply use $\frac{2}{3}Z^4(t)$ as an unbiased estimator for $\mathbb{V}(Z^2(t))$. It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{i=1}^T \frac{2}{3}Z^4(i)W_{jk,i}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$. Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels. This is likely due to the fact that the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points). One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH).\bigskip\\
Now that we have the likelihood, the specification of the prior is exactly the same as in \eqref{eq:ashprior}: independent Gaussian mixtures for every detail coefficient. ASH then provides us with the posterior mean, which will be used to obtain the final estimate of the variance function via the average basis inverse across all the shifts .\bigskip\\
\section{}\label{app:likelihood approx}\bigskip
\textbf{Gaussian Approximation to logit-Binomial Likelihood for Poisson denoising}\bigskip\\
Dropping the subscripts, we want to use a Gaussian likelihood to approximate $L(\Ga)$. Since the true variance of $\hat{\Ga}$ is unknown, the most natural approximation would be $\phi(\Ga;\hat{\Ga},se(\hat{\Ga})^2)$. This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
We next consider consider appropriate estimators for the parameters ie. $\hat{\Ga}$ and $se(\hat{\Ga})$. The obvious choice for $\hat{\Ga}$ and $se(\hat{\Ga})$ would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by 
\begin{eqnarray}
\hat{\Ga}_{MLE}=\log(S/F)&\ \ \ S=0,...,n\\
se(\hat{\Ga}_{MLE})=\sqrt{SF/n}&\ \ \ S=0,...,n
\end{eqnarray}
where $S$ is the number of successes in the binomial setup, and $F=n-S$ is the number of failures (in our case the even locations would be successes and odd locations failures). The MLE has one notable drawback however, in that it cannot deal well with extreme cases. This would in turn affect the normal approximation in a non-negligible way. To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie. when we have $\hat{p}=0$ or $n$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), while at the same time ensuring that $\hat{\Ga}$ is approximately unbiased for $\Ga$ (so that moment matching still makes sense), we propose a mix of Berkson's estimator and Tukey's estimator (see Gart \& Zweifel (1967)). Specifically, our final estimators for $\Ga$ and its standard error are given by
\begin{eqnarray}\label{eq:pseudoMLE1}
&&\hat{\Ga}=\left\{
\begin{array}{lll}
\log\{(S+0.5)/(F+0.5)\}-0.5&\ \ \ S=0\\
\log\{S/F\}&\ \ \ S=1,2,...,n-1\\
\log\{(S+0.5)/(F+0.5)\}+0.5&\ \ \ S=n\\
\end{array}
\right.\\ \label{eq:pseudoMLE1se}
&&se(\hat{\Ga})=\sqrt{V^*(\hat{\Ga})-\frac{1}{2}\{V_3(\hat{\Ga})\}^2\left\{V_3(\hat{\Ga})-\frac{4}{n}\right\}}
\end{eqnarray}
where
\begin{eqnarray}
&&V_3(\hat{\Ga})=\frac{n+1}{n}\left(\frac{1}{S+1}+\frac{1}{F+1}\right)\ \ \ S=0,...,n\\
\label{eq:pseudoMLE2}&&V^*(\hat{\Ga})=V_3(\hat{\Ga})\left\{1-\frac{2}{n}+\frac{V_3(\hat{\Ga})}{2}\right\}
\end{eqnarray}
This variance estimator is $V^{\ast\ast}$ from p. 182 of Gart \& Zweifel (1967), and is chosen because it is less biased (when $n$ is small) as compared to the asymptotic variance of the MLE (see Gart \& Zweifel (1967)). The other two variance estimators from Gart \& Zweifel (1967), $V_1^{++}$ and $V^{++}$, were also used in simulations and gave similar  results, but $V^{\ast\ast}$ was chosen for its simplicity.\bigskip\\

\section{}\label{app:reconstruction}\bigskip
\textbf{Signal reconstruction for Poisson denoising}\bigskip\\
Given the posterior means and variances of the $\Ga$'s from ASH, the first step to reconstructing the signal is to find the posterior means of $p_{sl}:=\frac{\Gl_{s+1,2l}}{\Gl_{sl}}$ and $q_{sl}:=\frac{\Gl_{s+1,2l+1}}{\Gl_{sl}}$ (for $s=0,...,J-1$ and $l=0,...,2^s-1$). Specifically, for each $s$ and $l$, we wish to find
\begin{eqnarray}\label{eq:pfromwc1}
&&E(p_{sl})\equiv E\left(\frac{e^{\Ga_{sl}}}{1+e^{\Ga_{sl}}}\right)\\
\label{eq:pfromwc2}&&E(q_{sl})\equiv E\left(\frac{e^{-\Ga_{sl}}}{1+e^{-\Ga_{sl}}}\right)\end{eqnarray}
Given that we already have the posterior expectations and variances for $\Ga_{sl}$, we can approximate \eqref{eq:pfromwc1}-\eqref{eq:pfromwc2} using the Delta method. First, define 
\begin{eqnarray}\label{eq:ff}ff(x)=\frac{e^x}{1+e^x}\end{eqnarray}
and consider the Taylor expansion of $ff(x)$ about $ff(E(x))$:
\begin{eqnarray}\label{eq:delta}ff(x)\approx ff(E(x))+ff'(E(x))(x-E(x))+\frac{ff''(E(x))}{2}(x-E(x))^2\end{eqnarray}
where
\begin{eqnarray}
\label{eq:fderiv}&&ff'(x)=\frac{e^x}{(1+e^x)^2}\\
\label{eq:sderiv}&&ff''(x)=\frac{e^x(1-e^{x})}{(1+e^x)^3}
\end{eqnarray}
It is easy to see that
\begin{eqnarray}
&&E(p_{sl})\approx ff(E(\Ga_{sl}))+\frac{ff''(E(\Ga_{sl}))}{2}Var(\Ga_{sl})\\
\label{eq:Ep}&&E(q_{sl})\approx ff(-E(\Ga_{sl}))+\frac{ff''(-E(\Ga_{sl}))}{2}Var(\Ga_{sl})
\end{eqnarray}
noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.\bigskip\\
Finally, we can easily back-transform to construct an estimated signal, by noting that we can express $\hat{\Gl}_k$ as a product of the $p$'s and $q$'s for any $k=1,2,...,n$. Specifically, let $\{c_1,...,c_J\}$ be the binary representation of $k-1$, and $d_m=\sum_{i=1}^m c_i2^{m-i}$ for $i=1,...,J-1$. We then have
\begin{eqnarray}\label{eq:product}\hat{\Gl}_k=\Gl_{00}p_{00}^{1-c_1}p_{1,d_1}^{1-c_2}...p_{J-1,d_{J-1}}^{1-c_J}q_{00}^{c_1}q_{1,d_1}^{c_2}...q_{J-1,d_{J-1}}^{c_J}\end{eqnarray}
where we usually estimate $\Gl_{00}$ by $\sum_l Y_l$ (see Kolaczyk (1999)). Using the independence of the $p$'s and $q$'s from different scales, we have:
\begin{eqnarray}\label{eq:Eproduct}E(\hat{\Gl}_k)=\Gl_{00}E(p_{00})^{1-c_1}E(p_{1,d_1})^{1-c_2}...E(p_{J-1,d_{J-1}})^{1-c_J}\notag\\
E(q_{00})^{c_1}E(q_{1,d_1})^{c_2}...E(q_{J-1,d_{J-1}})^{c_J}\end{eqnarray}
\bigskip\\
As an additional step, we can also construct a credible band around the signal using the posterior variances for inference purposes. From \eqref{eq:product} we have the following:
\begin{eqnarray}\label{eq:E2product}E(\hat{\Gl}_k^2)=\Gl_{00}^2E(p_{00}^2)^{1-c_1}E(p_{1,d_1}^2)^{1-c_2}...E(p_{J-1,d_{J-1}}^2)^{1-c_J}\notag\\
E(q_{00}^2)^{c_1}E(q_{1,d_1}^2)^{c_2}...E(q_{J-1,d_{J-1}}^2)^{c_J}\end{eqnarray}
To compute the terms in \eqref{eq:E2product}, we again make use of the Delta method (with $ff(x)=(\frac{e^x}{1+e^x})^2$) to obtain:
\begin{eqnarray}
&E(p_{sl}^2)\approx \left(ff(E(\Ga_{sl}))+\frac{ff''(E(\Ga_{sl}))}{2}Var(\Ga_{sl})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(\Ga_{sl}))\}^2Var(\Ga_{sl})\\
&E(q_{sl}^2)\approx \left(ff(-E(\Ga_{sl}))+\frac{ff''(-E(\Ga_{sl}))}{2}Var(\Ga_{sl})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(-\Ga_{sl}))\}^2Var(\Ga_{sl})
\end{eqnarray}
Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\hat{\Gl}_k)$, which allows us to construct credible intervals.\bigskip\\
Note here that in order for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see Coifman \& Donoho (1995), and Kolaczyk (1999)) rather than as described above. The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points. To be more specific, the TI table contains the $\Ga_{sl}$ for all circulant shifts of the signal. Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations. Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
\begin{eqnarray}
\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
\end{eqnarray}
which is an approximation to the true quantity we wish to compute, given by
\begin{eqnarray}
E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
\end{eqnarray}
\end{appendices}
\end{document}

### 2015-04-27 paper/draft_2.tex
added pois data; updated code for creating tables

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb,amsfonts,fullpage,verbatim,bm,graphicx,enumerate,epstopdf,lscape,enumitem}
\usepackage[titletoc,title]{appendix}
\usepackage[dvipsnames,usenames]{color}
\usepackage[pdftex,pagebackref,colorlinks=true,pdfpagemode=UseNone,urlcolor=blue,linkcolor=blue,citecolor=BrickRed,pdfstartview=FitH,plainpages=true]{hyperref}
\usepackage[top=1.15in,bottom=1.15in,left=1.25in,right=1.25in,letterpaper]{geometry}
\usepackage[font=scriptsize]{caption}
\usepackage{caption,subcaption}

\setlist{noitemsep}

\def\CC{\mathbb{C}}
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}
\def\PP{\mathbb{P}}
\def\EE{\mathbb{E}}
\def\II{\mathbb{I}}

\newcommand{\Ga}{\alpha}
\newcommand{\Gb}{\beta}
\newcommand{\Gg}{\gamma}     \newcommand{\GG}{\Gamma}
\newcommand{\Gd}{\delta}     \newcommand{\GD}{\Delta}
\newcommand{\Ge}{\epsilon}
\newcommand{\Gf}{\phi}       \newcommand{\GF}{\Phi}
\newcommand{\Gh}{\theta}
\newcommand{\Gi}{\iota}
\newcommand{\Gk}{\kappa}
\newcommand{\Gl}{\lambda}    \newcommand{\GL}{\Lambda}
\newcommand{\Go}{\omega}     \newcommand{\GO}{\Omega}
\newcommand{\Gs}{\sigma}     \newcommand{\GS}{\Sigma}
\newcommand{\Gt}{\tau}
\newcommand{\Gz}{\zeta}
\newcommand{\s}{\sigma}
\newcommand{\tr}{\triangle}

\begin{document}

\title{\textbf{Title}}
\date{}
\maketitle

\section{Abstract}
\section{Introduction}
In recent years, the use of various shrinkage and thresholding procedures has become ever more popular in a variety of applications where sparsity is a desirable notion. Here the term ``sparsity'' is loosely defined in the sense that it also includes the case where there are many near-zero (as opposed to exactly zero) terms, as shrinkage procedures often produce. The most prominent usage of such procedures appear in multiresolution denoising analyses such as wavelets, where sparsity in a transformed domain often corresponds to smoothness in the data space [references]. Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are usually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references]. In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.\bigskip\\
Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators. These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994). Not only are wavelet methods locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, but they are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001]. While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al. (2001) has demonstrated that various Bayesian shrinkage methods can often outperform thresholding methods in finite samples, where performance is measured by mean squared error (MSE). However, many existing Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications. Furthermore, it is not easy to apply the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we subsequently describe. On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and use ASH as the common shrinkage procedure in both the problems.\bigskip\\
The first problem relates to the frequently encountered Gaussian case. Although the theory for mean estimation with homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], the existing methods for variance estimation with heteroskedastic errors have been far and few between. Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators. Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous approaches using a wavelet thresholding approach on first order differences. While Cai \& Wang (2008) proved that their technique was asymptotically optimal, we will demonstrate how we can further improve the finite sample performance of previous variance estimation procedures by incorporating ASH into a novel wavelet denoising framework. [mention the lack of available software?]\bigskip\\
The second task is to denoise a Poisson distributed signal. This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest. This problem is particularly interesting in the sense that there are many different ways to perform signal recovery. Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by noting that the variance of a Poisson count is equal to its mean. Kolaczyk (1997, 1999a) derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d. Gaussian case.  However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in optimal finite sample performance. Furthermore, both these methods are quite sensitive to the choice of the primary resolution level due to the Poisson nature of the data. Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by Kolaczyk (1999b) to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen. We will improve upon the prior (and likelihood) specification by using ASH as the main shrinkage procedure in a Bayesian framework similar to that of Kolaczyk (1999b). \bigskip\\
Both these problems are generally harder to deal with than the classical problem of i.i.d. Gaussian errors, and usually requires some work in extending the ideas from methods aimed at the latter task. Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage. \bigskip\\
As a generic shrinkage method, ASH takes as input a vector of estimates $\hat{\Gb}_i,i=1,...,n$ and their standard errors $\hat{\s}_i\equiv se(\hat{\Gb}_i),i=1,...n$, and outputs shrunken estimates of $\bm{\Gb}$. Specifically, the likelihoods for the true parameters $\Gb_i,i=1,...n$ are assumed to be iid $N(\Gb_i;\hat{\Gb}_i,\hat{\s}_i^2)$. ASH then assumes exchangeability of the $\Gb_i$'s and sets the following ``shrinkage'' prior on $\Gb_i$ for each $i$:
\begin{eqnarray}
\Gb_i|\bm{\pi}=\sum_{k=1}^m \pi_k N(\Gb_i;0,s_k^2)
\end{eqnarray}
Note that $\bm{\pi}$ and $\bm{s}^2$ is shared across all the $\Gb_i$'s, allowing one to borrow information across all the observations. The full likelihood for $\bm{\pi}$ given $\bm{\hat{\Gb}}$ and $\bm{\hat{\s}}$ is then a product of likelihoods for $\bm{\pi}$ given each $\hat{\Gb}_i$ and $\hat{\s}_i$. Since the likelihoods are Gaussian and the priors are mixtures of Gaussians, the posterior distribution of $\Gb_i$ given $\hat{\Gb}_i$ and $\bm{\hat{\pi}}$ is analytically tractable, where the mixing proportions $\bm{\hat{\pi}}$ are maximum likelihood estimates. The posterior mean of $\Gb_i$ is taken to be the point estimate of $\Gb_i$, resulting in a shrinkage procedure.\bigskip\\
The flexibility and computational efficiency of this shrinkage procedure is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here. Gaussian mixture priors can effectively approximate any unimodal distribution, allowing us to apply this single shrinkage procedure to the two problems we will be focusing on. At the same time, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising too much accuracy. Furthermore, it should be noted that many wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method. On the other hand, we can apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter. For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??). With the main shrinkage method accounted for, we will now proceed to explore the two aforementioned problems in detail. Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.
\section{Method}
\subsection{Gaussian denoising with heteroskedastic errors}
We first consider the application of ASH in the context of the nonparametric regression model with i.i.d. Gaussian errors that are spatially structured. Specifically, consider the model
\begin{eqnarray}\label{eq:1d gaussian model}
Y_i=\mu_i+\Ge_i
\end{eqnarray}
for $i=1,...,n$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve sampled on an equally spaced grid, and $\Ge_i$ are independent $N(0,\s^2)$ noise. Assume that $n=2^J$ for some integer $J$, as is standard in the wavelet literature. To better understand and motivate our method, we first look at wavelet shrinkage from a Bayesian perspective.\bigskip\\
Given an orthogonal $n\times n$ matrix $W$ representing the orthonormal wavelet basis chosen, we have that the wavelet coefficients $\bm{d}$ are given by
\begin{eqnarray}
\bm{d}=W\bm{Y}
\end{eqnarray}
where $\mathbb{V}(Y)=\s^2I$. Hence, we can easily see that
\begin{eqnarray}\label{eq:waveletcoef}
\bm{d}\sim N_n(\bm{\Ga},\s^2I)
\end{eqnarray}
where $\bm{\Ga}=W\mathbb{E}(\bm{Y})$. This implies that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods for $\Ga_i$, $i=1,...,n$. As such, a natural and computationally convenient approach is to set independent priors on $\Ga_i$ as a form of ``shrinkage''. Here we apply the priors from ASH to each resolution level separately, resulting in
%Although there are many choices for the prior, we use the Gaussian mixture prior from ASH in our method, given by
\begin{eqnarray}\label{eq:ashprior}
\Ga_{jk}=\sum_{l=1}^m \pi_l^{(j)} N(0,(s_l^{(j)})^2)
\end{eqnarray}
with $\sum_l \pi_l^{(j)}=1$, for $j=1,...,J$. $\pi_i^{(j)}$ and $(s_i^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level, and $m$ is the number of mixture components. In ASH, $m$ is usually chosen so that it is large enough to reasonably approximate any unimodal distribution, while maintaining a reasonable computational speed. Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,J$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$. By applying the inverse wavelet transform on the posterior mean $\hat{\bm{\Ga}}$ that ASH produces, one can obtain the posterior mean of $\bm{\mu}$, which serves as an estimate that minimizes the MSE. One could also construct credible bands using the posterior variances.\bigskip\\
While many existing methods do a good job of signal denoising in the presence of i.i.d. (Gaussian) errors, heteroskedastic (but still independent) errors present a different challenge. One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize. If the true variances were known, one could obviously write out the full likelihood and proceed to compute the posterior mean/median using some specified prior. However, this would be computationally cumbersome, and may not be feasible when extended to multiple signals or higher dimensions. A suitable prior might also be difficult to find. As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).\bigskip\\
To describe our approach in more detail, first assume that the true variance function is known and given by $\mathbb{V}(\Ge_i)=\s_i$, and that the true mean function is given by $\bm{\mu}=(\mu_1,...,\mu_t)$, where $T=2^J$ for some positive integer $J$. Hence
\begin{eqnarray}
\bm{Y}\sim N_n(\bm{\mu},\Sigma)
\end{eqnarray}
where $\Sigma=\textrm{diag}(\s_1,...,\s_T)$ is a diagonal matrix. For the rest of this subsection, we will use the non-decimated wavelet transform (NDWT) instead of the standard DWT to achieve translation invariance. This property of translation invariance reduces the presence of artifacts, which often occur near discontinuities in the underlying signal (see eg. Coifman \& Donoho (1995)). Now let $W$ be the matrix associated with the NDWT for a given wavelet basis, so that
\begin{eqnarray}
\bm{d}\sim N_n(\bm{\Ga},\tilde{\Sigma})
\end{eqnarray}
where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Sigma}=W\Sigma W^T$. By treating the likelihood for $\bm{\Ga}$ as if it were independent, we can write the likelihood as follows (using the double index mentioned above):
\begin{eqnarray}\label{eq:likelihood}
L(\bm{\Ga}|\bm{d})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(d_{jk}|\Ga_{jk})
\end{eqnarray}
where $P(d_{jk}|\Ga_{jk})=\phi(d_{jk};\Ga_{jk},\tilde{\Sigma}_{(jk,jk)})$. Note that there are $n$ coefficients at each resolution level instead of $2^j$ for resolution $j$ because we are using the NDWT instead of the standard wavelet transform. Here $\phi$ denotes the Gaussian density function. Since $\Sigma$ is diagonal, it is easy to see that $\tilde{\Sigma}_{(jk,jk)}=\sum_{i=1}^T \Sigma_{ii}W_{jk,i}^2$. In our method, we use ASH to assign independent priors to $\Ga_{jk}$ as with \eqref{eq:ashprior}. %ASH also allows us to estimate the $\pi_i$'s via a maximum likelihood approach and fix the $\s_i$'s by using a grid of values. This particular choice of prior specification is extremely flexible, being able to approximate any symmetrical zero-centered distribution, as well as allowing for a relatively easy estimation of the hyperparameters through empirical Bayes. See ASH for more details regarding this choice of prior (?)
While ASH produces shrunken estimates of $\Ga_{jk}$ for $j,k>0$, we estimate $\Ga_{00}$ using the corresponding scaling coefficient, which seems intuitively appealing. Finally, we can obtain an estimate of $\mu$ by using the average basis inverse, which is essentially an average of the inverse wavelet transforms for every shift of the data (see Coifman \& Donoho (1995)) since we are using the NDWT. Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, which takes only $n\log(n)$ time.\bigskip\\
While we assumed that the true variances are known for mean estimation, the problem of variance estimation itself is a non-trivial one. Here we make the reasonable assumption that the variance function is also spatially structured, in addition to the mean function. The approach we took is similar in spirit to that of Cai \& Wang (2008), since we make use of wavelet decomposition as well. However, while they use first order differences, we look at the squared residuals. As such, we need a reasonably accurate estimator of the mean function in order to form sensible residuals. For clarity of presentation, we will first assume that the true mean function is known. Define
\begin{eqnarray}\label{eq:varobs1}
Z_i^2=(Y_i-\mu_i)^2
\end{eqnarray}
to be the ``observations'' for the unknown variance function. Note that $\mathbb{E}(Z_i^2)=\s_i^2$, so that $Z_i^2$ is unbiased for the true variance at point $i$. At this point we can treat this as yet another mean estimation problem, with the added complication that the variance of $Z_i^2$ has a $\chi^2$ distribution squared. To simplify the problem, we approximate this likelihood by a Gaussian likelihood. Of course, better likelihoods and priors could be used that reflect the skewness in the distributions of the ``observations'', but we found that a normal approximation works reasonably well (especially for smoother variance functions), and has the key advantage of being easy and fast to implement. The variance estimation process is then very similar to one for mean estimation as described above, with a few extra details. The full procedure is outlined in Appendix \ref{app:var estimation}.\bigskip\\
Now that we can now estimate $\bm{\mu}$ given $\bm{\s}^2$ and vice versa, a natural procedure for jointly estimating $\bm{\mu}$ and $\bm{\s}^2$ is an iterative one. That is, we estimate $\bm{\mu}$ given some initial estimate of $\bm{\s}^2$, then estimate $\bm{\s}^2$ given the previous estimate of $\bm{\mu}$, and repeat this procedure for as long as is necessary. Although this iterative procedure (using squared residuals) could go on for a long time, and convergence is difficult to prove, we found via simulations that two cycles is usually sufficient to produce relatively accurate estimates. A natural initial estimate would be the square of first order differences between adjacent points, as discussed in previous variance estimation papers (eg Cai \& Wang (2008)). This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough. To be more specific, the initial variance estimates are defined by
\begin{eqnarray}\label{eq:initial var est}
\hat{\s}_i^2=\frac{1}{2}\left(\sum_{i=1}^n(Y_i-Y_{i-1})^2+\sum_{i=1}^n(Y_i-Y_{i+1})^2\right)
\end{eqnarray}
where $Y_0\equiv Y_n$ and $Y_{n+1}\equiv Y_1$, since wavelet methods typically assume that the function is periodic. In summary, our approach for joint mean and variance estimation can be described in three steps:
\begin{enumerate}
\item Using squared first order differences \eqref{eq:initial var est} as our estimates of $\bm{\s}^2$, we estimate $\bm{\mu}$ as if $\bm{\s}^2$ was known (see the above procedure for the case when $\bm{\s}^2$ is known)
\item Given the estimate of $\bm{\mu}$, take squared residuals and treat those as ``observations'' for $\bm{\s}^2$. Next, we project them into wavelet space and apply some form of shrinkage to the wavelet coefficients, before projecting them back into data space to obtain an estimate of $\bm{\s}^2$.
\item Repeat steps (1)-(2) once to obtain the final estimates of $\bm{\mu}$ and $\bm{\s}^2$ respectively.
\end{enumerate}
\subsection{Poisson denoising}
Next we turn to another popular nonparametric regression problem and demonstrate how we could make use of ASH. Specifically, we assume an underlying signal $\Gl_i$, $i=1,...,n$ with $n=2^J$ for some positive integer $J$ as with the Gaussian case. Further assume that each data point $Y_i$, $i=1,...,n$ is realized from a Poisson distribution with mean $\Gl_i$ ie. $Y_i=\textrm{Pois}(\Gl_i)$. Our goal is to recover the true intensity $\bm{\Gl}$ as accurately as possible, given $Y_k$. To make our approach easier to understand and relate it to wavelet-based methods, we first summarize the data in a recursive manner (see Kolaczyk (1999) and Nowak (1998):
\begin{eqnarray}Y_{Jk}\equiv Y_k\end{eqnarray}
for $k=1,...,n$, and
\begin{eqnarray}Y_{jk}=Y_{j+1,2k}+Y_{j+1,2k+1}\end{eqnarray}
for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$, so that we are looking at the sum of adjacent pairs of ``points'' as we move to coarser resolutions, where a point is already itself a sum of the true data points. Another way to define the $Y$'s is
\begin{eqnarray}Y_{jk}=\sum_{l=k2^{J-j}+1}^{(k+1)2^{J-j}}Y_l\end{eqnarray}
for $j=0,...,J$ and $k=0,...,2^j-1$.
Further define the following:
\begin{eqnarray}\Gl_{Jk}\equiv \Gl_k\end{eqnarray}
for $k=1,...,n$, and
\begin{eqnarray}\Gl_{jk}=\Gl_{j+1,2k}+\Gl_{j+1,2k+1}\end{eqnarray}
for $j=0,...,J-1$ and $k=0,...,2^j-1$. Furthermore, define
\begin{eqnarray}\label{eq:poisson wc}\Ga_{jk}=\log(\Gl_{j+1,2k})-\log(\Gl_{j+1,2k+1})\\\end{eqnarray}
for $s=0,...,J-1$ and $l=0,...,2^j-1$. The ${\Ga}$'s defined this way is extremely similar to the (true) Haar wavelet coefficients, which forms the basis of our approach. Using this recursive representation, we can see that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods, where $\bm{\Ga}$ is the vector of all the $\Ga_{sl}$'s. To be specific, we have
\begin{eqnarray}
L(\bm{\Ga}|\mathbf{Y})&=&P(\mathbf{Y}|\bm{\Ga})\\
&=&P(Y_{0,0}|\Gl_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}P(Y_{j+1,2k}|Y_{j,k},\Ga_{j,k})\\
&=&L(\Gl_{0,0}|Y_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}L(\Ga_{j,k}|Y_{j+1,2k},Y_{j,k})
\end{eqnarray}
where the factorization is due to the recursive definition above. Note that $Y_{00}|\Gl_{00}\sim \textrm{Pois}(\Gl_{00})$. Now for any give $j,k$, $Y_{jk}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable. Hence
\[Y_{j+1,2k}|Y_{jk},\Ga_{jk}\sim \textrm{Bin}({Y_{jk},\frac{1}{1+e^{-\Ga_{jk}}}\equiv\frac{\Gl_{j+1,2k}}{\Gl_{jk}}})\]
Whereas Kolaczyk (1999) sets a conjugate prior (which is a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and uses a Binomial likelihood, we felt that the two-component mixture prior is too inflexible. As such, we work with the parameters $\Ga_{sl}$ as defined in \eqref{eq:poisson wc} and approximate the logit-Binomial (is there such a thing?) likelihoods by Gaussian likelihoods. Furthermore, these parameters can be more easily connected to the true wavelet coefficients since they consist of (log) differences rather than ratios.\bigskip\\
To describe the approximation process in more detail, we drop the subscripts for notational convenience. One direct approximation of the likelihood for $\Ga$ is $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$ for some appropriate estimator $\hat{\Ga}$. This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$. The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by
\begin{eqnarray}
\hat{\Ga}_{MLE}=\log(S/F)&\ \ \ S=0,...,N\\
se(\hat{\Ga}_{MLE})=\sqrt{SF/N}&\ \ \ S=0,...,N
\end{eqnarray}
where $S$ is the number of successes in the binomial setup, and $F=N-S$ is the number of failures (in our case the even locations would be successes and odd locations failures). The MLE has one notable drawback however, in that it cannot deal well with extreme cases. This would in turn affect the normal approximation in a non-negligible way. To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie. when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), while at the same time ensuring that $\hat{\Ga}$ is approximately unbiased for $\Ga$ so that moment matching still makes sense, we propose a mix of Berkson's estimator and Tukey's estimator. Specifically, our final estimators for $\Ga$ and its standard error are given by
\begin{eqnarray}\label{eq:pseudoMLE1}
&&\hat{\Ga}=\left\{
\begin{array}{lll}
\log\{(S+0.5)/(F+0.5)\}-0.5&\ \ \ S=0\\
\log\{S/F\}&\ \ \ S=1,2,...,N-1\\
\log\{(S+0.5)/(F+0.5)\}+0.5&\ \ \ S=N\\
\end{array}
\right.\\ \label{eq:pseudoMLE1se}
&&se(\hat{\Ga})=\sqrt{V^*(\hat{\Ga})-\frac{1}{2}\{V_3(\hat{\Ga})\}^2\left\{V_3(\hat{\Ga})-\frac{4}{N}\right\}}
\end{eqnarray}
where
\begin{eqnarray}
&&V_3(\hat{\Ga})=\frac{N+1}{N}\left(\frac{1}{S+1}+\frac{1}{F+1}\right)\ \ \ S=0,...,N\\
\label{eq:pseudoMLE2}&&V^*(\hat{\Ga})=V_3(\hat{\Ga})\left\{1-\frac{2}{N}+\frac{V_3(\hat{\Ga})}{2}\right\}
\end{eqnarray}
The square of the standard error in \eqref{eq:pseudoMLE1se} corresponds to $V^{\ast\ast}$ from p. 182 of Gart \& Zweifel (1967), and is chosen because it is less biased for the true variance of $\hat{\Ga}$ (when $N$ is small) as compared to the asymptotic variance of the MLE (see Gart \& Zweifel (1967)). The other two variance estimators from Gart \& Zweifel (1967), $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.\bigskip\\
Finally, to reconstruct the signal in the original space using the posterior distribution of the $\Ga$'s (which are in the logit space), we make use of the Delta method. For full details on the reconstruction process as well as the Delta method, see Appendix \ref{app:reconstruction}.
\section{Simulations}
Our simulations will focus on the Gaussian and Poisson cases separately. For the Gaussian case, our results will mostly revolve around mean estimation, which is often of interest in many signal recovery problems. To fully explore the performance of the various methods, we consider in our simulations different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions. Specifically, we chose 7 representative mean functions from Antoniadis et al. (2001), namely ``Spikes'', ``Bumps'', ``Blocks'', ``Angles'', ``Doppler'', ``Blip'', and ``Corner''. We feel that these functions encompass most of the local features of commonly seen signals. These mean functions were rescaled to be between 0.2 and 0.8, as in Antoniadis et al. (2001). We also considered sample sizes for $n=256,512,1024$ and 4096, though only results from $n=1024$ will be presented here for conciseness. In our simulations we allowed for SNR=1, a high noise scenario, and SNR=3, a moderate noise scenario. Here, SNR is defined as
\begin{eqnarray}\label{eq:snr}
SNR=\frac{\sqrt{\frac{1}{T-1}\sum_{t=1}^T(\mu_t-\bar{\mu})^2}}{\frac{1}{T}\sum_{t=1}^T\s_t}
\end{eqnarray}
as in Gao (1997) and Delouille (2004). We did not consider low noise situations as the effect of heteroskedasticity on mean estimation is often lost, and many procedures which assume homoskedastic errors perform just as well as methods which do take heteroskedasticity into account. Finally, we considered 5 different variance functions, one of which is constant variance (ie the homoskedastic case), and the rest are commonly used variance functions from eg. Cai \& Wang (2008).\bigskip\\
To highlight the flexibility of our method, we first present the results for the homoskedastic case. Here we compare our method, which does not assume homoskedasticity (and hence jointly estimates the mean and variance), to various popular wavelet based methods which do assume homoskedasticity. For illustration purposes, we also include the case where our method does assume homoskedasticity and takes an estimated $\s$ as input (this is also a feature of our method). Note that we use a second order difference estimate of the variance as described by Hall et al. (1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods for computational simplicity. The practical difference between these two estimators is small, unless the mean function is extremely irregular. Specifically, we include the following methods for this particular simulation study:
\begin{enumerate}
\item SMASH using joint estimation, Haar basis (denoted by SMASH, joint, Haar)
\item SMASH using joint estimation, Symmlet 8 basis (denoted by SMASH, joint, Symm8)
\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI, RMAD, Symm8). See Gao (1997)
\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI, SMASH, Symm8)
\item SMASH using difference estimator, Symmlet 8 basis (denoted by SMASH, homo, Symm8)
\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI, homo, Symm8). See Coifman \& Donoho (1995)
\item EbayesThresh using difference estimator, Symmlet 8 basis (denoted by Ebayes, homo, Symm8). See Johnstone \& Silverman (2004)
\item SureShrink using MAD estimator, Symmlet 8 basis (denoted by SURE, homo, Symm8). See Donoho \& Johnstone (1994)
\item Bayesian shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)
\item SMASH given true variance, Symmlet 8 basis (denoted by SMASH, truth, Symm8)
\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI, truth, Symm8)
\end{enumerate}
Here compare our method mainly against TI thresholding, which often produced the smallest mean squared error (MSE) amongst all the methods discussed in the extensive simulation study conducted by Antoniadis et al. (2001). At the same time, we included SureShrink as it performs well in terms of mean square bias. We also compared our method against two other Bayesian approaches, of which the method described in Clyde \& George (1999,2000) was also included in Antoniadis et al. (2001) and performed well in terms of MSE. The other Bayesian approach, EbayesThresh, is more recent and and hence included as part of our study. Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation, while methods (5)-(9) all estimate a constant variance. Methods (10) and (11) are provided the true variance function and are included as benchmarks. Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above. Here MISE is defined as
\begin{eqnarray}\label{eq:mise}
MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
\end{eqnarray}
, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 57.1 & 146.5 & 65.0 & 50.6 & 76.8 & 24.1 & 8.2 \\
  SMASH, joint, Symm8 & 60.1 & 152.7 & 97.7 & 49.5 & 53.4 & 35.5 & 7.7 \\
  TI, RMAD, Symm8 & 84.0 & 253.7 & 152.2 & 66.7 & 70.2 & 42.0 & 8.6 \\
  TI, SMASH, Symm8 & 79.2 & 218.8 & 144.9 & 65.7 & 67.7 & 40.7 & 8.4 \\
  SMASH, homo, Symm8 & 61.0 & 154.9 & 100.2 & 50.1 & 54.9 & 35.8 & 7.8 \\
  TI, homo, Symm8 & 82.7 & 235.5 & 150.5 & 66.7 & 68.4 & 41.4 & 8.5 \\
  Ebayes, homo, Symm8 & 70.7 & 152.2 & 98.0 & 52.5 & 51.5 & 37.9 & 8.1 \\
  SURE, homo, Symm8 & 369.1 & 418.1 & 301.4 & 482.4 & 275.8 & 272.1 & 97.4 \\
  PostMean, homo, Symm8 & 101.4 & 185.1 & 113.0 & 86.2 & 70.5 & 53.2 & 13.3 \\
  SMASH, truth, Symm8 & 60.9 & 153.6 & 100.0 & 50.1 & 54.9 & 35.5 & 7.7 \\
  TI, truth, Symm8 & 83.1 & 234.7 & 150.8 & 67.1 & 69.1 & 41.3 & 8.5 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for iid Gaussian errors, SNR=1}
\label{table:homo1}
\end{table}
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 11.8 & 18.4 & 7.4 & 10.3 & 18.0 & 3.6 & 1.7 \\
  SMASH, joint, Symm8 & 9.8 & 26.2 & 23.9 & 8.3 & 9.8 & 5.8 & 1.2 \\
  TI, RMAD, Symm8 & 10.9 & 33.7 & 30.7 & 9.4 & 13.5 & 6.6 & 1.5 \\
  TI, SMASH, Symm8 & 10.2 & 24.0 & 26.7 & 9.2 & 10.8 & 6.0 & 1.4 \\
  SMASH, homo, Symm8 & 9.8 & 22.4 & 22.9 & 8.3 & 9.2 & 5.6 & 1.2 \\
  TI, homo, Symm8 & 10.9 & 27.3 & 30.4 & 9.4 & 10.8 & 6.4 & 1.5 \\
  Ebayes, homo, Symm8 & 10.8 & 24.8 & 23.3 & 9.0 & 9.3 & 5.9 & 1.3 \\
  SURE, homo, Symm8 & 43.5 & 65.0 & 54.0 & 57.3 & 40.3 & 37.3 & 11.3 \\
  PostMean, homo, Symm8 & 15.2 & 30.9 & 26.8 & 13.1 & 12.7 & 9.0 & 2.0 \\
  SMASH, truth, Symm8 & 9.7 & 21.4 & 21.5 & 8.3 & 9.2 & 5.5 & 1.2 \\
  TI, truth, Symm8 & 10.9 & 26.1 & 29.7 & 9.4 & 10.8 & 6.4 & 1.5 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for iid Gaussian errors, SNR=3}
\label{table:homo3}
\end{table}
From Tables \ref{table:homo1} and \ref{table:homo3}, we see that our method almost always outperform other methods for all the test functions in terms of MISE as defined above. Furthermore, two key observations should be noted here. First, estimating the variance without the assumption of homoskedasticity does not decrease the performance of our method in any way. In fact, the MISEs for the case where our method estimates the mean and variance jointly and the optimal scenario where our method estimates the mean given the true function are extremely similar. As such, there is no need to specifically assume homoskedasticity or otherwise when using our method. Second, the Haar and the Symmlet 8 bases perform similarly, with each outperforming the other slightly for different test functions. As such, the default option for our method is actually the Haar basis due to computational reasons. \bigskip\\
Having shown that our method performs well in the case of homoskedastic errors without assuming homoskedasticity, we next show the performance gain of our method in the case when the errors are actually heteroskedastic. In total, we considered four different variance functions, namely function $V_2$ as defined in Cai \& Wang (2008), here slightly modified to be
\[V_2(x)=0.0001+4*(e^{(-550*(x-0.2)^2)}+e^{(-200*(x-0.5)^2)}+e^{(-950*(x-0.8)^2)})\]
, the Doppler and Bumps functions from Donoho \& Johnstone (1994), as well as the Clipped Blocks function from Fryzlewicz \& Nason (2001). The same mean functions, SNRs and smoothing methods were used in the heteroskedastic case as in the iid case. Tables \ref{table:hetero_v2_1} - \ref{table:hetero_bump_3} give partial results from our simulation study; the full results are given in Appendix \ref{}.\\
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 108.5 & 282.2 & 112.4 & 86.9 & 113.7 & 62.5 & 15.5 \\
  SMASH, joint, Symm8 & 117.4 & 264.4 & 147.1 & 95.5 & 87.1 & 76.6 & 13.8 \\
  TI, RMAD, Symm8 & 191.9 & 268.6 & 168.5 & 154.0 & 107.1 & 90.9 & 22.5 \\
  TI, SMASH, Symm8 & 171.5 & 410.9 & 217.8 & 123.6 & 120.3 & 85.0 & 16.5 \\
  SMASH, homo, Symm8 & 413.7 & 501.7 & 356.1 & 553.6 & 314.7 & 296.9 & 106.1 \\
  TI, homo, Symm8 & 2007.9 & 1553.2 & 1416.9 & 3170.2 & 1460.2 & 1663.8 & 644.0 \\
  SMASH, truth, Symm8 & 115.6 & 221.4 & 128.4 & 93.1 & 74.6 & 77.5 & 13.7 \\
  TI, truth, Symm8 & 188.4 & 336.0 & 194.8 & 124.7 & 101.1 & 86.3 & 17.1 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=1, Gaussian errors}
\label{table:hetero_v2_1}
\end{table}
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 22.0 & 49.7 & 19.1 & 16.9 & 23.3 & 10.2 & 3.0 \\
  SMASH, joint, Symm8 & 20.4 & 59.2 & 40.0 & 14.3 & 11.7 & 18.7 & 2.7 \\
  TI, RMAD, Symm8 & 25.2 & 53.5 & 35.6 & 19.4 & 16.7 & 17.4 & 3.8 \\
  TI, SMASH, Symm8 & 24.3 & 64.7 & 43.5 & 16.1 & 14.4 & 18.9 & 3.3 \\
  SMASH, homo, Symm8 & 50.8 & 64.1 & 58.5 & 65.2 & 39.9 & 37.7 & 12.6 \\
  TI, homo, Symm8 & 225.3 & 174.0 & 159.5 & 354.4 & 156.5 & 186.0 & 71.8 \\
  SMASH, truth, Symm8 & 20.0 & 43.6 & 31.0 & 13.9 & 9.1 & 19.2 & 2.6 \\
  TI, truth, Symm8 & 25.9 & 66.6 & 42.8 & 17.1 & 10.0 & 22.2 & 3.6 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=3, Gaussian errors}
\end{table}
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 223.1 & 650.9 & 275.9 & 233.6 & 232.6 & 148.0 & 47.4 \\
  SMASH, joint, Symm8 & 231.7 & 606.4 & 293.6 & 263.1 & 194.9 & 154.4 & 44.5 \\
  TI, RMAD, Symm8 & 1621.6 & 1464.5 & 1221.0 & 2543.6 & 1197.5 & 1334.5 & 512.2 \\
  TI, SMASH, Symm8 & 335.9 & 798.1 & 422.0 & 385.4 & 274.6 & 207.8 & 62.5 \\
  SMASH, homo, Symm8 & 1242.1 & 1199.3 & 940.4 & 1836.5 & 910.0 & 973.8 & 366.3 \\
  TI, homo, Symm8 & 3289.2 & 2543.4 & 2310.3 & 5206.6 & 2404.7 & 2731.0 & 1060.4 \\
  SMASH, truth, Symm8 & 114.0 & 633.3 & 214.9 & 115.9 & 100.6 & 81.5 & 15.6 \\
  TI, truth, Symm8 & 171.0 & 799.0 & 324.7 & 170.4 & 140.0 & 95.0 & 18.6 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for the Bumps variance function, SNR=1, Gaussian errors}
\end{table}
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
  \hline
SMASH, joint, Haar & 34.9 & 137.1 & 56.0 & 32.9 & 46.9 & 20.5 & 6.9 \\
  SMASH, joint, Symm8 & 29.4 & 122.2 & 71.3 & 33.8 & 30.8 & 28.7 & 5.9 \\
  TI, RMAD, Symm8 & 174.8 & 183.1 & 153.4 & 286.2 & 137.0 & 152.1 & 57.4 \\
  TI, SMASH, Symm8 & 41.4 & 148.1 & 86.5 & 49.2 & 41.5 & 35.5 & 8.5 \\
  SMASH, homo, Symm8 & 141.3 & 167.3 & 127.7 & 209.1 & 112.9 & 114.0 & 41.6 \\
  TI, homo, Symm8 & 366.6 & 286.7 & 259.9 & 580.2 & 264.8 & 304.2 & 118.0 \\
  SMASH, truth, Symm8 & 14.9 & 162.9 & 67.1 & 16.9 & 16.0 & 13.2 & 2.5 \\
  TI, truth, Symm8 & 17.1 & 242.4 & 82.9 & 23.0 & 20.7 & 16.8 & 2.9 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for the Bumps variance function, SNR=3, Gaussian errors}
\label{table:hetero_bump_3}
\end{table}
\bigskip\\
In all the scenarios presented in Tables \ref{table:hetero_v2_1} - \ref{table:hetero_bump_3}, it is obvious that the mean estimates deviate substantially from the true mean if the heteroskedastic nature of the variance functions is not taken into account. We also note that our method can nearly achieve the ``optimal'' MISE (ie the MISE for the case when our method is given the true variance) for variance function $V_2$, but not for the other. This is likely due to the fact that function $V_2$ is relatively smooth, and hence easier to estimate than the extremely jumpy and peaky Bumps function. Furthermore, the MISEs of our method are often smaller than the ones produced by TI-thresholding even when TI-thresholding is supplied the true variance function, where the latter procedure has been shown to be asymptotically optimal (see Gao (1997)). Hence, the finite sample performance of our method is guaranteed to a certain extent through these simulation studies. At the same time, using the variance function estimated by our method instead of running MAD also improves the performance of TI-thresholding, demonstrating the ability of our method to estimate the variance function relatively accurately. However, our method is still superior to TI-thresholding no matter the type of variance estimate that TI-thresholding uses in these simulation studies.\bigskip\\
Since our method also provides variance estimates, one could potentially perform similar assessments for different variance functions as with mean functions. In this particular study, we compare our method against the only joint mean and variance estimation procedure for which we could find available software. Specifically, we consider the Mean Field Variational Bayes (MFVB) methodology developed by Menictas \& Wand (2014) for heteroskedastic Gaussian regression. Since MFVB is splines-based (and hence less locally adaptive), we chose the smooth mean and standard deviation functions (A) from Menictas \& Wand (2014) as our test functions, plotted in Figure \ref{fig:mfvb_fn} and denoted by $m(\cdot)$ and $sd(\cdot)$ respectively. We then considered two different simulation scenarios:
\begin{enumerate}
\item $n=500$ independent $(X_i,Y_i)$ pairs were generated. The $X_i$'s were distributed as Uniform(0,1), and the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$. The performance of a given method is measured by the standard MSE evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation functions.
\item $n=1024$ independent $(X_i,Y_i)$ pairs were generated. The $X_i$'s were deterministic and equally spaced on (0,1), while the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$. The performance of a given method is measured by the MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation functions.
\end{enumerate}
\begin{figure}[ht]
\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{mfvb_mean.pdf}
        \caption{}
        \label{fig:seq_peak_data}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{mfvb_var.pdf}
        \caption{}
        \label{fig:seq_peak_est}
    \end{subfigure}
    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.}
    \label{fig:mfvb_fn}
\end{figure}
In the first scenario, the number of data points is not a power of two, nor are the point equally spaced. To deal with these complications, we adapted and modified the standard symmetric extension procedure commonly adopted in wavelet settings. We first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points. This ensures that the number of data points in the new ``dataset'' is a power of two, and the mean curve would be continuous at the right edge. To further ensure that the input to the Gaussian denoising method is periodic, we then reflected the new dataset about the right edge and used this as the final input. In order to obtain the original mean and variance functions, we extracted the first $n$ points from the outputs (mean and variance) of our denoising technique. Since the data points are not evenly spaced, we took the simplest approach and applied our method treating the observations as if they were evenly spaced. This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (see Sardy et al. (1999)). Evaluation of MSE at the 201 equally spaced points is then based on simple linear interpolation between the estimated points. Tables \ref{table:mfvb_comp} displays the MSEs over 100 independent runs for each scenario.
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Scenario 1}&\multicolumn{2}{c}{Scenario 2}\\
\cline{2-5}
& mean & sd & mean & sd \\
\hline
MFVB & 0.0330 & 0.0199 & 0.0172 & 0.0085 \\
SMASH & 0.0334 & 0.0187 & 0.0158 & 0.0065 \\
\hline
\end{tabular}
\caption{MSEs of MFVB and SMASH for two simulation scenarios}
\label{table:mfvb_comp}
\end{table}
\bigskip\\
Note that wavelets in general are poorly suited for dealing with the setup in Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced. Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of wavelet methods. At the same time, spline-based methods such as MFVB are well suited to dealing with smooth mean and variance functions such as those used in the simulations, whereas wavelet methods can better deal with spatial inhomogeneity which are present in functions such as those presented in Tables
\ref{table:homo1} - \ref{table:hetero_bump_3}. Despite these limitations, our method performs comparably to MFVB in terms of mean estimation for the simulation scheme presented in Scenario 1, and has a lower MSE in terms of variance estimation. For Scenario 2, our method outperforms MFVB in both mean and variance estimation despite the smoothness of the test functions used. \bigskip\\
Summarizing the simulation studies conducted so far, we have demonstrated that our method does a reasonable job of mean and variance estimation for a variety of situations in the Gaussian case. As such, we now turn our attention to the Poisson case. For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in Timmermann \& Nowak (1999) and Fryzlewicz \& Nason (2004), over 100 independent runs. Specifically, the ``Spikes'', ``Angles'', ``Bursts'',``Clipped Blocks'',``Bumps'' and ``Heavisine'' functions were chosen. The first 5 were part of a simulation study by Besbeas et al. (2004), and the ``Heavisine'' function was considered by Fryzlewicz \& Nason (2004). These test functions were then shifted and scaled to have (min,max) intensities of (0.01,3), (1/8,8) and (1/128,8), of which the latter two were the values used in Fryzlewicz \& Nason (2004). The low intensity scenario of (0.01,3) was chosen to reflect the small number of counts often present in certain types of high-throughput sequencing data, an application we will demonstrate in more detail later on. To assess the performance of our method, we used the same MISE as defined above for the Gaussian case, and considered the following methods in our simulation study:
\begin{enumerate}
\item SMASH
\item Haar-Fisz transform and variance stabilization (denoted by Haar-Fisz). See Fryzlewicz \& Nason (2004).
\item Anscombe transformation with the universal threshold using hard thresholding (denoted by Anscombe, universal). See Donoho (1993).
\item Anscombe transformation with the cross-validation threshold using hard thresholding (denoted by Anscombe, CV)
\item Corrected Haar thresholds using hard thresholding (denoted by Haar thresholds). See Kolazyk (1997).
\item Conditional variance stabilization with the non-decimated wavelet transform (denoted by CVS). See Jansen (2006).
\item Bayesian multi-scale multiplicative innovations model (denoted by BMMIM). See Timmermann \& Nowak (1999).
\item Bayesian multi-scale model (denoted by BMSM). See Kolaczyk (1999b).
\end{enumerate}
The Haar-Fisz transform uses 50 external cyclespins as suggested by Fryzlewicz \& Nason (2004). The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation and CVS use the Symmlet 10 basis, as recommended by the corresponding software. Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 5,6 and 7 for all other methods. We present the MISEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\
\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & (0.01,3) & (1/8,8) & (1/128,128) \\
  \hline
SMASH & 145.3 & 68.5 & 10.2 \\
  Haar-Fisz & 369.5 & 140.4 & 9.8 \\
  Anscombe, universal & 459.0 & 163.7 & 10.1 \\
  Anscombe, CV & 458.8 & 162.6 & 10.1 \\
  Haar thresholds & 295.8 & 168.3 & 89.4 \\
  CVS & 5201.1 & 1083.5 & 122.8 \\
  BMMIM & 277.2 & 110.1 & 18.1 \\
  BMSM & 147.4 & 73.9 & 10.5 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for the Angles function for Poisson data}
\label{table:pois_angles}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{rrrr}
  \hline
 & (0.01,3) & (1/8,8) & (1/128,128) \\
  \hline
SMASH & 2597.5 & 1194.6 & 141.2 \\
  Haar-Fisz & 2849.9 & 1572.3 & 184.0 \\
  Anscombe, universal & 3500.0 & 2029.9 & 194.9 \\
  Anscombe, CV & 3520.7 & 2070.0 & 196.3 \\
  Haar thresholds & 3151.9 & 1601.4 & 173.7 \\
  CVS & 9410.7 & 3457.5 & 194.9 \\
  BMMIM & 3089.9 & 2065.3 & 222.2 \\
  BMSM & 4036.8 & 1889.9 & 171.1 \\
   \hline
\end{tabular}
\caption{MISEs of various methods for the Bumps function for Poisson data}
\label{table:pois_bumps}
\end{table}

From Tables \ref{table:pois_angles} and \ref{table:pois_bumps} we can see that our method consistently outperforms other methods discussed here. This is particularly evident for the low intensity cases (ie (min,max) intensity of (0.01,3) and (1/8,8)), which are of primary interest in our application to sequencing data. At the same time, our method still performs competitively even when the average/peak intensity is high. Note that our method substantially improves on the performance of other methods for test function ``Bumps'', which is extremely hard to estimate due to its inhomogeneity.

Overall, these simulation studies demonstrate the ability of our method to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptiveness of the shrinkage procedure ASH. Although we have considered an extensive range of problems here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has to be determined. In the next section, we will apply our method to two example datasets that have been discussed in previous work, and comment on the resulting estimates.
\bigskip\\
\section{Application to real datasets}
\subsection{Three-month Treasury Bill Yields}
In this section we apply the Gaussian and Poisson denoising techniques to one example dataset each. For the Gaussian case, we looked at yields of secondary market rates from three-month Treasure bills, which were recorded weekly on Fridays. These rates were quoted on a discount basis and annualized using a 360-day year of bank interest. To match the analysis in Fan \& Yao (1998), we used 1735 weekly observations spanning Jan. 5 1962 to Mar. 31 1995. The data are plotted in Figure \ref{fig:tb_raw_data}. Similar to Fan \& Yao (1998), we fit an autoregressive model of order 5 (AR(5)) to the data and obtained the following:
\begin{eqnarray}
T_t=1.228T_{t-1}-0.234T_{t-2}+0.028T_{t-3}+0.039T_{t-4}-0.066T_{t-5}+Y_t
\end{eqnarray}
where $T_t, t=1,...,1735$ is the time series for the yields, and $Y_t$ are the residuals from fitting the model. Figure \ref{fig:tb_res} shows the plot of $Y_t$ against $X_t\equiv T_{t-1}$. Our goal is to estimate the mean function defined by $E(Y_t|X_t=x)$ as well as the variance function $V(Y_t|X_t=x)$. Note that standard wavelet techniques are not designed for such types of data, where 1) repeated observations are present and 2) the number of data points is not a power of two and the points are unevenly spaced. To tackle the first issue, we use the median of the repeated observations at their respective sample points (see eg Delouille et al. (2004)). Next, we applied the procedure described in the Simulations section when comparing our method against MFVB, which was a modified version of symmetric extension. This deals with the second complication. The estimated mean and conditional variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.\bigskip\\
\begin{figure}[h]
\centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_a.pdf}
        \caption{}
        \label{fig:tb_raw_data}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_b.pdf}
        \caption{}
        \label{fig:tb_res}
    \end{subfigure}

    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_c.pdf}
        \caption{}
        \label{fig:tb_mean}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_d.pdf}
        \caption{}
        \label{fig:tb_var}
    \end{subfigure}
    \caption{Analysis of yields from three-month Treasury Bills. (a) Raw data of interest rates as a function of time. (b) Residuals $Y_t$ from fitting an AR(5) model to the data against $X_t\equiv T_{t-1}$. The red curve is the estimated mean curve from SMASH. (c) Plot of a zoomed-in version of the estimated mean curve, with approximate 95\% credible bands. (d) The estimated conditional variance curve, with approximate 95\% credible bands.}
\end{figure}
\bigskip\\
Except for possible boundary effects, our mean and conditional variance estimates are similar to those of Fan \& Yao (1998). Unfortunately, these boundary effects are difficult to deal with for non-periodic functions in the wavelet case, and our usage of symmetric extension with the Haar basis is just one possible solution. Better alternatives have been suggested by eg. Su et al. (2013), but is beyond the scope of discussion in this paper. Similar to the analysis in Fan \& Yao (1998), we found the correlation coefficient between the logarithm of $x_t$ and the logarithm $\hat{V}^{1/2}(Y_t|x_t)$ to be 0.949, which further supports the structural volatility model suggested by Andersen and Lund (source?):
\begin{eqnarray}
Var^{1/2}(Y_t|x_t)=\Ga x_t^{\Gb}
\end{eqnarray}
By performing least squares regression of $\log(\hat{V}^{1/2}(Y_t|x_t))$ on $\log(x_t)$, we have that $\hat{\Ga}=0.0106$ and $\hat{\Gb}=1.429$, which are similar to the values reported in Fan \& Yao (1998).
\newpage
\subsection{ChIP-Seq Data}
Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly seen in the field of genomics. Specifically, we chose an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute. This dataset contains reads from chromatin immunoprecipitation sequencing (ChIP-seq) measuring transcription factor binding in two different cell types, with two samples for each cell type. Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1. Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
\begin{figure}[h]
\centering
\includegraphics[scale=0.7]{smoothing_all.pdf}
\caption{Estimated intensities from SMASH for 4 samples; the first two samples are two replicates from GM12878, a lymphoblastoid cell line, and the last two samples are two replicates from H1hesc, which are human embryonic stem cells. The reads are taken from position 880001 to 1011072 on chromosome 1.}
\label{fig:seq_smooth}
\end{figure}
\bigskip
One goal of analyzing ChIP-seq data is to discover regions where transcription factors are likely to bind to DNA, thereby allowing us to better understand the mechanisms underlying gene regulation. These binding regions are often reflected in the data as ``peaks'', where more counts are present than background noise. Our method allows us to identify these peaks by looking at the estimated intensity function. In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples. To ensure that our method performs sensibly, we took the same region from only the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the region. The results are shown in Figure \ref{fig:seq_peak}.\\
\newpage
\begin{figure}[h]
\centering
    \begin{subfigure}[b]{0.85\textwidth}
        \centering
        \includegraphics[width=\textwidth]{peaks_comp_a.pdf}
        \caption{}
        \label{fig:seq_peak_data}
    \end{subfigure}

    \begin{subfigure}[b]{0.85\textwidth}
        \centering
        \includegraphics[width=\textwidth]{peaks_comp_b.pdf}
        \caption{}
        \label{fig:seq_peak_est}
    \end{subfigure}
    \caption{Analysis of reads taken from the GM12878 cell line, spanning position 880001 to 1011072 on chromosome 1. (a) Raw sequencing counts. (b) Estimated intensity function from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).}
    \label{fig:seq_peak}
\end{figure}
From Figure \ref{fig:seq_peak_est} it is clear the intensity estimate from our method can recognize the peaks detected by MACS. Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads. At the same time, our method also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
\section{Discussion}
In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques. Both the applications discussed in this paper relaxes the standard assumption of i.i.d. Gaussian noise, and thus present us with challenging tasks. Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, allowing it to be potentially used in a variety of other applications where shrinkage is desirable.\bigskip\\
In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as approximate credible intervals to provide uncertainty estimates. In the case of (possibly heteroskedastic) Gaussian errors, we are able to estimate the variance function as well, which can be used to provide frequentist confidence intervals for other forms of mean estimation. To the best of our knowledge, there is no readily available software which implements joint mean and variance estimation in the wavelet literature. We have also tested our method in simulations and found that it is relatively robust to simple forms of autocorrelation between the errors (details needed). In the case of Poisson regression, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods by utilizing ASH as the shrinkage procedure, which allows for more flexibility and precision. In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution. In both of the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used. On the other hand, the so-called primary resolution level in almost all of the other wavelet-based methods actually affects their performance substantially, depending on the underlying mean and/or variance function. Hence, our fully adaptive procedures allow users to easily apply them to any given dataset, depending on context.\bigskip\\
We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature in terms of pointwise accuracy (MSE in this case). Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussians used indicate that our methods are computationally fast, since the posteriors can be computed analytically. In the Gaussian case, the only available method (which we implemented ourselves) for mean estimation with heteroskedastic errors is a non-Bayesian thresholding procedure, making it difficult to assess the relative computational efficiency of our method. Furthermore, the lack of readily available software for variance estimation made it extremely difficult to assess the relative performance of our method in that context as well. On the other hand, we were able to compare our method to some of the more popular denoising techniques in the Poisson case. Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods (Kolaczyk 1999) by utilizing ASH as the shrinkage procedure, which allows for more flexibility and accuracy. This is particularly evident in the case where the mean intensity is low, as is common in many high-throughput genomic sequencing datasets. Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm, due to the fact that we do not have to perform external cycle-spinning. Unfortunately, we were not able to directly compare the computational efficiency of our method to other methods due to differences in the programming software involved including that of the multiscale approach from Kolaczyk (1999).\bigskip\\
Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios. Even while restricting ourselves to the one-dimensional domain, our methods could be used in the case of multiple samples, otherwise known as regression analysis of functional data (see Morris 2006). Instead of dealing with a vector of observations, we could perform regression analysis on a matrix of observations, each row of which would encapsulate a sample with observations that are temporally or spatially structured. While Morris (2006) proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category. Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby imposing even less restrictions on the assumptions behind the regression model. In the simplest case, we could potentially obtain spatially structured differences between the samples by including a single covariate into the regression model that categorizes each sample. In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where differential expression is present between say, different tissues, as per our sequencing example in the previous section. The Gaussian model could potentially be used in...(??).\bigskip\\
With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible. For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in Nowak (1998) (again, reference technical report). However, recent advances in image denoising problems have shown that wavelet transformations might not be the most ideal due to the presence of smooth curves in many images such as photographs. We could thus attempt to use ASH as a shrinkage procedure in other types of transformations such as curvelets, and that could be a potential direction for future work.
\newpage
\section{Reference}

\begin{appendices}
\section{}\label{app:var estimation}\bigskip
\textbf{Variance estimation for Gaussian denoising}\bigskip\\
With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$. Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$. As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
\begin{eqnarray}
L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
\end{eqnarray}
However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions. As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
\begin{eqnarray}
P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
\end{eqnarray}
so that
\begin{eqnarray}\label{eq:gaus approx}
L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
\end{eqnarray}
where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients. Since these variances are unknown, we estimate them from the data and then proceed to treat them as known. More specifically, since $Z_i\sim N(0,\s_i^2)$, we have that
\begin{eqnarray}
&\mathbb{E}(Z_i^4)\approx 3\s_i^4\notag\\
\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z_i^2)\approx 2\s_i^4
\end{eqnarray}
and so we simply use $\frac{2}{3}Z_i^4$ as an unbiased estimator for $\mathbb{V}(Z_i^2)$. It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{l=1}^n \frac{2}{3}Z_l^4W_{jk,l}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$. These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters. Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels. This is likely due to the fact that the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points). One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.\bigskip\\

\section{}\label{app:reconstruction}\bigskip
\textbf{Signal reconstruction for Poisson denoising}\bigskip\\
Given the posterior means and variances of the $\Ga$'s from ASH, the first step to reconstructing the signal is to find the posterior means of $p_{jk}:=\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and $q_{jk}:=\frac{\Gl_{j+1,2k+1}}{\Gl_{jk}}$ (for $j=0,...,J-1$ and $k=0,...,2^j-1$). Specifically, for each $j$ and $k$, we wish to find
\begin{eqnarray}\label{eq:pfromwc1}
&&E(p_{jk})\equiv E\left(\frac{e^{\Ga_{jk}}}{1+e^{\Ga_{jk}}}\right)\\
\label{eq:pfromwc2}&&E(q_{jk})\equiv E\left(\frac{e^{-\Ga_{jk}}}{1+e^{-\Ga_{jk}}}\right)\end{eqnarray}
Given that we already have the posterior expectations and variances for $\Ga_{jk}$, we can approximate \eqref{eq:pfromwc1}-\eqref{eq:pfromwc2} using the Delta method. First, define
\begin{eqnarray}\label{eq:ff}ff(x)=\frac{e^x}{1+e^x}\end{eqnarray}
and consider the Taylor expansion of $ff(x)$ about $ff(E(x))$:
\begin{eqnarray}\label{eq:delta}ff(x)\approx ff(E(x))+ff'(E(x))(x-E(x))+\frac{ff''(E(x))}{2}(x-E(x))^2\end{eqnarray}
where
\begin{eqnarray}
\label{eq:fderiv}&&ff'(x)=\frac{e^x}{(1+e^x)^2}\\
\label{eq:sderiv}&&ff''(x)=\frac{e^x(1-e^{x})}{(1+e^x)^3}
\end{eqnarray}
It is easy to see that
\begin{eqnarray}
&&E(p_{jk})\approx ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\\
\label{eq:Ep}&&E(q_{jk})\approx ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})
\end{eqnarray}
noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.\bigskip\\
Finally, we can easily back-transform to construct an estimated signal, by noting that we can express $\Gl_i$ as a product of the $p$'s and $q$'s for any $i=1,2,...,n$. Specifically, let $\{c_1,...,c_J\}$ be the binary representation of $i-1$, and $d_m=\sum_{j=1}^m c_j2^{m-j}$ for $j=1,...,J-1$. We then have
\begin{eqnarray}\label{eq:product}\Gl_k=\Gl_{00}p_{00}^{1-c_1}p_{1,d_1}^{1-c_2}...p_{J-1,d_{J-1}}^{1-c_J}q_{00}^{c_1}q_{1,d_1}^{c_2}...q_{J-1,d_{J-1}}^{c_J}\end{eqnarray}
where we usually estimate $\Gl_{00}$ by $\sum_l Y_l$ (see Kolaczyk (1999)). Using the independence of the $p$'s and $q$'s from different scales, we have:
\begin{eqnarray}\label{eq:Eproduct}E(\Gl_i)=\Gl_{00}E(p_{00})^{1-c_1}E(p_{1,d_1})^{1-c_2}...E(p_{J-1,d_{J-1}})^{1-c_J}\notag\\
E(q_{00})^{c_1}E(q_{1,d_1})^{c_2}...E(q_{J-1,d_{J-1}})^{c_J}\end{eqnarray}
\bigskip\\
As an additional step, we can also construct a credible band around the signal using the posterior variances for inference purposes. From \eqref{eq:product} we have the following:
\begin{eqnarray}\label{eq:E2product}E(\Gl_i^2)=\Gl_{00}^2E(p_{00}^2)^{1-c_1}E(p_{1,d_1}^2)^{1-c_2}...E(p_{J-1,d_{J-1}}^2)^{1-c_J}\notag\\
E(q_{00}^2)^{c_1}E(q_{1,d_1}^2)^{c_2}...E(q_{J-1,d_{J-1}}^2)^{c_J}\end{eqnarray}
To compute the terms in \eqref{eq:E2product}, we again make use of the Delta method (with $ff(x)=(\frac{e^x}{1+e^x})^2$) to obtain:
\begin{eqnarray}
&E(p_{jk}^2)\approx \left(ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(\Ga_{jk}))\}^2Var(\Ga_{jk})\\
&E(q_{jk}^2)\approx \left(ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(-\Ga_{jk}))\}^2Var(\Ga_{jk})
\end{eqnarray}
Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.\bigskip\\
Note here that in order for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see Coifman \& Donoho (1995), and Kolaczyk (1999)) rather than as described above. The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points. To be more specific, the TI table contains the $\Ga_{jk}$ for all circulant shifts of the signal. Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations. Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
\begin{eqnarray}
\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
\end{eqnarray}
which is an approximation to the true quantity we wish to compute, given by
\begin{eqnarray}
E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
\end{eqnarray}
\end{appendices}
\end{document}

### 2015-04-27 paper/table_pois.R

@@ -74,6 +74,14 @@ rownames(mise.ang.table)=tex.row.names
 colnames(mise.ang.table)=tex.col.names
 rownames(mise.b.table)=tex.row.names
 colnames(mise.b.table)=tex.col.names
+rownames(mise.cb.table)=tex.row.names
+colnames(mise.cb.table)=tex.col.names
+rownames(mise.s.table)=tex.row.names
+colnames(mise.s.table)=tex.col.names
+rownames(mise.hs.table)=tex.row.names
+colnames(mise.hs.table)=tex.col.names
+rownames(mise.bur.table)=tex.row.names
+colnames(mise.bur.table)=tex.col.names
 
 
 print(xtable(mise.ang.table,caption="MISE of various methods for the Angles function",digits=1))

### 2015-04-27 pois_data/plot.R

@@ -1,0 +1,52 @@
+library(smash)
+
+
+load("reg_880000_1011072.Robj")
+
+bppos=880001:1011072
+
+res1=ashsmooth.pois(M[1,])
+res2=ashsmooth.pois(M[2,])
+res3=ashsmooth.pois(M[3,])
+res4=ashsmooth.pois(M[4,])
+
+
+pdf("smoothing_all.pdf")
+par(mfrow=c(4,1))
+plot(bppos,res1,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell GM12878, Replicate 1")
+plot(bppos,res2,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell GM12878, Replicate 2")
+plot(bppos,res3,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell H1hesc, Replicate 1")
+plot(bppos,res4,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell H1hesc, Replicate 2")
+dev.off()
+
+
+peaks=read.table("Gm1287peaks_chr1_sorted")
+peaks=peaks[order(peaks[,2]),]
+all.base=1:peaks[dim(peaks)[1],3]
+peaks.start=peaks[,2][peaks[,2]>=880000&peaks[,2]<=1011072]
+peaks.end=peaks[,3][peaks[,3]>=880000&peaks[,3]<=1011072]
+
+res=ashsmooth.pois(M[1,]+M[2,],post.var=TRUE)
+
+pdf("peaks_comp_a.pdf",height=5,width=10)
+plot(bppos,M[1,]+M[2,],xlab="position",ylab="counts",pch=16,cex=0.7)
+dev.off()
+
+pdf("peaks_comp_b.pdf",height=5,width=10)
+plot(bppos,res$est,type='l',xlab="position",ylab="intensity")
+for(i in 1:length(peaks.start)){
+  segments(peaks.start[i],-0.02,peaks.end[i],-0.02,col=2,lwd=4)
+}
+dev.off()
+
+
+
+#lines((res$est+3*sqrt(res$var)),col=2)
+#lines((res$est-3*sqrt(res$var)),col=2)
+
+#res.thresh=res$est
+#res.thresh[(res$est+3*sqrt(res$var)>=0)&(res$est-3*sqrt(res$var)<=0)]=0
+#plot(res.thresh,type='l')
+
[…]

### 2015-05-04 paper/draft_2.tex
modified tables in draft

@@
 While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al.
-(2001) has demonstrated that various Bayesian shrinkage methods can often outperform thresholding methods in finite samples, where performance is measured by mean squared error (MSE).
+(2001) has demonstrated that various Bayesian shrinkage methods are usually more data adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE).
 However, many existing Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications.
 Furthermore, it is not easy to apply the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we subsequently describe.
-On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and use ASH as the common shrinkage procedure in both the problems.\bigskip\\
+On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and uses ASH as the common shrinkage procedure in both the problems.\bigskip\\
 The first problem relates to the frequently encountered Gaussian case.
@@
 The posterior mean of $\Gb_i$ is taken to be the point estimate of $\Gb_i$, resulting in a shrinkage procedure.\bigskip\\
-The flexibility and computational efficiency of this shrinkage procedure is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here.
-Gaussian mixture priors can effectively approximate any unimodal distribution, allowing us to apply this single shrinkage procedure to the two problems we will be focusing on.
+The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here.
+As with many other Bayesian procedures, ASH borrows information across all available data, and is hence extremely data adaptive.
+At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a name for this?) is that it allows for variable variances as input, a feature that the latter methods lack.
+This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above.
+Furthermore, Gaussian mixture priors can effectively approximate any unimodal distribution, allowing for a more flexible prior than many other procedures.
 At the same time, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising too much accuracy.
-Furthermore, it should be noted that many wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method.
-On the other hand, we can apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter.
+It should be noted that typical wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method.
+However, we are able to apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter.
 For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??).
@@
 To describe the approximation process in more detail, we drop the subscripts for notational convenience.
-One direct approximation of the likelihood for $\Ga$ is $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$ for some appropriate estimator $\hat{\Ga}$.
+One direct approximation of the likelihood for $\Ga$ is the Laplace approximation, which results in the Gaussian likelihood given by $\phi(\Ga;\hat{\Ga}_{MLE},\mathbb{V}(\hat{\Ga}_{MLE}))$.
+Here $\phi$ is the normal density function, and $\hat{\Ga}_{MLE}$ is the maximum likelihood estimator.
+We would then estimate $\mathbb{V}(\hat{\Ga}_{MLE})$ by the square of the asymptotic standard deviation for $\hat{\Ga}_{MLE}$.
+Specifically,
+% for some appropriate estimator $\hat{\Ga}$.
 This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
-We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$.
+%We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$.
 The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by
@@
 The MLE has one notable drawback however, in that it cannot deal well with extreme cases.
-This would in turn affect the normal approximation in a non-negligible way.
+This would in turn affect the likelihood approximation in a non-negligible way.
 To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie.
-when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), while at the same time ensuring that $\hat{\Ga}$ is approximately unbiased for $\Ga$ so that moment matching still makes sense, we propose a mix of Berkson's estimator and Tukey's estimator.
+when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), we instead aim to find a suitable estimator $\hat{\Ga}$ for $\Ga$.
+Next, we approximate the distribution of $\hat{\Ga}$ by a Gaussian distribution, so that the likelihood for $\Ga$ is automatically Gaussian, given by $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$.
+To that end, we propose a mix of Berkson's estimator and Tukey's estimator as suggested in Gart \& Zweifel (1967).
 Specifically, our final estimators for $\Ga$ and its standard error are given by
@@
 For illustration purposes, we also include the case where our method does assume homoskedasticity and takes an estimated $\s$ as input (this is also a feature of our method).
-Note that we use a second order difference estimate of the variance as described by Hall et al.
-(1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods for computational simplicity.
+Note that, for computational simplicity, we use a second order difference estimate of the variance as described by Hall et al.
+(1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods .
 The practical difference between these two estimators is small, unless the mean function is extremely irregular.
@@
 \item SMASH using joint estimation, Symmlet 8 basis (denoted by SMASH, joint, Symm8)
-\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI, RMAD, Symm8). See Gao (1997)
-\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI, SMASH, Symm8)
+\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI-thresh, RMAD, Symm8). See Gao (1997)
+\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI-thresh, SMASH, Symm8)
 \item SMASH using difference estimator, Symmlet 8 basis (denoted by SMASH, homo, Symm8)
-\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI, homo, Symm8). See Coifman \& Donoho (1995)
 \item EbayesThresh using difference estimator, Symmlet 8 basis (denoted by Ebayes, homo, Symm8). See Johnstone \& Silverman (2004)
+\item Empirical Bayes shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)
 \item SureShrink using MAD estimator, Symmlet 8 basis (denoted by SURE, homo, Symm8). See Donoho \& Johnstone (1994)
-\item Bayesian shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)
+\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI-thresh, homo, Symm8). See Coifman \& Donoho (1995)
 \item SMASH given true variance, Symmlet 8 basis (denoted by SMASH, truth, Symm8)
-\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI, truth, Symm8)
+\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI-thresh, truth, Symm8)
 \end{enumerate}
@@
 (2001).
-At the same time, we included SureShrink as it performs well in terms of mean square bias.
+!!!!!!!!!!!!!!![describe these procedures earlier?]We also included three other adaptive methods, namely EbayesThresh by Johnstone \& Silverman (2005), the Empirical Bayes approach by Clyde \& George (1999,2000), as well as SureShrink, developed by Donoho \& Johnstone (1994).
+Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation.
+In particular, we provide two ways to estimate the variance function in TI-thresholding: method (3) uses the running MAD approach as described in Gao (1997), and method (4) uses the variance estimate from SMASH.
+On the other hand, methods (5)-(9) all assume homoskedasticity and estimate a constant variance.
+Specifically, EbayesThresh places a Laplace prior on the wavelet coefficients, and we fix the scale parameter of the Laplace prior to be 0.5, as the marginal maximum likelihood implementation often fails to converge.
+The posterior mean is then taken to be the final estimate of the wavelet coefficients.
+Details for the Empirical Bayes approach by Clyde \& George (1999,2000), SureShrink, and homoskedastic TI-thresholding can be found in Antoniadis et al.
+(2001).
+Further, we have ordered methods (5)-(9) in what we deem to be decreasing adaptivity.
+Finally, methods (10) and (11) are provided the true variance function and are included as benchmarks.
+Tables \ref{table:homo1} and \ref{table:homo3} displays the relative MSEs of various methods for the 7 test functions and 2 SNRs mentioned above, where the relative MSEs are the standard MSEs rescaled (for each test function and SNR) so that the baseline method has a MSE of 1.
+In our simulation study, the baseline method will be SMASH, using the Haar basis.
+ %At the same time, we included SureShrink as it performs well in terms of mean square bias.
 We also compared our method against two other Bayesian approaches, of which the method described in Clyde \& George (1999,2000) was also included in Antoniadis et al.
@@
 The other Bayesian approach, EbayesThresh, is more recent and and hence included as part of our study.
-Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation, while methods (5)-(9) all estimate a constant variance.
-Methods (10) and (11) are provided the true variance function and are included as benchmarks.
-Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above.
-Here MISE is defined as
-\begin{eqnarray}\label{eq:mise}
-MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
-\end{eqnarray}
-, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.
+%Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above. Here MISE is defined as
+%\begin{eqnarray}\label{eq:mise}
+%MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
+%\end{eqnarray}
+%, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.
 \begin{table}[ht]
@@
   \hline
-SMASH, joint, Haar & 57.1 & 146.5 & 65.0 & 50.6 & 76.8 & 24.1 & 8.2 \\
-  SMASH, joint, Symm8 & 60.1 & 152.7 & 97.7 & 49.5 & 53.4 & 35.5 & 7.7 \\
-  TI, RMAD, Symm8 & 84.0 & 253.7 & 152.2 & 66.7 & 70.2 & 42.0 & 8.6 \\
-  TI, SMASH, Symm8 & 79.2 & 218.8 & 144.9 & 65.7 & 67.7 & 40.7 & 8.4 \\
-  SMASH, homo, Symm8 & 61.0 & 154.9 & 100.2 & 50.1 & 54.9 & 35.8 & 7.8 \\
-  TI, homo, Symm8 & 82.7 & 235.5 & 150.5 & 66.7 & 68.4 & 41.4 & 8.5 \\
-  Ebayes, homo, Symm8 & 70.7 & 152.2 & 98.0 & 52.5 & 51.5 & 37.9 & 8.1 \\
-  SURE, homo, Symm8 & 369.1 & 418.1 & 301.4 & 482.4 & 275.8 & 272.1 & 97.4 \\
-  PostMean, homo, Symm8 & 101.4 & 185.1 & 113.0 & 86.2 & 70.5 & 53.2 & 13.3 \\
-  SMASH, truth, Symm8 & 60.9 & 153.6 & 100.0 & 50.1 & 54.9 & 35.5 & 7.7 \\
-  TI, truth, Symm8 & 83.1 & 234.7 & 150.8 & 67.1 & 69.1 & 41.3 & 8.5 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 1.05 & 1.04 & 1.50 & 1.00 & 0.69 & 1.50 & 0.94 \\
+  TI-thresh, RMAD, Symm8 & 2.03 & 2.38 & 3.34 & 1.63 & 1.17 & 2.34 & 1.28 \\
+  TI-thresh, SMASH, Symm8 & 1.40 & 1.54 & 2.32 & 1.35 & 0.89 & 1.74 & 1.07 \\
+  SMASH, homo, Symm8 & 1.05 & 1.05 & 1.53 & 1.00 & 0.71 & 1.51 & 0.94 \\
+  Ebayes, homo, Symm8 & 1.30 & 1.01 & 1.49 & 1.16 & 0.77 & 1.66 & 1.09 \\
+  PostMean, homo, Symm8 & 1.80 & 1.26 & 1.75 & 1.71 & 0.89 & 2.14 & 1.61 \\
+  SURE, homo, Symm8 & 6.26 & 2.83 & 4.60 & 9.45 & 3.28 & 10.63 & 11.41 \\
+  TI-thresh, homo, Symm8 & 1.47 & 1.64 & 2.39 & 1.37 & 0.90 & 1.74 & 1.08 \\
+  SMASH, truth, Symm8 & 1.05 & 1.04 & 1.52 & 1.00 & 0.70 & 1.51 & 0.94 \\
+  TI-thresh, truth, Symm8 & 1.45 & 1.59 & 2.35 & 1.36 & 0.90 & 1.72 & 1.07 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for iid Gaussian errors, SNR=1}
+\caption{Relative MSE of various methods for iid Gaussian errors, SNR=1}
 \label{table:homo1}
@@
   \hline
-SMASH, joint, Haar & 11.8 & 18.4 & 7.4 & 10.3 & 18.0 & 3.6 & 1.7 \\
-  SMASH, joint, Symm8 & 9.8 & 26.2 & 23.9 & 8.3 & 9.8 & 5.8 & 1.2 \\
-  TI, RMAD, Symm8 & 10.9 & 33.7 & 30.7 & 9.4 & 13.5 & 6.6 & 1.5 \\
-  TI, SMASH, Symm8 & 10.2 & 24.0 & 26.7 & 9.2 & 10.8 & 6.0 & 1.4 \\
-  SMASH, homo, Symm8 & 9.8 & 22.4 & 22.9 & 8.3 & 9.2 & 5.6 & 1.2 \\
-  TI, homo, Symm8 & 10.9 & 27.3 & 30.4 & 9.4 & 10.8 & 6.4 & 1.5 \\
-  Ebayes, homo, Symm8 & 10.8 & 24.8 & 23.3 & 9.0 & 9.3 & 5.9 & 1.3 \\
-  SURE, homo, Symm8 & 43.5 & 65.0 & 54.0 & 57.3 & 40.3 & 37.3 & 11.3 \\
-  PostMean, homo, Symm8 & 15.2 & 30.9 & 26.8 & 13.1 & 12.7 & 9.0 & 2.0 \\
-  SMASH, truth, Symm8 & 9.7 & 21.4 & 21.5 & 8.3 & 9.2 & 5.5 & 1.2 \\
-  TI, truth, Symm8 & 10.9 & 26.1 & 29.7 & 9.4 & 10.8 & 6.4 & 1.5 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 0.82 & 1.41 & 3.20 & 0.77 & 0.54 & 1.72 & 0.69 \\
+  TI-thresh, RMAD, Symm8 & 1.12 & 2.34 & 5.80 & 0.94 & 0.84 & 2.84 & 1.10 \\
+  TI-thresh, SMASH, Symm8 & 0.88 & 1.39 & 4.03 & 0.85 & 0.60 & 1.85 & 0.83 \\
+  SMASH, homo, Symm8 & 0.81 & 1.21 & 3.07 & 0.77 & 0.50 & 1.65 & 0.69 \\
+  Ebayes, homo, Symm8 & 0.96 & 1.36 & 2.98 & 0.88 & 0.58 & 1.76 & 0.83 \\
+  PostMean, homo, Symm8 & 1.28 & 1.69 & 3.63 & 1.18 & 0.70 & 2.54 & 1.13 \\
+  SURE, homo, Symm8 & 3.38 & 3.45 & 7.39 & 5.05 & 2.11 & 10.14 & 6.34 \\
+  TI-thresh, homo, Symm8 & 0.91 & 1.50 & 4.13 & 0.86 & 0.61 & 1.90 & 0.85 \\
+  SMASH, truth, Symm8 & 0.81 & 1.15 & 2.86 & 0.77 & 0.50 & 1.63 & 0.69 \\
+  TI-thresh, truth, Symm8 & 0.90 & 1.41 & 3.96 & 0.86 & 0.60 & 1.87 & 0.84 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for iid Gaussian errors, SNR=3}
+\caption{Relative MSE of various methods for iid Gaussian errors, SNR=3} 
 \label{table:homo3}
@@
   \hline
-SMASH, joint, Haar & 108.5 & 282.2 & 112.4 & 86.9 & 113.7 & 62.5 & 15.5 \\
-  SMASH, joint, Symm8 & 117.4 & 264.4 & 147.1 & 95.5 & 87.1 & 76.6 & 13.8 \\
-  TI, RMAD, Symm8 & 191.9 & 268.6 & 168.5 & 154.0 & 107.1 & 90.9 & 22.5 \\
-  TI, SMASH, Symm8 & 171.5 & 410.9 & 217.8 & 123.6 & 120.3 & 85.0 & 16.5 \\
-  SMASH, homo, Symm8 & 413.7 & 501.7 & 356.1 & 553.6 & 314.7 & 296.9 & 106.1 \\
-  TI, homo, Symm8 & 2007.9 & 1553.2 & 1416.9 & 3170.2 & 1460.2 & 1663.8 & 644.0 \\
-  SMASH, truth, Symm8 & 115.6 & 221.4 & 128.4 & 93.1 & 74.6 & 77.5 & 13.7 \\
-  TI, truth, Symm8 & 188.4 & 336.0 & 194.8 & 124.7 & 101.1 & 86.3 & 17.1 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 1.02 & 0.91 & 1.23 & 1.38 & 0.71 & 1.27 & 0.90 \\
+  TI-thresh, RMAD, Symm8 & 3.39 & 1.52 & 2.66 & 6.64 & 1.77 & 4.43 & 5.69 \\
+  TI-thresh, SMASH, Symm8 & 1.83 & 1.46 & 1.97 & 1.84 & 0.93 & 1.56 & 1.03 \\
+  SMASH, homo, Symm8 & 1.88 & 1.07 & 1.92 & 4.91 & 1.56 & 3.41 & 4.40 \\
+  TI-thresh, homo, Symm8 & 8.66 & 2.79 & 6.73 & 29.84 & 7.15 & 19.45 & 29.05 \\
+  SMASH, truth, Symm8 & 1.00 & 0.71 & 1.14 & 1.33 & 0.55 & 1.13 & 0.85 \\
+  TI-thresh, truth, Symm8 & 1.88 & 1.22 & 1.81 & 1.83 & 0.78 & 1.42 & 1.04 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=1, Gaussian errors}
+\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=1, Gaussian errors} 
 \label{table:hetero_v2_1}
@@
   \hline
-SMASH, joint, Haar & 22.0 & 49.7 & 19.1 & 16.9 & 23.3 & 10.2 & 3.0 \\
-  SMASH, joint, Symm8 & 20.4 & 59.2 & 40.0 & 14.3 & 11.7 & 18.7 & 2.7 \\
-  TI, RMAD, Symm8 & 25.2 & 53.5 & 35.6 & 19.4 & 16.7 & 17.4 & 3.8 \\
-  TI, SMASH, Symm8 & 24.3 & 64.7 & 43.5 & 16.1 & 14.4 & 18.9 & 3.3 \\
-  SMASH, homo, Symm8 & 50.8 & 64.1 & 58.5 & 65.2 & 39.9 & 37.7 & 12.6 \\
-  TI, homo, Symm8 & 225.3 & 174.0 & 159.5 & 354.4 & 156.5 & 186.0 & 71.8 \\
-  SMASH, truth, Symm8 & 20.0 & 43.6 & 31.0 & 13.9 & 9.1 & 19.2 & 2.6 \\
-  TI, truth, Symm8 & 25.9 & 66.6 & 42.8 & 17.1 & 10.0 & 22.2 & 3.6 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 0.83 & 1.26 & 2.34 & 1.11 & 0.45 & 1.90 & 0.72 \\
+  TI-thresh, RMAD, Symm8 & 2.12 & 1.68 & 3.03 & 4.09 & 0.90 & 3.55 & 3.39 \\
+  TI-thresh, SMASH, Symm8 & 0.98 & 1.48 & 3.17 & 1.32 & 0.50 & 2.17 & 0.84 \\
+  SMASH, homo, Symm8 & 1.68 & 1.16 & 2.50 & 3.18 & 1.09 & 2.83 & 2.65 \\
+  TI-thresh, homo, Symm8 & 6.72 & 2.34 & 5.18 & 17.54 & 3.61 & 13.22 & 16.13 \\
+  SMASH, truth, Symm8 & 0.80 & 0.84 & 1.66 & 1.07 & 0.35 & 1.80 & 0.70 \\
+  TI-thresh, truth, Symm8 & 0.99 & 1.15 & 2.34 & 1.29 & 0.38 & 2.11 & 0.83 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for variance function V2 as in Cai \& Wang (2008), SNR=3, Gaussian errors}
+\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=3, Gaussian errors}
 \end{table}
@@
   \hline
-SMASH, joint, Haar & 223.1 & 650.9 & 275.9 & 233.6 & 232.6 & 148.0 & 47.4 \\
-  SMASH, joint, Symm8 & 231.7 & 606.4 & 293.6 & 263.1 & 194.9 & 154.4 & 44.5 \\
-  TI, RMAD, Symm8 & 1621.6 & 1464.5 & 1221.0 & 2543.6 & 1197.5 & 1334.5 & 512.2 \\
-  TI, SMASH, Symm8 & 335.9 & 798.1 & 422.0 & 385.4 & 274.6 & 207.8 & 62.5 \\
-  SMASH, homo, Symm8 & 1242.1 & 1199.3 & 940.4 & 1836.5 & 910.0 & 973.8 & 366.3 \\
-  TI, homo, Symm8 & 3289.2 & 2543.4 & 2310.3 & 5206.6 & 2404.7 & 2731.0 & 1060.4 \\
-  SMASH, truth, Symm8 & 114.0 & 633.3 & 214.9 & 115.9 & 100.6 & 81.5 & 15.6 \\
-  TI, truth, Symm8 & 171.0 & 799.0 & 324.7 & 170.4 & 140.0 & 95.0 & 18.6 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 1.00 & 0.93 & 1.05 & 1.08 & 0.83 & 1.02 & 0.92 \\
+  TI-thresh, RMAD, Symm8 & 5.52 & 2.00 & 3.71 & 7.88 & 4.08 & 6.70 & 7.72 \\
+  TI-thresh, SMASH, Symm8 & 1.13 & 1.20 & 1.40 & 1.25 & 0.95 & 1.11 & 1.00 \\
+  SMASH, homo, Symm8 & 5.11 & 1.85 & 3.35 & 7.07 & 3.81 & 6.07 & 6.90 \\
+  TI-thresh, homo, Symm8 & 13.47 & 3.94 & 8.21 & 19.95 & 10.02 & 16.94 & 19.78 \\
+  SMASH, truth, Symm8 & 0.45 & 0.93 & 0.72 & 0.41 & 0.39 & 0.47 & 0.28 \\
+  TI-thresh, truth, Symm8 & 0.66 & 1.19 & 1.11 & 0.60 & 0.55 & 0.56 & 0.33 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for the Bumps variance function, SNR=1, Gaussian errors}
+\caption{Relative MSE of various methods for the Bumps variance function, SNR=1, Gaussian errors}
 \end{table}
@@
   \hline
-SMASH, joint, Haar & 34.9 & 137.1 & 56.0 & 32.9 & 46.9 & 20.5 & 6.9 \\
-  SMASH, joint, Symm8 & 29.4 & 122.2 & 71.3 & 33.8 & 30.8 & 28.7 & 5.9 \\
-  TI, RMAD, Symm8 & 174.8 & 183.1 & 153.4 & 286.2 & 137.0 & 152.1 & 57.4 \\
-  TI, SMASH, Symm8 & 41.4 & 148.1 & 86.5 & 49.2 & 41.5 & 35.5 & 8.5 \\
-  SMASH, homo, Symm8 & 141.3 & 167.3 & 127.7 & 209.1 & 112.9 & 114.0 & 41.6 \\
-  TI, homo, Symm8 & 366.6 & 286.7 & 259.9 & 580.2 & 264.8 & 304.2 & 118.0 \\
-  SMASH, truth, Symm8 & 14.9 & 162.9 & 67.1 & 16.9 & 16.0 & 13.2 & 2.5 \\
-  TI, truth, Symm8 & 17.1 & 242.4 & 82.9 & 23.0 & 20.7 & 16.8 & 2.9 \\
+SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
+  SMASH, joint, Symm8 & 0.83 & 0.87 & 1.23 & 0.98 & 0.66 & 1.33 & 0.86 \\
+  TI-thresh, RMAD, Symm8 & 4.10 & 1.25 & 2.41 & 6.42 & 2.35 & 5.58 & 6.27 \\
+  TI-thresh, SMASH, Symm8 & 0.88 & 1.14 & 1.60 & 1.12 & 0.67 & 1.60 & 0.95 \\
+  SMASH, homo, Symm8 & 3.85 & 1.20 & 2.26 & 5.80 & 2.37 & 5.10 & 5.63 \\
+  TI-thresh, homo, Symm8 & 9.95 & 2.06 & 4.60 & 16.02 & 5.52 & 13.50 & 15.85 \\
+  SMASH, truth, Symm8 & 0.39 & 1.12 & 1.13 & 0.44 & 0.32 & 0.58 & 0.32 \\
+  TI-thresh, truth, Symm8 & 0.45 & 1.65 & 1.39 & 0.60 & 0.41 & 0.72 & 0.37 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for the Bumps variance function, SNR=3, Gaussian errors}
+\caption{Relative MSE of various methods for the Bumps variance function, SNR=3, Gaussian errors} 
 \label{table:hetero_bump_3}
@@
 The low intensity scenario of (0.01,3) was chosen to reflect the small number of counts often present in certain types of high-throughput sequencing data, an application we will demonstrate in more detail later on.
-To assess the performance of our method, we used the same MISE as defined above for the Gaussian case, and considered the following methods in our simulation study:
+To assess the performance of our method, we used the same relative MSE as defined above for the Gaussian case, and considered the following methods in our simulation study:
 \begin{enumerate}
@@
 \item Corrected Haar thresholds using hard thresholding (denoted by Haar thresholds). See Kolazyk (1997).
-\item Conditional variance stabilization with the non-decimated wavelet transform (denoted by CVS). See Jansen (2006).
 \item Bayesian multi-scale multiplicative innovations model (denoted by BMMIM). See Timmermann \& Nowak (1999).
@@
 The Haar-Fisz transform uses 50 external cyclespins as suggested by Fryzlewicz \& Nason (2004).
-The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation and CVS use the Symmlet 10 basis, as recommended by the corresponding software.
-Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 5,6 and 7 for all other methods.
-We present the MISEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\
+The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation uses the Symmlet 10 basis, as recommended by the corresponding software.
+Out of the three Bayesian methods included in this simulation study, SMASH and BMSM both estimate the hyperparameters for their respective priors by maximum likelihood, while BMMIM uses fixed hyperparameters as recommended in Besbeas (2004).
+In addition, we also considered the conditional variance stabilization (CVS) approach described in Jansen (2006).
+However, we did not include the MSEs for CVS as we did not obtain sensible results, and are wary that we were misusing the software.
+Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 4,5,6 and 7 for all other methods.
+We present the relative MSEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\
 \begin{table}[ht]
@@
   \hline
-SMASH & 145.3 & 68.5 & 10.2 \\
-  Haar-Fisz & 369.5 & 140.4 & 9.8 \\
-  Anscombe, universal & 459.0 & 163.7 & 10.1 \\
-  Anscombe, CV & 458.8 & 162.6 & 10.1 \\
-  Haar thresholds & 295.8 & 168.3 & 89.4 \\
-  CVS & 5201.1 & 1083.5 & 122.8 \\
-  BMMIM & 277.2 & 110.1 & 18.1 \\
-  BMSM & 147.4 & 73.9 & 10.5 \\
+SMASH & 1.00 & 1.00 & 1.00 \\
+  BMSM & 1.15 & 1.04 & 1.01 \\
+  BMMIM & 1.53 & 1.49 & 21.99 \\
+  Haar-Fisz & 2.05 & 2.47 & 4.36 \\
+  Anscombe, universal & 2.61 & 2.80 & 4.24 \\
+  Haar thresholds & 1.52 & 1.66 & 12.17 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for the Angles function for Poisson data}
+\caption{Relative MSE of various methods for the Clipped Blocks function for Poisson data} 
 \label{table:pois_angles}
@@
 
-\begin{table}[ht]
+begin{table}[ht]
 \centering
@@
   \hline
-SMASH & 2597.5 & 1194.6 & 141.2 \\
-  Haar-Fisz & 2849.9 & 1572.3 & 184.0 \\
-  Anscombe, universal & 3500.0 & 2029.9 & 194.9 \\
-  Anscombe, CV & 3520.7 & 2070.0 & 196.3 \\
-  Haar thresholds & 3151.9 & 1601.4 & 173.7 \\
-  CVS & 9410.7 & 3457.5 & 194.9 \\
-  BMMIM & 3089.9 & 2065.3 & 222.2 \\
-  BMSM & 4036.8 & 1889.9 & 171.1 \\
+SMASH & 1.00 & 1.00 & 1.00 \\
+  BMSM & 1.55 & 1.58 & 1.21 \\
+  BMMIM & 1.32 & 1.86 & 2.06 \\
+  Haar-Fisz & 1.20 & 1.39 & 1.31 \\
+  Anscombe, universal & 1.55 & 1.88 & 1.39 \\
+  Haar thresholds & 1.35 & 1.38 & 1.23 \\
    \hline
 \end{tabular}
-\caption{MISEs of various methods for the Bumps function for Poisson data}
+\caption{Relative MSE of various methods for the Bumps function for Poisson data}
 \label{table:pois_bumps}
@@
 Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1.
-Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
-\begin{figure}[h]
-\centering
-\includegraphics[scale=0.7]{smoothing_all.pdf}
-\caption{Estimated intensities from SMASH for 4 samples; the first two samples are two replicates from GM12878, a lymphoblastoid cell line, and the last two samples are two replicates from H1hesc, which are human embryonic stem cells.
+%Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
+%\begin{figure}[h]
+%\centering
+%\includegraphics[scale=0.7]{smoothing_all.pdf}
+%\caption{Estimated intensities from SMASH for 4 samples; the first two samples are two replicates from GM12878, a lymphoblastoid cell line, and the last two samples are two replicates from H1hesc, which are human embryonic stem cells.
 The reads are taken from position 880001 to 1011072 on chromosome 1.}
-\label{fig:seq_smooth}
-\end{figure}
-\bigskip
+%\label{fig:seq_smooth}
+%\end{figure}
+%\bigskip
 One goal of analyzing ChIP-seq data is to discover regions where transcription factors are likely to bind to DNA, thereby allowing us to better understand the mechanisms underlying gene regulation.
@@
 Our method allows us to identify these peaks by looking at the estimated intensity function.
-In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
-To ensure that our method performs sensibly, we took the same region from only the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the region.
+%In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
+To ensure that our method performs sensibly, we pooled the reads for the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region.
 The results are shown in Figure \ref{fig:seq_peak}.\\

### 2015-05-04 paper/table_gaus.R

@@ -1,9 +1,9 @@
 library(xtable)
 
-scale.baseline = function(x) x/x[2]
+scale.baseline = function(x) x/x[1]
 
 mise.res = aggregate(mise ~ method + scenario, res, mean)
-table.order = c(6, 10, 16, 17, 8, 3, 5, 13, 14, 12, 20)
+table.order = c(6, 10, 16, 18, 8, 3, 5, 13, 14, 12, 20)
 colname.order = c(7, 4, 3, 1, 6, 2, 5)
 
 tex.row.names = c("SMASH, joint, Haar",
@@ -42,31 +42,33 @@ for(i in 1:dim(design)[1]){
   assign(paste0("table",table.suffix),table.temp)
 }
 
-print(xtable(table.1.v1,caption="MISE of various methods for iid Gaussian errors, RSNR=1",digits=1))
-print(xtable(table.3.v1,caption="MISE of various methods for iid Gaussian errors, RSNR=3",digits=1))
+ndigits=2
+
+print(xtable(table.1.v1,caption="Relative MSE of various methods for iid Gaussian errors, SNR=1",digits=ndigits))
+print(xtable(table.3.v1,caption="Relative MSE of various methods for iid Gaussian errors, SNR=3",digits=ndigits))
 
 
 ####
 
-print(xtable(table.1.v2,caption="MISE of various methods for variance function V2 as in Cai & Wang (2008), RSNR=1",digits=1))
-print(xtable(table.3.v2,caption="MISE of various methods for variance function V2 as in Cai & Wang (2008), RSNR=3",digits=1))
-print(xtable(table.1.v3,caption="MISE of various methods for the Doppler variance function, RSNR=1",digits=1))
-print(xtable(table.3.v3,caption="MISE of various methods for the Doppler variance function, RSNR=3",digits=1))
-print(xtable(table.1.v4,caption="MISE of various methods for the Bumps variance function, RSNR=1",digits=1))
-print(xtable(table.3.v4,caption="MISE of various methods for the Bumps variance function, RSNR=3",digits=1))
-print(xtable(table.1.v5,caption="MISE of various methods for the Clipped Blocks variance function, RSNR=1",digits=1))
-print(xtable(table.3.v5,caption="MISE of various methods for the Clipped Blocks variance function, RSNR=3",digits=1))
+print(xtable(table.1.v2,caption="Relative MSE of various methods for variance function V2 as in Cai & Wang (2008), SNR=1, Gaussian errors",digits=ndigits))
[…]

### 2015-05-04 paper/table_pois.R

@@ -1,41 +1,65 @@
 library(xtable)
 
+scale.baseline = function(x) x/x[1]
+
 tex.row.names=c("SMASH",
-"Haar-Fisz",
-"Anscombe, universal",
-"Anscombe, CV",
-"Haar thresholds",
-"CVS",
-"BMMIM",
-"BMSM"
+                "BMSM",
+                "BMMIM",
+                "Haar-Fisz",
+                "Anscombe, universal",
+                "Haar thresholds"
 )
 
 tex.col.names=c("(0.01,3)","(1/8,8)","(1/128,128)")
 
 
-mise.s.1.table=mise.s.1[c(1,4,8,7,9,5,3,2)]
-mise.s.8.table=mise.s.8[c(1,4,8,7,9,5,3,2)]
-mise.s.128.table=mise.s.128[c(1,4,8,7,9,5,3,2)]
+# mise.s.1.table=mise.s.1[c(1,4,8,7,9,5,3,2)]
+# mise.s.8.table=mise.s.8[c(1,4,8,7,9,5,3,2)]
+# mise.s.128.table=mise.s.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.ang.1.table=mise.ang.1[c(1,4,8,7,9,5,3,2)]
+# mise.ang.8.table=mise.ang.8[c(1,4,8,7,9,5,3,2)]
+# mise.ang.128.table=mise.ang.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.bur.1.table=mise.bur.1[c(1,4,8,7,9,5,3,2)]
+# mise.bur.8.table=mise.bur.8[c(1,4,8,7,9,5,3,2)]
+# mise.bur.128.table=mise.bur.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.cb.1.table=mise.cb.1[c(1,4,8,7,9,5,3,2)]
+# mise.cb.8.table=mise.cb.8[c(1,4,8,7,9,5,3,2)]
+# mise.cb.128.table=mise.cb.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.b.1.table=mise.b.1[c(1,4,8,7,9,5,3,2)]
+# mise.b.8.table=mise.b.8[c(1,4,8,7,9,5,3,2)]
+# mise.b.128.table=mise.b.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.hs.1.table=mise.hs.1[c(1,4,8,7,9,5,3,2)]
[…]

### 2015-05-21 paper/plot_gaus.R
small changes; wrote code to mark out best method

@@ -1,0 +1,111 @@
+library(dplyr)
+library(reshape2)
+library(ggplot2)
+
+
+##plots in main body of paper
+mean.table = melt(table.1.v1)
+names(mean.table) = c("method", "testfunction", "mse")
+
+pdf("paper/smash_gaus_1_v1.pdf",width = 10, height = 5)
+ggplot(mean.table %>% filter(method != "SURE, homo, Symm8"
+                             & method != "SMASH, truth, Symm8"
+                             & method != "TI-thresh, truth, Symm8"
+                             & method != "TI-thresh, SMASH, Symm8"
+                             & method != "SMASH, joint, Haar"), aes(x = testfunction, y = mse, fill = method)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  xlab("Test Function") + 
+  ylab("Relative MSE") + 
+  ggtitle("MSE of various methods relative to \"SMASH, joint, Haar\", for i.i.d. Gaussian noise, SNR = 1") +
+  geom_abline(intercept = 1, slope = 0, linetype = 2, size = 0.3)
+dev.off()
+
+
+mean.table = melt(table.3.v1)
+names(mean.table) = c("method", "testfunction", "mse")
+
+pdf("paper/smash_gaus_3_v1.pdf",width = 10, height = 5)
+ggplot(mean.table %>% filter(method != "SURE, homo, Symm8"
+                             & method != "SMASH, truth, Symm8"
+                             & method != "TI-thresh, truth, Symm8"
+                             & method != "TI-thresh, SMASH, Symm8"
+                             & method != "SMASH, joint, Haar"), aes(x = testfunction, y = mse, fill = method)) +
+  geom_bar(stat = "identity", position = "dodge") +
+  xlab("Test Function") + 
+  ylab("Relative MSE") + 
+  ggtitle("MSE of various methods relative to \"SMASH, joint, Haar\", for i.i.d. Gaussian noise, SNR = 3") +
+  geom_abline(intercept = 1, slope = 0, linetype = 2, size = 0.3)
+dev.off()
+
+
+
+# qplot(x = testfunction, y = mse, fill = method, xlab = "Test Function", ylab = "Relative MSE", main = "MSE of various methods relative to \"SMASH, joint, Haar\", for i.i.d. Gaussian noise, SNR = 1",
+#                        data = mean.table %>% filter(method != "SURE, homo, Symm8"
+#                                                     & method != "SMASH, truth, Symm8"
[…]

### 2015-06-01 paper/draft_3.tex
some text revision

--- 2015-05-04 paper/draft_2.tex
@@
 \section{Introduction}
-In recent years, the use of various shrinkage and thresholding procedures has become ever more popular in a variety of applications where sparsity is a desirable notion.
-Here the term ``sparsity'' is loosely defined in the sense that it also includes the case where there are many near-zero (as opposed to exactly zero) terms, as shrinkage procedures often produce.
+In recent years, various shrinkage and thresholding procedures have become ever more popular in many applications where sparsity is desired.
+Here ``sparsity'' is loosely defined in that it also includes the case where many terms are near-zero, as opposed to exactly zero.
 The most prominent usage of such procedures appear in multiresolution denoising analyses such as wavelets, where sparsity in a transformed domain often corresponds to smoothness in the data space [references].
-Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are usually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references].
+Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are actually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references].
 In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.\bigskip\\
@@
 These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994).
-Not only are wavelet methods locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, but they are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001].
+Wavelet methods are locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, yet are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001].
 While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al.
 (2001) has demonstrated that various Bayesian shrinkage methods are usually more data adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE).
-However, many existing Bayesian wavelet methods are often computationally intensive, and may not be practical for large scale applications.
-Furthermore, it is not easy to apply the same thresholding or Bayesian shrinkage rules to other nonparametric regression problems, two of which we subsequently describe.
-On the other hand, our method is computationally faster than previous Bayesian methods while still possessing good finite sample performance, and uses ASH as the common shrinkage procedure in both the problems.\bigskip\\
-The first problem relates to the frequently encountered Gaussian case.
-Although the theory for mean estimation with homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], the existing methods for variance estimation with heteroskedastic errors have been far and few between.
+However, many Bayesian methods require specific distributional assumptions, and are not easily extensible to more complex problems, two of which we subsequently describe.
+On the other hand, our method simplies the task by making approximations, while still possessing good finite sample performance and computational efficiency.
+These approximations also allows us to use ASH as the common shrinkage procedure in both the problems.\bigskip\\
+The first problem relates to mean and variance estimation with Gaussian noise.
+Although the framework for homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], existing methods dealing with heteroskedastic errors have been far and few between.
 Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators.
-Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous approaches using a wavelet thresholding approach on first order differences.
-While Cai \& Wang (2008) proved that their technique was asymptotically optimal, we will demonstrate how we can further improve the finite sample performance of previous variance estimation procedures by incorporating ASH into a novel wavelet denoising framework.
+Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous variance estimation methods using a wavelet thresholding approach on first order differences.
+Here we present an approach that estimates both the mean and variance accurately by incorporating ASH into a novel wavelet denoising framework.
 [mention the lack of available software?]\bigskip\\
@@
 This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest.
-This problem is particularly interesting in the sense that there are many different ways to perform signal recovery.
-Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by noting that the variance of a Poisson count is equal to its mean.
+This problem is interesting in that there are many different ways to perform signal recovery.
+Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by exploiting the mean-variance relationship of a Poisson distribution.
 Kolaczyk (1997, 1999a) derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d.
 Gaussian case.
-However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in optimal finite sample performance.
-Furthermore, both these methods are quite sensitive to the choice of the primary resolution level due to the Poisson nature of the data.
+However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance.
+Furthermore, both these methods are quite sensitive to the choice of the primary resolution level as simulations have shown.
 Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by Kolaczyk (1999b) to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen.
@@
 \bigskip\\
-Both these problems are generally harder to deal with than the classical problem of i.i.d.
-Gaussian errors, and usually requires some work in extending the ideas from methods aimed at the latter task.
+Both the aforementioned problems are harder to deal with than the classical problem of i.i.d.
+Gaussian errors, and usually requires one to extend the ideas from the latter task.
 Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage.
@@
 \end{eqnarray}
-Note that $\bm{\pi}$ and $\bm{s}^2$ is shared across all the $\Gb_i$'s, allowing one to borrow information across all the observations.
+Note that $\bm{\pi}$ and $\bm{s}^2$ are shared across all the $\Gb_i$'s, allowing one to borrow information across all observations.
 The full likelihood for $\bm{\pi}$ given $\bm{\hat{\Gb}}$ and $\bm{\hat{\s}}$ is then a product of likelihoods for $\bm{\pi}$ given each $\hat{\Gb}_i$ and $\hat{\s}_i$.
@@
 The posterior mean of $\Gb_i$ is taken to be the point estimate of $\Gb_i$, resulting in a shrinkage procedure.\bigskip\\
-The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet setting described here.
-As with many other Bayesian procedures, ASH borrows information across all available data, and is hence extremely data adaptive.
-At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a name for this?) is that it allows for variable variances as input, a feature that the latter methods lack.
+The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet settings described here.
+As an Empirical Bayes procedure, ASH borrows information across all available data and is extremely data adaptive.
+At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a name for this?) variable variances are allowed as input, a feature which latter methods lack.
 This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above.
 Furthermore, Gaussian mixture priors can effectively approximate any unimodal distribution, allowing for a more flexible prior than many other procedures.
-At the same time, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising too much accuracy.
-It should be noted that typical wavelet methods require the specification of a primary resolution level as an extra parameter, which could substantially influence the accuracy of the method.
-However, we are able to apply ASH to every resolution in the wavelet transformation, sparing the need for such a parameter.
+In tackling these two specific problems, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising accuracy.
+Typical wavelet methods require the specification of a primary resolution level as a ``tuning'' parameter, which could substantially influence the accuracy of the method.
+However, applying ASH to every resolution in the wavelet transformationwe spares us the need for such a parameter.
 For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??).
-With the main shrinkage method accounted for, we will now proceed to explore the two aforementioned problems in detail.
+With the main shrinkage method accounted for, we will proceed to explore the two aforementioned problems in detail.
 Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.
@@
 $\pi_i^{(j)}$ and $(s_i^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level, and $m$ is the number of mixture components.
-In ASH, $m$ is usually chosen so that it is large enough to reasonably approximate any unimodal distribution, while maintaining a reasonable computational speed.
+In ASH, $m$ is usually chosen so that it is large enough to reasonably approximate any unimodal distribution, while maintaining an acceptable computational speed.
 Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,J$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$.
@@
 One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize.
-If the true variances were known, one could obviously write out the full likelihood and proceed to compute the posterior mean/median using some specified prior.
+Given the true variances and hence the likelihood, one could compute the posterior distribution using some specified prior.
 However, this would be computationally cumbersome, and may not be feasible when extended to multiple signals or higher dimensions.
@@
 For the rest of this subsection, we will use the non-decimated wavelet transform (NDWT) instead of the standard DWT to achieve translation invariance.
-This property of translation invariance reduces the presence of artifacts, which often occur near discontinuities in the underlying signal (see eg.
+This in turn reduces the presence of artifacts, which often occur near discontinuities in the underlying signal (see eg.
 Coifman \& Donoho (1995)).
@@
 where $P(d_{jk}|\Ga_{jk})=\phi(d_{jk};\Ga_{jk},\tilde{\Sigma}_{(jk,jk)})$.
-Note that there are $n$ coefficients at each resolution level instead of $2^j$ for resolution $j$ because we are using the NDWT instead of the standard wavelet transform.
+Note that there are $n$ coefficients at each resolution level instead of $2^j$ for resolution $j$ due to the NDWT.
 Here $\phi$ denotes the Gaussian density function.
@@
 Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, which takes only $n\log(n)$ time.\bigskip\\
-While we assumed that the true variances are known for mean estimation, the problem of variance estimation itself is a non-trivial one.
+Although we have assumed that the true variances were known for mean estimation, the problem of variance estimation itself is a non-trivial one.
 Here we make the reasonable assumption that the variance function is also spatially structured, in addition to the mean function.
@@
 However, while they use first order differences, we look at the squared residuals.
-As such, we need a reasonably accurate estimator of the mean function in order to form sensible residuals.
+As such, we need a reasonably accurate estimator of the mean function to form sensible residuals.
 For clarity of presentation, we will first assume that the true mean function is known.
@@
 Now that we can now estimate $\bm{\mu}$ given $\bm{\s}^2$ and vice versa, a natural procedure for jointly estimating $\bm{\mu}$ and $\bm{\s}^2$ is an iterative one.
-That is, we estimate $\bm{\mu}$ given some initial estimate of $\bm{\s}^2$, then estimate $\bm{\s}^2$ given the previous estimate of $\bm{\mu}$, and repeat this procedure for as long as is necessary.
-Although this iterative procedure (using squared residuals) could go on for a long time, and convergence is difficult to prove, we found via simulations that two cycles is usually sufficient to produce relatively accurate estimates.
-A natural initial estimate would be the square of first order differences between adjacent points, as discussed in previous variance estimation papers (eg Cai \& Wang (2008)).
+That is, we estimate $\bm{\mu}$ given some initial estimate of $\bm{\s}^2$, then estimate $\bm{\s}^2$ given the previous estimate of $\bm{\mu}$, and iterate the process.
+In our simulations, we have found that two cycles are usually sufficient to produce relatively accurate estimates.
+To start off the algorithmm, an initial estimate would be the square of first order differences between adjacent points, as discussed in previous variance estimation papers (eg Cai \& Wang (2008)).
 This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough.
@@
 \end{eqnarray}
-where $Y_0\equiv Y_n$ and $Y_{n+1}\equiv Y_1$, since wavelet methods typically assume that the function is periodic.
-In summary, our approach for joint mean and variance estimation can be described in three steps:
+where $Y_0\equiv Y_n$ and $Y_{n+1}\equiv Y_1$, due to periodicity assumptions in wavelet methods. In summary, our approach for joint mean and variance estimation can be described in three steps:
 \begin{enumerate}
-\item Using squared first order differences \eqref{eq:initial var est} as our estimates of $\bm{\s}^2$, we estimate $\bm{\mu}$ as if $\bm{\s}^2$ was known (see the above procedure for the case when $\bm{\s}^2$ is known)
+\item Using squared first order differences \eqref{eq:initial var est} as estimates of $\bm{\s}^2$, estimate $\bm{\mu}$ as if $\bm{\s}^2$ was known (see above for the case when $\bm{\s}^2$ is known)
 \item Given the estimate of $\bm{\mu}$, take squared residuals and treat those as ``observations'' for $\bm{\s}^2$.
-Next, we project them into wavelet space and apply some form of shrinkage to the wavelet coefficients, before projecting them back into data space to obtain an estimate of $\bm{\s}^2$.
+Next, project them into wavelet space and apply shrinkage to the wavelet coefficients, before projecting them back into data space to obtain an estimate of $\bm{\s}^2$.
 \item Repeat steps (1)-(2) once to obtain the final estimates of $\bm{\mu}$ and $\bm{\s}^2$ respectively.
@@
 Next we turn to another popular nonparametric regression problem and demonstrate how we could make use of ASH.
-Specifically, we assume an underlying signal $\Gl_i$, $i=1,...,n$ with $n=2^J$ for some positive integer $J$ as with the Gaussian case.
+Specifically, we also assume an underlying signal $\Gl_i$, $i=1,...,n$ with $n=2^J$ for some positive integer $J$.
 Further assume that each data point $Y_i$, $i=1,...,n$ is realized from a Poisson distribution with mean $\Gl_i$ ie.
@@
 \begin{eqnarray}Y_{jk}=Y_{j+1,2k}+Y_{j+1,2k+1}\end{eqnarray}
-for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$, so that we are looking at the sum of adjacent pairs of ``points'' as we move to coarser resolutions, where a point is already itself a sum of the true data points.
+for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$, so that we are looking at the sum of adjacent pairs of ``points'' as we move to coarser resolutions, where a point is already itself a sum of the data points.
 Another way to define the $Y$'s is
@@
 Note that $Y_{00}|\Gl_{00}\sim \textrm{Pois}(\Gl_{00})$.
-Now for any give $j,k$, $Y_{jk}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable.
+For any given $j,k$, $Y_{jk}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable.
 Hence
 \[Y_{j+1,2k}|Y_{jk},\Ga_{jk}\sim \textrm{Bin}({Y_{jk},\frac{1}{1+e^{-\Ga_{jk}}}\equiv\frac{\Gl_{j+1,2k}}{\Gl_{jk}}})\]
-Whereas Kolaczyk (1999) sets a conjugate prior (which is a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and uses a Binomial likelihood, we felt that the two-component mixture prior is too inflexible.
+Whereas Kolaczyk (1999) sets a conjugate shrinkage prior (a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and uses a Binomial likelihood, we felt that the two-component mixture prior is too inflexible.
 As such, we work with the parameters $\Ga_{sl}$ as defined in \eqref{eq:poisson wc} and approximate the logit-Binomial (is there such a thing?) likelihoods by Gaussian likelihoods.
@@
 Next, we approximate the distribution of $\hat{\Ga}$ by a Gaussian distribution, so that the likelihood for $\Ga$ is automatically Gaussian, given by $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$.
-To that end, we propose a mix of Berkson's estimator and Tukey's estimator as suggested in Gart \& Zweifel (1967).
-Specifically, our final estimators for $\Ga$ and its standard error are given by
+To that end, our final estimator will still be the MLE, but with Tukey's modification (Gart \& Zweifel (1967)) at the endpoints where $S=\{0,N\}$.
+Specifically, the estimator for $\Ga$ and its standard error are given by
 \begin{eqnarray}\label{eq:pseudoMLE1}
@@
 The other two variance estimators from Gart \& Zweifel (1967), $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.\bigskip\\
-Finally, to reconstruct the signal in the original space using the posterior distribution of the $\Ga$'s (which are in the logit space), we make use of the Delta method.
+Finally, the Delta method is used to reconstruct the signal in the original space from the posterior distribution of the $\Ga$'s (which are in the logit space).
 For full details on the reconstruction process as well as the Delta method, see Appendix \ref{app:reconstruction}.
@@
 We also note that our method can nearly achieve the ``optimal'' MISE (ie the MISE for the case when our method is given the true variance) for variance function $V_2$, but not for the other.
-This is likely due to the fact that function $V_2$ is relatively smooth, and hence easier to estimate than the extremely jumpy and peaky Bumps function.
+This is likely because function $V_2$ is relatively smooth, and hence is easier to estimate than the extremely jumpy and peaky Bumps function.
 Furthermore, the MISEs of our method are often smaller than the ones produced by TI-thresholding even when TI-thresholding is supplied the true variance function, where the latter procedure has been shown to be asymptotically optimal (see Gao (1997)).
@@
 To further ensure that the input to the Gaussian denoising method is periodic, we then reflected the new dataset about the right edge and used this as the final input.
-In order to obtain the original mean and variance functions, we extracted the first $n$ points from the outputs (mean and variance) of our denoising technique.
+To obtain the original mean and variance functions, we extracted the first $n$ points from the outputs (mean and variance) of our denoising technique.
 Since the data points are not evenly spaced, we took the simplest approach and applied our method treating the observations as if they were evenly spaced.
@@
 
-begin{table}[ht]
+\begin{table}[ht]
 \centering
@@
 This deals with the second complication.
-The estimated mean and conditional variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.\bigskip\\
+The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.\bigskip\\
 \begin{figure}[h]
@@
 In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques.
-Both the applications discussed in this paper relaxes the standard assumption of i.i.d.
-Gaussian noise, and thus present us with challenging tasks.
-Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, allowing it to be potentially used in a variety of other applications where shrinkage is desirable.\bigskip\\
-In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as approximate credible intervals to provide uncertainty estimates.
-In the case of (possibly heteroskedastic) Gaussian errors, we are able to estimate the variance function as well, which can be used to provide frequentist confidence intervals for other forms of mean estimation.
+Both applications discussed in this paper relax the standard assumption of i.i.d.
+Gaussian noise, and are thus challenging tasks.
+Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, demonstrating its potential in many other applications.\bigskip\\
+In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as approximate credible intervals as a measure of uncertainty.
+In addition, we can also estimate the variance function if desired, which can be used to provide frequentist confidence intervals for other forms of mean estimation.
 To the best of our knowledge, there is no readily available software which implements joint mean and variance estimation in the wavelet literature.
-We have also tested our method in simulations and found that it is relatively robust to simple forms of autocorrelation between the errors (details needed).
-In the case of Poisson regression, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods by utilizing ASH as the shrinkage procedure, which allows for more flexibility and precision.
-In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution.
-In both of the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used.
-On the other hand, the so-called primary resolution level in almost all of the other wavelet-based methods actually affects their performance substantially, depending on the underlying mean and/or variance function.
+We have also confirmed through simulations that our method is relatively robust to simple forms of autocorrelation between the errors (details needed).
+In the case of Poisson regression, we improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods by utilizing ASH as the shrinkage procedure, which allows for more flexibility and precision.
+%In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution.
+In both the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used.
+On the other hand, the primary resolution level in almost all of the other wavelet-based methods actually affects their performance in varying degrees, depending on the underlying mean and/or variance function.
 Hence, our fully adaptive procedures allow users to easily apply them to any given dataset, depending on context.\bigskip\\
@@
 Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussians used indicate that our methods are computationally fast, since the posteriors can be computed analytically.
-In the Gaussian case, the only available method (which we implemented ourselves) for mean estimation with heteroskedastic errors is a non-Bayesian thresholding procedure, making it difficult to assess the relative computational efficiency of our method.
-Furthermore, the lack of readily available software for variance estimation made it extremely difficult to assess the relative performance of our method in that context as well.
+In the Gaussian case, our simulation study demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d.
+errors, whilst maintaining the same accuracy in the presence of heteroskedastic errors.
+Unfortunately, the lack of readily available software for variance estimation made it difficult to assess the performance of our method in that context.
 On the other hand, we were able to compare our method to some of the more popular denoising techniques in the Poisson case.
 Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods (Kolaczyk 1999) by utilizing ASH as the shrinkage procedure, which allows for more flexibility and accuracy.
-This is particularly evident in the case where the mean intensity is low, as is common in many high-throughput genomic sequencing datasets.
-Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm, due to the fact that we do not have to perform external cycle-spinning.
-Unfortunately, we were not able to directly compare the computational efficiency of our method to other methods due to differences in the programming software involved including that of the multiscale approach from Kolaczyk (1999).\bigskip\\
+This is particularly evident when the mean intensity is low, as is common in many high-throughput genomic sequencing datasets.
+Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm since we do not have to perform external cycle-spinning.
+Unfortunately, we were not able to directly compare the computational efficiency of our method to other methods due to differences in the programming software involved.\bigskip\\
 Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios.
-Even while restricting ourselves to the one-dimensional domain, our methods could be used in the case of multiple samples, otherwise known as regression analysis of functional data (see Morris 2006).
-Instead of dealing with a vector of observations, we could perform regression analysis on a matrix of observations, each row of which would encapsulate a sample with observations that are temporally or spatially structured.
+In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see Morris 2006).
+Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which would encapsulate a sample with temporally or spatially structured data points.
 While Morris (2006) proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category.
-Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby imposing even less restrictions on the assumptions behind the regression model.
-In the simplest case, we could potentially obtain spatially structured differences between the samples by including a single covariate into the regression model that categorizes each sample.
-In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where differential expression is present between say, different tissues, as per our sequencing example in the previous section.
+Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby relaxing their assumptions.
+In the simplest case, we could obtain spatially structured differences between groups by including a single covariate that categorizes each sample.
+In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where differential expression is present between say, different cell lines, as per our sequencing example in the previous section.
 The Gaussian model could potentially be used in...(??).\bigskip\\
@@
 For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in Nowak (1998) (again, reference technical report).
-However, recent advances in image denoising problems have shown that wavelet transformations might not be the most ideal due to the presence of smooth curves in many images such as photographs.
-We could thus attempt to use ASH as a shrinkage procedure in other types of transformations such as curvelets, and that could be a potential direction for future work.
+However, recent research in image denoising problems has shown that wavelet transformations might not be ideal due to smooth curves being present in many images such as photographs.
+We could thus incorporate ASH into other types of transformations such as curvelets, which would be a potential direction for future work.
 \newpage
@@
 Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels.
-This is likely due to the fact that the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
+This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
 One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH).
@@
 Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.\bigskip\\
-Note here that in order for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see Coifman \& Donoho (1995), and Kolaczyk (1999)) rather than as described above.
+Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see Coifman \& Donoho (1995), and Kolaczyk (1999)) rather than as described above.
 The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points.

### 2015-06-05 paper/draft_3.tex
small changes to paper and draft

@@
 \subsection{Gaussian denoising with heteroskedastic errors}
-We first consider the application of ASH in the context of the nonparametric regression model with i.i.d. Gaussian errors that are spatially structured. Specifically, consider the model
+Consider the nonparametric regression model with i.i.d. Gaussian errors:
 \begin{eqnarray}\label{eq:1d gaussian model}
@@
 \end{eqnarray}
-for $i=1,...,n$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve sampled on an equally spaced grid, and $\Ge_i$ are independent $N(0,\s^2)$ noise.
+for $i=1,...,n$, where $\bm{Y}$ is the vector of observations, $\bm{\mu}$ is the mean curve, and $\Ge_i$ are independent $N(0,\s^2)$ noise.
 Assume that $n=2^J$ for some integer $J$, as is standard in the wavelet literature.
-To better understand and motivate our method, we first look at wavelet shrinkage from a Bayesian perspective.\bigskip\\
-Given an orthogonal $n\times n$ matrix $W$ representing the orthonormal wavelet basis chosen, we have that the wavelet coefficients $\bm{d}$ are given by
+To motivate our method, we first describe wavelet shrinkage from a Bayesian perspective.
+
+The wavelet coefficients $\bm{d}$ are given by
 \begin{eqnarray}
 \bm{d}=W\bm{Y}
-\end{eqnarray}
-where $\mathbb{V}(Y)=\s^2I$. Hence, we can easily see that
+\end{eqnarray
+where $W$ denotes the orthogonal $n\times n$ matrix corresponding to the orthonormal wavelet basis chosen.
+Since $\mathbb{V}(Y)=\s^2I$,
 \begin{eqnarray}\label{eq:waveletcoef}

### 2015-06-05 pois_data/plot.R

@@ -20,7 +20,7 @@ plot(bppos,res4,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Ce
 dev.off()
 
 
-peaks=read.table("Gm1287peaks_chr1_sorted")
+peaks=read.table("pois_data/Gm1287peaks_chr1_sorted")
 peaks=peaks[order(peaks[,2]),]
 all.base=1:peaks[dim(peaks)[1],3]
 peaks.start=peaks[,2][peaks[,2]>=880000&peaks[,2]<=1011072]
@@ -29,7 +29,7 @@ peaks.end=peaks[,3][peaks[,3]>=880000&peaks[,3]<=1011072]
 res=ashsmooth.pois(M[1,]+M[2,],post.var=TRUE)
 
 pdf("peaks_comp_a.pdf",height=5,width=10)
-plot(bppos,M[1,]+M[2,],xlab="position",ylab="counts",pch=1,cex=0.6,col=alpha("black",0.3))
+plot(bppos,M[1,]+M[2,],xlab="position",ylab="counts",pch=16,cex=0.5,col=alpha("black",0.04))
 dev.off()
 
 pdf("peaks_comp_b.pdf",height=5,width=10)

### 2015-08-07 paper/draft_3.tex
updated plots

@@
 Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are actually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references].
-In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.\bigskip\\
+In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.
+
 Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators.
 These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994).
-Wavelet methods are locally adaptive in the sense that they achieve the optimal minimax rate over a wide variety of functions, yet are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001].
+Wavelet methods are locally adaptive in that they achieve the optimal minimax rate over a wide variety of functions, yet are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001].
 While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al.
-(2001) has demonstrated that various Bayesian shrinkage methods are usually more data adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE).
+(2001) has demonstrated that various Bayesian shrinkage methods are usually more adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE).
 However, many Bayesian methods require specific distributional assumptions, and are not easily extensible to more complex problems, two of which we subsequently describe.
 On the other hand, our method simplies the task by making approximations, while still possessing good finite sample performance and computational efficiency.
-These approximations also allows us to use ASH as the common shrinkage procedure in both the problems.\bigskip\\
+These approximations also allow us to use ASH as the common shrinkage procedure in both the problems.
+
 The first problem relates to mean and variance estimation with Gaussian noise.
@@
 Here we present an approach that estimates both the mean and variance accurately by incorporating ASH into a novel wavelet denoising framework.
-[mention the lack of available software?]\bigskip\\
+[mention the lack of available software?]
+
 The second task is to denoise a Poisson distributed signal.
 This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest.
-This problem is interesting in that there are many different ways to perform signal recovery.
+This problem is interesting because there are many distinct ways to perform signal recovery.
 Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by exploiting the mean-variance relationship of a Poisson distribution.
@@
 However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance.
-Furthermore, both these methods are quite sensitive to the choice of the primary resolution level as simulations have shown.
+Furthermore, both these methods are quite sensitive to the choice of the primary resolution level as our simulations will show.
 Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by Kolaczyk (1999b) to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen.
 We will improve upon the prior (and likelihood) specification by using ASH as the main shrinkage procedure in a Bayesian framework similar to that of Kolaczyk (1999b).
-\bigskip\\
-Both the aforementioned problems are harder to deal with than the classical problem of i.i.d.
-Gaussian errors, and usually requires one to extend the ideas from the latter task.
+
+Both the aforementioned problems are harder to deal with than the classical problem with i.i.d.
+Gaussian errors, and usually requires extension of the ideas from the latter task.
 Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage.
-\bigskip\\
+
 As a generic shrinkage method, ASH takes as input a vector of estimates $\hat{\Gb}_i,i=1,...,n$ and their standard errors $\hat{\s}_i\equiv se(\hat{\Gb}_i),i=1,...n$, and outputs shrunken estimates of $\bm{\Gb}$.
-Specifically, the likelihoods for the true parameters $\Gb_i,i=1,...n$ are assumed to be iid $N(\Gb_i;\hat{\Gb}_i,\hat{\s}_i^2)$.
+Specifically, the likelihoods for the true parameters $\Gb_i,i=1,...n$ are assumed to be i.i.d.
+$N(\Gb_i;\hat{\Gb}_i,\hat{\s}_i^2)$.
 ASH then assumes exchangeability of the $\Gb_i$'s and sets the following ``shrinkage'' prior on $\Gb_i$ for each $i$:
@@
 Since the likelihoods are Gaussian and the priors are mixtures of Gaussians, the posterior distribution of $\Gb_i$ given $\hat{\Gb}_i$ and $\bm{\hat{\pi}}$ is analytically tractable, where the mixing proportions $\bm{\hat{\pi}}$ are maximum likelihood estimates.
-The posterior mean of $\Gb_i$ is taken to be the point estimate of $\Gb_i$, resulting in a shrinkage procedure.\bigskip\\
+The posterior mean of $\Gb_i$ is taken to be the point estimate of $\Gb_i$, resulting in shrinkage.
+
 The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet settings described here.
 As an Empirical Bayes procedure, ASH borrows information across all available data and is extremely data adaptive.
-At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a name for this?) variable variances are allowed as input, a feature which latter methods lack.
+At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a reference for this?) is that variable variances are allowed as input, a feature which latter methods lack.
 This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above.
-Furthermore, Gaussian mixture priors can effectively approximate any unimodal distribution, allowing for a more flexible prior than many other procedures.
+Furthermore, Gaussian mixtures can effectively approximate any unimodal distribution, allowing for an extremely flexible prior.
 In tackling these two specific problems, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising accuracy.
@@
 \bm{d}=W\bm{Y}
-\end{eqnarray
+\end{eqnarray}
 where $W$ denotes the orthogonal $n\times n$ matrix corresponding to the orthonormal wavelet basis chosen.
@@
 $\pi_i^{(j)}$ and $(s_i^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level, and $m$ is the number of mixture components.
-In ASH, $m$ is usually chosen so that it is large enough to reasonably approximate any unimodal distribution, while maintaining an acceptable computational speed.
+In ASH, $m$ is usually chosen to reasonably approximate any unimodal distribution, while maintaining an acceptable computational speed.
 Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,J$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$.
-By applying the inverse wavelet transform on the posterior mean $\hat{\bm{\Ga}}$ that ASH produces, one can obtain the posterior mean of $\bm{\mu}$, which serves as an estimate that minimizes the MSE.
-One could also construct credible bands using the posterior variances.\bigskip\\
-While many existing methods do a good job of signal denoising in the presence of i.i.d.
+By applying the inverse wavelet transform to the posterior mean $\hat{\bm{\Ga}}$ that ASH produces, one can obtain the posterior mean of $\bm{\mu}$, which serves as an estimate that minimizes the MSE.
+One could also construct credible bands using the posterior variances.
+
+While many existing methods perform well in the presence of i.i.d.
 (Gaussian) errors, heteroskedastic (but still independent) errors present a different challenge.
 One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize.
-Given the true variances and hence the likelihood, one could compute the posterior distribution using some specified prior.
-However, this would be computationally cumbersome, and may not be feasible when extended to multiple signals or higher dimensions.
-A suitable prior might also be difficult to find.
-As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).\bigskip\\
+Given the true variances and hence the likelihood, one could compute the full posterior distribution using some specified prior.
+However, this would be computationally cumbersome, and may be infeasible when extended to multiple signals or higher dimensions.
+In this case, a suitable prior might also be difficult to find.
+As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).
+
 To describe our approach in more detail, first assume that the true variance function is known and given by $\mathbb{V}(\Ge_i)=\s_i$, and that the true mean function is given by $\bm{\mu}=(\mu_1,...,\mu_t)$, where $T=2^J$ for some positive integer $J$.
@@
 Coifman \& Donoho (1995)).
-Now let $W$ be the matrix associated with the NDWT for a given wavelet basis, so that
+Then,
 \begin{eqnarray}
@@
 \end{eqnarray}
-where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Sigma}=W\Sigma W^T$.
-By treating the likelihood for $\bm{\Ga}$ as if it were independent, we can write the likelihood as follows (using the double index mentioned above):
+where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Sigma}=W\Sigma W^T$, where $W$ is the matrix associated with the NDWT for a given wavelet basis.
+By treating the likelihood for $\bm{\Ga}$ as if it were independent, it can be written as follows(using the double index mentioned above):
 \begin{eqnarray}\label{eq:likelihood}
@@
 Finally, we can obtain an estimate of $\mu$ by using the average basis inverse, which is essentially an average of the inverse wavelet transforms for every shift of the data (see Coifman \& Donoho (1995)) since we are using the NDWT.
-Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, which takes only $n\log(n)$ time.\bigskip\\
-Although we have assumed that the true variances were known for mean estimation, the problem of variance estimation itself is a non-trivial one.
+Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, taking only $n\log(n)$ time.
+
+Though we have assumed that the true variances were known for mean estimation, the problem of variance estimation itself is a non-trivial one.
 Here we make the reasonable assumption that the variance function is also spatially structured, in addition to the mean function.
-The approach we took is similar in spirit to that of Cai \& Wang (2008), since we make use of wavelet decomposition as well.
+The approach we took is similar in spirit to that of Cai \& Wang (2008), making use of wavelet decomposition as well.
 However, while they use first order differences, we look at the squared residuals.
@@
 The variance estimation process is then very similar to one for mean estimation as described above, with a few extra details.
-The full procedure is outlined in Appendix \ref{app:var estimation}.\bigskip\\
-Now that we can now estimate $\bm{\mu}$ given $\bm{\s}^2$ and vice versa, a natural procedure for jointly estimating $\bm{\mu}$ and $\bm{\s}^2$ is an iterative one.
+The full procedure is outlined in Appendix \ref{app:var estimation}.
+
+Now that we can estimate $\bm{\mu}$ given $\bm{\s}^2$ and vice versa, a natural procedure for jointly estimating $\bm{\mu}$ and $\bm{\s}^2$ is an iterative one.
 That is, we estimate $\bm{\mu}$ given some initial estimate of $\bm{\s}^2$, then estimate $\bm{\s}^2$ given the previous estimate of $\bm{\mu}$, and iterate the process.
@@
 Next we turn to another popular nonparametric regression problem and demonstrate how we could make use of ASH.
-Specifically, we also assume an underlying signal $\Gl_i$, $i=1,...,n$ with $n=2^J$ for some positive integer $J$.
+Specifically, we again assume an underlying signal $\Gl_i$, $i=1,...,n$ with $n=2^J$ for some positive integer $J$.
 Further assume that each data point $Y_i$, $i=1,...,n$ is realized from a Poisson distribution with mean $\Gl_i$ ie.
@@
 \begin{eqnarray}Y_{jk}=Y_{j+1,2k}+Y_{j+1,2k+1}\end{eqnarray}
-for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$, so that we are looking at the sum of adjacent pairs of ``points'' as we move to coarser resolutions, where a point is already itself a sum of the data points.
-Another way to define the $Y$'s is
+for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$. Hence, we are summing more blocks of observations as we move to coarser levels. Another way to define the $Y$'s is
 \begin{eqnarray}Y_{jk}=\sum_{l=k2^{J-j}+1}^{(k+1)2^{J-j}}Y_l\end{eqnarray}
@@
 \[Y_{j+1,2k}|Y_{jk},\Ga_{jk}\sim \textrm{Bin}({Y_{jk},\frac{1}{1+e^{-\Ga_{jk}}}\equiv\frac{\Gl_{j+1,2k}}{\Gl_{jk}}})\]
-Whereas Kolaczyk (1999) sets a conjugate shrinkage prior (a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and uses a Binomial likelihood, we felt that the two-component mixture prior is too inflexible.
-As such, we work with the parameters $\Ga_{sl}$ as defined in \eqref{eq:poisson wc} and approximate the logit-Binomial (is there such a thing?) likelihoods by Gaussian likelihoods.
-Furthermore, these parameters can be more easily connected to the true wavelet coefficients since they consist of (log) differences rather than ratios.\bigskip\\
+Kolaczyk (1999) set a conjugate shrinkage prior (a mixture of a point mass at 0.5 and a uniform distribution, similar to the ``spike and slab'' prior for the Gaussian case) for the parameters $\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and used a Binomial likelihood.
+However, we work with the parameters $\Ga_{sl}$ as defined in \eqref{eq:poisson wc} and approximate the logit-Binomial (is there such a thing?) likelihoods by Gaussian likelihoods, and replace the two-component prior in Kolaczyk (1999) by the more flexible prior from ASH.
+Furthermore, these parameters can be more easily connected to the true wavelet coefficients since they consist of (log) differences rather than ratios.
+
 To describe the approximation process in more detail, we drop the subscripts for notational convenience.
@@
 % for some appropriate estimator $\hat{\Ga}$.
-This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).\bigskip\\
+This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).
+
 %We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$.
@@
 182 of Gart \& Zweifel (1967), and is chosen because it is less biased for the true variance of $\hat{\Ga}$ (when $N$ is small) as compared to the asymptotic variance of the MLE (see Gart \& Zweifel (1967)).
-The other two variance estimators from Gart \& Zweifel (1967), $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.\bigskip\\
+The other two variance estimators from Gart \& Zweifel (1967), $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.
+
 Finally, the Delta method is used to reconstruct the signal in the original space from the posterior distribution of the $\Ga$'s (which are in the logit space).
@@
 \section{Simulations}
-Our simulations will focus on the Gaussian and Poisson cases separately.
-For the Gaussian case, our results will mostly revolve around mean estimation, which is often of interest in many signal recovery problems.
-To fully explore the performance of the various methods, we consider in our simulations different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions.
-Specifically, we chose 7 representative mean functions from Antoniadis et al.
-(2001), namely ``Spikes'', ``Bumps'', ``Blocks'', ``Angles'', ``Doppler'', ``Blip'', and ``Corner''.
-We feel that these functions encompass most of the local features of commonly seen signals.
-These mean functions were rescaled to be between 0.2 and 0.8, as in Antoniadis et al.
-(2001).
-We also considered sample sizes for $n=256,512,1024$ and 4096, though only results from $n=1024$ will be presented here for conciseness.
-In our simulations we allowed for SNR=1, a high noise scenario, and SNR=3, a moderate noise scenario.
-Here, SNR is defined as
-\begin{eqnarray}\label{eq:snr}
-SNR=\frac{\sqrt{\frac{1}{T-1}\sum_{t=1}^T(\mu_t-\bar{\mu})^2}}{\frac{1}{T}\sum_{t=1}^T\s_t}
-\end{eqnarray}
-as in Gao (1997) and Delouille (2004).
-We did not consider low noise situations as the effect of heteroskedasticity on mean estimation is often lost, and many procedures which assume homoskedastic errors perform just as well as methods which do take heteroskedasticity into account.
-Finally, we considered 5 different variance functions, one of which is constant variance (ie the homoskedastic case), and the rest are commonly used variance functions from eg.
-Cai \& Wang (2008).\bigskip\\
-To highlight the flexibility of our method, we first present the results for the homoskedastic case.
-Here we compare our method, which does not assume homoskedasticity (and hence jointly estimates the mean and variance), to various popular wavelet based methods which do assume homoskedasticity.
-For illustration purposes, we also include the case where our method does assume homoskedasticity and takes an estimated $\s$ as input (this is also a feature of our method).
-Note that, for computational simplicity, we use a second order difference estimate of the variance as described by Hall et al.
-(1990) rather than the median absolute deviation (MAD) estimate that is commonly used in thresholding methods .
-The practical difference between these two estimators is small, unless the mean function is extremely irregular.
-Specifically, we include the following methods for this particular simulation study:
+We now seek to validate the advantages of our method, named ``SMASH'', via simulation studies.
+To thoroughly investigate the performance of SMASH, we consider the Gaussian and Poisson cases separately.
+
+For the Gaussian case, we focus our attention mostly on mean estimation.
+Different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions were considered, to ensure that SMASH behaves well in a variety of settings.
+However, only a small portion of the results will be shown here to highlight key findings from the rather extensive simulation study.
+Full results from the study can be found \textcolor{red}{state where?}.
+
+To demonstrate the robustness of SMASH, we first consider homoskedastic errors.
+Due to the large number of methods available in the literature for this setting, we chose only a subset.
+The methods we considered in our simulation are discussed in detail in Antoniadis et al.
+(2001), and in particular Translation Invariant (TI) thresholding by Coifman \& Donoho (1995) performed the best on average, where performance is measured by mean squared error (MSE).
+We also considered the popular Empirical Bayes shrinkage procedure by Johnstone \& Silverman (2005), called Ebayesthresh.
+Figure \ref{fig:gaus_homo_comp} shows the mean integrated squared errors (MISEs) of SMASH, TI-thresholding, and Ebayesthresh for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024; figure \ref{fig:gaus_homo_comp} compares the MISEs of SMASH with two different options for the same scenario: the first assumes the default and hence estimates the mean without any assumptions on the variance function, while the second estimates the mean given the true variance function.
+The figures clearly indicate that the performance of SMASH is not impacted by the lack of explicit assumptions imposed on the variance function: it outperforms two of the most accurate wavelet denoising algorithms for i.i.d.
+Gaussian noise even when the i.i.d.
+assumption holds, and performs nearly as well as when the variance function is known, which is the best-case scenario for any denoising technique.
+These results also extend to other mean functions, SNRs and sample sizes.
+
+\begin{figure}[ht]
+\centering
+	   \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_gaus_homo_comp.pdf}
+        \caption{}
+        \label{fig:gaus_homo_comp}
+    \end{subfigure}
+    \hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_gaus_homo_smash.pdf}
+        \caption{}
+        \label{fig:gaus_homo_smash}
+    \end{subfigure}
+    \caption{Violin plots of MISEs for various methods.
+Dashed green line indicates the median MISE for SMASH.
+a) compares SMASH against two popular and accurate denoising methods: TI-thresholding and Ebayesthresh, and b) demonstrates the performance gain of SMASH when it is provided the true variance.}
+    \label{fig:gaus_homo}
+\end{figure}
+
+Having shown that SMASH performs well in the homoskedastic case without any explicit assumptions on the Gaussian noise, we now demonstrate its performance gain when the errors are heteroskedastic.
+Figure \ref{fig:simple_eg} demonstrates that SMASH is able to better capture the true signal than TI-thresh (with variance estimated by running median absolute deviation (RMAD)) on a simple simulation.
+For the sake of presentation, figure \ref{fig:gaus_hetero} highlights only the results from SMASH, TI-thresh (with various choices of variance estimation) and EbayesThresh for the ``Spikes'' mean function, with the ``Clipped Blocks'' variance function, a SNR of 3 and a sample size of 1024.
+Nevertheless, similar results hold in general for different mean and variance functions, SNRs, and sample sizes.
+\begin{figure}[ht]
+\centering
+	\includegraphics[width=\textwidth]{simple_eg.pdf}
+	\caption{Simple illustration of heteroskedastic Gaussian denoising.
+Top left plot shows the mean function, top right plot shows the variance function, bottom left plot shows a sample dataset, and bottom right plot shows the estimated mean functions from SMASH and TI-thresh against the true mean function.}
+	\label{fig:simple_eg}
+\end{figure}
+
+\begin{figure}[ht]
+\centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_gaus_hetero_ti.pdf}
+        \caption{}
+        \label{fig:gaus_hetero_ti}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_gaus_hetero_homo.pdf}
+        \caption{}
+        \label{fig:gaus_hetero_homo}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_gaus_hetero_smash.pdf}
+        \caption{}
+        \label{fig:gaus_hetero_smash}
+    \end{subfigure}
+    \caption{Violin plots of MISEs for various methods.
+Dashed green line indicates the median MISE for SMASH.
+a) compares SMASH against TI-thresh with variance estimated by RMAD, variance estimated by SMASH, and the true variance.
+b) demonstrates the importance of taking heteroskedasticity into account, and c) reveals the performance gain of SMASH when it is provided the true variance.}
+    \label{fig:gaus_hetero}
+\end{figure}
+
+Several facts are immediately clear from figure \ref{fig:gaus_hetero}: 
 \begin{enumerate}
-\item SMASH using joint estimation, Haar basis (denoted by SMASH, joint, Haar)
-\item SMASH using joint estimation, Symmlet 8 basis (denoted by SMASH, joint, Symm8)
-\item TI thresholding using variance estimated by running MAD, Symmlet 8 basis (denoted by TI-thresh, RMAD, Symm8). See Gao (1997)
-\item TI thresholding using variance estimated by SMASH, Symmlet 8 basis (denoted by TI-thresh, SMASH, Symm8)
-\item SMASH using difference estimator, Symmlet 8 basis (denoted by SMASH, homo, Symm8)
-\item EbayesThresh using difference estimator, Symmlet 8 basis (denoted by Ebayes, homo, Symm8). See Johnstone \& Silverman (2004)
-\item Empirical Bayes shrinkage using MAD estimator, Symmlet 8 basis (denoted by PostMean, homo, Symm8). See Clyde \& George (1999,2000)
-\item SureShrink using MAD estimator, Symmlet 8 basis (denoted by SURE, homo, Symm8). See Donoho \& Johnstone (1994)
-\item TI thresholding using MAD estimator, Symmlet 8 basis (denoted by TI-thresh, homo, Symm8). See Coifman \& Donoho (1995)
-\item SMASH given true variance, Symmlet 8 basis (denoted by SMASH, truth, Symm8)
-\item TI thresholding given true variance, Symmlet 8 basis (denoted by TI-thresh, truth, Symm8)
+\item From \ref{fig:gaus_hetero_ti}: SMASH does better than all TI-thresh variants, including the case when the true variance is provided, demonstrating the excellent finite sample performance of SMASH.
+\item From \ref{fig:gaus_hetero_ti}: using the variance estimate from SMASH as an input to TI-thresh improves the accuracy of TI-thresh substantially, compared with using RMAD to estimate the variance as in Gao (1997)
+\item From \ref{fig:gaus_hetero_homo}: accounting for heteroskedasticity allows SMASH to vastly outperform methods which assume homoskedastic errors.
+\item From \ref{fig:gaus_hetero_homo}: empirical Bayes methods are more robust to violations of homoskedasticity compared with TI-thresholding.
+\item From \ref{fig:gaus_hetero_smash}: Providing the true variance to SMASH does not substantially improve the performance of the methods compared to the case when SMASH estimates its own variance function.
+Hence, we can reasonably assume that SMASH does a good job of variance estimation, although this claim relies heavily on the variance function at hand.
+For example, the Bumps variance function (see appendix ?) is extremely difficult to estimate, and SMASH will perform much better when provided with the true variance function.
 \end{enumerate}
-Here compare our method mainly against TI thresholding, which often produced the smallest mean squared error (MSE) amongst all the methods discussed in the extensive simulation study conducted by Antoniadis et al.
-(2001).
-!!!!!!!!!!!!!!![describe these procedures earlier?]We also included three other adaptive methods, namely EbayesThresh by Johnstone \& Silverman (2005), the Empirical Bayes approach by Clyde \& George (1999,2000), as well as SureShrink, developed by Donoho \& Johnstone (1994).
-Note that methods (1)-(4) do not assume homoskedastic errors and perform their own variance estimation.
-In particular, we provide two ways to estimate the variance function in TI-thresholding: method (3) uses the running MAD approach as described in Gao (1997), and method (4) uses the variance estimate from SMASH.
-On the other hand, methods (5)-(9) all assume homoskedasticity and estimate a constant variance.
-Specifically, EbayesThresh places a Laplace prior on the wavelet coefficients, and we fix the scale parameter of the Laplace prior to be 0.5, as the marginal maximum likelihood implementation often fails to converge.
-The posterior mean is then taken to be the final estimate of the wavelet coefficients.
-Details for the Empirical Bayes approach by Clyde \& George (1999,2000), SureShrink, and homoskedastic TI-thresholding can be found in Antoniadis et al.
-(2001).
-Further, we have ordered methods (5)-(9) in what we deem to be decreasing adaptivity.
-Finally, methods (10) and (11) are provided the true variance function and are included as benchmarks.
-Tables \ref{table:homo1} and \ref{table:homo3} displays the relative MSEs of various methods for the 7 test functions and 2 SNRs mentioned above, where the relative MSEs are the standard MSEs rescaled (for each test function and SNR) so that the baseline method has a MSE of 1.
-In our simulation study, the baseline method will be SMASH, using the Haar basis.
- %At the same time, we included SureShrink as it performs well in terms of mean square bias.
-We also compared our method against two other Bayesian approaches, of which the method described in Clyde \& George (1999,2000) was also included in Antoniadis et al.
-(2001) and performed well in terms of MSE.
-The other Bayesian approach, EbayesThresh, is more recent and and hence included as part of our study.
-%Tables \ref{table:homo1} and \ref{table:homo3} displays the mean integrated squared error (MISE) of various methods for the 7 test functions and 2 SNRs mentioned above. Here MISE is defined as
-%\begin{eqnarray}\label{eq:mise}
-%MISE=\sum_{r=1}^R{\frac{10000*\sum_{i=1}^n(\hat{\mu}^{(r)}_i-\mu_i)^2}{\sum_{i=1}^n \mu_i^2}}
-%\end{eqnarray}
-%, which is simply the standard MSE rescaled in order to produce more comparable numbers. Here $R$ is the number of runs in each simulation (100 in our study) and $n$ is the sample size.
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 1.05 & 1.04 & 1.50 & 1.00 & 0.69 & 1.50 & 0.94 \\
-  TI-thresh, RMAD, Symm8 & 2.03 & 2.38 & 3.34 & 1.63 & 1.17 & 2.34 & 1.28 \\
-  TI-thresh, SMASH, Symm8 & 1.40 & 1.54 & 2.32 & 1.35 & 0.89 & 1.74 & 1.07 \\
-  SMASH, homo, Symm8 & 1.05 & 1.05 & 1.53 & 1.00 & 0.71 & 1.51 & 0.94 \\
-  Ebayes, homo, Symm8 & 1.30 & 1.01 & 1.49 & 1.16 & 0.77 & 1.66 & 1.09 \\
-  PostMean, homo, Symm8 & 1.80 & 1.26 & 1.75 & 1.71 & 0.89 & 2.14 & 1.61 \\
-  SURE, homo, Symm8 & 6.26 & 2.83 & 4.60 & 9.45 & 3.28 & 10.63 & 11.41 \\
-  TI-thresh, homo, Symm8 & 1.47 & 1.64 & 2.39 & 1.37 & 0.90 & 1.74 & 1.08 \\
-  SMASH, truth, Symm8 & 1.05 & 1.04 & 1.52 & 1.00 & 0.70 & 1.51 & 0.94 \\
-  TI-thresh, truth, Symm8 & 1.45 & 1.59 & 2.35 & 1.36 & 0.90 & 1.72 & 1.07 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for iid Gaussian errors, SNR=1}
-\label{table:homo1}
-\end{table}
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 0.82 & 1.41 & 3.20 & 0.77 & 0.54 & 1.72 & 0.69 \\
-  TI-thresh, RMAD, Symm8 & 1.12 & 2.34 & 5.80 & 0.94 & 0.84 & 2.84 & 1.10 \\
-  TI-thresh, SMASH, Symm8 & 0.88 & 1.39 & 4.03 & 0.85 & 0.60 & 1.85 & 0.83 \\
-  SMASH, homo, Symm8 & 0.81 & 1.21 & 3.07 & 0.77 & 0.50 & 1.65 & 0.69 \\
-  Ebayes, homo, Symm8 & 0.96 & 1.36 & 2.98 & 0.88 & 0.58 & 1.76 & 0.83 \\
-  PostMean, homo, Symm8 & 1.28 & 1.69 & 3.63 & 1.18 & 0.70 & 2.54 & 1.13 \\
-  SURE, homo, Symm8 & 3.38 & 3.45 & 7.39 & 5.05 & 2.11 & 10.14 & 6.34 \\
-  TI-thresh, homo, Symm8 & 0.91 & 1.50 & 4.13 & 0.86 & 0.61 & 1.90 & 0.85 \\
-  SMASH, truth, Symm8 & 0.81 & 1.15 & 2.86 & 0.77 & 0.50 & 1.63 & 0.69 \\
-  TI-thresh, truth, Symm8 & 0.90 & 1.41 & 3.96 & 0.86 & 0.60 & 1.87 & 0.84 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for iid Gaussian errors, SNR=3}
-\label{table:homo3}
-\end{table}
-From Tables \ref{table:homo1} and \ref{table:homo3}, we see that our method almost always outperform other methods for all the test functions in terms of MISE as defined above.
-Furthermore, two key observations should be noted here.
-First, estimating the variance without the assumption of homoskedasticity does not decrease the performance of our method in any way.
-In fact, the MISEs for the case where our method estimates the mean and variance jointly and the optimal scenario where our method estimates the mean given the true function are extremely similar.
-As such, there is no need to specifically assume homoskedasticity or otherwise when using our method.
-Second, the Haar and the Symmlet 8 bases perform similarly, with each outperforming the other slightly for different test functions.
-As such, the default option for our method is actually the Haar basis due to computational reasons.
-\bigskip\\
-Having shown that our method performs well in the case of homoskedastic errors without assuming homoskedasticity, we next show the performance gain of our method in the case when the errors are actually heteroskedastic.
-In total, we considered four different variance functions, namely function $V_2$ as defined in Cai \& Wang (2008), here slightly modified to be
-\[V_2(x)=0.0001+4*(e^{(-550*(x-0.2)^2)}+e^{(-200*(x-0.5)^2)}+e^{(-950*(x-0.8)^2)})\]
-, the Doppler and Bumps functions from Donoho \& Johnstone (1994), as well as the Clipped Blocks function from Fryzlewicz \& Nason (2001).
-The same mean functions, SNRs and smoothing methods were used in the heteroskedastic case as in the iid case.
-Tables \ref{table:hetero_v2_1} - \ref{table:hetero_bump_3} give partial results from our simulation study; the full results are given in Appendix \ref{}.\\
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 1.02 & 0.91 & 1.23 & 1.38 & 0.71 & 1.27 & 0.90 \\
-  TI-thresh, RMAD, Symm8 & 3.39 & 1.52 & 2.66 & 6.64 & 1.77 & 4.43 & 5.69 \\
-  TI-thresh, SMASH, Symm8 & 1.83 & 1.46 & 1.97 & 1.84 & 0.93 & 1.56 & 1.03 \\
-  SMASH, homo, Symm8 & 1.88 & 1.07 & 1.92 & 4.91 & 1.56 & 3.41 & 4.40 \\
-  TI-thresh, homo, Symm8 & 8.66 & 2.79 & 6.73 & 29.84 & 7.15 & 19.45 & 29.05 \\
-  SMASH, truth, Symm8 & 1.00 & 0.71 & 1.14 & 1.33 & 0.55 & 1.13 & 0.85 \\
-  TI-thresh, truth, Symm8 & 1.88 & 1.22 & 1.81 & 1.83 & 0.78 & 1.42 & 1.04 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=1, Gaussian errors}
-\label{table:hetero_v2_1}
-\end{table}
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 0.83 & 1.26 & 2.34 & 1.11 & 0.45 & 1.90 & 0.72 \\
-  TI-thresh, RMAD, Symm8 & 2.12 & 1.68 & 3.03 & 4.09 & 0.90 & 3.55 & 3.39 \\
-  TI-thresh, SMASH, Symm8 & 0.98 & 1.48 & 3.17 & 1.32 & 0.50 & 2.17 & 0.84 \\
-  SMASH, homo, Symm8 & 1.68 & 1.16 & 2.50 & 3.18 & 1.09 & 2.83 & 2.65 \\
-  TI-thresh, homo, Symm8 & 6.72 & 2.34 & 5.18 & 17.54 & 3.61 & 13.22 & 16.13 \\
-  SMASH, truth, Symm8 & 0.80 & 0.84 & 1.66 & 1.07 & 0.35 & 1.80 & 0.70 \\
-  TI-thresh, truth, Symm8 & 0.99 & 1.15 & 2.34 & 1.29 & 0.38 & 2.11 & 0.83 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Clipped Blocks variance function, SNR=3, Gaussian errors}
-\end{table}
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 1.00 & 0.93 & 1.05 & 1.08 & 0.83 & 1.02 & 0.92 \\
-  TI-thresh, RMAD, Symm8 & 5.52 & 2.00 & 3.71 & 7.88 & 4.08 & 6.70 & 7.72 \\
-  TI-thresh, SMASH, Symm8 & 1.13 & 1.20 & 1.40 & 1.25 & 0.95 & 1.11 & 1.00 \\
-  SMASH, homo, Symm8 & 5.11 & 1.85 & 3.35 & 7.07 & 3.81 & 6.07 & 6.90 \\
-  TI-thresh, homo, Symm8 & 13.47 & 3.94 & 8.21 & 19.95 & 10.02 & 16.94 & 19.78 \\
-  SMASH, truth, Symm8 & 0.45 & 0.93 & 0.72 & 0.41 & 0.39 & 0.47 & 0.28 \\
-  TI-thresh, truth, Symm8 & 0.66 & 1.19 & 1.11 & 0.60 & 0.55 & 0.56 & 0.33 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Bumps variance function, SNR=1, Gaussian errors}
-\end{table}
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrrrrr}
-  \hline
- & Spikes & Bumps & Block & Angles & Doppler & Blip & Corner \\
-  \hline
-SMASH, joint, Haar & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 & 1.00 \\
-  SMASH, joint, Symm8 & 0.83 & 0.87 & 1.23 & 0.98 & 0.66 & 1.33 & 0.86 \\
-  TI-thresh, RMAD, Symm8 & 4.10 & 1.25 & 2.41 & 6.42 & 2.35 & 5.58 & 6.27 \\
-  TI-thresh, SMASH, Symm8 & 0.88 & 1.14 & 1.60 & 1.12 & 0.67 & 1.60 & 0.95 \\
-  SMASH, homo, Symm8 & 3.85 & 1.20 & 2.26 & 5.80 & 2.37 & 5.10 & 5.63 \\
-  TI-thresh, homo, Symm8 & 9.95 & 2.06 & 4.60 & 16.02 & 5.52 & 13.50 & 15.85 \\
-  SMASH, truth, Symm8 & 0.39 & 1.12 & 1.13 & 0.44 & 0.32 & 0.58 & 0.32 \\
-  TI-thresh, truth, Symm8 & 0.45 & 1.65 & 1.39 & 0.60 & 0.41 & 0.72 & 0.37 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Bumps variance function, SNR=3, Gaussian errors}
-\label{table:hetero_bump_3}
-\end{table}
-\bigskip\\
-In all the scenarios presented in Tables \ref{table:hetero_v2_1} - \ref{table:hetero_bump_3}, it is obvious that the mean estimates deviate substantially from the true mean if the heteroskedastic nature of the variance functions is not taken into account.
-We also note that our method can nearly achieve the ``optimal'' MISE (ie the MISE for the case when our method is given the true variance) for variance function $V_2$, but not for the other.
-This is likely because function $V_2$ is relatively smooth, and hence is easier to estimate than the extremely jumpy and peaky Bumps function.
-Furthermore, the MISEs of our method are often smaller than the ones produced by TI-thresholding even when TI-thresholding is supplied the true variance function, where the latter procedure has been shown to be asymptotically optimal (see Gao (1997)).
-Hence, the finite sample performance of our method is guaranteed to a certain extent through these simulation studies.
-At the same time, using the variance function estimated by our method instead of running MAD also improves the performance of TI-thresholding, demonstrating the ability of our method to estimate the variance function relatively accurately.
-However, our method is still superior to TI-thresholding no matter the type of variance estimate that TI-thresholding uses in these simulation studies.\bigskip\\
+
 Since our method also provides variance estimates, one could potentially perform similar assessments for different variance functions as with mean functions.
-In this particular study, we compare our method against the only joint mean and variance estimation procedure for which we could find available software.
+In this particular study, we compare our method against the only joint mean and variance estimation procedure for which software is easily available.
 Specifically, we consider the Mean Field Variational Bayes (MFVB) methodology developed by Menictas \& Wand (2014) for heteroskedastic Gaussian regression.
-Since MFVB is splines-based (and hence less locally adaptive), we chose the smooth mean and standard deviation functions (A) from Menictas \& Wand (2014) as our test functions, plotted in Figure \ref{fig:mfvb_fn} and denoted by $m(\cdot)$ and $sd(\cdot)$ respectively.
+Since MFVB is splines-based (and hence less adaptive locally), we chose the smooth mean and standard deviation functions (A) from Menictas \& Wand (2014) as our test functions, plotted in Figure \ref{fig:mfvb_fn} and denoted by $m(\cdot)$ and $sd(\cdot)$ respectively.
 We then considered two different simulation scenarios:
@@
         \caption{}
-        \label{fig:seq_peak_data}
+        \label{fig:mfvb_mean}
     \end{subfigure}
@@
         \caption{}
-        \label{fig:seq_peak_est}
+        \label{fig:mfvb_var}
     \end{subfigure}
@@
 In the first scenario, the number of data points is not a power of two, nor are the point equally spaced.
-To deal with these complications, we adapted and modified the standard symmetric extension procedure commonly adopted in wavelet settings.
+To deal with these complications, we adapted and modified the standard symmetric extension procedure commonly used in wavelet settings.
 We first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points.
@@
 Evaluation of MSE at the 201 equally spaced points is then based on simple linear interpolation between the estimated points.
-Tables \ref{table:mfvb_comp} displays the MSEs over 100 independent runs for each scenario.
+Tables \ref{table:mfvb_comp} display the MSEs over 100 independent runs for each scenario.
 \begin{table}[ht]
@@
 \end{table}
-\bigskip\\
+
 Note that wavelets in general are poorly suited for dealing with the setup in Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced.
-Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of wavelet methods.
-At the same time, spline-based methods such as MFVB are well suited to dealing with smooth mean and variance functions such as those used in the simulations, whereas wavelet methods can better deal with spatial inhomogeneity which are present in functions such as those presented in Tables
-\ref{table:homo1} - \ref{table:hetero_bump_3}.
-Despite these limitations, our method performs comparably to MFVB in terms of mean estimation for the simulation scheme presented in Scenario 1, and has a lower MSE in terms of variance estimation.
-For Scenario 2, our method outperforms MFVB in both mean and variance estimation despite the smoothness of the test functions used.
-\bigskip\\
-Summarizing the simulation studies conducted so far, we have demonstrated that our method does a reasonable job of mean and variance estimation for a variety of situations in the Gaussian case.
+Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of SMASH.
+At the same time, spline-based methods such as MFVB are well suited to dealing with smooth mean and variance functions such as those used in the simulations, whereas wavelet methods can better deal with spatial inhomogeneity which are present in functions such as those presented in Figure \ref{fig:gaus_homo}.
+Despite all these limitations, our method performs comparably to MFVB in terms of mean estimation for the simulation scheme presented in Scenario 1, and has a lower MSE in terms of variance estimation.
+For Scenario 2, our method outperforms MFVB in both mean and variance estimation.
+
+Thus far, we have demonstrated that our method does a good job of mean and variance estimation for a variety of situations in the Gaussian case.
 As such, we now turn our attention to the Poisson case.
 For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in Timmermann \& Nowak (1999) and Fryzlewicz \& Nason (2004), over 100 independent runs.
-Specifically, the ``Spikes'', ``Angles'', ``Bursts'',``Clipped Blocks'',``Bumps'' and ``Heavisine'' functions were chosen.
-The first 5 were part of a simulation study by Besbeas et al.
-(2004), and the ``Heavisine'' function was considered by Fryzlewicz \& Nason (2004).
-These test functions were then shifted and scaled to have (min,max) intensities of (0.01,3), (1/8,8) and (1/128,8), of which the latter two were the values used in Fryzlewicz \& Nason (2004).
-The low intensity scenario of (0.01,3) was chosen to reflect the small number of counts often present in certain types of high-throughput sequencing data, an application we will demonstrate in more detail later on.
-To assess the performance of our method, we used the same relative MSE as defined above for the Gaussian case, and considered the following methods in our simulation study:
-\begin{enumerate}
-\item SMASH
-\item Haar-Fisz transform and variance stabilization (denoted by Haar-Fisz). See Fryzlewicz \& Nason (2004).
-\item Anscombe transformation with the universal threshold using hard thresholding (denoted by Anscombe, universal). See Donoho (1993).
-\item Anscombe transformation with the cross-validation threshold using hard thresholding (denoted by Anscombe, CV)
-\item Corrected Haar thresholds using hard thresholding (denoted by Haar thresholds). See Kolazyk (1997).
-\item Bayesian multi-scale multiplicative innovations model (denoted by BMMIM). See Timmermann \& Nowak (1999).
-\item Bayesian multi-scale model (denoted by BMSM). See Kolaczyk (1999b).
-\end{enumerate}
-The Haar-Fisz transform uses 50 external cyclespins as suggested by Fryzlewicz \& Nason (2004).
-The Anscombe transformations use the Symmlet 8 basis, while the Haar-Fisz transformation uses the Symmlet 10 basis, as recommended by the corresponding software.
-Out of the three Bayesian methods included in this simulation study, SMASH and BMSM both estimate the hyperparameters for their respective priors by maximum likelihood, while BMMIM uses fixed hyperparameters as recommended in Besbeas (2004).
-In addition, we also considered the conditional variance stabilization (CVS) approach described in Jansen (2006).
-However, we did not include the MSEs for CVS as we did not obtain sensible results, and are wary that we were misusing the software.
-Except for BMSM and our method (which are entirely adaptive), we considered primary resolution levels of 4,5,6 and 7 for all other methods.
-We present the relative MSEs for test functions ``Angles'' and ``Bumps'' in Tables \ref{table:pois_angles} and \ref{table:pois_bumps} respectively; full simulation results can be found in Appendix \ref{}.\bigskip\\
-\begin{table}[ht]
+Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (Fryzlewicz \& Nason (2004)) and BMSM (Kolaczyk (1999b)), which are two popular and accurate Poisson denoising techniques, for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8), which are of primary interest.
+Complete results, including a (min,max) intensity of (1/128, 128), are included in appendix \textcolor{red}{where?}.
+From figure \ref{fig:pois_sim}, it is clear that SMASH outperforms both methods, and the claim holds true in general.
+As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asmyptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
+Besides the assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
+Here we analyzed primary resolution levels of 4, 5, 6 and 7.
+On the other hand, SMASH outperforms BMSM consistently, even though our method is based on the same likelihood factorization used in the latter.
+We can thus conclude that the choice of ASH as the shrinkage procedure (with the necessary likelihood approximations) is superior to that used in BMSM.
+As will be discussed later, using the formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model.
+\begin{figure}
 \centering
-\begin{tabular}{rrrr}
-  \hline
- & (0.01,3) & (1/8,8) & (1/128,128) \\
-  \hline
-SMASH & 1.00 & 1.00 & 1.00 \\
-  BMSM & 1.15 & 1.04 & 1.01 \\
-  BMMIM & 1.53 & 1.49 & 21.99 \\
-  Haar-Fisz & 2.05 & 2.47 & 4.36 \\
-  Anscombe, universal & 2.61 & 2.80 & 4.24 \\
-  Haar thresholds & 1.52 & 1.66 & 12.17 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Clipped Blocks function for Poisson data}
-\label{table:pois_angles}
-\end{table}
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
+        \caption{}
+        \label{fig:pois_1}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
+        \caption{}
+        \label{fig:pois_8}
+    \end{subfigure}
+    \caption{Violin plots of MISEs for various methods. a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8)}
+    \label{fig:pois_sim}
+\end{figure}
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrr}
-  \hline
- & (0.01,3) & (1/8,8) & (1/128,128) \\
-  \hline
-SMASH & 1.00 & 1.00 & 1.00 \\
-  BMSM & 1.55 & 1.58 & 1.21 \\
-  BMMIM & 1.32 & 1.86 & 2.06 \\
-  Haar-Fisz & 1.20 & 1.39 & 1.31 \\
-  Anscombe, universal & 1.55 & 1.88 & 1.39 \\
-  Haar thresholds & 1.35 & 1.38 & 1.23 \\
-   \hline
-\end{tabular}
-\caption{Relative MSE of various methods for the Bumps function for Poisson data}
-\label{table:pois_bumps}
-\end{table}
-
-From Tables \ref{table:pois_angles} and \ref{table:pois_bumps} we can see that our method consistently outperforms other methods discussed here.
-This is particularly evident for the low intensity cases (ie (min,max) intensity of (0.01,3) and (1/8,8)), which are of primary interest in our application to sequencing data.
-At the same time, our method still performs competitively even when the average/peak intensity is high.
-Note that our method substantially improves on the performance of other methods for test function ``Bumps'', which is extremely hard to estimate due to its inhomogeneity.
+In terms of computation, we note that SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter method needs to be rerun for each shift of the data.
+However, a direct comparison between SMASH and BMSM is uninformative, as they are coded in different programming environments.
+Nevertheless, the similarities between the two methods imply that they should behave identically in this aspect, barring differences in coding.
 
 Overall, these simulation studies demonstrate the ability of our method to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptiveness of the shrinkage procedure ASH.
-Although we have considered an extensive range of problems here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has to be determined.
+Although we have considered an extensive range of scenarios here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has yet to be determined.
 In the next section, we will apply our method to two example datasets that have been discussed in previous work, and comment on the resulting estimates.
-\bigskip\\
+
 \section{Application to real datasets}
@@
 This deals with the second complication.
-The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.\bigskip\\
-\begin{figure}[h]
+The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.
+
+\begin{figure}
 \centering
@@
     \end{subfigure}
-
     \begin{subfigure}[b]{0.4\textwidth}
@@
 \end{figure}
-\bigskip\\
+
 Except for possible boundary effects, our mean and conditional variance estimates are similar to those of Fan \& Yao (1998).
@@
 \newpage
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
     \end{subfigure}
-
     \begin{subfigure}[b]{0.85\textwidth}
@@
 \end{figure}
-From Figure \ref{fig:seq_peak_est} it is clear the intensity estimate from our method can recognize the peaks detected by MACS.
+From Figure \ref{fig:seq_peak_est} it is clear that SMASH can recognize the peaks detected by MACS.
 Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.
-At the same time, our method also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
+At the same time, SMASH also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
 \section{Discussion}
@@
 Gaussian noise, and are thus challenging tasks.
-Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, demonstrating its potential in many other applications.\bigskip\\
-In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as approximate credible intervals as a measure of uncertainty.
-In addition, we can also estimate the variance function if desired, which can be used to provide frequentist confidence intervals for other forms of mean estimation.
-To the best of our knowledge, there is no readily available software which implements joint mean and variance estimation in the wavelet literature.
-We have also confirmed through simulations that our method is relatively robust to simple forms of autocorrelation between the errors (details needed).
-In the case of Poisson regression, we improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods by utilizing ASH as the shrinkage procedure, which allows for more flexibility and precision.
+Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, revealing its potential in many other applications.
+
+In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as their approximate posterior variances as a measure of uncertainty.
+In addition, the variance function can also be estimated, which would provide frequentist confidence intervals for other forms of mean estimation.
+To the best of our knowledge, there is no readily available software in the wavelet literature that implements joint mean and variance estimation.
+Simulations have also confirmed that our method is relatively robust to simple forms of autocorrelation between the errors (details needed).
+In the case of Poisson regression, we improved upon the conjugate Beta priors in Kolaczak (1999) by using ASH as a shrinkage procedure, which allows for more flexibility and precision.
 %In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution.
@@
 On the other hand, the primary resolution level in almost all of the other wavelet-based methods actually affects their performance in varying degrees, depending on the underlying mean and/or variance function.
-Hence, our fully adaptive procedures allow users to easily apply them to any given dataset, depending on context.\bigskip\\
-We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature in terms of pointwise accuracy (MSE in this case).
-Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussians used indicate that our methods are computationally fast, since the posteriors can be computed analytically.
-In the Gaussian case, our simulation study demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d.
-errors, whilst maintaining the same accuracy in the presence of heteroskedastic errors.
-Unfortunately, the lack of readily available software for variance estimation made it difficult to assess the performance of our method in that context.
+Hence, our fully adaptive procedure allows users to easily apply it to any given dataset, depending on the type of noise.
+
+We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature, in terms of pointwise accuracy (MSE in this case).
+Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussian priors imply that our methods are computationally fast, since the posteriors can be computed analytically.
+In the Gaussian case, simulation results demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d.
+errors (without explicitly assuming thus), whilst maintaining superior accuracy when heteroskedastic errors are present.
+Unfortunately, the lack of readily available software (except for MFVB, as described in Menictas \& Wand (2014)) for variance estimation made it difficult to assess the performance of our method in that context.
 On the other hand, we were able to compare our method to some of the more popular denoising techniques in the Poisson case.
-Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods (Kolaczyk 1999) by utilizing ASH as the shrinkage procedure, which allows for more flexibility and accuracy.
+Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods (Kolaczyk (1999)) by using ASH as the shrinkage procedure, which allows for more flexibility and accuracy.
 This is particularly evident when the mean intensity is low, as is common in many high-throughput genomic sequencing datasets.
-Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm since we do not have to perform external cycle-spinning.
-Unfortunately, we were not able to directly compare the computational efficiency of our method to other methods due to differences in the programming software involved.\bigskip\\
+Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm.
+Unfortunately, we were not able to directly compare the computational efficiency of our method to many other methods due to differences in the programming software involved.
+
 Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios.
-In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see Morris 2006).
-Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which would encapsulate a sample with temporally or spatially structured data points.
+In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see Morris (2006)).
+Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which encapsulates a sample with temporally or spatially structured data points.
 While Morris (2006) proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category.
@@
 In the simplest case, we could obtain spatially structured differences between groups by including a single covariate that categorizes each sample.
-In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where differential expression is present between say, different cell lines, as per our sequencing example in the previous section.
-The Gaussian model could potentially be used in...(??).\bigskip\\
+In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where structured differences are present between say, various cell lines, as per our sequencing example in the previous section.
+The Gaussian model could potentially be used in...(??).
+
 With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible.
 For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in Nowak (1998) (again, reference technical report).
-However, recent research in image denoising problems has shown that wavelet transformations might not be ideal due to smooth curves being present in many images such as photographs.
+However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable.
 We could thus incorporate ASH into other types of transformations such as curvelets, which would be a potential direction for future work.
@@
 \section{}\label{app:var estimation}\bigskip
-\textbf{Variance estimation for Gaussian denoising}\bigskip\\
+\textbf{Variance estimation for Gaussian denoising}
+
 With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$.
@@
 One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH).
-The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.\bigskip\\
+The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.
 
 \section{}\label{app:reconstruction}\bigskip
-\textbf{Signal reconstruction for Poisson denoising}\bigskip\\
+\textbf{Signal reconstruction for Poisson denoising}
+
 Given the posterior means and variances of the $\Ga$'s from ASH, the first step to reconstructing the signal is to find the posterior means of $p_{jk}:=\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and $q_{jk}:=\frac{\Gl_{j+1,2k+1}}{\Gl_{jk}}$ (for $j=0,...,J-1$ and $k=0,...,2^j-1$).
@@
 \end{eqnarray}
-noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.\bigskip\\
+noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.
+
 Finally, we can easily back-transform to construct an estimated signal, by noting that we can express $\Gl_i$ as a product of the $p$'s and $q$'s for any $i=1,2,...,n$.
@@
 E(q_{00})^{c_1}E(q_{1,d_1})^{c_2}...E(q_{J-1,d_{J-1}})^{c_J}\end{eqnarray}
-\bigskip\\
+
 As an additional step, we can also construct a credible band around the signal using the posterior variances for inference purposes. From \eqref{eq:product} we have the following:
@@
 \end{eqnarray}
-Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.\bigskip\\
+Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.
+
 Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see Coifman \& Donoho (1995), and Kolaczyk (1999)) rather than as described above.

### 2015-10-26 paper/draft_3_no_fig.tex
added draft with no figures

--- 2015-08-07 paper/draft_3.tex
@@
 
-\begin{figure}[ht]
-\centering
-	   \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_homo_comp.pdf}
-        \caption{}
-        \label{fig:gaus_homo_comp}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_homo_smash.pdf}
-        \caption{}
-        \label{fig:gaus_homo_smash}
-    \end{subfigure}
-    \caption{Violin plots of MISEs for various methods.
+%\begin{figure}[ht]
+%\centering
+	   %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_gaus_homo_comp.pdf}
+        %\caption{}
+        %\label{fig:gaus_homo_comp}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_gaus_homo_smash.pdf}
+        %\caption{}
+        %\label{fig:gaus_homo_smash}
+    %\end{subfigure}
+    %\caption{Violin plots of MISEs for various methods.
 Dashed green line indicates the median MISE for SMASH.
 a) compares SMASH against two popular and accurate denoising methods: TI-thresholding and Ebayesthresh, and b) demonstrates the performance gain of SMASH when it is provided the true variance.}
-    \label{fig:gaus_homo}
-\end{figure}
+    %\label{fig:gaus_homo}
+%\end{figure}
 
@@
 Nevertheless, similar results hold in general for different mean and variance functions, SNRs, and sample sizes.
-\begin{figure}[ht]
-\centering
-	\includegraphics[width=\textwidth]{simple_eg.pdf}
-	\caption{Simple illustration of heteroskedastic Gaussian denoising.
+%\begin{figure}[ht]
+%\centering
+	%\includegraphics[width=\textwidth]{simple_eg.pdf}
+	%\caption{Simple illustration of heteroskedastic Gaussian denoising.
 Top left plot shows the mean function, top right plot shows the variance function, bottom left plot shows a sample dataset, and bottom right plot shows the estimated mean functions from SMASH and TI-thresh against the true mean function.}
-	\label{fig:simple_eg}
-\end{figure}
-
-\begin{figure}[ht]
-\centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_ti.pdf}
-        \caption{}
-        \label{fig:gaus_hetero_ti}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_homo.pdf}
-        \caption{}
-        \label{fig:gaus_hetero_homo}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_smash.pdf}
-        \caption{}
-        \label{fig:gaus_hetero_smash}
-    \end{subfigure}
-    \caption{Violin plots of MISEs for various methods.
+	%\label{fig:simple_eg}
+%\end{figure}    
+%
+%\begin{figure}[ht]
+%\centering
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_gaus_hetero_ti.pdf}
+        %\caption{}
+        %\label{fig:gaus_hetero_ti}
+    %\end{subfigure}
+		%\hfill
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_gaus_hetero_homo.pdf}
+        %\caption{}
+        %\label{fig:gaus_hetero_homo}
+    %\end{subfigure}
+		%\hfill
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_gaus_hetero_smash.pdf}
+        %\caption{}
+        %\label{fig:gaus_hetero_smash}
+    %\end{subfigure}
+    %\caption{Violin plots of MISEs for various methods.
 Dashed green line indicates the median MISE for SMASH.
@@
 b) demonstrates the importance of taking heteroskedasticity into account, and c) reveals the performance gain of SMASH when it is provided the true variance.}
-    \label{fig:gaus_hetero}
-\end{figure}
+    %\label{fig:gaus_hetero}
+%\end{figure}
 
@@
 \end{enumerate}
-\begin{figure}[ht]
-\centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{mfvb_mean.pdf}
-        \caption{}
-        \label{fig:mfvb_mean}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{mfvb_var.pdf}
-        \caption{}
-        \label{fig:mfvb_var}
-    \end{subfigure}
-    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.}
-    \label{fig:mfvb_fn}
-\end{figure}
+%\begin{figure}[ht]
+%\centering
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{mfvb_mean.pdf}
+        %\caption{}
+        %\label{fig:mfvb_mean}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{mfvb_var.pdf}
+        %\caption{}
+        %\label{fig:mfvb_var}
+    %\end{subfigure}
+    %\caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.}
+    %\label{fig:mfvb_fn}
+%\end{figure}
 In the first scenario, the number of data points is not a power of two, nor are the point equally spaced.
@@
 As will be discussed later, using the formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model.
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
-        \caption{}
-        \label{fig:pois_1}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
-        \caption{}
-        \label{fig:pois_8}
-    \end{subfigure}
-    \caption{Violin plots of MISEs for various methods. a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8)}
-    \label{fig:pois_sim}
-\end{figure}
+%\begin{figure}
+%\centering
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_pois_1.pdf}
+        %\caption{}
+        %\label{fig:pois_1}
+    %\end{subfigure}
+		%\hfill
+    %\begin{subfigure}[b]{0.45\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{violin_pois_8.pdf}
+        %\caption{}
+        %\label{fig:pois_8}
+    %\end{subfigure}
+    %\caption{Violin plots of MISEs for various methods. a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8)}
+    %\label{fig:pois_sim}
+%\end{figure}
 
@@
 
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_a.pdf}
-        \caption{}
-        \label{fig:tb_raw_data}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_b.pdf}
-        \caption{}
-        \label{fig:tb_res}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_c.pdf}
-        \caption{}
-        \label{fig:tb_mean}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_d.pdf}
-        \caption{}
-        \label{fig:tb_var}
-    \end{subfigure}
-    \caption{Analysis of yields from three-month Treasury Bills.
+%\begin{figure}
+%\centering
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_a.pdf}
+        %\caption{}
+        %\label{fig:tb_raw_data}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_b.pdf}
+        %\caption{}
+        %\label{fig:tb_res}
+    %\end{subfigure}
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_c.pdf}
+        %\caption{}
+        %\label{fig:tb_mean}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_d.pdf}
+        %\caption{}
+        %\label{fig:tb_var}
+    %\end{subfigure}
+    %\caption{Analysis of yields from three-month Treasury Bills.
 (a) Raw data of interest rates as a function of time.
@@
 (d) The estimated conditional variance curve, with approximate 95\% credible bands.}
-\end{figure}
+%\end{figure}
 
@@
 \newpage
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.85\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{peaks_comp_a.pdf}
-        \caption{}
-        \label{fig:seq_peak_data}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.85\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{peaks_comp_b.pdf}
-        \caption{}
-        \label{fig:seq_peak_est}
-    \end{subfigure}
-    \caption{Analysis of reads taken from the GM12878 cell line, spanning position 880001 to 1011072 on chromosome 1.
+%\begin{figure}
+%\centering
+    %\begin{subfigure}[b]{0.85\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{peaks_comp_a.pdf}
+        %\caption{}
+        %\label{fig:seq_peak_data}
+    %\end{subfigure}
+    %\begin{subfigure}[b]{0.85\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{peaks_comp_b.pdf}
+        %\caption{}
+        %\label{fig:seq_peak_est}
+    %\end{subfigure}
+    %\caption{Analysis of reads taken from the GM12878 cell line, spanning position 880001 to 1011072 on chromosome 1.
 (a) Raw sequencing counts.
 (b) Estimated intensity function from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).}
-    \label{fig:seq_peak}
-\end{figure}
+    %\label{fig:seq_peak}
+%\end{figure}
 From Figure \ref{fig:seq_peak_est} it is clear that SMASH can recognize the peaks detected by MACS.

### 2015-10-26 paper/vioplot_col.R
modified some plots

@@ -1,0 +1,261 @@
+# vioplot.col = function(x, ..., range = 1.5, h = NULL, ylim = NULL, names = NULL, 
+#                        horizontal = FALSE, col = "magenta", border = "black", lty = 1, 
+#                        lwd = 1, rectCol = "black", colMed = "white", pchMed = 19, 
+#                        at, add = FALSE, wex = 1, drawRect = TRUE) 
+# {
+#   datas <- list(x, ...)
+#   n <- length(datas)
+#   if (missing(at)) 
+#     at <- 1:n
+#   if(length(col)==1) col <- rep(col,n)
+#   upper <- vector(mode = "numeric", length = n)
+#   lower <- vector(mode = "numeric", length = n)
+#   q1 <- vector(mode = "numeric", length = n)
+#   q3 <- vector(mode = "numeric", length = n)
+#   med <- vector(mode = "numeric", length = n)
+#   base <- vector(mode = "list", length = n)
+#   height <- vector(mode = "list", length = n)
+#   baserange <- c(Inf, -Inf)
+#   args <- list(display = "none")
+#   if (!(is.null(h))) 
+#     args <- c(args, h = h)
+#   for (i in 1:n) {
+#     data <- datas[[i]]
+#     data.min <- min(data)
+#     data.max <- max(data)
+#     q1[i] <- quantile(data, 0.25)
+#     q3[i] <- quantile(data, 0.75)
+#     med[i] <- median(data)
+#     iqd <- q3[i] - q1[i]
+#     upper[i] <- min(q3[i] + range * iqd, data.max)
+#     lower[i] <- max(q1[i] - range * iqd, data.min)
+#     est.xlim <- c(min(lower[i], data.min), max(upper[i], 
+#                                                data.max))
+#     smout <- do.call("sm.density", c(list(data, xlim = est.xlim), 
+#                                      args))
+#     hscale <- 0.4/max(smout$estimate) * wex
+#     base[[i]] <- smout$eval.points
+#     height[[i]] <- smout$estimate * hscale
+#     t <- range(base[[i]])
+#     baserange[1] <- min(baserange[1], t[1])
+#     baserange[2] <- max(baserange[2], t[2])
+#   }
+#   if (!add) {
+#     xlim <- if (n == 1) 
+#       at + c(-0.5, 0.5)
+#     else range(at) + min(diff(at))/2 * c(-1, 1)
+#     if (is.null(ylim)) {
[…]

### 2015-11-20 paper/draft_5.tex
added new draft; updated more  figures

\documentclass[12pt]{article}
\usepackage{amsmath,amsthm,amssymb,amsfonts,fullpage,verbatim,bm,graphicx,enumerate,epstopdf,lscape,enumitem}
\usepackage[titletoc,title]{appendix}
\usepackage[dvipsnames,usenames]{color}
\usepackage[pdftex,pagebackref,colorlinks=true,pdfpagemode=UseNone,urlcolor=blue,linkcolor=blue,citecolor=BrickRed,pdfstartview=FitH,plainpages=true]{hyperref}
\usepackage[top=1.15in,bottom=1.15in,left=1.25in,right=1.25in,letterpaper]{geometry}
\usepackage[font=scriptsize]{caption}
\usepackage{cite}
\usepackage{caption,subcaption}

\setlist{noitemsep}

\def\CC{\mathbb{C}}
\def\RR{\mathbb{R}}
\def\ZZ{\mathbb{Z}}
\def\PP{\mathbb{P}}
\def\EE{\mathbb{E}}

\newcommand{\Ga}{\alpha}
\newcommand{\Gb}{\beta}
\newcommand{\Gg}{\gamma}     \newcommand{\GG}{\Gamma}
\newcommand{\Gd}{\delta}     \newcommand{\GD}{\Delta}
\newcommand{\Ge}{\epsilon}
\newcommand{\Gf}{\phi}       \newcommand{\GF}{\Phi}
\newcommand{\Gh}{\theta}
\newcommand{\Gi}{\iota}
\newcommand{\Gk}{\kappa}
\newcommand{\Gl}{\lambda}    \newcommand{\GL}{\Lambda}
\newcommand{\Go}{\omega}     \newcommand{\GO}{\Omega}
\newcommand{\Gs}{\sigma}     \newcommand{\GS}{\Sigma}
\newcommand{\Gt}{\tau}
\newcommand{\Gz}{\zeta}
\newcommand{\s}{\sigma}
\newcommand{\tr}{\triangle}

\begin{document}

\title{\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals (?)}}
\date{}
\maketitle

\section{Abstract}

\section{Introduction}

Shrinkage and sparsity play a key role in many areas of modern statistics, including, for example, high-dimensional regression \cite{Tibshirani1996Regression}, covariance or precision matrix estimation \cite{Bickel2008Covariance}, multiple testing \cite{efron:xx} and signal denoising \cite{Donoho1994Ideal, donoho95}. One attractive way to achieve shrinkage and sparsity is via Bayesian or Empirical Bayes (EB) methods (e.g.\cite{efron?, Johnstone2005Empirical, Clyde2000Flexible,george.mccullogh,bayesian-covariance-estimation}).  
However, these methods are usually perceived to require context-specific implementations, and this overhead can limit their use in practice. Here we consider a flexible EB approach to shrinkage, which we call {\it adaptive shrinkage}, whose goal is to provide a generic shrinkage method that could be useful for a range of applications. 
We show how this single shrinkage method can produce effective results for several denoising problems, including smoothing Gaussian means in the presence of heteroskedastic variance, smoothing of Gaussian variances, and smoothing Poisson means. These are all settings that are relatively underserved by existing EB implementations, and indeed  we are unaware of any existing EB implementation for smoothing either the mean or the variance in the heteroskedastic Gaussian case.
Consistent with previous studies (\cite{Antoniadis2001Wavelet}) we find these EB methods to be more accurate than commonly-used thresholding rules, and, in the Poisson case, competitive with a purpose-built EB method.

%Methods used to achieve shrinkage and sparsity include simple thresholding rules
%(e.g.~\cite{TI-thresh, SURE, others?,thresholding-outside-of-wavelets?}), penalized likelihood approaches (e.g.~\cite{lasso,elasticnet,glasso}), and 
%Bayesian or Empirical Bayesian (EB) methods (e.g.\cite{efron?, johnstone.silverman.xx,clyde.george.jrssb,george.mccullogh,bayesian-covariance-estimation}.
%While thresholding rules and penalized likelihood methods can possess good asymptotic properties in theory, empirical
%comparisons have found that Bayesian and EB methods can perform better in practice \cite{antoniadis:2001,guan.stephens.largescaleregression}.
%However, Bayesian and EB methods are usually perceived to require context-specific implementations, and this
%overhead can limit their application.
%Our goal here is to outline a strategy that can reduce this implementational overhead, and apply it to produce EB shrinkage methods for signal denoising problems.
%DO we want to highlight ash or the generic strategy? Or both? Current text highlights mostly the strategy,
%leaving ash as just a component of it.
%Could add "Indeed one of our goals is to showcase the flexibility of this EB approach to shrinkage" as second
%sentence of next paragraph?

%Among their most prominent
%applications has been signal denoising, which can be achieved by inducing sparsity or shrinkage in a transformed (e.g. wavelet)
%domain \cite{donoho.johnston.xx}. This approach to signal denoising has strong theoretical support, and is often accurate and computationally convenient, so it has
%become widely used. Consequently many approaches have been suggested for achieving the desired shrinkage, including both
%simple thresholding rules \cite{TI-thresh, SURE, others?} and Bayes or Empirical Bayes (EB) methods \cite{johnstone.silverman.xx,clyde.george.jrssb}.
%Although classical thresholding rules have been shown to possess good asymptotic properties in theory, EB methods often
%perform better in practice \cite{antoniadis:2001}.

\def\ash{{\tt ash}}
\def\bhat{\hat{\beta}}
\def\shat{\hat{s}}

The {\it adaptive shrinkage} (\ash) method is described in detail in a companion paper, \cite{stephens:2015},
which applies \ash~to estimate false discovery rates (FDR) in multiple testing settings. 
Here we apply the same method to a different problem, signal denoising.  In brief,
\ash~aims to provide EB shrinkage estimates of quantities $\beta_1,\dots,\beta_J$, given observed estimates of these quantities $\bhat_1,\dots,\bhat_J$, 
and corresponding standard errors $\shat_1,\dots,\shat_J$. In common with most EB methods \ash~assumes that the $\beta_j$ come from some common underlying distribution, $g$, which is estimated from all the data (as $\hat{g}$ say), and
uses the posterior mean,  $E(\beta_j | \bhat_j, \shat_j, \hat{g})$ as a shrinkage estimate of $\beta_j$.
Key features that make \ash~attractive as a flexible and generic approach to shrinkage include: 
i) its flexible semi-parametric modelling of $g$, under the constraint that it be uni-modal at 0 (and, optionally, symmetric); ii) its incorporation of the precision of each measurement through the standard errors $\shat_j$, so that the amount of shrinkage adapts to the precision of each measurement;  iii) its computational simplicity and speed: e.g.~our {\tt R} implementation typically takes a fraction of a second for $J=1000$;
iv) its computational stability, with, for example, minimal problems due to convergence to local optima \cite{stephens:2015}.

% treating the observations as conditionally independent from a normal model, $\bhat_j | \beta_j, \shat_j \sim N(\beta_j, \shat_j)$. Given the estimate $\hat{g}$ for $g$, \ash~then computes the posterior distiributions $\beta_j | \bhat_j, \shat_j, \hat{g}$,vand provides the posterior mean of $\beta_j$ as a shrinkage estimate for $\beta_j$.

%The name ``adaptive shrinkage" comes from the fact that shrinkage is adaptive to both the overall signal in the data (through estimation of $g$), and to the precision of each observation (through incorporation of $\shat_j$), with imprecise observations being shrunk most strongly.

The \ash~method makes assumptions, particularly conditional independence of observations, and normality of likelihood $p(\bhat_j | \beta_j, \shat_j)$, that will often be violated in practice,
and indeed are violated in our applications here. However, as we demonstrate later, it can nonetheless produce good shrinkage estimates. 
Essentially, we treat
%highlighting the potential of treating ??
\ash~as a generic or ``black box" shrinkage procedure, which inputs
estimates and their corresponding standard errors and outputs shrinkage estimates, without worrying too much about 
the details. Of course, one must be careful about how far one takes this.  And in more complex applications 
(e.g. large-scale regression and covariance estimation) it is unclear whether this strategy can be usefully applied. However,
we believe our results here for signal denoising, together with those in \cite{stephens:15} for FDR estimation, illustrate \ash's potential and flexibility. 
%maybe move to discussion

%In this paper we use \ash~to tackle several signal denoising problems,  including Poisson smoothing,
%and smoothing both the mean and variance of heteroskedastic Gaussian data. 
Shrinkage methods are widely-used in signal denoising applications, because signal denoising can be accurately and conveniently achieved by shrinkage in a transformed (e.g.~wavelet) domain \cite{Donoho1994Ideal}. 
Commonly-used shrinkage methods include both
simple thresholding rules \cite{Coifman1995Translationinvariant, Donoho1994Ideal, donoho95} and EB methods \cite{Johnstone2005Empirical, Clyde2000Flexible}.
Being an EB method, \ash~has much in common with these previous EB methods, but generalizes them in two ways: first, 
\ash~allows more flexibility in the underlying distribution $g$ than the Laplace or spike-and-slab
distributions used in \cite{Johnstone2005Empirical, Clyde2000Flexible}; second \ash~allows for variations in precision in the transformed observations (e.g. wavelet coefficients). The latter property is particularly important for
the Poisson and heteroskedastic Gaussian settings we consider here.

Software implementations of our methods are available in the R packages {\tt ashr} (Adaptive SHrinkage in R)
and {\tt smash} (SMoothing by Adaptive SHrinkage), available from 
\url{http://www.github.com/stephens999/ashr} and \url{http://www.github.com/stephenslab/smash} respectively.

%Although classical thresholding rules have been shown to possess good asymptotic properties in theory, EB methods often
%perform better in practice \cite{antoniadis:2001}.

%Our goals in this paper are therefore two-fold. FIrst, to showcase the potential for the adaptive shrinkage method to provide a simple and effective
% solution to shrinkage estimation in important practical problems; and, second, to provide software implementations of this 
% idea for smoothing Poisson and heteroskedastic Gaussian signals - settings that are underserved by existing implementations.

%In recent years, various shrinkage and thresholding procedures have become ever more popular in many applications where sparsity is desired. Here ``sparsity'' is loosely defined in that it also includes the case where many terms are near-zero, as opposed to exactly zero. The most prominent usage of such procedures appear in multiresolution denoising analyses such as wavelets, where sparsity in a transformed domain often corresponds to smoothness in the data space [references]. Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are actually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references]. In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.

%Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators. These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994). Wavelet methods are locally adaptive in that they achieve the optimal minimax rate over a wide variety of functions, yet are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001]. While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al. (2001) has demonstrated that various Bayesian shrinkage methods are usually more adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE). However, many Bayesian methods require specific distributional assumptions, and are not easily extensible to more complex problems, two of which we subsequently describe. On the other hand, our method simplies the task by making approximations, while still possessing good finite sample performance and computational efficiency. These approximations also allow us to use ASH as the common shrinkage procedure in both the problems.

Move some of this material to the relevant place? or discussion?

The first problem relates to mean and variance estimation with Gaussian noise. Although the framework for homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], methods dealing with heteroskedastic errors are uncommon. Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators. Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous variance estimation methods using a wavelet thresholding approach on first order differences. Here we present an approach that estimates both the mean and variance accurately by incorporating ASH into a novel wavelet denoising framework. [mention the lack of available software?]

The second task is to denoise a Poisson distributed signal. This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest. This problem is interesting because there are many distinct ways to perform signal recovery. Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by exploiting the mean-variance relationship of a Poisson distribution. Kolaczyk (1997, 1999a) derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d. Gaussian case.  However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance. Furthermore, both these methods are quite sensitive to the choice of the primary resolution level as our simulations will show. Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by Kolaczyk (1999b) to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen. We will improve upon the prior (and likelihood) specification by using ASH as the main shrinkage procedure in a Bayesian framework similar to that of Kolaczyk (1999b).

%Both the aforementioned problems are harder to deal with than the classical problem with i.i.d. Gaussian errors, and usually requires extension of the ideas from the latter task. Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage.

%The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet settings described here. As an Empirical Bayes procedure, ASH borrows information across all available data and is extremely data adaptive. At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a reference for this?) is that variable variances are allowed as input, a feature which latter methods lack. This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above. Furthermore, Gaussian mixtures can effectively approximate any unimodal distribution, allowing for an extremely flexible prior. In tackling these two specific problems, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising accuracy. Typical wavelet methods require the specification of a primary resolution level as a ``tuning'' parameter, which could substantially influence the accuracy of the method. However, applying ASH to every resolution in the wavelet transformationwe spares us the need for such a parameter. For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??). With the main shrinkage method accounted for, we will proceed to explore the two aforementioned problems in detail. Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.

\section{Methods}

\def\bY{\bm{Y}}
\def\bmu{\bm{\mu}}
\def\bp{\bm{p}}
\def\be{\bm{\epsilon}}
\def\tbY{\tilde\bY}
\def\tbe{\tilde\be}
\def\tbmu{\tilde\bmu}
\def\tmu{\tilde\mu}
\def\tY{\tilde{Y}}
\def\s{\sigma}
\def\|{\,|\,}

\subsection{Adaptive shrinkage}

Here we briefly outline the adaptive shrinkage method; see \cite{stephens:2015} for full details.
Adaptive shrinkage (\ash) is an EB method
for estimating quantities $\beta=(\beta_1,\dots,\beta_n)$ from noisy estimates 
$\bhat=(\bhat_1,\dots,\bhat_n)$ and their corresponding standard errors $\shat = (\shat_1,\dots,\shat_n)$. 
In its simpest form it assumes the hierarchical model
\begin{align}
\beta_j \| \shat_j & \sim g \\
\bhat_j \| \beta_j, \shat_j & \sim N(\beta_j, \shat_j^2),
\end{align}
where the distribution $g$ is constrained to be unimodal and symmetric. This constraint on $g$ can
be flexibly achieved using 
a mixture of zero-centered normal distributions
\begin{equation}
g(\cdot)=\sum_{k=0}^K \pi_0 N(\cdot;0,\sigma_k^2),
\end{equation}
where the mixture weights $\pi_0,\dots,\pi_K$ are non-negative and sum to 1, and $N(\cdot; \mu,\sigma^2)$ denotes
the density of a normal distribution with mean $\mu$ and variance $\sigma^2$.
A key idea, which substantially simplies inference, is to take
$\sigma_0,\dots,\sigma_K$ to be a fixed grid of values. ranging from very small (e.g.~$\sigma_0=0$,
in which case $g$ includes a point mass at 0) to very large. Estimating $g$ then boils down to estimating
the mixture weights $\pi$, which is done by maximum likelihood using a simple EM algorithm.
Given an estimate $\hat{g}$ for $g$, the conditional distributions $p(\beta_j \| \bhat, \shat, \hat{g})$ are analytically
tractable, and the posterior mean $E(\beta_j \| \bhat, \shat, \hat{g})$ provides a shrinkage point estimate for $\beta_j$.

\cite{stephens:2015} also introduces various embellishments that are implemented in the {\tt ashr}
package, including generalizing the normal likelihood to a $t$ likelihood, and dropping the symmetric
constraint on $g$ by replacing the mixture
of normals with a more flexible (though less smooth) mixture of uniforms. However, we do not use these embellishments here. 
CHECK: IS THIS TRUE. WHAT PARAMETERS DO WE USE?
We also do not use the penalty term on the likelihood introduced in \cite{stephens:2015} for FDR applications,
because it is unnecessary in this context, and has little effect on the shrinkage estimates.

%\cite{stephens:2015} demonstrates the potential for this adaptive shrinkage approach to  estimate false discovery rates and related quantities in settings where the primary goal is to identify the $\beta_j$ that differ ``significantly" from 0. Our work here compliments this, by demonstrating  the potential for this approach to provide the adaptive shrinkage estimates that its name promises.

\subsection{Signal Denoising}

A common generic signal denoising problem, sometimes known as ``non-parametric regression", involves
estimating a ``spatially-structured" mean $\bmu=(\mu_1,\dots,\mu_T)$, from corresponding
noisy observations $\bY = (Y_1,\dots,Y_T)$, where $t=1,\dots,T$ indexes location in a one-dimensional space,
such as time, or, as in our example later, location along the genome. 
 By ``spatially-structured" we mean that $\mu_t$ will often be similar to $\mu_t'$ for small $|t-t'|$, though we do not rule
out occasional abrupt changes in $\mu$.  For convenience we assume that $T=2^J$ for some integer $J$, as is common when using wavelet methods.

The most studied denoising problem is the homoskedastic Gaussian case; that is, 
the data $Y_t$ have Gaussian noise and constant variance.
Here we consider the more general case of Gaussian data with
spatially-structured mean {\it and} spatially-structured (non-constant) variance. 
In some settings the changes in variance may themselves be of interest, and our methods provide explicit estimates for the variance as well as the mean. In addition we consider Poisson data (where the variance depends on the mean, so 
a spatially-structure mean implies spatially-structure variance).
To build up to these more interesting cases we start with the simplest setting: 
Gaussian noise with known variance.

\subsubsection{Gaussian noise; estimate mean (known variance)}

Suppose the $Y_t$ are independent noisy observations of the $\mu_t$, with Gaussian noise of known variance $\s^2_t$. That is,
\begin{equation}\label{eq:1d gaussian model}
\bY =\bmu+\be
\end{equation}
where $\be \sim N(0,D)$ with $D$ the diagonal matrix with diagonal entries $(\s_1^2,\dots,\s_T^2)$.

%To motivate our method, we first describe wavelet shrinkage from a Bayesian perspective.
Wavelet denoising involves first applying a discrete wavelet transform to the data $\bY$. This
involves pre-multiplying $\bY$ by an orthogonal $n\times n$ matrix $W$ that depends on the orthonormal wavelet basis chosen. Pre-multiplying (\ref{eq:1d gaussian model}) by $W$ yields
\begin{equation} 
W\bY=W\bmu + W\be 
\end{equation}
which, using $\,\tilde{}\,$ to denote the wavelet transform, we write
\begin{equation} \label{eq:wc}
\tbY=\tbmu + \tbe,
\end{equation}
where $\tbe \sim N(0,W D W')$.

A key feature of the wavelet tranform is that if $\bmu$ is spatially structured 
then many elements of $\tbmu=W\bmu$ will tend to be close to zero, and vice versa.
In other words, smoothing in the data domain corresponds to shrinking in the wavelet domain.
Thus, one can obtain a spatially structured estimate of
mean $\bmu$ by first using shrinkage methods to estimate $\tbmu$ and then
reversing the wavelet transform.

%This process is often referred to as ``wavelet shrinkage estimation", because the estimates $\tmu_j$ are obtained from $\tY_j$ by ``shrinking" them towards zero.

Here we use the adaptive shrinkage method to obtain shrinkage estimates for $\tbmu$.
Focussing on the marginals of (\ref{eq:wc}), we have
\begin{equation} \label{eq:normlik}
\tY_j | \tmu_j, s^2_j \sim N(\tmu_j, \omega^2_j).
\end{equation}
%Note that the elements of $\tY$ are not independent unless the variances $\sigma^2_t$ are all equal. 
where
\begin{equation}
\omega^2_j:=\sum_{t=1}^T \s^2_t W_{jt}^2,
\end{equation}
are the diagonal elements of $WDW'$.
Thus, applying ash with $\bhat_j = \tY_j$ and $\shat_j = \omega_j$ yields shrinkage estimates for the $\tmu_j$.
(In practice it is important to group the wavelet-transformed observations $j$ 
by their resolution level before shrinking; see note below.)
Of course, by focusing on the marginals we are ignoring any correlations among the $\tY_j$, and this
is the primary simplification here. (We are not alone in making this simplification;
see also \cite{Silverman1999Wavelets} for example.)

The above outlines the basic strategy, but there are some important
 additional implementational details:
\begin{itemize}
\item Rather than use a single wavelet transforrm, we use the ``non-decimated" wavelet transform, which treats the observations as coming
from a circle, rather than a line, and averages results over all $T$ possible rotations of the data. Although not always necessary, this is a standard trick to reduce artifacts that can occur near discontinuities in the underlying signal (see eg. \cite{Coifman1995Translationinvariant}). COMMENT: WHat about reflection before doing this?
DO OTHER EB APPROACHES CONSIDER THE NDWT? ALSO, POINT FOR DISCUSSION: NDWT INCREASES DEPENDENCE, SO MAKE INDEPENDENCE ASSUMPTION WORSE, BUT MUCH BETTER TO DO IT THAN NOT TO DO IT!
\item The non-decimated wavelet transform yields $T$ wavelet coefficients (transformed values of $\bY$) 
at each of $J=\log_2(T)$ resolution levels.
We apply ash separately to the wavelet coefficients at each resolution level, so that
a different distribution $g$ for the $(\tmu_j)$ is estimated for each resolution. This is the usual way that
EB approaches are applied in this context (e.g.~\cite{checkcgandjs}) and indeed is crucial because
the underlying distribution $g$  will vary with resolution (because smoothness of $\bmu$ will vary with resolution).  
\item Although we have presented the wavelet transform as a matrix multiplication, which is an $o(T^2)$ operation, in practice both the wavelet transform and the inverse tranform are implemented using
Mallat's pyramid algorithm, taking only $T\log(T)$ operations. Do we need $o(T \log T)$ or $O()$? What about the TI table? Is there a different name for the algorithm for the reverse transform?
\end{itemize}
%\item Ash yields a posterior distribution for each $\tmu_t$. A simple approach would
%be to use the posterior mean for $\tmu_t$ and then invert the wavelet transform; however we instead use the delta method?

%Since $\mathbb{V}(Y)=\s^2I$,
%\begin{eqnarray}\label{eq:waveletcoef}
%\bm{d}\sim N_n(\bm{\Ga},\s^2I)
%\end{eqnarray}
%where $\bm{\Ga}=W\mathbb{E}(\bm{Y})$. This implies that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods for $\Ga_t$, $i=1,...,n$. As such, a natural and computationally convenient approach is to set independent priors on $\Ga_t$ as a form of ``shrinkage''. Here we apply the priors from ASH to each resolution level separately, resulting in
%%Although there are many choices for the prior, we use the Gaussian mixture prior from ASH in our method, given by
%\begin{eqnarray}\label{eq:ashprior}
%\Ga_{jk}=\sum_{l=1}^m \pi_l^{(j)} N(0,(s_l^{(j)})^2)
%\end{eqnarray}
%with $\sum_l \pi_l^{(j)}=1$, for $j=1,...,J$. $\pi_t^{(j)}$ and $(s_t^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level, and $m$ is the number of mixture components. In ASH, $m$ is usually chosen to reasonably approximate any unimodal distribution, while maintaining an acceptable computational speed. Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,J$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$. By applying the inverse wavelet transform to the posterior mean $\hat{\bm{\Ga}}$ that ASH produces, one can obtain the posterior mean of $\bm{\mu}$, which serves as an estimate that minimizes the MSE. One could also construct credible bands using the posterior variances.
%
%While many existing methods perform well in the presence of i.i.d. (Gaussian) errors, heteroskedastic (but still independent) errors present a different challenge. One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize. Given the true variances and hence the likelihood, one could compute the full posterior distribution using some specified prior. However, this would be computationally cumbersome, and may be infeasible when extended to multiple signals or higher dimensions. In this case, a suitable prior might also be difficult to find. As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).

%To describe our approach in more detail, first assume that the true variance function is known and given by $\mathbb{V}(\Ge_t)=\s_t$, and that the true mean function is given by $\bm{\mu}=(\mu_1,...,\mu_t)$, where $T=2^J$ for some positive integer $J$. Hence
%\begin{eqnarray}
%\bm{Y}\sim N_n(\bm{\mu},\Sigma)
%\end{eqnarray}
%where $\Sigma=\textrm{diag}(\s_1,...,\s_T)$ is a diagonal matrix. For the rest of this subsection, we will use the non-decimated wavelet transform (NDWT) instead of the standard DWT to achieve translation invariance. This in turn reduces the presence of artifacts, which often occur near discontinuities in the underlying signal (see eg. Coifman \& Donoho (1995)). Then,
%\begin{eqnarray}
%\bm{d}\sim N_n(\bm{\Ga},\tilde{\Sigma})
%\end{eqnarray}
%where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Sigma}=W\Sigma W^T$, where $W$ is the matrix associated with the NDWT for a given wavelet basis. By treating the likelihood for $\bm{\Ga}$ as if it were independent, it can be written as follows(using the double index mentioned above):
%\begin{eqnarray}\label{eq:likelihood}
%L(\bm{\Ga}|\bm{d})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(d_{jk}|\Ga_{jk})
%\end{eqnarray}
%where $P(d_{jk}|\Ga_{jk})=\phi(d_{jk};\Ga_{jk},\tilde{\Sigma}_{(jk,jk)})$. Note that there are $n$ coefficients at each resolution level instead of $2^j$ for resolution $j$ due to the NDWT. Here $\phi$ denotes the Gaussian density function. Since $\Sigma$ is diagonal, it is easy to see that $\tilde{\Sigma}_{(jk,jk)}=\sum_{t=1}^T \Sigma_{ti}_{tW_{jk,i}^2$. In our method, we use ASH to assign independent priors to $\Ga_{jk}$ as with \eqref{eq:ashprior}. %ASH also allows us to estimate the $\pi_t$'s via a maximum likelihood approach and fix the $\s_t$'s by using a grid of values. This particular choice of prior specification is extremely flexible, being able to approximate any symmetrical zero-centered distribution, as well as allowing for a relatively easy estimation of the hyperparameters through empirical Bayes. See ASH for more details regarding this choice of prior (?)
%While ASH produces shrunken estimates of $\Ga_{jk}$ for $j,k>0$, we estimate $\Ga_{00}$ using the corresponding scaling coefficient, which seems intuitively appealing. Finally, we can obtain an estimate of $\mu$ by using the average basis inverse, which is essentially an average of the inverse wavelet transforms for every shift of the data (see Coifman \& Donoho (1995)) since we are using the NDWT. Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, taking only $n\log(n)$ time.

\subsubsection{Estimating spatially structured variance (known mean)}

Although we assumed variances to be known above, the problem of variance estimation is itself non-trivial. 
A common approach is to assume that the variance is constant ($\sigma_t=\sigma$), and that changes in the adjacent means $\mu_t-\mu_{t+1}$ are negligible, so 
\begin{equation} \label{eq:constvar}
\hat{\sigma} = (1/T) \sum_{t=1}^{T} (Y_t-Y_{t-1})^2
\end{equation}
(with $Y_0:=Y_T$) provides an unbiased estimate for $\sigma$. ...CHECK WITH TOM
Here we make the more flexible assumption that the variance function is spatially structured, and use wavelet shrinkage to estimate it.

Assume initially that the mean $\mu_t$ is known, and define
\begin{eqnarray}\label{eq:varobs1}
Z_t^2=(Y_t-\mu_t)^2_t
\end{eqnarray}
to be the ``observations'' for the unknown variance function. Note that $\mathbb{E}(Z_t^2)=\s_t^2$, and so
we have a mean estimation problem. To tackle this we use the mean estimation procedure above (effectively treating the wavelet-transformed values $WZ_t^2$ as Gaussian when really they are linear combinations of $\chi^2$ random variables). To apply this procedure we need the variance
of $Z_t^2$, $\mathbb{V}(Z_t^2)$, which is unknown.
Here we use $\frac{2}{3}Z_t^4$ as an approximately (CHECK) 
unbiased estimator for $\mathbb{V}(Z_t^2)$. (This follows from the distributional result that, when $Z^2 \sim \s^2 \chi^2$, then $\mathbb{E}(Z^4)\approx 3\s^4$, and $\mathbb{V}(Z^2)\approx 2\s^4$.)

Despite the approximations being made here, we have found this procedure to work well in practice in most cases,
perhaps with a tendancy to oversmooth quickly-varying variance functions. (IS THIS A FAIR SUMMARY? DO
WE REALLY KNOW IT IS OVERSMOOTHING? IS IT POSSIBLE TO DO BETTER?)
%Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels. This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).

This approach is similar in spirit to \cite{Cai2008Adaptive}, but they use first order differences instead of the squared residuals, removing the need to jointly estimate the mean and variance. 
WHY DID WE DO THIS? DID IT PERFORM BETTER? How do they deal with the unknown variance?

   One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). LET'S TALK MORE ABOUT THAT...

%MOVE THIS TO DISCUSSION?
%Of course, better likelihoods and priors could be used that reflect the skewness in the distributions of the ``observations'', but we found that a normal approximation works reasonably well (especially for smoother variance functions), and has the key advantage of being easy and fast to implement. The variance estimation process is then very similar to one for mean estimation as described above, with a few extra details. The full procedure is outlined in Appendix \ref{app:var estimation}.

\subsubsection{Estimating spatially-structured mean and variance}

Having specified procedures for estimating the means with variances known, and the variances with means known,
we iterate these procedures to deal with the (typical) case where both are unknown.
We initialize the algorithm by estimating the variance vector $\bm{\s}^2$ using
\begin{eqnarray}\label{eq:initial var est}
\hat{\s}_t^2=\frac{1}{2}\left((Y_t-Y_{t-1})^2+(Y_t-Y_{t+1})^2\right)
\end{eqnarray}
where $Y_0\equiv Y_n$ and $Y_{T+1}\equiv Y_1$ (equivalent to putting the observations on a circle). 
%This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough.
IS THIS as in (eg Cai \& Wang (2008)).? ALSO IS THIS CORRECT? I REMOVED A SUM OVER T THAT TOM HAD.
ALSO, DID WE TRY USING \eqref{eq:constantvar})?
Then we iterate:
\begin{enumerate}
\item[1] Estimate $\bm{\mu}$ as if $\bm{\s}^2$ is known (with the value obtained from the previous step).
\item[2] Estimate $\bm{\s}^2$ as if ${\bm{\mu}}$ is known (with the value obtained by the previous step); return to 1.
\end{enumerate}
We cannot guarantee that this procedure will converge in general. In our simulations we found
that two iterations of steps 1-2 yielded accurate results (so the full procedure consists of initialize + Steps 1-2-1-2).

 \subsection{Smoothing Poisson data}

\def\Poi{\text{Poi}}
\def\Bin{\text{Bin}}

Now assume that each $Y_t$ has a Poisson distribution with mean $\mu_t$.
To do denoising here we apply adaptive shrinkage to the Poisson multiscale models
from \cite{Nowak2000Statistical} and \cite{Timmermann1999Multiscale}, which are an analogue of
wavelet methods for Poisson data.

To explain the idea, first recall the following elementary distributional result:
if $Y_1,Y_2$ are independent, with $Y_j \sim \Poi(\mu_j)$ then 
\begin{align}
Y_1 + Y_2 & \sim \Poi(\mu_1 + \mu_2) \\
Y_1 | (Y_1+Y_2) & \sim \Bin(Y_1+Y_2, \mu_1/(\mu_1+\mu_2)).
\end{align}

To extend this to $T=4$, introduce the notation $v_{i:j}$ to denote, for any vector $v$, 
the sum $\sum_{t=i}^{t=j} v_t$.  Then 
\begin{align} 
Y_{1:4} & \sim \Poi(\mu_{1:4}) \label{eqn:y14} \\
Y_{1:2} | Y_{1:4} & \sim \Bin(Y_{1:4}, \mu_{1:2}/\mu_{1:4})  \label{eqn:y12} \\
Y_1 | Y_{1:2} & \sim \Bin(Y_{1:2}, \mu_1/\mu_{1:2}) \label{eqn:y1} \\ 
Y_3 | Y_{3:4} & \sim \Bin(Y_{3:4}, \mu_3/\mu_{3:4}). \label{eqn:y3}
\end{align} 
Together these models are exactly equivalent to $Y_j \sim \Poi(\mu_j)$, and
they decompose the overall distribution $Y_1,\dots,Y_4$ into parts involving aspects of the data at 
increasing resolution: (\ref{eqn:y14}) represents the coarsest resolution (the sum of all data points), 
whereas (\ref{eqn:y1}) and (\ref{eqn:y3}) represent the finest resolution, with (\ref{eqn:y12}) in between. 
Further, this representation suggests a reparameterization, from $\bmu=(\mu_1,\mu_2,\mu_3,\mu_4)$
to $\mu_{1:4}$ plus the binomial parameters $\bp=(\mu_{1:2}/\mu_{1:4}, \mu_1/\mu_{1:2}, \mu_3/\mu_{3:4})$, where 
$p_1$ controls lower-resolution changes in the mean vector $\mu$ and $p_2,p_3$ control higher resolution changes.

This idea extends naturally to $T=2^J$ for any $J$, reparameterizing $\bmu$ into its sum $\mu_{1:T}$
and a vector $\bp$ of $T-1$ binomial probabilities that capture features of $\bmu$ at different resolutions.
This can be thought of as an analogue of the wavelet transform of $\bmu$ for Poisson data.

Note that, in this reparameterization, $p_j=0.5 \, \forall j$ corresponds to the case of a constant mean vector,
and values of $p_j$ far from 0.5 correspond to large changes in $\mu$ (at some scale).
Thus estimating a spatially-structured $\bmu$ can be achieved by shrinkage estimation of $\bp$, with shrinkage towards $p_j=0.5$. Both \cite{Nowak2000Statistical} and \cite{Timmermann1999Multiscale} use purpose-built Bayesian models to
achieve this shrinkage, by introducing a prior distribution on elements of $\bp$ that is
a mixture of a point mass at 0.5 (creating shrinkage toward 0.5) 
and a Beta distribution. Here we take a different approach, reparameterizing $\alpha_j = \log(p_j/(1-p_j))$,
and then using adaptive shrinkage to shrink $\alpha_j$ towards 0.

To apply adaptive shrinkage we need an estimate $\hat{\alpha}_{j}$ and corresponding standard error $\hat{s}_j$
for each $j$. This boils down to estimating a log-odds ratio, and its standard error, which is a well-studied problem
(e.g. \cite{Gart1967Bias}). The main challenge is in dealing satisfactorily with cases where the mle for $\alpha_j$ is infinite. Our choice of estimates, based on results from \cite{Gart1967Bias}, are described in Appendix \ref{}.

The output of adaptive shrinkage is a posterior distribution on each $\alpha_j$. The simplest approach
to obtain estimates of $\bmu$  would be to estimate
$\alpha_j$ by its posterior mean, and then reverse the reparameterization. 
The resulting estimate of $\mu_t$ would be the exponential of the posterior
mean for $\log(\mu_t)$ (because each $\log_(\mu_t)$ is a linear combination of $\alpha_j$). [IS THIS TRUE?]
An alternative is to estimate the posterior mean using the Delta method; see Appendix \ref{app:reconstruction}.

%(For example, to go to $T=8$, we have $Y_{1:8} \sim Poi(\mu_{1:8})$, $Y_{1:4} | Y_{1:8} \sim \Bin(Y_{1:8}, \mu_{1:4}/\mu_{1:8})$, and then (\ref{eqn:y12})-(\ref{eqn:y3}) and their analogues replacing indices 1-4 with 5-8.)

%Note that, just as for the original parameterization $Y_j \sim \Poi(\mu_j)$, the likelihood for the parameters in this reparameterization factorizes into a product of four terms, one for each parameter, corresponding to the four distributions (\ref{eqn:y14})-(\ref{eqn:y3}).

\section{Results}

\subsection{Illustration}

Idea of adaptive shrinkage.

By estimating the uni-modal distribution from the data, ash uses the data to
determine how sparse $\tbmu$ should be,
and therefore how spatially structured $\bmu$ should be. Thus the degree of spatial smoothing is adaptive to the dataset: more smoothing for
datasets that appear consistent with a smooth signal.

\subsection{Simulations}
We now seek to validate the advantages of our method, named ``SMASH'', via simulation studies. To thoroughly investigate the performance of SMASH, we consider the Gaussian and Poisson cases separately.

For the Gaussian case, we focus our attention mostly on mean estimation. Different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions were considered, to ensure that SMASH behaves well in a variety of settings. However, only a small portion of the results will be shown here to highlight key findings from the rather extensive simulation study. Full results from the study can be found in the Supplementary Materials.

We first present a simple illustration of our method as a signal denoising technique. Figure \ref{fig:simple_eg} demonstrates that SMASH is able to better capture the true signal than TI-thresholding (with variance estimated by running median absolute deviation (RMAD); see \cite{Gao1997Wavelet}) on a simple simulated signal.

\begin{figure}
\centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_1.pdf}
        \caption{}
        \label{fig:simple_eg_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_2.pdf}
        \caption{}
        \label{fig:simple_eg_2}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_3.pdf}
        \caption{}
        \label{fig:simple_eg_3}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_4.pdf}
        \caption{}
        \label{fig:simple_eg_4}
    \end{subfigure}
				\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_5.pdf}
        \caption{}
        \label{fig:simple_eg_5}
    \end{subfigure}
    \caption{Simple illustration of the advantages of SMASH over TI-thresholding under heteroskedastic Gaussian errors. Top left plot shows the mean function, top right plot shows the variance function, bottom left plot shows a sample dataset, and bottom right plot shows the estimated mean functions from SMASH and TI-thresh against the true mean function.}
    \label{fig:simple_eg}
\end{figure}

To demonstrate the robustness of SMASH, we now consider only homoskedastic errors. Due to the large number of methods available in the literature for this setting, we chose only a subset. The methods we considered in our simulation are discussed in detail in \cite{Antoniadis2001Wavelet}, and in particular Translation Invariant (TI) thresholding by \cite{Coifman1995Translationinvariant} performed the best for most of the test signals, where performance is measured by mean squared error (MSE). We also considered the popular Empirical Bayes shrinkage procedure by \cite{Johnstone2005Empirical}, called Ebayesthresh. Figure \ref{fig:gaus_homo} compares the mean integrated squared errors (MISEs) of TI-thresholding and Ebayesthresh to SMASH with two different options for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024. The default option in SMASH estimates the mean without any homoskedastic assumptions on the variance function, while the second options estimates the mean given the true variance function. We can clearly see that the performance of SMASH is not impacted by the lack of homoskedastic assumptions imposed on the variance function: it outperforms two of the most accurate wavelet denoising algorithms for i.i.d. Gaussian noise even when the i.i.d. assumption holds, and performs nearly as well as when the variance function is known, which is the best-case scenario for any denoising technique. These results also extend to other mean functions, SNRs and sample sizes (see Supplementary Materials for more details).

\begin{figure}
\centering
    \includegraphics[width=\textwidth]{violin_gaus_homo.pdf}
    \caption{Violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for the ``Spikes'' mean function. Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH. a) demonstrates the performance gain of SMASH over two popular and accurate denoising methods: TI-thresholding and Ebayesthresh, and b) shows that SMASH with variance estimated can perform nearly as well as when it is given the true variance.}
    \label{fig:gaus_homo}
\end{figure}

Having shown that SMASH performs well in the homoskedastic case without any explicit assumptions on the Gaussian noise, we now demonstrate its performance gain when the errors are heteroskedastic. For the sake of presentation, figure \ref{fig:gaus_hetero} highlights only the results from SMASH, TI-thresh (with various choices of variance estimation) and EbayesThresh for just two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024. Nevertheless, similar results hold in general for different mean and variance functions, SNRs, and sample sizes (see Supplementary Materials for more details).

\begin{figure}
\centering
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_gaus_hetero_1.pdf}
        \caption{}
        \label{fig:gaus_hetero_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_gaus_hetero_sd_1.pdf}
        \caption{}
        \label{fig:gaus_hetero_sd_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_gaus_hetero_2.pdf}
        \caption{}
        \label{fig:gaus_hetero_2}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_gaus_hetero_sd_2.pdf}
        \caption{}
        \label{fig:gaus_hetero_sd_2}
    \end{subfigure}
    \caption{Violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function. Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH. a) and c) demonstrates the performance gain of SMASH over TI-thresh with different variance options: variance estimated by RMAD, variance estimated by SMASH, and the true variance. b) and d) plots the associated.}
    \label{fig:gaus_hetero}
\end{figure}

Several facts are immediately clear from figure \ref{fig:gaus_hetero}: 
\begin{enumerate}
\item SMASH does better than all TI-thresh variants, including the case when the true variance is provided, demonstrating the excellent finite sample performance of SMASH.
\item using the variance estimate from SMASH as an input to TI-thresh improves the accuracy of TI-thresh substantially, compared with using RMAD to estimate the variance as in \cite{Gao1997Wavelet}
\item accounting for heteroskedasticity allows SMASH to vastly outperform methods which assume homoskedastic errors.
\item empirical Bayes methods are more robust to violations of homoskedasticity compared with TI-thresholding.
\end{enumerate}

It should also be noted that providing the true variance to SMASH does not result in substantial gains compared to the case when SMASH estimates its own variance function for most of the test functions (results shown in the supplementary materials). Hence, we can reasonably assume that SMASH does a good job of variance estimation, although this claim relies heavily on the variance function at hand. For example, the Bumps variance function (see appendix ?) is extremely difficult to estimate, and SMASH will perform much better when provided with the true variance function.

Since our method also provides variance estimates, one could potentially perform similar assessments for different variance functions as with mean functions. In this particular study, we compare our method against the only joint mean and variance estimation procedure for which software is easily available. Specifically, we consider the Mean Field Variational Bayes (MFVB) methodology developed by \cite{Menictas2015Variational} for heteroskedastic Gaussian regression. Here we note that the MFVB approach is not well suited for dealing with standard test functions in the wavelet literature, as it is based on penalized splines (simulation studies were conducted to confirm this observation; results not shown). Hence, we chose the smooth mean and standard deviation functions (A) from \cite{Menictas2015Variational} as our test functions, plotted in Figure \ref{fig:mfvb_fn} and denoted by $m(\cdot)$ and $sd(\cdot)$ respectively. We then considered two different simulation scenarios:
\begin{enumerate}
\item $n=500$ independent $(X_i,Y_i)$ pairs were generated. The $X_i$'s were distributed as Uniform(0,1), and the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$. The performance of a given method is measured by the standard MSE evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation functions.
\item $n=1024$ independent $(X_i,Y_i)$ pairs were generated. The $X_i$'s were deterministic and equally spaced on (0,1), while the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$. The performance of a given method is measured by the MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation functions.
\end{enumerate}
\begin{figure}[ht]
\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{mfvb_mean.pdf}
        \caption{}
        \label{fig:mfvb_mean}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{mfvb_var.pdf}
        \caption{}
        \label{fig:mfvb_var}
    \end{subfigure}
    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.}
    \label{fig:mfvb_fn}
\end{figure}
In the first scenario, the number of data points is not a power of two, nor are the point equally spaced. To deal with these complications, we adapted and modified the standard symmetric extension procedure commonly used in wavelet settings. We first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points. This ensures that the number of data points in the new ``dataset'' is a power of two, and the mean curve would be continuous at the right edge. To further ensure that the input to the Gaussian denoising method is periodic, we then reflected the new dataset about the right edge and used this as the final input. To obtain the original mean and variance functions, we extracted the first $n$ points from the outputs (mean and variance) of our denoising technique. Since the data points are not evenly spaced, we took the simplest approach and applied our method treating the observations as if they were evenly spaced. This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (see eg. \cite{Sardy1999Wavelet}). Evaluation of MSE at the 201 equally spaced points is then based on simple linear interpolation between the estimated points. Tables \ref{table:mfvb_comp} display the MSEs over 100 independent runs for each scenario.
\begin{table}[ht]
\centering
\begin{tabular}{rrrrr}
\hline
& \multicolumn{2}{c}{Scenario 1}&\multicolumn{2}{c}{Scenario 2}\\
\cline{2-5}
& mean & sd & mean & sd \\
\hline
MFVB & 0.0330 & 0.0199 & 0.0172 & 0.0085 \\
SMASH & 0.0334 & 0.0187 & 0.0158 & 0.0065 \\
\hline
\end{tabular}
\caption{MSEs of MFVB and SMASH for two simulation scenarios}
\label{table:mfvb_comp}
\end{table}

Note that wavelets in general are poorly suited for dealing with the setup in Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced. Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of SMASH. At the same time, spline-based methods such as MFVB are well suited to dealing with smooth mean and variance functions such as those used in the simulations, whereas wavelet methods can better deal with spatial inhomogeneity which are present in functions such as those presented in Figure \ref{fig:gaus_homo}. Despite all these limitations, our method performs comparably to MFVB in terms of mean estimation for the simulation scheme presented in Scenario 1, and has a lower MSE in terms of variance estimation. For Scenario 2, our method outperforms MFVB in both mean and variance estimation.

Thus far, we have demonstrated that our method does a good job of mean and variance estimation for a variety of situations in the Gaussian case. As such, we now turn our attention to the Poisson case. For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale} and \cite{Fryzlewicz2004HaarFisz}, over 100 independent runs. Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}), which are two popular and accurate Poisson denoising techniques, for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8). The low intensities are of primary interest in genomic applications, and so we focus our attention to these. Complete results, including a (min,max) intensity of (1/128, 128), are included in appendix \textcolor{red}{where?}. From figure \ref{fig:pois_sim}, it is clear that SMASH outperforms both methods, and the claim holds true in general. As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asmyptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead. Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz in general. Here we analyzed primary resolution levels of 4, 5, 6 and 7. On the other hand, SMASH outperforms BMSM consistently, even though our method is based on the same likelihood factorization used in the latter. We can thus conclude that the choice of ASH as the shrinkage procedure (with the necessary likelihood approximations) is superior to that used in BMSM. More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
\begin{figure}
\centering
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
        \caption{}
        \label{fig:pois_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.45\textwidth}
        \centering
        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
        \caption{}
        \label{fig:pois_8}
    \end{subfigure}
    \caption{Violin plots of MISEs for various methods. a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8)}
    \label{fig:pois_sim}
\end{figure}

In terms of computation, we note that SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter method needs to be rerun for each shift of the data. However, a direct comparison between SMASH and BMSM is uninformative, as they are coded in different programming environments. Nevertheless, the similarities between the two methods imply that they should behave identically in this aspect, barring differences in actual implementation.

Overall, these simulation studies demonstrate the ability of our method to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptiveness of the shrinkage procedure ASH. Although we have considered an extensive range of scenarios here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has yet to be determined. In the next section, we will apply our method to two example datasets that have been discussed in previous work, and comment on the resulting estimates.

\section{Application to real datasets}
\subsection{Three-month Treasury Bill Yields}
In this section we apply the Gaussian and Poisson denoising techniques to one example dataset each. For the Gaussian case, we looked at yields of secondary market rates from three-month Treasure bills, which were recorded weekly on Fridays. These rates were quoted on a discount basis and annualized using a 360-day year of bank interest. To match the analysis in \cite{Fan1998Efficient}, we used 1735 weekly observations spanning Jan. 5 1962 to Mar. 31 1995. The data are plotted in Figure \ref{fig:tb_raw_data}. Similar to \cite{Fan1998Efficient}, we fit an autoregressive model of order 5 (AR(5)) to the data and obtained the following:
\begin{eqnarray}
T_t=1.228T_{t-1}-0.234T_{t-2}+0.028T_{t-3}+0.039T_{t-4}-0.066T_{t-5}+Y_t
\end{eqnarray}
where $T_t, t=1,...,1735$ is the time series for the yields, and $Y_t$ are the residuals from fitting the model. Figure \ref{fig:tb_res} shows the plot of $Y_t$ against $X_t\equiv T_{t-1}$. Our goal is to estimate the mean function defined by $E(Y_t|X_t=x)$ as well as the variance function $V(Y_t|X_t=x)$. Note that standard wavelet techniques are not designed for such types of data, where 1) repeated observations are present and 2) the number of data points is not a power of two and the points are unevenly spaced. To tackle the first issue, we use the median of the repeated observations at their respective sample points (see eg \cite{Delouille2004Smooth}). Next, we applied the procedure described in the Simulations section when comparing our method against MFVB, which was a modified version of symmetric extension. This deals with the second complication. The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.

\begin{figure}
\centering
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_a.pdf}
        \caption{}
        \label{fig:tb_raw_data}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_b.pdf}
        \caption{}
        \label{fig:tb_res}
    \end{subfigure}
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_c.pdf}
        \caption{}
        \label{fig:tb_mean}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.4\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures_treasury_d.pdf}
        \caption{}
        \label{fig:tb_var}
    \end{subfigure}
    \caption{Analysis of yields from three-month Treasury Bills. (a) Raw data of interest rates as a function of time. (b) Residuals $Y_t$ from fitting an AR(5) model to the data against $X_t\equiv T_{t-1}$. The red curve is the estimated mean curve from SMASH. (c) Plot of a zoomed-in version of the estimated mean curve, with approximate 95\% credible bands. (d) The estimated conditional variance curve, with approximate 95\% credible bands.}
\end{figure}

Except for possible boundary effects, our mean and conditional variance estimates are similar to those of \cite{Fan1998Efficient}. Unfortunately, these boundary effects are difficult to deal with for non-periodic functions in the wavelet case, and our usage of symmetric extension with the Haar basis is just one possible solution. Better alternatives have been suggested by eg. Su et al. (2013), but is beyond the scope of discussion in this paper. Similar to the analysis in \cite{Fan1998Efficient}, we found the correlation coefficient between the logarithm of $x_t$ and the logarithm $\hat{V}^{1/2}(Y_t|x_t)$ to be 0.949, which further supports the structural volatility model suggested by Andersen and Lund (source?):
\begin{eqnarray}
Var^{1/2}(Y_t|x_t)=\Ga x_t^{\Gb}
\end{eqnarray}
By performing least squares regression of $\log(\hat{V}^{1/2}(Y_t|x_t))$ on $\log(x_t)$, we have that $\hat{\Ga}=0.0106$ and $\hat{\Gb}=1.429$, which are similar to the values reported in \cite{Fan1998Efficient}.
\newpage
\subsection{ChIP-Seq Data}
Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly seen in the field of genomics. Specifically, we chose an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute. This dataset contains reads from chromatin immunoprecipitation sequencing (ChIP-seq) measuring transcription factor binding in two different cell types, with two samples for each cell type. Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1.
%Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
%\begin{figure}[h]
%\centering
%\includegraphics[scale=0.7]{smoothing_all.pdf}
%\caption{Estimated intensities from SMASH for 4 samples; the first two samples are two replicates from GM12878, a lymphoblastoid cell line, and the last two samples are two replicates from H1hesc, which are human embryonic stem cells. The reads are taken from position 880001 to 1011072 on chromosome 1.}
%\label{fig:seq_smooth}
%\end{figure}
%\bigskip
One goal of analyzing ChIP-seq data is to discover regions where transcription factors are likely to bind to DNA, thereby allowing us to better understand the mechanisms underlying gene regulation. These binding regions are often reflected in the data as ``peaks'', where more counts are present than background noise. Our method allows us to identify these peaks by looking at the estimated intensity function.
%In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
To ensure that our method performs sensibly, we pooled the reads for the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region. The results are shown in Figure \ref{fig:seq_peak}.\\
\newpage
\begin{figure}
\centering
    \begin{subfigure}[b]{0.85\textwidth}
        \centering
        \includegraphics[width=\textwidth]{peaks_comp_a.pdf}
        \caption{}
        \label{fig:seq_peak_data}
    \end{subfigure}
    \begin{subfigure}[b]{0.85\textwidth}
        \centering
        \includegraphics[width=\textwidth]{peaks_comp_b.pdf}
        \caption{}
        \label{fig:seq_peak_est}
    \end{subfigure}
    \caption{Analysis of reads taken from the GM12878 cell line, spanning positions 880001 to 1011072 on chromosome 1. (a) Raw sequencing counts. (b) Estimated intensity function from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).}
    \label{fig:seq_peak}
\end{figure}
From Figure \ref{fig:seq_peak_est} it is clear that SMASH can recognize the peaks detected by MACS. Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads. At the same time, SMASH also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\

\section{Discussion}
In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques. Both applications discussed in this paper relax the standard assumption of i.i.d. Gaussian noise, and are thus challenging tasks. Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, revealing its potential in many other applications.

In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as their approximate posterior variances as a measure of uncertainty. In addition, the variance function can also be estimated, which would provide frequentist confidence intervals for other forms of mean estimation. To the best of our knowledge, there is no readily available software in the wavelet literature that implements joint mean and variance estimation. Simulations have also confirmed that our method is relatively robust to simple forms of autocorrelation between the errors (details needed). In the case of Poisson regression, we improved upon the conjugate Beta priors in \cite{Kolaczyk1999Bayesian} by using ASH as a shrinkage procedure, which allows for more flexibility and precision. %In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution. 
In both the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used. On the other hand, the primary resolution level in almost all of the other wavelet-based methods actually affects their performance in varying degrees, depending on the underlying mean and/or variance function. Hence, our fully adaptive procedure allows users to easily apply it to any given dataset, depending on the type of noise.

We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature, in terms of pointwise accuracy (MSE in this case). Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussian priors imply that our methods are computationally fast, since the posteriors can be computed analytically. In the Gaussian case, simulation results demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d. errors (without explicitly assuming thus), whilst maintaining superior accuracy when heteroskedastic errors are present. Unfortunately, the lack of readily available software (except for MFVB, as described in \cite{Menictas2015Variational}) for variance estimation made it difficult to assess the performance of our method in that context. On the other hand, we were able to compare our method to some of the more popular denoising techniques in the Poisson case. Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods \cite{Kolaczyk1999Bayesian}) by using ASH as the shrinkage procedure, which allows for more flexibility and accuracy. This is particularly evident when the mean intensity is low, as is common in many high-throughput genomic sequencing datasets. Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm. Unfortunately, we were not able to directly compare the computational efficiency of our method to many other methods due to differences in the programming software involved.

Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios. In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see \cite{Morris2006Waveletbased}). Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which encapsulates a sample with temporally or spatially structured data points. While \cite{Morris2006Waveletbased} proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category. Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby relaxing their assumptions. In the simplest case, we could obtain spatially structured differences between groups by including a single covariate that categorizes each sample. In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where structured differences are present between say, various cell lines, as per our sequencing example in the previous section. The Gaussian model could potentially be used in...(??).

With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible. For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}. However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable. We could thus incorporate ASH into other types of transformations such as curvelets, which would be a potential direction for future work.
\newpage
\section{Reference}

\begin{appendices}
\section{}\label{app:var estimation}\bigskip
\textbf{Variance estimation for Gaussian denoising}

With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$. Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$. As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
\begin{eqnarray}
L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
\end{eqnarray}
However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions. As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
\begin{eqnarray}
P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
\end{eqnarray}
so that
\begin{eqnarray}\label{eq:gaus approx}
L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
\end{eqnarray}
where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients. Since these variances are unknown, we estimate them from the data and then proceed to treat them as known. More specifically, since $Z_t\sim N(0,\s_t^2)$, we have that
\begin{eqnarray}
&\mathbb{E}(Z_t^4)\approx 3\s_t^4\notag\\
\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z_t^2)\approx 2\s_t^4
\end{eqnarray}
and so we simply use $\frac{2}{3}Z_t^4$ as an unbiased estimator for $\mathbb{V}(Z_t^2)$. It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{l=1}^n \frac{2}{3}Z_l^4W_{jk,l}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$. These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters. Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels. This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points). One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.

\section{}\label{app:reconstruction}\bigskip
\textbf{Poisson denoising}

First summarize the data in a recursive manner: 
\begin{eqnarray}
Y_{Jk}\equiv Y_k\end{eqnarray}
for $k=1,...,n$, and
\begin{eqnarray}
Y_{jk}=Y_{j+1,2k}+Y_{j+1,2k+1}
\end{eqnarray}
for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$. Hence, we are summing more blocks of observations as we move to coarser levels.

This recursive scheme leads to:
\begin{eqnarray}
Y_{jk}=\sum_{l=k2^{J-j}+1}^{(k+1)2^{J-j}}Y_l
\end{eqnarray}
for $j=0,...,J$ and $k=0,...,2^j-1$.

Further define the following:
\begin{eqnarray}\Gl_{Jk}\equiv \Gl_k\end{eqnarray}
for $k=1,...,n$, and
\begin{eqnarray}\Gl_{jk}=\Gl_{j+1,2k}+\Gl_{j+1,2k+1}\end{eqnarray}
for $j=0,...,J-1$ and $k=0,...,2^j-1$. 
Furthermore, define
\begin{eqnarray}\label{eq:poisson wc}\Ga_{jk}=\log(\Gl_{j+1,2k})-\log(\Gl_{j+1,2k+1})\\\end{eqnarray}
for $s=0,...,J-1$ and $l=0,...,2^j-1$. The ${\Ga}$'s defined this way is extremely similar to the (true) Haar wavelet coefficients, which forms the basis of our approach. Using this recursive representation, we can see that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods, where $\bm{\Ga}$ is the vector of all the $\Ga_{sl}$'s. To be specific, we have
\begin{eqnarray}
L(\bm{\Ga}|\mathbf{Y})&=&P(\mathbf{Y}|\bm{\Ga})\\
&=&P(Y_{0,0}|\Gl_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}P(Y_{j+1,2k}|Y_{j,k},\Ga_{j,k})\\
&=&L(\Gl_{0,0}|Y_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}L(\Ga_{j,k}|Y_{j+1,2k},Y_{j,k})
\end{eqnarray}
where the factorization is due to the recursive definition above. Note that $Y_{00}|\Gl_{00}\sim \textrm{Pois}(\Gl_{00})$. For any given $j,k$, $Y_{jk}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable. Hence
\[Y_{j+1,2k}|Y_{jk},\Ga_{jk}\sim \textrm{Bin}({Y_{jk},\frac{1}{1+e^{-\Ga_{jk}}}\equiv\frac{\Gl_{j+1,2k}}{\Gl_{jk}}})\]

\subsection{Estimates and standard errors for $\alpha_j$}

Each $\alpha_{j}$ is a ratio of the form $\log(\mu_{a:b}/\mu_{c:d})$ whose maximum likelihood estimate (mle) is $\log(Y_{a:b}/Y_{c:d})$. The main challenge here is that the mle is not well behaved when either the numerator or denominator of $Y_{a:b}/Y_{c:d}$ is 0. To deal with this, when either is 0 we use Tukey's modification \cite{Gart1967Bias}. Specifically, letting $S$ denote $Y_{a:b}$ and $F$ denote $Y_{c:d}$ (corresponding to thinking of these as successes and failures in a binomial experiment, given $Y_{a:b}+Y_{c:d}$), we use
\begin{eqnarray}\label{eq:pseudoMLE1}
&&\hat{\Ga}=\left\{
\begin{array}{lll}
\log\{(S+0.5)/(F+0.5)\}-0.5&\ \ \ S=0\\
\log\{S/F\}&\ \ \ S=1,2,...,N-1\\
\log\{(S+0.5)/(F+0.5)\}+0.5&\ \ \ S=N\\
\end{array}
\right.\\ \label{eq:pseudoMLE1se}
&&se(\hat{\Ga})=\sqrt{V^*(\hat{\Ga})-\frac{1}{2}\{V_3(\hat{\Ga})\}^2\left\{V_3(\hat{\Ga})-\frac{4}{N}\right\}}
\end{eqnarray}
where
\begin{eqnarray}
&&V_3(\hat{\Ga})=\frac{N+1}{N}\left(\frac{1}{S+1}+\frac{1}{F+1}\right)\ \ \ S=0,...,N\\
\label{eq:pseudoMLE2}&&V^*(\hat{\Ga})=V_3(\hat{\Ga})\left\{1-\frac{2}{N}+\frac{V_3(\hat{\Ga})}{2}\right\}
\end{eqnarray}
The square of the standard error in \eqref{eq:pseudoMLE1se} corresponds to $V^{\ast\ast}$ from p. 182 of \cite{Gart1967Bias}, and is chosen because it is less biased for the true variance of $\hat{\Ga}$ (when $N$ is small) as compared to the asymptotic variance of the MLE (see \cite{Gart1967Bias}). The other two variance estimators from \cite{Gart1967Bias}, $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.

%One direct approximation of the likelihood for $\Ga$ is the Laplace approximation, which results in the Gaussian likelihood given by $\phi(\Ga;\hat{\Ga}_{MLE},\mathbb{V}(\hat{\Ga}_{MLE}))$. Here $\phi$ is the normal density function, and $\hat{\Ga}_{MLE}$ is the maximum likelihood estimator. We would then estimate $\mathbb{V}(\hat{\Ga}_{MLE})$ by the square of the asymptotic standard deviation for $\hat{\Ga}_{MLE}$. Specifically,
% for some appropriate estimator $\hat{\Ga}$. This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).

%We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$. The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by
%\begin{eqnarray}
%\hat{\Ga}_{MLE}=\log(S/F)&\ \ \ S=0,...,N\\
%se(\hat{\Ga}_{MLE})=\sqrt{SF/N}&\ \ \ S=0,...,N
%\end{eqnarray}
%where $S$ is the number of successes in the binomial setup, and $F=N-S$ is the number of failures (in our case the even locations would be successes and odd locations failures). The MLE has one notable drawback however, in that it cannot deal well with extreme cases. This would in turn affect the likelihood approximation in a non-negligible way. To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie. when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), we instead aim to find a suitable estimator $\hat{\Ga}$ for $\Ga$. Next, we approximate the distribution of $\hat{\Ga}$ by a Gaussian distribution, so that the likelihood for $\Ga$ is automatically Gaussian, given by $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$.

\subsection{Signal reconstruction}

Given the posterior means and variances of the $\Ga$'s from ASH, the first step to reconstructing the signal is to find the posterior means of $p_{jk}:=\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and $q_{jk}:=\frac{\Gl_{j+1,2k+1}}{\Gl_{jk}}$ (for $j=0,...,J-1$ and $k=0,...,2^j-1$). Specifically, for each $j$ and $k$, we wish to find
\begin{eqnarray}\label{eq:pfromwc1}
&&E(p_{jk})\equiv E\left(\frac{e^{\Ga_{jk}}}{1+e^{\Ga_{jk}}}\right)\\
\label{eq:pfromwc2}&&E(q_{jk})\equiv E\left(\frac{e^{-\Ga_{jk}}}{1+e^{-\Ga_{jk}}}\right)\end{eqnarray}
Given that we already have the posterior expectations and variances for $\Ga_{jk}$, we can approximate \eqref{eq:pfromwc1}-\eqref{eq:pfromwc2} using the Delta method. First, define
\begin{eqnarray}\label{eq:ff}ff(x)=\frac{e^x}{1+e^x}\end{eqnarray}
and consider the Taylor expansion of $ff(x)$ about $ff(E(x))$:
\begin{eqnarray}\label{eq:delta}ff(x)\approx ff(E(x))+ff'(E(x))(x-E(x))+\frac{ff''(E(x))}{2}(x-E(x))^2\end{eqnarray}
where
\begin{eqnarray}
\label{eq:fderiv}&&ff'(x)=\frac{e^x}{(1+e^x)^2}\\
\label{eq:sderiv}&&ff''(x)=\frac{e^x(1-e^{x})}{(1+e^x)^3}
\end{eqnarray}
It is easy to see that
\begin{eqnarray}
&&E(p_{jk})\approx ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\\
\label{eq:Ep}&&E(q_{jk})\approx ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})
\end{eqnarray}
noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.

Finally, we can easily back-transform to construct an estimated signal, by noting that we can express $\Gl_t$ as a product of the $p$'s and $q$'s for any $i=1,2,...,n$. Specifically, let $\{c_1,...,c_J\}$ be the binary representation of $i-1$, and $d_m=\sum_{j=1}^m c_j2^{m-j}$ for $j=1,...,J-1$. We then have
\begin{eqnarray}\label{eq:product}\Gl_k=\Gl_{00}p_{00}^{1-c_1}p_{1,d_1}^{1-c_2}...p_{J-1,d_{J-1}}^{1-c_J}q_{00}^{c_1}q_{1,d_1}^{c_2}...q_{J-1,d_{J-1}}^{c_J}\end{eqnarray}
where we usually estimate $\Gl_{00}$ by $\sum_l Y_l$ (see Kolaczyk (1999)). Using the independence of the $p$'s and $q$'s from different scales, we have:
\begin{eqnarray}\label{eq:Eproduct}E(\Gl_t)=\Gl_{00}E(p_{00})^{1-c_1}E(p_{1,d_1})^{1-c_2}...E(p_{J-1,d_{J-1}})^{1-c_J}\notag\\
E(q_{00})^{c_1}E(q_{1,d_1})^{c_2}...E(q_{J-1,d_{J-1}})^{c_J}\end{eqnarray}

As an additional step, we can also construct a credible band around the signal using the posterior variances for inference purposes. From \eqref{eq:product} we have the following:
\begin{eqnarray}\label{eq:E2product}E(\Gl_t^2)=\Gl_{00}^2E(p_{00}^2)^{1-c_1}E(p_{1,d_1}^2)^{1-c_2}...E(p_{J-1,d_{J-1}}^2)^{1-c_J}\notag\\
E(q_{00}^2)^{c_1}E(q_{1,d_1}^2)^{c_2}...E(q_{J-1,d_{J-1}}^2)^{c_J}\end{eqnarray}
To compute the terms in \eqref{eq:E2product}, we again make use of the Delta method (with $ff(x)=(\frac{e^x}{1+e^x})^2$) to obtain:
\begin{eqnarray}
&E(p_{jk}^2)\approx \left(ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(\Ga_{jk}))\}^2Var(\Ga_{jk})\\
&E(q_{jk}^2)\approx \left(ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
& \hspace{1.5 in}\{ff'(E(-\Ga_{jk}))\}^2Var(\Ga_{jk})
\end{eqnarray}
Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.

Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Multiscale}) rather than as described above. The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points. To be more specific, the TI table contains the $\Ga_{jk}$ for all circulant shifts of the signal. Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations. Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
\begin{eqnarray}
\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
\end{eqnarray}
which is an approximation to the true quantity we wish to compute, given by
\begin{eqnarray}
E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
\end{eqnarray}
\end{appendices}

\bibliography{smash}
\bibliographystyle{plain}

\end{document}

### 2015-11-20 paper/image.scale.R

@@ -1,0 +1,34 @@
+image.scale <- function(z, zlim, col = heat.colors(12),
+                        breaks, horiz=TRUE, ylim=NULL, xlim=NULL, ...){
+  if(!missing(breaks)){
+    if(length(breaks) != (length(col)+1)){stop("must have one more break than colour")}
+  }
+  if(missing(breaks) & !missing(zlim)){
+    breaks <- seq(zlim[1], zlim[2], length.out=(length(col)+1)) 
+  }
+  if(missing(breaks) & missing(zlim)){
+    zlim <- range(z, na.rm=TRUE)
+    zlim[2] <- zlim[2]+c(zlim[2]-zlim[1])*(1E-3)#adds a bit to the range in both directions
+    zlim[1] <- zlim[1]-c(zlim[2]-zlim[1])*(1E-3)
+    breaks <- seq(zlim[1], zlim[2], length.out=(length(col)+1))
+  }
+  poly <- vector(mode="list", length(col))
+  for(i in seq(poly)){
+    poly[[i]] <- c(breaks[i], breaks[i+1], breaks[i+1], breaks[i])
+  }
+  xaxt <- ifelse(horiz, "s", "n")
+  yaxt <- ifelse(horiz, "n", "s")
+  if(horiz){YLIM<-c(0,1); XLIM<-range(breaks)}
+  if(!horiz){YLIM<-range(breaks); XLIM<-c(0,1)}
+  if(missing(xlim)) xlim=XLIM
+  if(missing(ylim)) ylim=YLIM
+  plot(1,1,t="n",ylim=ylim, xlim=xlim, xaxt=xaxt, yaxt=yaxt, xaxs="i", yaxs="i", ...)  
+  for(i in seq(poly)){
+    if(horiz){
+      polygon(poly[[i]], c(0,0,1,1), col=col[i], border=NA)
+    }
+    if(!horiz){
+      polygon(c(0,0,1,1), poly[[i]], col=col[i], border=NA)
+    }
+  }
+}

### 2015-11-20 paper/plot_pois.R

@@ -23,16 +23,32 @@ mise.hf.ti.r.6.bur.8 = mise.sep(t(est.hf.ti.r.6.bur.8), mu.bur.8)
 mise.hf.ti.r.7.bur.8 = mise.sep(t(est.hf.ti.r.7.bur.8), mu.bur.8)
 mise.hf.ti.r.bur.8 = colMeans(matrix(c(mise.hf.ti.r.4.bur.8, mise.hf.ti.r.5.bur.8, mise.hf.ti.r.6.bur.8, mise.hf.ti.r.7.bur.8), byrow = TRUE, nr = 4))
 
-pdf("paper/violin_pois_1.pdf", height = 8, width = 12)
-par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 6.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
-vioplot.col(mise.ash.bur.1, mise.BMSM.bur.1, mise.hf.ti.r.bur.1, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
-title(xlab = "Method", ylab = "MISE", line = 4)
-abline(h = median(mise.ash.bur.1), lty = 3, col = 3)
+# #vertical
+# pdf("paper/violin_pois_1.pdf", height = 8, width = 12)
+# par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 6.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
+# vioplot.col(mise.ash.bur.1, mise.BMSM.bur.1, mise.hf.ti.r.bur.1, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+# title(xlab = "Method", ylab = "MISE", line = 4)
+# abline(h = median(mise.ash.bur.1), lty = 3, col = 3)
+# dev.off()
+# 
+# pdf("paper/violin_pois_8.pdf", height = 8, width = 12)
+# par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 6.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
+# vioplot.col(mise.ash.bur.8, mise.BMSM.bur.8, mise.hf.ti.r.bur.8, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+# title(xlab = "Method", ylab = "MISE", line = 4)
[…]

### 2015-11-20 paper/vioplot_col.R

@@ -235,7 +235,7 @@ vioplot.col <- function(x,...,range=1.5,h=NULL,ylim=NULL,names=NULL, horizontal=
     if(!add){
       plot.window(xlim = ylim, ylim = xlim)
       axis(1)
-      axis(2,at = at, label=label )
+      axis(2,at = at, label=label, las = 2)
     }
     
     box()
@@ -243,7 +243,7 @@ vioplot.col <- function(x,...,range=1.5,h=NULL,ylim=NULL,names=NULL, horizontal=
       # plot left/right density curve
       polygon( c(base[[i]], rev(base[[i]])),
                c(at[i]-height[[i]], rev(at[i]+height[[i]])),
-               col = col[i %% length(col) + 1], border=border, lty=lty, lwd=lwd)
+               col = col[i], border=border, lty=lty, lwd=lwd)
       
       if(drawRect){
         # plot IQR

### 2015-12-01 paper/draft_5.tex
minor changes to code

@@
 
-The {\it adaptive shrinkage} (\ash) method is described in detail in a companion paper, \cite{stephens:2015},
-which applies \ash~to estimate false discovery rates (FDR) in multiple testing settings. 
-Here we apply the same method to a different problem, signal denoising.  In brief,
-\ash~aims to provide EB shrinkage estimates of quantities $\beta_1,\dots,\beta_J$, given observed estimates of these quantities $\bhat_1,\dots,\bhat_J$, 
-and corresponding standard errors $\shat_1,\dots,\shat_J$.
-In common with most EB methods \ash~assumes that the $\beta_j$ come from some common underlying distribution, $g$, which is estimated from all the data (as $\hat{g}$ say), and
-uses the posterior mean,  $E(\beta_j | \bhat_j, \shat_j, \hat{g})$ as a shrinkage estimate of $\beta_j$.
-Key features that make \ash~attractive as a flexible and generic approach to shrinkage include: 
-i) its flexible semi-parametric modelling of $g$, under the constraint that it be uni-modal at 0 (and, optionally, symmetric); ii) its incorporation of the precision of each measurement through the standard errors $\shat_j$, so that the amount of shrinkage adapts to the precision of each measurement;  iii) its computational simplicity and speed: e.g.~our {\tt R} implementation typically takes a fraction of a second for $J=1000$;
-iv) its computational stability, with, for example, minimal problems due to convergence to local optima \cite{stephens:2015}.
+The {\it adaptive shrinkage} (\ash) method is described in detail in a companion paper, \cite{stephens:2015}, which applies \ash~to estimate false discovery rates (FDR) in multiple testing settings.
+Here we apply the same method to a different problem, signal denoising.
+In brief, \ash~aims to provide EB shrinkage estimates of quantities $\beta_1,\dots,\beta_J$, given observed estimates of these quantities $\bhat_1,\dots,\bhat_J$, and corresponding standard errors $\shat_1,\dots,\shat_J$.
+In common with most EB methods \ash~assumes that the $\beta_j$ come from some common underlying distribution, $g$, which is estimated from all the data (as $\hat{g}$ say), and uses the posterior mean,  $E(\beta_j | \bhat_j, \shat_j, \hat{g})$ as a shrinkage estimate of $\beta_j$.
+Key features that make \ash~attractive as a flexible and generic approach to shrinkage include: i) its flexible semi-parametric modelling of $g$, under the constraint that it be uni-modal at 0 (and, optionally, symmetric); ii) its incorporation of the precision of each measurement through the standard errors $\shat_j$, so that the amount of shrinkage adapts to the precision of each measurement;  iii) its computational simplicity and speed: e.g.~our {\tt R} implementation typically takes a fraction of a second for $J=1000$; iv) its computational stability, with, for example, minimal problems due to convergence to local optima \cite{stephens:2015}.
 
@@
 a mixture of zero-centered normal distributions
+
 \begin{equation}
@@
 of normals with a more flexible (though less smooth) mixture of uniforms. However, we do not use these embellishments here.
-CHECK: IS THIS TRUE. WHAT PARAMETERS DO WE USE?
-We also do not use the penalty term on the likelihood introduced in \cite{stephens:2015} for FDR applications,
-because it is unnecessary in this context, and has little effect on the shrinkage estimates.
 
@@
 
-A key feature of the wavelet tranform is that if $\bmu$ is spatially structured 
+A key feature of the wavelet transform is that if $\bmu$ is spatially structured 
 then many elements of $\tbmu=W\bmu$ will tend to be close to zero, and vice versa.
@@
 \begin{itemize}
-\item Rather than use a single wavelet transforrm, we use the ``non-decimated" wavelet transform, which treats the observations as coming
+\item Rather than use a single wavelet transform, we use the ``non-decimated" wavelet transform, which treats the observations as coming
 from a circle, rather than a line, and averages results over all $T$ possible rotations of the data.
 Although not always necessary, this is a standard trick to reduce artifacts that can occur near discontinuities in the underlying signal (see eg.
-\cite{Coifman1995Translationinvariant}).
-COMMENT: WHat about reflection before doing this?
-DO OTHER EB APPROACHES CONSIDER THE NDWT? ALSO, POINT FOR DISCUSSION: NDWT INCREASES DEPENDENCE, SO MAKE INDEPENDENCE ASSUMPTION WORSE, BUT MUCH BETTER TO DO IT THAN NOT TO DO IT!
+Coifman \& Donoho (1995)).
+%COMMENT: WHat about reflection before doing this? ans: all the test fns are periodic
+%DO OTHER EB APPROACHES CONSIDER THE NDWT? yes ebayesthresh software discusses this option
 \item The non-decimated wavelet transform yields $T$ wavelet coefficients (transformed values of $\bY$) 
@@
 \item Although we have presented the wavelet transform as a matrix multiplication, which is an $o(T^2)$ operation, in practice both the wavelet transform and the inverse tranform are implemented using
-Mallat's pyramid algorithm, taking only $T\log(T)$ operations. Do we need $o(T \log T)$ or $O()$? What about the TI table? Is there a different name for the algorithm for the reverse transform?
+efficient algorithms \cite{beylkin.92,coifman.donoho.94}, implemented in the {\tt wavethresh} package \cite{}, taking only $O(T\log T)$ operations. 
 \end{itemize}
@@
 Although we assumed variances to be known above, the problem of variance estimation is itself non-trivial. 
-A common approach is to assume that the variance is constant ($\sigma_t=\sigma$), and that changes in the adjacent means $\mu_t-\mu_{t+1}$ are negligible, so 
+A common approach is to assume that the variance is constant ($\sigma_t=\sigma$), and that changes in the adjacent means $\mu_t-\mu_{t+1}$ are negligible, and to use an unbiased estimate for $\sigma$ such as
 \begin{equation} \label{eq:constvar}
-\hat{\sigma} = (1/T) \sum_{t=1}^{T} (Y_t-Y_{t-1})^2
+\hat{\sigma}^2 = (1/2T) \sum_{t=1}^{T} (Y_t-Y_{t-1})^2
 \end{equation}
-(with $Y_0:=Y_T$) provides an unbiased estimate for $\sigma$. ...CHECK WITH TOM
+(with $Y_0:=Y_T$.
 Here we make the more flexible assumption that the variance function is spatially structured, and use wavelet shrinkage to estimate it.
+Our approach is similar in spirit to \cite{cai.wang}, but we jointly estimate the mean and variance functions whereas they estimate only the variance function.
 
@@
 of $Z_t^2$, $\mathbb{V}(Z_t^2)$, which is unknown.
-Here we use $\frac{2}{3}Z_t^4$ as an approximately (CHECK) 
-unbiased estimator for $\mathbb{V}(Z_t^2)$. (This follows from the distributional result that, when $Z^2 \sim \s^2 \chi^2$, then $\mathbb{E}(Z^4)\approx 3\s^4$, and $\mathbb{V}(Z^2)\approx 2\s^4$.)
+Here we use $\frac{2}{3}Z_t^4$ as an 
+unbiased estimator for $\mathbb{V}(Z_t^2)$. (This follows from the distributional result that, when $Z^2 \sim \s^2 \chi^2$, then $\mathbb{E}(Z^4)= 3\s^4$, and $\mathbb{V}(Z^2)=2\s^4$.)
 
 Despite the approximations being made here, we have found this procedure to work well in practice in most cases,
-perhaps with a tendancy to oversmooth quickly-varying variance functions. (IS THIS A FAIR SUMMARY? DO
-WE REALLY KNOW IT IS OVERSMOOTHING? IS IT POSSIBLE TO DO BETTER?)
+perhaps with a tendancy to oversmooth quickly-varying variance functions. 
 %Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels.
 This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
-
-This approach is similar in spirit to \cite{Cai2008Adaptive}, but they use first order differences instead of the squared residuals, removing the need to jointly estimate the mean and variance. 
-WHY DID WE DO THIS? DID IT PERFORM BETTER? How do they deal with the unknown variance?
-
-   One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH). LET'S TALK MORE ABOUT THAT...
 
@@
 %This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough.
-IS THIS as in (eg Cai \& Wang (2008)).? ALSO IS THIS CORRECT? I REMOVED A SUM OVER T THAT TOM HAD.
-ALSO, DID WE TRY USING \eqref{eq:constantvar})?
 Then we iterate:
@@
     \end{subfigure}
-    \caption{Simple illustration of the advantages of SMASH over TI-thresholding under heteroskedastic Gaussian errors.
-Top left plot shows the mean function, top right plot shows the variance function, bottom left plot shows a sample dataset, and bottom right plot shows the estimated mean functions from SMASH and TI-thresh against the true mean function.}
+    \caption{shows both ASH and SMASH at work.
+(a) shows the mean and variance functions, as well as one realized dataset.
+(b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse and one fine.
+(c) demonstrates the shrinkage properties of ASH for the two scales of interest: the coefficients at the fine scale are substantially shrunk, but barely so for the coarse scale.
+(d) shows the shrinkage effect of ASH on the fine scale wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision.
+(e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has notable artifacts.}
     \label{fig:simple_eg}
@@
 \centering
-    \includegraphics[width=\textwidth]{violin_gaus_homo.pdf}
-    \caption{Violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for the ``Spikes'' mean function.
+    \includegraphics[width=0.65\textwidth]{violin_gaus_homo.pdf}
+    \caption{Compares various wavelet-based methods for denoising data with homoskedastic Gaussian errors for the ``Spikes'' mean function.
+Violin plots of MISEs for (from bottom to top) SMASH, SMASH with homoskedastic assumption, TI-thresholding with homoskedastic assumption, Ebayesthresh with homoskedastic assumption, and SMASH with known true variance are shown in the figure.
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-a) demonstrates the performance gain of SMASH over two popular and accurate denoising methods: TI-thresholding and Ebayesthresh, and b) shows that SMASH with variance estimated can perform nearly as well as when it is given the true variance.}
+We note the performance gain of SMASH over both TI-thresholding and Ebayesthresh, and that SMASH with estimated variance can perform nearly as well as when it is given the true variance.}
     \label{fig:gaus_homo}
@@
 \centering
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{0.65\textwidth}
         \centering
@@
 		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_sd_1.pdf}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \raisebox{0.5\height}{\includegraphics[width=\textwidth]{violin_gaus_hetero_sd_1.pdf}}
         \caption{}
@@
 		\hfill
-    \begin{subfigure}[b]{0.5\textwidth}
+    \begin{subfigure}[b]{0.65\textwidth}
         \centering
@@
 		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_sd_2.pdf}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \raisebox{0.5\height}{\includegraphics[width=\textwidth]{violin_gaus_hetero_sd_2.pdf}}
         \caption{}
@@
     \end{subfigure}
-    \caption{Violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function.
+    \caption{Compares various wavelet-based methods for denoising data with heteroskedastic Gaussian errors.
+Figures on the left show violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function.
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-a) and c) demonstrates the performance gain of SMASH over TI-thresh with different variance options: variance estimated by RMAD, variance estimated by SMASH, and the true variance.
-b) and d) plots the associated.}
+Figures on the right plot the associated mean and variance functions.
+We note the performance gain of SMASH over TI-thresh with different variance options: variance estimated by RMAD, variance estimated by SMASH, and the true variance.}
     \label{fig:gaus_hetero}
@@
 \item accounting for heteroskedasticity allows SMASH to vastly outperform methods which assume homoskedastic errors.
-\item empirical Bayes methods are more robust to violations of homoskedasticity compared with TI-thresholding.
+\item SMASH is more robust to violations of homoskedasticity compared with both Ebayesthresh (shown) and TI-thresholding (not shown due to space limitations).
 \end{enumerate}

### 2015-12-01 package/smash/R/backup/ashsmooth_bk.R

@@ -1,0 +1,1060 @@
+#Disclaimer: Functions "interleave", "lsift", "rshift", "simplify", "setAshParam.gaus" and 'setAshParam.pois' in this file are adapted from the same functions defined in package "Multiseq" under the GPL license, authored by Ester Pantaleo, Heejung Shim,
+#Matthew Stephens and Zhengrong Xing.
+#All TI table (eg "titable", "ParentTItable") and reconstruction (eg "reverse.pwave", "reverse.gwave") functions and their respective Rcpp counterparts are adapted and modified from functions "ParentTItable" and "reverse.pwave" in package "Multiseq" 
+#under the GPL license, authored by Ester Pantaleo, Heejung Shim, Matthew Stephens and Zhengrong Xing, which are in turn ported into R from Matlab functions "BMSMShrink" and "TISumProd" as part of 
+#the BMSM project maintained by Eric Kolaczyk
+#The "wd" ("wd.D") and "threshold" ("threshold.haar", "threshold.var") class of functions are adapted and modified from "wd" and "threshold.wd" respectively in package "wavethresh" under th GPL license, authored buy Guy Nason.
+
+
+#' Interleave two vectors
+#' @param x,y: two vectors of the same length
+#' @return a vector of length twice that of x (or y)
+interleave=function(x,y){
+  return(as.vector(rbind(x,y)))
+}
+
+
+#' Shift a vector one unit to the right
+#' @param x: a vector
+#' @return a vector of the same length as that of x 
+rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
+lshift = function(x){return(c(x[-1],x[1]))}
+
+
+#' Produces two TI tables. One table contains the difference between adjacent pairs of data in the same resolution, and the other table contains the sum.
+#' @param sig: a signal of length a power of 2
+#' @return a list of two TI tables in the form of matrices
+titable=function(sig){
+  n = length(sig)
+  J = log2(n)
+
+  dmat = matrix(0, nrow=J+1, ncol=n)
+  ddmat = matrix(0, nrow=J+1, ncol=n)
+  dmat[1,] = sig
+  ddmat[1,] = sig
+  
+  #dmat[1,] = as.matrix(sig)  
+  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
+  
+  for(D in 0:(J-1)){
+    nD = 2^(J-D); 
+    nDo2 = nD/2;
+    twonD = 2*nD;
+    for(l in 0:(2^D-1)){
[…]

### 2015-12-01 package/smash/R/backup/deltamethod.R

@@ -1,0 +1,124 @@
+#Disclaimer: The functions defined in this file are adapted from the same functions defined in package "Multiseq" under the GPL license, authored by Ester Pantaleo, Heejung Shim,
+#Matthew Stephens and Zhengrong Xing
+ 
+ff_exp = function(x){
+  return(exp(-log(1+exp(-x))))
+}
+
+ffdash = function(x){
+  return(1/(1+exp(x)))
+}
+
+ffdd = function(x){
+  ex=exp(x)
+  return(-ex/(1+ex)^2)
+}
+
+ffdashdd = function(x){
+  ex=exp(x)
+  return(-ex/(1+ex)^3)
+}
+
+#first and second  derivatives of ff
+ff.deriv_exp = function(x){
+  ex = exp(x)
+  return(list(first = ex/(1+2*ex+ex^2), second= (ex-ex^3)/(1+4*ex+6*ex^2+4*ex^3+ex^4)))
+}
+
+#first and second  derivatives of ffdash
+ffdash.deriv = function(x){
+  ex=exp(x)
+  return(list(first= -ex/(1+ex)^2, second= ex*(ex-1)*(1+ex)^(-3)))
+}
+
+ffdd.deriv = function(x){
+  ex=exp(x)
+  return(list(first= ex*(ex-1)*(1+ex)^(-3), second= ex*(4*ex-ex^2-1)*(1+ex)^(-4)))
+}
+
+ffdashdd.deriv = function(x){
+  ex=exp(x)
+  return(list(first=ex*(2*ex-1)*(1+ex)^(-4), second=ex*(7*ex-4*ex^2-1)*(1+ex)^(-5)))
+}
+
+#return estimated E(ff(X)) and var(ff(X)) by delta method
+#INPUT: mx =E(X) and vx = Var(X)
+ff.moments_exp = function(mx,vx){
+  d = ff.deriv_exp(mx)
+  return(list(mean=ff_exp(mx)+d$second*vx/2, var=(d$first^2*vx), meansq=ff_exp(mx)^2+(d$second*vx/2)^2+(d$first^2+ff_exp(mx)*d$second)*vx))
+}
+
+#return estimated E(ff'(X)) and var(ff'(X)) by delta method
+#INPUT: mx =E(X) and vx = Var(X)
+ffdash.moments = function(mx,vx){
+  d = ffdash.deriv(mx)
[…]

### 2015-12-01 package/smash/R/backup/glm_approx.R

@@ -1,0 +1,525 @@
+##Disclaimer: The functions defined in this file are adapted from the nearly identical functions defined in package "Multiseq" under the GPL license, authored by Ester Pantaleo, Heejung Shim,
+#Matthew Stephens and Zhengrong Xing
+
+
+#' Compute approximately unbiased variance estimates for the estimators for logit(p) when n is small
+#' @param n: number of trials
+#' @param s: number of successes
+#' @param f: number of failures
+v3=function(n,s,f){
+    return((n+1)/n*(1/(s+1)+1/(f+1)))
+}
+
+#' Compute approximately unbiased variance estimates for the estimators for logit(p) when n is small
+#' @param n: number of trials
+#' @param s: number of successes
+#' @param f: number of failures
+vs=function(n,s,f){
+    vv=v3(n,s,f)
+    return(vv*(1-2/n+vv/2))
+}
+
+#' Compute approximately unbiased variance estimates for the estimators for logit(p) when n is small
+#' @param n: number of trials
+#' @param s: number of successes
+#' @param f: number of failures
+vss=function(n,s,f){
+    vv=v3(n,s,f)
+    return(vs(n,s,f)-1/2*vv^2*(vv-4/n))
+}
+
+
+#' Modified glm function to return relevant outputs, not allowing for underdispersion
+#' @param x: covariante
+#' @param y: response
+#' @param forcebin: see glm.approx
+#' @param repara: see glm.approx
+#' @param ...: other inputs to glm.fit
+#' @return a vector of intercept and slope estimates and their SEs
+safe.quasibinomial.glm.fit=function(x,y,forcebin=FALSE,repara=FALSE,...){
+    if(forcebin){
+        z=glm.fit(x,y,family=binomial(),...)
+        p1=1L:z$rank
+        covmat=chol2inv(z$qr[[1]][p1, p1, drop = FALSE])
+        se=sqrt(diag(covmat))
+        if(repara==TRUE){
+            if(length(covmat)<=1){
+                covmubeta=NA
+            }else{
+                covmubeta=covmat[2,1]
+            }
+            mbvar=covmubeta/se[2]^2
+            z$coef[1]=z$coef[1]-z$coef[2]*mbvar
+            se[1]=sqrt(se[1]^2+mbvar^2*se[2]^2-2*mbvar*covmubeta)
+        }
+    }else{
[…]

### 2015-12-01 package/smash/R/deltamethod.R

@@ -1,124 +1,124 @@
-#Disclaimer: The functions defined in this file are adapted from the same functions defined in package "Multiseq" under the GPL license, authored by Ester Pantaleo, Heejung Shim,
-#Matthew Stephens and Zhengrong Xing
- 
-ff_exp = function(x){
-  return(exp(-log(1+exp(-x))))
+# Disclaimer: The functions defined in this file are adapted from the same functions defined in package 'Multiseq'
+# under the GPL license, authored by Ester Pantaleo, Heejung Shim, Matthew Stephens and Zhengrong Xing
+
+ff_exp = function(x) {
+    return(exp(-log(1 + exp(-x))))
 }
 
-ffdash = function(x){
-  return(1/(1+exp(x)))
+ffdash = function(x) {
+    return(1/(1 + exp(x)))
 }
 
-ffdd = function(x){
-  ex=exp(x)
-  return(-ex/(1+ex)^2)
+ffdd = function(x) {
+    ex = exp(x)
+    return(-ex/(1 + ex)^2)
 }
 
-ffdashdd = function(x){
-  ex=exp(x)
-  return(-ex/(1+ex)^3)
+ffdashdd = function(x) {
+    ex = exp(x)
+    return(-ex/(1 + ex)^3)
 }
 
-#first and second  derivatives of ff
-ff.deriv_exp = function(x){
-  ex = exp(x)
-  return(list(first = ex/(1+2*ex+ex^2), second= (ex-ex^3)/(1+4*ex+6*ex^2+4*ex^3+ex^4)))
+# first and second derivatives of ff
+ff.deriv_exp = function(x) {
+    ex = exp(x)
+    return(list(first = ex/(1 + 2 * ex + ex^2), second = (ex - ex^3)/(1 + 4 * ex + 6 * ex^2 + 4 * ex^3 + ex^4)))
 }
 
-#first and second  derivatives of ffdash
-ffdash.deriv = function(x){
-  ex=exp(x)
-  return(list(first= -ex/(1+ex)^2, second= ex*(ex-1)*(1+ex)^(-3)))
+# first and second derivatives of ffdash
+ffdash.deriv = function(x) {
+    ex = exp(x)
[…]

### 2015-12-01 paper/image.scale.R

@@ -1,3 +1,5 @@
+#Disclaimer: This function is courtesy of Pretty R at inside-R.org
+
 image.scale <- function(z, zlim, col = heat.colors(12),
                         breaks, horiz=TRUE, ylim=NULL, xlim=NULL, ...){
   if(!missing(breaks)){

### 2015-12-01 paper/vioplot_col.R

@@ -1,106 +1,5 @@
-# vioplot.col = function(x, ..., range = 1.5, h = NULL, ylim = NULL, names = NULL, 
-#                        horizontal = FALSE, col = "magenta", border = "black", lty = 1, 
-#                        lwd = 1, rectCol = "black", colMed = "white", pchMed = 19, 
-#                        at, add = FALSE, wex = 1, drawRect = TRUE) 
-# {
-#   datas <- list(x, ...)
-#   n <- length(datas)
-#   if (missing(at)) 
-#     at <- 1:n
-#   if(length(col)==1) col <- rep(col,n)
-#   upper <- vector(mode = "numeric", length = n)
-#   lower <- vector(mode = "numeric", length = n)
-#   q1 <- vector(mode = "numeric", length = n)
-#   q3 <- vector(mode = "numeric", length = n)
-#   med <- vector(mode = "numeric", length = n)
-#   base <- vector(mode = "list", length = n)
-#   height <- vector(mode = "list", length = n)
-#   baserange <- c(Inf, -Inf)
-#   args <- list(display = "none")
-#   if (!(is.null(h))) 
-#     args <- c(args, h = h)
-#   for (i in 1:n) {
-#     data <- datas[[i]]
-#     data.min <- min(data)
-#     data.max <- max(data)
-#     q1[i] <- quantile(data, 0.25)
-#     q3[i] <- quantile(data, 0.75)
-#     med[i] <- median(data)
-#     iqd <- q3[i] - q1[i]
-#     upper[i] <- min(q3[i] + range * iqd, data.max)
-#     lower[i] <- max(q1[i] - range * iqd, data.min)
-#     est.xlim <- c(min(lower[i], data.min), max(upper[i], 
-#                                                data.max))
-#     smout <- do.call("sm.density", c(list(data, xlim = est.xlim), 
-#                                      args))
-#     hscale <- 0.4/max(smout$estimate) * wex
-#     base[[i]] <- smout$eval.points
-#     height[[i]] <- smout$estimate * hscale
-#     t <- range(base[[i]])
-#     baserange[1] <- min(baserange[1], t[1])
-#     baserange[2] <- max(baserange[2], t[2])
-#   }
-#   if (!add) {
-#     xlim <- if (n == 1) 
-#       at + c(-0.5, 0.5)
-#     else range(at) + min(diff(at))/2 * c(-1, 1)
-#     if (is.null(ylim)) {
-#       ylim <- baserange
-#     }
-#   }
[…]

### 2016-01-08 ashprof/smash_ash_profile.Rmd
added ash profiling

---
title: "ASH profiling in SMASH"
output: html_document
---

Tests the three optimization methods in ASH: "mixEM", "cxxMixSquarem" and "mixIP"

```{r}
library(SMASH)

load("data.Robj")

wd = smash:::titable(X.s)$difftable
wv = smash:::titable(sigma.t^2)$sumtable

scale = 10

time.em = matrix(0, nr = 100, nc = 2)
time.squarem = matrix(0, nr = 100, nc = 2)
time.ip = matrix(0, nr = 100, nc = 2)
for(i in 1:100){
  time.em[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "mixEM", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
  time.squarem[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "cxxMixSquarem", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
  time.ip[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "mixIP", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
}

summary(time.em)
summary(time.squarem)
summary(time.ip)

scale = 2

time.em = matrix(0, nr = 100, nc = 2)
time.squarem = matrix(0, nr = 100, nc = 2)
time.ip = matrix(0, nr = 100, nc = 2)
for(i in 1:100){
  time.em[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "mixEM", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
  time.squarem[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "cxxMixSquarem", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
  time.ip[i, ] = system.time(ash(wd[scale, ], sqrt(wv[scale, ]), prior = "nullbiased", optmethod = "mixIP", pointmass = TRUE, nullcheck = TRUE, mixsd = NULL, mixcompdist = "normal", gridmult = 2, df = NULL))[1:2]
}

summary(time.em)
summary(time.squarem)
summary(time.ip)

```

### 2016-01-08 paper/draft_5.tex
added ash profiling

@@
 
-The first problem relates to mean and variance estimation with Gaussian noise.
-Although the framework for homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], methods dealing with heteroskedastic errors are uncommon.
-Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators.
-Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous variance estimation methods using a wavelet thresholding approach on first order differences.
-Here we present an approach that estimates both the mean and variance accurately by incorporating ASH into a novel wavelet denoising framework.
-[mention the lack of available software?]
+Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, 
+are uncommon, particularly compared with the well-studied homoskedastic case. 
+Previous non-wavelet-based work includes Fan \& Yao (1998), who estimated the variance by smoothing the squared residuals using local polynomial smoothing, and Brown \& Levine (2007) who employed difference-based kernel estimators.
+The only wavelet-based method we have found is Cai \& Wang (2008), which applied
+a wavelet thresholding approach to first order differences. Unfortunately none of these methods have available software implementations.
+mention Wand work.
 
@@
 (d) shows the shrinkage effect of ASH on the fine scale wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision.
-(e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has notable artifacts.}
+(e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has noticeable artifacts.}
     \label{fig:simple_eg}

### 2016-01-08 package/smash/R/backup/jash.R

@@ -1,0 +1,561 @@
+#Disclaimer: The functions defined in this file are adapted from the same functions used in the project "JASH", supervised by Mengyin Lu and Matthew Stephens 
+
+# Y: N by n observation matrix (N tests, n replicate obs for each test)
+# Model: Y_{jk}|beta_j,tau_j ~ N(beta_j,1/tau_j)
+# Prior: beta_j|tau_j~N(mu_j,1/(c_l*tau_j)), tau_j~lambda_k*Gamma(a_m,a_m), w.p. pi_{klm}
+# Mixture constraint: sum(pi_{klm})=1
+# Or: sum(pi_k)=1, sum(pi_l)=1, sum(pi_m)=1 for each param
+# a_m, lambda_k, c_l, mu_j are known
+######################################################
+library(qvalue)
+qval.from.localfdr = function(localfdr){
+  o = order(localfdr)
+  qvalue=rep(NA,length(localfdr))
+  qvalue[o] = (cumsum(sort(localfdr))/(1:sum(!is.na(localfdr))))
+  return(qvalue)
+}
+
+
+# post_pi computes the posterior probability 
+# P(beta_j,tau_j belongs to the i'th component | Y)
+post_pi = function(N,n,M,K,L,a.vec,b.vec,d.vec,mu,MEAN,SSE,pi){
+  post.gammab=0.5*(outer(SSE,rep(1,M*L*K))+outer((MEAN-mu)^2,n*d.vec)+outer(rep(1,N),2*b.vec))
+  post.pi.mat = exp(outer(rep(1,N),log(pi)+a.vec*log(b.vec)-lgamma(a.vec)+0.5*log(d.vec)+lgamma(a.vec+n/2))-
+                      log(post.gammab)*
+                      outer(rep(1,N),a.vec+n/2))
+  return(list(gammab=post.gammab,pimat=post.pi.mat))
+  
+#   post.pi.mat = exp(outer(rep(1,N),log(pi)+a.vec*log(b.vec)-lgamma(a.vec)+log(sqrt(d.vec)+lgamma(a.vec+n/2))-
+#     log(0.5*(outer(SSE,rep(1,M*L*K))+outer((MEAN-mu)^2,n*d.vec)+outer(rep(1,N),2*b.vec)))*
[…]

### 2016-01-08 package/smash/R/jash.R

@@ -1,561 +1,558 @@
-#Disclaimer: The functions defined in this file are adapted from the same functions used in the project "JASH", supervised by Mengyin Lu and Matthew Stephens 
+# Disclaimer: The functions defined in this file are adapted from the same functions used in the project 'JASH',
+# supervised by Mengyin Lu and Matthew Stephens
 
-# Y: N by n observation matrix (N tests, n replicate obs for each test)
-# Model: Y_{jk}|beta_j,tau_j ~ N(beta_j,1/tau_j)
-# Prior: beta_j|tau_j~N(mu_j,1/(c_l*tau_j)), tau_j~lambda_k*Gamma(a_m,a_m), w.p. pi_{klm}
-# Mixture constraint: sum(pi_{klm})=1
-# Or: sum(pi_k)=1, sum(pi_l)=1, sum(pi_m)=1 for each param
-# a_m, lambda_k, c_l, mu_j are known
-######################################################
+# Y: N by n observation matrix (N tests, n replicate obs for each test) Model: Y_{jk}|beta_j,tau_j ~
+# N(beta_j,1/tau_j) Prior: beta_j|tau_j~N(mu_j,1/(c_l*tau_j)), tau_j~lambda_k*Gamma(a_m,a_m), w.p. pi_{klm} Mixture
+# constraint: sum(pi_{klm})=1 Or: sum(pi_k)=1, sum(pi_l)=1, sum(pi_m)=1 for each param a_m, lambda_k, c_l, mu_j are
+# known
 library(qvalue)
-qval.from.localfdr = function(localfdr){
-  o = order(localfdr)
-  qvalue=rep(NA,length(localfdr))
-  qvalue[o] = (cumsum(sort(localfdr))/(1:sum(!is.na(localfdr))))
-  return(qvalue)
+qval.from.localfdr = function(localfdr) {
+    o = order(localfdr)
+    qvalue = rep(NA, length(localfdr))
+    qvalue[o] = (cumsum(sort(localfdr))/(1:sum(!is.na(localfdr))))
+    return(qvalue)
 }
 
 
-# post_pi computes the posterior probability 
[…]

### 2016-01-08 package/smash/R/wd_var.R

@@ -112,7 +112,7 @@ wd.var <- function (data, filter.number = 10, family = "DaubLeAsymm", type = "wa
 
 
 
-convert.var=function (wd, ...) 
+convert.var <- function (wd, ...) 
 {
     if (wd$type != "station") 
         stop("Object to convert must be of type \"station\" ")
@@ -143,7 +143,7 @@ convert.var=function (wd, ...)
 
 
 
-AvBasis.var=function (wst, Ccode = TRUE, ...) 
+AvBasis.var <- function (wst, Ccode = TRUE, ...) 
 {
     nlevels <- nlevelsWT(wst)
     if (is.null(wst$filter$G)) {

### 2016-01-09 paper/draft_5.tex
added motorcycle data

@@
 These are all settings that are relatively underserved by existing EB implementations, and indeed  we are unaware of any existing EB implementation for smoothing either the mean or the variance in the heteroskedastic Gaussian case.
-Consistent with previous studies (\cite{Antoniadis2001Wavelet}) we find these EB methods to be more accurate than commonly-used thresholding rules, and, in the Poisson case, competitive with a purpose-built EB method.
+Consistent with previous studies (\cite{Antoniadis2001Wavelet}, \cite{Besbeas2004Comparative}) we find these EB methods to be more accurate than commonly-used thresholding rules, and, in the Poisson case, competitive with a purpose-built EB method.
+
+Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, are uncommon, particularly compared with the well-studied homoskedastic case.
+Previous non-wavelet-based work includes \cite{Fan1998Efficient}, who estimated the variance by smoothing the squared residuals using local polynomial smoothing, and \cite{Brown2007Variance} who employed difference-based kernel estimators.
+The only wavelet-based method for variance estimation we have found is \cite{Cai2008Adaptive}, which applied a wavelet thresholding approach to first order differences.
+Unfortunately none of these methods have available software implementations.
+(WAND'S WORK?)
+
+For Poisson data, variance stabilizing techniques together with normal approximations have been proposed by \cite{D93} and \cite{Fryzlewicz2004HaarFisz}, by exploiting the mean-variance relationship of a Poisson distribution.
+\cite{Kolaczyk1996NonParametric} and \cite{kolaczyk1999wavelet} derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d.
+Gaussian case.
+However, \cite{Fryzlewicz2004HaarFisz} is computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance.
+Furthermore, all of these methods are sensitive to the choice of the primary resolution level as subsequent simulations will show.
+Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by \cite{Kolaczyk1999Bayesian} to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen.
 
@@
 The {\it adaptive shrinkage} (\ash) method is described in detail in a companion paper, \cite{stephens:2015}, which applies \ash~to estimate false discovery rates (FDR) in multiple testing settings.
-Here we apply the same method to a different problem, signal denoising.
+Here we apply the same method to the signal denoising problems described above.
 In brief, \ash~aims to provide EB shrinkage estimates of quantities $\beta_1,\dots,\beta_J$, given observed estimates of these quantities $\bhat_1,\dots,\bhat_J$, and corresponding standard errors $\shat_1,\dots,\shat_J$.
@@
 These approximations also allow us to use ASH as the common shrinkage procedure in both the problems.
-
-Move some of this material to the relevant place? or discussion?
-
-Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, 
-are uncommon, particularly compared with the well-studied homoskedastic case. 
-Previous non-wavelet-based work includes Fan \& Yao (1998), who estimated the variance by smoothing the squared residuals using local polynomial smoothing, and Brown \& Levine (2007) who employed difference-based kernel estimators.
-The only wavelet-based method we have found is Cai \& Wang (2008), which applied
-a wavelet thresholding approach to first order differences. Unfortunately none of these methods have available software implementations.
-mention Wand work.
-
-The second task is to denoise a Poisson distributed signal.
-This often occurs in the experimental sciences such as gamma-ray burst signals in astronomy [references], and more recently in genetics where high throughput sequencing data is of interest.
-This problem is interesting because there are many distinct ways to perform signal recovery.
-Variance stabilizing techniques together with normal approximations have been proposed by Donoho (1993) and Fryzlewicz \& Nason (2001), by exploiting the mean-variance relationship of a Poisson distribution.
-Kolaczyk (1997, 1999a) derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d.
-Gaussian case.
-However, variance stabilizing methods are computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance.
-Furthermore, both these methods are quite sensitive to the choice of the primary resolution level as our simulations will show.
-Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by Kolaczyk (1999b) to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen.
-We will improve upon the prior (and likelihood) specification by using ASH as the main shrinkage procedure in a Bayesian framework similar to that of Kolaczyk (1999b).
 
@@
 (a) shows the mean and variance functions, as well as one realized dataset.
-(b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse and one fine.
-(c) demonstrates the shrinkage properties of ASH for the two scales of interest: the coefficients at the fine scale are substantially shrunk, but barely so for the coarse scale.
-(d) shows the shrinkage effect of ASH on the fine scale wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision.
+(b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse (scale 1) and one fine (scale 7).
+(c) demonstrates the shrinkage properties of ASH for the two scales of interest (scales 1 and 7): the coefficients at the fine scale (scale 7) are substantially shrunk, but barely so for the coarse scale.
+(d) shows the shrinkage effect of ASH on the fine scale (scale 7) wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision.
 (e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has noticeable artifacts.}
@@
 As such, we now turn our attention to the Poisson case.
-For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale} and \cite{Fryzlewicz2004HaarFisz}, over 100 independent runs.
+For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}, over 100 independent runs.
 Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}), which are two popular and accurate Poisson denoising techniques, for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8).
@@
 Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz in general.
-Here we analyzed primary resolution levels of 4, 5, 6 and 7.
+Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}.
 On the other hand, SMASH outperforms BMSM consistently, even though our method is based on the same likelihood factorization used in the latter.
@@
 \section{Application to real datasets}
-\subsection{Three-month Treasury Bill Yields}
-In this section we apply the Gaussian and Poisson denoising techniques to one example dataset each.
+%\subsection{Three-month Treasury Bill Yields}
+%In this section we apply the Gaussian and Poisson denoising techniques to one example dataset each.
 For the Gaussian case, we looked at yields of secondary market rates from three-month Treasure bills, which were recorded weekly on Fridays.
@@
 Similar to \cite{Fan1998Efficient}, we fit an autoregressive model of order 5 (AR(5)) to the data and obtained the following:
-\begin{eqnarray}
-T_t=1.228T_{t-1}-0.234T_{t-2}+0.028T_{t-3}+0.039T_{t-4}-0.066T_{t-5}+Y_t
-\end{eqnarray}
-where $T_t, t=1,...,1735$ is the time series for the yields, and $Y_t$ are the residuals from fitting the model.
+%\begin{eqnarray}
+%T_t=1.228T_{t-1}-0.234T_{t-2}+0.028T_{t-3}+0.039T_{t-4}-0.066T_{t-5}+Y_t
+%\end{eqnarray}
+%where $T_t, t=1,...,1735$ is the time series for the yields, and $Y_t$ are the residuals from fitting the model.
 Figure \ref{fig:tb_res} shows the plot of $Y_t$ against $X_t\equiv T_{t-1}$.
@@
 The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.
-
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_a.pdf}
-        \caption{}
-        \label{fig:tb_raw_data}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_b.pdf}
-        \caption{}
-        \label{fig:tb_res}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_c.pdf}
-        \caption{}
-        \label{fig:tb_mean}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.4\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{figures_treasury_d.pdf}
-        \caption{}
-        \label{fig:tb_var}
-    \end{subfigure}
-    \caption{Analysis of yields from three-month Treasury Bills.
+%
+%\begin{figure}
+%\centering
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_a.pdf}
+        %\caption{}
+        %\label{fig:tb_raw_data}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_b.pdf}
+        %\caption{}
+        %\label{fig:tb_res}
+    %\end{subfigure}
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_c.pdf}
+        %\caption{}
+        %\label{fig:tb_mean}
+    %\end{subfigure}
+    %\hfill
+    %\begin{subfigure}[b]{0.4\textwidth}
+        %\centering
+        %\includegraphics[width=\textwidth]{figures_treasury_d.pdf}
+        %\caption{}
+        %\label{fig:tb_var}
+    %\end{subfigure}
+    %\caption{Analysis of yields from three-month Treasury Bills.
 (a) Raw data of interest rates as a function of time.
@@
 (d) The estimated conditional variance curve, with approximate 95\% credible bands.}
-\end{figure}
-
-Except for possible boundary effects, our mean and conditional variance estimates are similar to those of \cite{Fan1998Efficient}.
+%\end{figure}
+%
+%Except for possible boundary effects, our mean and conditional variance estimates are similar to those of \cite{Fan1998Efficient}.
 Unfortunately, these boundary effects are difficult to deal with for non-periodic functions in the wavelet case, and our usage of symmetric extension with the Haar basis is just one possible solution.
@@
 Similar to the analysis in \cite{Fan1998Efficient}, we found the correlation coefficient between the logarithm of $x_t$ and the logarithm $\hat{V}^{1/2}(Y_t|x_t)$ to be 0.949, which further supports the structural volatility model suggested by Andersen and Lund (source?):
-\begin{eqnarray}
-Var^{1/2}(Y_t|x_t)=\Ga x_t^{\Gb}
-\end{eqnarray}
-By performing least squares regression of $\log(\hat{V}^{1/2}(Y_t|x_t))$ on $\log(x_t)$, we have that $\hat{\Ga}=0.0106$ and $\hat{\Gb}=1.429$, which are similar to the values reported in \cite{Fan1998Efficient}.
+%\begin{eqnarray}
+%Var^{1/2}(Y_t|x_t)=\Ga x_t^{\Gb}
+%\end{eqnarray}
+%By performing least squares regression of $\log(\hat{V}^{1/2}(Y_t|x_t))$ on $\log(x_t)$, we have that $\hat{\Ga}=0.0106$ and $\hat{\Gb}=1.429$, which are similar to the values reported in \cite{Fan1998Efficient}.
+\subsection{Motorcycle Acceleration Data}
+\begin{figure}
+\centering
+    \includegraphics[width=0.65\textwidth]{motorcycle.pdf}
+    \caption{}
+    \label{fig:motorcycle}
+\end{figure}
+
+Talk about this being a fast one-step procedure.
+Compare with Delouille and note that we do not have to manually remove detail coefficients.
+Could also do better visually by using better interpolation methods
 \newpage

### 2016-01-09 gaus_data/delouille/ethanol.R

@@ -1,32 +1,23 @@
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_alt2.R"))
-
+library(smash)
 library(lattice)
 
-x.ini=sort(ethanol$E)
-y.ini=ethanol$NOx[order(ethanol$E)]
+x.ini = sort(ethanol$E)
+y.ini = ethanol$NOx[order(ethanol$E)]
 
-x=unique(x.ini)
-y=0
+x = unique(x.ini)
+y = 0
 for(i in 1:length(x)){
-  y[i]=median(y.ini[x.ini==x[i]])
+  y[i] = median(y.ini[x.ini == x[i]])
 }
 
 
 y.exp=c(y,y[length(y):(2*length(y)-128+1)])
-y.final=c(y.exp,y.exp[length(y.exp):1])
+y.final = c(y.exp, y.exp[length(y.exp):1])
 
-y.est=bayesmooth(y.final)
-y.est.alt2=bayesmooth.alt2(y.final)
 
-y.est=y.est[1:length(y)]
-y.est.alt2=y.est.alt2[1:length(y)]
-
-y.var.est=bayesmooth(y.final,v.est=TRUE)
-y.var.est.alt2=bayesmooth.alt2(y.final,v.est=TRUE)
+y.var.est=ashsmooth.gaus(y.final,v.est=TRUE)
 
 y.var.est=y.var.est[1:length(y)]
-y.var.est.alt2=y.var.est.alt2[1:length(y)]
 
 plot(x,y,ylim=c(-1,5))
 lines(x,y.est,col=2)

### 2016-01-09 gaus_data/delouille/mc.R

@@ -1,36 +1,41 @@
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_alt2.R"))
-
+library(smash)
 library(MASS)
 
-x.ini=sort(mcycle$times)
-y.ini=mcycle$accel[order(mcycle$times)]
-
-x=unique(x.ini)
-y=0
-for(i in 1:length(x)){
-  y[i]=median(y.ini[x.ini==x[i]])
+#wrapper function to return estimated mean and variance function given raw data
+smash.wrapper = function(x.ini, y.ini){
+  #Take the median of observations with repeated x values
+  x = unique(x.ini)
+  y = 0
+  for(i in 1:length(x)){
+    y[i] = median(y.ini[x.ini == x[i]])
+  }
+  
+  #Mirror the data twice to make it periodic and a power of 2
+  y.exp = c(y, y[length(y):(2*length(y) - 2^ceiling(log2(length(y))) + 1)])
+  y.final = c(y.exp, y.exp[length(y.exp):1])
+  
+  #Run SMASH
+  y.est = ashsmooth.gaus(y.final, v.est=TRUE, joint = TRUE, family = "DaubLeAsymm", filter.number = 8)
+  
+  y.mu.est = y.est$mu.res[1:length(y)]
+  y.var.est = y.est$var.res[1:length(y)]
+  return(list(x = x, y = y, mu.est = y.mu.est, var.est = y.var.est))
 }
 
 
-y.exp=c(y,y[length(y):(2*length(y)-128+1)])
-y.final=c(y.exp,y.exp[length(y.exp):1])
 
-y.est=bayesmooth(y.final)
-y.est.alt2=bayesmooth.alt2(y.final)
+#Obtain initial data
+x.ini = sort(mcycle$times)
+y.ini = mcycle$accel[order(mcycle$times)]
 
-y.est=y.est[1:length(y)]
-y.est.alt2=y.est.alt2[1:length(y)]
+x.ini = sort(ethanol$E)
+y.ini = ethanol$NOx[order(ethanol$E)]
 
-y.var.est=bayesmooth(y.final,v.est=TRUE)
-y.var.est.alt2=bayesmooth.alt2(y.final,v.est=TRUE)
 
[…]

### 2016-01-09 paper/plot_gaus.R

@@ -470,12 +470,13 @@ layout(matrix(c(1, 1, 1, 3, 2, 0), nrow = 3), widths = c(8, 2), heights = c(2, 4
 par(mar = c(7.1, 7.1, 2.1, 1.1), cex.axis = 2.5, cex.sub = 2.5, cex.lab = 2.5, mgp = c(3, 1.5, 0))
 plot(wc.sim[4, ], wc.sim.shrunk[[3]]$PosteriorMean, xlim = c(-1, 1), pch = 20, cex = 1.4, xlab = "", ylab = "", ylim = c(-1, 1), col = grey(col.bw.3))
 title(xlab = "empirical wavelet coefficients", ylab = "estimated wavelet coefficients", line = 4)
-par(mar = c(1, 1, 0.1, 5.1), cex.axis = 2, cex.sub = 2, cex.lab = 2, mgp = c(3, 1.3, 0))
+legend('bottomright', legend = c("wavelet coefficients, scale 7"), cex = 1.5, pch = c(20, 20), col = grey(0.1))
+par(mar = c(1, 1, 0.1, 5.1), cex.axis = 2, cex.sub = 3, cex.lab = 2, mgp = c(3, 1.3, 0))
 image.scale(volcano, col = grey(breaks), breaks = breaks.ori, horiz = FALSE, yaxt = "n")
 axis(4, at = seq(0, 0.25, 0.05), las = 2)
 par(mar = c(0.1, 0.1, 0.1 ,0.1))
 plot(1, 1, xlim = c(0, 1), ylim = c(0, 1), type = "n", axes = FALSE)
-legend(x = -0.25, y = 0.17, legend = "standard deviation", cex = 1.5, bty = "n")
+legend(x = -0.25, y = 0.17, legend = "standard error", cex = 1.5, bty = "n")
 dev.off()
 
 pdf("paper/simple_eg_5.pdf", height = 6, width = 8)

### 2016-02-09 paper/draft_5.tex
updated section on gaussian eg

@@
 
-Talk about this being a fast one-step procedure.
-Compare with Delouille and note that we do not have to manually remove detail coefficients.
-Could also do better visually by using better interpolation methods
+We first apply the Gaussian version of SMASH on the well known motorcycle acceleration dataset from \cite{silverman1985some}.
+The data consists of 133 observations measuring head acceleration in a simulated motorcycle accident that is used to test crash helmets.
+The dependent variable is $acceleration$ (in $g$), and the independent variable is $time$ (in ms).
+To deal with repeated measurements, we simply take the median of the measurements for acceleration for any given $time$ value.
+To address the issue of non-equal spacing between the data points, we applied the procedure described in the Simulations section when comparing our method against MFVB.
+The fitted mean and variance curves are shown in Figure \ref{fig:motorcycle}.
+Comparing our fit with that of \cite{Delouille2004Smooth}, which also employs a wavelet-based approach, we note two advantages to using SMASH.
+First, our method provides a measure of uncertainty (through both the credible band for the mean curve as well as the variance curve itself), which is often of interest in many applications.
+Second, our method is able to produce a visually appealing fit when used without having to tune any parameters, while the approach in \cite{Delouille2004Smooth} requires an $adhoc$ removal of fine scale detail coefficients to avoid introducing artifacts into the fit.
+
+Although SMASH does a reasonably good job of performing nonparametric regression on the given dataset, we do recognize that there are better ways to deal with the fact that the observations are not equally spaced, which can then reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in the literature.
+Nevertheless, we can use SMASH directly out of the box in many settings where Gaussian denoising is required, making it an extremely versatile tool.
 \newpage

### 2016-02-15 intro/intro.Rmd
updates to intro
re-organization of repo

@@
 ```{r}
+#create mean function
 spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
@@
 
+#load packages
 library(wavethresh)
@@
 library(caTools)
-source(file.path("../Rcode/bayesmooth.R"))
-source(file.path("../Rcode/ti_thresh.R"))
+library(smash)
 
+#define functions to be used later
 mse=function(x,y) mean((x-y)^2)
@@
 
-##Default R wavelet method, written into a single function
+##Default R wavelet thresholding method, written into a single function
 waveti.u=function (x, filter.number = 10, family = "DaubLeAsymm", min.level = 3, noise.level){
-    TT <- length(x)
-    thresh <- noise.level * sqrt(2 * log(TT))    
-    x.w <- wd(x, filter.number, family, type = "station")
-    x.w.t <- threshold(x.w, levels = (min.level):(x.w$nlevels - 1), policy = "manual", value = thresh, type = "hard")
-    x.w.t.r <- AvBasis(convert(x.w.t))
+    TT = length(x)
+    thresh = noise.level * sqrt(2 * log(TT))    
+    x.w = wd(x, filter.number, family, type = "station")
+    x.w.t = threshold(x.w, levels = (min.level):(x.w$nlevels - 1), policy = "manual", value = thresh, type = "hard")
+    x.w.t.r = AvBasis(convert(x.w.t))
     return(x.w.t.r)
@@
 
+##Similarly for Ebayesthresh
 waveti.ebayes=function (x, filter.number = 10, family = "DaubLeAsymm", min.level = 3, noise.level){
@@
     J=log2(n)
-    x.w <- wd(x, filter.number, family, type = "station")
+    x.w = wd(x, filter.number, family, type = "station")
     for(j in min.level:(J-1)){
@@
 
-mu.est=apply(X.s,1,bayesmooth)
-mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
+mu.est=apply(X.s,1,ashsmooth.gaus)
+mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="smash")
 mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
@@
 
-##Bayesmooth
+##SMASH
 mise(t(mu.est),mu.t,10)
-##TI thresholding with variance estimated from bayesmooth
+##TI thresholding with variance estimated from smash
 mise(t(mu.est.tivar.ash),mu.t,10)
@@
 
-plot(mu.t,type='l')
+plot(mu.t, xlab = "", ylab = "",type='l')
 lines(mu.est[,1],col=2)
@@
 lines(mu.est.ti.ebayes[1,],col=6)
+legend("topright", legend = c("smash", "ti_rmad", "ti_homo", "ebayes_homo"), col = c(2, 3, 4, 6))
 ```
@@
 
-mu.est=apply(X.s,1,bayesmooth)
-mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
+mu.est=apply(X.s,1,ashsmooth.gaus)
+mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="smash", ashparam = list(nullcheck = FALSE))
 mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
@@
 
-##Bayesmooth
+##smash
 mise(t(mu.est),mu.t,10)
-##TI thresholding with variance estimated from bayesmooth
+##TI thresholding with variance estimated from smash
 mise(t(mu.est.tivar.ash),mu.t,10)
@@
 ```{r fig.width=12, fig.height=12}
-plot(mu.t,type='l')
+plot(mu.t,xlab = "", ylab = "", type='l')
 lines(mu.est[,1],col=2)
@@
 lines(mu.est.ti.ebayes[1,],col=6)
+legend("topright", legend = c("smash", "ti_rmad", "ti_homo", "ebayes_homo"), col = c(2, 3, 4, 6))
 
@@
 
+#define test functions
 pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
@@
 
-var.est.1=bayesmooth(X.s.1,v.est=TRUE)
-var.est.2=bayesmooth(X.s.2,v.est=TRUE)
-var.est.3=bayesmooth(X.s.3,v.est=TRUE)
-var.est.4=bayesmooth(X.s.4,v.est=TRUE)
+var.est.1=ashsmooth.gaus(X.s.1,v.est=TRUE)
+var.est.2=ashsmooth.gaus(X.s.2,v.est=TRUE)
+var.est.3=ashsmooth.gaus(X.s.3,v.est=TRUE)
+var.est.4=ashsmooth.gaus(X.s.4,v.est=TRUE)
 
@@
 par(mfrow=c(2,2))
-plot(sigma.t.1^2,type='l')
+plot(sigma.t.1^2, xlab = "", ylab = "",type='l', main = "V1")
 lines(var.est.1,col=2)
-plot(sigma.t.2^2,type='l')
+plot(sigma.t.2^2, xlab = "", ylab = "",type='l', main = "V2")
 lines(var.est.2,col=2)
-plot(sigma.t.3^2,type='l')
+plot(sigma.t.3^2, xlab = "", ylab = "",type='l', main = "V3")
 lines(var.est.3,col=2)
-plot(sigma.t.4^2,type='l')
+plot(sigma.t.4^2, xlab = "", ylab = "",type='l', main = "V4")
 lines(var.est.4,col=2)
@@
 
-Now we take a look at how this wavelet-based approach handles unevenly spaced data. Wavelet methods are not optimized for unevenly spaced, but still works.
+Now we take a look at how this wavelet-based approach handles unevenly spaced data.
+Wavelet methods are not optimized for unevenly spaced, but still works.
+We first look at the case when the data are normally spaced.
 
@@
 
-##Bayesmooth
+##smash
 mise(t(mu.est),mu.t,10)
-##TI thresholding with variance estimated from bayesmooth
-mise(t(mu.est.tivar.ash),mu.t,10)
-##TI thresholding with variance estimated from running MAD
-mise(t(mu.est.tivar.mad),mu.t,10)
-##TI thresholding with constant variance (estimated)
-mise(mu.est.ti,mu.t,10)
-##EBayes with constant variance (estimated)
-mise(mu.est.ti.ebayes,mu.t,10)
-
-##MISEs for the grid
-xgrid=1:n/n
-mu.est.inter=matrix(0,10,n)
-mu.est.tivar.ash.inter=matrix(0,10,n)
-mu.est.tivar.mad.inter=matrix(0,10,n)
-mu.est.ti.inter=matrix(0,10,n)
-mu.est.ti.ebayes.inter=matrix(0,10,n)
-for(i in 1:10){
-  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
-  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
-  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
-  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
-  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y
-
-}
-mu.t.inter=(spike.f(xgrid)+1)/5
-
-mise(mu.est.inter,mu.t.inter,10)
-mise(mu.est.tivar.ash.inter,mu.t.inter,10)
-mise(mu.est.tivar.mad.inter,mu.t.inter,10)
-mise(mu.est.ti.inter,mu.t.inter,10)
-mise(mu.est.ti.ebayes.inter,mu.t.inter,10)
-
-```
-
-```{r fig.width=12, fig.height=12}
-par(mfrow=c(1,1))
-plot(t,mu.t,type='l')
-lines(t,mu.est[,1],col=2)
-lines(t,mu.est.tivar.mad[,1],col=3)
-lines(t,mu.est.ti[1,],col=4)
-lines(t,mu.est.ti.ebayes[1,],col=6)
-```
-
-We then look at the case of non-constant variance
-```{r}
-##non-constant variance
-sigma.ini=sqrt(var2)
-sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2
-
-set.seed(327)
-X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)
-
-mu.est=apply(X.s,1,bayesmooth)
-mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="bayesm")
-mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
-
-mu.est.ti=matrix(0,10,n)
-mu.est.ti.ebayes=matrix(0,10,n)
-for(i in 1:10){
-  sig.est=sig.est.func(X.s[i,],n)
-  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
-  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
-}
-
-##MISEs
-
-##Bayesmooth
-mise(t(mu.est),mu.t,10)
-##TI thresholding with variance estimated from bayesmooth
+##TI thresholding with variance estimated from smash
 mise(t(mu.est.tivar.ash),mu.t,10)
@@
 
+We then look at the case of non-constant variance
+```{r}
+##non-constant variance
+sigma.ini=sqrt(var2)
+sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2
+
+set.seed(327)
+X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)
+
+mu.est=apply(X.s,1,ashsmooth.gaus)
+mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="smash")
+mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
+
+mu.est.ti=matrix(0,10,n)
+mu.est.ti.ebayes=matrix(0,10,n)
+for(i in 1:10){
+  sig.est=sig.est.func(X.s[i,],n)
+  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
+  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
+}
+
+##MISEs
+
+##smash
+mise(t(mu.est),mu.t,10)
+##TI thresholding with variance estimated from smash
+mise(t(mu.est.tivar.ash),mu.t,10)
+##TI thresholding with variance estimated from running MAD
+mise(t(mu.est.tivar.mad),mu.t,10)
+##TI thresholding with constant variance (estimated)
+mise(mu.est.ti,mu.t,10)
+##EBayes with constant variance (estimated)
+mise(mu.est.ti.ebayes,mu.t,10)
+
+##MISEs for the grid
+xgrid=1:n/n
+mu.est.inter=matrix(0,10,n)
+mu.est.tivar.ash.inter=matrix(0,10,n)
+mu.est.tivar.mad.inter=matrix(0,10,n)
+mu.est.ti.inter=matrix(0,10,n)
+mu.est.ti.ebayes.inter=matrix(0,10,n)
+for(i in 1:10){
+  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
+  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
+  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
+  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
+  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y
+
+}
+mu.t.inter=(spike.f(xgrid)+1)/5
+
+mise(mu.est.inter,mu.t.inter,10)
+mise(mu.est.tivar.ash.inter,mu.t.inter,10)
+mise(mu.est.tivar.mad.inter,mu.t.inter,10)
+mise(mu.est.ti.inter,mu.t.inter,10)
+mise(mu.est.ti.ebayes.inter,mu.t.inter,10)
+
+```
+
+```{r fig.width=12, fig.height=12}
+par(mfrow=c(1,1))
+plot(t,mu.t, xlab = "", ylab = "",type='l')
+lines(t,mu.est[,1],col=2)
+lines(t,mu.est.tivar.mad[,1],col=3)
+lines(t,mu.est.ti[1,],col=4)
+lines(t,mu.est.ti.ebayes[1,],col=6)
+legend("topright", legend = c("smash", "ti_rmad", "ti_homo", "ebayes_homo"), col = c(2, 3, 4, 6))
+
+```
+
+Now for the case when the data are distributed according to a Poisson Process.
+
+```{r}
+n=1024
+t=c(0,rexp(n-1,1))
+t=cumsum(t)
+t=(t-min(t))/(max(t)-min(t))
+
+mu.s=spike.f(t)
+
+##mean function
+mu.t=(1+mu.s)/5
+
+##signal to noise ratio
+rsnr=sqrt(1)
+
+##variance functions
+var1=rep(1,n)
+var2=(0.0001+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
+```
+
+```
+
+We first look at the case of constant variance
+```{r}
+##constant variance
+sigma.ini=sqrt(var1)
+sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2
+
+set.seed(327)
+X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)
+
+mu.est=apply(X.s,1,ashsmooth.gaus)
+mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="smash")
+mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
+
+mu.est.ti=matrix(0,10,n)
+mu.est.ti.ebayes=matrix(0,10,n)
+for(i in 1:10){
+  sig.est=sig.est.func(X.s[i,],n)
+  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
+  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
+}
+
+##MISEs for the sample points
+
+##smash
+mise(t(mu.est),mu.t,10)
+##TI thresholding with variance estimated from smash
+mise(t(mu.est.tivar.ash),mu.t,10)
+##TI thresholding with variance estimated from running MAD
+mise(t(mu.est.tivar.mad),mu.t,10)
+##TI thresholding with constant variance (estimated)
+mise(mu.est.ti,mu.t,10)
+##EBayes with constant variance (estimated)
+mise(mu.est.ti.ebayes,mu.t,10)
+
+##MISEs for the grid
+xgrid=1:n/n
+mu.est.inter=matrix(0,10,n)
+mu.est.tivar.ash.inter=matrix(0,10,n)
+mu.est.tivar.mad.inter=matrix(0,10,n)
+mu.est.ti.inter=matrix(0,10,n)
+mu.est.ti.ebayes.inter=matrix(0,10,n)
+for(i in 1:10){
+  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
+  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
+  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
+  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
+  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y
+
+}
+mu.t.inter=(spike.f(xgrid)+1)/5
+
+mise(mu.est.inter,mu.t.inter,10)
+mise(mu.est.tivar.ash.inter,mu.t.inter,10)
+mise(mu.est.tivar.mad.inter,mu.t.inter,10)
+mise(mu.est.ti.inter,mu.t.inter,10)
+mise(mu.est.ti.ebayes.inter,mu.t.inter,10)
+
+```
+
+```{r fig.width=12, fig.height=12}
+par(mfrow=c(1,1))
+plot(t,mu.t, xlab = "", ylab = "",type='l')
+lines(t,mu.est[,1],col=2)
+lines(t,mu.est.tivar.mad[,1],col=3)
+lines(t,mu.est.ti[1,],col=4)
+lines(t,mu.est.ti.ebayes[1,],col=6)
+legend("topright", legend = c("smash", "ti_rmad", "ti_homo", "ebayes_homo"), col = c(2, 3, 4, 6))
+
+```
+
+We then look at the case of non-constant variance
+```{r}
+##non-constant variance
+sigma.ini=sqrt(var2)
+sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2
+
+set.seed(327)
+X.s=matrix(rnorm(10*n,mu.t,sigma.t),nrow=10,byrow=TRUE)
+
+mu.est=apply(X.s,1,ashsmooth.gaus,ashparam=list(nullcheck=FALSE))
+mu.est.tivar.ash=apply(X.s,1,ti.thresh,method="smash",ashparam=list(nullcheck=FALSE))
+mu.est.tivar.mad=apply(X.s,1,ti.thresh,method="rmad")
+
+mu.est.ti=matrix(0,10,n)
+mu.est.ti.ebayes=matrix(0,10,n)
+for(i in 1:10){
+  sig.est=sig.est.func(X.s[i,],n)
+  mu.est.ti[i,]=waveti.u(X.s[i,],noise.level=sig.est)
+  mu.est.ti.ebayes[i,]=waveti.ebayes(X.s[i,],noise.level=sig.est)
+}
+
+##MISEs
+
+##smash
+mise(t(mu.est),mu.t,10)
+##TI thresholding with variance estimated from smash
+mise(t(mu.est.tivar.ash),mu.t,10)
+##TI thresholding with variance estimated from running MAD
+mise(t(mu.est.tivar.mad),mu.t,10)
+##TI thresholding with constant variance (estimated)
+mise(mu.est.ti,mu.t,10)
+##EBayes with constant variance (estimated)
+mise(mu.est.ti.ebayes,mu.t,10)
+
+##MISEs for the grid
+xgrid=1:n/n
+mu.est.inter=matrix(0,10,n)
+mu.est.tivar.ash.inter=matrix(0,10,n)
+mu.est.tivar.mad.inter=matrix(0,10,n)
+mu.est.ti.inter=matrix(0,10,n)
+mu.est.ti.ebayes.inter=matrix(0,10,n)
+for(i in 1:10){
+  mu.est.inter[i,]=approx(t,mu.est[,i],xgrid)$y
+  mu.est.tivar.ash.inter[i,]=approx(t,mu.est.tivar.ash[,i],xgrid)$y
+  mu.est.tivar.mad.inter[i,]=approx(t,mu.est.tivar.mad[,i],xgrid)$y
+  mu.est.ti.inter[i,]=approx(t,mu.est.ti[i,],xgrid)$y
+  mu.est.ti.ebayes.inter[i,]=approx(t,mu.est.ti.ebayes[i,],xgrid)$y
+
+}
+mu.t.inter=(spike.f(xgrid)+1)/5
+
+mise(mu.est.inter,mu.t.inter,10)
+mise(mu.est.tivar.ash.inter,mu.t.inter,10)
+mise(mu.est.tivar.mad.inter,mu.t.inter,10)
+mise(mu.est.ti.inter,mu.t.inter,10)
+mise(mu.est.ti.ebayes.inter,mu.t.inter,10)
+
+```
+
+```{r fig.width=12, fig.height=12}
+par(mfrow=c(1,1))
+plot(t,mu.t, xlab  ="",  ylab = "",type='l')
+lines(t,mu.est[,1],col=2)
+lines(t,mu.est.tivar.mad[,1],col=3)
+lines(t,mu.est.ti[1,],col=4)
+lines(t,mu.est.ti.ebayes[1,],col=6)
+legend("topright", legend = c("smash", "ti_rmad", "ti_homo", "ebayes_homo"), col = c(2, 3, 4, 6))
+
+```
+
 Now we look at some of the simulations in a couple of papers, as well as the datasets used in them.
@@
 
-  mu.est=bayesmooth(y.data)
+  mu.est=ashsmooth.gaus(y.data)
   mu.est=mu.est[1:200]
-  var.est=bayesmooth(y.data,v.est=TRUE)
+  var.est=ashsmooth.gaus(y.data,v.est=TRUE)
   var.est=var.est[1:200]
@@
 
-plot(x,mu.t,type='l')
+plot(x,mu.t, xlab = "", ylab = "",type='l', main = "mean function")
 lines(x,mu.est[1:200],col=2)
 
-plot(x,sigma.t^2,type='l')
+plot(x,sigma.t^2, xlab = "", ylab = "",type='l', main = "var function")
 lines(x,var.est[1:200],col=2)
@@
 ```{r}
-data=read.csv("../gaus_data/treas_bill/treas_bill.csv",header=FALSE)
+data=read.csv("../code_paper/gaus_data/treas_bill/treas_bill.csv",header=FALSE)
 data=as.numeric(data[,1])
@@
 
-y.est=bayesmooth(y.final)
-y.est.var=bayesmooth(y.final,v.est=TRUE)
+y.est=ashsmooth.gaus(y.final)
+y.est.var=ashsmooth.gaus(y.final,v.est=TRUE)
 
@@
 par(mfrow=c(2,2))
-plot(data,type='l')
+plot(data, xlab = "year", ylab = "interest rate",type='l')
 
 plot(x,y)
-lines(x.mod,y.est[1:(length(y.mod))],col=2)
+lines(x.mod,y.est[1:(length(y.mod))], xlab = "X", ylab = "Y",col=2)
 
-plot(x.mod,y.est[1:(length(y.mod))],type='l',ylim=c(-0.3,0.3))
+plot(x.mod,y.est[1:(length(y.mod))], xlab = "X", ylab = "Y",type='l',ylim=c(-0.3,0.3))
 
-plot(x.mod,sqrt(y.est.var[1:(length(y.mod))]),type='l')
+plot(x.mod,sqrt(y.est.var[1:(length(y.mod))]), xlab = "X",  ylab = "volatility",type='l')
 ````
@@
 
-  mu.est<-bayesmooth(y.final)
+  mu.est<-ashsmooth.gaus(y.final)
   mu.est=mu.est[1:n]
@@
 
-y.est=bayesmooth(y.final)
+y.est=ashsmooth.gaus(y.final)
 y.est=y.est[1:length(y)]
-y.var.est=bayesmooth(y.final,v.est=TRUE)
+y.var.est=ashsmooth.gaus(y.final,v.est=TRUE)
 y.var.est=y.var.est[1:length(y)]
@@
 
-plot(x,y,ylim=c(-150,100))
+plot(x,y, xlab = "time", ylab = "acceleration",ylim=c(-150,100), main = "mean function")
 lines(x,y.est,col=2)
-plot(x,y.var.est,type='l')
+plot(x,y.var.est, xlab = "time", ylab = "acceleration",type='l', main = "var function")
 
@@
 
-plot(x,y,ylim=c(-1,5))
+plot(x,y, xlab = "ethonal", ylab = "NOx",ylim=c(-1,5), main = "mean function")
 lines(x,y.est,col=2)
-plot(x,y.var.est,type='l')
+plot(x,y.var.est, xlab = "ethonal", ylab = "NOx",type='l', main = "var function")
 

### 2016-02-15 Rcode/bash.R

@@ -1,66 +1,0 @@
-#EM algorithm for estimating mixing proportions given TI table,
-#parent TI table and beta parameters  
-binash=function(tit,ptit,qq,mode=1,maxit=2000,tol=1e-5){
-  n=dim(tit)[2]
-  J=dim(tit)[1]-1
-  nt=tit[-1,]
-  ns=ptit[,((1:(2*n))%%2==1)]
-  nf=nt-ns
-  maxit=maxit
-  tol=tol
-  convcrit=10.0
-  iter=0
-  lik=NULL
-  likk=0
-  if(mode==1){
-    pip1=0.5*rep(1,J)
-    while((convcrit > tol) & (iter < maxit)){ 
-      lik.old=likk
-      pi=pip1
-      pmat0=log(pi)+nt*log(1/2)
-      pmat1=log(1-pi)+lbeta(ns+qq,nf+qq)-lbeta(qq,qq)
-      pm=pmax(pmat0,pmat1)
-      pmat0=pmat0-pm
-      pmat1=pmat1-pm
-      pmat=exp(pmat0)/(exp(pmat0)+exp(pmat1))
-      #likk=apply(log(exp(pmat0)+exp(pmat1)),1,sum)
-      likk=apply(log(exp(pmat0)+exp(pmat1))+pm,1,sum)
-      lik=cbind(lik,likk)
-      pip1=rowMeans(pmat)
-      pip1=pmax(pip1,1e-8)
-      p=pip1
-      convcrit=max((likk-lik.old)^2)
-      iter=iter+1
-    }
-  }else if(mode==2){
-    K=length(qq)
-    pip1=1/K*matrix(1,nrow=J,ncol=K)
-    qq=qq%o%rep(1,n)
-    rK=rep(1,K)
-    pmat_i=list(0)
-    for(j in 1:J){
-      nns=rK%o%ns[j,]
-      nnf=rK%o%nf[j,]
-      pmat_i[[j]]=lbeta(nns+qq,nnf+qq)-lbeta(qq,qq)
-    }
-    while((convcrit > tol) & (iter < maxit)){    
-      pi=pip1
-      lik.old=likk
-      for(j in 1:J){
-        pp=pi[j,]%o%rep(1,n)
-        pmat=log(pp)+pmat_i[[j]]
-        pm=apply(pmat,2,max)
-        pmat=pmat-rK%o%pm
-        pip1.norm=exp(pmat)/(rK%o%colSums(exp(pmat)))
[…]

### 2016-02-15 Rcode/jash_old.r

@@ -1,578 +1,0 @@
-# Y: N by n observation matrix (N tests, n replicate obs for each test)
-# Model: Y_{jk}|beta_j,tau_j ~ N(beta_j,1/tau_j)
-# Prior: beta_j|tau_j~N(mu_j,1/(c_l*tau_j)), tau_j~lambda_k*Gamma(a_m,a_m), w.p. pi_{klm}
-# Mixture constraint: sum(pi_{klm})=1
-# Or: sum(pi_k)=1, sum(pi_l)=1, sum(pi_m)=1 for each param
-# a_m, lambda_k, c_l, mu_j are known
-######################################################
-library(qvalue)
-qval.from.localfdr = function(localfdr){
-  o = order(localfdr)
-  qvalue=rep(NA,length(localfdr))
-  qvalue[o] = (cumsum(sort(localfdr))/(1:sum(!is.na(localfdr))))
-  return(qvalue)
-}
-
-
-# post_pi computes the posterior probability 
-# P(beta_j,tau_j belongs to the i'th component | Y)
-post_pi = function(N,n,M,K,L,a.vec,b.vec,d.vec,mu,MEAN,SSE,pi){
-  post.gammab=0.5*(outer(SSE,rep(1,M*L*K))+outer((MEAN-mu)^2,n*d.vec)+outer(rep(1,N),2*b.vec))
-  post.pi.mat = exp(outer(rep(1,N),log(pi)+a.vec*log(b.vec)-lgamma(a.vec)+0.5*log(d.vec)+lgamma(a.vec+n/2))-
-                      log(post.gammab)*
-                      outer(rep(1,N),a.vec+n/2))
-  return(list(gammab=post.gammab,pimat=post.pi.mat))
-  
-#   post.pi.mat = exp(outer(rep(1,N),log(pi)+a.vec*log(b.vec)-lgamma(a.vec)+log(sqrt(d.vec)+lgamma(a.vec+n/2))-
-#     log(0.5*(outer(SSE,rep(1,M*L*K))+outer((MEAN-mu)^2,n*d.vec)+outer(rep(1,N),2*b.vec)))*
-#     outer(rep(1,N),a.vec+n/2))
- 
-#   post.pi.mat = outer(rep(1,N),pi*(b.vec)^a.vec/gamma(a.vec)*sqrt(d.vec*(gamma(a.vec+n/2)))/
[…]

### 2016-02-15 Rcode/threshold_haar.R

@@ -1,32 +1,0 @@
-threshold.haar <- function (vdtable, vtable, levels, type = "hard", policy = "universal")
-{
-    wmean <- vdtable[-1,]/2
-    d <- NULL
-    n <- dim(vdtable)[2]
-    nthresh <- length(levels)
-    thresh <- list(0)
-    for (i in 1:nthresh) {
-        d <- vdtable[levels[i]+2,]
-        noise.level <- sqrt(vtable[levels[i]+2,])
-        nd <- length(d)
-        thresh[[i]] <- sqrt(2*log(nd*log2(nd))) * noise.level
-    }
-    for (i in 1:nthresh) {
-        d <- vdtable[levels[i]+2,]
-        if (type == "hard") {
-            d[abs(d) <= thresh[[i]]] <- 0
-        }
-        else if (type == "soft") {
-            d <- (d * (abs(d) - thresh[[i]]) * (abs(d) > thresh[[i]]))/abs(d)
-            d[is.na(d)] <- 0
-        }
-        wmean[levels[i]+1,] <- d/2
-    }
-    return(wmean)
-}
-
-
-
-
-
-

### 2016-02-15 Rcode/ti_thresh.R

@@ -1,623 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/threshold_haar.R")
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/threshold_var.R")
-
-
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-library(caTools)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
[…]

### 2016-02-15 Rcode/vash.R

@@ -1,203 +1,0 @@
-# Prior of se: se|pi,alpha.vec,c ~ pi*IG(alpha_k,c*(alpha_k-1))
-# Likelihood: varhat|se ~ sj*Gamma(n/2,n/2)
-# pi, alpha.vec, c: known
-# Posterior weight of P(se|varhat) (IG mixture distn)
-post_pi = function(n,varhat,alpha.vec,modalpha.vec,c,pi){
-  N = length(varhat)
-  K = length(alpha.vec)
-  post.pi.mat = exp(outer(rep(1,N),log(pi))+n/2*log(n/2)-lgamma(n/2)
-                  +(n/2-1)*outer(log(varhat),rep(1,K))
-                  +outer(rep(1,N),alpha.vec*log(c*modalpha.vec)-lgamma(alpha.vec)+lgamma(alpha.vec+n/2))
-                  -outer(rep(1,N),alpha.vec+n/2)*log(outer(rep(1,N),c*modalpha.vec)+outer(n/2*varhat,rep(1,K))))
-  return(pimat=post.pi.mat)
-}
-
-# Normalize pi to make sum(pi)=1
-normalized_pi = function(pi.mat){
-  n = dim(pi.mat)[2]
-  pi.normalized = pi.mat/outer(rowSums(pi.mat),rep(1,n))  
-  return(pi.normalized)
-}
-
-# Posterior distn P(se|varhat)
-# alpha.vec, c, pi: known
-# varhat: observed (standard errors)^2
-post_distn = function(n,varhat,alpha.vec,modalpha.vec,c,pi){ 
-  N = length(varhat)
-  K = length(alpha.vec)
-  post.pi = normalized_pi(post_pi(n,varhat,alpha.vec,modalpha.vec,c,pi))
-  
-  post.IG.parama = outer(rep(1,N),alpha.vec+n/2)
-  post.IG.paramb = outer(rep(1,N),c*modalpha.vec)+outer(n/2*varhat,rep(1,K))
-  
-  # Posterior mean: E(var|varhat)
-  post.mixmean = post.IG.paramb/(post.IG.parama-1)
-  post.mean = apply(post.pi*post.mixmean,1,sum)
-  
-  return(list(pi=post.pi,mean=post.mean,gammaa=post.IG.parama,gammab=post.IG.paramb))
-}
-
-# Log-likelihood: L(varhat|c,pi,alpha.vec)
[…]

### 2016-02-15 ashprof/ashprof_new.R

@@ -1,8 +1,0 @@
-systime = system.time(ashsmooth.gaus(X.s,filter.number=1,family="DaubExPhase"))
-
-tempfile = "ashprofile_ip.txt"
-Rprof(tempfile, interval = 0.1)
-mu.est.haar<-ashsmooth.gaus(X.s,filter.number=1,family="DaubExPhase")
-Rprof(NULL)
-
-summaryRprof(tempfile)

### 2016-02-15 ashprof/ashprof_old.R

@@ -1,8 +1,0 @@
-systime = system.time(ashsmooth.gaus(X.s,filter.number=1,family="DaubExPhase"))
-
-tempfile = "ashprofile.txt"
-Rprof(tempfile, interval = 0.1)
-mu.est.haar<-ashsmooth.gaus(X.s,filter.number=1,family="DaubExPhase")
-Rprof(NULL)
-
-summaryRprof(tempfile)

### 2016-02-15 gaus_data/delouille/mc.R

@@ -1,42 +1,0 @@
-library(smash)
-library(MASS)
-
-#wrapper function to return estimated mean and variance function given raw data
-smash.wrapper = function(x.ini, y.ini){
-  #Take the median of observations with repeated x values
-  x = unique(x.ini)
-  y = 0
-  for(i in 1:length(x)){
-    y[i] = median(y.ini[x.ini == x[i]])
-  }
-  
-  #Mirror the data twice to make it periodic and a power of 2
-  y.exp = c(y, y[length(y):(2*length(y) - 2^ceiling(log2(length(y))) + 1)])
-  y.final = c(y.exp, y.exp[length(y.exp):1])
-  
-  #Run SMASH
-  y.est = ashsmooth.gaus(y.final, v.est=TRUE, joint = TRUE, family = "DaubLeAsymm", filter.number = 8)
-  
-  y.mu.est = y.est$mu.res[1:length(y)]
-  y.var.est = y.est$var.res[1:length(y)]
-  return(list(x = x, y = y, mu.est = y.mu.est, var.est = y.var.est))
-}
-
-
-
-#Obtain initial data
-x.ini = sort(mcycle$times)
-y.ini = mcycle$accel[order(mcycle$times)]
-
-x.ini = sort(ethanol$E)
-y.ini = ethanol$NOx[order(ethanol$E)]
-
-
-plot(x, y, ylim = c(-150,100))
-lines(x, y.mu.est, col = 2)
-lines(x, y.mu.est + 2*sqrt(y.var.est), col = 4)
-lines(x, y.mu.est - 2*sqrt(y.var.est), col = 4)
-
-
-
-

### 2016-02-15 gaus_data/delouille/mc_ethanol.R

@@ -1,68 +1,0 @@
-library(smash)
-library(MASS)
-library(lattice)
-library(scales)
-
-#Wrapper function to return estimated mean and variance function given raw data
-smash.wrapper = function(x.ini, y.ini){
-  #Take the median of observations with repeated x values
-  x = unique(x.ini)
-  y = 0
-  for(i in 1:length(x)){
-    y[i] = median(y.ini[x.ini == x[i]])
-  }
-  
-  #Mirror the data twice to make it periodic and a power of 2
-  y.exp = c(y, y[length(y):(2*length(y) - 2^ceiling(log2(length(y))) + 1)])
-  y.final = c(y.exp, y.exp[length(y.exp):1])
-  
-  #Run SMASH
-  y.est = ashsmooth.gaus(y.final, v.est=TRUE, joint = TRUE, family = "DaubLeAsymm", filter.number = 8)
-  
-  y.mu.est = y.est$mu.res[1:length(y)]
-  y.var.est = y.est$var.res[1:length(y)]
-  return(list(x = x, y = y, mu.est = y.mu.est, var.est = y.var.est))
-}
-
-
-
-#Obtain motorcycle data
-x.ini.mc = sort(mcycle$times)
-y.ini.mc = mcycle$accel[order(mcycle$times)]
-#Get estimates
-res.mc = smash.wrapper(x.ini.mc, y.ini.mc)
-
-#Obtain ethanol data
-x.ini.eth = sort(ethanol$E)
-y.ini.eth = ethanol$NOx[order(ethanol$E)]
-#Get estimates
-res.eth = smash.wrapper(x.ini.eth, y.ini.eth)
-
-
-
-pdf("paper/motorcycle.pdf", height = 6, width = 8)
-par(cex.axis = 1.3, cex.sub = 1.8, cex.lab = 1.5, mar = c(5.1, 5.1, 2.1, 2.1), mgp = c(3, 1.3, 0))
-plot(res.mc$x, res.mc$mu.est, type = 'l', ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)), max(res.mc$y + 2 * sqrt(res.mc$var.est))), xlab = "time (ms)", ylab = "acceleration (g)", lwd = 1.7)
[…]

### 2016-02-15 gaus_data/treas_bill/analysis.R

@@ -1,108 +1,0 @@
-data=read.csv("D:/Grad School/Spring 2013/multiscale_ash/gaus_data/treas_bill/treas_bill_ave.csv",header=FALSE)
-data=as.numeric(data[,1])
-
-
-library(smash)
-
-
-y=ar(data,FALSE,5)$res
-y=y[!is.na(y)]
-x=sort(data[5:(length(data)-1)])
-y=y[order(data[5:(length(data)-1)])]
-
-
-#coef=c(1.0733,-0.0423,0.0165,0.0228,-0.0773)
-
-resid.comp=function(data,coef){
-  smean=mean(data)
-  ord=length(coef)
-  res=NULL
-  for(i in (length(coef)+1):length(data)){
-    res[i-ord]=(data[i]-smean)-(sum(coef*(data[(i-1):(i-ord)]-smean)))
-  }
-  return(res)
-}
-
-#y=resid.comp(data,coef)
-#x=sort(data[5:(length(data)-1)])
-#y=y[order(data[5:(length(data)-1)])]
-
-
-plot(x,y)
-
-
-####
-xmin=min(x)
-xmax=max(x)
-
-bin.size=(xmax-xmin)/32
-x.seq=seq(xmin,xmax,bin.size)
-x.seq.l=x.seq[1:32]
-x.seq.u=x.seq[2:33]
-y.agg=0
-for(i in 1:32){
-  y.agg[i]=y[x>=x.seq.l[i]&x<x.seq.u[i]]
-}
-y.agg[1024]=y[x>=x.seq.l[1024]&x<=x.seq.u[1024]]
-
-y.approx=approx(x,y,n=1024,method='constant',rule=2)$y
-x.approx=approx(x,y,n=1024,method='constant',rule=2)$x
-
-lines(x.approx,y.approx,col=2)
-y.est.approx=bayesmooth(y.approx)
-y.est.var.approx=bayesmooth(y.approx,v.est=TRUE)
-
-plot(x,y)
-lines(x.approx,y.est.approx,col=2)
-####
-
-x.mod=unique(x)
-y.mod=0
-for(i in 1:length(x.mod)){
-  y.mod[i]=median(y[x==x.mod[i]])
-}
-
-
-y.exp=c(y.mod,y.mod[length(y.mod):(2*length(y.mod)-2^10+1)])
-y.final=c(y.exp,y.exp[length(y.exp):1])
-
[…]

### 2016-02-15 paper/code_plot.R

@@ -1,50 +1,0 @@
-
-#' Interleave two vectors
-#' @param x,y: two vectors of the same length
-#' @return a vector of length twice that of x (or y)
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#' Shift a vector one unit to the right
-#' @param x: a vector
-#' @return a vector of the same length as that of x 
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#' Produces two TI tables. One table contains the difference between adjacent pairs of data in the same resolution, and the other table contains the sum.
-#' @param sig: a signal of length a power of 2
-#' @return a list of two TI tables in the form of matrices
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-  
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
-      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
-      rdiffx = rx[seq(from=1,to=nD-1, by=2)] - rx[seq(from=2,to=nD,by=2)]
-      dmat[D+2,ind] = c(lsumx,rsumx)
-      ddmat[D+2,ind] = c(ldiffx,rdiffx)
-    }
-  }
-  return(list(sumtable=dmat,difftable=ddmat))
-}

### 2016-02-15 paper/plot_pois.R

@@ -1,54 +1,0 @@
-library(vioplot)
-source("paper/vioplot_col.R")
-
-l2norm = function(x) sum(x^2)
-mise.sep = function(x, y) 10000 * apply(x - matrix(rep(y, times = 100), nrow = 100, byrow = T), 1, l2norm)/l2norm(y)
-
-mise.BMSM.bur.1 = mise.sep((est.BMSM.bur.1), mu.bur.1)
-mise.BMSM.bur.8 = mise.sep((est.BMSM.bur.8), mu.bur.8)
-
-
-mise.ash.bur.1 = mise.sep(t(est.ash.bur.1), mu.bur.1)
-mise.ash.bur.8 = mise.sep(t(est.ash.bur.8), mu.bur.8)
-
-mise.hf.ti.r.4.bur.1 = mise.sep(t(est.hf.ti.r.4.bur.1), mu.bur.1)
-mise.hf.ti.r.5.bur.1 = mise.sep(t(est.hf.ti.r.5.bur.1), mu.bur.1)
-mise.hf.ti.r.6.bur.1 = mise.sep(t(est.hf.ti.r.6.bur.1), mu.bur.1)
-mise.hf.ti.r.7.bur.1 = mise.sep(t(est.hf.ti.r.7.bur.1), mu.bur.1)
-mise.hf.ti.r.bur.1 = colMeans(matrix(c(mise.hf.ti.r.4.bur.1, mise.hf.ti.r.5.bur.1, mise.hf.ti.r.6.bur.1, mise.hf.ti.r.7.bur.1), byrow = TRUE, nr = 4))
-
-mise.hf.ti.r.4.bur.8 = mise.sep(t(est.hf.ti.r.4.bur.8), mu.bur.8)
-mise.hf.ti.r.5.bur.8 = mise.sep(t(est.hf.ti.r.5.bur.8), mu.bur.8)
-mise.hf.ti.r.6.bur.8 = mise.sep(t(est.hf.ti.r.6.bur.8), mu.bur.8)
-mise.hf.ti.r.7.bur.8 = mise.sep(t(est.hf.ti.r.7.bur.8), mu.bur.8)
-mise.hf.ti.r.bur.8 = colMeans(matrix(c(mise.hf.ti.r.4.bur.8, mise.hf.ti.r.5.bur.8, mise.hf.ti.r.6.bur.8, mise.hf.ti.r.7.bur.8), byrow = TRUE, nr = 4))
-
-# #vertical
[…]

### 2016-02-15 paper/vioplot_col.R

@@ -1,160 +1,0 @@
-#DISCLAIMER: This function is modified and adapted from the "vioplot" function  in package "vioplot", designed to be able to allow for varying colors for the violin plots, as well as
-#dealing with horizontal violin plots in a more appealing manner.
-
-
-library(sm)
-vioplot.col <- function(x,...,range=1.5,h=NULL,ylim=NULL,names=NULL, horizontal=FALSE,
-                    col="magenta", border="black", lty=1, lwd=1, rectCol="black", colMed="white", pchMed=19, at, add=FALSE, wex=1,
-                    drawRect=TRUE)
-{
-  # process multiple datas
-  datas <- list(x,...)
-  n <- length(datas)
-  
-  if(missing(at)) at <- 1:n
-  
-  # pass 1
-  #
-  # - calculate base range
-  # - estimate density
-  #
-  
-  # setup parameters for density estimation
-  upper  <- vector(mode="numeric",length=n)
-  lower  <- vector(mode="numeric",length=n)
-  q1     <- vector(mode="numeric",length=n)
-  q3     <- vector(mode="numeric",length=n)
-  med    <- vector(mode="numeric",length=n)
-  base   <- vector(mode="list",length=n)
-  height <- vector(mode="list",length=n)
-  baserange <- c(Inf,-Inf)
-  
-  # global args for sm.density function-call
-  args <- list(display="none")
-  
-  if (!(is.null(h)))
-    args <- c(args, h=h)
-  
-  for(i in 1:n) {
-    data<-datas[[i]]
-    
-    # calculate plot parameters
-    #   1- and 3-quantile, median, IQR, upper- and lower-adjacent
-    data.min <- min(data)
-    data.max <- max(data)
-    q1[i]<-quantile(data,0.25)
-    q3[i]<-quantile(data,0.75)
-    med[i]<-median(data)
-    iqd <- q3[i]-q1[i]
-    upper[i] <- min( q3[i] + range*iqd, data.max )
-    lower[i] <- max( q1[i] - range*iqd, data.min )
-    
-    #   strategy:
-    #       xmin = min(lower, data.min))
-    #       ymax = max(upper, data.max))
-    #
-    
-    est.xlim <- c( min(lower[i], data.min), max(upper[i], data.max) )
-    
-    # estimate density curve
-    smout <- do.call("sm.density", c( list(data, xlim=est.xlim), args ) )
[…]

### 2016-02-15 pois_data/plot.R

@@ -1,52 +1,0 @@
-library(smash)
-library(scales)
-
-load("reg_880000_1011072.Robj")
-
-bppos=880001:1011072
-
-res1=ashsmooth.pois(M[1,])
-res2=ashsmooth.pois(M[2,])
-res3=ashsmooth.pois(M[3,])
-res4=ashsmooth.pois(M[4,])
-
-
-pdf("smoothing_all.pdf")
-par(mfrow=c(4,1))
-plot(bppos,res1,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell GM12878, Replicate 1")
-plot(bppos,res2,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell GM12878, Replicate 2")
-plot(bppos,res3,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell H1hesc, Replicate 1")
-plot(bppos,res4,type='l',xlab="position",ylab="intensity",ylim=c(0,5.5),main="Cell H1hesc, Replicate 2")
-dev.off()
-
-
-peaks=read.table("pois_data/Gm1287peaks_chr1_sorted")
-peaks=peaks[order(peaks[,2]),]
-all.base=1:peaks[dim(peaks)[1],3]
-peaks.start=peaks[,2][peaks[,2]>=880000&peaks[,2]<=1011072]
-peaks.end=peaks[,3][peaks[,3]>=880000&peaks[,3]<=1011072]
-
-res=ashsmooth.pois(M[1,]+M[2,],post.var=TRUE)
-
-pdf("peaks_comp_a.pdf",height=5,width=10)
-plot(bppos,M[1,]+M[2,],xlab="position",ylab="counts",pch=16,cex=0.5,col=alpha("black",0.04))
-dev.off()
-
-pdf("peaks_comp_b.pdf",height=5,width=10)
-plot(bppos,res$est,type='l',xlab="position",ylab="intensity")
-for(i in 1:length(peaks.start)){
-  segments(peaks.start[i],-0.02,peaks.end[i],-0.02,col=2,lwd=4)
-}
-dev.off()
-
-
-
-#lines((res$est+3*sqrt(res$var)),col=2)
-#lines((res$est-3*sqrt(res$var)),col=2)
-
-#res.thresh=res$est
[…]

### 2016-02-15 simulation_1d_g/Fan_sims/sim_cubic.R

@@ -1,146 +1,0 @@
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_alt.R"))
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_alt1.R"))
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth_est_var.R"))
-
-mu.mad=0
-var.mad=0
-mu.mad.alt=0
-var.mad.alt=0
-mu.mad.alt1=0
-var.mad.alt1=0
-mu.mad.ev=0
-var.mad.ev=0
-
-for(i in 1:400){
-x=sort(runif(200,-2,2))
-err=rnorm(200)
-sigma.t=0.4*exp(-2*x^2)+0.2
-mu.t=x+2*exp(-16*x^2)
-y=mu.t+sigma.t*err
-
-xgrid=seq(-1.8,1.8,length.out=101)
-mu.t.inter=xgrid+2*exp(-16*xgrid^2)
-var.t.inter=(0.4*exp(-2*xgrid^2)+0.2)^2
-
-y.exp=c(y,y[200:145])
-y.data=c(y.exp,y.exp[256:1])
-
-mu.est=bayesmooth(y.data)
-mu.est=mu.est[1:200]
-var.est=bayesmooth(y.data,v.est=TRUE)
-var.est=var.est[1:200]
-
-mu.est.inter=approx(x,mu.est,xgrid,'linear')$y
-var.est.inter=approx(x,var.est,xgrid,'linear')$y
-
-mu.mad[i]=1/101*sum(abs(mu.est.inter-mu.t.inter))
-var.mad[i]=1/101*sum(abs(var.est.inter-var.t.inter))
-
-mu.est=bayesmooth.alt(y.data)
-mu.est=mu.est[1:200]
-var.est=bayesmooth.alt(y.data,v.est=TRUE)
-var.est=var.est[1:200]
-
-mu.est.inter=approx(x,mu.est,xgrid,'linear')$y
-var.est.inter=approx(x,var.est,xgrid,'linear')$y
-
-mu.mad.alt[i]=1/101*sum(abs(mu.est.inter-mu.t.inter))
-var.mad.alt[i]=1/101*sum(abs(var.est.inter-var.t.inter))
-
[…]

### 2016-02-15 simulation_1d_g/debug_vc.R

@@ -1,156 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=2^10
-t=1:n/n
-mu.s=spike.f(t)
-
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-
-
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-mu.dop=3/(max(mu.dop)-min(mu.dop))*(mu.dop-min(mu.dop))
-
-sig=((2*t + 0.5)*(t <= 0.15)) + 
-       ((-12*(t-0.15) + 0.8)*(t > 0.15 & t <= 0.2)) + 
-       0.2*(t > 0.2 & t <= 0.5) + 
-       ((6*(t - 0.5) + 0.2)*(t > 0.5 & t <= 0.6)) + 
-       ((-10*(t - 0.6) + 0.8)*(t > 0.6 & t <= 0.65)) + 
-       ((-0.5*(t - 0.65) + 0.3)*(t > 0.65 & t <= 0.85)) + 
-       ((2*(t - 0.85) + 0.2)*(t > 0.85))
-mu.ang = 3/5*((5/(max(sig)-min(sig)))*sig - 1.6)-0.0419569
-
-
-
-heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99 / 3.366185
-mu.hs = mu.hs - min(mu.hs)
-
-
-
-pos=c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
[…]

### 2016-02-15 simulation_1d_g/qsub_run_var.sh

@@ -1,37 +1,0 @@
-#!/bin/sh
-#
-#
-#**************************************************************************************************#    
-#            FILE:       qsub_run_multiseq.sh                            
-#           USAGE:       qsub_run_multiseq.sh sample_sheet OUT_DIR < list_loci
-#                        note: make sure that the bed file list_loci ends with a new line
-#                        sample_sheet is a text file containing sample specification
-#                        OUT_DIR is the directory where you want to save results              
-#     DESCRIPTION:       use this script to run run_multiseq.R on the list of loci in list_loci
-#         EXAMPLE:       qsub_run_multiseq.sh ../data/samplesheet.txt /KG/epantaleo/results_run_multiseq/ < list_loci
-#**************************************************************************************************#  
-
-MEM=20g
-OUT_DIR=$1
-
-#check arguments
-if [ -z ${OUT_DIR} ]; then
-    echo "ERROR: incorrect number of arguments. Aborting. "
-    exit 1
-fi
-
-#create output directory (if it doesn't already exist) 
-if [ ! -d "${OUT_DIR}" ]; then
-    mkdir ${OUT_DIR}
-fi
-
-#create directory for logs (if it doesn't already exist)
-LOG_DIR=${OUT_DIR}"logs/"
-if [ ! -d "${LOG_DIR}" ]; then
-    mkdir ${LOG_DIR}
-fi
-
-#run multiseq on each locus in list_loci using qsub
-echo "/data/tools/R-3.0.3/bin/Rscript method_comp_var.R" | \
-qsub -l h_vmem=${MEM} -v PATH -cwd  -o ${LOG_DIR}"res_log.out" -e ${LOG_DIR}"res_log.err"
- 

### 2016-02-15 simulation_1d_g/qsub_run_var_s8.sh

@@ -1,37 +1,0 @@
-#!/bin/sh
-#
-#
-#**************************************************************************************************#    
-#            FILE:       qsub_run_multiseq.sh                            
-#           USAGE:       qsub_run_multiseq.sh sample_sheet OUT_DIR < list_loci
-#                        note: make sure that the bed file list_loci ends with a new line
-#                        sample_sheet is a text file containing sample specification
-#                        OUT_DIR is the directory where you want to save results              
-#     DESCRIPTION:       use this script to run run_multiseq.R on the list of loci in list_loci
-#         EXAMPLE:       qsub_run_multiseq.sh ../data/samplesheet.txt /KG/epantaleo/results_run_multiseq/ < list_loci
-#**************************************************************************************************#  
-
-MEM=20g
-OUT_DIR=$1
-
-#check arguments
-if [ -z ${OUT_DIR} ]; then
-    echo "ERROR: incorrect number of arguments. Aborting. "
-    exit 1
-fi
-
-#create output directory (if it doesn't already exist) 
-if [ ! -d "${OUT_DIR}" ]; then
-    mkdir ${OUT_DIR}
-fi
-
-#create directory for logs (if it doesn't already exist)
-LOG_DIR=${OUT_DIR}"logs/"
-if [ ! -d "${LOG_DIR}" ]; then
-    mkdir ${LOG_DIR}
-fi
-
-#run multiseq on each locus in list_loci using qsub
-echo "/data/tools/R-3.0.3/bin/Rscript method_comp_var_followup_s8.R" | \
-qsub -l h_vmem=${MEM} -v PATH -cwd  -o ${LOG_DIR}"res_log.out" -e ${LOG_DIR}"res_log.err"
- 

### 2016-02-15 simulation_1d_g/tests/gaussian_test.R

@@ -1,121 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=1024
-t=1:n/n
-mu.s=spike.f(t)
-
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-
-mu.b0=2
-set.seed(415)
-#X.b=rnorm(n,mu.b0*(mu.b),sigma.t)
-X.b=rnorm(n,(mu.b/max(mu.b)),sigma.t)
-
-
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-mu.dop=3/(max(mu.dop)-min(mu.dop))*(mu.dop-min(mu.dop))
-
-sig=((2*t + 0.5)*(t <= 0.15)) + 
-       ((-12*(t-0.15) + 0.8)*(t > 0.15 & t <= 0.2)) + 
-       0.2*(t > 0.2 & t <= 0.5) + 
-       ((6*(t - 0.5) + 0.2)*(t > 0.5 & t <= 0.6)) + 
-       ((-10*(t - 0.6) + 0.8)*(t > 0.6 & t <= 0.65)) + 
-       ((-0.5*(t - 0.65) + 0.3)*(t > 0.65 & t <= 0.85)) + 
-       ((2*(t - 0.85) + 0.2)*(t > 0.85))
-mu.ang = 3/5*((5/(max(sig)-min(sig)))*sig - 1.6)-0.0419569
-
-
-
-heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99 / 3.366185
-mu.hs = mu.hs - min(mu.hs)
-
-
-
[…]

### 2016-02-15 simulation_1d_g/tests/gaussian_test_unequal.R

@@ -1,126 +1,0 @@
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R"))
-source("simulation_1d_g/threshold_var.R")
-source("simulation_1d_g/threshold_mod.R")
-source("simulation_1d_g/wd_var.R")
-library(wavethresh)
-library(caTools)
-
-
-la10.sure3=function (x) 
-{
-    x.w <- wd(x)
-    x.w.t <- threshold.wd.mod(x.w)
-    x.w.t.r <- wr(x.w.t)
-    return(x.w.t.r)
-}
-
-la10.ti3u=function (x, filter.number = 10, family = "DaubLeAsymm", min.level = 3, noise.level) 
-{
-    TT <- length(x)
-    thresh <- noise.level * sqrt(2 * log(TT))    
-    x.w <- wd(x, filter.number, family, type = "station")
-    x.w.t <- threshold(x.w, levels = (min.level):(x.w$nlevels - 1), policy = "manual", value = thresh, type = "hard")
-    x.w.t.r <- AvBasis(convert(x.w.t))
-    return(x.w.t.r)
-}
-
-
-waveti.var=function (x, sigma=NULL, filter.number = 8, family = "DaubLeAsymm", min.level = 3) 
-{
-    n <- length(x)
-    J <- log2(n)
-    if(length(sigma)==1) sigma <- rep(sigma,n)
-    x.w <- wd(x, filter.number, family, type = "station")
-    if(is.null(sigma)){
-      win.size <- round(n/10)
-      odd.boo <- (win.size%%2==1)
-      win.size <- win.size+(1-odd.boo)
-      sigma <- runmad(accessD(x.w,J-1),win.size,endrule="func")
-    }
-    x.w.v <- wd.var(sigma^2, filter.number, family,type='station')
-    x.w.t <- threshold.wd.var(x.w, x.w.v, levels = (min.level):(J-1))
-    x.w.t.r <- AvBasis(convert(x.w.t))
[…]

### 2016-02-15 simulation_1d_g/tests/inter.R

@@ -1,16 +1,0 @@
-inter.samp=function(x,y,nn){
-  n=length(x)
-  xmax=max(x)
-  xmin=min(x)
-  xgrid.old=c(0,(x-xmin)*(n-1)/(xmax-xmin)+1,n+1)
-  mgrid=(xgrid.old[1:(n+1)]+xgrid.old[2:(n+2)])/2
-  mgrid.l=mgrid[1:n]
-  mgrid.u=mgrid[2:(n+1)]
-  delta=n/nn
-  xgrid.new=0.5+(1:nn-0.5)*delta
-  y.new=0
-  for(i in 1:nn){
-    y.new[i]=y[xgrid.new[i]>=mgrid.l&xgrid.new[i]<mgrid.u]
-  }
-  return(list(x=xgrid.new,y=y.new))
-}

### 2016-02-15 simulation_1d_g/tests/variance_test.R

@@ -1,153 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=2^12
-t=1:n/n
-mu.s=spike.f(t)
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-#mu.sine=3/4*sin(40*pi*t)
-mu.sine=sin(20*t)
-var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
-var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
-var4=3.4*(2+mu.dop)
-var3=mu.b
-var5=(t-0.5)^2+0.5
-var6=exp(-100*(t-0.5)^2)
-var7=0.5+1.5*mu.s
-sigma.t=sqrt(var3)
-#sigma.t=seq(2,10,length.out=n)
-#sigma.t=rep(2,n)
-l2norm=function(x) sum(x^2)
-mise=function(x,y) l2norm(x-y)/l2norm(y)
-mse=function(x,y) mean((x-y)^2)
-mu.s0=100
-set.seed(1121)
-X.s=rnorm(n,0,sigma.t)
-set.seed(1121)
-X.s=matrix(rnorm(100*n,5*mu.sine,sigma.t),nrow=100,byrow=TRUE)
-
[…]

### 2016-02-15 simulation_1d_g/threshold_var.R

@@ -1,33 +1,0 @@
-threshold.var <- function (x.w, x.w.v, levels, type = "hard")
-{
-    d <- NULL
-    n <- 2^nlevelsWT(x.w)
-    J <- nlevelsWT(x.w)
-    nthresh <- length(levels)
-    thresh <- list(0)
-    for (i in 1:nthresh) {
-        d <- accessD(x.w,level=levels[i])
-        ind <- (((J-1)-levels[i])*n+1):((J-levels[i])*n)
-        noise.level <- sqrt(x.w.v[ind])
-        nd <- length(d)
-        thresh[[i]] <- sqrt(2*log(nd*log2(nd))) * noise.level
-    }
-    for (i in 1:nthresh) {
-        d <- accessD(x.w,level=levels[i])
-        if (type == "hard") {
-            d[abs(d) <= thresh[[i]]] <- 0
-        }
-        else if (type == "soft") {
-            d <- (d * (abs(d) - thresh[[i]]) * (abs(d) > thresh[[i]]))/abs(d)
-            d[is.na(d)] <- 0
-        }
-        x.w=putD(x.w,level=levels[i],v=d)
-    }
-    return(x.w)
-}
-
-
-
-
-
-

### 2016-02-15 simulation_1d_g/wip/1d_sim_g.R

@@ -1,411 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=1024
-t=1:n/n
-
-mu.s=spike.f(t)
-
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-
-mu.b0=2
-set.seed(415)
-#X.b=rnorm(n,mu.b0*(mu.b),sigma.t)
-X.b=rnorm(n,(mu.b/max(mu.b)),sigma.t)
-
-
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-mu.dop=3/(max(mu.dop)-min(mu.dop))*(mu.dop-min(mu.dop))
-
-sig=((2*t + 0.5)*(t <= 0.15)) + 
-       ((-12*(t-0.15) + 0.8)*(t > 0.15 & t <= 0.2)) + 
-       0.2*(t > 0.2 & t <= 0.5) + 
-       ((6*(t - 0.5) + 0.2)*(t > 0.5 & t <= 0.6)) + 
-       ((-10*(t - 0.6) + 0.8)*(t > 0.6 & t <= 0.65)) + 
-       ((-0.5*(t - 0.65) + 0.3)*(t > 0.65 & t <= 0.85)) + 
-       ((2*(t - 0.85) + 0.2)*(t > 0.85))
-mu.ang = 3/5*((5/(max(sig)-min(sig)))*sig - 1.6)-0.0419569
-
-
-
-heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99 / 3.366185
[…]

### 2016-02-15 simulation_1d_g/wip/bayesmooth_log.R

@@ -1,444 +1,0 @@
-source("../Rcode/wd_var.R")
-library(wavethresh)
-require(ashr)
-require(Rcpp)
-require(inline)
-
-
-#interleave two vectors
-interleave=function(x,y){
-  return(as.vector(rbind(x,y)))
-}
-
-
-#shift a vector right and left respectively
-rshift = function(x){L=length(x); return(c(x[L],x[-L]))}
-lshift = function(x){return(c(x[-1],x[1]))}
-
-
-#The following produces both a TItable,
-#and a "parent" table whose pairwise comparisons would be used to create a TI table
-#So, for example, in the ith row, elements 1, 2 would be the parents of the
-#first element in the (i+1)the row of the TI table
-# INPUT: sig, an n vector of Poisson counts at n locations
-# OUTPUT: a list, with elements
-# TItable - the usual TI table
-# parent - the parent values used to make the TI table
-titable=function(sig){
-  n = length(sig)
-  J = log2(n)
-  
-# Create decomposition table of signal, using pairwise sums,
-# keeping just the values that are *not* redundant under the
-# shift-invariant scheme.  This is very similar to TI-tables
-# in Donoho and Coifman's TI-denoising framework.
-  dmat = matrix(0, nrow=J+1, ncol=n)
-  ddmat = matrix(0, nrow=J+1, ncol=n)
-  dmat[1,] = sig
-  ddmat[1,] = sig
-
-  #dmat[1,] = as.matrix(sig)  
-  #dmat2 = matrix(0, nrow=J, ncol=2*n) #the parent table
-  
-  for(D in 0:(J-1)){
-    nD = 2^(J-D); 
-    nDo2 = nD/2;
-    twonD = 2*nD;
-    for(l in 0:(2^D-1)){
-      ind = (l*nD+1):((l+1)*nD)
-      #ind2 = (l*twonD+1):((l+1)*twonD)
-      x = dmat[D+1,ind]
-      lsumx = x[seq(from=1,to=nD-1, by=2)] + x[seq(from=2,to=nD,by=2)]
-      ldiffx = x[seq(from=1,to=nD-1, by=2)] - x[seq(from=2,to=nD,by=2)]
-      rx = rshift(x);
-      rsumx = rx[seq(from=1,to=nD-1, by=2)] + rx[seq(from=2,to=nD,by=2)]
[…]

### 2016-02-15 simulation_1d_g/wip/s8_debug.R

@@ -1,56 +1,0 @@
-source("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wip/s8_comp.R")
-source("D:/Grad School/Spring 2013/multiscale_ash/ash/bayesmooth.R")
-
-
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=1024
-t=1:n/n
-
-mu.s=spike.f(t)
-
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-
-
-rsnr=sqrt(3)
-mu.t=(1+mu.b)/5
-var2=(0.01+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
-sigma.ini=sqrt(var2)
-sigma.t=sigma.ini/mean(sigma.ini)*sd(mu.t)/rsnr^2
-
-x=rnorm(n,mu.t,sigma.t)
-
-mse=function(x,y) mean((x-y)^2)
-l2norm=function(x) sum(x^2)
-mise=function(x,y) 10000*mean(apply(x-rep(1,100)%o%y,1,l2norm)/l2norm(y))
-
-
-system.time(mu.true.s8<-bayesmooth(x,sigma.t,basis="symm8",gridmult=0))
-system.time(mu.true.haar<-bayesmooth(x,sigma.t,gridmult=0))
-
-system.time(mu.est.s8<-bayesmooth(x,basis="symm8",gridmult=0))
-system.time(mu.est.haar<-bayesmooth(x,gridmult=0))
-
-
-mse(mu.true.s8,mu.t)
-mse(mu.true.haar,mu.t)
-mse(mu.est.s8,mu.t)
[…]

### 2016-02-15 simulation_1d_g/wip/test_vash_debug.R

@@ -1,35 +1,0 @@
-x=X.s
-
-  n = length(x)
-  J = log2(n)
-
-  wmean = matrix(0,J,n) 
-
-    var.est=(x-mu.t)^2
-
-    vtable=cxxtitable(2/3*var.est^2)$sumtable
-    vdtable=cxxtitable(var.est)$difftable
-    vrtable=cxxtirtable(var.est)
-    fac1=c(3,2,1.5)
-    fac2=c(2,1.5,1)
-    #fac1=rep(1,3)
-    #fac2=rep(1,3)
-j=10
-
-      if(j>=0&j<=1){
-        virtable=vrtable[j+2,]
-        virtable=fac1[1]*(abs(virtable)>=log(4))+fac1[2]*(abs(virtable)>=log(2)&abs(virtable)<log(4))+fac1[3]*(abs(virtable)<log(2))
-      }else if(j>=2&j<=5){
-        virtable=vrtable[j+2,]
-        virtable=fac2[1]*(abs(virtable)>=log(4))+fac2[2]*(abs(virtable)>=log(2)&abs(virtable)<log(4))+fac2[3]*(abs(virtable)<log(2))
-      }else{
-        virtable=1
-      }
-      vt=vash(vtable[j+2,],10)$PosteriorMean
-
-
-plot(vt,vtable[j+2,]/virtable)
-abline(0,1,lty=2)
-
-plot(vt,vtable[j+2,],xlim=c(6000,18000))
-abline(0,1,lty=2)

### 2016-02-15 simulation_1d_g/wip/testing_log.R

@@ -1,45 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=2^12
-t=1:n/n
-mu.s=spike.f(t)
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-#mu.sine=3/4*sin(40*pi*t)
-mu.sine=sin(20*t)
-var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
-var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
-var4=3.4*(2+mu.dop)
-var3=mu.b
-var5=(t-0.5)^2+0.5
-var6=exp(-100*(t-0.5)^2)
-var7=0.5+1.5*mu.s
-sigma.t=sqrt(var2)
-l2norm=function(x) sum(x^2)
-mise=function(x,y) l2norm(x-y)/l2norm(y)
-mse=function(x,y) mean((x-y)^2)
-mu.s0=100
-set.seed(1121)
-X.s=rnorm(n,0,sigma.t)
-set.seed(1121)
-
-
-
-source(file.path("D:/Grad School/Spring 2013/multiscale_ash/simulation_1d_g/wip/bayesmooth_cur.R"))
[…]

### 2016-02-15 simulation_1d_g/wip/variance_test.R

@@ -1,143 +1,0 @@
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-n=2^12
-t=1:n/n
-mu.s=spike.f(t)
-pos = c(.1, .13, .15, .23, .25, .40, .44, .65, .76, .78, .81)
-hgt = c(2, 3.6, 2, 5, 7.5, 6.9, 2, 4.8, 2, 4.1, 2.3)
-wth = c(.005, .005, .006, .01, .01, .03, .01, .01, .005, .008, .005)
-mu.b = rep(0,n)
-for(j in 1:length(pos)){
-  mu.b = mu.b + hgt[j]/(( 1 + (abs(t - pos[j])/wth[j]))^4)
-}
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.dop=dop.f(t)
-#mu.sine=3/4*sin(40*pi*t)
-mu.sine=sin(20*t)
-var1=1.42*((3-20*t)*(t>=0&t<0.1)+(20*t-1)*(t>=0.1&t<0.25)+(4+(1-4*t)*18/19)*(t>=0.25&t<0.725)+(2.2+10*(t-0.725))*(t>=0.725&t<0.89)+(3.85-85*(t-0.89)/11)*(t>=0.89&t<=1))
-var2=(1+4*(exp(-550*(t-0.2)^2)+exp(-200*(t-0.5)^2)+exp(-950*(t-0.8)^2)))/1.35
-var4=3.4*(2+mu.dop)
-var3=mu.b
-var5=(t-0.5)^2+0.5
-var6=exp(-100*(t-0.5)^2)
-var7=0.5+1.5*mu.s
-sigma.t=sqrt(var3)
-#sigma.t=seq(2,10,length.out=n)
-#sigma.t=rep(2,n)
-l2norm=function(x) sum(x^2)
-mise=function(x,y) l2norm(x-y)/l2norm(y)
-mse=function(x,y) mean((x-y)^2)
-mu.s0=100
-set.seed(1121)
-X.s=rnorm(n,0,sigma.t)
-set.seed(1121)
-X.s=matrix(rnorm(100*n,5*mu.sine,sigma.t),nrow=100,byrow=TRUE)
-
[…]

### 2016-02-15 simulation_1d_p/method_comp_remote.R

@@ -1,776 +1,0 @@
-library(haarfisz)
-
-##generate signal
-mse=function(x,y) mean((x-y)^2)
-l2norm=function(x) sum(x^2)
-mise=function(x,y) 10000*mean(apply(x-matrix(rep(y,times=100),nrow=100,byrow=T),1,l2norm)/l2norm(y))
-
-n=1024
-t=1:n/n
-
-spike.f=function(x) (0.75*exp(-500*(x-0.23)^2)+1.5*exp(-2000*(x-0.33)^2)+3*exp(-8000*(x-0.47)^2)+2.25*exp(-16000*(x-0.69)^2)+0.5*exp(-32000*(x-0.83)^2))
-mu.s=spike.f(t)
-
-dop.f=function(x) sqrt(x*(1-x))*sin((2*pi*1.05)/(x+0.05))
-mu.ang=dop.f(t)
-
-sig=((2*t + 0.5)*(t <= 0.15)) + 
-       ((-12*(t-0.15) + 0.8)*(t > 0.15 & t <= 0.2)) + 
-       0.2*(t > 0.2 & t <= 0.5) + 
-       ((6*(t - 0.5) + 0.2)*(t > 0.5 & t <= 0.6)) + 
-       ((-10*(t - 0.6) + 0.8)*(t > 0.6 & t <= 0.65)) + 
-       ((-0.5*(t - 0.65) + 0.3)*(t > 0.65 & t <= 0.85)) + 
-       ((2*(t - 0.85) + 0.2)*(t > 0.85))
-mu.ang = 3/5*((5/(max(sig)-min(sig)))*sig - 1.6)-0.0419569
-
-
-heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99 / 3.366185
-mu.hs = mu.hs - min(mu.hs)
-
-I_1 = exp(-(abs(t-0.2)/0.01)^1.2)*(t<=0.2) + exp(-(abs(t-0.2)/0.03)^1.2)*(t>0.2);
-I_2 = exp(-(abs(t-0.3)/0.01)^1.2)*(t<=0.3) + exp(-(abs(t-0.3)/0.03)^1.2)*(t>0.3);
[…]

### 2016-02-15 paper/draft_6.tex
added new files

--- 2016-02-09 paper/draft_5.tex
@@
 Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, are uncommon, particularly compared with the well-studied homoskedastic case.
-Previous non-wavelet-based work includes \cite{Fan1998Efficient}, who estimated the variance by smoothing the squared residuals using local polynomial smoothing, and \cite{Brown2007Variance} who employed difference-based kernel estimators.
+Previous non-wavelet-based work includes \cite{Fan1998Efficient}, who estimated the variance by smoothing the squared residuals using local polynomial smoothing, \cite{Brown2007Variance}, who employed difference-based kernel estimators, and \cite{Menictas2015Variational}, who developed a Bayesian mean field variational methodology for both mean and variance estimation.
 The only wavelet-based method for variance estimation we have found is \cite{Cai2008Adaptive}, which applied a wavelet thresholding approach to first order differences.
-Unfortunately none of these methods have available software implementations.
-(WAND'S WORK?)
+Unfortunately software implementation is only available in \cite{Menictas2015Variational}.
 
@@
 \ash~allows more flexibility in the underlying distribution $g$ than the Laplace or spike-and-slab
-distributions used in \cite{Johnstone2005Empirical, Clyde2000Flexible}; second \ash~allows for variations in precision in the transformed observations (e.g.
+distributions used in \cite{Johnstone2005Empirical, Clyde2000Flexible}; second, \ash~allows for variations in precision in the transformed observations (e.g.
 wavelet coefficients).
@@
 from a circle, rather than a line, and averages results over all $T$ possible rotations of the data.
-Although not always necessary, this is a standard trick to reduce artifacts that can occur near discontinuities in the underlying signal (see eg.
-Coifman \& Donoho (1995)).
+Although not always necessary, this is a standard trick to reduce artifacts that can occur near discontinuities in the underlying signal (eg.
+\cite{Coifman1995Translationinvariant}).
 %COMMENT: WHat about reflection before doing this? ans: all the test fns are periodic
@@
 a different distribution $g$ for the $(\tmu_j)$ is estimated for each resolution. This is the usual way that
-EB approaches are applied in this context (e.g.~\cite{checkcgandjs}) and indeed is crucial because
+EB approaches are applied in this context (e.g.~\cite{Johnstone2005Empirical}) and indeed is crucial because
 the underlying distribution $g$  will vary with resolution (because smoothness of $\bmu$ will vary with resolution).  
-\item Although we have presented the wavelet transform as a matrix multiplication, which is an $o(T^2)$ operation, in practice both the wavelet transform and the inverse tranform are implemented using
-efficient algorithms \cite{beylkin.92,coifman.donoho.94}, implemented in the {\tt wavethresh} package \cite{}, taking only $O(T\log T)$ operations. 
+\item Although we have presented the wavelet transform as a matrix multiplication, which is an $o(T^2)$ operation, in practice both the wavelet transform and the inverse transform are implemented using
+efficient algorithms \cite{Beylkin1992Ontherepresentation,Coifman1995Translationinvariant}, implemented in the {\tt wavethresh} package \cite{Nason_wavethresh}, taking only $O(T\log T)$ operations. 
 \end{itemize}
@@
 \end{equation}
-(with $Y_0:=Y_T$.
+with $Y_0:=Y_T$.
 Here we make the more flexible assumption that the variance function is spatially structured, and use wavelet shrinkage to estimate it.
-Our approach is similar in spirit to \cite{cai.wang}, but we jointly estimate the mean and variance functions whereas they estimate only the variance function.
+Our approach is similar in spirit to \cite{Cai2008Adaptive}, but we jointly estimate the mean and variance functions whereas they estimate only the variance function.
 
@@
 To extend this to $T=4$, introduce the notation $v_{i:j}$ to denote, for any vector $v$, 
-the sum $\sum_{t=i}^{t=j} v_t$.  Then 
+the sum $\sum_{t=i}^j v_t$.  Then 
 \begin{align} 
@@
 Thus estimating a spatially-structured $\bmu$ can be achieved by shrinkage estimation of $\bp$, with shrinkage towards $p_j=0.5$.
-Both \cite{Nowak2000Statistical} and \cite{Timmermann1999Multiscale} use purpose-built Bayesian models to
+Both \cite{kolaczyk1999wavelet} and \cite{Timmermann1999Multiscale} use purpose-built Bayesian models to
 achieve this shrinkage, by introducing a prior distribution on elements of $\bp$ that is
@@
 \cite{Gart1967Bias}).
-The main challenge is in dealing satisfactorily with cases where the mle for $\alpha_j$ is infinite.
+The main challenge is in dealing satisfactorily with cases where the maximum likelihood estimator (MLE) for $\alpha_j$ is infinite.
 Our choice of estimates, based on results from \cite{Gart1967Bias}, are described in Appendix \ref{}.
@@
 The resulting estimate of $\mu_t$ would be the exponential of the posterior
-mean for $\log(\mu_t)$ (because each $\log_(\mu_t)$ is a linear combination of $\alpha_j$). [IS THIS TRUE?]
-An alternative is to estimate the posterior mean using the Delta method; see Appendix \ref{app:reconstruction}.
-
-%(For example, to go to $T=8$, we have $Y_{1:8} \sim Poi(\mu_{1:8})$, $Y_{1:4} | Y_{1:8} \sim \Bin(Y_{1:8}, \mu_{1:4}/\mu_{1:8})$, and then (\ref{eqn:y12})-(\ref{eqn:y3}) and their analogues replacing indices 1-4 with 5-8.)
-
+mean for $\log(\mu_t)$ (because each $\log(\mu_t)$ is a linear combination of $\alpha_j$).
+Alternatively we can estimate $\mu_t$ by approximating its posterior mean using the Delta method; see Appendix \ref{app:reconstruction}.
+Both methods are implemented in our software; for the results here we use the latter method 
+to be more comparable with previous approaches that estimate $\mu$ on the raw scale rather than $\log$ scale.
 %Note that, just as for the original parameterization $Y_j \sim \Poi(\mu_j)$, the likelihood for the parameters in this reparameterization factorizes into a product of four terms, one for each parameter, corresponding to the four distributions (\ref{eqn:y14})-(\ref{eqn:y3}).
@@
 datasets that appear consistent with a smooth signal.
-
-\subsection{Simulations}
-We now seek to validate the advantages of our method, named ``SMASH'', via simulation studies.
-To thoroughly investigate the performance of SMASH, we consider the Gaussian and Poisson cases separately.
-
-For the Gaussian case, we focus our attention mostly on mean estimation.
-Different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions were considered, to ensure that SMASH behaves well in a variety of settings.
-However, only a small portion of the results will be shown here to highlight key findings from the rather extensive simulation study.
-Full results from the study can be found in the Supplementary Materials.
 
@@
 
-To demonstrate the robustness of SMASH, we now consider only homoskedastic errors.
-Due to the large number of methods available in the literature for this setting, we chose only a subset.
-The methods we considered in our simulation are discussed in detail in \cite{Antoniadis2001Wavelet}, and in particular Translation Invariant (TI) thresholding by \cite{Coifman1995Translationinvariant} performed the best for most of the test signals, where performance is measured by mean squared error (MSE).
-We also considered the popular Empirical Bayes shrinkage procedure by \cite{Johnstone2005Empirical}, called Ebayesthresh.
+\subsection{Simulations}
+
+We conducted extensive simulation studies to compare the performance of our method with existing approaches.
+
+For the Gaussian case, we focus on mean estimation, initially with homoskedastic errors. We modelled our simulation study after
+\cite{Antoniadis2001Wavelet}, using many of the same test functions, a variety of sample sizes, two different signal to noise ratios (SNRs), and including
+the best-performing methods from their comparison.
+In particular Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE).
+We also considered the popular Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
 Figure \ref{fig:gaus_homo} compares the mean integrated squared errors (MISEs) of TI-thresholding and Ebayesthresh to SMASH with two different options for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024.
-The default option in SMASH estimates the mean without any homoskedastic assumptions on the variance function, while the second options estimates the mean given the true variance function.
+The default version of SMASH estimates the mean without any homoskedastic assumptions on the variance function, while the other version of SMASH estimates the mean given the true variance function.
 We can clearly see that the performance of SMASH is not impacted by the lack of homoskedastic assumptions imposed on the variance function: it outperforms two of the most accurate wavelet denoising algorithms for i.i.d.
@@
 These results also extend to other mean functions, SNRs and sample sizes (see Supplementary Materials for more details).
+ Different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions were considered, to ensure that SMASH behaves well in a variety of settings.
+However, only a small portion of the results will be shown here to highlight key findings from the extensive simulation study.
+Full results from the study can be found in the Supplementary Materials.
+
+We focus initially on estimation of a Gaussian mean with homoskedastic errors. Due to the large number of methods available in the literature for this setting, we chose only a subset.
 
@@
 Having shown that SMASH performs well in the homoskedastic case without any explicit assumptions on the Gaussian noise, we now demonstrate its performance gain when the errors are heteroskedastic.
-For the sake of presentation, figure \ref{fig:gaus_hetero} highlights only the results from SMASH, TI-thresh (with various choices of variance estimation) and EbayesThresh for just two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024.
+For the sake of presentation, Figure \ref{fig:gaus_hetero} highlights only the results from SMASH, TI-thresh (with various choices of variance estimation) and EbayesThresh for just two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024.
 Nevertheless, similar results hold in general for different mean and variance functions, SNRs, and sample sizes (see Supplementary Materials for more details).
@@
 
-It should also be noted that providing the true variance to SMASH does not result in substantial gains compared to the case when SMASH estimates its own variance function for most of the test functions (results shown in the supplementary materials).
+It should also be noted that providing the true variance to SMASH does not result in substantial gains compared to the case when SMASH estimates its own variance function for most of the test functions (results shown in the Supplementary Materials).
 Hence, we can reasonably assume that SMASH does a good job of variance estimation, although this claim relies heavily on the variance function at hand.
-For example, the Bumps variance function (see appendix ?) is extremely difficult to estimate, and SMASH will perform much better when provided with the true variance function.
+For example, the Bumps variance function (see Appendix ??) is extremely difficult to estimate, and SMASH will perform much better when provided with the true variance function.
 
@@
     \end{subfigure}
-    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.}
+    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.
+These functions correspond to mean and standard deviation functions (A) from \cite{Menictas2015Variational}.}
     \label{fig:mfvb_fn}
@@
 Since the data points are not evenly spaced, we took the simplest approach and applied our method treating the observations as if they were evenly spaced.
-This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (see eg.
+This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (eg.
 \cite{Sardy1999Wavelet}).
 Evaluation of MSE at the 201 equally spaced points is then based on simple linear interpolation between the estimated points.
-Tables \ref{table:mfvb_comp} display the MSEs over 100 independent runs for each scenario.
+Table \ref{table:mfvb_comp} displays the MSEs over 100 independent runs for each scenario.
 \begin{table}[ht]
@@
 \end{tabular}
-\caption{MSEs of MFVB and SMASH for two simulation scenarios}
+\caption{Compares the performance (in MSE) of SMASH and MFVB for two simulation scenarios, with the mean and variance functions as shown in \ref{fig:mfvb_fn}.
+SMASH is comparable to MFVB in mean estimation and outperforms the latter in variance estimation in Scenario 1, where the data are not equally spaced and not a power of 2.
+SMASH outperforms MFVB in both mean and variance estimation in Scenario 2, where the data are equally spaced and a power of 2.}
 \label{table:mfvb_comp}
@@
 The low intensities are of primary interest in genomic applications, and so we focus our attention to these.
-Complete results, including a (min,max) intensity of (1/128, 128), are included in appendix \textcolor{red}{where?}.
-From figure \ref{fig:pois_sim}, it is clear that SMASH outperforms both methods, and the claim holds true in general.
+Complete results, including a (min,max) intensity of (1/128, 128), are included in Supplementary Materials.
+It is clear from Figure \ref{fig:pois_sim} that SMASH outperforms both methods, and the claim holds true in general.
 As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asmyptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
@@
 On the other hand, SMASH outperforms BMSM consistently, even though our method is based on the same likelihood factorization used in the latter.
-We can thus conclude that the choice of ASH as the shrinkage procedure (with the necessary likelihood approximations) is superior to that used in BMSM.
+We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM.
 More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
@@
     \end{subfigure}
-    \caption{Violin plots of MISEs for various methods. a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8)}
+    \caption{Compares various approaches for denoising Poisson data for the ``Bursts'' test function where a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).
+Violin plots of MISEs for (from bottom to top) SMASH, BMSM and Haar-Fisz are shown in the figure.
+Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
+We note the performance gain of SMASH over both BMSM and Haar-Fisz.}
     \label{fig:pois_sim}
@@
     \includegraphics[width=0.65\textwidth]{motorcycle.pdf}
-    \caption{}
+    \caption{Results from fitting SMASH to the motorcycle acceleration data discussed in \cite{silverman1985some}.
+Both the mean curve (solid black line) and the variance around the mean curve (dashed red line) are shown.
+We note that SMASH does a good job of capturing both the mean as well as the variation in the data without requiring and parameter tuning.}
     \label{fig:motorcycle}
@@
 We first apply the Gaussian version of SMASH on the well known motorcycle acceleration dataset from \cite{silverman1985some}.
-The data consists of 133 observations measuring head acceleration in a simulated motorcycle accident that is used to test crash helmets.
+The data consists of 133 observations measuring head acceleration in a simulated motorcycle accident which is used to test crash helmets.
 The dependent variable is $acceleration$ (in $g$), and the independent variable is $time$ (in ms).
@@
 \subsection{ChIP-Seq Data}
-Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly seen in the field of genomics.
+Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly used in the field of genomics.
 Specifically, we chose an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute.
@@
 %In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
-To ensure that our method performs sensibly, we pooled the reads for the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region.
+To ensure that our method performs sensibly, we pooled the reads for just the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region.
 The results are shown in Figure \ref{fig:seq_peak}.\\
@@
         \centering
-        \includegraphics[width=\textwidth]{peaks_comp_a.pdf}
+        \includegraphics[width=\textwidth]{peaks_comp_a.png}
         \caption{}
@@
     \end{subfigure}
-    \caption{Analysis of reads taken from the GM12878 cell line, spanning positions 880001 to 1011072 on chromosome 1.
-(a) Raw sequencing counts.
-(b) Estimated intensity function from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).}
+    \caption{Analysis of next-generation sequencing data from the ENCODE project, corresponding to sequencing reads from the GM12878 cell line and spanning positions 880001 to 1011072 on chromosome 1.
+(a) plots the actual sequencing counts (summed across both replicates).
+A rough signal can be visualized by looking at darker regions of the plot, which correspond to higher concentrations of data points.
+(b) plots the estimated intensity function obtained from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).
+We can observe not only the location of the peaks from the SMASH estimate (which MACS does provide), but also the amplitude of the signals, something which MACS fails to reveal.
+The plot also reveal weak signals that MACS fail to capture, but of interest nonetheless.}
     \label{fig:seq_peak}
 \end{figure}
-From Figure \ref{fig:seq_peak_est} it is clear that SMASH can recognize the peaks detected by MACS.
+From Figure \ref{fig:seq_peak_est} it is clear that SMASH also captures the peaks detected by MACS.
 Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.

### 2016-02-15 code_paper/gaus_data/delouille/ethanol.R

@@ -1,0 +1,27 @@
+library(smash)
+library(lattice)
+
+x.ini = sort(ethanol$E)
+y.ini = ethanol$NOx[order(ethanol$E)]
+
+x = unique(x.ini)
+y = 0
+for(i in 1:length(x)){
+  y[i] = median(y.ini[x.ini == x[i]])
+}
+
+
+y.exp=c(y,y[length(y):(2*length(y)-128+1)])
+y.final = c(y.exp, y.exp[length(y.exp):1])
+
+
+y.var.est=ashsmooth.gaus(y.final,v.est=TRUE)
+
+y.var.est=y.var.est[1:length(y)]
+
+plot(x,y,ylim=c(-1,5))
+lines(x,y.est,col=2)
+plot(x,y.var.est,type='l')
+
+
+

### 2016-02-15 code_paper/gaus_data/treas_bill/analysis.R

@@ -1,0 +1,108 @@
+data=read.csv("D:/Grad School/Spring 2013/multiscale_ash/gaus_data/treas_bill/treas_bill_ave.csv",header=FALSE)
+data=as.numeric(data[,1])
+
+
+library(smash)
+
+
+y=ar(data,FALSE,5)$res
+y=y[!is.na(y)]
+x=sort(data[5:(length(data)-1)])
+y=y[order(data[5:(length(data)-1)])]
+
+
+#coef=c(1.0733,-0.0423,0.0165,0.0228,-0.0773)
+
+resid.comp=function(data,coef){
+  smean=mean(data)
+  ord=length(coef)
+  res=NULL
+  for(i in (length(coef)+1):length(data)){
+    res[i-ord]=(data[i]-smean)-(sum(coef*(data[(i-1):(i-ord)]-smean)))
+  }
+  return(res)
+}
+
+#y=resid.comp(data,coef)
+#x=sort(data[5:(length(data)-1)])
+#y=y[order(data[5:(length(data)-1)])]
+
+
+plot(x,y)
+
+
+####
+xmin=min(x)
+xmax=max(x)
+
+bin.size=(xmax-xmin)/32
+x.seq=seq(xmin,xmax,bin.size)
+x.seq.l=x.seq[1:32]
+x.seq.u=x.seq[2:33]
+y.agg=0
+for(i in 1:32){
+  y.agg[i]=y[x>=x.seq.l[i]&x<x.seq.u[i]]
+}
+y.agg[1024]=y[x>=x.seq.l[1024]&x<=x.seq.u[1024]]
+
+y.approx=approx(x,y,n=1024,method='constant',rule=2)$y
+x.approx=approx(x,y,n=1024,method='constant',rule=2)$x
+
+lines(x.approx,y.approx,col=2)
+y.est.approx=bayesmooth(y.approx)
+y.est.var.approx=bayesmooth(y.approx,v.est=TRUE)
+
+plot(x,y)
+lines(x.approx,y.est.approx,col=2)
+####
+
+x.mod=unique(x)
+y.mod=0
+for(i in 1:length(x.mod)){
+  y.mod[i]=median(y[x==x.mod[i]])
+}
+
+
+y.exp=c(y.mod,y.mod[length(y.mod):(2*length(y.mod)-2^10+1)])
+y.final=c(y.exp,y.exp[length(y.exp):1])
+
[…]

### 2016-02-15 code_paper/sim/plot_pois.R

@@ -1,0 +1,39 @@
+#This script produces the plots for the Poisson simulations in the paper
+
+library(vioplot)
+source("code_paper/sim/vioplot_col.R")
+load("res_paper/res_pois.RData")
+
+
+mise.hf.ti.r.bur.1 = colMeans(matrix(c(mise.hf.ti.r.4.bur.1, mise.hf.ti.r.5.bur.1, mise.hf.ti.r.6.bur.1, mise.hf.ti.r.7.bur.1), byrow = TRUE, nr = 4))
+mise.hf.ti.r.bur.8 = colMeans(matrix(c(mise.hf.ti.r.4.bur.8, mise.hf.ti.r.5.bur.8, mise.hf.ti.r.6.bur.8, mise.hf.ti.r.7.bur.8), byrow = TRUE, nr = 4))
+
+# #vertical
+# pdf("paper/violin_pois_1.pdf", height = 8, width = 12)
+# par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 6.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
+# vioplot.col(mise.ash.bur.1, mise.BMSM.bur.1, mise.hf.ti.r.bur.1, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+# title(xlab = "Method", ylab = "MISE", line = 4)
+# abline(h = median(mise.ash.bur.1), lty = 3, col = 3)
+# dev.off()
+# 
+# pdf("paper/violin_pois_8.pdf", height = 8, width = 12)
+# par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 6.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
+# vioplot.col(mise.ash.bur.8, mise.BMSM.bur.8, mise.hf.ti.r.bur.8, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+# title(xlab = "Method", ylab = "MISE", line = 4)
+# abline(h = median(mise.ash.bur.8), lty = 3, col = 3)
+# dev.off()
+
+#horizontal
+pdf("paper/violin_pois_1.pdf", height = 8, width = 8)
+par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
[…]

### 2016-02-15 code_paper/sim/table_gaus.R

@@ -1,0 +1,254 @@
+#This script produces supplementary tables for Gaussian simulations
+
+
+library(xtable)
+
+load("res_paper/res_gaus_dscr.RData")
+
+scale.baseline = function(x) x/x[1]
+
+mise.res = aggregate(mise ~ method + scenario, res, mean)
+table.order = c(6, 10, 16, 18, 8, 3, 5, 13, 14, 12, 20)
+colname.order = c(7, 4, 3, 1, 6, 2, 5)
+
+tex.row.names = c("SMASH, joint, Haar",
+                  "SMASH, joint, Symm8",
+                  "TI-thresh, RMAD, Symm8",
+                  "TI-thresh, SMASH, Symm8",
+                  "SMASH, homo, Symm8",
+                  "Ebayes, homo, Symm8",
+                  "PostMean, homo, Symm8",
+                  "SURE, homo, Symm8",
+                  "TI-thresh, homo, Symm8",
+                  "SMASH, truth, Symm8",
+                  "TI-thresh, truth, Symm8"
+)
+
+tex.col.names = c("Spikes", "Bumps", "Block", "Angles", "Doppler", "Blip", "Corner")
+
+library(AlgDesign)
+
+rsnr=sqrt(c(1,3))
+varfn=1:5
+
+design=gen.factorial(c(length(rsnr),length(varfn)),center=FALSE)
+
+for(i in 1:dim(design)[1]){
+  table.suffix = paste0(".",rsnr[design[i,1]]^2,".","v",varfn[design[i,2]])  
+  
+  name.ind = grep(paste0("*",table.suffix), mise.res$scenario)
+  table.temp = matrix(mise.res[name.ind, 3], 20, 7)
+  table.temp = table.temp[table.order, colname.order]
+  table.temp = apply(table.temp, 2, scale.baseline)
+  
+  rownames(table.temp) = tex.row.names
+  colnames(table.temp) = tex.col.names
+  
+  assign(paste0("table",table.suffix),table.temp)
+}
+
+ndigits=2
+
+edit.smallest = function(x){
+  x[which(x == min(x))] = paste0(min(x), "(*)")
+  return(x)
+}
+
+
+mark.smallest = function(table, ndigits){
+  table = apply(table, 2, sprintf, fmt = paste0("%.", ndigits, "f"))
+  table = apply(table, 2, edit.smallest)
+  return(table)
+}
+
+
[…]

### 2016-02-15 code_paper/sim/table_pois.R

@@ -1,0 +1,124 @@
+#This script produces supplementary tables for Poisson simulations
+
+library(xtable)
+
+load("res_paper/res_pois.RData")
+
+scale.baseline = function(x) x/x[1]
+
+tex.row.names=c("SMASH",
+                "BMSM",
+                "BMMIM",
+                "Haar-Fisz",
+                "Anscombe, universal",
+                "Haar thresholds"
+)
+
+tex.col.names=c("(0.01,3)","(1/8,8)","(1/128,128)")
+
+
+# mise.s.1.table=mise.s.1[c(1,4,8,7,9,5,3,2)]
+# mise.s.8.table=mise.s.8[c(1,4,8,7,9,5,3,2)]
+# mise.s.128.table=mise.s.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.ang.1.table=mise.ang.1[c(1,4,8,7,9,5,3,2)]
+# mise.ang.8.table=mise.ang.8[c(1,4,8,7,9,5,3,2)]
+# mise.ang.128.table=mise.ang.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.bur.1.table=mise.bur.1[c(1,4,8,7,9,5,3,2)]
+# mise.bur.8.table=mise.bur.8[c(1,4,8,7,9,5,3,2)]
+# mise.bur.128.table=mise.bur.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.cb.1.table=mise.cb.1[c(1,4,8,7,9,5,3,2)]
+# mise.cb.8.table=mise.cb.8[c(1,4,8,7,9,5,3,2)]
+# mise.cb.128.table=mise.cb.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.b.1.table=mise.b.1[c(1,4,8,7,9,5,3,2)]
+# mise.b.8.table=mise.b.8[c(1,4,8,7,9,5,3,2)]
+# mise.b.128.table=mise.b.128[c(1,4,8,7,9,5,3,2)]
+# 
+# mise.hs.1.table=mise.hs.1[c(1,4,8,7,9,5,3,2)]
+# mise.hs.8.table=mise.hs.8[c(1,4,8,7,9,5,3,2)]
+# mise.hs.128.table=mise.hs.128[c(1,4,8,7,9,5,3,2)]
+
[…]

### 2016-02-18 paper/draft_6.tex
update draft

@@
 
-\title{\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals (?)}}
+\title{\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals}}
 \date{}
@@
 
-Idea of adaptive shrinkage.
-
-By estimating the uni-modal distribution from the data, ash uses the data to
-determine how sparse $\tbmu$ should be,
-and therefore how spatially structured $\bmu$ should be. Thus the degree of spatial smoothing is adaptive to the dataset: more smoothing for
-datasets that appear consistent with a smooth signal.
-
-We first present a simple illustration of our method as a signal denoising technique.
-Figure \ref{fig:simple_eg} demonstrates that SMASH is able to better capture the true signal than TI-thresholding (with variance estimated by running median absolute deviation (RMAD); see \cite{Gao1997Wavelet}) on a simple simulated signal.
+Figure \ref{fig:simple_eg} illustrates the main features of adaptive shrinkage (ash) applied 
+to a denoising problem. The data (panel a) is first transformed into wavelet coefficients (WCs) at different scales.
+Each such ``observed" WC can be thought of as a noisy estimate of some ``true" WC for the (unknown) mean that we wish to estimate.
+We also compute, for each WC, an associated standard error that depends on the variance of the data about the mean.
+The idea behind wavelet denoising is to ``shrink" the observed WCs towards 0, which produces a smoother estimate of the mean than the observed data.
+
+A crucial question is, of course, how much to shrink. A key idea behind ash is that the shrinkage is ``adaptive", in that it
+determined by the data, in two distinct ways. First, if at a particular scale many observed WCs are ``large" (compared with their standard errors)
+then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{}) will have a long tail.
+Consequently ash will shrink less at this scale than at scales where few observed
+WCs are large, for which the estimated $g$ will have a short tail.
+This is illustrated in panels b-c: at scale 1, many observed WCs are large (b), and so very little shrinkage is applied to these estimates (c).
+In contrast, at scale 7, few observed WCs are large (b), and so stronger shrinkage is applied (c). Second, the shrinkage is adaptive to 
+the standard error for each WC: at a given scale, WCs with larger standard error are shrunk more strongly than WCs with small standard error.
+This is illustrated in panel d). (The standard errors vary among WCs here because of the hetereskedastic variance.)
+
+ The end result is that i) data that are consistent with a smooth signal, get smoothed more strongly; ii) smoothing is stronger in areas
+ of the signal with larger variance. In this example the smoothed signal from ash is visually (and also quantitatively) more accurate than
+ using TI-thresholding (with variance estimated by running median absolute deviation (RMAD); see \cite{Gao1997Wavelet}) (panel e).
 
@@
 
+ \subsubsection{Gaussian mean estimation}
+
 For the Gaussian case, we focus on mean estimation, initially with homoskedastic errors. We modelled our simulation study after
@@
 the best-performing methods from their comparison.
-In particular Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE).
-We also considered the popular Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
-Figure \ref{fig:gaus_homo} compares the mean integrated squared errors (MISEs) of TI-thresholding and Ebayesthresh to SMASH with two different options for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024.
-The default version of SMASH estimates the mean without any homoskedastic assumptions on the variance function, while the other version of SMASH estimates the mean given the true variance function.
-We can clearly see that the performance of SMASH is not impacted by the lack of homoskedastic assumptions imposed on the variance function: it outperforms two of the most accurate wavelet denoising algorithms for i.i.d.
-Gaussian noise even when the i.i.d.
-assumption holds, and performs nearly as well as when the variance function is known, which is the best-case scenario for any denoising technique.
-These results also extend to other mean functions, SNRs and sample sizes (see Supplementary Materials for more details).
- Different test functions, sample sizes, signal-to-noise ratios (SNR) and variance functions were considered, to ensure that SMASH behaves well in a variety of settings.
-However, only a small portion of the results will be shown here to highlight key findings from the extensive simulation study.
-Full results from the study can be found in the Supplementary Materials.
-
-We focus initially on estimation of a Gaussian mean with homoskedastic errors. Due to the large number of methods available in the literature for this setting, we chose only a subset.
+In particular their results showed that Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE).
+We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
+
+Figure \ref{fig:gaus_homo} compares the mean integrated squared errors (MISEs) of TI-thresholding and Ebayesthresh to SMASH for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024.
+We applied SMASH in three ways, the first (SMASH) estimating the variance function allowing for heteroskedasticity, the second estimating the variance assuming homoskedasticity (SMASH-homo) and the
+third using the true variance function (SMASH true variance), which could be viewed as a "gold standard".
+The results show that all three versions of SMASH outperform both EbayesThresh and TI-thresholding.
+Notably all three SMASH versions perform very similarly, demonstrating that
+in this case there is little cost in allowing for heterskedasticity when the truth is homoskedastic.
+
+We obtained similar results for other mean functions, SNRs and sample sizes (see Supplementary Materials).
 
@@
     \includegraphics[width=0.65\textwidth]{violin_gaus_homo.pdf}
-    \caption{Compares various wavelet-based methods for denoising data with homoskedastic Gaussian errors for the ``Spikes'' mean function.
+    \caption{Comparison of wavelet-based methods for mean estimation with homoskedastic Gaussian errors for the ``Spikes'' mean function.
 Violin plots of MISEs for (from bottom to top) SMASH, SMASH with homoskedastic assumption, TI-thresholding with homoskedastic assumption, Ebayesthresh with homoskedastic assumption, and SMASH with known true variance are shown in the figure.
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-We note the performance gain of SMASH over both TI-thresholding and Ebayesthresh, and that SMASH with estimated variance can perform nearly as well as when it is given the true variance.}
+SMASH outperforms both TI-thresholding and Ebayesthresh, and SMASH with estimated variance performs nearly as well as with true variance.}
     \label{fig:gaus_homo}
@@
 
-Having shown that SMASH performs well in the homoskedastic case without any explicit assumptions on the Gaussian noise, we now demonstrate its performance gain when the errors are heteroskedastic.
-For the sake of presentation, Figure \ref{fig:gaus_hetero} highlights only the results from SMASH, TI-thresh (with various choices of variance estimation) and EbayesThresh for just two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024.
-Nevertheless, similar results hold in general for different mean and variance functions, SNRs, and sample sizes (see Supplementary Materials for more details).
+Turning now to heteroskedastic errors, we compare results from SMASH (run three different ways, as above) with EbayesThresh (which assumes
+homoskedastic variance) and TI-thresh. For TI-thresh we considered three different ways of estimating the heteroskedastic variance: RMAD 
+(\cite{Gao1997Wavelet}), the SMASH estimated variance, and the true variance. (TI-thresh with homoskedastic variance performed very poorly; Supplementary Results.) Figure \ref{fig:gaus_hetero} 
+shows results for two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024.
+
+To summarize the main patterns in Figure \ref{fig:gaus_hetero}:
+\begin{enumerate}
+\item SMASH outperforms all TI-thresh variants (including, here, TI with the true variance).
+\item SMASH performs almost as well for mean estimation when estimating the variance as when given the true variance.
+\item Allowing for heteroskedasticity within SMASH can substantially improve accuracy of mean estimation (compare SMASH with SMASH-homo and EbayesThresh).
+\item TI-thresh performs considerably better when used with the SMASH variance estimate than with the RMAD variance estimate.
+\end{enumerate}
+
+These main patterns hold for a variety of different mean and variance functions, SNRs, and sample sizes (see Supplementary Materials).
+Some variance functions are harder to estimate than others (e.g.
+the ``Bumps" function), and in these cases providing methods the true variance can greatly increase
+accuracy compared with estimating the variance. 
+As might be expected, the gain in allowing for heteroskedastic variance tends to be greatest when the variance functions are more
+volatile.
 
@@
     \end{subfigure}
-    \caption{Compares various wavelet-based methods for denoising data with heteroskedastic Gaussian errors.
-Figures on the left show violin plots of MISEs for various methods in denoising data with homoskedastic Gaussian errors for two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function.
+    \caption{Comparison of wavelet-based methods for mean estimation with heteroskedastic Gaussian errors.
+Figures on the left show violin plots of MISEs for various methods on two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function.
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-Figures on the right plot the associated mean and variance functions.
-We note the performance gain of SMASH over TI-thresh with different variance options: variance estimated by RMAD, variance estimated by SMASH, and the true variance.}
+Figures on the right plot the mean and variance functions used.}
     \label{fig:gaus_hetero}
@@
 
-Several facts are immediately clear from figure \ref{fig:gaus_hetero}: 
+\subsubsection{Gaussian variance estimation}
+
+One unusual feature of SMASH is that it performs joint mean and variance estimation.
+Indeed, we found only one other joint mean and variance estimation procedure for which we could obtain software (CHECK):
+the Mean Field Variational Bayes (MFVB) method for heteroskedastic Gaussian regression \cite{Menictas2015Variational}. 
+This method is based on penalized splines, and so is not well suited to many standard test functions in the wavelet literature, which
+often contain ``spiky" local features not well captured by splines. Hence, we compared SMASH and MFVB on some
+smoother mean and variance (standard deviation) functions, specifically scenario A from \cite{Menictas2015Variational} (shown in Figure \ref{fig:mfvb_fn}),
+using scripts kindly provided by M.~Menictas.
+
+We simulated data under two different scenarios:
 \begin{enumerate}
-\item SMASH does better than all TI-thresh variants, including the case when the true variance is provided, demonstrating the excellent finite sample performance of SMASH.
-\item using the variance estimate from SMASH as an input to TI-thresh improves the accuracy of TI-thresh substantially, compared with using RMAD to estimate the variance as in \cite{Gao1997Wavelet}
-\item accounting for heteroskedasticity allows SMASH to vastly outperform methods which assume homoskedastic errors.
-\item SMASH is more robust to violations of homoskedasticity compared with both Ebayesthresh (shown) and TI-thresholding (not shown due to space limitations).
-\end{enumerate}
-
-It should also be noted that providing the true variance to SMASH does not result in substantial gains compared to the case when SMASH estimates its own variance function for most of the test functions (results shown in the Supplementary Materials).
-Hence, we can reasonably assume that SMASH does a good job of variance estimation, although this claim relies heavily on the variance function at hand.
-For example, the Bumps variance function (see Appendix ??) is extremely difficult to estimate, and SMASH will perform much better when provided with the true variance function.
-
-Since our method also provides variance estimates, one could potentially perform similar assessments for different variance functions as with mean functions.
-In this particular study, we compare our method against the only joint mean and variance estimation procedure for which software is easily available.
-Specifically, we consider the Mean Field Variational Bayes (MFVB) methodology developed by \cite{Menictas2015Variational} for heteroskedastic Gaussian regression.
-Here we note that the MFVB approach is not well suited for dealing with standard test functions in the wavelet literature, as it is based on penalized splines (simulation studies were conducted to confirm this observation; results not shown).
-Hence, we chose the smooth mean and standard deviation functions (A) from \cite{Menictas2015Variational} as our test functions, plotted in Figure \ref{fig:mfvb_fn} and denoted by $m(\cdot)$ and $sd(\cdot)$ respectively.
-We then considered two different simulation scenarios:
-\begin{enumerate}
-\item $n=500$ independent $(X_i,Y_i)$ pairs were generated.
-The $X_i$'s were distributed as Uniform(0,1), and the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$.
-The performance of a given method is measured by the standard MSE evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation functions.
-\item $n=1024$ independent $(X_i,Y_i)$ pairs were generated.
-The $X_i$'s were deterministic and equally spaced on (0,1), while the $Y_i$'s were distributed as $N(m(x_i),sd(x_i))$.
-The performance of a given method is measured by the MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation functions.
+\item We generated $n=500$ independent $(X_i,Y_i)$ pairs, with $X_i \sim$ Uniform(0,1), and $Y_i | X_i=x_i \sim N(m(x_i),s(x_i)^2)$
+where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_fn}). We measured performance by the MSE 
+evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation.
+\item We generated $n=1024$ independent $(X_i,Y_i)$ pairs, with the $X_i$'s (deterministically) equally spaced on (0,1), and $Y_i|X_i$ as above.
+Performance is measured by MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation.
 \end{enumerate}
@@
 \end{figure}
-In the first scenario, the number of data points is not a power of two, nor are the point equally spaced.
-To deal with these complications, we adapted and modified the standard symmetric extension procedure commonly used in wavelet settings.
-We first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points.
-This ensures that the number of data points in the new ``dataset'' is a power of two, and the mean curve would be continuous at the right edge.
-To further ensure that the input to the Gaussian denoising method is periodic, we then reflected the new dataset about the right edge and used this as the final input.
-To obtain the original mean and variance functions, we extracted the first $n$ points from the outputs (mean and variance) of our denoising technique.
-Since the data points are not evenly spaced, we took the simplest approach and applied our method treating the observations as if they were evenly spaced.
-This approach is not only intuitively appealing, but can also be considered a formal treatment of unequally spaced data in traditional wavelet settings (eg.
-\cite{Sardy1999Wavelet}).
-Evaluation of MSE at the 201 equally spaced points is then based on simple linear interpolation between the estimated points.
-Table \ref{table:mfvb_comp} displays the MSEs over 100 independent runs for each scenario.
+
+The first scenario presents some issues for SMASH because the number of data points is not a power of two, nor are the point equally spaced.
+To deal with the first issue, following standard ideas in the wavelet literature, we first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points, so that the number of data points in the new ``dataset'' is a power of two, and the mean curve is continuous at the right edge.
+To further ensure that the input to SMASH is periodic, we reflected the new dataset about the right edge and used this as the final input.
+To deal with the second issue we follow the common practice of treating the observations as if they are evenly spaced (see \cite{Sardy1999Wavelet} for discussion).
+To estimate the original mean and variance functions, we extract the first $n$ points from the SMASH estimated mean and variance.
+To evaluate MSE at the 201 equally spaced points (Scenario 1) we use simple linear interpolation between the estimated points.
+
+Table \ref{table:mfvb_comp} shows mean MSEs over 100 independent runs for each scenario.
 \begin{table}[ht]
@@
 
-Note that wavelets in general are poorly suited for dealing with the setup in Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced.
+Note that wavelets in general are poorly suited to Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced.
 Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of SMASH.
@@
 
-Thus far, we have demonstrated that our method does a good job of mean and variance estimation for a variety of situations in the Gaussian case.
-As such, we now turn our attention to the Poisson case.
+\subsubsection{Poisson Data}
+
 For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}, over 100 independent runs.
@@
 As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asmyptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
-Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz in general.
+Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
 Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}.

### 2016-02-22 paper/draft_6.tex
changes to codes for plotting and updates to draft

@@
     \end{subfigure}
-    \caption{shows both ASH and SMASH at work.
-(a) shows the mean and variance functions, as well as one realized dataset.
+    \caption{Shows both ASH and SMASH at work.
+(a) shows the mean function $\pm$2 standard deviations, as well as one realized dataset.
 (b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse (scale 1) and one fine (scale 7).
@@
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-Figures on the right plot the mean and variance functions used.}
+Figures on the right plot the mean functions $\pm$2 standard deviations.}
     \label{fig:gaus_hetero}
@@
 
-\subsubsection{Gaussian variance estimation}
+\subsubsection{Gaussian variance estimation}\label{sec:mfvb}
 
@@
 often contain ``spiky" local features not well captured by splines. Hence, we compared SMASH and MFVB on some
-smoother mean and variance (standard deviation) functions, specifically scenario A from \cite{Menictas2015Variational} (shown in Figure \ref{fig:mfvb_fn}),
+smoother mean and variance (standard deviation) functions, specifically scenario A in Figure 5 from \cite{Menictas2015Variational} (shown in Figure \ref{fig:mfvb_eg}),
 using scripts kindly provided by M.~Menictas.
@@
 \item We generated $n=500$ independent $(X_i,Y_i)$ pairs, with $X_i \sim$ Uniform(0,1), and $Y_i | X_i=x_i \sim N(m(x_i),s(x_i)^2)$
-where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_fn}). We measured performance by the MSE 
+where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_eg}). We measured performance by the MSE 
 evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation.
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{mfvb_mean.pdf}
-        \caption{}
-        \label{fig:mfvb_mean}
-    \end{subfigure}
-    \hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{mfvb_var.pdf}
-        \caption{}
-        \label{fig:mfvb_var}
-    \end{subfigure}
-    \caption{Mean (a) and variance (b) functions used in the simulation study comparing SMASH against MFVB.
+    \includegraphics[width=\textwidth]{mfvb_eg.pdf}
+    \caption{Shows the mean function $m(x)$ $\pm$2 standard deviations $s(x)$ used in the simulation study comparing SMASH against MFVB.
 These functions correspond to mean and standard deviation functions (A) from \cite{Menictas2015Variational}.}
-    \label{fig:mfvb_fn}
+    \label{fig:mfvb_eg}
 \end{figure}
@@
 
-Note that wavelets in general are poorly suited to Scenario 1; not only are the number of data points not a power of two, they are also not equally spaced.
-Also, linear interpolation between sample points was used in computing the MSE, further impacting the accuracy of SMASH.
-At the same time, spline-based methods such as MFVB are well suited to dealing with smooth mean and variance functions such as those used in the simulations, whereas wavelet methods can better deal with spatial inhomogeneity which are present in functions such as those presented in Figure \ref{fig:gaus_homo}.
-Despite all these limitations, our method performs comparably to MFVB in terms of mean estimation for the simulation scheme presented in Scenario 1, and has a lower MSE in terms of variance estimation.
-For Scenario 2, our method outperforms MFVB in both mean and variance estimation.
+In addition to the issues stated above for Scenario 1 with regards to wavelet-based methods (SMASH in particular), linear interpolation between sample points was also used in computing the MSE, further impacting the accuracy of SMASH.
+On the other hand, spline-based methods such as \cite{Menictas2015Variational} are well suited to dealing with smooth mean and variance functions presented in this particular simulation study.
+Despite all these limitations, SMASH performs comparably to MFVB in terms of mean estimation for Scenario 1, and has a lower MSE in terms of standard deviation estimation.
+For Scenario 2, SMASH outperforms MFVB in both mean and variance estimation.
 
@@
 For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}, over 100 independent runs.
-Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}), which are two popular and accurate Poisson denoising techniques, for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8).
-The low intensities are of primary interest in genomic applications, and so we focus our attention to these.
+Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}) for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8).
+We focus our attention on low intensities as they are of primary interest in many genomic applications.
 Complete results, including a (min,max) intensity of (1/128, 128), are included in Supplementary Materials.
-It is clear from Figure \ref{fig:pois_sim} that SMASH outperforms both methods, and the claim holds true in general.
-As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asmyptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
+Figure \ref{fig:pois_sim} demonstrates that SMASH outperforms both methods for this scenario, and the claim holds true in general.
+As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asymptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
 Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
 Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}.
-On the other hand, SMASH outperforms BMSM consistently, even though our method is based on the same likelihood factorization used in the latter.
-We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM.
+On the other hand, SMASH outperforms BMSM consistently, even though it is based on the same likelihood factorization used in the latter.
+We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM in the simulation study.
 More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
@@
 Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-We note the performance gain of SMASH over both BMSM and Haar-Fisz.}
+We note the performance gain of SMASH over both BMSM and Haar-Fisz in these scenarios.}
     \label{fig:pois_sim}
@@
 
-In terms of computation, we note that SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter method needs to be rerun for each shift of the data.
+In terms of computation, SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter must be rerun for each shift of the data.
 However, a direct comparison between SMASH and BMSM is uninformative, as they are coded in different programming environments.
-Nevertheless, the similarities between the two methods imply that they should behave identically in this aspect, barring differences in actual implementation.
-
-Overall, these simulation studies demonstrate the ability of our method to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptiveness of the shrinkage procedure ASH.
+Nevertheless, similarities between the two methods imply that they should behave identically in this aspect, barring differences in actual implementation.
+
+Overall, these simulation studies demonstrate the ability of SMASH to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptivity of the shrinkage procedure ASH.
 Although we have considered an extensive range of scenarios here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has yet to be determined.
@@
 To deal with repeated measurements, we simply take the median of the measurements for acceleration for any given $time$ value.
-To address the issue of non-equal spacing between the data points, we applied the procedure described in the Simulations section when comparing our method against MFVB.
+To address the issue of non-equal spacing between the data points, we applied the procedure described in \ref{sec:mfvb}.
 The fitted mean and variance curves are shown in Figure \ref{fig:motorcycle}.
@@
 
-Although SMASH does a reasonably good job of performing nonparametric regression on the given dataset, we do recognize that there are better ways to deal with the fact that the observations are not equally spaced, which can then reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in the literature.
-Nevertheless, we can use SMASH directly out of the box in many settings where Gaussian denoising is required, making it an extremely versatile tool.
+Although SMASH does a reasonably good job of performing nonparametric regression on the given dataset, we do recognize that there are better ways to deal with unequally spaced observations, which can then reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in the literature.
+Nevertheless, we can use SMASH directly out of the box under most circumstances, making it an extremely versatile tool.
 \newpage
@@
 \end{figure}
-From Figure \ref{fig:seq_peak_est} it is clear that SMASH also captures the peaks detected by MACS.
+From Figure \ref{fig:seq_peak_est} it is clear that SMASH captures the peaks detected by MACS.
 Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.

### 2016-02-22 code_paper/gaus_data/delouille/mc_ethanol.R

@@ -40,13 +40,13 @@ res.eth = smash.wrapper(x.ini.eth, y.ini.eth)
 
 
 
-pdf("paper/motorcycle.pdf", height = 6, width = 8)
-par(cex.axis = 1.3, cex.sub = 1.8, cex.lab = 1.5, mar = c(5.1, 5.1, 2.1, 2.1), mgp = c(3, 1.3, 0))
-plot(res.mc$x, res.mc$mu.est, type = 'l', ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)), max(res.mc$y + 2 * sqrt(res.mc$var.est))), xlab = "time (ms)", ylab = "acceleration (g)", lwd = 1.7)
-lines(res.mc$x, res.mc$mu.est + 2 * sqrt(res.mc$var.est), col = 2, lty = 5, lwd = 1.8)
-lines(res.mc$x, res.mc$mu.est - 2 * sqrt(res.mc$var.est), col = 2, lty = 5, lwd = 1.8)
-points(res.mc$x, res.mc$y, cex = 0.7, pch = 16, col = alpha("black", 0.5))
-dev.off()
+# pdf("paper/motorcycle.pdf", height = 6, width = 8)
+# par(cex.axis = 1.3, cex.sub = 1.8, cex.lab = 1.5, mar = c(5.1, 5.1, 2.1, 2.1), mgp = c(3, 1.3, 0))
+# plot(res.mc$x, res.mc$mu.est, type = 'l', ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)), max(res.mc$y + 2 * sqrt(res.mc$var.est))), xlab = "time (ms)", ylab = "acceleration (g)", lwd = 1.7)
+# lines(res.mc$x, res.mc$mu.est + 2 * sqrt(res.mc$var.est), col = 2, lty = 5, lwd = 1.8)
+# lines(res.mc$x, res.mc$mu.est - 2 * sqrt(res.mc$var.est), col = 2, lty = 5, lwd = 1.8)
+# points(res.mc$x, res.mc$y, cex = 0.7, pch = 16, col = alpha("black", 0.5))
+# dev.off()
 
 
 pdf("paper/motorcycle.pdf", height = 6, width = 8)

### 2016-02-22 code_paper/gaus_data/mfvb_sim/comparison.R

@@ -1,8 +1,5 @@
 library(smash)
-source("D:/Grad School/Spring 2013/mfvb/ZOSull.r")
-source("D:/Grad School/Spring 2013/mfvb/wait.r")
-source("D:/Grad School/Spring 2013/mfvb/meanVarMFVB.r")
-
+#source MFVB files here
 
 mse.mu.uneven.mfvb=0
 mse.mu.uneven.haar=0
@@ -363,10 +360,17 @@ save.image("comparison.RData")
 
 #################
 gTrue <- function(x) return(exp(0.1 + cos(4*pi*x)))
+xgrid = (0:10000)/10000
 
-pdf("mfvb_mean.pdf",width=8,height=5)
-plot(fTrue,ylim=c(-2,2),ylab="m(X)",xlab="X",main="mean function")
-dev.off()
-pdf("mfvb_var.pdf",width=8,height=5)
-plot(gTrue,ylim=c(0,3.5),ylab="var(X)",xlab="X",main="variance function")
+# pdf("mfvb_mean.pdf",width=8,height=5)
+# plot(fTrue,ylim=c(-2,2),ylab="m(X)",xlab="X",main="mean function")
+# dev.off()
+# pdf("mfvb_var.pdf",width=8,height=5)
+# plot(gTrue,ylim=c(0,3.5),ylab="var(X)",xlab="X",main="variance function")
+# dev.off()
+
+pdf("paper/mfvb_eg.pdf", width = 8, height = 5)
+plot(xgrid, fTrue(xgrid), type = "l", ylim = c(-5, 5), ylab = "y(X)", xlab = "X")
+lines(xgrid, fTrue(xgrid) + 2 * sqrt(gTrue(xgrid)), col = 2, lty = 2)
+lines(xgrid, fTrue(xgrid) - 2 * sqrt(gTrue(xgrid)), col = 2, lty = 2)
 dev.off()

### 2016-03-02 paper/draft_6.tex
small updates to draft

@@
 The only wavelet-based method for variance estimation we have found is \cite{Cai2008Adaptive}, which applied a wavelet thresholding approach to first order differences.
-Unfortunately software implementation is only available in \cite{Menictas2015Variational}.
+In no case could we find publicly-available software implementations of these methods (but we did receive
+code by email from \cite{Menictas2015Variational}, which we use in our comparisons).
 
@@
 Here we make the more flexible assumption that the variance function is spatially structured, and use wavelet shrinkage to estimate it.
-Our approach is similar in spirit to \cite{Cai2008Adaptive}, but we jointly estimate the mean and variance functions whereas they estimate only the variance function.
+Our approach is similar in spirit to \cite{Delouille2004Smooth}, and also to \cite{Cai2008Adaptive} (although the latter estimates only the variance function).
 
@@
 We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
+All the methods were applied using the Symmlet8 wavelet basis \cite{}.
 
@@
 One unusual feature of SMASH is that it performs joint mean and variance estimation.
-Indeed, we found only one other joint mean and variance estimation procedure for which we could obtain software (CHECK):
-the Mean Field Variational Bayes (MFVB) method for heteroskedastic Gaussian regression \cite{Menictas2015Variational}. 
+Indeed, we found no existing R packages aimed at doing this. However we were able to obtain code
+implementing the Mean Field Variational Bayes (MFVB) method for heteroskedastic Gaussian regression \cite{Menictas2015Variational} (M.~Menictas, personal communication). 
 This method is based on penalized splines, and so is not well suited to many standard test functions in the wavelet literature, which
 often contain ``spiky" local features not well captured by splines. Hence, we compared SMASH and MFVB on some
-smoother mean and variance (standard deviation) functions, specifically scenario A in Figure 5 from \cite{Menictas2015Variational} (shown in Figure \ref{fig:mfvb_eg}),
+smoother mean and variance (standard deviation) functions, specifically scenario A in Figure 5 from \cite{Menictas2015Variational} (Figure \ref{fig:mfvb_eg}),
 using scripts kindly provided by M.~Menictas.
@@
 
-The first scenario presents some issues for SMASH because the number of data points is not a power of two, nor are the point equally spaced.
+The first scenario presents some issues for SMASH because the number of data points is not a power of two, nor are the points equally-spaced.
 To deal with the first issue, following standard ideas in the wavelet literature, we first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points, so that the number of data points in the new ``dataset'' is a power of two, and the mean curve is continuous at the right edge.
@@
 Table \ref{table:mfvb_comp} shows mean MSEs over 100 independent runs for each scenario.
+Despite the fact that these simulation scenarios -- particularly Scenario 1 -- seem better suited to MFVB than SMASH, 
+SMASH performs comparably or better than MFVB for both mean and variance estimation in both Scenarios. 
 \begin{table}[ht]
@@
 \cline{2-5}
-& mean & sd & mean & sd \\
+& MSE (for mean) & MSE (for sd) & MSE (for mean) & MSE (for sd) \\
 \hline
@@
 \end{tabular}
-\caption{Compares the performance (in MSE) of SMASH and MFVB for two simulation scenarios, with the mean and variance functions as shown in \ref{fig:mfvb_fn}.
-SMASH is comparable to MFVB in mean estimation and outperforms the latter in variance estimation in Scenario 1, where the data are not equally spaced and not a power of 2.
-SMASH outperforms MFVB in both mean and variance estimation in Scenario 2, where the data are equally spaced and a power of 2.}
+\caption{Comparison of accuracy (MSE) of SMASH and MFVB for two simulation scenarios.  True mean and sd functions are shown in \ref{fig:mfvb_fn}. 
+In Scenario 1 the data are not equally spaced and not a power of 2; here SMASH is comparable to MFVB in mean estimation and more accurate for sd estimation.
+In Scenario 2 the data are equally spaced and a power of 2; here SMASH outperforms MFVB in both mean and sd estimation.}
 \label{table:mfvb_comp}
@@
 
-In addition to the issues stated above for Scenario 1 with regards to wavelet-based methods (SMASH in particular), linear interpolation between sample points was also used in computing the MSE, further impacting the accuracy of SMASH.
-On the other hand, spline-based methods such as \cite{Menictas2015Variational} are well suited to dealing with smooth mean and variance functions presented in this particular simulation study.
-Despite all these limitations, SMASH performs comparably to MFVB in terms of mean estimation for Scenario 1, and has a lower MSE in terms of standard deviation estimation.
-For Scenario 2, SMASH outperforms MFVB in both mean and variance estimation.
-
 \subsubsection{Poisson Data}
 
-For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}, over 100 independent runs.
-Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}) for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8).
-We focus our attention on low intensities as they are of primary interest in many genomic applications.
-Complete results, including a (min,max) intensity of (1/128, 128), are included in Supplementary Materials.
-Figure \ref{fig:pois_sim} demonstrates that SMASH outperforms both methods for this scenario, and the claim holds true in general.
-As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asymptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
-Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
+To assess SMASH on Poisson data we simulated data from
+several different test functions from \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}.
+We varied the minimum and maximum intensity of each test function, using (min,max) intensities of (0.01,3), (1/8,8) and (1/128,128).
+For each test function and intensity level we simulated 100 datasets, each with $n=1024$ data points.
+We focus on results for the first two intensity settings, which have smaller average intensity.
+These settings produce smaller average counts, making them more challenging, and also more representative of the kinds of genomic application that we consider below.
+Complete results are included in Supplementary Materials.
+
+We compared SMASH with eight other methods, but we focus here on the comparisons with the best-performing other methods, which are Haar-Fisz (HF) (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}).
+The latter, like SMASH, is an Empirical Bayes method,  but with a less flexible prior distribution on the
+multi-scale coefficients. The HF method involves first performing a transformation on the Poisson counts, and applying Gaussian wavelet methods to the transformed data. 
+There are many choices for Gaussian wavelet methods, and the performance depends on these choices (and with different choices being optimal for different data sets). 
+The settings we used here are documented in Supplementary Information, and were chosen by us to optimize (average) performance through moderately extensive experimentation on a range of simulations.
+
+In summary, SMASH outperformed both HF and BMSM in the majority of simulations, with the gain in accuracy being strongest for the more challenging lower-intensity
+scenarios. A typical result is shown in Figure \ref{fig:pois_sim}, with complete results in Supplementary Information (\url{?}). 
+Among the other two methods, BMSM tends to be the more consistent performer. HF, with the settings
+we used here, performs quite variably, being worse than the other two in most scenarios, but occassionally performing the best (specifically for the Angles, Bursts and Spikes test functions,
+with (min,max) intensity (1/128,128)). As noted above, the HF transform can be used with many settings, so the results here should be viewed as a guide to the 
+performance that can be achieved in practice.
+
+%Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
 Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}.
@@
     \end{subfigure}
-    \caption{Compares various approaches for denoising Poisson data for the ``Bursts'' test function where a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).
-Violin plots of MISEs for (from bottom to top) SMASH, BMSM and Haar-Fisz are shown in the figure.
-Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-We note the performance gain of SMASH over both BMSM and Haar-Fisz in these scenarios.}
+    \caption{Comparison of methods for denoising Poisson data (for the ``Bursts'' test function).
+The violin plots show distributions of MISE for each method over 100 datsets, with smaller values indicating better performance.
+The dashed green line indicates the median MISE for SMASH.
+Panel a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).}
     \label{fig:pois_sim}
@@
 
-In terms of computation, SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter must be rerun for each shift of the data.
-However, a direct comparison between SMASH and BMSM is uninformative, as they are coded in different programming environments.
-Nevertheless, similarities between the two methods imply that they should behave identically in this aspect, barring differences in actual implementation.
-
-Overall, these simulation studies demonstrate the ability of SMASH to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptivity of the shrinkage procedure ASH.
+One disadvantage of the HF transform is that, to achieve translation invariance (TI), the transform has to be done explicitly for each shift of the data: the tricks usually used to do this efficiently \cite{coifman.donoho.titable} do not work here.
+Thus, making HF fully translation invariant increases computation by a factor of $T$, rather than the factor of $\log(T)$ for the other methods.
+Here we follow advice in \cite{} to reduce the computational burden by averaging over 50 shifts of the data rather than $T$.
+Even so, HF was substantially slower than the other methods.
+ A direct comparison of computational efficiency between SMASH and BMSM is difficult, as they are coded in different programming environments.
+Nevertheless, similarities between the two methods suggest that they should have similar computational cost.
+ Both SMASH and BMSM took, typically, less than a second per dataset in our simulations.
+
+%Overall, these simulation studies demonstrate the ability of SMASH to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptivity of the shrinkage procedure ASH.
 Although we have considered an extensive range of scenarios here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has yet to be determined.
@@
 
-\section{Application to real datasets}
+\section{Illustrative applications}
 %\subsection{Three-month Treasury Bill Yields}
@@
     \caption{Results from fitting SMASH to the motorcycle acceleration data discussed in \cite{silverman1985some}.
-Both the mean curve (solid black line) and the variance around the mean curve (dashed red line) are shown.
-We note that SMASH does a good job of capturing both the mean as well as the variation in the data without requiring and parameter tuning.}
+The figure shows the estimate mean curve (solid black line) with $\pm2$ the estimated standard deviation curve (dashed red line).}
     \label{fig:motorcycle}
@@
 
-We first apply the Gaussian version of SMASH on the well known motorcycle acceleration dataset from \cite{silverman1985some}.
-The data consists of 133 observations measuring head acceleration in a simulated motorcycle accident which is used to test crash helmets.
-The dependent variable is $acceleration$ (in $g$), and the independent variable is $time$ (in ms).
-To deal with repeated measurements, we simply take the median of the measurements for acceleration for any given $time$ value.
-To address the issue of non-equal spacing between the data points, we applied the procedure described in \ref{sec:mfvb}.
-The fitted mean and variance curves are shown in Figure \ref{fig:motorcycle}.
-Comparing our fit with that of \cite{Delouille2004Smooth}, which also employs a wavelet-based approach, we note two advantages to using SMASH.
-First, our method provides a measure of uncertainty (through both the credible band for the mean curve as well as the variance curve itself), which is often of interest in many applications.
-Second, our method is able to produce a visually appealing fit when used without having to tune any parameters, while the approach in \cite{Delouille2004Smooth} requires an $adhoc$ removal of fine scale detail coefficients to avoid introducing artifacts into the fit.
-
-Although SMASH does a reasonably good job of performing nonparametric regression on the given dataset, we do recognize that there are better ways to deal with unequally spaced observations, which can then reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in the literature.
-Nevertheless, we can use SMASH directly out of the box under most circumstances, making it an extremely versatile tool.
-\newpage
+As a further illustration of the heteroskedastic Gaussian version of SMASH, we apply it to the motorcycle acceleration dataset from \cite{silverman1985some}.
+The data consist of 133 observations measuring head acceleration in a simulated motorcycle accident that is used to test crash helmets.
+The dependent variable is {\it acceleration} (in {\it g}), and the independent variable is {\it time} (in {\it ms}).
+To deal with repeated measurements, we take the median of the measurements for acceleration for any given {\it time} value.
+As in Section \ref{sec:mfvb} we treat the
+data as if they are equally spaced although they are not. The fitted mean and variance curves (Figure \ref{fig:motorcycle})  
+provide a visually appealing fit to the data, and were achieved without hand tuning of any parameters. This contrasts with
+results in \cite{Delouille2004Smooth} -- which also uses a wavelet-based approach for heteroskedastic variance, but accounts for the unequal spacing of the data -- which required the {\it ad hoc} removal of high-resolution wavelet coefficients to produce a visual appealing fit.
+
+%Although SMASH does a reasonably good job here, we recognize that there are better ways to deal with unequally spaced observations, which can 
+%reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in \cite{xx}.
+
 \subsection{ChIP-Seq Data}
-Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly used in the field of genomics.
-Specifically, we chose an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute.
-This dataset contains reads from chromatin immunoprecipitation sequencing (ChIP-seq) measuring transcription factor binding in two different cell types, with two samples for each cell type.
-Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1.
+
+To further illustrate our Poisson de-noising procedure we applied it to data from genomic sequencing.
+Specifically we applied SMASH to chromatin immunoprecipitation sequencing (ChIP-seq) data for the transcription factor {\it YY1} in cell line GM12878
+collected by the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project. 
+The data (e.g.~Figure \ref{fig:seq_peak_data}) consist of counts of sequencing reads mapping to each location in genome. These can be treated as
+arising from an inhomogeneous Poisson process, whose intensity at base $b$ is related to the strength of the binding 
+of the transcription factor near $b$. Because binding tends to be quite localized, the intensity is low on average (the vast majority of 
+counts are 0), but has a small number of intense ``peaks". Identifying these peaks can help discover regions where 
+binding occurs, which is an important component of understanding gene regulation. Consequently there are
+many methods published for ``peak detection" in ChIP-Seq data \cite{wilbanks:2010}.
+
+Our goal here is to outline how Poisson de-noising could provide an alternative approach to the analysis of ChIP-seq data.
+The idea is simply to estimate the underlying intensity function, and then identify ``peaks" as regions where the estimated intensity
+exceeds some threshold.
+
+To illustrate this idea we applied SMASH to ChIP-seq data from a region of length $2^{15} (\approx 33k)$ basepairs from chromosome 1
+(hg18 (or 19?) chr1:880001-1011072). The estimated intensity is shown in Figure \ref{fig:seq_peak_est}, overlaid on peaks called by
+the popular peak calling software MACS \cite{}. We see that the locations with the strongest SMASH intensity estimates 
+corresponds to peaks found by MACS.
+However, the intensity estimate also suggests the presence of several additional weaker peaks not identified by MACS.
+
+The reliable calling of peaks in ChIP-seq data is a multi-faceted problem, and a full assessment lies outside the scope of this paper.
+Nonetheless, we believe that these illustrative results suggest that this approach could be worth pursuing further. 
+One nice feature of the multi-scale poisson approach is that it deals well with a range of intensity functions, and could
+perform well even in settings where peaks are broad and/or not especially well defined. In contrast, the performance of 
+different peak-finding algorithms is often reported to be quite sensitive to the ``kinds" of peak
+that are present, meaning that an algorithm that performs well in one setting may perform poorly in another.
+
+%One advantage compared with many peak-calling approaches is that the method would provide an estimated intensity at every base-pair.
+
+%Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.
+At the same time, SMASH also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
+
 %Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
@@
 %\bigskip
-One goal of analyzing ChIP-seq data is to discover regions where transcription factors are likely to bind to DNA, thereby allowing us to better understand the mechanisms underlying gene regulation.
-These binding regions are often reflected in the data as ``peaks'', where more counts are present than background noise.
-Our method allows us to identify these peaks by looking at the estimated intensity function.
+
 %In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
-To ensure that our method performs sensibly, we pooled the reads for just the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region.
-The results are shown in Figure \ref{fig:seq_peak}.\\
-\newpage
-\begin{figure}
+
+\begin{figure}[p]
 \centering
@@
     \end{subfigure}
-    \caption{Analysis of next-generation sequencing data from the ENCODE project, corresponding to sequencing reads from the GM12878 cell line and spanning positions 880001 to 1011072 on chromosome 1.
-(a) plots the actual sequencing counts (summed across both replicates).
-A rough signal can be visualized by looking at darker regions of the plot, which correspond to higher concentrations of data points.
-(b) plots the estimated intensity function obtained from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).
-We can observe not only the location of the peaks from the SMASH estimate (which MACS does provide), but also the amplitude of the signals, something which MACS fails to reveal.
-The plot also reveal weak signals that MACS fail to capture, but of interest nonetheless.}
+    \caption{Illustration of how SMASH could be used to identify peaks in ChIP-seq data.
+Panel (a) shows counts (summed across two replicate experiments).
+Due to over-plotting, darker regions of the plot correspond to higher concentrations of data points.
+Panel (b) shows the estimated intensity function from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).}
     \label{fig:seq_peak}
 \end{figure}
-From Figure \ref{fig:seq_peak_est} it is clear that SMASH captures the peaks detected by MACS.
-Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.
-At the same time, SMASH also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
 
 \section{Discussion}
-In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques.
+
+We have  adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques.
 Both applications discussed in this paper relax the standard assumption of i.i.d.
@@
 Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, revealing its potential in many other applications.
+
+First, our method provides a measure of uncertainty (through both the credible band for the mean curve as well as the variance curve itself), which is often of interest in many applications.
 
@@
 Hence, our fully adaptive procedure allows users to easily apply it to any given dataset, depending on the type of noise.
+
+potential to use likelihood to assess wavelet basis?
 
@@
 
-Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios.
+Although we focused on one-dimensional univariate denoising, our methods could be extended to more complex scenarios.
 In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see \cite{Morris2006Waveletbased}).
@@
 For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}.
-However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable.
-We could thus incorporate ASH into other types of transformations such as curvelets, which would be a potential direction for future work.
+However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable \cite{}.
+We could thus incorporate ASH into other types of transformations such as curvelets \cite{}, which would be a potential direction for future work.
 \newpage

### 2016-03-03 paper/draft_7.tex
added draft 7, which updated simulations section and fixed parts of tex

--- 2016-03-02 paper/draft_6.tex
@@
 \begin{align}
-\beta_j \| \shat_j & \sim g \\
+\label{eq:ash_model_1}\beta_j \| \shat_j & \sim g \\
 \bhat_j \| \beta_j, \shat_j & \sim N(\beta_j, \shat_j^2),
@@
 determined by the data, in two distinct ways. First, if at a particular scale many observed WCs are ``large" (compared with their standard errors)
-then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{}) will have a long tail.
+then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{eq:ash_model_1}) will have a long tail.
 Consequently ash will shrink less at this scale than at scales where few observed
@@
 We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
-All the methods were applied using the Symmlet8 wavelet basis \cite{}.
+All the methods were applied using the Symmlet8 wavelet basis \cite{Daubechies1992Ten}.
 
@@
     \caption{Shows the mean function $m(x)$ $\pm$2 standard deviations $s(x)$ used in the simulation study comparing SMASH against MFVB.
-These functions correspond to mean and standard deviation functions (A) from \cite{Menictas2015Variational}.}
+These functions correspond to mean and standard deviation functions (A) in Figure 5 from \cite{Menictas2015Variational}.}
     \label{fig:mfvb_eg}
@@
 
-We compared SMASH with eight other methods, but we focus here on the comparisons with the best-performing other methods, which are Haar-Fisz (HF) (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}).
+We compared SMASH with six other methods, but we focus here on the comparisons with the best-performing other methods, which are Haar-Fisz (HF) (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}).
 The latter, like SMASH, is an Empirical Bayes method,  but with a less flexible prior distribution on the
@@
 In summary, SMASH outperformed both HF and BMSM in the majority of simulations, with the gain in accuracy being strongest for the more challenging lower-intensity
-scenarios. A typical result is shown in Figure \ref{fig:pois_sim}, with complete results in Supplementary Information (\url{?}). 
+scenarios. A typical result is shown in Figure \ref{fig:pois_sim}, with complete results in Supplementary Information. 
 Among the other two methods, BMSM tends to be the more consistent performer. HF, with the settings
-we used here, performs quite variably, being worse than the other two in most scenarios, but occassionally performing the best (specifically for the Angles, Bursts and Spikes test functions,
+we used here, performs quite variably, being worse than the other two in most scenarios, but occasionally performing the best (specifically for the Angles, Bursts and Spikes test functions,
 with (min,max) intensity (1/128,128)). As noted above, the HF transform can be used with many settings, so the results here should be viewed as a guide to the 
@@
 \centering
+		\begin{subfigure}[b]{0.75\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{bursts_pois.pdf}
+        \caption{}
+        \label{fig:bursts_fn}
+    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
@@
     \end{subfigure}
-    \caption{Comparison of methods for denoising Poisson data (for the ``Bursts'' test function).
-The violin plots show distributions of MISE for each method over 100 datsets, with smaller values indicating better performance.
+    \caption{Comparison of methods for denoising Poisson data for the ``Bursts'' test function.
+(a) shows the (unscaled) test function.
+The violin plots in (b) and (c) show distributions of MISE for each method over 100 datsets, with smaller values indicating better performance.
 The dashed green line indicates the median MISE for SMASH.
-Panel a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).}
+Panel (b) corresponds to a (min,max) intensity of (0.01,3), and (c) corresponds to a (min,max) intensity of (1/8,8).}
     \label{fig:pois_sim}
@@
 
-One disadvantage of the HF transform is that, to achieve translation invariance (TI), the transform has to be done explicitly for each shift of the data: the tricks usually used to do this efficiently \cite{coifman.donoho.titable} do not work here.
+One disadvantage of the HF transform is that, to achieve translation invariance (TI), the transform has to be done explicitly for each shift of the data: the tricks usually used to do this efficiently \cite{Coifman1995Translationinvariant} do not work here.
 Thus, making HF fully translation invariant increases computation by a factor of $T$, rather than the factor of $\log(T)$ for the other methods.
-Here we follow advice in \cite{} to reduce the computational burden by averaging over 50 shifts of the data rather than $T$.
+Here we follow advice in \cite{Fryzlewicz2004HaarFisz} to reduce the computational burden by averaging over 50 shifts of the data rather than $T$.
 Even so, HF was substantially slower than the other methods.
@@
 binding occurs, which is an important component of understanding gene regulation. Consequently there are
-many methods published for ``peak detection" in ChIP-Seq data \cite{wilbanks:2010}.
+many methods published for ``peak detection" in ChIP-Seq data \cite{Wilbanks2010Evaluation}.
 
@@
 
-To illustrate this idea we applied SMASH to ChIP-seq data from a region of length $2^{15} (\approx 33k)$ basepairs from chromosome 1
-(hg18 (or 19?) chr1:880001-1011072). The estimated intensity is shown in Figure \ref{fig:seq_peak_est}, overlaid on peaks called by
-the popular peak calling software MACS \cite{}. We see that the locations with the strongest SMASH intensity estimates 
+To illustrate this idea we applied SMASH to ChIP-seq data from a region of length $2^{17} (\approx 131k)$ basepairs from chromosome 1
+(hg19 chr1:880001-1011072). The estimated intensity is shown in Figure \ref{fig:seq_peak_est}, overlaid on peaks called by
+the popular peak calling software MACS \cite{Zhang2008Modelbased}. We see that the locations with the strongest SMASH intensity estimates 
 corresponds to peaks found by MACS.
@@
 For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}.
-However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable \cite{}.
-We could thus incorporate ASH into other types of transformations such as curvelets \cite{}, which would be a potential direction for future work.
+However, recent research in image denoising problems has shown that discontinuities along edges present in many images such as photographs might render wavelet transformations undesirable \cite{Cande00}.
+We could thus incorporate ASH into other types of transformations such as curvelets \cite{Cande00}, which would be a potential direction for future work.
 \newpage
@@
 Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$.
-As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
+Again we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
 \begin{eqnarray}
@@
 These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters.
-Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels.
-This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
+Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the wavelet coefficients at the finer levels.
+This is likely because the distribution of the wavelet coefficients is extremely skewed, especially when the true coefficients are small (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
 One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH).
@@
 
-Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Multiscale}) rather than as described above.
+Note here that for the reconstructed signal to possess the property of shift invariance (\cite{Coifman1995Translationinvariant}), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Bayesian}) rather than as described above.
 The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points.

### 2016-03-03 paper/supplementary/supplementary.tex
started writing supplementary materials

--- 2016-02-22 paper/draft_6.tex
@@
 
-\section{Abstract}
+\section{Simulation study for Gaussian data}
+As noted in the main text, we performed an extensive simulation study for Gaussian errors using a variety of test functions (7 mean functions and 5 variance functions, including constant variance), signal-to-noise ratios (SNR = 1 and 3) and sample sizes ($T=256,512,1024$).
+The results for $T=256,512$ are saved under ~/res_paper/res_gaus_256.RData and ~/res_paper/res_gaus_512.RData respectively, while results for $T=1024$ are presented in a DSC framework (https://github.com/stephens999/dscr), saved under ~/res_paper/res_gaus_dscr.RData.
+In particular, we include an RShiny app as an interactive way to present the results for $T=1024$, the code for which can be found in the dscr-smash repo (https://github.com/zrxing/dscr-smash), under graphs.Rmd.
+In particular, users can view the boxplots of MISEs for the methods and test functions they are interested in by checking the appropriate boxes.
+For more details refer to graphs.Rmd.
 
-\section{Introduction}
+In addition to the performance of the various methods, Table \ref{} also provides additional information for each of the method that we used in the simulation study.
 
-Shrinkage and sparsity play a key role in many areas of modern statistics, including, for example, high-dimensional regression \cite{Tibshirani1996Regression}, covariance or precision matrix estimation \cite{Bickel2008Covariance}, multiple testing \cite{efron:xx} and signal denoising \cite{Donoho1994Ideal, donoho95}.
-One attractive way to achieve shrinkage and sparsity is via Bayesian or Empirical Bayes (EB) methods (e.g.\cite{efron?, Johnstone2005Empirical, Clyde2000Flexible,george.mccullogh,bayesian-covariance-estimation}).
-However, these methods are usually perceived to require context-specific implementations, and this overhead can limit their use in practice.
-Here we consider a flexible EB approach to shrinkage, which we call {\it adaptive shrinkage}, whose goal is to provide a generic shrinkage method that could be useful for a range of applications.
-We show how this single shrinkage method can produce effective results for several denoising problems, including smoothing Gaussian means in the presence of heteroskedastic variance, smoothing of Gaussian variances, and smoothing Poisson means.
-These are all settings that are relatively underserved by existing EB implementations, and indeed  we are unaware of any existing EB implementation for smoothing either the mean or the variance in the heteroskedastic Gaussian case.
-Consistent with previous studies (\cite{Antoniadis2001Wavelet}, \cite{Besbeas2004Comparative}) we find these EB methods to be more accurate than commonly-used thresholding rules, and, in the Poisson case, competitive with a purpose-built EB method.
+\section{Simulation study for Poisson data}
+The results from the simulation study for Poisson noise are shown in the following tables.
+Each of the six tables presents results for the corresponding mean function, and includes results for all three (min,max) intensity levels ((0.01,3), (1/8,8), (1/128,128)).
 
-Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, are uncommon, particularly compared with the well-studied homoskedastic case.
-Previous non-wavelet-based work includes \cite{Fan1998Efficient}, who estimated the variance by smoothing the squared residuals using local polynomial smoothing, \cite{Brown2007Variance}, who employed difference-based kernel estimators, and \cite{Menictas2015Variational}, who developed a Bayesian mean field variational methodology for both mean and variance estimation.
-The only wavelet-based method for variance estimation we have found is \cite{Cai2008Adaptive}, which applied a wavelet thresholding approach to first order differences.
-Unfortunately software implementation is only available in \cite{Menictas2015Variational}.
-
-For Poisson data, variance stabilizing techniques together with normal approximations have been proposed by \cite{D93} and \cite{Fryzlewicz2004HaarFisz}, by exploiting the mean-variance relationship of a Poisson distribution.
-\cite{Kolaczyk1996NonParametric} and \cite{kolaczyk1999wavelet} derived thresholds achieving optimal asymptotic properties in the context of wavelet transformations, similar to the thresholds in the i.i.d.
-Gaussian case.
-However, \cite{Fryzlewicz2004HaarFisz} is computationally inefficient due to the presence of external cycle-spinning, and threshold-based methods may not result in satisfactory finite sample performance.
-Furthermore, all of these methods are sensitive to the choice of the primary resolution level as subsequent simulations will show.
-Multiscale analysis using recursive dyadic partitions within a Bayesian framework was later developed by \cite{Kolaczyk1999Bayesian} to make use of a particular form of likelihood factorization, but a relatively inflexible conjugate prior was chosen.
-
-%Methods used to achieve shrinkage and sparsity include simple thresholding rules
-%(e.g.~\cite{TI-thresh, SURE, others?,thresholding-outside-of-wavelets?}), penalized likelihood approaches (e.g.~\cite{lasso,elasticnet,glasso}), and 
-%Bayesian or Empirical Bayesian (EB) methods (e.g.\cite{efron?, johnstone.silverman.xx,clyde.george.jrssb,george.mccullogh,bayesian-covariance-estimation}.
-%While thresholding rules and penalized likelihood methods can possess good asymptotic properties in theory, empirical
-%comparisons have found that Bayesian and EB methods can perform better in practice \cite{antoniadis:2001,guan.stephens.largescaleregression}.
-%However, Bayesian and EB methods are usually perceived to require context-specific implementations, and this
-%overhead can limit their application.
-%Our goal here is to outline a strategy that can reduce this implementational overhead, and apply it to produce EB shrinkage methods for signal denoising problems.
-%DO we want to highlight ash or the generic strategy? Or both? Current text highlights mostly the strategy,
-%leaving ash as just a component of it.
-%Could add "Indeed one of our goals is to showcase the flexibility of this EB approach to shrinkage" as second
-%sentence of next paragraph?
-
-%Among their most prominent
-%applications has been signal denoising, which can be achieved by inducing sparsity or shrinkage in a transformed (e.g. wavelet)
-%domain \cite{donoho.johnston.xx}. This approach to signal denoising has strong theoretical support, and is often accurate and computationally convenient, so it has
-%become widely used. Consequently many approaches have been suggested for achieving the desired shrinkage, including both
-%simple thresholding rules \cite{TI-thresh, SURE, others?} and Bayes or Empirical Bayes (EB) methods \cite{johnstone.silverman.xx,clyde.george.jrssb}.
-%Although classical thresholding rules have been shown to possess good asymptotic properties in theory, EB methods often
-%perform better in practice \cite{antoniadis:2001}.
-
-\def\ash{{\tt ash}}
-\def\bhat{\hat{\beta}}
-\def\shat{\hat{s}}
-
-The {\it adaptive shrinkage} (\ash) method is described in detail in a companion paper, \cite{stephens:2015}, which applies \ash~to estimate false discovery rates (FDR) in multiple testing settings.
-Here we apply the same method to the signal denoising problems described above.
-In brief, \ash~aims to provide EB shrinkage estimates of quantities $\beta_1,\dots,\beta_J$, given observed estimates of these quantities $\bhat_1,\dots,\bhat_J$, and corresponding standard errors $\shat_1,\dots,\shat_J$.
-In common with most EB methods \ash~assumes that the $\beta_j$ come from some common underlying distribution, $g$, which is estimated from all the data (as $\hat{g}$ say), and uses the posterior mean,  $E(\beta_j | \bhat_j, \shat_j, \hat{g})$ as a shrinkage estimate of $\beta_j$.
-Key features that make \ash~attractive as a flexible and generic approach to shrinkage include: i) its flexible semi-parametric modelling of $g$, under the constraint that it be uni-modal at 0 (and, optionally, symmetric); ii) its incorporation of the precision of each measurement through the standard errors $\shat_j$, so that the amount of shrinkage adapts to the precision of each measurement;  iii) its computational simplicity and speed: e.g.~our {\tt R} implementation typically takes a fraction of a second for $J=1000$; iv) its computational stability, with, for example, minimal problems due to convergence to local optima \cite{stephens:2015}.
-
-% treating the observations as conditionally independent from a normal model, $\bhat_j | \beta_j, \shat_j \sim N(\beta_j, \shat_j)$.
-Given the estimate $\hat{g}$ for $g$, \ash~then computes the posterior distiributions $\beta_j | \bhat_j, \shat_j, \hat{g}$,vand provides the posterior mean of $\beta_j$ as a shrinkage estimate for $\beta_j$.
-
-%The name ``adaptive shrinkage" comes from the fact that shrinkage is adaptive to both the overall signal in the data (through estimation of $g$), and to the precision of each observation (through incorporation of $\shat_j$), with imprecise observations being shrunk most strongly.
-
-The \ash~method makes assumptions, particularly conditional independence of observations, and normality of likelihood $p(\bhat_j | \beta_j, \shat_j)$, that will often be violated in practice,
-and indeed are violated in our applications here. However, as we demonstrate later, it can nonetheless produce good shrinkage estimates. 
-Essentially, we treat
-%highlighting the potential of treating ??
-\ash~as a generic or ``black box" shrinkage procedure, which inputs
-estimates and their corresponding standard errors and outputs shrinkage estimates, without worrying too much about 
-the details. Of course, one must be careful about how far one takes this.  And in more complex applications 
-(e.g. large-scale regression and covariance estimation) it is unclear whether this strategy can be usefully applied. However,
-we believe our results here for signal denoising, together with those in \cite{stephens:15} for FDR estimation, illustrate \ash's potential and flexibility. 
-%maybe move to discussion
-
-%In this paper we use \ash~to tackle several signal denoising problems,  including Poisson smoothing,
-%and smoothing both the mean and variance of heteroskedastic Gaussian data. 
-Shrinkage methods are widely-used in signal denoising applications, because signal denoising can be accurately and conveniently achieved by shrinkage in a transformed (e.g.~wavelet) domain \cite{Donoho1994Ideal}.
-Commonly-used shrinkage methods include both
-simple thresholding rules \cite{Coifman1995Translationinvariant, Donoho1994Ideal, donoho95} and EB methods \cite{Johnstone2005Empirical, Clyde2000Flexible}.
-Being an EB method, \ash~has much in common with these previous EB methods, but generalizes them in two ways: first, 
-\ash~allows more flexibility in the underlying distribution $g$ than the Laplace or spike-and-slab
-distributions used in \cite{Johnstone2005Empirical, Clyde2000Flexible}; second, \ash~allows for variations in precision in the transformed observations (e.g.
-wavelet coefficients).
-The latter property is particularly important for
-the Poisson and heteroskedastic Gaussian settings we consider here.
-
-Software implementations of our methods are available in the R packages {\tt ashr} (Adaptive SHrinkage in R)
-and {\tt smash} (SMoothing by Adaptive SHrinkage), available from 
-\url{http://www.github.com/stephens999/ashr} and \url{http://www.github.com/stephenslab/smash} respectively.
-
-%Although classical thresholding rules have been shown to possess good asymptotic properties in theory, EB methods often
-%perform better in practice \cite{antoniadis:2001}.
-
-%Our goals in this paper are therefore two-fold. FIrst, to showcase the potential for the adaptive shrinkage method to provide a simple and effective
-% solution to shrinkage estimation in important practical problems; and, second, to provide software implementations of this 
-% idea for smoothing Poisson and heteroskedastic Gaussian signals - settings that are underserved by existing implementations.
-
-%In recent years, various shrinkage and thresholding procedures have become ever more popular in many applications where sparsity is desired.
-Here ``sparsity'' is loosely defined in that it also includes the case where many terms are near-zero, as opposed to exactly zero.
-The most prominent usage of such procedures appear in multiresolution denoising analyses such as wavelets, where sparsity in a transformed domain often corresponds to smoothness in the data space [references].
-Other examples include estimation of covariance and precision matrices (though thresholding is used more often here since zero terms are actually desired) [references], accounting for different measurement precisions in FDR control for multiple testing [references], or more generally optimizing penalized likelihood problems such as LASSO [references].
-In this paper we will look at a flexible and adaptive shrinkage method named ASH, and illustrate its value in two key areas of univariate wavelet denoising.
-
-%Before delving deeper into the two denoising tasks, we first present a brief overview of wavelet estimators.
-These estimators have become extremely popular in nonparametric regression problems following the seminal paper by Donoho \& Johnstone (1994).
-Wavelet methods are locally adaptive in that they achieve the optimal minimax rate over a wide variety of functions, yet are also computationally faster than many other adaptive methods such as variable-bandwidth kernel methods [antoniadis 2001].
-While classical thresholding estimators have been shown to possess optimal asymptotic properties, an extensive simulation study by Antoniadis et al.
-(2001) has demonstrated that various Bayesian shrinkage methods are usually more adaptive than thresholding methods in finite samples, outperforming the latter in terms of mean squared error (MSE).
-However, many Bayesian methods require specific distributional assumptions, and are not easily extensible to more complex problems, two of which we subsequently describe.
-On the other hand, our method simplies the task by making approximations, while still possessing good finite sample performance and computational efficiency.
-These approximations also allow us to use ASH as the common shrinkage procedure in both the problems.
-
-%Both the aforementioned problems are harder to deal with than the classical problem with i.i.d.
-Gaussian errors, and usually requires extension of the ideas from the latter task.
-Before proceeding to describe the two problems in detail, we will first describe briefly the portion of ASH that performs shrinkage.
-
-%The flexibility and computational efficiency of ASH is immediately obvious, which motivates us to extend this method to the more complex wavelet settings described here.
-As an Empirical Bayes procedure, ASH borrows information across all available data and is extremely data adaptive.
-At the same time, the key advantage of ASH over other Empirical Bayes procedures such as EbayesThresh [Johnstone \& Silverman (2005)] and the commonly used ``spike-and-slab'' prior (is there a reference for this?) is that variable variances are allowed as input, a feature which latter methods lack.
-This is also the primary reason we can use ASH as the only shrinkage procedure in both the problems described above.
-Furthermore, Gaussian mixtures can effectively approximate any unimodal distribution, allowing for an extremely flexible prior.
-In tackling these two specific problems, we can speed up the entire signal denoising problem via likelihood approximations (discussed in the next section), allowing our method to be computationally efficient without compromising accuracy.
-Typical wavelet methods require the specification of a primary resolution level as a ``tuning'' parameter, which could substantially influence the accuracy of the method.
-However, applying ASH to every resolution in the wavelet transformationwe spares us the need for such a parameter.
-For an in-depth understanding of the original motivations and applications of ASH, see Stephens (??).
-With the main shrinkage method accounted for, we will proceed to explore the two aforementioned problems in detail.
-Note that one only needs to supply a vector of estimates $\hat{\Gb}$ and their standard errors se$(\hat{\Gb})$ to ASH to obtain posterior estimates; hence, we will focus on obtaining these estimates and standard errors when describing our methods.
-
-\section{Methods}
-
-\def\bY{\bm{Y}}
-\def\bmu{\bm{\mu}}
-\def\bp{\bm{p}}
-\def\be{\bm{\epsilon}}
-\def\tbY{\tilde\bY}
-\def\tbe{\tilde\be}
-\def\tbmu{\tilde\bmu}
-\def\tmu{\tilde\mu}
-\def\tY{\tilde{Y}}
-\def\s{\sigma}
-\def\|{\,|\,}
-
-\subsection{Adaptive shrinkage}
-
-Here we briefly outline the adaptive shrinkage method; see \cite{stephens:2015} for full details.
-Adaptive shrinkage (\ash) is an EB method
-for estimating quantities $\beta=(\beta_1,\dots,\beta_n)$ from noisy estimates 
-$\bhat=(\bhat_1,\dots,\bhat_n)$ and their corresponding standard errors $\shat = (\shat_1,\dots,\shat_n)$. 
-In its simpest form it assumes the hierarchical model
-\begin{align}
-\beta_j \| \shat_j & \sim g \\
-\bhat_j \| \beta_j, \shat_j & \sim N(\beta_j, \shat_j^2),
-\end{align}
-where the distribution $g$ is constrained to be unimodal and symmetric. This constraint on $g$ can
-be flexibly achieved using 
-a mixture of zero-centered normal distributions
-
-\begin{equation}
-g(\cdot)=\sum_{k=0}^K \pi_0 N(\cdot;0,\sigma_k^2),
-\end{equation}
-where the mixture weights $\pi_0,\dots,\pi_K$ are non-negative and sum to 1, and $N(\cdot; \mu,\sigma^2)$ denotes
-the density of a normal distribution with mean $\mu$ and variance $\sigma^2$.
-A key idea, which substantially simplies inference, is to take
-$\sigma_0,\dots,\sigma_K$ to be a fixed grid of values. ranging from very small (e.g.~$\sigma_0=0$,
-in which case $g$ includes a point mass at 0) to very large. Estimating $g$ then boils down to estimating
-the mixture weights $\pi$, which is done by maximum likelihood using a simple EM algorithm.
-Given an estimate $\hat{g}$ for $g$, the conditional distributions $p(\beta_j \| \bhat, \shat, \hat{g})$ are analytically
-tractable, and the posterior mean $E(\beta_j \| \bhat, \shat, \hat{g})$ provides a shrinkage point estimate for $\beta_j$.
-
-\cite{stephens:2015} also introduces various embellishments that are implemented in the {\tt ashr}
-package, including generalizing the normal likelihood to a $t$ likelihood, and dropping the symmetric
-constraint on $g$ by replacing the mixture
-of normals with a more flexible (though less smooth) mixture of uniforms. However, we do not use these embellishments here.
-
-%\cite{stephens:2015} demonstrates the potential for this adaptive shrinkage approach to  estimate false discovery rates and related quantities in settings where the primary goal is to identify the $\beta_j$ that differ ``significantly" from 0.
-Our work here compliments this, by demonstrating  the potential for this approach to provide the adaptive shrinkage estimates that its name promises.
-
-\subsection{Signal Denoising}
-
-A common generic signal denoising problem, sometimes known as ``non-parametric regression", involves
-estimating a ``spatially-structured" mean $\bmu=(\mu_1,\dots,\mu_T)$, from corresponding
-noisy observations $\bY = (Y_1,\dots,Y_T)$, where $t=1,\dots,T$ indexes location in a one-dimensional space,
-such as time, or, as in our example later, location along the genome. 
- By ``spatially-structured" we mean that $\mu_t$ will often be similar to $\mu_t'$ for small $|t-t'|$, though we do not rule
-out occasional abrupt changes in $\mu$.  For convenience we assume that $T=2^J$ for some integer $J$, as is common when using wavelet methods.
-
-The most studied denoising problem is the homoskedastic Gaussian case; that is, 
-the data $Y_t$ have Gaussian noise and constant variance.
-Here we consider the more general case of Gaussian data with
-spatially-structured mean {\it and} spatially-structured (non-constant) variance. 
-In some settings the changes in variance may themselves be of interest, and our methods provide explicit estimates for the variance as well as the mean.
-In addition we consider Poisson data (where the variance depends on the mean, so
-a spatially-structure mean implies spatially-structure variance).
-To build up to these more interesting cases we start with the simplest setting: 
-Gaussian noise with known variance.
-
-\subsubsection{Gaussian noise; estimate mean (known variance)}
-
-Suppose the $Y_t$ are independent noisy observations of the $\mu_t$, with Gaussian noise of known variance $\s^2_t$. That is,
-\begin{equation}\label{eq:1d gaussian model}
-\bY =\bmu+\be
-\end{equation}
-where $\be \sim N(0,D)$ with $D$ the diagonal matrix with diagonal entries $(\s_1^2,\dots,\s_T^2)$.
-
-%To motivate our method, we first describe wavelet shrinkage from a Bayesian perspective.
-Wavelet denoising involves first applying a discrete wavelet transform to the data $\bY$. This
-involves pre-multiplying $\bY$ by an orthogonal $n\times n$ matrix $W$ that depends on the orthonormal wavelet basis chosen. Pre-multiplying (\ref{eq:1d gaussian model}) by $W$ yields
-\begin{equation} 
-W\bY=W\bmu + W\be 
-\end{equation}
-which, using $\,\tilde{}\,$ to denote the wavelet transform, we write
-\begin{equation} \label{eq:wc}
-\tbY=\tbmu + \tbe,
-\end{equation}
-where $\tbe \sim N(0,W D W')$.
-
-A key feature of the wavelet transform is that if $\bmu$ is spatially structured 
-then many elements of $\tbmu=W\bmu$ will tend to be close to zero, and vice versa.
-In other words, smoothing in the data domain corresponds to shrinking in the wavelet domain.
-Thus, one can obtain a spatially structured estimate of
-mean $\bmu$ by first using shrinkage methods to estimate $\tbmu$ and then
-reversing the wavelet transform.
-
-%This process is often referred to as ``wavelet shrinkage estimation", because the estimates $\tmu_j$ are obtained from $\tY_j$ by ``shrinking" them towards zero.
-
-Here we use the adaptive shrinkage method to obtain shrinkage estimates for $\tbmu$.
-Focussing on the marginals of (\ref{eq:wc}), we have
-\begin{equation} \label{eq:normlik}
-\tY_j | \tmu_j, s^2_j \sim N(\tmu_j, \omega^2_j).
-\end{equation}
-%Note that the elements of $\tY$ are not independent unless the variances $\sigma^2_t$ are all equal. 
-where
-\begin{equation}
-\omega^2_j:=\sum_{t=1}^T \s^2_t W_{jt}^2,
-\end{equation}
-are the diagonal elements of $WDW'$.
-Thus, applying ash with $\bhat_j = \tY_j$ and $\shat_j = \omega_j$ yields shrinkage estimates for the $\tmu_j$.
-(In practice it is important to group the wavelet-transformed observations $j$ 
-by their resolution level before shrinking; see note below.)
-Of course, by focusing on the marginals we are ignoring any correlations among the $\tY_j$, and this
-is the primary simplification here. (We are not alone in making this simplification;
-see also \cite{Silverman1999Wavelets} for example.)
-
-The above outlines the basic strategy, but there are some important
- additional implementational details:
-\begin{itemize}
-\item Rather than use a single wavelet transform, we use the ``non-decimated" wavelet transform, which treats the observations as coming
-from a circle, rather than a line, and averages results over all $T$ possible rotations of the data.
-Although not always necessary, this is a standard trick to reduce artifacts that can occur near discontinuities in the underlying signal (eg.
-\cite{Coifman1995Translationinvariant}).
-%COMMENT: WHat about reflection before doing this? ans: all the test fns are periodic
-%DO OTHER EB APPROACHES CONSIDER THE NDWT? yes ebayesthresh software discusses this option
-\item The non-decimated wavelet transform yields $T$ wavelet coefficients (transformed values of $\bY$) 
-at each of $J=\log_2(T)$ resolution levels.
-We apply ash separately to the wavelet coefficients at each resolution level, so that
-a different distribution $g$ for the $(\tmu_j)$ is estimated for each resolution. This is the usual way that
-EB approaches are applied in this context (e.g.~\cite{Johnstone2005Empirical}) and indeed is crucial because
-the underlying distribution $g$  will vary with resolution (because smoothness of $\bmu$ will vary with resolution).  
-\item Although we have presented the wavelet transform as a matrix multiplication, which is an $o(T^2)$ operation, in practice both the wavelet transform and the inverse transform are implemented using
-efficient algorithms \cite{Beylkin1992Ontherepresentation,Coifman1995Translationinvariant}, implemented in the {\tt wavethresh} package \cite{Nason_wavethresh}, taking only $O(T\log T)$ operations. 
-\end{itemize}
-%\item Ash yields a posterior distribution for each $\tmu_t$. A simple approach would
-%be to use the posterior mean for $\tmu_t$ and then invert the wavelet transform; however we instead use the delta method?
-
-%Since $\mathbb{V}(Y)=\s^2I$,
-%\begin{eqnarray}\label{eq:waveletcoef}
-%\bm{d}\sim N_n(\bm{\Ga},\s^2I)
-%\end{eqnarray}
-%where $\bm{\Ga}=W\mathbb{E}(\bm{Y})$.
-This implies that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods for $\Ga_t$, $i=1,...,n$.
-As such, a natural and computationally convenient approach is to set independent priors on $\Ga_t$ as a form of ``shrinkage''.
-Here we apply the priors from ASH to each resolution level separately, resulting in
-%%Although there are many choices for the prior, we use the Gaussian mixture prior from ASH in our method, given by
-%\begin{eqnarray}\label{eq:ashprior}
-%\Ga_{jk}=\sum_{l=1}^m \pi_l^{(j)} N(0,(s_l^{(j)})^2)
-%\end{eqnarray}
-%with $\sum_l \pi_l^{(j)}=1$, for $j=1,...,J$.
-$\pi_t^{(j)}$ and $(s_t^{(j)})^2$ are hyperparameters that are shared between coefficients in the same resolution level, and $m$ is the number of mixture components.
-In ASH, $m$ is usually chosen to reasonably approximate any unimodal distribution, while maintaining an acceptable computational speed.
-Note that, for notational convenience, we have switched to a double index following standard wavelet convention for indices: here $j=1,...,J$ is the resolution level, and $k=0,...,2^j-1$ is the location within each resolution level $j$.
-By applying the inverse wavelet transform to the posterior mean $\hat{\bm{\Ga}}$ that ASH produces, one can obtain the posterior mean of $\bm{\mu}$, which serves as an estimate that minimizes the MSE.
-One could also construct credible bands using the posterior variances.
-%
-%While many existing methods perform well in the presence of i.i.d.
-(Gaussian) errors, heteroskedastic (but still independent) errors present a different challenge.
-One key obstacle when dealing with heteroskedastic errors is that the likelihood for $\bm{\Ga}$ does not necessarily factorize.
-Given the true variances and hence the likelihood, one could compute the full posterior distribution using some specified prior.
-However, this would be computationally cumbersome, and may be infeasible when extended to multiple signals or higher dimensions.
-In this case, a suitable prior might also be difficult to find.
-As such, one key aspect of our approach is to treat the wavelet coefficients as if they were independent, so that the true likelihood is approximated by a composite likelihood (see Silverman (1999) for an example where this is done).
-
-%To describe our approach in more detail, first assume that the true variance function is known and given by $\mathbb{V}(\Ge_t)=\s_t$, and that the true mean function is given by $\bm{\mu}=(\mu_1,...,\mu_t)$, where $T=2^J$ for some positive integer $J$.
-Hence
-%\begin{eqnarray}
-%\bm{Y}\sim N_n(\bm{\mu},\Sigma)
-%\end{eqnarray}
-%where $\Sigma=\textrm{diag}(\s_1,...,\s_T)$ is a diagonal matrix.
-For the rest of this subsection, we will use the non-decimated wavelet transform (NDWT) instead of the standard DWT to achieve translation invariance.
-This in turn reduces the presence of artifacts, which often occur near discontinuities in the underlying signal (see eg.
-Coifman \& Donoho (1995)).
-Then,
-%\begin{eqnarray}
-%\bm{d}\sim N_n(\bm{\Ga},\tilde{\Sigma})
-%\end{eqnarray}
-%where $\bm{d}$ is the vector of detail coefficients, $\bm{\Ga}=W\bm{\mu}$, and $\tilde{\Sigma}=W\Sigma W^T$, where $W$ is the matrix associated with the NDWT for a given wavelet basis.
-By treating the likelihood for $\bm{\Ga}$ as if it were independent, it can be written as follows(using the double index mentioned above):
-%\begin{eqnarray}\label{eq:likelihood}
-%L(\bm{\Ga}|\bm{d})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(d_{jk}|\Ga_{jk})
-%\end{eqnarray}
-%where $P(d_{jk}|\Ga_{jk})=\phi(d_{jk};\Ga_{jk},\tilde{\Sigma}_{(jk,jk)})$.
-Note that there are $n$ coefficients at each resolution level instead of $2^j$ for resolution $j$ due to the NDWT.
-Here $\phi$ denotes the Gaussian density function.
-Since $\Sigma$ is diagonal, it is easy to see that $\tilde{\Sigma}_{(jk,jk)}=\sum_{t=1}^T \Sigma_{ti}_{tW_{jk,i}^2$.
-In our method, we use ASH to assign independent priors to $\Ga_{jk}$ as with \eqref{eq:ashprior}.
-%ASH also allows us to estimate the $\pi_t$'s via a maximum likelihood approach and fix the $\s_t$'s by using a grid of values.
-This particular choice of prior specification is extremely flexible, being able to approximate any symmetrical zero-centered distribution, as well as allowing for a relatively easy estimation of the hyperparameters through empirical Bayes.
-See ASH for more details regarding this choice of prior (?)
-%While ASH produces shrunken estimates of $\Ga_{jk}$ for $j,k>0$, we estimate $\Ga_{00}$ using the corresponding scaling coefficient, which seems intuitively appealing.
-Finally, we can obtain an estimate of $\mu$ by using the average basis inverse, which is essentially an average of the inverse wavelet transforms for every shift of the data (see Coifman \& Donoho (1995)) since we are using the NDWT.
-Although the method described here uses a matrix formulation for easier conceptual understanding, the actual NDWT and inverse transform are done through Mallat's pyramid algorithm, taking only $n\log(n)$ time.
-
-\subsubsection{Estimating spatially structured variance (known mean)}
-
-Although we assumed variances to be known above, the problem of variance estimation is itself non-trivial. 
-A common approach is to assume that the variance is constant ($\sigma_t=\sigma$), and that changes in the adjacent means $\mu_t-\mu_{t+1}$ are negligible, and to use an unbiased estimate for $\sigma$ such as
-\begin{equation} \label{eq:constvar}
-\hat{\sigma}^2 = (1/2T) \sum_{t=1}^{T} (Y_t-Y_{t-1})^2
-\end{equation}
-with $Y_0:=Y_T$.
-Here we make the more flexible assumption that the variance function is spatially structured, and use wavelet shrinkage to estimate it.
-Our approach is similar in spirit to \cite{Cai2008Adaptive}, but we jointly estimate the mean and variance functions whereas they estimate only the variance function.
-
-Assume initially that the mean $\mu_t$ is known, and define
-\begin{eqnarray}\label{eq:varobs1}
-Z_t^2=(Y_t-\mu_t)^2_t
-\end{eqnarray}
-to be the ``observations'' for the unknown variance function. Note that $\mathbb{E}(Z_t^2)=\s_t^2$, and so
-we have a mean estimation problem.
-To tackle this we use the mean estimation procedure above (effectively treating the wavelet-transformed values $WZ_t^2$ as Gaussian when really they are linear combinations of $\chi^2$ random variables).
-To apply this procedure we need the variance
-of $Z_t^2$, $\mathbb{V}(Z_t^2)$, which is unknown.
-Here we use $\frac{2}{3}Z_t^4$ as an 
-unbiased estimator for $\mathbb{V}(Z_t^2)$. (This follows from the distributional result that, when $Z^2 \sim \s^2 \chi^2$, then $\mathbb{E}(Z^4)= 3\s^4$, and $\mathbb{V}(Z^2)=2\s^4$.)
-
-Despite the approximations being made here, we have found this procedure to work well in practice in most cases,
-perhaps with a tendancy to oversmooth quickly-varying variance functions. 
-%Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels.
-This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
-
-%MOVE THIS TO DISCUSSION?
-%Of course, better likelihoods and priors could be used that reflect the skewness in the distributions of the ``observations'', but we found that a normal approximation works reasonably well (especially for smoother variance functions), and has the key advantage of being easy and fast to implement.
-The variance estimation process is then very similar to one for mean estimation as described above, with a few extra details.
-The full procedure is outlined in Appendix \ref{app:var estimation}.
-
-\subsubsection{Estimating spatially-structured mean and variance}
-
-Having specified procedures for estimating the means with variances known, and the variances with means known,
-we iterate these procedures to deal with the (typical) case where both are unknown.
-We initialize the algorithm by estimating the variance vector $\bm{\s}^2$ using
-\begin{eqnarray}\label{eq:initial var est}
-\hat{\s}_t^2=\frac{1}{2}\left((Y_t-Y_{t-1})^2+(Y_t-Y_{t+1})^2\right)
-\end{eqnarray}
-where $Y_0\equiv Y_n$ and $Y_{T+1}\equiv Y_1$ (equivalent to putting the observations on a circle). 
-%This estimator has the property that it is approximately unbiased for the variance at the two corresponding points, provided that the mean and the variance function is smooth enough.
-Then we iterate:
-\begin{enumerate}
-\item[1] Estimate $\bm{\mu}$ as if $\bm{\s}^2$ is known (with the value obtained from the previous step).
-\item[2] Estimate $\bm{\s}^2$ as if ${\bm{\mu}}$ is known (with the value obtained by the previous step); return to 1.
-\end{enumerate}
-We cannot guarantee that this procedure will converge in general. In our simulations we found
-that two iterations of steps 1-2 yielded accurate results (so the full procedure consists of initialize + Steps 1-2-1-2).
-
- \subsection{Smoothing Poisson data}
-
-\def\Poi{\text{Poi}}
-\def\Bin{\text{Bin}}
-
-Now assume that each $Y_t$ has a Poisson distribution with mean $\mu_t$.
-To do denoising here we apply adaptive shrinkage to the Poisson multiscale models
-from \cite{Nowak2000Statistical} and \cite{Timmermann1999Multiscale}, which are an analogue of
-wavelet methods for Poisson data.
-
-To explain the idea, first recall the following elementary distributional result:
-if $Y_1,Y_2$ are independent, with $Y_j \sim \Poi(\mu_j)$ then 
-\begin{align}
-Y_1 + Y_2 & \sim \Poi(\mu_1 + \mu_2) \\
-Y_1 | (Y_1+Y_2) & \sim \Bin(Y_1+Y_2, \mu_1/(\mu_1+\mu_2)).
-\end{align}
-
-To extend this to $T=4$, introduce the notation $v_{i:j}$ to denote, for any vector $v$, 
-the sum $\sum_{t=i}^j v_t$.  Then 
-\begin{align} 
-Y_{1:4} & \sim \Poi(\mu_{1:4}) \label{eqn:y14} \\
-Y_{1:2} | Y_{1:4} & \sim \Bin(Y_{1:4}, \mu_{1:2}/\mu_{1:4})  \label{eqn:y12} \\
-Y_1 | Y_{1:2} & \sim \Bin(Y_{1:2}, \mu_1/\mu_{1:2}) \label{eqn:y1} \\ 
-Y_3 | Y_{3:4} & \sim \Bin(Y_{3:4}, \mu_3/\mu_{3:4}). \label{eqn:y3}
-\end{align} 
-Together these models are exactly equivalent to $Y_j \sim \Poi(\mu_j)$, and
-they decompose the overall distribution $Y_1,\dots,Y_4$ into parts involving aspects of the data at 
-increasing resolution: (\ref{eqn:y14}) represents the coarsest resolution (the sum of all data points), 
-whereas (\ref{eqn:y1}) and (\ref{eqn:y3}) represent the finest resolution, with (\ref{eqn:y12}) in between. 
-Further, this representation suggests a reparameterization, from $\bmu=(\mu_1,\mu_2,\mu_3,\mu_4)$
-to $\mu_{1:4}$ plus the binomial parameters $\bp=(\mu_{1:2}/\mu_{1:4}, \mu_1/\mu_{1:2}, \mu_3/\mu_{3:4})$, where 
-$p_1$ controls lower-resolution changes in the mean vector $\mu$ and $p_2,p_3$ control higher resolution changes.
-
-This idea extends naturally to $T=2^J$ for any $J$, reparameterizing $\bmu$ into its sum $\mu_{1:T}$
-and a vector $\bp$ of $T-1$ binomial probabilities that capture features of $\bmu$ at different resolutions.
-This can be thought of as an analogue of the wavelet transform of $\bmu$ for Poisson data.
-
-Note that, in this reparameterization, $p_j=0.5 \, \forall j$ corresponds to the case of a constant mean vector,
-and values of $p_j$ far from 0.5 correspond to large changes in $\mu$ (at some scale).
-Thus estimating a spatially-structured $\bmu$ can be achieved by shrinkage estimation of $\bp$, with shrinkage towards $p_j=0.5$.
-Both \cite{kolaczyk1999wavelet} and \cite{Timmermann1999Multiscale} use purpose-built Bayesian models to
-achieve this shrinkage, by introducing a prior distribution on elements of $\bp$ that is
-a mixture of a point mass at 0.5 (creating shrinkage toward 0.5) 
-and a Beta distribution. Here we take a different approach, reparameterizing $\alpha_j = \log(p_j/(1-p_j))$,
-and then using adaptive shrinkage to shrink $\alpha_j$ towards 0.
-
-To apply adaptive shrinkage we need an estimate $\hat{\alpha}_{j}$ and corresponding standard error $\hat{s}_j$
-for each $j$. This boils down to estimating a log-odds ratio, and its standard error, which is a well-studied problem
-(e.g.
-\cite{Gart1967Bias}).
-The main challenge is in dealing satisfactorily with cases where the maximum likelihood estimator (MLE) for $\alpha_j$ is infinite.
-Our choice of estimates, based on results from \cite{Gart1967Bias}, are described in Appendix \ref{}.
-
-The output of adaptive shrinkage is a posterior distribution on each $\alpha_j$. The simplest approach
-to obtain estimates of $\bmu$  would be to estimate
-$\alpha_j$ by its posterior mean, and then reverse the reparameterization. 
-The resulting estimate of $\mu_t$ would be the exponential of the posterior
-mean for $\log(\mu_t)$ (because each $\log(\mu_t)$ is a linear combination of $\alpha_j$).
-Alternatively we can estimate $\mu_t$ by approximating its posterior mean using the Delta method; see Appendix \ref{app:reconstruction}.
-Both methods are implemented in our software; for the results here we use the latter method 
-to be more comparable with previous approaches that estimate $\mu$ on the raw scale rather than $\log$ scale.
-%Note that, just as for the original parameterization $Y_j \sim \Poi(\mu_j)$, the likelihood for the parameters in this reparameterization factorizes into a product of four terms, one for each parameter, corresponding to the four distributions (\ref{eqn:y14})-(\ref{eqn:y3}).
-
-\section{Results}
-
-\subsection{Illustration}
-
-Figure \ref{fig:simple_eg} illustrates the main features of adaptive shrinkage (ash) applied 
-to a denoising problem. The data (panel a) is first transformed into wavelet coefficients (WCs) at different scales.
-Each such ``observed" WC can be thought of as a noisy estimate of some ``true" WC for the (unknown) mean that we wish to estimate.
-We also compute, for each WC, an associated standard error that depends on the variance of the data about the mean.
-The idea behind wavelet denoising is to ``shrink" the observed WCs towards 0, which produces a smoother estimate of the mean than the observed data.
-
-A crucial question is, of course, how much to shrink. A key idea behind ash is that the shrinkage is ``adaptive", in that it
-determined by the data, in two distinct ways. First, if at a particular scale many observed WCs are ``large" (compared with their standard errors)
-then ash infers that, at this scale, many of the true WCs may also be large - that is, the estimated distribution $g$ in (\ref{}) will have a long tail.
-Consequently ash will shrink less at this scale than at scales where few observed
-WCs are large, for which the estimated $g$ will have a short tail.
-This is illustrated in panels b-c: at scale 1, many observed WCs are large (b), and so very little shrinkage is applied to these estimates (c).
-In contrast, at scale 7, few observed WCs are large (b), and so stronger shrinkage is applied (c). Second, the shrinkage is adaptive to 
-the standard error for each WC: at a given scale, WCs with larger standard error are shrunk more strongly than WCs with small standard error.
-This is illustrated in panel d). (The standard errors vary among WCs here because of the hetereskedastic variance.)
-
- The end result is that i) data that are consistent with a smooth signal, get smoothed more strongly; ii) smoothing is stronger in areas
- of the signal with larger variance. In this example the smoothed signal from ash is visually (and also quantitatively) more accurate than
- using TI-thresholding (with variance estimated by running median absolute deviation (RMAD); see \cite{Gao1997Wavelet}) (panel e).
-
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{simple_eg_1.pdf}
-        \caption{}
-        \label{fig:simple_eg_1}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{simple_eg_2.pdf}
-        \caption{}
-        \label{fig:simple_eg_2}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{simple_eg_3.pdf}
-        \caption{}
-        \label{fig:simple_eg_3}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{simple_eg_4.pdf}
-        \caption{}
-        \label{fig:simple_eg_4}
-    \end{subfigure}
-				\hfill
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{simple_eg_5.pdf}
-        \caption{}
-        \label{fig:simple_eg_5}
-    \end{subfigure}
-    \caption{Shows both ASH and SMASH at work.
-(a) shows the mean function $\pm$2 standard deviations, as well as one realized dataset.
-(b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse (scale 1) and one fine (scale 7).
-(c) demonstrates the shrinkage properties of ASH for the two scales of interest (scales 1 and 7): the coefficients at the fine scale (scale 7) are substantially shrunk, but barely so for the coarse scale.
-(d) shows the shrinkage effect of ASH on the fine scale (scale 7) wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision.
-(e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has noticeable artifacts.}
-    \label{fig:simple_eg}
-\end{figure}
-
-\subsection{Simulations}
-
-We conducted extensive simulation studies to compare the performance of our method with existing approaches.
-
- \subsubsection{Gaussian mean estimation}
-
-For the Gaussian case, we focus on mean estimation, initially with homoskedastic errors. We modelled our simulation study after
-\cite{Antoniadis2001Wavelet}, using many of the same test functions, a variety of sample sizes, two different signal to noise ratios (SNRs), and including
-the best-performing methods from their comparison.
-In particular their results showed that Translation Invariant (TI) thresholding (\cite{Coifman1995Translationinvariant}) performed the best for most of the test signals, where performance is measured by mean squared error (MSE).
-We also considered the Empirical Bayes shrinkage procedure (\cite{Johnstone2005Empirical}), named Ebayesthresh.
-
-Figure \ref{fig:gaus_homo} compares the mean integrated squared errors (MISEs) of TI-thresholding and Ebayesthresh to SMASH for the ``Spikes'' mean function, with a signal to noise ratio of 3 and sample size 1024.
-We applied SMASH in three ways, the first (SMASH) estimating the variance function allowing for heteroskedasticity, the second estimating the variance assuming homoskedasticity (SMASH-homo) and the
-third using the true variance function (SMASH true variance), which could be viewed as a "gold standard".
-The results show that all three versions of SMASH outperform both EbayesThresh and TI-thresholding.
-Notably all three SMASH versions perform very similarly, demonstrating that
-in this case there is little cost in allowing for heterskedasticity when the truth is homoskedastic.
-
-We obtained similar results for other mean functions, SNRs and sample sizes (see Supplementary Materials).
-
-\begin{figure}
-\centering
-    \includegraphics[width=0.65\textwidth]{violin_gaus_homo.pdf}
-    \caption{Comparison of wavelet-based methods for mean estimation with homoskedastic Gaussian errors for the ``Spikes'' mean function.
-Violin plots of MISEs for (from bottom to top) SMASH, SMASH with homoskedastic assumption, TI-thresholding with homoskedastic assumption, Ebayesthresh with homoskedastic assumption, and SMASH with known true variance are shown in the figure.
-Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-SMASH outperforms both TI-thresholding and Ebayesthresh, and SMASH with estimated variance performs nearly as well as with true variance.}
-    \label{fig:gaus_homo}
-\end{figure}
-
-Turning now to heteroskedastic errors, we compare results from SMASH (run three different ways, as above) with EbayesThresh (which assumes
-homoskedastic variance) and TI-thresh. For TI-thresh we considered three different ways of estimating the heteroskedastic variance: RMAD 
-(\cite{Gao1997Wavelet}), the SMASH estimated variance, and the true variance. (TI-thresh with homoskedastic variance performed very poorly; Supplementary Results.) Figure \ref{fig:gaus_hetero} 
-shows results for two sets of test functions: the ``Spikes'' mean function with the ``Clipped Blocks'' variance function and the ``Corner'' mean function with ``Doppler'' variance function, both with SNRs of 3 and sample sizes of 1024.
-
-To summarize the main patterns in Figure \ref{fig:gaus_hetero}:
-\begin{enumerate}
-\item SMASH outperforms all TI-thresh variants (including, here, TI with the true variance).
-\item SMASH performs almost as well for mean estimation when estimating the variance as when given the true variance.
-\item Allowing for heteroskedasticity within SMASH can substantially improve accuracy of mean estimation (compare SMASH with SMASH-homo and EbayesThresh).
-\item TI-thresh performs considerably better when used with the SMASH variance estimate than with the RMAD variance estimate.
-\end{enumerate}
-
-These main patterns hold for a variety of different mean and variance functions, SNRs, and sample sizes (see Supplementary Materials).
-Some variance functions are harder to estimate than others (e.g.
-the ``Bumps" function), and in these cases providing methods the true variance can greatly increase
-accuracy compared with estimating the variance. 
-As might be expected, the gain in allowing for heteroskedastic variance tends to be greatest when the variance functions are more
-volatile.
-
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.65\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_1.pdf}
-        \caption{}
-        \label{fig:gaus_hetero_1}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \raisebox{0.5\height}{\includegraphics[width=\textwidth]{violin_gaus_hetero_sd_1.pdf}}
-        \caption{}
-        \label{fig:gaus_hetero_sd_1}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.65\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_gaus_hetero_2.pdf}
-        \caption{}
-        \label{fig:gaus_hetero_2}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.3\textwidth}
-        \centering
-        \raisebox{0.5\height}{\includegraphics[width=\textwidth]{violin_gaus_hetero_sd_2.pdf}}
-        \caption{}
-        \label{fig:gaus_hetero_sd_2}
-    \end{subfigure}
-    \caption{Comparison of wavelet-based methods for mean estimation with heteroskedastic Gaussian errors.
-Figures on the left show violin plots of MISEs for various methods on two sets of mean-variance functions: ``Spikes'' mean function with ``Clipped Blocks'' variance function, and ``Corner'' mean function with ``Doppler'' variance function.
-Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-Figures on the right plot the mean functions $\pm$2 standard deviations.}
-    \label{fig:gaus_hetero}
-\end{figure}
-
-\subsubsection{Gaussian variance estimation}\label{sec:mfvb}
-
-One unusual feature of SMASH is that it performs joint mean and variance estimation.
-Indeed, we found only one other joint mean and variance estimation procedure for which we could obtain software (CHECK):
-the Mean Field Variational Bayes (MFVB) method for heteroskedastic Gaussian regression \cite{Menictas2015Variational}. 
-This method is based on penalized splines, and so is not well suited to many standard test functions in the wavelet literature, which
-often contain ``spiky" local features not well captured by splines. Hence, we compared SMASH and MFVB on some
-smoother mean and variance (standard deviation) functions, specifically scenario A in Figure 5 from \cite{Menictas2015Variational} (shown in Figure \ref{fig:mfvb_eg}),
-using scripts kindly provided by M.~Menictas.
-
-We simulated data under two different scenarios:
-\begin{enumerate}
-\item We generated $n=500$ independent $(X_i,Y_i)$ pairs, with $X_i \sim$ Uniform(0,1), and $Y_i | X_i=x_i \sim N(m(x_i),s(x_i)^2)$
-where $m(\cdot)$ and $s(\cdot)$ denote the mean and standard deviation functions (Figure \ref{fig:mfvb_eg}). We measured performance by the MSE 
-evaluated at 201 equally spaced points on $(X_{min},X_{max})$ for both the mean and the standard deviation.
-\item We generated $n=1024$ independent $(X_i,Y_i)$ pairs, with the $X_i$'s (deterministically) equally spaced on (0,1), and $Y_i|X_i$ as above.
-Performance is measured by MSE evaluated at the 1024 $X_i$'s for both the mean and the standard deviation.
-\end{enumerate}
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=\textwidth]{mfvb_eg.pdf}
-    \caption{Shows the mean function $m(x)$ $\pm$2 standard deviations $s(x)$ used in the simulation study comparing SMASH against MFVB.
-These functions correspond to mean and standard deviation functions (A) from \cite{Menictas2015Variational}.}
-    \label{fig:mfvb_eg}
-\end{figure}
-
-The first scenario presents some issues for SMASH because the number of data points is not a power of two, nor are the point equally spaced.
-To deal with the first issue, following standard ideas in the wavelet literature, we first mirrored the data about the right edge and extract the first $2^{\lfloor\log_2(2n)\rfloor}$ sample points, so that the number of data points in the new ``dataset'' is a power of two, and the mean curve is continuous at the right edge.
-To further ensure that the input to SMASH is periodic, we reflected the new dataset about the right edge and used this as the final input.
-To deal with the second issue we follow the common practice of treating the observations as if they are evenly spaced (see \cite{Sardy1999Wavelet} for discussion).
-To estimate the original mean and variance functions, we extract the first $n$ points from the SMASH estimated mean and variance.
-To evaluate MSE at the 201 equally spaced points (Scenario 1) we use simple linear interpolation between the estimated points.
-
-Table \ref{table:mfvb_comp} shows mean MSEs over 100 independent runs for each scenario.
-\begin{table}[ht]
-\centering
-\begin{tabular}{rrrrr}
-\hline
-& \multicolumn{2}{c}{Scenario 1}&\multicolumn{2}{c}{Scenario 2}\\
-\cline{2-5}
-& mean & sd & mean & sd \\
-\hline
-MFVB & 0.0330 & 0.0199 & 0.0172 & 0.0085 \\
-SMASH & 0.0334 & 0.0187 & 0.0158 & 0.0065 \\
-\hline
-\end{tabular}
-\caption{Compares the performance (in MSE) of SMASH and MFVB for two simulation scenarios, with the mean and variance functions as shown in \ref{fig:mfvb_fn}.
-SMASH is comparable to MFVB in mean estimation and outperforms the latter in variance estimation in Scenario 1, where the data are not equally spaced and not a power of 2.
-SMASH outperforms MFVB in both mean and variance estimation in Scenario 2, where the data are equally spaced and a power of 2.}
-\label{table:mfvb_comp}
-\end{table}
-
-In addition to the issues stated above for Scenario 1 with regards to wavelet-based methods (SMASH in particular), linear interpolation between sample points was also used in computing the MSE, further impacting the accuracy of SMASH.
-On the other hand, spline-based methods such as \cite{Menictas2015Variational} are well suited to dealing with smooth mean and variance functions presented in this particular simulation study.
-Despite all these limitations, SMASH performs comparably to MFVB in terms of mean estimation for Scenario 1, and has a lower MSE in terms of standard deviation estimation.
-For Scenario 2, SMASH outperforms MFVB in both mean and variance estimation.
-
-\subsubsection{Poisson Data}
-
-For this simulation study, we considered different test functions and Poisson intensities for a given sample size of $n=1024$ as in \cite{Timmermann1999Multiscale}, \cite{Fryzlewicz2004HaarFisz} and \cite{Besbeas2004Comparative}, over 100 independent runs.
-Figure \ref{fig:pois_sim} compares the MISE of SMASH with Haar-Fisz (\cite{Fryzlewicz2004HaarFisz}) and BMSM (\cite{Kolaczyk1999Bayesian}) for the ``Bursts'' function with (min,max) intensities of (0.01,3) and (1/8,8).
-We focus our attention on low intensities as they are of primary interest in many genomic applications.
-Complete results, including a (min,max) intensity of (1/128, 128), are included in Supplementary Materials.
-Figure \ref{fig:pois_sim} demonstrates that SMASH outperforms both methods for this scenario, and the claim holds true in general.
-As an exception, Haar-Fisz outperforms both SMASH and BMSM for certain test functions with a (min,max) intensity of (1/128,128) when the asymptotic variance of 1 is assumed in the Gaussian wavelet thresholding stage of the Haar-Fisz algorithm, but underperforms when the variance is estimated from the data instead.
-Besides the somewhat strong assumption of unit variance, the inconsistent performance of Haar-Fisz could also be attributed to the choice of the primary resolution level used, which can substantially affect the performance of Haar-Fisz.
-Here we analyzed primary resolution levels of 4, 5, 6 and 7, similar to \cite{Besbeas2004Comparative}.
-On the other hand, SMASH outperforms BMSM consistently, even though it is based on the same likelihood factorization used in the latter.
-We can thus conclude that the choice of ASH as the shrinkage procedure is superior to that used in BMSM in the simulation study.
-More importantly, using this formulation in SMASH also makes it easily extensible to multiple samples in the context of a (generalized) linear model, something we will briefly describe in the Discussion section.
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_pois_1.pdf}
-        \caption{}
-        \label{fig:pois_1}
-    \end{subfigure}
-		\hfill
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{violin_pois_8.pdf}
-        \caption{}
-        \label{fig:pois_8}
-    \end{subfigure}
-    \caption{Compares various approaches for denoising Poisson data for the ``Bursts'' test function where a) corresponds to a (min,max) intensity of (0.01,3), and b) corresponds to a (min,max) intensity of (1/8,8).
-Violin plots of MISEs for (from bottom to top) SMASH, BMSM and Haar-Fisz are shown in the figure.
-Smaller MISE implies better performance; dashed green line indicates the median MISE for SMASH.
-We note the performance gain of SMASH over both BMSM and Haar-Fisz in these scenarios.}
-    \label{fig:pois_sim}
-\end{figure}
-
-In terms of computation, SMASH is much more efficient than Haar-Fisz with external cyclespinning, as the latter must be rerun for each shift of the data.
-However, a direct comparison between SMASH and BMSM is uninformative, as they are coded in different programming environments.
-Nevertheless, similarities between the two methods imply that they should behave identically in this aspect, barring differences in actual implementation.
-
-Overall, these simulation studies demonstrate the ability of SMASH to accurately recover the mean functions for both the Gaussian and Poisson cases, and highlight the flexibility and adaptivity of the shrinkage procedure ASH.
-Although we have considered an extensive range of scenarios here, including different SNRs, sample sizes, variance functions, test functions and mean intensities where applicable, the performance of our method on real data has yet to be determined.
-In the next section, we will apply our method to two example datasets that have been discussed in previous work, and comment on the resulting estimates.
-
-\section{Application to real datasets}
-%\subsection{Three-month Treasury Bill Yields}
-%In this section we apply the Gaussian and Poisson denoising techniques to one example dataset each.
-For the Gaussian case, we looked at yields of secondary market rates from three-month Treasure bills, which were recorded weekly on Fridays.
-These rates were quoted on a discount basis and annualized using a 360-day year of bank interest.
-To match the analysis in \cite{Fan1998Efficient}, we used 1735 weekly observations spanning Jan.
-5 1962 to Mar.
-31 1995.
-The data are plotted in Figure \ref{fig:tb_raw_data}.
-Similar to \cite{Fan1998Efficient}, we fit an autoregressive model of order 5 (AR(5)) to the data and obtained the following:
-%\begin{eqnarray}
-%T_t=1.228T_{t-1}-0.234T_{t-2}+0.028T_{t-3}+0.039T_{t-4}-0.066T_{t-5}+Y_t
-%\end{eqnarray}
-%where $T_t, t=1,...,1735$ is the time series for the yields, and $Y_t$ are the residuals from fitting the model.
-Figure \ref{fig:tb_res} shows the plot of $Y_t$ against $X_t\equiv T_{t-1}$.
-Our goal is to estimate the mean function defined by $E(Y_t|X_t=x)$ as well as the variance function $V(Y_t|X_t=x)$.
-Note that standard wavelet techniques are not designed for such types of data, where 1) repeated observations are present and 2) the number of data points is not a power of two and the points are unevenly spaced.
-To tackle the first issue, we use the median of the repeated observations at their respective sample points (see eg \cite{Delouille2004Smooth}).
-Next, we applied the procedure described in the Simulations section when comparing our method against MFVB, which was a modified version of symmetric extension.
-This deals with the second complication.
-The estimated mean and variance functions are given in Figures \ref{fig:tb_res} and \ref{fig:tb_var} respectively.
-%
-%\begin{figure}
-%\centering
-    %\begin{subfigure}[b]{0.4\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{figures_treasury_a.pdf}
-        %\caption{}
-        %\label{fig:tb_raw_data}
-    %\end{subfigure}
-    %\hfill
-    %\begin{subfigure}[b]{0.4\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{figures_treasury_b.pdf}
-        %\caption{}
-        %\label{fig:tb_res}
-    %\end{subfigure}
-    %\begin{subfigure}[b]{0.4\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{figures_treasury_c.pdf}
-        %\caption{}
-        %\label{fig:tb_mean}
-    %\end{subfigure}
-    %\hfill
-    %\begin{subfigure}[b]{0.4\textwidth}
-        %\centering
-        %\includegraphics[width=\textwidth]{figures_treasury_d.pdf}
-        %\caption{}
-        %\label{fig:tb_var}
-    %\end{subfigure}
-    %\caption{Analysis of yields from three-month Treasury Bills.
-(a) Raw data of interest rates as a function of time.
-(b) Residuals $Y_t$ from fitting an AR(5) model to the data against $X_t\equiv T_{t-1}$.
-The red curve is the estimated mean curve from SMASH.
-(c) Plot of a zoomed-in version of the estimated mean curve, with approximate 95\% credible bands.
-(d) The estimated conditional variance curve, with approximate 95\% credible bands.}
-%\end{figure}
-%
-%Except for possible boundary effects, our mean and conditional variance estimates are similar to those of \cite{Fan1998Efficient}.
-Unfortunately, these boundary effects are difficult to deal with for non-periodic functions in the wavelet case, and our usage of symmetric extension with the Haar basis is just one possible solution.
-Better alternatives have been suggested by eg.
-Su et al.
-(2013), but is beyond the scope of discussion in this paper.
-Similar to the analysis in \cite{Fan1998Efficient}, we found the correlation coefficient between the logarithm of $x_t$ and the logarithm $\hat{V}^{1/2}(Y_t|x_t)$ to be 0.949, which further supports the structural volatility model suggested by Andersen and Lund (source?):
-%\begin{eqnarray}
-%Var^{1/2}(Y_t|x_t)=\Ga x_t^{\Gb}
-%\end{eqnarray}
-%By performing least squares regression of $\log(\hat{V}^{1/2}(Y_t|x_t))$ on $\log(x_t)$, we have that $\hat{\Ga}=0.0106$ and $\hat{\Gb}=1.429$, which are similar to the values reported in \cite{Fan1998Efficient}.
-\subsection{Motorcycle Acceleration Data}
-\begin{figure}
-\centering
-    \includegraphics[width=0.65\textwidth]{motorcycle.pdf}
-    \caption{Results from fitting SMASH to the motorcycle acceleration data discussed in \cite{silverman1985some}.
-Both the mean curve (solid black line) and the variance around the mean curve (dashed red line) are shown.
-We note that SMASH does a good job of capturing both the mean as well as the variation in the data without requiring and parameter tuning.}
-    \label{fig:motorcycle}
-\end{figure}
-
-We first apply the Gaussian version of SMASH on the well known motorcycle acceleration dataset from \cite{silverman1985some}.
-The data consists of 133 observations measuring head acceleration in a simulated motorcycle accident which is used to test crash helmets.
-The dependent variable is $acceleration$ (in $g$), and the independent variable is $time$ (in ms).
-To deal with repeated measurements, we simply take the median of the measurements for acceleration for any given $time$ value.
-To address the issue of non-equal spacing between the data points, we applied the procedure described in \ref{sec:mfvb}.
-The fitted mean and variance curves are shown in Figure \ref{fig:motorcycle}.
-Comparing our fit with that of \cite{Delouille2004Smooth}, which also employs a wavelet-based approach, we note two advantages to using SMASH.
-First, our method provides a measure of uncertainty (through both the credible band for the mean curve as well as the variance curve itself), which is often of interest in many applications.
-Second, our method is able to produce a visually appealing fit when used without having to tune any parameters, while the approach in \cite{Delouille2004Smooth} requires an $adhoc$ removal of fine scale detail coefficients to avoid introducing artifacts into the fit.
-
-Although SMASH does a reasonably good job of performing nonparametric regression on the given dataset, we do recognize that there are better ways to deal with unequally spaced observations, which can then reveal the discontinuities in the first derivative around 15, 23 and 32 ms, as discussed in the literature.
-Nevertheless, we can use SMASH directly out of the box under most circumstances, making it an extremely versatile tool.
-\newpage
-\subsection{ChIP-Seq Data}
-Here we apply our Poisson de-noising procedure to next generation sequencing data, commonly used in the field of genomics.
-Specifically, we chose an example dataset from the ENCODE (\textbf{Enc}yclopedia \textbf{O}f \textbf{D}NA \textbf{E}lements) project launched by the National Human Genome Research Institute.
-This dataset contains reads from chromatin immunoprecipitation sequencing (ChIP-seq) measuring transcription factor binding in two different cell types, with two samples for each cell type.
-Due to the massive size of the data, we selected a representative portion of the reads of length $2^{15}$ from chromosome 1.
-%Since we are looking mainly at univariate denoising here, we ran our method on each sample separately to produce the the plots in Figure \ref{fig:seq_smooth}.\\
-%\begin{figure}[h]
-%\centering
-%\includegraphics[scale=0.7]{smoothing_all.pdf}
-%\caption{Estimated intensities from SMASH for 4 samples; the first two samples are two replicates from GM12878, a lymphoblastoid cell line, and the last two samples are two replicates from H1hesc, which are human embryonic stem cells.
-The reads are taken from position 880001 to 1011072 on chromosome 1.}
-%\label{fig:seq_smooth}
-%\end{figure}
-%\bigskip
-One goal of analyzing ChIP-seq data is to discover regions where transcription factors are likely to bind to DNA, thereby allowing us to better understand the mechanisms underlying gene regulation.
-These binding regions are often reflected in the data as ``peaks'', where more counts are present than background noise.
-Our method allows us to identify these peaks by looking at the estimated intensity function.
-%In Figure \ref{fig:seq_smooth}, we immediately notice the presence of several large peaks around position 895000 for the first three samples, and around position 952000 for the last two samples.
-To ensure that our method performs sensibly, we pooled the reads for just the GM12878 cell line and ran our method as well as a popular peak calling procedure MACS on the selected region.
-The results are shown in Figure \ref{fig:seq_peak}.\\
-\newpage
-\begin{figure}
-\centering
-    \begin{subfigure}[b]{0.85\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{peaks_comp_a.png}
-        \caption{}
-        \label{fig:seq_peak_data}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.85\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{peaks_comp_b.pdf}
-        \caption{}
-        \label{fig:seq_peak_est}
-    \end{subfigure}
-    \caption{Analysis of next-generation sequencing data from the ENCODE project, corresponding to sequencing reads from the GM12878 cell line and spanning positions 880001 to 1011072 on chromosome 1.
-(a) plots the actual sequencing counts (summed across both replicates).
-A rough signal can be visualized by looking at darker regions of the plot, which correspond to higher concentrations of data points.
-(b) plots the estimated intensity function obtained from SMASH (black solid line) and location of peaks called by MACS (red markers beneath the estimated intensity).
-We can observe not only the location of the peaks from the SMASH estimate (which MACS does provide), but also the amplitude of the signals, something which MACS fails to reveal.
-The plot also reveal weak signals that MACS fail to capture, but of interest nonetheless.}
-    \label{fig:seq_peak}
-\end{figure}
-From Figure \ref{fig:seq_peak_est} it is clear that SMASH captures the peaks detected by MACS.
-Rather than calling peaks based on certain thresholds however, our method allows users to determine the relative strength and width of each peak, which provides a more comprehensive summary of the sequencing reads.
-At the same time, SMASH also provides the posterior variances for the intensity estimates, allowing for the option of calling peaks based on thresholds if desired.\\
-
-\section{Discussion}
-In this paper we have briefly introduced the adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques.
-Both applications discussed in this paper relax the standard assumption of i.i.d.
-Gaussian noise, and are thus challenging tasks.
-Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, revealing its potential in many other applications.
-
-In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as their approximate posterior variances as a measure of uncertainty.
-In addition, the variance function can also be estimated, which would provide frequentist confidence intervals for other forms of mean estimation.
-To the best of our knowledge, there is no readily available software in the wavelet literature that implements joint mean and variance estimation.
-Simulations have also confirmed that our method is relatively robust to simple forms of autocorrelation between the errors (details needed).
-In the case of Poisson regression, we improved upon the conjugate Beta priors in \cite{Kolaczyk1999Bayesian} by using ASH as a shrinkage procedure, which allows for more flexibility and precision.
-%In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution.
-In both the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used.
-On the other hand, the primary resolution level in almost all of the other wavelet-based methods actually affects their performance in varying degrees, depending on the underlying mean and/or variance function.
-Hence, our fully adaptive procedure allows users to easily apply it to any given dataset, depending on the type of noise.
-
-We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature, in terms of pointwise accuracy (MSE in this case).
-Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussian priors imply that our methods are computationally fast, since the posteriors can be computed analytically.
-In the Gaussian case, simulation results demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d.
-errors (without explicitly assuming thus), whilst maintaining superior accuracy when heteroskedastic errors are present.
-Unfortunately, the lack of readily available software (except for MFVB, as described in \cite{Menictas2015Variational}) for variance estimation made it difficult to assess the performance of our method in that context.
-On the other hand, we were able to compare our method to some of the more popular denoising techniques in the Poisson case.
-Specifically, we have improved upon the conjugate Beta priors used in conjunction with the binomial likelihoods \cite{Kolaczyk1999Bayesian}) by using ASH as the shrinkage procedure, which allows for more flexibility and accuracy.
-This is particularly evident when the mean intensity is low, as is common in many high-throughput genomic sequencing datasets.
-Our method is also much faster and comparable in accuracy to the popular Haar-Fisz algorithm.
-Unfortunately, we were not able to directly compare the computational efficiency of our method to many other methods due to differences in the programming software involved.
-
-Although we have only focused on one-dimensional univariate denoising here, our methods can be extended to various scenarios.
-In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see \cite{Morris2006Waveletbased}).
-Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which encapsulates a sample with temporally or spatially structured data points.
-While \cite{Morris2006Waveletbased} proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category.
-Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby relaxing their assumptions.
-In the simplest case, we could obtain spatially structured differences between groups by including a single covariate that categorizes each sample.
-In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where structured differences are present between say, various cell lines, as per our sequencing example in the previous section.
-The Gaussian model could potentially be used in...(??).
-
-With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible.
-For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}.
-However, recent research in image denoising problems has shown that smooth curves present in many images such as photographs might render wavelet transformations undesirable.
-We could thus incorporate ASH into other types of transformations such as curvelets, which would be a potential direction for future work.
-\newpage
-\section{Reference}
-
-\begin{appendices}
-\section{}\label{app:var estimation}\bigskip
-\textbf{Variance estimation for Gaussian denoising}
-
-With $\bm{Z}$ as defined in \eqref{eq:varobs1}, we apply the wavelet transform $W$ to $\bm{Z}^2$, and obtain the wavelet coefficients $\bm{\Gd}=W\bm{Z}^2$.
-Note that $\mathbb{E}(\bm{\Gd})=(\bm{\Gg})$, where $\bm{\Gg}=W\bm{\s}^2$.
-As with \eqref{eq:likelihood}, we treat the likelihood for $\bm{\Gg}$ as if it were independent, resulting in
-\begin{eqnarray}
-L(\bm{\Gg}|\bm{\Gd})=\prod_{j=0}^J\prod_{k=0}^{T-1}P(\Gd_{jk}|\Gg_{jk})
-\end{eqnarray}
-However, the likelihoods $L(\Gg_{jk}|\Gd_{jk})$ are not normal, and have no simple closed form expressions.
-As such, we approximate the likelihood by a normal likelihood through matching the moments of a normal distribution to the distribution $P(\Gd_{jk}|\Gg_{jk})$ i.e.
-\begin{eqnarray}
-P(\Gd_{jk}|\Gg_{jk})\approx N(\Gg_{jk},\hat{\mathbb{V}}(\Gd_{jk}))
-\end{eqnarray}
-so that
-\begin{eqnarray}\label{eq:gaus approx}
-L(\Gg_{jk}|\Gd_{jk})\approx \phi(\Gd_{jk};\Gg_{jk},\mathbb{V}(\Gd_{jk}))
-\end{eqnarray}
-where $\phi$ is the normal density function, and $\mathbb{V}(\Gd_{jk})$ is the variance of the detail coefficients.
-Since these variances are unknown, we estimate them from the data and then proceed to treat them as known.
-More specifically, since $Z_t\sim N(0,\s_t^2)$, we have that
-\begin{eqnarray}
-&\mathbb{E}(Z_t^4)\approx 3\s_t^4\notag\\
-\label{eq:varvarest}\Rightarrow&\mathbb{V}(Z_t^2)\approx 2\s_t^4
-\end{eqnarray}
-and so we simply use $\frac{2}{3}Z_t^4$ as an unbiased estimator for $\mathbb{V}(Z_t^2)$.
-It then follows that $\hat{\mathbb{V}}(\Gd_{jk})$ is given by $\sum_{l=1}^n \frac{2}{3}Z_l^4W_{jk,l}^2$, and is unbiased for $\mathbb{V}(\Gd_{jk})$.
-These will be the inputs to ASH, which then produces shrunk estimates in the form of posterior means for the corresponding parameters.
-Although this works well in most cases, there are variance functions for which the above procedure tends to overshrink the detail coefficients at the finer levels.
-This is likely because the distribution of the wavelet coefficients are extremely skewed, especially when the true coefficients are large (at coarser levels the distributions are much less skewed since we are dealing a linear combination of a large number of data points).
-One way around this issue is to employ a procedure that jointly shrinks the coefficients $\bm{\Gg}$ and their variance estimates (see JASH).
-The final estimate of the variance function is obtained from the posterior means via the average basis inverse across all the shifts.
-
-\section{}\label{app:reconstruction}\bigskip
-\textbf{Poisson denoising}
-
-First summarize the data in a recursive manner: 
-\begin{eqnarray}
-Y_{Jk}\equiv Y_k\end{eqnarray}
-for $k=1,...,n$, and
-\begin{eqnarray}
-Y_{jk}=Y_{j+1,2k}+Y_{j+1,2k+1}
-\end{eqnarray}
-for resolution $j=0,...,J-1$ and location $k=0,...,2^j-1$. Hence, we are summing more blocks of observations as we move to coarser levels.
-
-This recursive scheme leads to:
-\begin{eqnarray}
-Y_{jk}=\sum_{l=k2^{J-j}+1}^{(k+1)2^{J-j}}Y_l
-\end{eqnarray}
-for $j=0,...,J$ and $k=0,...,2^j-1$.
-
-Further define the following:
-\begin{eqnarray}\Gl_{Jk}\equiv \Gl_k\end{eqnarray}
-for $k=1,...,n$, and
-\begin{eqnarray}\Gl_{jk}=\Gl_{j+1,2k}+\Gl_{j+1,2k+1}\end{eqnarray}
-for $j=0,...,J-1$ and $k=0,...,2^j-1$. 
-Furthermore, define
-\begin{eqnarray}\label{eq:poisson wc}\Ga_{jk}=\log(\Gl_{j+1,2k})-\log(\Gl_{j+1,2k+1})\\\end{eqnarray}
-for $s=0,...,J-1$ and $l=0,...,2^j-1$.
-The ${\Ga}$'s defined this way is extremely similar to the (true) Haar wavelet coefficients, which forms the basis of our approach.
-Using this recursive representation, we can see that the likelihood for $\bm{\Ga}$ factorizes into a product of likelihoods, where $\bm{\Ga}$ is the vector of all the $\Ga_{sl}$'s.
-To be specific, we have
-\begin{eqnarray}
-L(\bm{\Ga}|\mathbf{Y})&=&P(\mathbf{Y}|\bm{\Ga})\\
-&=&P(Y_{0,0}|\Gl_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}P(Y_{j+1,2k}|Y_{j,k},\Ga_{j,k})\\
-&=&L(\Gl_{0,0}|Y_{0,0})\prod_{j=0}^{J-1}\prod_{k=0}^{2^j-1}L(\Ga_{j,k}|Y_{j+1,2k},Y_{j,k})
-\end{eqnarray}
-where the factorization is due to the recursive definition above.
-Note that $Y_{00}|\Gl_{00}\sim \textrm{Pois}(\Gl_{00})$.
-For any given $j,k$, $Y_{jk}$ is a sum of two independent Poisson random variables, and is itself a Poisson random variable.
-Hence
-\[Y_{j+1,2k}|Y_{jk},\Ga_{jk}\sim \textrm{Bin}({Y_{jk},\frac{1}{1+e^{-\Ga_{jk}}}\equiv\frac{\Gl_{j+1,2k}}{\Gl_{jk}}})\]
-
-\subsection{Estimates and standard errors for $\alpha_j$}
-
-Each $\alpha_{j}$ is a ratio of the form $\log(\mu_{a:b}/\mu_{c:d})$ whose maximum likelihood estimate (mle) is $\log(Y_{a:b}/Y_{c:d})$.
-The main challenge here is that the mle is not well behaved when either the numerator or denominator of $Y_{a:b}/Y_{c:d}$ is 0.
-To deal with this, when either is 0 we use Tukey's modification \cite{Gart1967Bias}.
-Specifically, letting $S$ denote $Y_{a:b}$ and $F$ denote $Y_{c:d}$ (corresponding to thinking of these as successes and failures in a binomial experiment, given $Y_{a:b}+Y_{c:d}$), we use
-\begin{eqnarray}\label{eq:pseudoMLE1}
-&&\hat{\Ga}=\left\{
-\begin{array}{lll}
-\log\{(S+0.5)/(F+0.5)\}-0.5&\ \ \ S=0\\
-\log\{S/F\}&\ \ \ S=1,2,...,N-1\\
-\log\{(S+0.5)/(F+0.5)\}+0.5&\ \ \ S=N\\
-\end{array}
-\right.\\ \label{eq:pseudoMLE1se}
-&&se(\hat{\Ga})=\sqrt{V^*(\hat{\Ga})-\frac{1}{2}\{V_3(\hat{\Ga})\}^2\left\{V_3(\hat{\Ga})-\frac{4}{N}\right\}}
-\end{eqnarray}
-where
-\begin{eqnarray}
-&&V_3(\hat{\Ga})=\frac{N+1}{N}\left(\frac{1}{S+1}+\frac{1}{F+1}\right)\ \ \ S=0,...,N\\
-\label{eq:pseudoMLE2}&&V^*(\hat{\Ga})=V_3(\hat{\Ga})\left\{1-\frac{2}{N}+\frac{V_3(\hat{\Ga})}{2}\right\}
-\end{eqnarray}
-The square of the standard error in \eqref{eq:pseudoMLE1se} corresponds to $V^{\ast\ast}$ from p.
-182 of \cite{Gart1967Bias}, and is chosen because it is less biased for the true variance of $\hat{\Ga}$ (when $N$ is small) as compared to the asymptotic variance of the MLE (see \cite{Gart1967Bias}).
-The other two variance estimators from \cite{Gart1967Bias}, $V_1^{++}$ and $V^{++}$, were also considered in simulations and gave similar results, but $V^{\ast\ast}$ was chosen for its simple form.
-
-%One direct approximation of the likelihood for $\Ga$ is the Laplace approximation, which results in the Gaussian likelihood given by $\phi(\Ga;\hat{\Ga}_{MLE},\mathbb{V}(\hat{\Ga}_{MLE}))$.
-Here $\phi$ is the normal density function, and $\hat{\Ga}_{MLE}$ is the maximum likelihood estimator.
-We would then estimate $\mathbb{V}(\hat{\Ga}_{MLE})$ by the square of the asymptotic standard deviation for $\hat{\Ga}_{MLE}$.
-Specifically,
-% for some appropriate estimator $\hat{\Ga}$.
-This choice of parameters for the Gaussian approximation is also appropriate in the sense that it minimizes the Kullback-Leibler divergence between a Gaussian distribution and the likelihood for $\Ga$ (also known as moment matching).
-
-%We next consider appropriate estimators for the parameters $\Ga$ and $\sqrt{\mathbb{V}(\hat{\Ga})}$.
-The obvious choice would be the MLE of $\Ga$ and its asymptotic standard error respectively, given by
-%\begin{eqnarray}
-%\hat{\Ga}_{MLE}=\log(S/F)&\ \ \ S=0,...,N\\
-%se(\hat{\Ga}_{MLE})=\sqrt{SF/N}&\ \ \ S=0,...,N
-%\end{eqnarray}
-%where $S$ is the number of successes in the binomial setup, and $F=N-S$ is the number of failures (in our case the even locations would be successes and odd locations failures).
-The MLE has one notable drawback however, in that it cannot deal well with extreme cases.
-This would in turn affect the likelihood approximation in a non-negligible way.
-To improve the accuracy of the approximation at the endpoints of the binomial distribution (ie.
-when we have $\hat{p}=0$ or $N$, so that $\hat{\Ga}=-\infty$ or $\infty$ respectively), we instead aim to find a suitable estimator $\hat{\Ga}$ for $\Ga$.
-Next, we approximate the distribution of $\hat{\Ga}$ by a Gaussian distribution, so that the likelihood for $\Ga$ is automatically Gaussian, given by $\phi(\Ga;\hat{\Ga},\mathbb{V}(\hat{\Ga}))$.
-
-\subsection{Signal reconstruction}
-
-Given the posterior means and variances of the $\Ga$'s from ASH, the first step to reconstructing the signal is to find the posterior means of $p_{jk}:=\frac{\Gl_{j+1,2k}}{\Gl_{jk}}$ and $q_{jk}:=\frac{\Gl_{j+1,2k+1}}{\Gl_{jk}}$ (for $j=0,...,J-1$ and $k=0,...,2^j-1$).
-Specifically, for each $j$ and $k$, we wish to find
-\begin{eqnarray}\label{eq:pfromwc1}
-&&E(p_{jk})\equiv E\left(\frac{e^{\Ga_{jk}}}{1+e^{\Ga_{jk}}}\right)\\
-\label{eq:pfromwc2}&&E(q_{jk})\equiv E\left(\frac{e^{-\Ga_{jk}}}{1+e^{-\Ga_{jk}}}\right)\end{eqnarray}
-Given that we already have the posterior expectations and variances for $\Ga_{jk}$, we can approximate \eqref{eq:pfromwc1}-\eqref{eq:pfromwc2} using the Delta method. First, define
-\begin{eqnarray}\label{eq:ff}ff(x)=\frac{e^x}{1+e^x}\end{eqnarray}
-and consider the Taylor expansion of $ff(x)$ about $ff(E(x))$:
-\begin{eqnarray}\label{eq:delta}ff(x)\approx ff(E(x))+ff'(E(x))(x-E(x))+\frac{ff''(E(x))}{2}(x-E(x))^2\end{eqnarray}
-where
-\begin{eqnarray}
-\label{eq:fderiv}&&ff'(x)=\frac{e^x}{(1+e^x)^2}\\
-\label{eq:sderiv}&&ff''(x)=\frac{e^x(1-e^{x})}{(1+e^x)^3}
-\end{eqnarray}
-It is easy to see that
-\begin{eqnarray}
-&&E(p_{jk})\approx ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\\
-\label{eq:Ep}&&E(q_{jk})\approx ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})
-\end{eqnarray}
-noting that we have already computed $E(\Ga)$ and $Var(\Ga)$.
-
-Finally, we can easily back-transform to construct an estimated signal, by noting that we can express $\Gl_t$ as a product of the $p$'s and $q$'s for any $i=1,2,...,n$.
-Specifically, let $\{c_1,...,c_J\}$ be the binary representation of $i-1$, and $d_m=\sum_{j=1}^m c_j2^{m-j}$ for $j=1,...,J-1$.
-We then have
-\begin{eqnarray}\label{eq:product}\Gl_k=\Gl_{00}p_{00}^{1-c_1}p_{1,d_1}^{1-c_2}...p_{J-1,d_{J-1}}^{1-c_J}q_{00}^{c_1}q_{1,d_1}^{c_2}...q_{J-1,d_{J-1}}^{c_J}\end{eqnarray}
-where we usually estimate $\Gl_{00}$ by $\sum_l Y_l$ (see Kolaczyk (1999)). Using the independence of the $p$'s and $q$'s from different scales, we have:
-\begin{eqnarray}\label{eq:Eproduct}E(\Gl_t)=\Gl_{00}E(p_{00})^{1-c_1}E(p_{1,d_1})^{1-c_2}...E(p_{J-1,d_{J-1}})^{1-c_J}\notag\\
-E(q_{00})^{c_1}E(q_{1,d_1})^{c_2}...E(q_{J-1,d_{J-1}})^{c_J}\end{eqnarray}
-
-As an additional step, we can also construct a credible band around the signal using the posterior variances for inference purposes. From \eqref{eq:product} we have the following:
-\begin{eqnarray}\label{eq:E2product}E(\Gl_t^2)=\Gl_{00}^2E(p_{00}^2)^{1-c_1}E(p_{1,d_1}^2)^{1-c_2}...E(p_{J-1,d_{J-1}}^2)^{1-c_J}\notag\\
-E(q_{00}^2)^{c_1}E(q_{1,d_1}^2)^{c_2}...E(q_{J-1,d_{J-1}}^2)^{c_J}\end{eqnarray}
-To compute the terms in \eqref{eq:E2product}, we again make use of the Delta method (with $ff(x)=(\frac{e^x}{1+e^x})^2$) to obtain:
-\begin{eqnarray}
-&E(p_{jk}^2)\approx \left(ff(E(\Ga_{jk}))+\frac{ff''(E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
-& \hspace{1.5 in}\{ff'(E(\Ga_{jk}))\}^2Var(\Ga_{jk})\\
-&E(q_{jk}^2)\approx \left(ff(-E(\Ga_{jk}))+\frac{ff''(-E(\Ga_{jk}))}{2}Var(\Ga_{jk})\right)^2+\notag\\
-& \hspace{1.5 in}\{ff'(E(-\Ga_{jk}))\}^2Var(\Ga_{jk})
-\end{eqnarray}
-Finally we combine \eqref{eq:Eproduct} and \eqref{eq:E2product} to find $Var(\Gl_k)$, which allows us to construct credible intervals.
-
-Note here that for the reconstructed signal to possess the property of shift invariance (see Coifman \& Donoho (1995)), the $\Ga$'s are extracted from a so-called translation invariant (TI) table (see \cite{Coifman1995Translationinvariant}, and \cite{Kolaczyk1999Multiscale}) rather than as described above.
-The idea remains the same however, and we can simply think of the extra $\Ga$'s as being defined similarly as the original $\Ga$'s, albeit from a shifted version of the original data points.
-To be more specific, the TI table contains the $\Ga_{jk}$ for all circulant shifts of the signal.
-Here we define the $t$-th shift of the signal $\bm{Y}$, denoted by $\bm{Y}^{(t)}$, to be created from $\bm{Y}$ itself by moving the first $n-t$ elements of $\bm{Y}$ $t$ positions to the right and then putting the last $t$ elements of $\bm{Y}$ in the first $t$ locations.
-Using this table, we are essentially computing the posterior expectations in \eqref{eq:Eproduct}-\eqref{eq:E2product} by averaging over all posterior expectations for every shift of the original signal ie.
-\begin{eqnarray}
-\label{eq:TIapproxexp}\frac{1}{n}\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})
-\end{eqnarray}
-which is an approximation to the true quantity we wish to compute, given by
-\begin{eqnarray}
-E(\hat{\Gl}_k)=\sum_{t=1}^n E(\hat{\Gl}_k^{(t)})P(\mbox{$t$-th shift})
-\end{eqnarray}
-\end{appendices}
-
-\bibliography{smash}
-\bibliographystyle{plain}
+In addition we explore the results from trying out different Gaussian de-noising procedures for the second step of the Haar-Fisz (HF) algorithm.
 

### 2016-03-10 paper/supplementary/supplementary.tex
more updates to supplementary materials and others

@@
 \usepackage{caption,subcaption}
+\usepackage{pbox}
 
@@
 
+\newcommand{\beginsupplement}{%
+        \setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+     }
+
 \begin{document}
+\beginsupplement
 
-\title{\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals}}
+\title{\textbf{Supplementary Materials}}
 \date{}
@@
 As noted in the main text, we performed an extensive simulation study for Gaussian errors using a variety of test functions (7 mean functions and 5 variance functions, including constant variance), signal-to-noise ratios (SNR = 1 and 3) and sample sizes ($T=256,512,1024$).
-The results for $T=256,512$ are saved under ~/res_paper/res_gaus_256.RData and ~/res_paper/res_gaus_512.RData respectively, while results for $T=1024$ are presented in a DSC framework (https://github.com/stephens999/dscr), saved under ~/res_paper/res_gaus_dscr.RData.
-In particular, we include an RShiny app as an interactive way to present the results for $T=1024$, the code for which can be found in the dscr-smash repo (https://github.com/zrxing/dscr-smash), under graphs.Rmd.
+For details of where the results are saved and what information they contain, refer to README.md from the \href{https://github.com/stephenslab/ashwave}{ashwave repo}.
+In particular, we include an RShiny app as an interactive way to present the results for $T=1024$, the code for which can be found in the \href{https://github.com/zrxing/dscr-smash}{dscr-smash repo}.
+For more details on the repo refer to the README.md file from the repo.
 In particular, users can view the boxplots of MISEs for the methods and test functions they are interested in by checking the appropriate boxes.
-For more details refer to graphs.Rmd.
+For more details on the RShiny display refer to graphs.Rmd in the dscr-smash repo.
+For reference, the mean and variance functions used in the simulation studes are shown below in Figures \ref{} and \ref{}
 
-In addition to the performance of the various methods, Table \ref{} also provides additional information for each of the method that we used in the simulation study.
+In addition to the performance of the various methods, we also provide code in the \href{https://github.com/stephenslab/ashwave}{ashwave repo} generating a table that provide additional details for each method used, including the associated software, variance assumption, wavelet basis, shrinkage procedure used, and other relevant information.
 
@@
 The results from the simulation study for Poisson noise are shown in the following tables.
-Each of the six tables presents results for the corresponding mean function, and includes results for all three (min,max) intensity levels ((0.01,3), (1/8,8), (1/128,128)).
+For reference, we first plot the intensity functions used in the simulation studies in Figure \ref{}.
+Each of the six tables (\ref{}-\ref{}) presents results for the corresponding mean function, and includes results for all three (min,max) intensity levels ((0.01,3), (1/8,8), (1/128,128)).
+As mentioned in the main text, we also explored several options for the Gaussian de-noising stage of the HF algorithm, and include the results in the following tables.
+Specifically, we considered four different options (all with 50 external cyclespins):
+\begin{enumerate}
+\item Hybrid of (1) Greedy tree de-noising (\cite{Baraniuk1999Optimal}) and (2) wavelet thresholding using ``leave-half-out'' crossvalidation (eg \cite{Nason1995Choice}).
+$j_0$ was set to the default value 3, and the noise level was estimated from the data.
+This corresponds to \bf{H:CV+BT CS} in \cite{Fryzlewicz2004HaarFisz}.
+\item Wavelet thresholding using the universal threshold (\cite{Donoho1994Ideal}).
+$j_0$ was set to the default value 3, and the noise level was estimated from the data.
+This corresponds to \bf{F\bowtie U CS} in \cite{Fryzlewicz2004HaarFisz}.
+\item Wavelet thresholding using the universal threshold for the non-decimated wavelet transform. Average over $j_0=4,5,6,7$ was chosen, and the noise level was estimated from the data.
+\item Wavelet thresholding using the universal threshold for the non-decimated wavelet transform.
+Average over $j_0=4,5,6,7$ was chosen, and the noise level was set to be 1 (which is the asymptotic variance under the Fiszs transform).
+This is the option for which we included the results in the main text, as it had the best overall performance.
+\end{enumerate}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{690.01} & 329.26 & 48.87 \\ 
+  BMSM & 1007.34 & 397.79 & 41.88 \\ 
+  BMMIM & 930.08 & 436.54 & 368.36 \\ 
+  Haar-Fisz & 722.19 & \textcolor{red}{287.44} & \textcolor{red}{18.06} \\ 
+  Anscombe & 1329.87 & 388.59 & 18.17 \\ 
+  Haar thresholds & 803.89 & 326.11 & 120.02 \\ 
+  L1\_penalty & 3085.65 & 2209.67 & 1516.78 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Spikes'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_sp}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{145.26} & \textcolor{red}{68.47} & 10.25 \\ 
+  BMSM & 147.40 & 73.87 & 10.49 \\ 
+  BMMIM & 245.89 & 100.17 & 71.26 \\ 
+  Haar-Fisz & 314.41 & 122.79 & \textcolor{red}{9.08} \\ 
+  Anscombe & 419.04 & 146.64 & 9.50 \\ 
+  Haar thresholds & 264.38 & 162.16 & 89.37 \\ 
+  L1\_penalty & 655.82 & 284.75 & 2979.23 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_ang}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{81.41} & \textcolor{red}{43.21} & \textcolor{red}{7.21} \\ 
+  BMSM & 85.29 & 44.22 & 7.35 \\ 
+  BMMIM & 205.09 & 81.49 & 11.22 \\ 
+  Haar-Fisz & 274.26 & 105.47 & 9.23 \\ 
+  Anscombe & 372.06 & 128.43 & 9.10 \\ 
+  Haar thresholds & 226.27 & 143.01 & 85.74 \\ 
+  L1\_penalty & 385.47 & 71.17 & 8.68 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Heavisine'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_hs}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{487.34} & \textcolor{red}{234.35} & 33.11 \\ 
+  BMSM & 706.04 & 301.86 & 34.42 \\ 
+  BMMIM & 654.11 & 290.91 & 531.79 \\ 
+  Haar-Fisz & 618.39 & 299.39 & \textcolor{red}{25.20} \\ 
+  Anscombe & 869.16 & 343.15 & 26.03 \\ 
+  Haar thresholds & 540.58 & 271.16 & 107.44 \\ 
+  L1\_penalty & 1836.73 & 1280.16 & 719.59 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Bursts'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_bur}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{307.80} & \textcolor{red}{137.28} & \textcolor{red}{6.82} \\ 
+  BMSM & 355.15 & 143.09 & 6.91 \\ 
+  BMMIM & 472.24 & 205.20 & 150.03 \\ 
+  Haar-Fisz & 632.21 & 338.55 & 29.72 \\ 
+  Anscombe & 804.70 & 384.46 & 28.94 \\ 
+  Haar thresholds & 467.64 & 228.14 & 82.99 \\ 
+  L1\_penalty & 1021.58 & 627.67 & 1961.42 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_cb}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{2597.46} & \textcolor{red}{1194.62} & \textcolor{red}{141.21} \\ 
+  BMSM & 4036.77 & 1889.94 & 171.07 \\ 
+  BMMIM & 3440.75 & 2226.20 & 291.22 \\ 
+  Haar-Fisz & 3113.37 & 1658.74 & 184.66 \\ 
+  Anscombe & 4038.42 & 2241.74 & 195.75 \\ 
+  Haar thresholds & 3517.89 & 1652.55 & 173.72 \\ 
+  L1\_penalty & 4705.77 & 3676.42 & 1774.51 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.}
+\label{table:pois_b}
+\end{table}
 
@@
 
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & NA & 280.29 & 312.35 & 408.32 \\ 
+  j0 = 5 \\
+ (where applicable) & NA & 246.95 & 234.90 & 408.32 \\ 
+  j0 = 6 \\
+ (where applicable) & NA & 254.54 & 261.18 & 408.32 \\ 
+  j0 = 7 \\
+ (where applicable) & NA & 367.98 & 460.04 & 408.32 \\ 
+  Average \\
+ (where applicable) & NA & 287.44 & 317.12 & 408.32 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Spikes'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_sp_8}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & 91.86 & 70.11 & 77.37 & 78.84 \\ 
+  j0 = 5 \\
+ (where applicable) & 91.86 & 65.09 & 65.43 & 78.84 \\ 
+  j0 = 6 \\
+ (where applicable) & 91.86 & 121.87 & 123.01 & 78.84 \\ 
+  j0 = 7 \\
+ (where applicable) & 91.86 & 234.08 & 237.28 & 78.84 \\ 
+  Average \\
+ (where applicable) & 91.86 & 122.79 & 125.77 & 78.84 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Angles'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_ang_8}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & 62.01 & 38.51 & 37.96 & 61.66 \\ 
+  j0 = 5 \\
+ (where applicable) & 62.01 & 59.24 & 58.61 & 61.66 \\ 
+  j0 = 6 \\
+ (where applicable) & 62.01 & 110.77 & 110.22 & 61.66 \\ 
+  j0 = 7 \\
+ (where applicable) & 62.01 & 213.36 & 213.13 & 61.66 \\ 
+  Average \\
+ (where applicable) & 62.01 & 105.47 & 104.98 & 61.66 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Heavisine'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_hs_8}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & NA & 331.11 & 340.45 & 384.56 \\ 
+  j0 = 5 \\
+ (where applicable) & NA & 323.51 & 294.31 & 384.56 \\ 
+  j0 = 6 \\
+ (where applicable) & NA & 211.35 & 235.24 & 384.56 \\ 
+  j0 = 7 \\
+ (where applicable) & NA & 331.58 & 404.25 & 384.56 \\ 
+  Average \\
+ (where applicable) & NA & 299.39 & 318.56 & 384.56 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Bursts'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_bur_8}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & 141.71 & 337.24 & 486.16 & 316.44 \\ 
+  j0 = 5 \\
+ (where applicable) & 141.71 & 333.16 & 384.27 & 316.44 \\ 
+  j0 = 6 \\
+ (where applicable) & 141.71 & 341.66 & 346.94 & 316.44 \\ 
+  j0 = 7 \\
+ (where applicable) & 141.71 & 342.12 & 341.76 & 316.44 \\ 
+  Average \\
+ (where applicable) & 141.71 & 338.54 & 389.78 & 316.44 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Clipped Blocks'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_cb_8}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{lrrrr}
+  \hline
+ & BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  \hline
+j0 = 4 \\
+ (where applicable) & NA & 1918.04 & 2553.46 & 1288.30 \\ 
+  j0 = 5 \\
+ (where applicable) & NA & 1815.30 & 1853.65 & 1288.30 \\ 
+  j0 = 6 \\
+ (where applicable) & NA & 1621.46 & 1440.67 & 1288.30 \\ 
+  j0 = 7 \\
+ (where applicable) & NA & 1280.15 & 1176.50 & 1288.30 \\ 
+  Average \\
+ (where applicable) & NA & 1658.74 & 1756.07 & 1288.30 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of different options for HF for the ``Bumps'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+\label{table:pois_hf_bump_8}
+\end{table}
+
 \end{document}

### 2016-03-10 code_paper/sim/table_gaus.R

@@ -1,6 +1,6 @@
 #This script produces supplementary tables for Gaussian simulations
 
-
+#The follow portion generates Tex tables for Gaussian simulations
 library(xtable)
 
 load("res_paper/res_gaus_dscr.RData")
@@ -91,7 +91,8 @@ print(xtable(table.3.v5.short,caption="Relative MSE of various methods for the C
 print(xtable(table.1.v4.short,caption="Relative MSE of various methods for the Bumps variance function, SNR=1, Gaussian errors",digits=ndigits))
 print(xtable(table.3.v4.short,caption="Relative MSE of various methods for the Bumps variance function, SNR=3, Gaussian errors",digits=ndigits))
 
-#####
+#####################
+#The following table includes additional information on the methods used in the simulations
 row.names.all = c("BAMS, homo, Symm8",
                   "BlockJS, homo, Symm8",
                   "Ebayes, homo, Symm8",

### 2016-03-10 package/smash/R/ashsmooth.R

@@ -328,13 +328,14 @@ shrink.wc = function(wc, wc.var.sqrt, prior, pointmass, nullcheck, VB, mixsd, mi
 #' @title mu.smooth
 #' @return 'mu.est' if posterior variances are not computed, and a list with elements 'mu.est' and 'mu.est.var' otherwise
 #' @keywords internal
-mu.smooth = function(wc, data.var, basis, tsum, Wl, post.var, prior, pointmass, nullcheck, VB, mixsd, mixcompdist, 
+mu.smooth = function(wc, data.var, basis, tsum, Wl, return.loglr, post.var, prior, pointmass, nullcheck, VB, mixsd, mixcompdist, 
     gridmult, J, n) {
     wmean = matrix(0, J, n)
     wvar = matrix(0, J, n)
     if (basis[[1]] == "haar") {
         y = wc
         vtable = cxxtitable(data.var)$sumtable
+        logLR.scale = 0
         for (j in 0:(J - 1)) {
             ind.nnull = (vtable[j + 2, ] != 0)
             zdat.ash = shrink.wc(y[j + 2, ind.nnull], sqrt(vtable[j + 2, ind.nnull]), prior = prior, pointmass = pointmass, 
@@ -342,6 +343,13 @@ mu.smooth = function(wc, data.var, basis, tsum, Wl, post.var, prior, pointmass, 
                 df = NULL, SGD = FALSE)
             wmean[j + 1, ind.nnull] = zdat.ash$PosteriorMean/2
             wmean[j + 1, !ind.nnull] = 0
+            if (return.loglr = TRUE) {
+                spins = 2^(j + 1)
+                zdat.ash$model = "EE"
+                logLR.temp = ashr:::calc_loglik(zdat.ash, y[j + 2, ind.nnull], sqrt(vtable[j + 2, ind.nnull]), NULL) -  
+                    sum(dnorm(y[j + 2, ind.nnull], 0, sqrt(vtable[j + 2, ind.nnull]), log = TRUE))
+                logLR.scale[j + 1] = logLR.temp/spins
+            }
             if (post.var == TRUE) {
                 wvar[j + 1, ind.nnull] = zdat.ash$PosteriorSD^2/4
                 wvar[j + 1, !ind.nnull] = 0
@@ -349,6 +357,9 @@ mu.smooth = function(wc, data.var, basis, tsum, Wl, post.var, prior, pointmass, 
         }
         wwmean = -wmean
[…]

### 2016-03-10 paper/supplementary/supplementary.tex
updated supplementary stuff

--- 2016-03-03 paper/supplementary/supplementary.tex
@@
 As noted in the main text, we performed an extensive simulation study for Gaussian errors using a variety of test functions (7 mean functions and 5 variance functions, including constant variance), signal-to-noise ratios (SNR = 1 and 3) and sample sizes ($T=256,512,1024$).
-The results for $T=256,512$ are saved under ~/res_paper/res_gaus_256.RData and ~/res_paper/res_gaus_512.RData respectively, while results for $T=1024$ are presented in a DSC framework (https://github.com/stephens999/dscr), saved under ~/res_paper/res_gaus_dscr.RData.
-In particular, we include an RShiny app as an interactive way to present the results for $T=1024$, the code for which can be found in the dscr-smash repo (https://github.com/zrxing/dscr-smash), under graphs.Rmd.
+For details of where the results are saved and what information they contain, refer to README.md from the \href{https://github.com/stephenslab/ashwave}{ashwave repo}.
+In particular, we include an RShiny app as an interactive way to present the results for $T=1024$, the code for which can be found in the \href{https://github.com/zrxing/dscr-smash}{dscr-smash repo}.
+For more details on the repo refer to the README.md file from the repo.
 In particular, users can view the boxplots of MISEs for the methods and test functions they are interested in by checking the appropriate boxes.
-For more details refer to graphs.Rmd.
+For more details on the RShiny display refer to graphs.Rmd in the dscr-smash repo.
+For reference, the mean and variance functions used in the simulation studes are shown below in Figures \ref{gaus_mean} and \ref{gaus_var}.
 
-In addition to the performance of the various methods, Table \ref{} also provides additional information for each of the method that we used in the simulation study.
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_sp.pdf}
+        \caption{}
+        \label{fig:gaus_sp}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_ang.pdf}
+        \caption{}
+        \label{fig:gaus_ang}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_blk.pdf}
+        \caption{}
+        \label{fig:gaus_blk}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_dop.pdf}
+        \caption{}
+        \label{fig:gaus_dop}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_bump.pdf}
+        \caption{}
+        \label{fig:gaus_bump}
+    \end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_blip.pdf}
+        \caption{}
+        \label{fig:gaus_blip}
+    \end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_cor.pdf}
+        \caption{}
+        \label{fig:gaus_cor}
+    \end{subfigure}
+    \caption{The seven mean functions used in the Gaussian simulations, all scaled to be between 0.2 and 0.8.}
+    \label{fig:gaus_mean}
+\end{figure}
+
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_var_cons.pdf}
+        \caption{}
+        \label{fig:gaus_var_cons}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_var_texp.pdf}
+        \caption{}
+        \label{fig:gaus_var_texp}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_var_dop.pdf}
+        \caption{}
+        \label{fig:gaus_var_dop}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_var_bump.pdf}
+        \caption{}
+        \label{fig:gaus_var_bump}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{gaus_var_cblk.pdf}
+        \caption{}
+        \label{fig:gaus_var_cblk}
+    \end{subfigure}
+    \caption{The five variance functions used in the Gaussian simulations, which are rescaled in the simulations to achieve the desired signal to noise ratios.}
+    \label{fig:gaus_var}
+\end{figure}
+
+In addition to the performance of the various methods, we also provide code in the \href{https://github.com/stephenslab/ashwave}{ashwave repo} generating a table that provide additional details for each method used, including the associated software, variance assumption, wavelet basis, shrinkage procedure used, and other relevant information.
 
@@
 The results from the simulation study for Poisson noise are shown in the following tables.
-Each of the six tables presents results for the corresponding mean function, and includes results for all three (min,max) intensity levels ((0.01,3), (1/8,8), (1/128,128)).
+For reference, we first plot the intensity functions used in the simulation studies in Figure \ref{fig:pois_mean}.
+Each of the six tables (\ref{table:pois_sp}-\ref{table:pois_b}) presents results for the corresponding mean function, and includes results for all three (min,max) intensity levels ((0.01,3), (1/8,8), (1/128,128)).
+As mentioned in the main text, we also explored several options for the Gaussian de-noising stage of the HF algorithm, and include the results in the following tables.
+Specifically, we considered four different options (all with 50 external cyclespins):
+\begin{enumerate}
+\item Hybrid of (1) Greedy tree de-noising (\cite{Baraniuk1999Optimal}) and (2) wavelet thresholding using ``leave-half-out'' crossvalidation (eg \cite{Nason1995Choice}).
+$j_0=3$ (default), and the noise level was estimated from the data.
+This corresponds to \textbf{H:CV+BT CS} in \cite{Fryzlewicz2004HaarFisz}.
+Note that the algorithm does not always converge for this option, resulting in NA values in the tables below.
+\item Wavelet thresholding using the universal threshold (\cite{Donoho1994Ideal}).
+$j_0=3$ (default), and the noise level was estimated from the data.
+This corresponds to \textbf{F$\bowtie$U CS} in \cite{Fryzlewicz2004HaarFisz}.
+\item Wavelet thresholding using the universal threshold for the non-decimated wavelet transform. Results averaged over $j_0=4,5,6,7$, and the noise level was estimated from the data.
+\item Wavelet thresholding using the universal threshold for the non-decimated wavelet transform.
+Results average over $j_0=4,5,6,7$, and the noise level was set to be 1 (which is the asymptotic variance under the Fisz transform).
+This is the option for which we included the results in the main text, as it had the best overall performance.
+\end{enumerate}
 
-In addition we explore the results from trying out different Gaussian de-noising procedures for the second step of the Haar-Fisz (HF) algorithm.
+\begin{figure}
+\centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_sp.pdf}
+        \caption{}
+        \label{fig:pois_sp}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_ang.pdf}
+        \caption{}
+        \label{fig:pois_ang}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_hs.pdf}
+        \caption{}
+        \label{fig:pois_hs}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_bur.pdf}
+        \caption{}
+        \label{fig:pois_bur}
+    \end{subfigure}
+		\hfill
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_cblk.pdf}
+        \caption{}
+        \label{fig:pois_cblk}
+    \end{subfigure}
+		\hfill
+		\begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{pois_bump.pdf}
+        \caption{}
+        \label{fig:pois_bump}
+    \end{subfigure}
+    \caption{The six intensity functions used in the Poisson simulations, which are rescaled to achieve the desired (min,max) intensities in the simulations.}
+    \label{fig:pois_mean}
+\end{figure}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{690.01} & 329.26 & 48.87 \\ 
+  BMSM & 1007.34 & 397.79 & 41.88 \\ 
+  BMMIM & 930.08 & 436.54 & 368.36 \\ 
+	Haar-Fisz (1) & 8194.60 & NA & 184.81 \\
+	Haar-Fisz (2) & 8074.05 & 408.32 & 158.68 \\
+	Haar-Fisz (3) & 5904.98 & 317.12 & 73.00 \\	
+  Haar-Fisz (4) & 722.19 & \textcolor{red}{287.44} & \textcolor{red}{18.06} \\ 
+  Anscombe & 1329.87 & 388.59 & 18.17 \\ 
+  Haar thresholds & 803.89 & 326.11 & 120.02 \\ 
+  L1\_penalty & 3085.65 & 2209.67 & 1516.78 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Spikes'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_sp}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{145.26} & \textcolor{red}{68.47} & 10.25 \\ 
+  BMSM & 147.40 & 73.87 & 10.49 \\ 
+  BMMIM & 245.89 & 100.17 & 71.26 \\ 
+	Haar-Fisz (1) & NA & 91.86 & 25.23 \\
+	Haar-Fisz (2) & 1020.76 & 78.84 & 12.22 \\
+	Haar-Fisz (3) & 614.95 & 125.78 & 11.29 \\	
+  Haar-Fisz (4) & 314.41 & 122.79 & \textcolor{red}{9.08} \\ 
+  Anscombe & 419.04 & 146.64 & 9.50 \\ 
+  Haar thresholds & 264.38 & 162.16 & 89.37 \\ 
+  L1\_penalty & 655.82 & 284.75 & 2979.23 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_ang}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{81.41} & \textcolor{red}{43.21} & \textcolor{red}{7.21} \\ 
+  BMSM & 85.29 & 44.22 & 7.35 \\ 
+  BMMIM & 205.09 & 81.49 & 11.22 \\ 
+	Haar-Fisz (1) & 135.42 & 62.01 & 8.10 \\
+	Haar-Fisz (2) & 105.72 & 61.66 & 6.29 \\
+	Haar-Fisz (3) & 273.97 & 104.99 & 9.98 \\	
+	Haar-Fisz (4) & 274.26 & 105.47 & 9.23 \\ 
+  Anscombe & 372.06 & 128.43 & 9.10 \\ 
+  Haar thresholds & 226.27 & 143.01 & 85.74 \\ 
+  L1\_penalty & 385.47 & 71.17 & 8.68 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Heavisine'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_hs}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{487.34} & \textcolor{red}{234.35} & 33.11 \\ 
+  BMSM & 706.04 & 301.86 & 34.42 \\ 
+  BMMIM & 654.11 & 290.91 & 531.79 \\ 
+	Haar-Fisz (1) & 6870.35 & NA & 157.15 \\
+	Haar-Fisz (2) & 6807.29 & 384.56 & 149.23 \\
+	Haar-Fisz (3) & 5619.13 & 318.57 & 94.20 \\	
+	Haar-Fisz (4) & 618.39 & 299.39 & \textcolor{red}{25.20} \\ 
+  Anscombe & 869.16 & 343.15 & 26.03 \\ 
+  Haar thresholds & 540.58 & 271.16 & 107.44 \\ 
+  L1\_penalty & 1836.73 & 1280.16 & 719.59 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Bursts'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_bur}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{307.80} & \textcolor{red}{137.28} & \textcolor{red}{6.82} \\ 
+  BMSM & 355.15 & 143.09 & 6.91 \\ 
+  BMMIM & 472.24 & 205.20 & 150.03 \\ 
+	Haar-Fisz (1) & NA & 141.71 & 31.23 \\
+	Haar-Fisz (2) & 879.20 & 316.44 & 26.71 \\
+	Haar-Fisz (3) & 741.49 & 389.79 & 48.41 \\	
+	Haar-Fisz (4) & 632.21 & 338.55 & 29.72 \\ 
+  Anscombe & 804.70 & 384.46 & 28.94 \\ 
+  Haar thresholds & 467.64 & 228.14 & 82.99 \\ 
+  L1\_penalty & 1021.58 & 627.67 & 1961.42 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_cb}
+\end{table}
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{rrrr}
+  \hline
+ & (0.01,3) & (1/8,8) & (1/128,128) \\ 
+  \hline
+SMASH & \textcolor{red}{2597.46} & \textcolor{red}{1194.62} & \textcolor{red}{141.21} \\ 
+  BMSM & 4036.77 & 1889.94 & 171.07 \\ 
+  BMMIM & 3440.75 & 2226.20 & 291.22 \\ 
+	Haar-Fisz (1) & 9515.68 & NA & 187.6 \\
+	Haar-Fisz (2) & 9249.05 & 1288.30 & 130.19 \\
+	Haar-Fisz (3) & 6286.05 & 1756.08 & 248.28 \\	
+	Haar-Fisz (4) & 3113.37 & 1658.74 & 184.66 \\ 
+  Anscombe & 4038.42 & 2241.74 & 195.75 \\ 
+  Haar thresholds & 3517.89 & 1652.55 & 173.72 \\ 
+  L1\_penalty & 4705.77 & 3676.42 & 1774.51 \\ 
+   \hline
+\end{tabular}
+\caption{Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
+Values colored in red indicates the smallest MISE amongst all methods (excluding Haar-Fisz (1-3)) for a given (min, max) intensity.}
+\label{table:pois_b}
+\end{table}
+
+%
+%In addition we explore the results from trying out different Gaussian de-noising procedures for the second step of the Haar-Fisz (HF) algorithm.
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & NA & 280.29 & 312.35 & 408.32 \\ 
+  %j0 = 5 \\
+ %(where applicable) & NA & 246.95 & 234.90 & 408.32 \\ 
+  %j0 = 6 \\
+ %(where applicable) & NA & 254.54 & 261.18 & 408.32 \\ 
+  %j0 = 7 \\
+ %(where applicable) & NA & 367.98 & 460.04 & 408.32 \\ 
+  %Average \\
+ %(where applicable) & NA & 287.44 & 317.12 & 408.32 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Spikes'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_sp_8}
+%\end{table}
+%
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & 91.86 & 70.11 & 77.37 & 78.84 \\ 
+  %j0 = 5 \\
+ %(where applicable) & 91.86 & 65.09 & 65.43 & 78.84 \\ 
+  %j0 = 6 \\
+ %(where applicable) & 91.86 & 121.87 & 123.01 & 78.84 \\ 
+  %j0 = 7 \\
+ %(where applicable) & 91.86 & 234.08 & 237.28 & 78.84 \\ 
+  %Average \\
+ %(where applicable) & 91.86 & 122.79 & 125.77 & 78.84 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Angles'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_ang_8}
+%\end{table}
+%
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & 62.01 & 38.51 & 37.96 & 61.66 \\ 
+  %j0 = 5 \\
+ %(where applicable) & 62.01 & 59.24 & 58.61 & 61.66 \\ 
+  %j0 = 6 \\
+ %(where applicable) & 62.01 & 110.77 & 110.22 & 61.66 \\ 
+  %j0 = 7 \\
+ %(where applicable) & 62.01 & 213.36 & 213.13 & 61.66 \\ 
+  %Average \\
+ %(where applicable) & 62.01 & 105.47 & 104.98 & 61.66 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Heavisine'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_hs_8}
+%\end{table}
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & NA & 331.11 & 340.45 & 384.56 \\ 
+  %j0 = 5 \\
+ %(where applicable) & NA & 323.51 & 294.31 & 384.56 \\ 
+  %j0 = 6 \\
+ %(where applicable) & NA & 211.35 & 235.24 & 384.56 \\ 
+  %j0 = 7 \\
+ %(where applicable) & NA & 331.58 & 404.25 & 384.56 \\ 
+  %Average \\
+ %(where applicable) & NA & 299.39 & 318.56 & 384.56 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Bursts'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_bur_8}
+%\end{table}
+%
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & 141.71 & 337.24 & 486.16 & 316.44 \\ 
+  %j0 = 5 \\
+ %(where applicable) & 141.71 & 333.16 & 384.27 & 316.44 \\ 
+  %j0 = 6 \\
+ %(where applicable) & 141.71 & 341.66 & 346.94 & 316.44 \\ 
+  %j0 = 7 \\
+ %(where applicable) & 141.71 & 342.12 & 341.76 & 316.44 \\ 
+  %Average \\
+ %(where applicable) & 141.71 & 338.54 & 389.78 & 316.44 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Clipped Blocks'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_cb_8}
+%\end{table}
+%
+%\begin{table}[ht]
+%\centering
+%\begin{tabular}{lrrrr}
+  %\hline
+ %& BT + CV & \pbox{20cm}{TI-universal \\ sd = 1} & \pbox{20cm}{TI-universal \\ sd estimated} & \pbox{20cm}{Universal \\ thresholding} \\ 
+  %\hline
+%j0 = 4 \\
+ %(where applicable) & NA & 1918.04 & 2553.46 & 1288.30 \\ 
+  %j0 = 5 \\
+ %(where applicable) & NA & 1815.30 & 1853.65 & 1288.30 \\ 
+  %j0 = 6 \\
+ %(where applicable) & NA & 1621.46 & 1440.67 & 1288.30 \\ 
+  %j0 = 7 \\
+ %(where applicable) & NA & 1280.15 & 1176.50 & 1288.30 \\ 
+  %Average \\
+ %(where applicable) & NA & 1658.74 & 1756.07 & 1288.30 \\ 
+   %\hline
+%\end{tabular}
+%\caption{Comparison of different options for HF for the ``Bumps'' test function for (min,max) intensity = (1/8,8).
+Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3.
+TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance).
+For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row.
+Note here that BT + CV do not converge due to numerical issues.
+Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.}
+%\label{table:pois_hf_bump_8}
+%\end{table}
+
+\bibliography{../smash}
 

### 2016-03-10 code_paper/sim/plot_supp.R

@@ -1,0 +1,202 @@
+### Functions for Gaussian simulations
+n = 1024
+t = 1:n/n
+
+
+spike.f = function(x) (0.75 * exp(-500 * (x - 0.23)^2) + 1.5 * exp(-2000 * (x - 0.33)^2) + 3 * exp(-8000 * (x - 0.47)^2) + 
+                         2.25 * exp(-16000 * (x - 0.69)^2) + 0.5 * exp(-32000 * (x - 0.83)^2))
+mu.s = spike.f(t)
+
+pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
+hgt = 2.97/5 * c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
+wth = c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005, 0.008, 0.005)
+mu.b = rep(0, n)
+for (j in 1:length(pos)) {
+  mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
+}
+
+
+dop.f = function(x) sqrt(x * (1 - x)) * sin((2 * pi * 1.05)/(x + 0.05))
+mu.dop = dop.f(t)
+mu.dop = 3/(max(mu.dop) - min(mu.dop)) * (mu.dop - min(mu.dop))
+mu.dop.var = 10 * dop.f(t)
+mu.dop.var = mu.dop.var - min(mu.dop.var)
+
+
+
+sig = ((2 * t + 0.5) * (t <= 0.15)) + ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) + 0.2 * (t > 0.2 & t <= 0.5) + 
+  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) + ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) + ((-0.5 * (t - 
+                                                                                                                   0.65) + 0.3) * (t > 0.65 & t <= 0.85)) + ((2 * (t - 0.85) + 0.2) * (t > 0.85))
+mu.ang = 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
+
+
+
[…]

### 2016-03-10 code_paper/sim/pois/sim_hf.R

@@ -1307,5 +1307,46 @@ colnames(mise.cb.128.table) = tex.col.names
 rownames(mise.b.128.table) = tex.row.names
 colnames(mise.b.128.table) = tex.col.names
 
-print(xtable(mise.s.8.table,caption="Comparison of different options for HF for the ``Spikes'' test function for (min,max) intensity = (1/8,8). Options BT + CV and Universal thresholding correspond to the two default oness used in {Fryzlewicz2004HaarFisz}, with primary resolution j0 =3. TI-universal corresponds to universal thresholding with translational invariance, with sd either estimated from the data or set to be 1 (which is the asymptotic variance). For TI-universal, we ran the HF with j0 = 4, 5, 6 and 7, corresponding to the first 4 rows, as well as the average of all 4 values, corresponding to the 5th row. Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_hf_sp_8",digits=2))
 
+mise.s.1.table = mise.s.1.table[, c(1, 4, 3, 2)]
+mise.ang.1.table = mise.ang.1.table[, c(1, 4, 3, 2)]
+mise.hs.1.table = mise.hs.1.table[, c(1, 4, 3, 2)]
+mise.bur.1.table = mise.bur.1.table[, c(1, 4, 3, 2)]
+mise.cb.1.table = mise.cb.1.table[, c(1, 4, 3, 2)]
+mise.b.1.table = mise.b.1.table[, c(1, 4, 3, 2)] 
+
+mise.s.8.table = mise.s.8.table[, c(1, 4, 3, 2)]
+mise.ang.8.table = mise.ang.8.table[, c(1, 4, 3, 2)]
+mise.hs.8.table = mise.hs.8.table[, c(1, 4, 3, 2)]
+mise.bur.8.table = mise.bur.8.table[, c(1, 4, 3, 2)]
+mise.cb.8.table = mise.cb.8.table[, c(1, 4, 3, 2)]
+mise.b.8.table = mise.b.8.table[, c(1, 4, 3, 2)]
+
+mise.s.128.table = mise.s.128.table[, c(1, 4, 3, 2)]
+mise.ang.128.table = mise.ang.128.table[, c(1, 4, 3, 2)]
[…]

### 2016-03-10 paper/draft_7.tex
updated draft

@@
 
-We have  adaptive shrinkage method ASH; while it was originally developed in the setting of FDR control for multiple comparisons, we have illustrated its usage as part of two wavelet denoising techniques.
-Both applications discussed in this paper relax the standard assumption of i.i.d.
-Gaussian noise, and are thus challenging tasks.
-Through these applications we are able to demonstrate the flexibility and accuracy of the shrinkage method, revealing its potential in many other applications.
-
-First, our method provides a measure of uncertainty (through both the credible band for the mean curve as well as the variance curve itself), which is often of interest in many applications.
-
-In both the aforementioned applications, our software allows users to easily obtain point estimates for the mean function as well as their approximate posterior variances as a measure of uncertainty.
-In addition, the variance function can also be estimated, which would provide frequentist confidence intervals for other forms of mean estimation.
-To the best of our knowledge, there is no readily available software in the wavelet literature that implements joint mean and variance estimation.
-Simulations have also confirmed that our method is relatively robust to simple forms of autocorrelation between the errors (details needed).
-In the case of Poisson regression, we improved upon the conjugate Beta priors in \cite{Kolaczyk1999Bayesian} by using ASH as a shrinkage procedure, which allows for more flexibility and precision.
-%In addition, we have proposed a new procedure to assess the performance of a given method on real datasets without knowing the underlying truth, under the assumption that the data follow a Poisson distribution.
-In both the applications, one further advantage of both our methods is that there is no tuning parameter other than the type of wavelet basis used.
-On the other hand, the primary resolution level in almost all of the other wavelet-based methods actually affects their performance in varying degrees, depending on the underlying mean and/or variance function.
-Hence, our fully adaptive procedure allows users to easily apply it to any given dataset, depending on the type of noise.
-
-potential to use likelihood to assess wavelet basis?
-
-We have also demonstrated through numerical studies that our methods mostly outperform their respective counterparts from the standard wavelet literature, in terms of pointwise accuracy (MSE in this case).
-Furthermore, the simplicity of the approximated Gaussian likelihoods as well as the conjugacy of the mixture Gaussian priors imply that our methods are computationally fast, since the posteriors can be computed analytically.
-In the Gaussian case, simulation results demonstrated that our method is competitive with standard wavelet methods in the case of i.i.d.
-errors (without explicitly assuming thus), whilst maintaining superior accuracy when heteroskedastic errors are present.
+\def\ash{\it ash}
+
+Here we have demonstrated a flexible EB approach to shrinkage, which we call ``adaptive shrinkage" (\ash), in the context of wavelet denoising. 
+The adaptive shrinkage approach is built on the assumption that the distribution of
+true effects -- here, wavelet coefficients -- is unimodal about zero. By estimating this unimodal distribution from the observed data, \ash 
+adapts the amount of shrinkage to the data in hand, so that data that ``look smooth" are smoothed more strongly than data that do not. 
+In addition \ash accounts for the precision of each measurement (here, observed wavelet coefficients), 
+so that less precise measurements are shrunk more strongly than precise measurements. This means that, for example, in heteroskedastic non-parametric regression, 
+the mean gets smoothed more strongly in regions where the variance is bigger.
+
+Notably, and unlike many wavelet shrinkage approaches, \ash is ``self-tuning", and requires no specification of a ``primary resolution level" \cite{}
+or other tuning parameters. This feature is due to the ``adaptive" nature of \ash noted above: when a particular resolution level shows no strong signal
+in the data, \ash learns this and adapts the amount of shrinkage/smoothing appropriately. Furthermore, because it is fundamentally a likelihood-based
+approach, \ash can also be used to automatically select an appropriate wavelet basis for each dataset -- which can have a strong impact on accuracy --
+by selecting the basis that achieves the highest likelihood. This self-tuning capability is important for two reasons.
+First it makes the method easy to use by non-experts, who may find appropriate specification of tuning parameters challenging. Second, it means that the
+method can be safely applied ``in production" to large numbers of datasets in settings, like genomics, where it is impractical to
+hand-select appropriate tuning parameters separately for every dataset.
+
+Our results here demonstrate that \ash provides a flexible, fast and accurate approach to smoothing and denoising. We illustrated the flexibility by applying
+it to two challenging problems - Gaussian heteroskedastic regression, and smoothing of Poisson signals. In both cases the accuracy of our method is
+consistently competitive with existing approaches for which software implementations are available. And although, like most EB methods,
+\ash requires more computation than a simple thresholding rule, the computations are fast enough to be applied to large problems. 
+This is partly because
+optimizing over the unimodal prior distribution assumed by \ash results in a convex optimization problem that can be solved very stably and quickly \cite{stephens:2016}.
+(For example, our implementation typically takes approximately yyy for 100,000 observations.)
+Besides its accuracy for point estimation, \ash also has the advantage over simple thresholding rules that it naturally provides measures of uncertainty in estimated
+wavelet coefficients, which in turn provide measures of uncertainty (e.g. credible bands) for estimated mean and variance functions, which may be of interest in some applications.
+
+Although we have focussed here on applications in one dimension, there is nothing to stop \ash being applied to multi-scale approaches in higher dimensions, such as image denoising, as in \cite{Nowak1999Multiscale} for example.
+For some types of images alternatives to wavelets, such as curvelets \cite{Cande00}, may produce better results,
+and applying \ash to those settings would be an interesting area for future work.
+%maybe discuss over-defined bases?
+
 Unfortunately, the lack of readily available software (except for MFVB, as described in \cite{Menictas2015Variational}) for variance estimation made it difficult to assess the performance of our method in that context.
@@
 
-Although we focused on one-dimensional univariate denoising, our methods could be extended to more complex scenarios.
-In the one-dimensional domain, our methods could be used in conjunction with multiple samples, otherwise known as regression analysis of functional data (see \cite{Morris2006Waveletbased}).
-Instead of dealing with a vector of observations, we perform regression analysis on a matrix of observations, each row of which encapsulates a sample with temporally or spatially structured data points.
-While \cite{Morris2006Waveletbased} proposed a way to solve a generic regression model, they implicitly assumed the same variance structure for each sample in the same group or category.
-Our work in the Gaussian case potentially allows for differing variance structures amongst all the samples, thereby relaxing their assumptions.
-In the simplest case, we could obtain spatially structured differences between groups by including a single covariate that categorizes each sample.
-In particular, the Poisson model is extremely useful for discovering regions in sequencing reads where structured differences are present between say, various cell lines, as per our sequencing example in the previous section.
-The Gaussian model could potentially be used in...(??).
-
-With some work, our methods could also be extended to higher dimensions, where a wider range of applications is possible.
-For example, we could attempt a straight extension to the two dimensional case for both the Gaussian and the Poisson cases as described in \cite{Nowak1999Multiscale}.
-However, recent research in image denoising problems has shown that discontinuities along edges present in many images such as photographs might render wavelet transformations undesirable \cite{Cande00}.
-We could thus incorporate ASH into other types of transformations such as curvelets \cite{Cande00}, which would be a potential direction for future work.
-\newpage
+Software
+Despite the fact that these settings
+arise quite commonly, there is a paucity of software implementations for both these problems, and our software package (smash
+To the best of our knowledge, there is no readily available software in the wavelet literature that implements joint mean and variance estimation.
+
 \section{Reference}

### 2018-07-03 dsc/graphs.Rmd
Added dscr-smash files.

---
title: "Graphs"
runtime: shiny
output: html_document
---

The following code generates an RShiny app which displays boxplots of MISEs from the full simulation study comparing SMASH to other wavelet-based methods for denoising Gaussian data. As mentioned in the companion paper, the results for a variety of test functions (both mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1 and 3, are presented here.

Scenarios denote a combination of mean function, SNR and variance function. Specifically, each scenario is named as [mean_function].[SNR].[variance_function], where the abbreviations are given by:
Mean function:  
Spikes - sp  
Bumps - bump  
Blocks - blk  
Angles - ang  
Doppler - dop  
Blip - blip  
Corner - cor

Variance function:  
Constant function - v1  
Triple exponential - v2  
Doppler - v3  
Bumps - v4  
Clipped Blocks - v5

On the other hand, we also ran a variety of methods in the simulation study. The methods are abbreviated as follows:  
EbayesThresh - ebayesthresh  
BAMS - bams  
BlockJS - blockjs 
Neighblock - neighblock  
SureShrink - sure  
Bayesian Posterior Mean - postmean  
TI thresholding - tithresh  
SMASH - smash

In addition, EbayeThresh, BAMS, BlockJS, Neighblock, Sureshrink and Bayesian Posterior Mean all assume homoskedastic noise and use the Symm8 basis by default. TI thresholding was run with both the homoskedastic (tithresh.homo) using the Symm8 (.s8) basis, as well as an estimated variance using RMAD (tithresh.rmad) and SMASH (tithresh.smash), with both the Haar (.haar) and the Symm8 (.s8) bases. In addition, TI thresholding was also run with the true variance provided (tithresh.true) using both the Haar (.haar) and the Symm8 (.s8) bases.

We ran SMASH with the homoskedatic (smash.homo) assumption using both Haar (haar) and Symm8 (.s8). In addition, SMASH was also run with the variance jointly estimated, using either the JASH procedure (smash.jash) or the ASH procedure (smash.haar and smash.s8 for the two different bases). Paralleling TI thresholding, we also ran SMASH with the true variance provided (smash.true) using both the Haar (.haar) and the Symm8 (.s8) bases.

```{r, echo=FALSE}
library(ggplot2)
library(dplyr)
load("res.RData")
scenario_names = as.character(unique(res$scenario))
method_names = as.character(unique(res$method))
#numeric_criteria = names(res)[unlist(lapply(res,is.numeric))]

inputPanel(    
    # Create the checkboxes and select them all by default
    checkboxGroupInput("scen.subset", "Choose Scenarios", 
                        choices  = scenario_names,
                        selected = "sp.1.v2"),

    checkboxGroupInput("method.subset", "Choose Methods", 
                        choices  = method_names,
                        selected = method_names),

    selectInput("criteria", "Choose Criteria", 
                        choices  = "mise",
                        selected = "mise")
)

renderPlot({
  res.filter = filter(res,scenario %in% input$scen.subset & method %in% input$method.subset)
  print(input)
  res.filter$value = res.filter[[input$criteria]]
  ggplot(res.filter, aes(method, value, color = method)) + geom_boxplot() + facet_grid(.~scenario) + 
    theme(axis.ticks = element_blank(), axis.text.x = element_blank())
})
```

### 2018-07-03 dsc/check.output.R

@@ -1,0 +1,37 @@
+
+# Load the old results.
+load("~/git/smash-paper/output/gaus_dscr.RData")
+out0 <- res
+
+# Load the new results.
+load("res.RData")
+out1 <- res
+
+relerr <- function (x, y)
+  abs(x - y)/abs(x)
+
+iter <- 0
+e    <- rep(0,1400)
+methods <- unique(out0$method)
+varfn.short <- c("cons", "texp", "dop", "bump", "cblk")
+for (m in methods) {
+  for (i in c("sp", "bump", "blk", "ang", "dop", "blip", "cor")) {
+    for (j in c(1,3)) {
+      for (k in 1:5) {
+        k0 <- paste0("v",k)
+        k1 <- varfn.short[k]
+        rows0 <- with(out0,which(method   == m &
+                                 scenario == paste(i,j,k0,sep = ".")))
+        rows1 <- with(out1,which(method == m &
+                                 scenario == paste(i,j,k1,sep = ".")))
+        x       <- head(out0$mise[rows0],n = 3)
+        y       <- out1$mise[rows1]
+        iter    <- iter + 1
+        e[iter] <- max(relerr(x,y))
+        if (e[iter] > 0.05) {
+          print(c(m,i,j,k1,e[iter]))
+        }
+      }
+    }
+  }
+}

### 2018-07-03 dsc/methods.R

@@ -1,0 +1,98 @@
+source_dir("methods")
+
+parse.period.delimited.name <- function(name) {
+  return(strsplit(name, ".", fixed = TRUE)[[1]])
+}
+
+build.period.delimited.name <- function(words) {
+  return(paste(words, collapse = "."))
+}
+
+suffix <- function(name) {
+  words <- parse.period.delimited.name(name)
+  return(words[length(words)])
+}
+
+remove.suffix <- function(name) {
+  words <- parse.period.delimited.name(name)
+  return(build.period.delimited.name(words[1:(length(words) - 1)]))
+}
+
+fxn.wrapper <- function(name, named.method) {
+    if ((suffix(name) == "s8") || (suffix(name) == "haar")) {
+        if (named.method) {
+            stem <- remove.suffix(remove.suffix(name))
+        } else {
+            stem <- remove.suffix(name)
+        }
+    } else {
+        stem <- name
+    }
+    return(parse(text = paste(stem, "wrapper", sep = ".")))
+}
+
+arg.list <- function(name, named.method, blank.arglist) {
+    args <- list()
+
+    if (!blank.arglist) {
+        if (named.method) {
+            args$method <- suffix(remove.suffix(name))
+        }
+
+        if (suffix(name) == "haar") {
+            args$filter.number <- 1
+            args$family <- "DaubExPhase"
+        } else {
+            
+            # This covers a suffix of "s8" but also the case
+            # "smash.jash".
+            args$filter.number <- 8
+            args$family <- "DaubLeAsymm"
+        }
+    }
+
+    return(args)
+}
+
+add.method.by.flags <- function(row) {
+  method.name <- as.character(row$name)
+  add_method(dsc_smash,
+             name = method.name,
+             fn   = eval(fxn.wrapper(method.name,row$named.method)),
+             args = arg.list(method.name,row$named.method,row$blank.arglist))
+}
+
+# Define methods and flags used to name the function wrappers and
+# argument lists. The first seven of this list use a blank argument
+# list. The tithresh.rmad and tithresh.smash methods put the
+# penultimate word in the argument list instead of using separate
+# wrappers.
+methods <- data.frame(list(name = c("ebayesthresh",
+                                    "bams.homo.s8",
+                                    "blockjs.homo.s8",
+                                    "neighblock.homo.s8",
+                                    "sure.homo.s8",
+                                    "postmean.homo.s8",
+                                    "tithresh.homo.s8",
+                                    "smash.homo.haar",
+                                    "smash.homo.s8",
[…]

### 2018-07-03 dsc/methods/bams.homo.wrapper.R

@@ -1,0 +1,13 @@
+bams.homo.wrapper = function(input, args) {
+  write(input$x, "input/ml_in.txt", ncolumns = length(input$x))
+  system(paste(matlab.exec,"-r \"run('methods/bams_matlab.m')\""),
+         ignore.stdout = TRUE)
+  if (Sys.info()["sysname"] == "Windows") {
+    while (!file.exists("input/ml_out.csv")) {
+      Sys.sleep(5)
+    }
+  }
+  mu.est = as.vector(read.csv("input/ml_out.csv", header = FALSE))
+  system("rm input/ml_in.txt input/ml_out.csv")
+  return(mu.est)
+} 

### 2018-07-03 dsc/methods/blockjs.homo.wrapper.R

@@ -1,0 +1,13 @@
+blockjs.homo.wrapper = function(input, args) {
+  write(input$x, "input/ml_in.txt", ncolumns = length(input$x))
+  system(paste(matlab.exec,"-r \"run('methods/blockjs_matlab.m')\""),
+         ignore.stdout = TRUE)
+  if (Sys.info()["sysname"] == "Windows") {
+    while (!file.exists("input/ml_out.csv")) {
+      Sys.sleep(5)
+    }
+  }
+  mu.est = as.vector(read.csv("input/ml_out.csv", header = FALSE))
+  system("rm input/ml_in.txt input/ml_out.csv")
+  return(mu.est)
+} 

### 2018-07-03 dsc/methods/blockjs_matlab.m

@@ -1,0 +1,7 @@
+load('../input/ml_in.txt');
+est = recblockJS('Augment', ml_in);
+csvwrite('../input/ml_out.csv', est);
+exit
+
+
+

### 2018-07-03 dsc/methods/neighblock_matlab.m

@@ -1,0 +1,6 @@
+load('../input/ml_in.txt');
+est = recneighblock(ml_in);
+csvwrite('../input/ml_out.csv', est);
+exit
+
+

### 2018-07-03 dsc/methods/smash.homo.wrapper.R

@@ -1,0 +1,10 @@
+#runs wavelet shrinkage method SMASH assuming a constant variance
+#inputs:
+#input: a list containing x: the data, sig.true the true sigma values, and sig.est: the estimated sigma values
+#args: a list containing family and filter.number, which determine the wavelet basis used
+#
+#returns the estimated (posterior mean) mean function
+smash.homo.wrapper = function(input, args) {
+  mu.est = smash.gaus(input$x, input$sig.est, filter.number = args$filter.number, family = args$family)
+  return(mu.est)
+} 

### 2018-07-03 dsc/methods/smash.wrapper.R

@@ -1,0 +1,10 @@
+#runs wavelet shrinkage method SMASH and jointly estimates the variance function
+#inputs:
+#input: a list containing x: the data, sig.true the true sigma values, and sig.est: the estimated sigma values
+#args: a list containing family and filter.number, which determine the wavelet basis used
+#
+#returns the estimated (posterior mean) mean function
+smash.wrapper = function(input, args) {
+  mu.est = smash.gaus(input$x, filter.number = args$filter.number, family = args$family)
+  return(mu.est)
+} 

### 2018-07-03 dsc/methods/sure.homo.wrapper.R

@@ -1,0 +1,13 @@
+sure.homo.wrapper = function(input, args) {
+  write(input$x, "input/ml_in.txt", ncolumns = length(input$x))
+  system(paste(matlab.exec,"-r \"run('methods/sure_matlab.m')\""),
+         ignore.stdout = TRUE)
+  if (Sys.info()["sysname"] == "Windows") {
+    while (!file.exists("input/ml_out.csv")) {
+      Sys.sleep(5)
+    }
+  }
+  mu.est = as.vector(read.csv("input/ml_out.csv", header = FALSE))
+  system("rm input/ml_in.txt input/ml_out.csv")
+  return(mu.est)
+} 

### 2018-07-03 dsc/methods/tithresh.homo.wrapper.R

@@ -1,0 +1,13 @@
+tithresh.homo.wrapper = function(input, args) {
+  write(input$x, "input/ml_in.txt", ncolumns = length(input$x))
+  system(paste(matlab.exec,"-r \"run('methods/tithresh_matlab.m')\""),
+         ignore.stdout = TRUE)
+  if (Sys.info()["sysname"] == "Windows") {
+    while (!file.exists("input/ml_out.csv")) {
+      Sys.sleep(5)
+    }
+  }
+  mu.est = as.vector(read.csv("input/ml_out.csv", header = FALSE))
+  system("rm input/ml_in.txt input/ml_out.csv")
+  return(mu.est)
+} 

### 2018-07-03 dsc/run_dsc.R

@@ -1,0 +1,31 @@
+library(dscr)
+library(AlgDesign)
+library(EbayesThresh)
+library(wavethresh)
+library(smashr)
+
+# SCRIPT PARAMETERS
+# -----------------
+# This specifies the command to start MATLAB. Note that the -r option
+# is added to this command to run the methods implemented in MATLAB.
+matlab.exec <- "matlab -nodisplay -nodesktop"
+
+# DEFINE THE DSC
+# --------------
+cat("Constructing DSC.\n")
+dscr.path <- getwd()
+dsc_smash <- new_dsc("mean_function_estimation","dscr-smash-output")
+source("scenarios.R")
+source("methods.R")
+source("score.R")
+
+# RUN THE DSC
+# -----------
+cat("Running DSC.\n")
+timing <- system.time(res <- run_dsc(dsc_smash))
+cat(sprintf("Computation took %d seconds.\n",round(timing["elapsed"])))
+
+# SAVE RESULTS TO FILE
+# --------------------
+cat("Saving DSC results to file.\n")
+save(list = c("dsc_smash","res"),file = "res.RData")

### 2018-07-03 dsc/scenarios.R

@@ -1,0 +1,15 @@
+source_dir("datamakers")
+
+meanfn = c(spikes.fn, bumps.fn, blocks.fn, angles.fn, doppler.fn, blip.fn, cor.fn)
+meanfn.short = c("sp", "bump", "blk", "ang", "dop", "blip", "cor")
+rsnr = sqrt(c(1, 3))
+varfn = c(cons.fn, texp.fn, doppler.fn, bumps.fn, cblocks.fn)
+varfn.short = c("cons", "texp", "dop", "bump", "cblk")
+
+design = gen.factorial(c(length(varfn), length(rsnr), length(meanfn)), center = FALSE)
+
+for (i in 1:dim(design)[1]) {
+  scenario.name = paste(meanfn.short[design[i, 3]], rsnr[design[i, 2]]^2, varfn.short[design[i, 1]], sep = ".")
+  scenario.args = list(n = 1024, rsnr = rsnr[design[i, 2]], meanfn = meanfn[[design[i, 3]]], varfn = varfn[[design[i, 1]]])
+  add_scenario(dsc_smash, name = scenario.name, fn = gaussian.1d, args = scenario.args, seed = 1:3)
+}

### 2018-08-23 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

---
title: "Spikes demo"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This script illustrates key features of the smash method on a small,
simulated data set.

Set up environment
------------------

We begin by loading the ashr, smashr, scales, ggplot2 and cowplot
packages, as well as some additional functions used in the code below.

```{r load-pkgs}
library(ashr)
library(smashr)
library(scales)
library(ggplot2)
suppressMessages(library(cowplot))
source("../code/misc.R")
```

Define the "spikes" mean function
---------------------------------

Function `spike.f` defines the mean signal.

```{r define-spikes}
n <- 1024
t <- 1:n/n
spike.f <-
  function (x) (0.75 * exp(-500   * (x - 0.23)^2) +
                1.5  * exp(-2000  * (x - 0.33)^2) +
                3    * exp(-8000  * (x - 0.47)^2) +
                2.25 * exp(-16000 * (x - 0.69)^2) +
                0.5  * exp(-32000 * (x - 0.83)^2))
mu.sp <- spike.f(t)
mu.sp <- (1 + mu.sp)/5
```

Simulate data
-------------

*Add text here.*

```{r simulate-data}
pos <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
hgt <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
sig.cb <- rep(0,length(t))
for (j in 1:length(pos)) 
  sig.cb <- sig.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
sig.cb[sig.cb < 0] <- 0
sig.cb <- 0.1 + (sig.cb - min(sig.cb))/max(sig.cb)
rsnr   <- sqrt(3)
sig.cb <- sig.cb/mean(sig.cb) * sd(mu.sp)/rsnr^2
x.sim  <- rnorm(n,mu.sp,sig.cb)
```

Plot the simulated data set.

```{r plot-simulated-data}
par(cex.axis = 0.8,cex.sub = 1,cex.lab = 1)
plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
     ylab = "",lwd = 1.7,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
points(x.sim,cex = 0.7,pch = 16,col = "darkblue")
```

Run SMASH and TI thresholding
-----------------------------

Apply smash and translation invariant (TI) thresholding to the
"spikes" data. Here, we run the TI thresholding twice---once when
the standard deviation (s.d.) function is provided, and once when it
is estimated using the MAD algorithm.

```{r denoise-signals}
sig.est  <- sqrt(2/(3 * (n - 2)) *
                 sum((1/2 * x.sim[1:(n-2)] - x.sim[2:(n-1)] + x.sim[3:n])^2/2))
mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                      filter.number = 8)
mu.ti.homo <- ti.thresh(x.sim,sigma = sig.est,family = "DaubLeAsymm",
                        filter.number = 8)
```

Get the wavelet coefficients and their variances.

```{r compute-wcs}
wc.sim     <- titable(x.sim)$difftable
wc.var.sim <- titable(sig.cb^2)$sumtable
wc.true    <- titable(mu.sp)$difftable
```

Get shrunken estimates of the wavelet coefficients.

```{r compute-shrunk-wcs}
wc.sim.shrunk <- vector("list",10)
wc.pres       <- vector("list",10)
for(j in 0:(log2(n) - 1)){
  wc.sim.shrunk[[j+1]] <-
    ash(wc.sim[j+2,],sqrt(wc.var.sim[j+2,]),prior = "nullbiased",
        pointmass = TRUE,mixsd = NULL,mixcompdist = "normal",
        gridmult = 2,df = NULL)$result
  wc.pres[[j+1]] <- 1/sqrt(wc.var.sim[j+2,])
}
```

Summarize results
-----------------

Plot the distribution of observed wavelet coefficients.

```{r}
par(cex.axis = 0.8,cex.lab = 0.8)
hist(wc.sim[4,],breaks = 2,xlab = "observed wavelet coefficients",
     xlim = c(-25,25),ylim = c(0,600),col = "darkblue",xaxp = c(-25,25,10),
     yaxp = c(0,600,6),main = "")
hist(wc.sim[10,],breaks = 40,add = TRUE,col = "darkorange")
```

Plot the observed wavelet coefficients (at scales 1 and 7 only)
vs. the "shrunken" wavelet coefficients estimated by adaptive
shrinkage.

```{r}
par(cex.axis = 0.8,cex.lab = 0.8)
plot(c(),c(),xlab = "observed wavelet coefficients",
     ylab = "shrunken wavelet coefficients",
     xlim = c(-2.5,2.5),ylim = c(-2.5,2.5))
abline(0,1,lty = 1,col = "gray",lwd = 1)
points(wc.sim[10,],wc.sim.shrunk[[9]]$PosteriorMean,pch = 20,cex = 0.6,
       col = "darkorange")
points(wc.sim[4,],wc.sim.shrunk[[3]]$PosteriorMean,pch = 20,cex = 0.6,
       col = "darkblue")
```

Plot the observed wavelet coefficients (at scale 7 only) vs. the
"shrunken" wavelet coefficients estimated by adaptive shrinkage, and
how how the amount of shrinkage depends on the standard error (s.e.)
in the observations.

```{r}
wc.sig.3 <- 1/wc.pres[[3]]
p <- ggplot(data.frame(observed = wc.sim[4,],
                       shrunken = wc.sim.shrunk[[3]]$PosteriorMean,
                       se       = wc.sig.3),
            aes(x = observed,y = shrunken,col = se)) +
  geom_point() +
  xlim(c(-1,1)) +
  ylim(c(-1,1)) +
  scale_color_gradientn(colors = c("deepskyblue","darkblue")) +
  theme_cowplot()
print(p)
```

Plot the ground-truth signal (mean function) and the signals
recovered by the TI thresholding and smash methods.

```{r}
par(cex.axis = 0.8)
plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.ti,col = "dodgerblue",lwd = 1.5)
lines(mu.smash,col = "orangered",lwd = 1.5)
cat("Demo is over.\n")
```

### 2018-08-23 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 
-This script illustrates key features of the smash method on a small,
-simulated data set.
+This script illustrates key features of the SMASH method on a small,
+simulated data set with heteroskedastic variances.
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+```
 
@@
 
-```{r load-pkgs}
+```{r load-pkgs, warning=FALSE}
 library(ashr)
@@
 
-Function `spike.f` defines the mean signal.
+Variable `mu.sp` defines the mean signal.
 
@@
 
-*Add text here.*
+Simulate the noisy observations from the normal distribution with
+means that are given by the "spikes" function, and with
+spatially-structured variances.
 
@@
 
-```{r plot-simulated-data}
-par(cex.axis = 0.8,cex.sub = 1,cex.lab = 1)
+```{r plot-simulated-data, fig.height=5, fig.width=10}
+par(cex.axis = 1,cex.lab = 1.5)
 plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
@@
 
+This plot shows the "spikes" mean function (the black line),
++/- 2 standard deviations (the yellow lines), and
+the simulated data (the blue points).
+
 Run SMASH and TI thresholding
@@
 
-Apply smash and translation invariant (TI) thresholding to the
-"spikes" data. Here, we run the TI thresholding twice---once when
-the standard deviation (s.d.) function is provided, and once when it
-is estimated using the MAD algorithm.
+Now we apply SMASH, as well as the translation invariant (TI)
+thresholding method, to the "spikes" data. Here we run the TI
+thresholding method twice---once when the variance is assumes to be
+constant ("homoskedastic"), and once when it is estimated using the
+RMAD algorithm. The first method yields very poor estimates, so they
+are not shown in the plots below.
+
+The SMASH method is able to estimate the variance.
 
@@
 mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
+mu.ti.homo <- ti.thresh(x.sim,sigma = sig.est,family = "DaubLeAsymm",
+                        filter.number = 8)
 mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
-                      filter.number = 8)
-mu.ti.homo <- ti.thresh(x.sim,sigma = sig.est,family = "DaubLeAsymm",
                       filter.number = 8)
@@
 
-Get the wavelet coefficients and their variances.
+It should take at the very most a few minutes to run SMASH and TI
+thresholding.
+
+Get the (true) wavelet coefficients and their variances.
 
@@
 
-Plot the distribution of observed wavelet coefficients.
+Plot the distribution of the observed wavelet coefficients at a
+coarser scale (scale = 1, orange) and at a finer scale (scale = 7,
+dark blue).
 
-```{r}
-par(cex.axis = 0.8,cex.lab = 0.8)
+```{r plot-wc-histogram, fig.height=4, fig.width=6}
+par(cex.axis = 1,cex.lab = 1.5)
 hist(wc.sim[4,],breaks = 2,xlab = "observed wavelet coefficients",
@@
 
+Observe that the scale = 7 WCs are much more concentrated near zero
+because the signal is smoother at this finer scale.
+
 Plot the observed wavelet coefficients (at scales 1 and 7 only)
@@
 
-```{r}
-par(cex.axis = 0.8,cex.lab = 0.8)
+```{r wc-scatterplot, fig.height=5, fig.width=5}
+par(cex.axis = 1,cex.lab = 1.5)
 plot(c(),c(),xlab = "observed wavelet coefficients",
@@
 abline(0,1,lty = 1,col = "gray",lwd = 1)
-points(wc.sim[10,],wc.sim.shrunk[[9]]$PosteriorMean,pch = 20,cex = 0.6,
+points(wc.sim[10,],wc.sim.shrunk[[9]]$PosteriorMean,pch = 20,cex = 1,
        col = "darkorange")
-points(wc.sim[4,],wc.sim.shrunk[[3]]$PosteriorMean,pch = 20,cex = 0.6,
+points(wc.sim[4,],wc.sim.shrunk[[3]]$PosteriorMean,pch = 20,cex = 1,
        col = "darkblue")
@@
             aes(x = observed,y = shrunken,col = se)) +
-  geom_point() +
+  geom_point(na.rm = TRUE) +
   xlim(c(-1,1)) +
@@
 ```
+
+The scale = 7 WCs are strongly shrunk toward zero, whereas the scale =
+1 WCs are not shrunk nearly as much; SMASH infers from the data that
+the scale = 7 WCs are heavily concentrated around zero, and
+consequently SMASH shrinks them more strongly.
 

### 2018-08-23 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 ```{r plot-simulated-data, fig.height=5, fig.width=10}
-par(cex.axis = 1,cex.lab = 1.5)
+par(cex.axis = 1,cex.lab = 1.25)
 plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
@@
 
-Get shrunken estimates of the wavelet coefficients.
+Get the shrunken estimates of the wavelet coefficients.
 
@@
 ```{r plot-wc-histogram, fig.height=4, fig.width=6}
-par(cex.axis = 1,cex.lab = 1.5)
+par(cex.axis = 1,cex.lab = 1.25)
 hist(wc.sim[4,],breaks = 2,xlab = "observed wavelet coefficients",
@@
 ```{r wc-scatterplot, fig.height=5, fig.width=5}
-par(cex.axis = 1,cex.lab = 1.5)
+par(cex.axis = 1,cex.lab = 1.25)
 plot(c(),c(),xlab = "observed wavelet coefficients",
@@
 
+Observe that the scale = 7 WCs are strongly shrunk toward zero,
+whereas the scale = 1 WCs are not shrunk nearly as much; SMASH
+infers from the data that the scale = 7 WCs are heavily concentrated
+around zero, and consequently SMASH shrinks them more strongly.
+
 Plot the observed wavelet coefficients (at scale 7 only) vs. the
@@
 
-```{r}
+```{r wc-scatterplot-2, fig.height=3.75, fig.width=5}
 wc.sig.3 <- 1/wc.pres[[3]]
@@
 
-The scale = 7 WCs are strongly shrunk toward zero, whereas the scale =
-1 WCs are not shrunk nearly as much; SMASH infers from the data that
-the scale = 7 WCs are heavily concentrated around zero, and
-consequently SMASH shrinks them more strongly.
+From this plot, we see that SMASH shrinks WCs differently
+depending on their precision; specifically, WCs that are less
+precise---i.e., higher standard error (s.e.)---are shrunk more
+strongly toward zero.
 
-Plot the ground-truth signal (mean function) and the signals
-recovered by the TI thresholding and smash methods.
+Finally, we plot the ground-truth signal (the mean function, drawn as
+a black line) and the signals recovered by TI thresholding (light blue
+line) and SMASH (the red line). The TI thresholding estimate shows
+notable artifacts.
 
-```{r}
-par(cex.axis = 0.8)
+```{r plot-mean-signal-vs-estimates, fig.height=5, fig.width=10}
+par(cex.axis = 1)
 plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
      ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
-lines(mu.ti,col = "dodgerblue",lwd = 1.5)
-lines(mu.smash,col = "orangered",lwd = 1.5)
-cat("Demo is over.\n")
+lines(mu.ti,col = "dodgerblue",lwd = 2)
+lines(mu.smash,col = "orangered",lwd = 2)
 ```

### 2018-08-24 analysis/shiny/shiny.Rmd
Got Shiny app running.

--- 2018-07-03 dsc/graphs.Rmd
@@
 
-The following code generates an RShiny app which displays boxplots of MISEs from the full simulation study comparing SMASH to other wavelet-based methods for denoising Gaussian data.
-As mentioned in the companion paper, the results for a variety of test functions (both mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1 and 3, are presented here.
+NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`
 
-Scenarios denote a combination of mean function, SNR and variance function. Specifically, each scenario is named as [mean_function].[SNR].[variance_function], where the abbreviations are given by:
+The following code generates an RShiny app which displays boxplots of
+MISEs from the full simulation study comparing SMASH to other
+wavelet-based methods for denoising Gaussian data. As mentioned in the
+companion paper, the results for a variety of test functions (both
+mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1
+and 3, are presented here.
+
+Scenarios denote a combination of mean function, SNR and variance
+function. Specifically, each scenario is named as
+[mean_function].[SNR].[variance_function], where the abbreviations are
+given by:
+
 Mean function:  
@@
 
-On the other hand, we also ran a variety of methods in the simulation study. The methods are abbreviated as follows:  
+On the other hand, we also ran a variety of methods in the simulation
+study. The methods are abbreviated as follows:
+
 EbayesThresh - ebayesthresh  
@@
 
-In addition, EbayeThresh, BAMS, BlockJS, Neighblock, Sureshrink and Bayesian Posterior Mean all assume homoskedastic noise and use the Symm8 basis by default.
-TI thresholding was run with both the homoskedastic (tithresh.homo) using the Symm8 (.s8) basis, as well as an estimated variance using RMAD (tithresh.rmad) and SMASH (tithresh.smash), with both the Haar (.haar) and the Symm8 (.s8) bases.
-In addition, TI thresholding was also run with the true variance provided (tithresh.true) using both the Haar (.haar) and the Symm8 (.s8) bases.
+In addition, EbayeThresh, BAMS, BlockJS, Neighblock, Sureshrink and
+Bayesian Posterior Mean all assume homoskedastic noise and use the
+Symm8 basis by default. TI thresholding was run with both the
+homoskedastic (tithresh.homo) using the Symm8 (.s8) basis, as well as
+an estimated variance using RMAD (tithresh.rmad) and SMASH
+(tithresh.smash), with both the Haar (.haar) and the Symm8 (.s8)
+bases. In addition, TI thresholding was also run with the true
+variance provided (tithresh.true) using both the Haar (.haar) and the
+Symm8 (.s8) bases.
 
-We ran SMASH with the homoskedatic (smash.homo) assumption using both Haar (haar) and Symm8 (.s8).
-In addition, SMASH was also run with the variance jointly estimated, using either the JASH procedure (smash.jash) or the ASH procedure (smash.haar and smash.s8 for the two different bases).
-Paralleling TI thresholding, we also ran SMASH with the true variance provided (smash.true) using both the Haar (.haar) and the Symm8 (.s8) bases.
+We ran SMASH with the homoskedatic (smash.homo) assumption using both
+Haar (haar) and Symm8 (.s8). In addition, SMASH was also run with the
+variance jointly estimated, using either the JASH procedure
+(smash.jash) or the ASH procedure (smash.haar and smash.s8 for the two
+different bases). Paralleling TI thresholding, we also ran SMASH with
+the true variance provided (smash.true) using both the Haar (.haar)
+and the Symm8 (.s8) bases.
 
@@
 library(dplyr)
-load("res.RData")
+load("../../dsc/results/res.RData")
 scenario_names = as.character(unique(res$scenario))
 method_names = as.character(unique(res$method))
-#numeric_criteria = names(res)[unlist(lapply(res,is.numeric))]
 
 inputPanel(
+
     # Create the checkboxes and select them all by default
@@
 renderPlot({
-  res.filter = filter(res,scenario %in% input$scen.subset & method %in% input$method.subset)
+  res.filter = filter(res,scenario %in% input$scen.subset &
+    method %in% input$method.subset)
   print(input)
   res.filter$value = res.filter[[input$criteria]]
-  ggplot(res.filter, aes(method, value, color = method)) + geom_boxplot() + facet_grid(.~scenario) + 
+  ggplot(res.filter, aes(method, value, color = method)) +
+    geom_boxplot() + facet_grid(.~scenario) + 
     theme(axis.ticks = element_blank(), axis.text.x = element_blank())

### 2018-08-24 analysis/plot_gaus.R

@@ -77,8 +77,6 @@ p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
 print(p)
 invisible(readline(prompt = "Press [enter] to continue analysis... "))
 
-stop()
-
 t = (1:1024)/1024
 
 hetero.data.smash = res[res$.id == "sp.3.v5" & res$method == "smash.s8" , ]
@@ -125,12 +123,16 @@ abline(v = median(hetero.data.smash$mise), lty = 3, col = 3)
 abline(h = 4.5, lty = 3)
 abline(h = 6.5, lty = 3)
 
+stop()
+
 par(cex.axis = 1.5, cex.lab = 1.5, cex.sub = 1.5, mar = c(6.1, 3.1, 4.1, 2.1))
 plot(mu, type = 'l', ylim = c(0, 1), axes = FALSE, xlab = "", ylab = "")
 lines(mu + 2* sd.fn, col = 2, lty = 5)
 lines(mu - 2* sd.fn, col = 2, lty = 5)
 axis(1, labels = FALSE, tick = FALSE)
 axis(2)
+
+stop()
 
 hetero.data.smash.2 = res[res$.id == "cor.3.v3" & res$method == "smash.s8" , ]
 hetero.data.smash.homo.2 = res[res$.id == "cor.3.v3" &

### 2018-09-27 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")
A few minor revisions to the spikes demo.

@@
 
-Observe that the scale = 7 WCs are much more concentrated near zero
-because the signal is smoother at this finer scale.
+Observe that the scale = 7 WCs (dark blue) are much more concentrated
+near zero because the signal is smoother at this finer scale.
 
@@
 
-Observe that the scale = 7 WCs are strongly shrunk toward zero,
-whereas the scale = 1 WCs are not shrunk nearly as much; SMASH
-infers from the data that the scale = 7 WCs are heavily concentrated
-around zero, and consequently SMASH shrinks them more strongly.
+Observe that the scale = 7 WCs (dark blue) are strongly shrunk toward
+zero, whereas the scale = 1 WCs (orange) are not shrunk nearly as
+much; SMASH infers from the data that the scale = 7 WCs are heavily
+concentrated around zero, and consequently SMASH shrinks them more
+strongly.
 
 Plot the observed wavelet coefficients (at scale 7 only) vs. the
-"shrunken" wavelet coefficients estimated by adaptive shrinkage, and
-how how the amount of shrinkage depends on the standard error (s.e.)
-in the observations.
+"shrunken" wavelet coefficients estimated by adaptive shrinkage in
+order to see how the amount of shrinkage depends on the standard error
+(s.e.) in the observations.
 
@@
 
-From this plot, we see that SMASH shrinks WCs differently
+From this plot, it is evident that SMASH shrinks WCs differently
 depending on their precision; specifically, WCs that are less
@@
 a black line) and the signals recovered by TI thresholding (light blue
-line) and SMASH (the red line). The TI thresholding estimate shows
-notable artifacts.
+line) and SMASH (the red line).
 
@@
 par(cex.axis = 1)
-plot(mu.sp,type = "l",col = "black",lwd = 2,xlab = "position",ylab = "",
+plot(mu.sp,type = "l",col = "black",lwd = ,xlab = "position",ylab = "",
      ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
-lines(mu.ti,col = "dodgerblue",lwd = 2)
-lines(mu.smash,col = "orangered",lwd = 2)
+lines(mu.ti,col = "dodgerblue",lwd = 3)
+lines(mu.smash,col = "orangered",lwd = 3)
 ```
+
+In this example, the smoothed signal from SMASH is noticeably more
+accurate than using TI thresholding (in which the variance is
+estimated by running the median absolute deviation, or "RMAD",
+method). The TI thresholding estimate shows notable artifacts.

### 2018-09-27 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 par(cex.axis = 1)
-plot(mu.sp,type = "l",col = "black",lwd = ,xlab = "position",ylab = "",
+plot(mu.sp,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
      ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))

### 2018-09-28 analysis/spikesdemo.Rmd
Working on summarize.gaussian.sims.R revisions for manuscript.

@@
 means that are given by the "spikes" function, and with
-spatially-structured variances.
+spatially-structured variances given by the "clipped blocks" function.
 

### 2018-09-28 analysis/gaussian.mean.est.Rmd
workflowr::wflow_publish("gaussian.mean.est.Rmd")

---
title: "Gaussian mean estimation in simulated data sets"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

TO DO: Give overview of this report.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

## Set up environment

Load the ggplot2 and cowplot packages, and the functions definining
the mean and variances used to simulate the data.

```{r load-pkgs}
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

## Load results

Load the results of the simulation experiments.

```{r load-results}
load("../output/gaus-dscr.RData")
```

## Summarize results on data sets with constant variances

This plot reproduces Fig. 2 of the manuscript comparing the
accuracy of estimated mean curves in the data sets simulated from
the "Spikes" mean function with constant variance.

First extract the data used to generate this plot.

```{r plot-1-extract-data}
homo.data.smash <-
  res[res$.id    == "sp.3.v1" &
      res$method == "smash.s8",]
homo.data.smash.homo <-
  res[res$.id    == "sp.3.v1" &
      res$method == "smash.homo.s8",]
homo.data.tithresh <-
  res[res$.id == "sp.3.v1" &
      res$method == "tithresh.homo.s8",]
homo.data.ebayes <-
  res[res$.id    == "sp.3.v1" &
      res$method == "ebayesthresh",]
homo.data.smash.true <-
  res[res$.id == "sp.3.v1" &
  res$method  == "smash.true.s8",]
homo.data <-
  res[res$.id == "sp.3.v1" &
  (res$method == "smash.s8" |
   res$method == "ebayesthresh" |
   res$method == "tithresh.homo.s8"),]
```

Transform these data into a data frame suitable for ggplot2.

```{r plot-2-transform-data}
pdat <-
  rbind(data.frame(method      = "smash",
                   method.type = "est",
                   mise        = homo.data.smash$mise),
        data.frame(method      = "smash.homo",
                   method.type = "homo",
                   mise        = homo.data.smash.homo$mise),
        data.frame(method      = "tithresh",
                   method.type = "homo",
                   mise        = homo.data.tithresh$mise),
        data.frame(method      = "ebayesthresh",
                   method.type = "homo",
                   mise        = homo.data.ebayes$mise),
        data.frame(method      = "smash.true",
                   method.type = "true",
                   mise        = homo.data.smash.true$mise))
pdat <-
  transform(pdat,
            method = factor(method,
                            names(sort(tapply(pdat$mise,pdat$method,mean),
                                       decreasing = TRUE))))
```

Create the combined boxplot and violin plot using ggplot2.

```{r plot-1-create}
p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
print(p)
```

### 2018-09-28 analysis/summarize.gaussian.sims.R

@@ -1,248 +1,0 @@
-# TO DO: Explain here what this script does, and how to use it.
-#
-# TO DO: (Perhaps) change the name of this file.
-#
-# SET UP ENVIROMENT
-# -----------------
-# Load the ggplot2 and cowplot packages, and the functions definining
-# the mean and variances used to simulate the data.
-library(ggplot2)
-library(cowplot)
-source("../code/signals.R")
-
-# LOAD RESULTS
-# ------------
-# Load the results of the simulation experiments.
-cat("Loading simulation results.\n")
-load("../output/gaus-dscr.RData")
-
-# PLOT #1
-# -------
-# This reproduces the plot in Fig. 2 of the manuscript comparing the
-# accuracy of estimated mean curves in the data sets simulated from
-# the "spikes" mean function with constant variance.  function.
-cat("Generating the first plot.\n")
-
-# Extract the data used to generate the first plot.
-homo.data.smash <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "smash.s8",]
-homo.data.smash.homo <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "smash.homo.s8",]
-homo.data.tithresh <-
-  res[res$.id == "sp.3.v1" &
-      res$method == "tithresh.homo.s8",]
-homo.data.ebayes <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "ebayesthresh",]
-homo.data.smash.true <-
-  res[res$.id == "sp.3.v1" &
-  res$method  == "smash.true.s8",]
-homo.data <-
-  res[res$.id == "sp.3.v1" &
-  (res$method == "smash.s8" |
-   res$method == "ebayesthresh" |
-   res$method == "tithresh.homo.s8"),]
-
-# Transform these data into a data frame suitable for ggplot2.
-pdat <-
-  rbind(data.frame(method      = "smash",
-                   method.type = "est",
-                   mise        = homo.data.smash$mise),
-        data.frame(method      = "smash.homo",
-                   method.type = "homo",
-                   mise        = homo.data.smash.homo$mise),
-        data.frame(method      = "tithresh",
-                   method.type = "homo",
-                   mise        = homo.data.tithresh$mise),
-        data.frame(method      = "ebayesthresh",
-                   method.type = "homo",
-                   mise        = homo.data.ebayes$mise),
[…]

### 2018-09-28 analysis/gaussian.mean.est.Rmd
I have a complete first draft of the gaussian.mean.est.Rmd analysis.

@@
 
-TO DO: Give overview of this report.
+*TO DO: Give overview of this report.*
 
@@
 
-```{r load-pkgs}
+```{r load-pkgs, message=FALSE, warning=FALSE}
 library(ggplot2)
@@
 
-## Summarize results on data sets with constant variances
+## Simulated data with constant variances
 
@@
 
-First extract the data used to generate this plot.
+First, extract the results used to generate this plot.
 
@@
 
-Transform these data into a data frame suitable for ggplot2.
+Transform these results into a data frame suitable for ggplot2.
 
-```{r plot-2-transform-data}
+```{r plot-1-transform-data}
 pdat <-
@@
 
-```{r plot-1-create}
+```{r plot-1-create, fig.height=4, fig.width=5}
 p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
@@
 ```
+
+From this plot, we see that three versions of SMASH outperformed
+EbayesThresh and TI thresholding.
+
+Next, we compare the same methods in simulated data sets with
+heteroskedastic errors.
+
+## Simulated data with heteroskedastic errors: "Spikes" mean signal and "Clipped Blocks" variance
+
+In this scenario, data sets are simulated using the "Spikes" mean
+function and the "Clipped Blocks" variance function. This plot shows
+the mean function as a block line, and the +/- 2 standard deviations
+as orange lines:
+
+```{r spikes-signal, fig.height=4, fig.width=6}
+t         <- (1:1024)/1024
+mu        <- spikes.fn(t,"mean")
+sigma.ini <- sqrt(cblocks.fn(t,"var"))
+sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
+par(cex.axis = 1,cex.lab = 1.25)
+plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
+     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
+lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+```
+
+Extract the results from running these simulations.
+
+```{r plot-2-extract-data}
+hetero.data.smash <-
+  res[res$.id == "sp.3.v5" & res$method == "smash.s8",]
+hetero.data.smash.homo <-
+  res[res$.id == "sp.3.v5" & res$method == "smash.homo.s8",]
+hetero.data.tithresh.homo <-
+  res[res$.id == "sp.3.v5" & res$method == "tithresh.homo.s8",]
+hetero.data.tithresh.rmad <-
+  res[res$.id == "sp.3.v5" & res$method == "tithresh.rmad.s8",]
+hetero.data.tithresh.smash <-
+  res[res$.id == "sp.3.v5" & res$method == "tithresh.smash.s8",]
+hetero.data.tithresh.true <-
+  res[res$.id == "sp.3.v5" & res$method == "tithresh.true.s8",]
+hetero.data.ebayes <-
+  res[res$.id == "sp.3.v5" & res$method == "ebayesthresh",]
+hetero.data.smash.true <-
+  res[res$.id == "sp.3.v5" & res$method == "smash.true.s8",]
+```
+
+Transform these results into a data frame suitable for ggplot2.
+
+```{r plot-2-transform-data}
+pdat <-
+  rbind(data.frame(method      = "smash",
+                   method.type = "est",
+                   mise        = hetero.data.smash$mise),
+        data.frame(method      = "smash.homo",
+                   method.type = "homo",
+                   mise        = hetero.data.smash.homo$mise),
+        data.frame(method      = "tithresh.rmad",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.rmad$mise),
+        data.frame(method      = "tithresh.smash",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.smash$mise),
+        data.frame(method      = "tithresh.true",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.true$mise),
+        data.frame(method      = "ebayesthresh",
+                   method.type = "homo",
+                   mise        = hetero.data.ebayes$mise),
+        data.frame(method      = "smash.true",
+                   method.type = "true",
+                   mise        = hetero.data.smash.true$mise))
+pdat <-
+  transform(pdat,
+            method = factor(method,
+                            names(sort(tapply(pdat$mise,pdat$method,mean),
+                                       decreasing = TRUE))))
+```
+
+Create the combined boxplot and violin plot using ggplot2.
+
+```{r plot-2-create, fig.height=4, fig.width=5}
+p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
+     geom_violin(fill = "skyblue",color = "skyblue") +
+     geom_boxplot(width = 0.15,outlier.shape = NA) +
+     scale_fill_manual(values=c("darkorange","dodgerblue","limegreen","gold"),
+                       guide = FALSE) +
+     coord_flip() +
+     scale_y_continuous(breaks = seq(10,70,10)) +
+     labs(x = "",y = "MISE") +
+     theme(axis.line = element_blank(),
+           axis.ticks.y = element_blank())
+print(p)
+```
+
+In this scenario, we see that SMASH, allowing for heteroskedastic
+errors, outperforms EbayesThresh and all variants of TI thresholding
+(including TI thresholding with the true variance). Further, SMASH
+performs almost as well when estimating the variance compared to when
+provided with the true variance.
+
+## Simulated data with heteroskedastic errors: "Corner" mean signal and "Doppler" variance
+
+In this next scenario, data sets are simulated using the "Corner" mean
+function and the "Doppler" variance function. This plot shows the mean
+function as a block line, and the +/- 2 standard deviations as orange
+lines:
+
+```{r corner-signal, fig.height=4, fig.width=6}
+mu        <- cor.fn(t,"mean") 
+sigma.ini <- sqrt(doppler.fn(t,"var"))
+sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
+plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
+     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
+lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+```
+
+Extract the results from running these simulations.
+
+```{r plot-3-extract-data}
+hetero.data.smash.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "smash.s8",]
+hetero.data.smash.homo.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "smash.homo.s8",]
+hetero.data.tithresh.homo.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "tithresh.homo.s8",]
+hetero.data.tithresh.rmad.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "tithresh.rmad.s8",]
+hetero.data.tithresh.smash.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "tithresh.smash.s8",]
+hetero.data.tithresh.true.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "tithresh.true.s8",]
+hetero.data.ebayes.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "ebayesthresh",]
+hetero.data.smash.true.2 <-
+  res[res$.id == "cor.3.v3" & res$method == "smash.true.s8",]
+```
+
+Transform these results into a data frame suitable for ggplot2.
+
+```{r plot-3-transform-data}
+pdat <-
+  rbind(data.frame(method      = "smash",
+                   method.type = "est",
+                   mise        = hetero.data.smash.2$mise),
+        data.frame(method      = "smash.homo",
+                   method.type = "homo",
+                   mise        = hetero.data.smash.homo.2$mise),
+        data.frame(method      = "tithresh.rmad",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.rmad.2$mise),
+        data.frame(method      = "tithresh.smash",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.smash.2$mise),
+        data.frame(method      = "tithresh.true",
+                   method.type = "tithresh",
+                   mise        = hetero.data.tithresh.true.2$mise),
+        data.frame(method      = "ebayesthresh",
+                   method.type = "homo",
+                   mise        = hetero.data.ebayes.2$mise),
+        data.frame(method      = "smash.true",
+                   method.type = "true",
+                   mise        = hetero.data.smash.true.2$mise))
+pdat <-
+  transform(pdat,
+            method = factor(method,
+                            names(sort(tapply(pdat$mise,pdat$method,mean),
+                                       decreasing = TRUE))))
+```
+
+Create the combined boxplot and violin plot using ggplot2.
+
+```{r plot-3-create, fig.height=4, fig.width=5}
+p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
+     geom_violin(fill = "skyblue",color = "skyblue") +
+     geom_boxplot(width = 0.15,outlier.shape = NA) +
+     scale_fill_manual(values=c("darkorange","dodgerblue","limegreen","gold"),
+                       guide = FALSE) +
+     coord_flip() +
+     scale_y_continuous(breaks = seq(1,5)) +
+     labs(x = "",y = "MISE") +
+     theme(axis.line = element_blank(),
+           axis.ticks.y = element_blank())
+print(p)
+```
+
+Similar to the "spikes" data sets, we see that the SMASH method
+allowing for heteroskedastic variances outperforms the TI thresholding
+and EbayesThresh approaches.

### 2018-09-28 analysis/temp.R

@@ -1,164 +1,0 @@
-# PLOT #2
-# -------
-# TO DO: Explain here what is shown in the second plot.
-cat("Generating the second plot.\n")
-
-# Extract the data used to generate the second plot.
-hetero.data.smash <-
-  res[res$.id == "sp.3.v5" & res$method == "smash.s8",]
-hetero.data.smash.homo <-
-  res[res$.id == "sp.3.v5" & res$method == "smash.homo.s8",]
-hetero.data.tithresh.homo <-
-  res[res$.id == "sp.3.v5" & res$method == "tithresh.homo.s8",]
-hetero.data.tithresh.rmad <-
-  res[res$.id == "sp.3.v5" & res$method == "tithresh.rmad.s8",]
-hetero.data.tithresh.smash <-
-  res[res$.id == "sp.3.v5" & res$method == "tithresh.smash.s8",]
-hetero.data.tithresh.true <-
-  res[res$.id == "sp.3.v5" & res$method == "tithresh.true.s8",]
-hetero.data.ebayes <-
-  res[res$.id == "sp.3.v5" & res$method == "ebayesthresh",]
-hetero.data.smash.true <-
-  res[res$.id == "sp.3.v5" & res$method == "smash.true.s8",]
-
-# Transform these data into a data frame suitable for ggplot2.
-pdat <-
-  rbind(data.frame(method      = "smash",
-                   method.type = "est",
-                   mise        = hetero.data.smash$mise),
-        data.frame(method      = "smash.homo",
-                   method.type = "homo",
-                   mise        = hetero.data.smash.homo$mise),
-        data.frame(method      = "tithresh.rmad",
-                   method.type = "tithresh",
-                   mise        = hetero.data.tithresh.rmad$mise),
-        data.frame(method      = "tithresh.smash",
-                   method.type = "tithresh",
-                   mise        = hetero.data.tithresh.smash$mise),
-        data.frame(method      = "tithresh.true",
-                   method.type = "tithresh",
-                   mise        = hetero.data.tithresh.true$mise),
-        data.frame(method      = "ebayesthresh",
-                   method.type = "homo",
-                   mise        = hetero.data.ebayes$mise),
-        data.frame(method      = "smash.true",
-                   method.type = "true",
-                   mise        = hetero.data.smash.true$mise))
-pdat <-
[…]

### 2018-09-29 analysis/gaussian.mean.est.Rmd
wflow_publish("gaussian.mean.est.Rmd")

@@
 
-*TO DO: Give overview of this report.*
+In this analysis, we assess the ability of different signal denoising
+methods to recover the true signal after being provided with
+Gaussian-distributed observations of the signal. We consider scenarios
+in which the data have homoskedastic errors (constant variance) and
+heteroskedastic errors (non-constant variance).
+
+Since the simulation experiments are very computationally intensive,
+they are implemented separately (see the "dsc" directory in this git
+repository), and here we only create plots to summarize the results of
+these experiments.
 
@@
 
-In this scenario, data sets are simulated using the "Spikes" mean
-function and the "Clipped Blocks" variance function. This plot shows
-the mean function as a block line, and the +/- 2 standard deviations
-as orange lines:
+In this scenario, data sets were simulated using the "Spikes" mean
+function and the "Clipped Blocks" variance function. The next couple
+plots reproduce part of Fig. 3 in the manuscript.
+
+This plot shows the mean function as a block line, and the +/- 2
+standard deviations as orange lines:
 
@@
 
-Extract the results from running these simulations.
+Extract the results from running the simulations.
 
@@
 
-In this scenario, we see that SMASH, allowing for heteroskedastic
-errors, outperforms EbayesThresh and all variants of TI thresholding
-(including TI thresholding with the true variance). Further, SMASH
-performs almost as well when estimating the variance compared to when
-provided with the true variance.
+In the "Spikes" scenario, we see that SMASH, when allowing for
+heteroskedastic errors, outperforms EbayesThresh and all variants of
+TI thresholding (including TI thresholding with the true variance).
+Further, SMASH performs almost as well when estimating the variance
+compared to when provided with the true variance.
 
@@
 
-In this next scenario, data sets are simulated using the "Corner" mean
-function and the "Doppler" variance function. This plot shows the mean
-function as a block line, and the +/- 2 standard deviations as orange
-lines:
+In this next scenario, the data sets were simulated using the "Corner"
+mean function and the "Doppler" variance function. These plots were
+also used for Fig. 3 of the manuscript.
+
+This plot shows the mean function as a block line, and the +/- 2
+standard deviations as orange lines:
 
@@
 
-Similar to the "spikes" data sets, we see that the SMASH method
-allowing for heteroskedastic variances outperforms the TI thresholding
-and EbayesThresh approaches.
+Similar to the "Spikes" scenario, we see that the SMASH method, when
+allowing for heteroskedastic variances, outperforms both the TI
+thresholding and EbayesThresh approaches.

### 2018-10-09 analysis/motorcycle.Rmd
Working on motorcycle .Rmd example.

---
title: "Motorcycle Acceleration example"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

An illustration of "smoothing via adaptive shrinkage" applied to the
Motorcycle Accident data. This implements the illustration application
described in Sec. 5.1 of the manuscript.

Set up environment
------------------

Load the MASS, scales, wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle
Accident data. Some additional functions are defined in
`functions.motorcycle.R`.

```{r load-pkgs}
library(MASS)
library(lattice)
library(smashr)
library(scales)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Prepare data for SMASH
----------------------

Load the motorcycle data, and order the data points by time.

```{r load-data}
data(mcycle)
x.ini.mc <- sort(mcycle$times)
y.ini.mc <- mcycle$accel[order(mcycle$times)]
```

Run SMASH
---------

Apply smash to the Motorcycle Accident data set.

```{r run-smash}
res.mc <- smash.wrapper(x.ini.mc,y.ini.mc)
```

Summarize results of SMASH analysis
-----------------------------------

Create a plot showing the Motorcycle Accident data and the smash
estimates (with the dashed red lines showing the confidence
intervals).

```{r plot-smash-estimates}
plot(res.mc$x,res.mc$mu.est,type = "l",
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
     xlab = "time (ms)", ylab = "acceleration (g)",lwd = 2,
	 col = "darkorange")
lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
	 lwd = 2,col = "dodgerblue")
lines(res.mc$x,res.mc$mu.est - 2*sqrt(res.mc$var.est),
      lty = 5,lwd = 2,col = "dodgerblue")
points(res.mc$x,res.mc$y,pch = 1,cex = 1,col = "black")
```

# PREPARE DATA FOR SMASH WITH HOMOGENEOUS VARIANCES
# -------------------------------------------------
# Load the motorcycle data for Empirical Bayes thresholding.
cat("Preparing Motorcycle data for Empirical Bayes thresholding.\n")
x.ini.ti.cons.mc = sort(mcycle$times)
y.ini.ti.cons.mc = mcycle$accel[order(mcycle$times)]

# Load the motorcycle data once more for the second smash analysis.
cat("Preparing Motorcycle data for smash analysis (with equal variances).\n")
x.ini.cons.mc = sort(mcycle$times)
y.ini.cons.mc = mcycle$accel[order(mcycle$times)]

# Apply Empirical Bayes thresholding to the Motorcycle Accident data set.
cat("Running Empirical Bayes thresholding on Motorcycle Accident data set.\n")
res.ti.cons.mc = tithresh.cons.wrapper(x.ini.mc, y.ini.mc)

# Apply smash (with equal variances) to the Motorcycle Accident data set.
cat("Running smash (with equal variances) on Motorcycle Accident data set.\n")
res.cons.mc = smash.cons.wrapper(x.ini.mc, y.ini.mc)

# PREPARE DATA FOR EMPIRICAL BAYES WITH SMASH-ESTIMATED VARIANCES
# ---------------------------------------------------------------
# Load the motorcycle data for Empirical Bayes thresholding (with
# smash-estimated variances).
cat("Preparing data for EbayesThresh (with smash-estimated variances).\n")
x.ini.ti.mc = sort(mcycle$times)
y.ini.ti.mc = mcycle$accel[order(mcycle$times)]

# Apply Empirical Bayes thresholding to the Motorcycle Accident data,
# with variances estimated by smash.
cat(paste("Running EbayesThresh (with smash-estimated variances) on",
          "Motorcycle data.\n"))
res.ti.mc = tithresh.wrapper(x.ini.mc, y.ini.mc)

# SUMMARIZE RESULTS FROM ALL METHODS
# ----------------------------------
# Create another plot showing the Motorcycle Accident data and the
# estimates provided by the four methods.
par(cex.axis = 1.5, cex.sub = 1.8, cex.lab = 1.5,
    mar = c(5.1, 5.1, 2.1, 2.1), mgp = c(3, 1.3, 0))
plot(res.mc$x, res.mc$mu.est, type = 'l',
     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
     xlab = "time (ms)", ylab = "acceleration (g)", lwd = 2)
lines(res.mc$x, res.mc$mu.est + 2 * sqrt(res.mc$var.est), col = 2,
      lty = 5, lwd = 1.8)
lines(res.mc$x, res.mc$mu.est - 2 * sqrt(res.mc$var.est), col = 2,
      lty = 5, lwd = 1.8)
lines(res.ti.cons.mc$x, res.ti.cons.mc$mu.est, lwd = 2, col = 4)
lines(res.cons.mc$x, res.cons.mc$mu.est, lwd = 2, col = 'brown')
lines(res.ti.mc$x, res.ti.mc$mu.est, lwd = 2, col = 'darkgreen')
points(res.mc$x, res.mc$y, cex = 0.7, pch = 16, col = alpha("black", 0.5))
legend('bottomright',
       legend = c('SMASH', 'SMASH, homo', 'TI-thresh, SMASH est',
                  'TI-EBthresh, homo'),
       lty = c(1, 1, 1, 1), lwd = c(2, 2, 2, 2),
       col = c(1, 'brown', 'darkgreen', 4))

### 2018-10-09 analysis/spikesdemo.Rmd
Added back signal plot to summarize.gaussian.sims.R.
Working on motorcycle .Rmd example.

@@
 
-This script illustrates key features of the SMASH method on a small,
-simulated data set with heteroskedastic variances.
+This small demonstration illustrates key features of the SMASH method
+on a small, simulated data set with heteroskedastic variances. This
+code implements the example given in Sec. 4.1 of the paper.
 
@@
 
-This plot shows the "spikes" mean function (the black line),
-+/- 2 standard deviations (the yellow lines), and
-the simulated data (the blue points).
+This plot shows the "spikes" mean function (the black line), +/- 2
+standard deviations (the orange lines), and the simulated data (the
+blue points).
 

### 2018-10-09 analysis/motorcycle.Rmd
Some more improvements to the motorcycle example.

@@
 
-An illustration of "smoothing via adaptive shrinkage" applied to the
-Motorcycle Accident data. This implements the illustration application
-described in Sec. 5.1 of the manuscript.
+An illustration of "smoothing via adaptive shrinkage" (SMASH) applied to the
+Motorcycle Accident data. This implements the "illustrative application"
+presented in Sec. 5.1 of the manuscript.
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+```
 
@@
 
-```{r load-pkgs}
+```{r load-pkgs, message=FALSE}
 library(MASS)
@@
 
-Load the motorcycle data, and order the data points by time.
+Load the motorcycle data from the MASS package, and order the data
+points by time.
 
-```{r load-data}
+```{r prepare-data}
 data(mcycle)
@@
 
-Apply smash to the Motorcycle Accident data set.
+Apply SMASH to the Motorcycle Accident data set.
 
@@
 
-```{r plot-smash-estimates}
+```{r plot-smash-estimates, fig.height=5, fig.width=7}
 plot(res.mc$x,res.mc$mu.est,type = "l",
@@
      xlab = "time (ms)", ylab = "acceleration (g)",lwd = 2,
-	 col = "darkorange")
+	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
 lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
@@
 
-# PREPARE DATA FOR SMASH WITH HOMOGENEOUS VARIANCES
-# -------------------------------------------------
-# Load the motorcycle data for Empirical Bayes thresholding.
-cat("Preparing Motorcycle data for Empirical Bayes thresholding.\n")
-x.ini.ti.cons.mc = sort(mcycle$times)
-y.ini.ti.cons.mc = mcycle$accel[order(mcycle$times)]
+Apply SMASH again, this time assuming equal variances
+-----------------------------------------------------
 
-# Load the motorcycle data once more for the second smash analysis.
-cat("Preparing Motorcycle data for smash analysis (with equal variances).\n")
-x.ini.cons.mc = sort(mcycle$times)
-y.ini.cons.mc = mcycle$accel[order(mcycle$times)]
+Apply SMASH (assuming with equal variances) to the Motorcycle Accident
+data set.
 
-# Apply Empirical Bayes thresholding to the Motorcycle Accident data set.
-cat("Running Empirical Bayes thresholding on Motorcycle Accident data set.\n")
-res.ti.cons.mc = tithresh.cons.wrapper(x.ini.mc, y.ini.mc)
+```{r run-smash-homo}
+res.cons.mc <- smash.cons.wrapper(x.ini.mc,y.ini.mc)
+```
 
-# Apply smash (with equal variances) to the Motorcycle Accident data set.
-cat("Running smash (with equal variances) on Motorcycle Accident data set.\n")
-res.cons.mc = smash.cons.wrapper(x.ini.mc, y.ini.mc)
+Apply other methods to the Motorcycle Accident data
+---------------------------------------------------
 
-# PREPARE DATA FOR EMPIRICAL BAYES WITH SMASH-ESTIMATED VARIANCES
-# ---------------------------------------------------------------
-# Load the motorcycle data for Empirical Bayes thresholding (with
-# smash-estimated variances).
-cat("Preparing data for EbayesThresh (with smash-estimated variances).\n")
-x.ini.ti.mc = sort(mcycle$times)
-y.ini.ti.mc = mcycle$accel[order(mcycle$times)]
+Apply Empirical Bayes thresholding to the Motorcycle Accident data set.
 
-# Apply Empirical Bayes thresholding to the Motorcycle Accident data,
-# with variances estimated by smash.
-cat(paste("Running EbayesThresh (with smash-estimated variances) on",
-          "Motorcycle data.\n"))
-res.ti.mc = tithresh.wrapper(x.ini.mc, y.ini.mc)
+```{r run-tithresh}
+res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc, y.ini.mc)
+```
 
-# SUMMARIZE RESULTS FROM ALL METHODS
-# ----------------------------------
-# Create another plot showing the Motorcycle Accident data and the
-# estimates provided by the four methods.
-par(cex.axis = 1.5, cex.sub = 1.8, cex.lab = 1.5,
-    mar = c(5.1, 5.1, 2.1, 2.1), mgp = c(3, 1.3, 0))
+Apply Empirical Bayes thresholding to the Motorcycle Accident data,
+this time using the variances estimated by SMASH.
+
+```{r run-tithresh-with-smash-var}
+res.ti.mc <- tithresh.wrapper(x.ini.mc,y.ini.mc)
+```
+
+SUMMARIZE RESULTS FROM ALL METHODS
+----------------------------------
+
+Create another plot showing the Motorcycle Accident data and the
+estimates provided by the four methods.
+
+```{r}
 plot(res.mc$x, res.mc$mu.est, type = 'l',
@@
        col = c(1, 'brown', 'darkgreen', 4))
+```

### 2018-10-10 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 
-Apply other methods to the Motorcycle Accident data
+Apply TI thresholding to the Motorcycle Accident data
 ---------------------------------------------------
 
-Apply Empirical Bayes thresholding to the Motorcycle Accident data set.
+Apply TI thresholding to the Motorcycle Accident data set.
 
 ```{r run-tithresh}
-res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc, y.ini.mc)
+res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
 ```
 
-Apply Empirical Bayes thresholding to the Motorcycle Accident data,
-this time using the variances estimated by SMASH.
+Apply TI thresholding to the Motorcycle Accident data, this time using
+the variances estimated by SMASH.
 
@@
 
-SUMMARIZE RESULTS FROM ALL METHODS
-----------------------------------
+Compare results from all methods
+--------------------------------
 
-Create another plot showing the Motorcycle Accident data and the
-estimates provided by the four methods.
+In this second plot, we compare the mean estimate provided by SMASH
+(with heteroskedastic variances; orange line) against homoskedastic
+SMASH (dotted magenta line), TI thresholding (dark blue line), and TI
+thresholding when the variances have been estimated by SMASH (dotted
+green line).
 
-```{r}
-plot(res.mc$x, res.mc$mu.est, type = 'l',
+```{r plot-all-estimates, fig.height=5, fig.width=7}
+plot(res.mc$x,res.mc$mu.est,type = "l",
      ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
               max(res.mc$y + 2 * sqrt(res.mc$var.est))),
-     xlab = "time (ms)", ylab = "acceleration (g)", lwd = 2)
-lines(res.mc$x, res.mc$mu.est + 2 * sqrt(res.mc$var.est), col = 2,
-      lty = 5, lwd = 1.8)
-lines(res.mc$x, res.mc$mu.est - 2 * sqrt(res.mc$var.est), col = 2,
-      lty = 5, lwd = 1.8)
-lines(res.ti.cons.mc$x, res.ti.cons.mc$mu.est, lwd = 2, col = 4)
-lines(res.cons.mc$x, res.cons.mc$mu.est, lwd = 2, col = 'brown')
-lines(res.ti.mc$x, res.ti.mc$mu.est, lwd = 2, col = 'darkgreen')
-points(res.mc$x, res.mc$y, cex = 0.7, pch = 16, col = alpha("black", 0.5))
-legend('bottomright',
-       legend = c('SMASH', 'SMASH, homo', 'TI-thresh, SMASH est',
-                  'TI-EBthresh, homo'),
-       lty = c(1, 1, 1, 1), lwd = c(2, 2, 2, 2),
-       col = c(1, 'brown', 'darkgreen', 4))
+	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
+	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
+lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
+lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
+      col = "darkblue")
+lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
+points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
 ```

### 2018-10-18 analysis/chipseq.Rmd
Working on chipseq R Markdown file.

---
title: "ChIP-seq example"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

An illustration of "smoothing via adaptive shrinkage" (SMASH) applied
to chromatin immunoprecipitation sequencing ("ChIP-seq") data. This
implements the SMASH analysis presented in Sec. 5.2 of the manuscript.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

Set up environment
------------------

We begin by loading the smashr, ggplot2 and cowplot packages, as well
as some additional functions used to implement the analysis below.

```{r load-pkgs, warning=FALSE}
source("../code/chipseq.functions.R")
library(smashr)
library(ggplot2)
library(cowplot)
```

Load the ChIP-seq data
----------------------

The ChIP-seq data are sequencing read counts for transcription
factor YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp
on chromosome 1. These data were collected as part of the ENCODE
("Encyclopedia Of DNA Elements") project.

```{r load-data}
load("../data/reg_880000_1011072.RData")
bppos  <- 880001:1011072
counts <- M[1,] + M[,2]
```

Note that there are two replicates of the GM12878 cell line, so we
analyze the combined read counts from both replicates, stored in the
`counts` vectors.

Run SMASH
---------

Next, we apply SMASH to the read counts to estimate the mean and
variance of the underlying signal. It may take several minutes to
complete this step.

```{r run-smash}
res <- smash.poiss(counts,post.var = TRUE)
```

Plot the SMASH estimates
------------------------

To provide a "baseline" to compare against the SMASH estimates, we
retrieve the peaks identified in the same ChIP-seq data using the MACS
software.

```{r load-macs-peaks}
macs.file <- "../data/Gm1287peaks_chr1_sorted.txt"
peaks <- read.macs.peaks(macs.file,min(bppos),max(bppos))
```

TO DO: Describe what is being shown in the plot.

```{r plot-smash-estimates}
nbreaks <- 80
p <- create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start+peaks$end)/2e6,
                         nbreaks) +
  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
```

### 2018-10-18 analysis/chipseq.R

@@ -1,71 +1,0 @@
-# An illustration of "smoothing via adaptive shrinkage" applied to
-# chromatin immunoprecipitation sequencing ("ChIP-seq") data. Compare
-# the plot generated by the code below against the figure in the
-# "ChIP-seq data" section of the paper.
-#
-# The ChIP-seq data are sequencing read counts for transcription
-# factor YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp
-# on chromosome 1. These data were collected as part of the ENCODE
-# ("Encyclopedia Of DNA Elements") project.
-#
-library(smashr)
-library(scales)
-library(ggplot2)
-library(cowplot)
-
-# LOAD DATA
-# ---------
-# Load the ChIP-seq data.
-cat("Loading Chip-seq data.\n")
-load("../data/reg_880000_1011072.RData")
-
-# PREPARE DATA
-# ------------
-# Prepare the data for analysis with smash.
-bppos <- 880001:1011072
-
-# RUN SMASH
-# ---------
-# Apply smash to the Motorcycle Accident data set.
-cat("Running smash on ChIP-seq data.\n")
-counts <- M[1,] + M[,2]
-res <- smash.poiss(counts,post.var = TRUE)
-
-# PLOT RESULTS
-# ------------
-# The first plot shows counts (summed across two replicate
-# experiments), with darker areas corresponding to higher numbers of
-# data points.
-plot(bppos,counts,xlab="position",ylab="counts",pch=16,cex=0.5,
-     col=alpha("black",0.04))
-
-breaks <- seq(880000,1011073,length.out = 80)
-x      <- cut(bppos,breaks)
-n      <- table(x,factor(counts))
-ggplot(data.frame(position = rep(breaks[-80],times = 8),
-                  count    = rep(0:7,each = 79),
-                  n        = as.vector(n),
-                  is.zero  = as.vector(n) == 0),
-       aes(x = position,y = count,size = sqrt(n),color = is.zero)) +
-  geom_point(shape = 1) +
-  scale_color_manual(values = c("black","white")) +
-  scale_size_area(max_size = 2.5)
-
-invisible(readline(prompt = "Press [enter] to view next plot... "))
-
-
-
-peaks       <- read.table("../data/Gm1287peaks_chr1_sorted.txt")
-peaks       <- peaks[order(peaks[,2]),]
-all.base    <- 1:peaks[dim(peaks)[1],3]
[…]

### 2018-10-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

@@
 
-```{r plot-smash-estimates}
-nbreaks <- 80
-p <- create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start+peaks$end)/2e6,
-                         nbreaks) +
+```{r plot-smash-estimates, fig.height=4, fig.width=8}
+create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
+                    nbreaks = 10) +
   scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +

### 2018-10-18 analysis/index.Rmd
wflow_publish("index.Rmd")

---
title: "SMASH companion code resources"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: false
---

## Contents

+ [Illustration of SMASH on "spikes" data set.](spikesdemo.html)

+ [Comparison of signal denoising methods in Gaussian-distributed data
  sets.](gaussian.mean.est.html)

+ [Application of SMASH to motorcycle acceleration data.](motorcycle.html)

+ [Application of SMASH to ChIP-seq data.](chipseq.html)

### 2018-10-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

--- 2018-10-18 analysis/chipseq.Rmd
@@
 
-```{r plot-smash-estimates}
-nbreaks <- 80
-p <- create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start+peaks$end)/2e6,
-                         nbreaks) +
+```{r plot-smash-estimates, fig.height=4, fig.width=8}
+create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
+                    nbreaks = 80) +
   scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +

### 2018-10-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

--- 2018-10-18 analysis/chipseq.Rmd
@@
 
-```{r plot-smash-estimates}
-nbreaks <- 80
-p <- create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start+peaks$end)/2e6,
-                         nbreaks) +
+```{r plot-smash-estimates, fig.height=3, fig.width=9}
+create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
+                    nbreaks = 80) +
   scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +

### 2018-10-19 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

@@
 
-```{r load-pkgs, warning=FALSE}
+```{r load-pkgs, warning=FALSE, message=FALSE}
 source("../code/chipseq.functions.R")
@@
 
-TO DO: Describe what is being shown in the plot.
+This next plot shows the intensity function estimated by SMASH (orange
+line). The read count data are depicted as light blue circles, in
+which the area of each circle is scaled by the number of data points
+that fall within each 1.6-kb "bin". (We show counts summarized within
+bins because there are too many data points to plot them
+individually.)
+
+The peaks identified by the MACS software are shown as red
+triangles. (Specifically, these are the *mean positions* of the
+identified peak intervals; the peak intervals are short enough that it
+is not useful to show both the start and end positions of these
+intervals.)
 
@@
 ```
+
+Based on this plot, it is clear that the the strongest SMASH intensity
+estimates align very closely with the peaks found by MACS.
+
+Intriguingly, the SMASH estimates also suggest the presence of several
+additional weaker peaks that were not identified by MACS.

### 2018-11-06 analysis/index.Rmd
Greatly simplified the README.

@@
 ---
-title: "SMASH companion code resources"
+title: "SMASH companion source code repository"
 site: workflowr::wflow_site
@@
 ---
+
+This repository contains source code and data accompanying our manuscript:
+
+> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
+Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
+signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).
+
+reproduce some of the
+empirical results presented in [Xing & Stephens (2016)][smashr-preprint].
+The new methods can be found in the [smashr package][smashr].
+
+If you find a bug, please post an [issue][issues].
+
+## Citing this work
+
+If you find any of the source code in this repository useful for your
+work, please cite our paper:
+
+> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
+Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
+signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).
+
+## License
+
+Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto * Matthew
+Stephens.
+
+All source code and software in this repository are made available
+under the terms of the
+[MIT license](https://opensource.org/licenses/mit-license.html). See
+the [LICENSE](LICENSE) file for the full text of the license.
+
+## Credits
+
+This project was developed by [Zhengrong Xing][zhengrong] at the
+University of Chicago, with support and contributions from
+[Peter Carbonetto][peter] and [Matthew Stephens][matthew].
+
+[smashr]: https://github.com/stephenslab/smashr
+[smashr-preprint]: http://arxiv.org/abs/1605.07787
+[dscr-smash]: https://github.com/stephenslab/dscr-smash
+[issues]: https://github.com/stephenslab/smash-paper/issues
+[zhengrong]: https://github.com/zrxing
+[peter]: http://pcarbo.github.io
+[matthew]: http://stephenslab.uchicago.edu
 

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

--- 2018-10-18 analysis/index.Rmd
@@
 
+This repository contains source code and data accompanying our manuscript,
+
+> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
+Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
+signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).
+
+The new methods can be found in the [smashr package][smashr].
+
 ## Contents
 
-+ [Illustration of SMASH on "spikes" data set.](spikesdemo.html)
+The following analyses generate some of the empirical results
+presented in [Xing & Stephens (2016)][smashr-preprint]. If you
+encounter a problem running any of the R code in these examples,
+please post an [issue][issues].
+
++ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
 
@@
 + [Application of SMASH to ChIP-seq data.](chipseq.html)
+
+## Citing this work
+
+If you find any of the source code in this repository useful for your
+work, please cite our paper:
+
+> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
+> Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
+> signals.* [arXiv:1709.10066][smash-preprint].
+
+## License
+
+Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
+Stephens.
+
+All source code and software in this repository are made available
+under the terms of the [MIT license][mit-license]. See the
+[LICENSE](LICENSE) file for the full text of the license.
+
+## Credits
+
+This project was developed by [Zhengrong Xing][zhengrong] at the
+University of Chicago, with support and contributions from
+[Peter Carbonetto][peter] and [Matthew Stephens][matthew].
+
+[smashr]: https://github.com/stephenslab/smashr
+[smash-preprint]: http://arxiv.org/abs/1605.07787
+[issues]: https://github.com/stephenslab/smash-paper/issues
+[mit-license]: https://opensource.org/licenses/mit-license.html
+[zhengrong]: https://github.com/zrxing
+[peter]: http://pcarbo.github.io
+[matthew]: http://stephenslab.uchicago.edu

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

@@
 The new methods can be found in the [smashr package][smashr].
-
-## Contents
-
-The following analyses generate some of the empirical results
-presented in [Xing & Stephens (2016)][smashr-preprint]. If you
-encounter a problem running any of the R code in these examples,
-please post an [issue][issues].
-
-+ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
-
-+ [Comparison of signal denoising methods in Gaussian-distributed data
-  sets.](gaussian.mean.est.html)
-
-+ [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
-
-+ [Application of SMASH to ChIP-seq data.](chipseq.html)
 
@@
 
+## Contents
+
+The following analyses generate some of the empirical results
+presented in [Xing & Stephens (2016)][smashr-preprint]. If you
+encounter a problem running any of the R code in these examples,
+please post an [issue][issues].
+
++ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
+
++ [Comparison of signal denoising methods in Gaussian-distributed data
+  sets.](gaussian.mean.est.html)
+
++ [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
+
++ [Application of SMASH to ChIP-seq data.](chipseq.html)
+
+## What's included in the git repository
+
+See here for the source repository. This is what you will find in the
+repository:
+
+*Fill out this section.*
+
 ## Credits
@@
 
+[smash-github]: https://github.com/stephenslab/smash-paper
 [smashr]: https://github.com/stephenslab/smashr

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

@@
 
-This repository contains source code and data accompanying our manuscript,
+This repository contains data and R source code accompanying our
+manuscript,
 
@@
 Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
-signals.* [arXiv:1709.10066](http://arxiv.org/abs/1605.07787).
+signals.* [arXiv:1709.10066][smash-preprint].
+
+If you find any of the source code in this repository useful for your
+work, please cite our paper.
 
 The new methods can be found in the [smashr package][smashr].
-
-## Citing this work
-
-If you find any of the source code in this repository useful for your
-work, please cite our paper:
-
-> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
-> Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
-> signals.* [arXiv:1709.10066][smash-preprint].
 
@@
 The following analyses generate some of the empirical results
-presented in [Xing & Stephens (2016)][smashr-preprint]. If you
+presented in [Xing & Stephens (2016)][smash-preprint]. If you
 encounter a problem running any of the R code in these examples,

### 2018-11-06 analysis/spikesdemo.Rmd
Working on improvements to the Spikes demo; mainly in the setup instructions.

@@
 This small demonstration illustrates key features of the SMASH method
-on a small, simulated data set with heteroskedastic variances. This
-code implements the example given in Sec. 4.1 of the paper.
+on a small, simulated data set with spatially structured variances. This
+code implements the example presented in Sec. 4.1 of the paper.
 
@@
 
-Set up environment
-------------------
+Initial setup instructions
+--------------------------
+
+To run this example on your own computer, please follow these setup
+instructions. These instructions assume you already have R and/or
+RStudio installed on your computer.
+
+Download or clone the [git repository][smash-github] on your computer.
+
+Launch R, and change the working directory to be the `analysis` folder
+inside your local copy of the `smash-paper` git repository.
+
+Install some of the packages used here, and in the code below:
+
+```{r install-pkgs-1, eval=FALSE}
+install.packages(c("devtools","ggplot2","cowplot"))
+```
+
+Finally, install the ashr and smashr packages from GitHub:
+
+```{r install-pkgs-2, eval=FALSE}
+library(devtools)
+install_github("stephens999/ashr",upgrade_dependencies = FALSE,
+               build_vignettes = TRUE)
+install_github("stephenslab/smashr",upgrade_dependencies = FALSE,
+               build_vignettes = TRUE)
+```
+
+Set up R environment
+--------------------
 
@@
 
-```{r load-pkgs, warning=FALSE}
+```{r load-pkgs, warning=FALSE, message=FALSE}
 library(ashr)
@@
 library(ggplot2)
-suppressMessages(library(cowplot))
+library(cowplot)
 source("../code/misc.R")
@@
 method). The TI thresholding estimate shows notable artifacts.
+
+[smash-github]: https://github.com/stephenslab/smash-paper

### 2018-11-06 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 library(devtools)
-install_github("stephens999/ashr",upgrade_dependencies = FALSE,
-               build_vignettes = TRUE)
-install_github("stephenslab/smashr",upgrade_dependencies = FALSE,
-               build_vignettes = TRUE)
+install_github("stephens999/ashr",upgrade_dependencies = FALSE)
+install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
 ```
+
+See the "Session Info" at the bottom of this example for the versions
+of the software and R packages that were used to generate the results
+shown below.
 
@@
 
-We begin by loading the ashr, smashr, scales, ggplot2 and cowplot
-packages, as well as some additional functions used in the code below.
+We begin by loading the ashr, smashr, ggplot2 and cowplot packages, as
+well as some additional functions used in the code below.
 
@@
 library(smashr)
-library(scales)
 library(ggplot2)
@@
 Simulate the noisy observations from the normal distribution with
-means that are given by the "spikes" function, and with
-spatially-structured variances given by the "clipped blocks" function.
+means that are given by the "Spikes" function, and with
+spatially structured variances given by the "Clipped Blocks" function.
 
@@
 plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
-     ylab = "",lwd = 1.7,xaxp = c(0,1024,4),yaxp = c(0,1,4))
+     ylab = "",lwd = 2,xaxp = c(0,1024,4),yaxp = c(0,1,4))
 lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
 lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
-points(x.sim,cex = 0.7,pch = 16,col = "darkblue")
+points(x.sim,cex = 0.7,pch = 16,col = "dodgerblue")
 ```
@@
 standard deviations (the orange lines), and the simulated data (the
-blue points).
+light blue points).
 

### 2018-11-06 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
-     ylab = "",lwd = 2,xaxp = c(0,1024,4),yaxp = c(0,1,4))
+     ylab = "",lwd = 3,xaxp = c(0,1024,4),yaxp = c(0,1,4))
 lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)

### 2018-11-06 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

@@
 
-Launch R, and change the working directory to be the `analysis` folder
-inside your local copy of the `smash-paper` git repository.
+Launch R, and change the working directory to be the "analysis" folder
+inside your local copy of the git repository.
 
-Install some of the packages used here, and in the code below:
+Install some of the packages used here and in the code below:
 
@@
 
-See the "Session Info" at the bottom of this example for the versions
-of the software and R packages that were used to generate the results
-shown below.
+See the "Session Info" at the bottom for the versions of the software
+and R packages that were used to generate the results shown below.
 

### 2018-11-06 analysis/motorcycle.Rmd

@@
 
-An illustration of "smoothing via adaptive shrinkage" (SMASH) applied to the
-Motorcycle Accident data. This implements the "illustrative application"
-presented in Sec. 5.1 of the manuscript.
+This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
+applied to the Motorcycle Accident data. This implements the
+"illustrative application" presented in Sec. 5.1 of the manuscript.
 
@@
 
-Set up environment
-------------------
+Initial setup instructions
+--------------------------
 
-Load the MASS, scales, wavethresh, EbayesThresh and smashr
-packages. The MASS package is loaded only for the Motorcycle
-Accident data. Some additional functions are defined in
-`functions.motorcycle.R`.
+To run this example on your own computer, please follow these setup
+instructions. These instructions assume you already have R and/or
+RStudio installed on your computer.
+
+Download or clone the [git repository][smash-github] on your computer.
+
+Launch R, and change the working directory to be the "analysis" folder
+inside your local copy of the git repository.
+
+Install the devtools, wavethresh and EbayesThresh packages used here
+and in the code below:
+
+```{r install-pkgs-1, eval=FALSE}
+install.packages(c("devtools","wavethresh","EbayesThresh"))
+```
+
+Finally, install the ashr and smashr packages from GitHub:
+
+```{r install-pkgs-2, eval=FALSE}
+library(devtools)
+install_github("stephens999/ashr",upgrade_dependencies = FALSE)
+install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
+```
+
+See the "Session Info" at the bottom for the versions of the software
+and R packages that were used to generate the results shown below.
+
+Set up R environment
+--------------------
+
+Load the MASS, wavethresh, EbayesThresh and smashr packages. The MASS
+package is loaded only for the Motorcycle Accident data. Some
+additional functions are defined in `functions.motorcycle.R`.
 
@@
 library(smashr)
-library(scales)
 library(wavethresh)
@@
 ```
+
+Note that the MASS and lattice packages are included in most standard
+R installations.
 
@@
 
-Apply SMASH (assuming with equal variances) to the Motorcycle Accident
-data set.
+Apply SMASH (assuming equal variances) to the Motorcycle Accident data
+set.
 
@@
 Apply TI thresholding to the Motorcycle Accident data
----------------------------------------------------
+-----------------------------------------------------
 

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 library(MASS)
+library(scales)
 library(lattice)
@@
 Note that the MASS and lattice packages are included in most standard
-R installations.
+R installations, so you probably don't need to install these packages
+separately.
 

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

--- 2018-11-06 analysis/motorcycle.Rmd
@@
 
-Load the MASS, wavethresh, EbayesThresh and smashr packages. The MASS
-package is loaded only for the Motorcycle Accident data. Some
-additional functions are defined in `functions.motorcycle.R`.
+Load the MASS, lattice wavethresh, EbayesThresh and smashr
+packages. The MASS package is loaded only for the Motorcycle Accident
+data. Some additional functions are defined in
+`functions.motorcycle.R`.
 
@@
 (with heteroskedastic variances; orange line) against homoskedastic
-SMASH (dotted magenta line), TI thresholding (dark blue line), and TI
-thresholding when the variances have been estimated by SMASH (dotted
-green line).
+SMASH (dotted magenta line).
 
-```{r plot-all-estimates, fig.height=5, fig.width=7}
+```{r plot-homo-smash-estimates, fig.height=5, fig.width=7}
 plot(res.mc$x,res.mc$mu.est,type = "l",
@@
 lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
+#  lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
+#        col = "darkblue")
+#  lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
+points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
+```
+
+And in this next plot, we compare the SMASH estimates (orange line)
+against the the mean estimates obtained by TI thresholding (dark blue
+line), and TI thresholding when the variances have been estimated by
+SMASH (dotted green line).
+
+```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
+plot(res.mc$x,res.mc$mu.est,type = "l",
+     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
+              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
+	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
+	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
 lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
@@
 ```
+
+*Add text here.*
+
+[smash-github]: https://github.com/stephenslab/smash-paper

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 (with heteroskedastic variances; orange line) against homoskedastic
-SMASH (dotted magenta line).
+SMASH (dotted, light blue line).
 
@@
 	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
-lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",col = "magenta")
-#  lines(res.ti.cons.mc$x,res.ti.cons.mc$mu.est,lwd = 2,lty = "solid",
-#        col = "darkblue")
-#  lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
+lines(res.cons.mc$x,res.cons.mc$mu.est,lwd = 2,lty = "dotted",
+      col = "dodgerblue")
 points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
@@
 
-*Add text here.*
+The TI thresholding estimate and the SMASH estimate with homoskedastic
+variances both show notable artifacts. When the TI thresholding method
+is provided with the SMASH variance estimates, the mean signal is much
+more smooth.
 

### 2018-11-06 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 
-And in this next plot, we compare the SMASH estimates (orange line)
-against the the mean estimates obtained by TI thresholding (dark blue
-line), and TI thresholding when the variances have been estimated by
-SMASH (dotted green line).
+And in this next plot, we compare the SMASH estimates (the orange
+line) against the the mean estimates obtained by TI thresholding (dark
+blue line), and TI thresholding when the variances have been estimated
+by SMASH (dotted green line).
 
@@
 variances both show notable artifacts. When the TI thresholding method
-is provided with the SMASH variance estimates, the mean signal is much
-more smooth.
+is provided with the SMASH variance estimate, the mean signal is
+substantially smoother.
 

### 2018-11-06 analysis/index.Rmd
wflow_publish("index.Rmd")

@@
 
-+ [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
+1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
 
-+ [Comparison of signal denoising methods in Gaussian-distributed data
+2. [Comparison of signal denoising methods in Gaussian-distributed data
    sets.](gaussian.mean.est.html)
 
-+ [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
+3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
 
-+ [Application of SMASH to ChIP-seq data.](chipseq.html)
+4. [Application of SMASH to ChIP-seq data.](chipseq.html)
 

### 2018-11-07 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")
Revised setup instructions for a couple .Rmd files.

@@
 
-An illustration of "smoothing via adaptive shrinkage" (SMASH) applied
-to chromatin immunoprecipitation sequencing ("ChIP-seq") data. This
-implements the SMASH analysis presented in Sec. 5.2 of the manuscript.
+This is an illustration of "SMoothing by Adaptive SHrinkage" (SMASH)
+applied to chromatin immunoprecipitation sequencing ("ChIP-seq")
+data. This implements the SMASH analysis presented in Sec. 5.2 of the
+manuscript.
 
@@
 knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+```
+
+Initial setup instructions
+--------------------------
+
+To run this example on your own computer, please follow these setup
+instructions. These instructions assume you already have R (optionally,
+RStudio) installed on your computer.
+
+Download or clone the [git repository][smash-github] on your computer.
+
+Launch R, and change the working directory to be the "analysis" folder
+inside your local copy of the git repository.
+
+Install the devtools, ggplot2 and cowplot packages used here and in
+the code below:
+
+```{r install-pkgs-1, eval=FALSE}
+install.packages(c("devtools","ggplot2","cowplot"))
 ```

### 2018-11-07 analysis/motorcycle.Rmd
Revised setup instructions for a couple .Rmd files.

@@
 
-Finally, install the ashr and smashr packages from GitHub:
+Finally, install the smashr package from GitHub:
 
 ```{r install-pkgs-2, eval=FALSE}
-library(devtools)
-install_github("stephens999/ashr",upgrade_dependencies = FALSE)
-install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
+devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
 ```

### 2018-11-07 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

@@
 
-Set up environment
-------------------
+Finally, install the smashr package from GitHub:
 
-We begin by loading the smashr, ggplot2 and cowplot packages, as well
-as some additional functions used to implement the analysis below.
+```{r install-pkgs-2, eval=FALSE}
+devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
+```
+
+See the "Session Info" at the bottom for the versions of the software
+and R packages that were used to generate the results shown below.
+
+Set up R environment
+--------------------
+
+Loading the smashr, ggplot2 and cowplot packages, as well as some
+additional functions used to implement the analysis below.
 
@@
 
-The ChIP-seq data are sequencing read counts for transcription
-factor YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp
-on chromosome 1. These data were collected as part of the ENCODE
-("Encyclopedia Of DNA Elements") project.
+The ChIP-seq data are sequencing read counts for transcription factor
+YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp on
+chromosome 1. These data were collected as part of the ENCODE
+("Encyclopedia Of DNA Elements") project. The data are included with
+the [git repository][smash-github].
 
@@
 additional weaker peaks that were not identified by MACS.
+
+[smash-github]: https://github.com/stephenslab/smash-paper

### 2018-11-08 analysis/index.Rmd
Moved around some of the files, and revising the home page.

@@
 
-1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
++ [**Illustration:** SMASH applied to the "spikes"
+data set.](spikesdemo.html)
 
-2. [Comparison of signal denoising methods in Gaussian-distributed data
-   sets.](gaussian.mean.est.html)
++ **Comparisons of signal denoising methods in simulated data:**
 
-3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
+   - [Estimating the mean signal from Gaussian-distributed
+      data.](gausshomo.html)
+   - Estimating the variance function from Gaussian-distributed data.
+   - Poisson-distributed data.
 
-4. [Application of SMASH to ChIP-seq data.](chipseq.html)
++ **Illustrative applications:**
+
+   - [Motorcycle acceleration data.](motorcycle.html)
+   - [ChIP-seq data.](chipseq.html)
 

### 2018-11-08 analysis/shiny.Rmd
Moved around some of the files, and revising the home page.

--- 2018-08-24 analysis/shiny/shiny.Rmd
@@
 library(dplyr)
-load("../../dsc/results/res.RData")
+load("../output/gaus-dscr.RData")
 scenario_names = as.character(unique(res$scenario))

### 2018-11-08 analysis/index.Rmd
wflow_publish("index.Rmd")

--- 2018-11-06 analysis/index.Rmd
@@
 
-1. [Illustration of SMASH applied to the "spikes" data set.](spikesdemo.html)
+[**Illustration:** SMASH applied to the "spikes" data set.](spikesdemo.html)
 
-2. [Comparison of signal denoising methods in Gaussian-distributed data
-   sets.](gaussian.mean.est.html)
+### Comparisons of signal denoising methods in simulated data
 
-3. [Application of SMASH to motorcycle acceleration data.](motorcycle.html)
+1. [Estimating the mean function from Gaussian-distributed
+data.](gausshomo.html)
 
-4. [Application of SMASH to ChIP-seq data.](chipseq.html)
+2. Estimating the variance function from Gaussian-distributed data.
+
+3. Poisson-distributed data.
+
+### Illustrative applications
+
+1. [Motorcycle acceleration data.](motorcycle.html)
+
+2. [ChIP-seq data.](chipseq.html)
 

### 2018-11-08 analysis/gaussvarest.Rmd
Moved around some files and revised TOC in home page.

# ---
# title: "Gaussian variance estimation in simulated data sets"
# ---
#
# This script implements the "Gaussian variance estimation" simulation
# experiments in the paper. In particular, we compare the Mean Field
# Variational Bayes method (MFVB) against SMASH in two scenarios. See
# the paper for the full description of these scenarios.
#
# The figure and table generated at the end of this script should
# match up with the figure and table shown in the paper.
#
# Note that this script could take an hour or several hours to
# complete as it runs the two methods on 100 simulated data sets for
# each of the two scenarios.
#
# We thank Menictas & Wand for generously sharing code that was used
# to implement these experiments.
#

# -----
# TO DO: Remove steps that are not included in the paper.
# -----

# SET UP ENVIRONMENT
# ------------------
# Load the smashr package, and some functions used in the analysis.
library(smashr)
source("../code/mfvb.functions.R")

# SCRIPT PARAMETERS
# -----------------
# Number of data sets simulated in the first (nsim1) and second
# (nsim2) simulation scenarios.
nsim1 <- 100
nsim2 <- 100

# Set hyperparameters.
Au.hyp      <- 1e5
Av.hyp      <- 1e5
sigsq.gamma <- 1e10
sigsq.beta  <- 1e10

# Set colours.
mainCol <- "darkslateblue"
ptCol   <- "paleturquoise3"
lineCol <- "skyblue"
axisCol <- "black"

# Set plotting size parameters.
cex.pt      <- 0.75
cex.mainVal <- 1.7
cex.labVal  <- 1.3
xlabVal     <- "x"

# FIRST SIMULATION SCENARIO
# -------------------------
mse.mu.uneven.mfvb <- 0
mse.mu.uneven.haar <- 0
mse.mu.uneven.s8   <- 0

mse.sd.uneven.mfvb <- 0
mse.sd.uneven.haar <- 0
mse.sd.uneven.s8   <- 0
mse.sd.uneven.j    <- 0
mse.sd.uneven.s8.j <- 0

lmse.sd.uneven.mfvb <- 0
lmse.sd.uneven.haar <- 0
lmse.sd.uneven.s8   <- 0
lmse.sd.uneven.j    <- 0
lmse.sd.uneven.s8.j <- 0

# Repeat for each data set simulated in the first simulation scenario.
cat(sprintf("Running %d simulations for Simulation Scenario 1.\n",nsim1))
for (j in 1:nsim1) {
  cat(sprintf("%d ",j))

  # Create the simulated data set
  # -----------------------------
  set.seed(3*j)
  n     <- 500
  xOrig <- runif(n)
  set.seed(3*j)
  yOrig <- fTrue(xOrig) + sqrt(exp(loggTrue(xOrig)))*rnorm(n)

  aOrig  <- min(xOrig)
  bOrig  <- max(xOrig)
  mean.x <- mean(xOrig)
  sd.x   <- sd(xOrig)
  mean.y <- mean(yOrig)
  sd.y   <- sd(yOrig)

  a <- (aOrig - mean.x)/sd.x
  b <- (bOrig - mean.x)/sd.x
  x <- (xOrig - mean.x)/sd.x
  y <- (yOrig - mean.y)/sd.y

  numIntKnotsU <- 17
  intKnotsU <- quantile(x,seq(0,1,length=numIntKnotsU+2)[-c(1,numIntKnotsU+2)])
  Zu        <- ZOSull(x,intKnots=intKnotsU,range.x=c(a,b))
  numKnotsU <- ncol(Zu)

  numIntKnotsV <- numIntKnotsU 
  intKnotsV <-
    quantile(x,seq(0,1,length = numIntKnotsV + 2)[-c(1,numIntKnotsV+2)])
  Zv        <- ZOSull(x,intKnots=intKnotsV,range.x=c(a,b))
  numKnotsV <- ncol(Zv)

  # Run Mean Field Variational Bayes (MFVB)
  # ---------------------------------------
  X     <- cbind(rep(1,n),x)
  Cumat <- cbind(X,Zu)
  Cvmat <- cbind(X,Zv)
  ncX   <- ncol(X)
  ncZu  <- ncol(Zu)
  ncZv  <- ncol(Zv)
  ncCu  <- ncol(Cumat)
  ncCv  <- ncol(Cvmat)

  MFVBfit <- meanVarMFVB(y,X,ncZu,ncZv,Au.hyp,Av.hyp,
                         sigsq.gamma,sigsq.beta)

  ng     <- 201
  xgOrig <- seq(aOrig,bOrig,length=ng)
  xg     <- (xgOrig - mean.x)/sd.x
  Xg     <- cbind(rep(1,ng),xg)
  Zug    <- ZOSull(xg,intKnots=intKnotsU,range.x=c(a,b))
  Cug    <- cbind(Xg,Zug)
  Zvg    <- ZOSull(xg,intKnots=intKnotsV,range.x=c(a,b))
  Cvg    <- cbind(Xg,Zvg)

  mu.q.nu       <- MFVBfit$mu.q.nu
  mu.q.omega    <- MFVBfit$mu.q.omega
  Sigma.q.nu    <- MFVBfit$Sigma.q.nu
  Sigma.q.omega <- MFVBfit$Sigma.q.omega

  fhatMFVBg        <- Cug%*%mu.q.nu
  fhatMFVBgOrig    <- fhatMFVBg*sd.y + mean.y
  logghatMFVBg     <- Cvg%*%mu.q.omega 
  logghatMFVBgOrig <- logghatMFVBg + 2*log(sd.y)

  sdloggMFVBgOrig      <- sqrt(diag(Cvg%*%Sigma.q.omega%*%t(Cvg))) 
  credLowloggMFVBgOrig <- logghatMFVBgOrig - qnorm(0.975)*sdloggMFVBgOrig
  credUpploggMFVBgOrig <- logghatMFVBgOrig + qnorm(0.975)*sdloggMFVBgOrig

  sqrtghatMFVBg     <- exp(0.5*Cvg %*% mu.q.omega 
                           + 0.125*diag(Cvg%*%Sigma.q.omega%*%t(Cvg)))
  sqrtghatMFVBgOrig <- sqrtghatMFVBg*sd.y

  # Run SMASH
  # ---------
  x.mod <- unique(sort(xOrig))
  y.mod <- 0
  for(i in 1:length(x.mod))
    y.mod[i] <- median(yOrig[xOrig == x.mod[i]])

  y.exp   <- c(y.mod,y.mod[length(y.mod):(2*length(y.mod)-2^9+1)])
  y.final <- c(y.exp,y.exp[length(y.exp):1])

  mu.est  <- smash.gaus(y.final,filter.number=1,family="DaubExPhase")
  var.est <- smash.gaus(y.final,v.est=TRUE)
  mu.est  <- mu.est[1:500]
  var.est <- var.est[1:500]

  mu.est.inter  <- approx(x.mod,mu.est,xgOrig,'linear')$y
  var.est.inter <- approx(x.mod,var.est,xgOrig,'linear')$y

  mse.mu.uneven.mfvb[j] <- mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
  mse.mu.uneven.haar[j] <- mean((mu.est.inter - fTrue(xgOrig))^2)

  mse.sd.uneven.mfvb[j]=mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.uneven.haar[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
  lmse.sd.uneven.mfvb[j]=mean((log(sqrtghatMFVBgOrig)-(loggTrue(xgOrig))/2)^2)
  lmse.sd.uneven.haar[j]=
    mean((log(sqrt(var.est.inter))-(loggTrue(xgOrig))/2)^2)

  mu.est       <- smash.gaus(y.final,filter.number=8,family="DaubLeAsymm")
  var.est      <- smash.gaus(y.final,v.est=TRUE,v.basis=TRUE,filter.number=8,
                             family="DaubLeAsymm")
  var.est.s8.j <- smash.gaus(y.final,v.est=TRUE,v.basis=TRUE,jash=TRUE,
                             filter.number=8,family="DaubLeAsymm")
  var.est.j    <- smash.gaus(y.final,v.est=TRUE,jash=TRUE)

  mu.est       <- mu.est[1:500]
  var.est      <- var.est[1:500]
  var.est.j    <- var.est.j[1:500]
  var.est.s8.j <- var.est.s8.j[1:500]

  mu.est.inter       <- approx(x.mod,mu.est,xgOrig,'linear')$y
  var.est.inter      <- approx(x.mod,var.est,xgOrig,'linear')$y
  var.est.inter.j    <- approx(x.mod,var.est.j,xgOrig,'linear')$y
  var.est.inter.s8.j <- approx(x.mod,var.est.s8.j,xgOrig,'linear')$y

  mse.mu.uneven.s8[j]=mean((mu.est.inter-fTrue(xgOrig))^2)
  mse.sd.uneven.s8[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.uneven.j[j] =mean((sqrt(var.est.inter.j)-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.uneven.s8.j[j] =
    mean((sqrt(var.est.inter.s8.j) - exp((loggTrue(xgOrig))/2))^2)
  lmse.sd.uneven.s8[j]=mean((log(sqrt(var.est.inter))-(loggTrue(xgOrig))/2)^2)
  lmse.sd.uneven.j[j]=mean((log(sqrt(var.est.inter.j))-(loggTrue(xgOrig))/2)^2)
  lmse.sd.uneven.s8.j[j] =
    mean((log(sqrt(var.est.inter.s8.j))-(loggTrue(xgOrig))/2)^2)
}
cat("\n")

# SECOND SIMULATION SCENARIO
# --------------------------
mse.mu.even.mfvb <- 0
mse.mu.even.haar <- 0
mse.mu.even.s8   <- 0

mse.sd.even.mfvb <- 0
mse.sd.even.haar <- 0
mse.sd.even.s8   <- 0
mse.sd.even.j    <- 0
mse.sd.even.s8.j <- 0

lmse.sd.even.mfvb <- 0
lmse.sd.even.haar <- 0
lmse.sd.even.s8   <- 0
lmse.sd.even.j    <- 0
lmse.sd.even.s8.j <- 0

# Repeat for each data set simulated in the second simulation scenario.
cat(sprintf("Running %d simulations for Simulation Scenario 2.\n",nsim2))
for (j in 1:nsim2) {
  cat(sprintf("%d ",j))

  # Create the simulated data set
  # -----------------------------
  n      <- 2^10
  xOrig  <- (1:n)/n
  set.seed(30*j)
  yOrig  <- fTrue(xOrig) + sqrt(exp(loggTrue(xOrig)))*rnorm(n)
  aOrig  <- min(xOrig)
  bOrig  <- max(xOrig)
  mean.x <- mean(xOrig)
  sd.x   <- sd(xOrig)
  mean.y <- mean(yOrig)
  sd.y   <- sd(yOrig)

  a <- (aOrig - mean.x)/sd.x
  b <- (bOrig - mean.x)/sd.x
  x <- (xOrig - mean.x)/sd.x
  y <- (yOrig - mean.y)/sd.y

  numIntKnotsU <- 17
  intKnotsU <- quantile(x,seq(0,1,length=numIntKnotsU+2)[-c(1,numIntKnotsU+2)])
  Zu        <- ZOSull(x,intKnots=intKnotsU,range.x=c(a,b))
  numKnotsU <- ncol(Zu)

  numIntKnotsV <- numIntKnotsU 
  intKnotsV <- quantile(x,seq(0,1,length=numIntKnotsV+2)[-c(1,numIntKnotsV+2)])
  Zv        <- ZOSull(x,intKnots=intKnotsV,range.x=c(a,b))
  numKnotsV <- ncol(Zv)

  # Run Mean Field Variational Bayes (MFVB)
  # ---------------------------------------
  X     <- cbind(rep(1,n),x)
  Cumat <- cbind(X,Zu)
  Cvmat <- cbind(X,Zv)
  ncX   <- ncol(X)
  ncZu  <- ncol(Zu)
  ncZv  <- ncol(Zv)
  ncCu  <- ncol(Cumat)
  ncCv  <- ncol(Cvmat)

  MFVBfit <- meanVarMFVB(y,X,ncZu,ncZv,Au.hyp,Av.hyp,
                       sigsq.gamma,sigsq.beta)

  ng     <- 2^10
  xgOrig <- seq(aOrig,bOrig,length=ng)
  xg  <- (xgOrig - mean.x)/sd.x
  Xg  <- cbind(rep(1,ng),xg)
  Zug <- ZOSull(xg,intKnots=intKnotsU,range.x=c(a,b))
  Cug <- cbind(Xg,Zug)
  Zvg <- ZOSull(xg,intKnots=intKnotsV,range.x=c(a,b))
  Cvg <- cbind(Xg,Zvg)

  mu.q.nu       <- MFVBfit$mu.q.nu
  mu.q.omega    <- MFVBfit$mu.q.omega
  Sigma.q.nu    <- MFVBfit$Sigma.q.nu
  Sigma.q.omega <- MFVBfit$Sigma.q.omega

  # Get the mean function estimate.
  fhatMFVBg     <- Cug %*% mu.q.nu
  fhatMFVBgOrig <- fhatMFVBg*sd.y + mean.y

  logghatMFVBg     <- Cvg%*%mu.q.omega 
  logghatMFVBgOrig <- logghatMFVBg + 2*log(sd.y)

  sdloggMFVBgOrig      <- sqrt(diag(Cvg%*%Sigma.q.omega%*%t(Cvg))) 
  credLowloggMFVBgOrig <- logghatMFVBgOrig - qnorm(0.975)*sdloggMFVBgOrig
  credUpploggMFVBgOrig <- logghatMFVBgOrig + qnorm(0.975)*sdloggMFVBgOrig

  sqrtghatMFVBg     <- exp(0.5*Cvg%*%mu.q.omega 
                           + 0.125*diag(Cvg%*%Sigma.q.omega%*%t(Cvg)))
  sqrtghatMFVBgOrig <- sqrtghatMFVBg*sd.y

  # Run SMASH
  # ---------
  mu.est  <- smash.gaus(yOrig,filter.number=1,family="DaubExPhase")
  var.est <- smash.gaus(yOrig,v.est=TRUE)

  mse.mu.even.mfvb[j] <- mean((fhatMFVBgOrig-fTrue(xgOrig))^2)
  mse.mu.even.haar[j] <- mean((mu.est-fTrue(xgOrig))^2)

  mse.sd.even.mfvb[j]  <- mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.even.haar[j]  <- mean((sqrt(var.est)-exp((loggTrue(xgOrig))/2))^2)
  lmse.sd.even.mfvb[j] <- mean((log(sqrtghatMFVBgOrig)-(loggTrue(xgOrig))/2)^2)
  lmse.sd.even.haar[j] <- mean((log(sqrt(var.est))-(loggTrue(xgOrig))/2)^2)

  mu.est       <- smash.gaus(yOrig,filter.number=8,family="DaubLeAsymm")
  var.est      <- smash.gaus(yOrig,v.est=TRUE,v.basis=TRUE,filter.number=8,
                             family="DaubLeAsymm")
  var.est.s8.j <- smash.gaus(yOrig,v.est=TRUE,v.basis=TRUE,jash=TRUE,
                             filter.number=8,family="DaubLeAsymm")
  var.est.j    <- smash.gaus(yOrig,v.est=TRUE,jash=TRUE)

  mse.mu.even.s8[j]   <-mean((mu.est-fTrue(xgOrig))^2)
  mse.sd.even.s8[j]   <-mean((sqrt(var.est)-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.even.j[j]    <-mean((sqrt(var.est.j)-exp((loggTrue(xgOrig))/2))^2)
  mse.sd.even.s8.j[j] <-mean((sqrt(var.est.s8.j)-exp((loggTrue(xgOrig))/2))^2)
  lmse.sd.even.s8[j]  <-mean((log(sqrt(var.est))-(loggTrue(xgOrig))/2)^2)
  lmse.sd.even.j[j]   <-mean((log(sqrt(var.est.j))-(loggTrue(xgOrig))/2)^2)
  lmse.sd.even.s8.j[j]<-mean((log(sqrt(var.est.s8.j))-(loggTrue(xgOrig))/2)^2)
}
cat("\n")

# PLOT MEAN & VARIANCE FUNCTIONS USED TO SIMULATE DATA
# ----------------------------------------------------
# Compare this plot against the one shown in Fig. 4 of the paper.
cat("Plotting mean and variance functions used to simulate data.\n")
xgrid <- (0:10000)/10000
plot(xgrid,fTrue(xgrid),type = "l",ylim = c(-5,5),ylab = "y",xlab = "X",
     lwd = 2)
lines(xgrid,fTrue(xgrid) + 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
lines(xgrid,fTrue(xgrid) - 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)

# SUMMARIZE RESULTS
# -----------------
# Compare this table against Table 1 in the paper.
cat("Summarizing results of simulations.\n")
cat(sprintf("MSE averaged across %d simulations in Scenario 1,\n",nsim1))
cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
mse.table <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb),
                     mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
                   c(mean(mse.mu.uneven.s8),mean(mse.sd.uneven.s8),
                     mean(mse.mu.even.s8),mean(mse.sd.even.s8)))
rownames(mse.table) <- c("MFVB","SMASH")
colnames(mse.table) <- c("mean","sd","mean","sd")
cat("         Scenario 1      Scenario 2   \n")
cat("      --------------- ----------------\n")
print(mse.table)

### 2018-11-08 analysis/index.Rmd
wflow_publish("index.Rmd")
Moved around some files and revised TOC in home page.

@@
 
-## License
-
-Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
-Stephens.
-
-All source code and software in this repository are made available
-under the terms of the [MIT license][mit-license]. See the
-[LICENSE](LICENSE) file for the full text of the license.
-
 ## Contents
@@
 
-[**Illustration:** SMASH applied to the "spikes" data set.](spikesdemo.html)
+### Illustration
 
-### Comparisons of signal denoising methods in simulated data
++ [SMASH applied to the "Spikes" data set.](spikesdemo.html)
+
+### Simulation experiments
 
 1. [Estimating the mean function from Gaussian-distributed
-data.](gausshomo.html)
+data.](gaussmeanest.html)
 
-2. Estimating the variance function from Gaussian-distributed data.
+2. [Estimating the variance function from Gaussian-distributed
+data](gaussvarest.html).
 
@@
 
+## License
+
+Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
+Stephens.
+
+All source code and software in this repository are made available
+under the terms of the [MIT license][mit-license]. See the
+[LICENSE](LICENSE) file for the full text of the license.
+
 ## Credits

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
-# ---
-# title: "Gaussian variance estimation in simulated data sets"
-# ---
-#
-# This script implements the "Gaussian variance estimation" simulation
-# experiments in the paper. In particular, we compare the Mean Field
-# Variational Bayes method (MFVB) against SMASH in two scenarios. See
-# the paper for the full description of these scenarios.
-#
-# The figure and table generated at the end of this script should
-# match up with the figure and table shown in the paper.
-#
-# Note that this script could take an hour or several hours to
-# complete as it runs the two methods on 100 simulated data sets for
-# each of the two scenarios.
-#
-# We thank Menictas & Wand for generously sharing code that was used
-# to implement these experiments.
-#
+---
+title: "Gaussian variance estimation in simulated data sets"
+author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
+output: workflowr::wflow_html
+---
 
-# -----
-# TO DO: Remove steps that are not included in the paper.
-# -----
+This script implements the "Gaussian variance estimation" simulation
+experiments in the paper. In particular, we compare the Mean Field
+Variational Bayes method (MFVB) against SMASH in two scenarios.
 
-# SET UP ENVIRONMENT
-# ------------------
-# Load the smashr package, and some functions used in the analysis.
+The figure and table generated at the end of this script should
+match up with the figure and table shown in the paper.
+
+Running the code could take several hours to complete as it runs the
+two methods on 100 simulated data sets for each of the two scenarios.
+
+We thank M. Menictas & M. Wand for generously sharing code that was
+used to implement these experiments.
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+```
+
+Initial setup instructions
+--------------------------
+
+To run this example on your own computer, please follow these setup
+instructions. These instructions assume you already have R and/or
+RStudio installed on your computer.
+
+First, download or clone the [git repository][smash-github] on your
+computer.
+
+Launch R, and change the working directory to be the "analysis" folder
+inside your local copy of the git repository.
+
+Finally, install the smashr package from GitHub:
+
+```{r install-pkgs-2, eval=FALSE}
+devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
+```
+
+See the "Session Info" at the bottom for the versions of the software
+and R packages that were used to generate the results shown below.
+
+Set up R environment
+--------------------
+
+Load the smashr package, as well as some functions used in the
+analysis below.
+
+```{r load-pkgs}
 library(smashr)
-source("../code/mfvb.functions.R")
+source("../code/mfvb.R")
+```
 
-# SCRIPT PARAMETERS
-# -----------------
-# Number of data sets simulated in the first (nsim1) and second
-# (nsim2) simulation scenarios.
-nsim1 <- 100
-nsim2 <- 100
+Analysis settings
+-----------------
 
-# Set hyperparameters.
+Specify the number of data sets simulated in the first and second
+simulation scenarios.
+
+```{r analysis-settings-1}
+nsim1 <- 10
+nsim2 <- 10
+```
+
+Next, specify the hyperparameters used in running the MFVB method.
+
+```{r analysis-settings-2}
 Au.hyp      <- 1e5
@@
 sigsq.beta  <- 1e10
+```
 
-# Set colours.
+These variables specify some colours used in the plots.
+
+```{r analysis-settings-3}
 mainCol <- "darkslateblue"
@@
 axisCol <- "black"
+```
 
-# Set plotting size parameters.
+These are additional plotting parameters.
+
+```{r analysis-settings-4}
 cex.pt      <- 0.75
@@
 xlabVal     <- "x"
+```
 
-# FIRST SIMULATION SCENARIO
-# -------------------------
+First simulation scenario
+-------------------------
+
+```{r simulation-1}
 mse.mu.uneven.mfvb <- 0
@@
 cat("\n")
+```
 
+```
 # SECOND SIMULATION SCENARIO
@@
 print(mse.table)
+```

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 experiments in the paper. In particular, we compare the Mean Field
-Variational Bayes method (MFVB) against SMASH in two scenarios.
+Variational Bayes (MFVB) method against SMASH in two scenarios.
 
@@
 
-First simulation scenario
--------------------------
+Plot mean and variance functions used to simulate data
+------------------------------------------------------
 
-```{r simulation-1}
+Compare this plot against the one shown in Fig. 4 of the paper.
+
+```{r plot-mean-and-variance, fig.height=4, fig.width=5}
+xgrid <- (0:10000)/10000
+plot(xgrid,fTrue(xgrid),type = "l",ylim = c(-5,5),ylab = "y",xlab = "X",
+     lwd = 2)
+lines(xgrid,fTrue(xgrid) + 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
+lines(xgrid,fTrue(xgrid) - 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
+```
+
+First simulation scenario: unevenly spaced data
+-----------------------------------------------
+
+In the first scenario, we simulated unevenly spaced data points, and
+assessed accuracy by computing the mean of the squared errors (MSE)
+evaluated at 201 equally spaced points.
+
+```{r simulation-1-initialize, eval=FALSE}
 mse.mu.uneven.mfvb  <- 0
-mse.mu.uneven.haar <- 0
-mse.mu.uneven.s8   <- 0
+mse.mu.uneven.smash <- 0
+mse.sd.uneven.mfvb  <- 0
+mse.sd.uneven.smash <- 0
+```
 
-mse.sd.uneven.mfvb <- 0
-mse.sd.uneven.haar <- 0
-mse.sd.uneven.s8   <- 0
-mse.sd.uneven.j    <- 0
-mse.sd.uneven.s8.j <- 0
+Run the SMASH and MFVB methods for each simulated data set.
 
-lmse.sd.uneven.mfvb <- 0
-lmse.sd.uneven.haar <- 0
-lmse.sd.uneven.s8   <- 0
-lmse.sd.uneven.j    <- 0
-lmse.sd.uneven.s8.j <- 0
-
-# Repeat for each data set simulated in the first simulation scenario.
-cat(sprintf("Running %d simulations for Simulation Scenario 1.\n",nsim1))
+```{r simulation-1-main-loop, eval=FALSE} 
+cat(sprintf("Running %d simulations: ",nsim1))
 for (j in 1:nsim1) {
@@
 
-  # Create the simulated data set
-  # -----------------------------
+  # SIMULATE DATA
   set.seed(3*j)
@@
 
-  # Run SMASH
-  # ---------
+  # RUN SMASH
   x.mod <- unique(sort(xOrig))
@@
   mse.mu.uneven.mfvb[j] <- mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
-  mse.mu.uneven.haar[j] <- mean((mu.est.inter - fTrue(xgOrig))^2)
-
-  mse.sd.uneven.mfvb[j]=mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.uneven.haar[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
-  lmse.sd.uneven.mfvb[j]=mean((log(sqrtghatMFVBgOrig)-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.uneven.haar[j]=
-    mean((log(sqrt(var.est.inter))-(loggTrue(xgOrig))/2)^2)
+  mse.sd.uneven.mfvb[j] <- mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
 
@@
                         family="DaubLeAsymm")
-  var.est.s8.j <- smash.gaus(y.final,v.est=TRUE,v.basis=TRUE,jash=TRUE,
-                             filter.number=8,family="DaubLeAsymm")
-  var.est.j    <- smash.gaus(y.final,v.est=TRUE,jash=TRUE)
 
@@
   var.est <- var.est[1:500]
-  var.est.j    <- var.est.j[1:500]
-  var.est.s8.j <- var.est.s8.j[1:500]
 
@@
   var.est.inter      <- approx(x.mod,var.est,xgOrig,'linear')$y
-  var.est.inter.j    <- approx(x.mod,var.est.j,xgOrig,'linear')$y
-  var.est.inter.s8.j <- approx(x.mod,var.est.s8.j,xgOrig,'linear')$y
 
@@
   mse.sd.uneven.s8[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.uneven.j[j] =mean((sqrt(var.est.inter.j)-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.uneven.s8.j[j] =
-    mean((sqrt(var.est.inter.s8.j) - exp((loggTrue(xgOrig))/2))^2)
-  lmse.sd.uneven.s8[j]=mean((log(sqrt(var.est.inter))-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.uneven.j[j]=mean((log(sqrt(var.est.inter.j))-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.uneven.s8.j[j] =
-    mean((log(sqrt(var.est.inter.s8.j))-(loggTrue(xgOrig))/2)^2)
 }
@@
 
-```
-# SECOND SIMULATION SCENARIO
-# --------------------------
+Second simulation scenario: evenly spaced points
+------------------------------------------------
+
+```{r, eval=FALSE}
 mse.mu.even.mfvb <- 0
-mse.mu.even.haar <- 0
 mse.mu.even.s8   <- 0
@@
 mse.sd.even.mfvb <- 0
-mse.sd.even.haar <- 0
 mse.sd.even.s8   <- 0
-mse.sd.even.j    <- 0
-mse.sd.even.s8.j <- 0
-
 lmse.sd.even.mfvb <- 0
-lmse.sd.even.haar <- 0
 lmse.sd.even.s8   <- 0
-lmse.sd.even.j    <- 0
-lmse.sd.even.s8.j <- 0
 
 # Repeat for each data set simulated in the second simulation scenario.
-cat(sprintf("Running %d simulations for Simulation Scenario 2.\n",nsim2))
+cat(sprintf("Running %d simulations: ",nsim2))
 for (j in 1:nsim2) {
@@
 
-# PLOT MEAN & VARIANCE FUNCTIONS USED TO SIMULATE DATA
-# ----------------------------------------------------
-# Compare this plot against the one shown in Fig. 4 of the paper.
-cat("Plotting mean and variance functions used to simulate data.\n")
-xgrid <- (0:10000)/10000
-plot(xgrid,fTrue(xgrid),type = "l",ylim = c(-5,5),ylab = "y",xlab = "X",
-     lwd = 2)
-lines(xgrid,fTrue(xgrid) + 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
-lines(xgrid,fTrue(xgrid) - 2*sqrt(gTrue(xgrid)),col = "darkorange",lwd = 2)
-
 # SUMMARIZE RESULTS

### 2018-11-09 code/mfvb.R

@@ -1,0 +1,249 @@
+# The source code for the ZOSull and meanVarMFVB functions was
+# generously shared by Marianne Menictas and Matt Wand from the
+# University of Technology, Sydney.
+
+# Specify true nonparametric mean and variance functions.
+fTrue    <- function(x) return(sin(3*pi*x^2))
+gTrue    <- function(x) return(exp(0.1 + cos(4*pi*x)))
+loggTrue <- function(x) return(0.1 + cos(4*pi*x))
+
+########## R function: ZOSull ##########
+
+# For creation of O'Sullivan-type Z matrices.
+
+# Last changed: 16 DEC 2009
+
+ZOSull <- function(x,range.x,intKnots,drv=0)
+{
+   # Check legality of range.x.
+  
+   if (!missing(range.x))
+   {
+      if (length(range.x)!=2) stop("range.x must be of length 2.")
+      if (range.x[1]>range.x[2]) stop("range.x[1] exceeds range.x[1].")
+      if (range.x[1]>min(x)) stop("range.x[1] must be <= than min(x).")
+      if (range.x[2]<max(x)) stop("range.x[2] must be >= than max(x).")
+
+   }
+   
+   if (drv>2) stop("splines not smooth enough for more than 2 derivatives")
+
+   library(splines)
+
+   # Set defaults for `range.x' and `intKnots'
+
+   if (missing(range.x))
+      range.x <- c(1.05*min(x)-0.05*max(x),1.05*max(x)-0.05*min(x))
+   
+   if (missing(intKnots))
+   {
+      numIntKnots <- min(length(unique(x)),35)
+      intKnots <- quantile(unique(x),seq(0,1,length=
+                  (numIntKnots+2))[-c(1,(numIntKnots+2))])
+   }
+   numIntKnots <- length(intKnots) 
+
+   # Obtain the penalty matrix.
+
+   allKnots <- c(rep(range.x[1],4),intKnots,rep(range.x[2],4)) 
+   K <- length(intKnots) ; L <- 3*(K+8)
[…]

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 ```{r install-pkgs-2, eval=FALSE}
-devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
+devtools::install_github("stephenslab/smashr")
 ```
@@
 
-```{r plot-mean-and-variance, fig.height=4, fig.width=5}
+```{r plot-mean-and-variance, fig.height=5, fig.width=6}
 xgrid <- (0:10000)/10000
@@
 
-In the first scenario, we simulated unevenly spaced data points, and
-assessed accuracy by computing the mean of the squared errors (MSE)
-evaluated at 201 equally spaced points.
+In the first scenario, we simulate data sets with unevenly spaced data
+points, and assesse accuracy by computing the mean of the squared
+errors (MSE) evaluated at 201 equally spaced points.
 
-```{r simulation-1-initialize, eval=FALSE}
+```{r simulation-1-initialize}
 mse.mu.uneven.mfvb  <- 0
@@
 
-  # Run Mean Field Variational Bayes (MFVB)
-  # ---------------------------------------
+  # RUN MEAN FIELD VARIATIONAL BAYES
   X     <- cbind(rep(1,n),x)
@@
 
-  mse.mu.uneven.mfvb[j] <- mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
-  mse.sd.uneven.mfvb[j] <- mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
+  mse.mu.uneven.mfvb[j]<-mean((fhatMFVBgOrig - fTrue(xgOrig))^2)
+  mse.sd.uneven.mfvb[j]<-mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
 
@@
 
-  mse.mu.uneven.s8[j]=mean((mu.est.inter-fTrue(xgOrig))^2)
-  mse.sd.uneven.s8[j]=mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
+  mse.mu.uneven.s8[j]<-mean((mu.est.inter-fTrue(xgOrig))^2)
+  mse.sd.uneven.s8[j]<-mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
 }
@@
 ```
+
+[smash-github]: https://github.com/stephenslab/smash-paper

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 experiments in the paper. In particular, we compare the Mean Field
-Variational Bayes (MFVB) method against SMASH in two scenarios.
-
-The figure and table generated at the end of this script should
-match up with the figure and table shown in the paper.
+Variational Bayes (MFVB) method against SMASH in two scenarios. The
+figure and table generated at the end of this script should match up
+with the figure and table shown in the paper.
 
@@
 
-In the first scenario, we simulate data sets with unevenly spaced data
-points, and assesse accuracy by computing the mean of the squared
+In the first scenario, we simulate data sets with 500 unevenly spaced data
+points, and assess accuracy by computing the mean of the squared
 errors (MSE) evaluated at 201 equally spaced points.
@@
 
-```{r simulation-1-main-loop, eval=FALSE} 
+```{r simulation-1-main-loop} 
 cat(sprintf("Running %d simulations: ",nsim1))
@@
 
-  mse.mu.uneven.s8[j]<-mean((mu.est.inter-fTrue(xgOrig))^2)
-  mse.sd.uneven.s8[j]<-mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
+  mse.mu.uneven.smash[j] <- mean((mu.est.inter-fTrue(xgOrig))^2)
+  mse.sd.uneven.smash[j] <-
+    mean((sqrt(var.est.inter)-exp((loggTrue(xgOrig))/2))^2)
 }
@@
 ------------------------------------------------
+
+In this scenario, we simulated evenly spaced data points.
 

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 ```{r knitr-opts, include=FALSE}
-knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,results = "hold",
+                      fig.align = "center")
 ```
@@
 }
-cat("\n")
 ```
@@
 
-In this scenario, we simulated evenly spaced data points.
+In this scenario, we simulate data sets with 1,024 evenly spaced data
+points. We assess accuracy separately for the mean and standard
+deviation as the mean of the MSEs evaluated at each of the locations.
 
-```{r, eval=FALSE}
+```{r simulation-2-initialize}
 mse.mu.even.mfvb  <- 0
-mse.mu.even.s8   <- 0
+mse.mu.even.smash <- 0
+mse.sd.even.mfvb  <- 0
+mse.sd.even.smash <- 0
+```
 
-mse.sd.even.mfvb <- 0
-mse.sd.even.s8   <- 0
-lmse.sd.even.mfvb <- 0
-lmse.sd.even.s8   <- 0
+Run the SMASH and MFVB methods for each simulated data set.
 
-# Repeat for each data set simulated in the second simulation scenario.
+```{r simulation-2-main-loop}
 cat(sprintf("Running %d simulations: ",nsim2))
@@
 
-  # Create the simulated data set
-  # -----------------------------
+  # SIMULATE DATA
   n      <- 2^10
@@
 
-  # Run SMASH
-  # ---------
+  # RUN SMASH
   mu.est  <- smash.gaus(yOrig,filter.number=1,family="DaubExPhase")
@@
   mse.mu.even.mfvb[j] <- mean((fhatMFVBgOrig-fTrue(xgOrig))^2)
-  mse.mu.even.haar[j] <- mean((mu.est-fTrue(xgOrig))^2)
-
   mse.sd.even.mfvb[j] <- mean((sqrtghatMFVBgOrig-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.even.haar[j]  <- mean((sqrt(var.est)-exp((loggTrue(xgOrig))/2))^2)
-  lmse.sd.even.mfvb[j] <- mean((log(sqrtghatMFVBgOrig)-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.even.haar[j] <- mean((log(sqrt(var.est))-(loggTrue(xgOrig))/2)^2)
 
@@
   var.est <- smash.gaus(yOrig,v.est=TRUE,v.basis=TRUE,filter.number=8,
-                             family="DaubLeAsymm")
-  var.est.s8.j <- smash.gaus(yOrig,v.est=TRUE,v.basis=TRUE,jash=TRUE,
-                             filter.number=8,family="DaubLeAsymm")
-  var.est.j    <- smash.gaus(yOrig,v.est=TRUE,jash=TRUE)
+                        family = "DaubLeAsymm")
 
-  mse.mu.even.s8[j]   <-mean((mu.est-fTrue(xgOrig))^2)
-  mse.sd.even.s8[j]   <-mean((sqrt(var.est)-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.even.j[j]    <-mean((sqrt(var.est.j)-exp((loggTrue(xgOrig))/2))^2)
-  mse.sd.even.s8.j[j] <-mean((sqrt(var.est.s8.j)-exp((loggTrue(xgOrig))/2))^2)
-  lmse.sd.even.s8[j]  <-mean((log(sqrt(var.est))-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.even.j[j]   <-mean((log(sqrt(var.est.j))-(loggTrue(xgOrig))/2)^2)
-  lmse.sd.even.s8.j[j]<-mean((log(sqrt(var.est.s8.j))-(loggTrue(xgOrig))/2)^2)
+  mse.mu.even.smash[j]  <- mean((mu.est - fTrue(xgOrig))^2)
+  mse.sd.even.smash[j]  <- mean((sqrt(var.est)-exp((loggTrue(xgOrig))/2))^2)
 }
-cat("\n")
+```
 
-# SUMMARIZE RESULTS
-# -----------------
-# Compare this table against Table 1 in the paper.
-cat("Summarizing results of simulations.\n")
+Summarize results of simulations
+--------------------------------
+
+Compare this table against Table 1 in the paper.
+
+```{r summarize-mse}
 cat(sprintf("MSE averaged across %d simulations in Scenario 1,\n",nsim1))
@@
                      mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
-                   c(mean(mse.mu.uneven.s8),mean(mse.sd.uneven.s8),
-                     mean(mse.mu.even.s8),mean(mse.sd.even.s8)))
+                   c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash),
+                     mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
 rownames(mse.table) <- c("MFVB","SMASH")

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 
-In the first scenario, we simulate data sets with 500 unevenly spaced data
-points, and assess accuracy by computing the mean of the squared
-errors (MSE) evaluated at 201 equally spaced points.
+In the first scenario, we simulate data sets with 500 unevenly spaced
+data points, and assess accuracy, separately for the mean and variance
+estimates) by computing the mean of the squared errors (MSE) evaluated
+at 201 equally spaced points.
 
@@
 
-Compare this table against Table 1 in the paper.
+The following two tables shows the mean squared error (MSE) averaged
+over the 100 simulations in each of the scenarios. Compare these
+results with Table 1 in the paper.
 
 ```{r summarize-mse}
-cat(sprintf("MSE averaged across %d simulations in Scenario 1,\n",nsim1))
+mse.table1 <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb)),
+                    c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash)))
+mse.table2 <- rbind(c(mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
+                    c(mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
+rownames(mse.table1) <- c("MFVB","SMASH")
+colnames(mse.table1) <- c("mean","sd")
+rownames(mse.table2) <- c("MFVB","SMASH")
+colnames(mse.table2) <- c("mean","sd")
+cat(sprintf("MSE averaged across %d simulations in Scenario 1:\n",nsim1))
+print(mse.table1)
 cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
-mse.table <- rbind(c(mean(mse.mu.uneven.mfvb),mean(mse.sd.uneven.mfvb),
-                     mean(mse.mu.even.mfvb),mean(mse.sd.even.mfvb)),
-                   c(mean(mse.mu.uneven.smash),mean(mse.sd.uneven.smash),
-                     mean(mse.mu.even.smash),mean(mse.sd.even.smash)))
-rownames(mse.table) <- c("MFVB","SMASH")
-colnames(mse.table) <- c("mean","sd","mean","sd")
-cat("         Scenario 1      Scenario 2   \n")
-cat("      --------------- ----------------\n")
-print(mse.table)
+print(mse.table2)
 ```
 
+In Scenario 1, the data are not equally spaced, and the number of data
+points is not a power of 2; in this setting, SMASH is more accurate in
+estimating both the mean and s.d.
+
+In Scenario 2, the data are equally spaced, and the number of data
+points is a power of 2; SMASH again outperforms MFVB in both mean and
+s.d. estimation.
+
 [smash-github]: https://github.com/stephenslab/smash-paper

### 2018-11-09 analysis/gaussvarest.Rmd
wflow_publish("gaussvarest.Rmd")

@@
 
-This script implements the "Gaussian variance estimation" simulation
+This analysis implements the "Gaussian variance estimation" simulation
 experiments in the paper. In particular, we compare the Mean Field
@@
 ```{r analysis-settings-1}
-nsim1 <- 10
-nsim2 <- 10
+nsim1 <- 100
+nsim2 <- 100
 ```
@@
 
-The following two tables shows the mean squared error (MSE) averaged
+The following two tables show the mean squared error (MSE) averaged
 over the 100 simulations in each of the scenarios. Compare these
@@
 print(mse.table1)
-cat(sprintf("and averaged across %d simulations in Scenario 2:\n",nsim2))
+cat("\n")
+cat(sprintf("MSE averaged across %d simulations in Scenario 2:\n",nsim2))
 print(mse.table2)

### 2018-12-02 analysis/gaussmeanest.Rmd
Moved dsc results file.

--- 2018-09-29 analysis/gaussian.mean.est.Rmd
@@
 
-Since the simulation experiments are very computationally intensive,
-they are implemented separately (see the "dsc" directory in this git
+Since the simulation experiments are computationally intensive, they
+are implemented separately (see the "dsc" directory in this git
 repository), and here we only create plots to summarize the results of
@@
 ```{r load-results}
-load("../output/gaus-dscr.RData")
+load("../output/dscr.RData")
 ```

### 2018-12-02 analysis/shiny.Rmd
Moved dsc results file.

@@
 library(dplyr)
-load("../output/gaus-dscr.RData")
+load("../output/dscr.RData")
 scenario_names = as.character(unique(res$scenario))

### 2018-12-04 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 Since the simulation experiments are computationally intensive, they
-are implemented separately (see the "dsc" directory in this git
+were implemented separately (see the "dsc" directory in this git
 repository), and here we only create plots to summarize the results of
@@
 
-This plot reproduces Fig. 2 of the manuscript comparing the
-accuracy of estimated mean curves in the data sets simulated from
-the "Spikes" mean function with constant variance.
+This plot reproduces Fig. 2 of the manuscript, which compares the
+accuracy of the mean curves estimated from the data sets that were
+simulated using the "Spikes" mean function with constant variance.
 
@@
 
-From this plot, we see that three versions of SMASH outperformed
-EbayesThresh and TI thresholding.
+From this plot, we see that the three variations of SMASH all
+outperformed EbayesThresh and TI thresholding in this setting.
 
@@
 
-In this scenario, data sets were simulated using the "Spikes" mean
-function and the "Clipped Blocks" variance function. The next couple
+In this scenario, the data sets were simulated using the "Spikes" mean
+function and the "Clipped Blocks" variance function. The next two
 plots reproduce part of Fig. 3 in the manuscript.
@@
 
-In the "Spikes" scenario, we see that SMASH, when allowing for
-heteroskedastic errors, outperforms EbayesThresh and all variants of
-TI thresholding (including TI thresholding with the true variance).
+In this scenario, we see that SMASH, when allowing for heteroskedastic
+errors, outperforms EbayesThresh and all variants of TI thresholding
+(including TI thresholding when provided with the true variance).
 Further, SMASH performs almost as well when estimating the variance
@@
 mean function and the "Doppler" variance function. These plots were
-also used for Fig. 3 of the manuscript.
+also used in Fig. 3 of the manuscript.
 

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

---
title: "Mean and variance functions used to simulate Gaussian data"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

## Set up environment

Load the ggplot2 and cowplot packages, and the functions definining
the mean and variances used to simulate the data.

```{r load-pkgs, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
source("../code/signals.R")
```

## Generate the ground-truth signals

Here, `n` specifies the length of the signals.

```{r specify-n}
n = 1024
t = 1:n/n
```

Some code.

```{r}
mu.s = spike.f(t)
```

More code.

```{r}
pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
hgt = 2.97/5 * c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
wth = c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005, 0.008, 0.005)
mu.b = rep(0, n)
for (j in 1:length(pos))
  mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)

mu.dop     = dop.f(t)
mu.dop     = 3/(max(mu.dop) - min(mu.dop)) * (mu.dop - min(mu.dop))
mu.dop.var = 10 * dop.f(t)
mu.dop.var = mu.dop.var - min(mu.dop.var)

sig = ((2 * t + 0.5) * (t <= 0.15)) +
      ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
      0.2 * (t > 0.2 & t <= 0.5) + 
      ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
      ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
      ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
      ((2 * (t - 0.85) + 0.2) * (t > 0.85))
mu.ang = 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569

heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
mu.hs = mu.hs - min(mu.hs)

pos    = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
hgt    = 2.88/5 * c(4, (-5), 3, (-4), 5, (-4.2), 2.1, 4.3, (-3.1), 2.1, (-4.2))
mu.blk = rep(0, n)
for (j in 1:length(pos))
  mu.blk = mu.blk + (1 + sign(t - pos[j])) * (hgt[j]/2)

mu.cblk = mu.blk
mu.cblk[mu.cblk < 0] = 0
```

Define the Blip mean function.

```{r define-blip}
mu.blip = (0.32 + 0.6 * t +
           0.3 * exp(-100 * (t - 0.3)^2)) * (t >= 0 & t <= 0.8) +
  (-0.28 + 0.6 * t + 0.3 * exp(-100 * (t - 1.3)^2)) * (t > 0.8 & t <= 1)
```

Define the Corner mean function.

```{r define-corner}
mu.cor = 623.87 * t^3 * (1 - 2 * t) * (t >= 0 & t <= 0.5) +
         187.161 * (0.125 - t^3) * t^4 * (t > 0.5 & t <= 0.8) +
         3708.470441 * (t - 1)^3 * (t > 0.8 & t <= 1)
mu.cor = (0.6/(max(mu.cor) - min(mu.cor))) * mu.cor
mu.cor = mu.cor - min(mu.cor) + 0.2
```

Define the rest of the mean functions.

```{r define-mean}
mu.sp   = (1 + mu.s)/5
mu.bump = (1 + mu.b)/5
mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
mu.ang  = (1 + mu.ang)/5
mu.dop  = (1 + mu.dop)/5
```

Define the variance functions.

```{r define-variance}
var1 = rep(1, n)
var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 = (1e-02 + 2 * mu.dop.var)
var4 = 1e-02 + mu.b
var5 = 1e-02 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var3 = var3/max(var3)
var4 = var4/max(var4)
var5 = var5/max(var5)
```

## Plot the signal means

These plots show each of the mean functions used to generate the
simulated data sets.

```{r plot-mean-functions, fig.height=10, fig.width=6}
plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"))
# plot(t,mu.dop,xlab = "",ylab = "",type = "l",main = "Doppler mean function")
# plot(t,mu.blip,xlab = "",ylab = "",type = "l",main = "Blip mean function")
# plot(t,mu.cor,xlab = "",ylab = "",type = "l",main = "Corner mean function")
```

## Plot the signal variances

These are rescaled in the simulations to achieve the desired signal
to noise ratios.

```{r plot-variance-functions}
plot(t,var1,xlab = "",ylab = "",ylim = c(0,1),type = "l",
     main = "Constant variance function")
plot(t,var2,xlab = "",ylab = "",type = "l",
     main = "Triple exponential variance function")
plot(t,var3,xlab = "",ylab = "",type = "l",main = "Doppler variance function")
plot(t,var4,xlab = "",ylab = "",type = "l",main = "Bumps variance function")
plot(t,var5,xlab = "",ylab = "",type = "l",main = "Clipped variance function")
```

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
           qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
-          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"))
-# plot(t,mu.dop,xlab = "",ylab = "",type = "l",main = "Doppler mean function")
-# plot(t,mu.blip,xlab = "",ylab = "",type = "l",main = "Blip mean function")
-# plot(t,mu.cor,xlab = "",ylab = "",type = "l",main = "Corner mean function")
+          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"),
+          qplot(t,mu.dop, geom = "line",xlab = "",ylab = "",main = "Doppler"),
+          qplot(t,mu.blip,geom = "line",xlab = "",ylab = "",main = "Blip"),
+          qplot(t,mu.cor, geom = "line",xlab = "",ylab = "",main = "Corner"),
+		  nrow = 4,ncol = 2)
 ```

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 ```{r plot-mean-functions, fig.height=10, fig.width=6}
-plot_grid(qplot(t,mu.sp,  geom = "line",xlab = "",ylab = "",main = "Spikes"),
-          qplot(t,mu.bump,geom = "line",xlab = "",ylab = "",main = "Bumps"),
-          qplot(t,mu.blk, geom = "line",xlab = "",ylab = "",main = "Blocks"),
-          qplot(t,mu.ang, geom = "line",xlab = "",ylab = "",main = "Angles"),
-          qplot(t,mu.dop, geom = "line",xlab = "",ylab = "",main = "Doppler"),
-          qplot(t,mu.blip,geom = "line",xlab = "",ylab = "",main = "Blip"),
-          qplot(t,mu.cor, geom = "line",xlab = "",ylab = "",main = "Corner"),
+plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
+          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
+          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
+          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
+          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
+          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
+          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
 		  nrow = 4,ncol = 2)
@@
 
-These are rescaled in the simulations to achieve the desired signal
-to noise ratios.
+These are rescaled in the simulations to achieve the desired
+signal-to-noise ratios (see the paper for a more detailed
+explanation).
 

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 
-```{r plot-variance-functions}
-plot(t,var1,xlab = "",ylab = "",ylim = c(0,1),type = "l",
-     main = "Constant variance function")
-plot(t,var2,xlab = "",ylab = "",type = "l",
-     main = "Triple exponential variance function")
-plot(t,var3,xlab = "",ylab = "",type = "l",main = "Doppler variance function")
-plot(t,var4,xlab = "",ylab = "",type = "l",main = "Bumps variance function")
-plot(t,var5,xlab = "",ylab = "",type = "l",main = "Clipped variance function")
+```{r plot-variance-functions, fig.height=7.5, fig.width=6}
+plot_grid(
+  qplot(t,var1,geom="line",xlab="",ylab="",main="Constant variance (v1)"),
+  qplot(t,var2,geom="line",xlab="",ylab="",main="Triple exponential (v2)"),
+  qplot(t,var3,geom="line",xlab="",ylab="",main="Doppler (v3)"),
+  qplot(t,var4,geom="line",xlab="",ylab="",main="Bumps (v4)"),
+  qplot(t,var5,geom="line",xlab="",ylab="",main="Clipped (v5)"),
+  nrow = 3,ncol = 2)
 ```

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 ---
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+```
 
@@
 
-Some code.
+Define the Spikes mean function.
 
-```{r}
+```{r define-spikes}
 mu.s = spike.f(t)
@@
 
-More code.
+Define the Bumps variance function.
 
-```{r}
+```{r define-bumps}
 pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
@@
   mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
+```
 
+Define the Doppler mean function.
+
+```{r define-doppler}
 mu.dop     = dop.f(t)
@@
 mu.dop.var = mu.dop.var - min(mu.dop.var)
+```
 
+Define the Angle mean function.
+
+```{r define-angle} 
 sig = ((2 * t + 0.5) * (t <= 0.15)) +
@@
 mu.ang = 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
+```
+Define the Block mean and variance functions.
 
-heavi = 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs = heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
-mu.hs = mu.hs - min(mu.hs)
-
+```{r define-block}
 pos    = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
@@
   mu.blk = mu.blk + (1 + sign(t - pos[j])) * (hgt[j]/2)
-
 mu.cblk = mu.blk
@@
 
-These plots show each of the mean functions used to generate the
-simulated data sets.
+These plots show each of the mean functions used in generating the
+Gaussian data sets.
 
@@
 
-These are rescaled in the simulations to achieve the desired
-signal-to-noise ratios (see the paper for a more detailed
-explanation).
+These plots show the variance functions used in generating the
+Gaussian data sets. In practice, these functions are rescaled in the
+simulations to achieve the desired signal-to-noise ratios (see the
+paper for a more detailed explanation).
 

### 2018-12-04 analysis/gaussian_signals.Rmd
wflow_publish(c("gaussian_signals.Rmd", "index.Rmd"))

@@
 ---
-title: "Mean and variance functions used to simulate Gaussian data"
+title: "Mean and variance functions used to simulate Gaussian data for mean-estimation experiments"
 author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"

### 2018-12-04 analysis/index.Rmd
wflow_publish(c("gaussian_signals.Rmd", "index.Rmd"))
Minor edits to home page.

@@
 
-2. [Estimating the variance function from Gaussian-distributed
-data](gaussvarest.html).
+2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean-estimation experiments.](gaussian_signals.html)
+
+3. [Estimating the variance function from Gaussian-distributed
+data.](gaussvarest.html)
 

### 2018-12-04 analysis/index.Rmd
Added shiny page to home.

@@
 
-2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean-estimation experiments.](gaussian_signals.html)
+2. [Plots of the mean and variance functions used to simulate Gaussian data for the mean estimation experiments.](gaussian_signals.html)
 
-3. [Estimating the variance function from Gaussian-distributed
+3. [Interactive (Shiny) plot for browsing results of Gaussian mean estimation experiments.](gauss_shiny.html)
+
+4. [Estimating the variance function from Gaussian-distributed
 data.](gaussvarest.html)

### 2018-12-06 analysis/gauss_shiny_setup.Rmd
wflow_publish("gauss_shiny_setup.Rmd")

--- 2018-12-02 analysis/shiny.Rmd
@@
 ---
-title: "Graphs"
-runtime: shiny
-output: html_document
+title: "Instructions for Interactive plot for exploring results of Gaussian mean estimation experimentsExplore"
+author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
+output: workflowr::wflow_html
 ---
+
+*Briefly explain here what this R Markdown document is for.*
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE)
+```
+
+```{r load-pkgs, echo=FALSE, warning=FALSE, message=FALSE}
+library(ggplot2)
+library(dplyr)
+library(rmarkdown)
+```
 
@@
 and 3, are presented here.
-
-Scenarios denote a combination of mean function, SNR and variance
-function. Specifically, each scenario is named as
-[mean_function].[SNR].[variance_function], where the abbreviations are
-given by:
-
-Mean function:  
-Spikes - sp  
-Bumps - bump  
-Blocks - blk  
-Angles - ang  
-Doppler - dop  
-Blip - blip  
-Corner - cor
-
-Variance function:  
-Constant function - v1  
-Triple exponential - v2  
-Doppler - v3  
-Bumps - v4  
-Clipped Blocks - v5
-
-On the other hand, we also ran a variety of methods in the simulation
-study. The methods are abbreviated as follows:
-
-EbayesThresh - ebayesthresh  
-BAMS - bams  
-BlockJS - blockjs 
-Neighblock - neighblock  
-SureShrink - sure  
-Bayesian Posterior Mean - postmean  
-TI thresholding - tithresh  
-SMASH - smash
-
-In addition, EbayeThresh, BAMS, BlockJS, Neighblock, Sureshrink and
-Bayesian Posterior Mean all assume homoskedastic noise and use the
-Symm8 basis by default. TI thresholding was run with both the
-homoskedastic (tithresh.homo) using the Symm8 (.s8) basis, as well as
-an estimated variance using RMAD (tithresh.rmad) and SMASH
-(tithresh.smash), with both the Haar (.haar) and the Symm8 (.s8)
-bases. In addition, TI thresholding was also run with the true
-variance provided (tithresh.true) using both the Haar (.haar) and the
-Symm8 (.s8) bases.
-
-We ran SMASH with the homoskedatic (smash.homo) assumption using both
-Haar (haar) and Symm8 (.s8). In addition, SMASH was also run with the
-variance jointly estimated, using either the JASH procedure
-(smash.jash) or the ASH procedure (smash.haar and smash.s8 for the two
-different bases). Paralleling TI thresholding, we also ran SMASH with
-the true variance provided (smash.true) using both the Haar (.haar)
-and the Symm8 (.s8) bases.
-
-```{r, echo=FALSE}
-library(ggplot2)
-library(dplyr)
-load("../output/dscr.RData")
-scenario_names = as.character(unique(res$scenario))
-method_names = as.character(unique(res$method))
-
-inputPanel(
-
-    # Create the checkboxes and select them all by default
-    checkboxGroupInput("scen.subset", "Choose Scenarios", 
-                        choices  = scenario_names,
-                        selected = "sp.1.v2"),
-
-    checkboxGroupInput("method.subset", "Choose Methods", 
-                        choices  = method_names,
-                        selected = method_names),
-
-    selectInput("criteria", "Choose Criteria", 
-                        choices  = "mise",
-                        selected = "mise")
-)
-
-renderPlot({
-  res.filter = filter(res,scenario %in% input$scen.subset &
-    method %in% input$method.subset)
-  print(input)
-  res.filter$value = res.filter[[input$criteria]]
-  ggplot(res.filter, aes(method, value, color = method)) +
-    geom_boxplot() + facet_grid(.~scenario) + 
-    theme(axis.ticks = element_blank(), axis.text.x = element_blank())
-})
-```

### 2018-12-06 analysis/gauss_shiny_setup.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))

@@
 ---
-title: "Instructions for Interactive plot for exploring results of Gaussian mean estimation experimentsExplore"
+title: "Instructions for running Shiny server to explore results of Gaussian mean estimation experiments"
 author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"

### 2018-12-06 analysis/gaussmeanest.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))

@@
 
-## Set up environment
+Set up environment
+------------------
 
@@
 
-## Load results
+Load results
+------------
 
@@
 
-## Simulated data with constant variances
+Simulated data with constant variances
+--------------------------------------
 
@@
 
-## Simulated data with heteroskedastic errors: "Spikes" mean signal and "Clipped Blocks" variance
+Simulated data with heteroskedastic errors: "Spikes" mean signal and "Clipped Blocks" variance
+----------------------------------------------------------------------------------------------
 
@@
 
-## Simulated data with heteroskedastic errors: "Corner" mean signal and "Doppler" variance
+Simulated data with heteroskedastic errors: "Corner" mean signal and "Doppler" variance
+---------------------------------------------------------------------------------------
 

### 2018-12-06 shiny/gauss_shiny.Rmd
I have an initial setup of the Shiny server document.

--- 2018-12-02 analysis/shiny.Rmd
@@
 ---
-title: "Graphs"
+title: "Interactive plot for exploring results of Gaussian mean estimation experiments"
 runtime: shiny
@@
 
-NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`
+*Briefly explain here what this R Markdown document is for.*
+
+```{r knitr-opts, include=FALSE}
+knitr::opts_chunk$set(comment = "#",collapse = TRUE)
+```
+
+```{r load-pkgs, warning=FALSE, message=FALSE}
+library(dplyr)
+library(ggplot2)
+library(rmarkdown)
+```
+
+Load results
+------------
+
+Load the results of the simulation experiments.
+
+```{r load-results}
+load("../output/dscr.RData")
+```
 
@@
 ```{r, echo=FALSE}
-library(ggplot2)
-library(dplyr)
-load("../output/dscr.RData")
 scenario_names = as.character(unique(res$scenario))
@@
 
-    # Create the checkboxes and select them all by default
+    # Create the checkboxes and select them all by default.
     checkboxGroupInput("scen.subset", "Choose Scenarios", 

### 2018-12-07 analysis/gauss_shiny_setup.Rmd
I have an initial setup of the Shiny server document.
Revised the Shiny plot; now I need to provide instructions for recreating it.

@@
 ```{r load-pkgs, echo=FALSE, warning=FALSE, message=FALSE}
+library(dplyr)
 library(ggplot2)
-library(dplyr)
+library(shiny)
 library(rmarkdown)
@@
 
-NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`
+```{r load-results, eval=FALSE}
+load("../output/dscr.RData")
+```
+
+NOTE: To launch the Shiny app, run:
+
+```{r launch-shiny eval=FALSE}
+run("../shiny/gauss_shiny.Rmd")
+```
 

### 2018-12-07 shiny/gauss_shiny.Rmd
Revised the Shiny plot; now I need to provide instructions for recreating it.

--- 2018-12-02 analysis/shiny.Rmd
@@
 
-NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`
+Below is a Shiny interactive plot that can be used to explore the
+results of the Gaussian mean estimation simulation study. In this
+simulation study, the signal denoising methods were compared in
+simulated data sets generated with a variety of mean and variance
+functions, and with different signal-to-noise ratios.
 
-The following code generates an RShiny app which displays boxplots of
-MISEs from the full simulation study comparing SMASH to other
-wavelet-based methods for denoising Gaussian data. As mentioned in the
-companion paper, the results for a variety of test functions (both
-mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1
-and 3, are presented here.
+See the text below for more details on how to interpret these results.
 
-Scenarios denote a combination of mean function, SNR and variance
-function. Specifically, each scenario is named as
-[mean_function].[SNR].[variance_function], where the abbreviations are
-given by:
+```{r create-shiny-plot, echo=FALSE, message=FALSE, warning=FALSE}
+# Load the dplyr, ggplot and rmarkdown packages.
+library(dplyr)
+library(ggplot2)
+library(cowplot)
+library(rmarkdown)
 
-Mean function:  
-Spikes - sp  
-Bumps - bump  
-Blocks - blk  
-Angles - ang  
-Doppler - dop  
-Blip - blip  
-Corner - cor
+# Load the results of the simulation experiments.
+load("../output/dscr.RData")
 
-Variance function:  
-Constant function - v1  
-Triple exponential - v2  
-Doppler - v3  
-Bumps - v4  
-Clipped Blocks - v5
-
-On the other hand, we also ran a variety of methods in the simulation
-study. The methods are abbreviated as follows:
-
-EbayesThresh - ebayesthresh  
-BAMS - bams  
-BlockJS - blockjs 
-Neighblock - neighblock  
-SureShrink - sure  
-Bayesian Posterior Mean - postmean  
-TI thresholding - tithresh  
-SMASH - smash
-
-In addition, EbayeThresh, BAMS, BlockJS, Neighblock, Sureshrink and
-Bayesian Posterior Mean all assume homoskedastic noise and use the
-Symm8 basis by default. TI thresholding was run with both the
-homoskedastic (tithresh.homo) using the Symm8 (.s8) basis, as well as
-an estimated variance using RMAD (tithresh.rmad) and SMASH
-(tithresh.smash), with both the Haar (.haar) and the Symm8 (.s8)
-bases. In addition, TI thresholding was also run with the true
-variance provided (tithresh.true) using both the Haar (.haar) and the
-Symm8 (.s8) bases.
-
-We ran SMASH with the homoskedatic (smash.homo) assumption using both
-Haar (haar) and Symm8 (.s8). In addition, SMASH was also run with the
-variance jointly estimated, using either the JASH procedure
-(smash.jash) or the ASH procedure (smash.haar and smash.s8 for the two
-different bases). Paralleling TI thresholding, we also ran SMASH with
-the true variance provided (smash.true) using both the Haar (.haar)
-and the Symm8 (.s8) bases.
-
-```{r, echo=FALSE}
-library(ggplot2)
-library(dplyr)
-load("../output/dscr.RData")
+# Set up the Shiny plot.
 scenario_names = as.character(unique(res$scenario))
@@
 
-inputPanel(
-
-    # Create the checkboxes and select them all by default
-    checkboxGroupInput("scen.subset", "Choose Scenarios", 
-                        choices  = scenario_names,
-                        selected = "sp.1.v2"),
-
-    checkboxGroupInput("method.subset", "Choose Methods", 
-                        choices  = method_names,
-                        selected = method_names),
-
-    selectInput("criteria", "Choose Criteria", 
-                        choices  = "mise",
-                        selected = "mise")
-)
-
+# Render the webpage with the interactive plot.
 renderPlot({
@@
   print(input)
-  res.filter$value = res.filter[[input$criteria]]
-  ggplot(res.filter, aes(method, value, color = method)) +
-    geom_boxplot() + facet_grid(.~scenario) + 
-    theme(axis.ticks = element_blank(), axis.text.x = element_blank())
+  res.filter$value = res.filter[["mise"]]
+  ggplot(res.filter,aes(x = method,y = value)) +
+    geom_boxplot() +
+    facet_grid(.~ scenario) +
+    labs(y = "error (MISE)") +
+    theme(axis.text.x = element_text(angle = 45,hjust = 1),
+	      axis.line = element_blank())
 })
+inputPanel(
+  checkboxGroupInput("scen.subset","scenario",choices = scenario_names,
+                     selected = "sp.1.v2"),
+  checkboxGroupInput("method.subset","method",choices = method_names,
+                     selected = method_names))
 ```
+
+The boxplots above summarize the error (specifically, mean of the
+integrated squared errors, or MISE) in the mean estimate when applying
+different methods in to different simulation scenarios.
+
+Each simulation scenario corresponds to a combination of a mean
+function, variance function, and signal-to-noise function used to
+simulated the Gaussian-distributed data. In the Shiny plot above, a
+scenario is labeled as "mean.SNR.variance", in which "mean",
+"variance" and "SNR" refer to the mean function, variance function and
+signal-to-noise ratio. See [here](gaussian_signal.html) for plots of
+the mean and variance functions.
+
+These are the different mean functions we used in the simulations:
+
+Spikes (sp)<br>
+Bumps (bump)<br>
+Blocks (blk)<br>
+Angles (ang)<br>
+Doppler (dop)<br>
+Blip (blip)<br>
+Corner (cor)
+
+And these are the variance functions we used:
+
+Constant function (v1)<br>
+Triple exponential (v2)<br>
+Doppler (v3)<br>
+Bumps (v4)<br>
+Clipped Blocks (v5)
+
+We used signal-to-noise ratios of 1 and 3.
+
+These are the methods we compared:
+
+EbayesThresh (ebayesthresh)
+BAMS (bams)
+BlockJS - blockjs 
+Neighblock (neighblock)
+SureShrink (sure)
+Bayesian Posterior Mean (postmean)
+TI thresholding (tithresh)
+SMASH (smash)
+
+Most of  these methods assume homoskedastic noise, and use the
+Symm8 basis by default. TI thresholding was run with both the
+homoskedastic ("tithresh.homo") using the Symm8 (.s8) basis, as well as
+with variance estimated variance using either RMAD ("tithresh.rmad") or SMASH
+("tithresh.smash"). TI thresholding was also run with the true
+variance provided ("tithresh.true").
+
+As for SMASH, we ran this method with the homoskedatic assumption
+("smash.homo"), and when the variance was estimated. For variance
+estimation in SMASH, we compared two approaches: JASH ("smash.jash")
+and the ASH-based procedure ("smash.haar" and" smash.s8" for the two
+different bases). We also evaluated SMASH when it was provided with
+the ground-truth variance.

### 2018-12-07 analysis/gauss_shiny_setup.Rmd
wflow_publish("gauss_shiny_setup.Rmd")

--- 2018-12-06 analysis/gauss_shiny_setup.Rmd
@@
 
-*Briefly explain here what this R Markdown document is for.*
+Here we give instructions for starting the Shiny server which will
+create an interactive plot from the results of the Gaussian mean
+estimation simulation study.
 
@@
 
-```{r load-pkgs, echo=FALSE, warning=FALSE, message=FALSE}
+First, you need make sure that the following R packages are installed
+on your computer: dplyr, ggplot2, cowplot, shiny and rmarkdown. See
+the "Session Info" at the bottom for the versions of the R packages we
+used.  Once you have installed these packages, run this code to verify
+that the packages are installed successfully:
+
+```{r load-pkgs, warning=FALSE, message=FALSE}
+library(dplyr)
 library(ggplot2)
-library(dplyr)
+library(cowplot)
+library(shiny)
 library(rmarkdown)
@@
 
-NOTE: To launch the Shiny app, run `rmarkdown::run("shiny.Rmd")`
+Now you are ready to create the Shiny server with this command:
 
-The following code generates an RShiny app which displays boxplots of
-MISEs from the full simulation study comparing SMASH to other
-wavelet-based methods for denoising Gaussian data. As mentioned in the
-companion paper, the results for a variety of test functions (both
-mean and variance functions) and 2 signal-to-noise ratios (SNRs), 1
-and 3, are presented here.
+```{r launch-shiny, eval=FALSE}
+rmarkdown::run("../shiny/gauss_shiny.Rmd")
+```
+
+The interactive plot will be launched in your Web browser, or in an
+RStudio panel, depending on whether you are using R or RStudio.

### 2018-12-07 shiny/gauss_shiny.Rmd
A small revision to the Shiny plot accompanying text.

@@
 ```{r create-shiny-plot, echo=FALSE, message=FALSE, warning=FALSE}
-# Load the dplyr, ggplot and rmarkdown packages.
+# Load the packages.
 library(dplyr)
@@
 library(rmarkdown)
+library(shiny)
 
@@
 
-Spikes (sp)<br>
-Bumps (bump)<br>
-Blocks (blk)<br>
-Angles (ang)<br>
-Doppler (dop)<br>
-Blip (blip)<br>
-Corner (cor)
+1. Spikes (sp)
+2. Bumps (bump)
+3. Blocks (blk)
+4. Angles (ang)
+5. Doppler (dop)
+6. Blip (blip)
+7. Corner (cor)
 
@@
 
-Constant function (v1)<br>
-Triple exponential (v2)<br>
-Doppler (v3)<br>
-Bumps (v4)<br>
-Clipped Blocks (v5)
+1. Constant function (v1)
+2. Triple exponential (v2)
+3. Doppler (v3)
+4. Bumps (v4)
+5. Clipped Blocks (v5)
 

### 2018-12-10 analysis/gaussmeanest.Rmd
Added pointers to dsc/README in relevant R Markdown files.

@@
 Since the simulation experiments are computationally intensive, they
-were implemented separately (see the "dsc" directory in this git
-repository), and here we only create plots to summarize the results of
+were implemented separately. (For instructions on re-running these
+simulation experiments, see the README in the "dsc" directory of the
+git repository). Here we create plots to summarize the results of
 these experiments.

### 2018-12-13 analysis/spikesdemo.Rmd
Adjusted setup steps in a few of the R Markdown files.
Moved around & deleted a bunch of files.

@@
 library(cowplot)
-source("../code/misc.R")
+source("../code/spikesdemo.functions.R")
 ```

### 2018-12-13 code/ethanol.R

@@ -1,40 +1,0 @@
-# An illustration of "smoothing via adaptive shrinkage" applied to the
-# Ethanol data set.
-
-# SET UP ENVIRONMENT
-# ------------------
-# Load the lattice and smashr packages. The lattice package is loaded
-# only for the Ethanol data set.
-library(smashr)
-library(lattice)
-
-# PREPARE DATA
-# ------------
-# Prepare the Ethanol data for analysis with smash.
-cat("Preparing data.\n")
-data(ethanol)
-x.ini = sort(ethanol$E)
-y.ini = ethanol$NOx[order(ethanol$E)]
-
-x = unique(x.ini)
-y = 0
-for(i in 1:length(x))
-  y[i] = median(y.ini[x.ini == x[i]])
-
-y.exp = c(y,y[length(y):(2*length(y)-128+1)])
-y.final = c(y.exp, y.exp[length(y.exp):1])
-
-# RUN SMASH
-# ---------
-# Apply smash to the Ethanol data set.
-cat("Running smash.\n")
-y.est     = smash.gaus(y.final)
-y.est     = y.est[1:length(y)]
-y.var.est = smash.gaus(y.final,v.est = TRUE)
-y.var.est = y.var.est[1:length(y)]
-
-# SUMMARIZE RESULTS
-# -----------------
-plot(x,y,ylim = c(-1,5))
-lines(x,y.est,col = 2)
-

### 2018-12-13 dsc/run_dsc.R

@@ -1,5 +1,6 @@
-# TO DO: Explain what this script does, and how to use it.
-library(dscr)
+# This R script implements the "Gaussian mean estimation" simulations
+# for the SMASH paper. For instructions on how to run this code, see
+# the accompanying README.
 library(AlgDesign)
 library(EbayesThresh)
 library(wavethresh)

### 2018-12-18 analysis/gauss_shiny_setup.Rmd
Added link to Shiny package.

@@
 ---
-title: "Instructions for running Shiny server to explore results of Gaussian mean estimation experiments"
+title: "Instructions for running Shiny app to explore results of Gaussian mean estimation experiments"
 author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
@@
 
-Here we give instructions for starting the Shiny server which will
-create an interactive plot from the results of the Gaussian mean
+Here we give instructions for starting the [Shiny app][shiny] which
+will create an interactive plot from the results of the Gaussian mean
 estimation simulation study.
@@
 
-Now you are ready to create the Shiny server with this command:
+Now you are ready to launch the Shiny app with this command:
 
@@
 RStudio panel, depending on whether you are using R or RStudio.
+
+[shiny]: https://cran.r-project.org/package=shiny

### 2018-12-19 analysis/poisson_plots.Rmd
Working on R Markdown for Poisson results.

---
title: "Add title here"
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This produces the plots for the Poisson simulations in the paper.

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

Set up environment
------------------

```{r}
library(vioplot)
source("vioplot_col.R")
load("../output/pois.RData")
```

plot the bursts test function

```{r}
n=1024
t=1:n/n
I_1 <- exp(-(abs(t-0.2)/0.01)^1.2)*(t<=0.2) +
     exp(-(abs(t-0.2)/0.03)^1.2)*(t>0.2)
I_2 <- exp(-(abs(t-0.3)/0.01)^1.2)*(t<=0.3) +
	 exp(-(abs(t-0.3)/0.03)^1.2)*(t>0.3);
I_3 <- exp(-(abs(t-0.4)/0.01)^1.2)*(t<=0.4) +
	 exp(-(abs(t-0.4)/0.03)^1.2)*(t>0.4);
mu.bur <- 2.99/4.51804*(4*I_1+3*I_2+4.5*I_3)
plot(mu.bur, type = 'l', xlab = "position", ylab = "intensity")
```

```{r}
mise.hf.ti.r.bur.1 =
    colMeans(matrix(c(mise.hf.ti.r.4.bur.1, mise.hf.ti.r.5.bur.1,
                      mise.hf.ti.r.6.bur.1, mise.hf.ti.r.7.bur.1),
                    byrow = TRUE, nr = 4))
mise.hf.ti.r.bur.8 = colMeans(matrix(c(mise.hf.ti.r.4.bur.8,
    mise.hf.ti.r.5.bur.8, mise.hf.ti.r.6.bur.8, mise.hf.ti.r.7.bur.8),
    byrow = TRUE, nr = 4))
```

```{r}
par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1),
    mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.bur.1, mise.BMSM.bur.1, mise.hf.ti.r.bur.1,
            horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"),
            col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.bur.1), lty = 3, col = 3)
```

```{r}
par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1),
    mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.bur.8, mise.BMSM.bur.8, mise.hf.ti.r.bur.8,
	horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"),
	col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.bur.8), lty = 3, col = 3)
```

#########################################
#To obtain violin plots for all test functions/intensities (most figures not shown in paper)

mise.hf.ti.r.s.1 = colMeans(matrix(c(mise.hf.ti.r.4.s.1, mise.hf.ti.r.5.s.1, mise.hf.ti.r.6.s.1, mise.hf.ti.r.7.s.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.s.8 = colMeans(matrix(c(mise.hf.ti.r.4.s.8, mise.hf.ti.r.5.s.8, mise.hf.ti.r.6.s.8, mise.hf.ti.r.7.s.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.s.128 = colMeans(matrix(c(mise.hf.ti.r.4.s.128, mise.hf.ti.r.5.s.128, mise.hf.ti.r.6.s.128, mise.hf.ti.r.7.s.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.s.1, mise.BMSM.s.1, mise.hf.ti.r.s.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.s.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.s.8, mise.BMSM.s.8, mise.hf.ti.r.s.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.s.128, mise.BMSM.s.128, mise.hf.ti.r.s.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

mise.hf.ti.r.ang.1 = colMeans(matrix(c(mise.hf.ti.r.4.ang.1, mise.hf.ti.r.5.ang.1, mise.hf.ti.r.6.ang.1, mise.hf.ti.r.7.ang.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.ang.8 = colMeans(matrix(c(mise.hf.ti.r.4.ang.8, mise.hf.ti.r.5.ang.8, mise.hf.ti.r.6.ang.8, mise.hf.ti.r.7.ang.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.ang.128 = colMeans(matrix(c(mise.hf.ti.r.4.ang.128, mise.hf.ti.r.5.ang.128, mise.hf.ti.r.6.ang.128, mise.hf.ti.r.7.ang.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.ang.1, mise.BMSM.ang.1, mise.hf.ti.r.ang.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.ang.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.ang.8, mise.BMSM.ang.8, mise.hf.ti.r.ang.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.ang.128, mise.BMSM.ang.128, mise.hf.ti.r.ang.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

mise.hf.ti.r.bur.1 = colMeans(matrix(c(mise.hf.ti.r.4.bur.1, mise.hf.ti.r.5.bur.1, mise.hf.ti.r.6.bur.1, mise.hf.ti.r.7.bur.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.bur.8 = colMeans(matrix(c(mise.hf.ti.r.4.bur.8, mise.hf.ti.r.5.bur.8, mise.hf.ti.r.6.bur.8, mise.hf.ti.r.7.bur.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.bur.128 = colMeans(matrix(c(mise.hf.ti.r.4.bur.128, mise.hf.ti.r.5.bur.128, mise.hf.ti.r.6.bur.128, mise.hf.ti.r.7.bur.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.bur.1, mise.BMSM.bur.1, mise.hf.ti.r.bur.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.bur.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.bur.8, mise.BMSM.bur.8, mise.hf.ti.r.bur.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.bur.128, mise.BMSM.bur.128, mise.hf.ti.r.bur.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

mise.hf.ti.r.cb.1 = colMeans(matrix(c(mise.hf.ti.r.4.cb.1, mise.hf.ti.r.5.cb.1, mise.hf.ti.r.6.cb.1, mise.hf.ti.r.7.cb.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.cb.8 = colMeans(matrix(c(mise.hf.ti.r.4.cb.8, mise.hf.ti.r.5.cb.8, mise.hf.ti.r.6.cb.8, mise.hf.ti.r.7.cb.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.cb.128 = colMeans(matrix(c(mise.hf.ti.r.4.cb.128, mise.hf.ti.r.5.cb.128, mise.hf.ti.r.6.cb.128, mise.hf.ti.r.7.cb.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.cb.1, mise.BMSM.cb.1, mise.hf.ti.r.cb.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.cb.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.cb.8, mise.BMSM.cb.8, mise.hf.ti.r.cb.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.cb.128, mise.BMSM.cb.128, mise.hf.ti.r.cb.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

mise.hf.ti.r.b.1 = colMeans(matrix(c(mise.hf.ti.r.4.b.1, mise.hf.ti.r.5.b.1, mise.hf.ti.r.6.b.1, mise.hf.ti.r.7.b.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.8 = colMeans(matrix(c(mise.hf.ti.r.4.b.8, mise.hf.ti.r.5.b.8, mise.hf.ti.r.6.b.8, mise.hf.ti.r.7.b.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.b.128 = colMeans(matrix(c(mise.hf.ti.r.4.b.128, mise.hf.ti.r.5.b.128, mise.hf.ti.r.6.b.128, mise.hf.ti.r.7.b.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.b.1, mise.BMSM.b.1, mise.hf.ti.r.b.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.b.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.b.8, mise.BMSM.b.8, mise.hf.ti.r.b.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.b.128, mise.BMSM.b.128, mise.hf.ti.r.b.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

mise.hf.ti.r.hs.1 = colMeans(matrix(c(mise.hf.ti.r.4.hs.1, mise.hf.ti.r.5.hs.1, mise.hf.ti.r.6.hs.1, mise.hf.ti.r.7.hs.1), byrow = TRUE, nr = 4))
mise.hf.ti.r.hs.8 = colMeans(matrix(c(mise.hf.ti.r.4.hs.8, mise.hf.ti.r.5.hs.8, mise.hf.ti.r.6.hs.8, mise.hf.ti.r.7.hs.8), byrow = TRUE, nr = 4))
mise.hf.ti.r.hs.128 = colMeans(matrix(c(mise.hf.ti.r.4.hs.128, mise.hf.ti.r.5.hs.128, mise.hf.ti.r.6.hs.128, mise.hf.ti.r.7.hs.128), byrow = TRUE, nr = 4))

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.hs.1, mise.BMSM.hs.1, mise.hf.ti.r.hs.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)
abline(v = median(mise.ash.hs.1), lty = 3, col = 3)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.hs.8, mise.BMSM.hs.8, mise.hf.ti.r.hs.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
vioplot.col(mise.ash.hs.128, mise.BMSM.hs.128, mise.hf.ti.r.hs.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
title(xlab = "MISE", line = 4)

### 2018-12-19 analysis/poisson_tables.Rmd
Working on R Markdown for Poisson results.

---
title: "Title goes here."
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This script produces supplementary tables for Poisson simulations.

```{r}
library(xtable)

load("../output/pois.RData")

tex.row.names <- c("SMASH",
                   "BMSM",
                   "BMMIM",
                   "Haar-Fisz",
                   "Anscombe",
                   "Haar thresholds",
                   "L1_penalty"
)

tex.col.names <- c("intensity (0.01,3)",
                   "intensity (1/8,8)",
                   "intensity (1/128,128)")

mise.s.1.table=mise.s.1[c(1,2,3,4,6,7,8)]
mise.s.8.table=mise.s.8[c(1,2,3,4,6,7,8)]
mise.s.128.table=mise.s.128[c(1,2,3,4,6,7,8)]

mise.ang.1.table=mise.ang.1[c(1,2,3,4,6,7,8)]
mise.ang.8.table=mise.ang.8[c(1,2,3,4,6,7,8)]
mise.ang.128.table=mise.ang.128[c(1,2,3,4,6,7,8)]

mise.bur.1.table=mise.bur.1[c(1,2,3,4,6,7,8)]
mise.bur.8.table=mise.bur.8[c(1,2,3,4,6,7,8)]
mise.bur.128.table=mise.bur.128[c(1,2,3,4,6,7,8)]

mise.cb.1.table=mise.cb.1[c(1,2,3,4,6,7,8)]
mise.cb.8.table=mise.cb.8[c(1,2,3,4,6,7,8)]
mise.cb.128.table=mise.cb.128[c(1,2,3,4,6,7,8)]

mise.b.1.table=mise.b.1[c(1,2,3,4,6,7,8)]
mise.b.8.table=mise.b.8[c(1,2,3,4,6,7,8)]
mise.b.128.table=mise.b.128[c(1,2,3,4,6,7,8)]

mise.hs.1.table=mise.hs.1[c(1,2,3,4,6,7,8)]
mise.hs.8.table=mise.hs.8[c(1,2,3,4,6,7,8)]
mise.hs.128.table=mise.hs.128[c(1,2,3,4,6,7,8)]

mise.s.table=cbind(mise.s.1.table,
mise.s.8.table,
mise.s.128.table
)

mise.ang.table <- cbind(mise.ang.1.table,
mise.ang.8.table,
mise.ang.128.table
)

mise.bur.table=cbind(mise.bur.1.table,
mise.bur.8.table,
mise.bur.128.table
)

mise.cb.table=cbind(mise.cb.1.table,
mise.cb.8.table,
mise.cb.128.table
)

mise.b.table=cbind(mise.b.1.table,
mise.b.8.table,
mise.b.128.table
)

mise.hs.table=cbind(mise.hs.1.table,
mise.hs.8.table,
mise.hs.128.table
)

rownames(mise.ang.table)=tex.row.names
colnames(mise.ang.table)=tex.col.names
rownames(mise.b.table)=tex.row.names
colnames(mise.b.table)=tex.col.names
rownames(mise.cb.table)=tex.row.names
colnames(mise.cb.table)=tex.col.names
rownames(mise.s.table)=tex.row.names
colnames(mise.s.table)=tex.col.names
rownames(mise.hs.table)=tex.row.names
colnames(mise.hs.table)=tex.col.names
rownames(mise.bur.table)=tex.row.names
colnames(mise.bur.table)=tex.col.names
```

```{r, results="asis"}
print(xtable(mise.s.table,caption="Comparison of methods for denoising Poisson data for the ``Spikes'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_sp",digits=2),type = "html")
```

```{r, results="asis"}
print(xtable(mise.ang.table,caption="Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_ang",digits=2),type = "html")
```

```{r, results="asis"}
print(xtable(mise.hs.table,caption="Comparison of methods for denoising Poisson data for the ``Heavisine'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_hs",digits=2),type = "html")
```

```{r, results="asis"}
print(xtable(mise.bur.table,caption="Comparison of methods for denoising Poisson data for the ``Bursts'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_bur",digits=2),type = "html")
```

```{r, results="asis"}
print(xtable(mise.cb.table,caption="Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_cb",digits=2),type = "html")
```

```{r, results="asis"}
print(xtable(mise.b.table,caption="Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_b",digits=2),type = "html")
```

### 2018-12-19 analysis/poisson_sims/table_pois.R

@@ -1,129 +1,0 @@
-#This script produces supplementary tables for Poisson simulations
-
-library(xtable)
-
-load("res_paper/res_pois.RData")
-
-scale.baseline = function(x) x/x[1]
-
-tex.row.names=c("SMASH",
-                "BMSM",
-                "BMMIM",
-                "Haar-Fisz",
-                "Anscombe",
-                "Haar thresholds",
-                "L1_penalty"
-)
-
-tex.col.names=c("intensity (0.01,3)","intensity (1/8,8)","intensity (1/128,128)")
-
-
-# mise.s.1.table=mise.s.1[c(1,4,8,7,9,5,3,2)]
-# mise.s.8.table=mise.s.8[c(1,4,8,7,9,5,3,2)]
-# mise.s.128.table=mise.s.128[c(1,4,8,7,9,5,3,2)]
-# 
-# mise.ang.1.table=mise.ang.1[c(1,4,8,7,9,5,3,2)]
-# mise.ang.8.table=mise.ang.8[c(1,4,8,7,9,5,3,2)]
-# mise.ang.128.table=mise.ang.128[c(1,4,8,7,9,5,3,2)]
-# 
-# mise.bur.1.table=mise.bur.1[c(1,4,8,7,9,5,3,2)]
-# mise.bur.8.table=mise.bur.8[c(1,4,8,7,9,5,3,2)]
-# mise.bur.128.table=mise.bur.128[c(1,4,8,7,9,5,3,2)]
-# 
-# mise.cb.1.table=mise.cb.1[c(1,4,8,7,9,5,3,2)]
-# mise.cb.8.table=mise.cb.8[c(1,4,8,7,9,5,3,2)]
-# mise.cb.128.table=mise.cb.128[c(1,4,8,7,9,5,3,2)]
-# 
-# mise.b.1.table=mise.b.1[c(1,4,8,7,9,5,3,2)]
-# mise.b.8.table=mise.b.8[c(1,4,8,7,9,5,3,2)]
-# mise.b.128.table=mise.b.128[c(1,4,8,7,9,5,3,2)]
-# 
-# mise.hs.1.table=mise.hs.1[c(1,4,8,7,9,5,3,2)]
-# mise.hs.8.table=mise.hs.8[c(1,4,8,7,9,5,3,2)]
[…]

### 2018-12-20 analysis/poisson.Rmd
Working on poisson analysis.

---
title: "Title goes here."
author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
output: workflowr::wflow_html
---

This script produces supplementary tables for Poisson simulations.

*Explain which set of results correspond to the plots given in the main
text.*

```{r knitr-opts, include=FALSE}
knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
```

Analysis settings
-----------------

We will extract the results from these methods:

```{r selected-methods}
methods <- c("ash","BMSM","haarfisz_R")
```

Specify the row and column names for the tables:

```{r table-row-and-col-names}
table.row.names <- c("SMASH","BMSM","Haar-Fisz")
table.col.names <- c("intensity (0.01,3)","intensity (1/8,8)",
                     "intensity (1/128,128)")
```

Set up environment
------------------

*Add text here.*

```{r load-pkgs, message=FALSE, warning=FALSE}
library(ggplot2)
library(cowplot)
library(xtable)
```

Load results
------------

Load the results of the simulation experiments.

```{r load-results}
load("../output/pois.RData")
```

## Spikes data

Summarize the results from the Spikes simulations in a table.

Comparison of methods for denoising Poisson data for the "Spikes"
test function for 3 different (min,max) intensities ((0.01,3),
(1/8,8), (1/128,128)). Performance is measured using MISE over 100
independent datasets, with smaller values indicating better
performance. Values colored in red indicates the smallest MISE amongst
all methods for a given (min, max) intensity.

```{r spikes-table, results="asis"}
mise.s.table   <- cbind(mise.s.1[methods],
                        mise.s.8[methods],
                        mise.s.128[methods])
rownames(mise.s.table) <- table.row.names
colnames(mise.s.table) <- table.col.names
print(xtable(mise.s.table),type = "html")
```

Summarize the results from the Spikes simulations in combined violin
and boxplots.

```{r spikes-violin-plots, fig.height=5, fig.width=7}
mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
                                     mise.hf.ti.r.5.s.1,
                                     mise.hf.ti.r.6.s.1,
	  		                         mise.hf.ti.r.7.s.1))
mise.hf.ti.r.s.8   <- colMeans(rbind(mise.hf.ti.r.4.s.8,
					                 mise.hf.ti.r.5.s.8,
                                     mise.hf.ti.r.6.s.8,
						  	         mise.hf.ti.r.7.s.8))
mise.hf.ti.r.s.128 <- colMeans(rbind(mise.hf.ti.r.4.s.128,
									 mise.hf.ti.r.5.s.128,
                                     mise.hf.ti.r.6.s.128,
									 mise.hf.ti.r.7.s.128))
p <- ggplot(pdat1,aes(x = method,y = mise,fill = method.type)) +
     geom_violin(fill = "skyblue",color = "skyblue") +
     geom_boxplot(width = 0.15,outlier.shape = NA) +
     scale_y_continuous(breaks = seq(6,16,2)) +
     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
                       guide = FALSE) +
     coord_flip() +
     labs(x = "",y = "MISE") +
     theme(axis.line = element_blank(),
           axis.ticks.y = element_blank())
```

Combine the results of the simulation experiments into several larger
tables.

```{r get-spikes-results}
mise.ang.table <- cbind(mise.ang.1[methods],
                        mise.ang.8[methods],
                        mise.ang.128[methods])
mise.bur.table <- cbind(mise.bur.1[methods],
                        mise.bur.8[methods],
                        mise.bur.128[methods])
mise.cb.table  <- cbind(mise.cb.1[methods],
                        mise.cb.8[methods],
                        mise.cb.128[methods])
mise.b.table   <- cbind(mise.b.1[methods],
                        mise.b.8[methods],
                        mise.b.128[methods])
mise.hs.table  <- cbind(mise.hs.1[methods],
                        mise.hs.8[methods],
                        mise.hs.128[methods])
rownames(mise.ang.table) <- table.row.names
rownames(mise.b.table)   <- table.row.names
rownames(mise.cb.table)  <- table.row.names
rownames(mise.hs.table)  <- table.row.names
rownames(mise.bur.table) <- table.row.names
colnames(mise.ang.table) <- table.col.names
colnames(mise.b.table)   <- table.col.names
colnames(mise.cb.table)  <- table.col.names
colnames(mise.hs.table)  <- table.col.names
colnames(mise.bur.table) <- table.col.names
```

### Angles data

```{r, results="asis"}
print(xtable(mise.ang.table,caption="Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_ang",digits=2),type = "html")
```

### Heavisine data

```{r, results="asis"}
print(xtable(mise.hs.table,caption="Comparison of methods for denoising Poisson data for the ``Heavisine'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_hs",digits=2),type = "html")
```

### Bursts data

```{r, results="asis"}
print(xtable(mise.bur.table,caption="Comparison of methods for denoising Poisson data for the ``Bursts'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_bur",digits=2),type = "html")
```

### Clipped Blocks data

```{r, results="asis"}
print(xtable(mise.cb.table,caption="Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_cb",digits=2),type = "html")
```

### Bumps data

```{r, results="asis"}
print(xtable(mise.b.table,caption="Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)). Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance. Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_b",digits=2),type = "html")
```

### 2018-12-20 analysis/poisson_plots.Rmd
Working on poisson analysis.

@@
 load("../output/pois.RData")
-```
-
-plot the bursts test function
-
-```{r}
-n=1024
-t=1:n/n
-I_1 <- exp(-(abs(t-0.2)/0.01)^1.2)*(t<=0.2) +
-     exp(-(abs(t-0.2)/0.03)^1.2)*(t>0.2)
-I_2 <- exp(-(abs(t-0.3)/0.01)^1.2)*(t<=0.3) +
-	 exp(-(abs(t-0.3)/0.03)^1.2)*(t>0.3);
-I_3 <- exp(-(abs(t-0.4)/0.01)^1.2)*(t<=0.4) +
-	 exp(-(abs(t-0.4)/0.03)^1.2)*(t>0.4);
-mu.bur <- 2.99/4.51804*(4*I_1+3*I_2+4.5*I_3)
-plot(mu.bur, type = 'l', xlab = "position", ylab = "intensity")
 ```
@@
 
-#########################################
-#To obtain violin plots for all test functions/intensities (most figures not shown in paper)
-
-mise.hf.ti.r.s.1 = colMeans(matrix(c(mise.hf.ti.r.4.s.1, mise.hf.ti.r.5.s.1, mise.hf.ti.r.6.s.1, mise.hf.ti.r.7.s.1), byrow = TRUE, nr = 4))
-mise.hf.ti.r.s.8 = colMeans(matrix(c(mise.hf.ti.r.4.s.8, mise.hf.ti.r.5.s.8, mise.hf.ti.r.6.s.8, mise.hf.ti.r.7.s.8), byrow = TRUE, nr = 4))
-mise.hf.ti.r.s.128 = colMeans(matrix(c(mise.hf.ti.r.4.s.128, mise.hf.ti.r.5.s.128, mise.hf.ti.r.6.s.128, mise.hf.ti.r.7.s.128), byrow = TRUE, nr = 4))
-
-par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
-vioplot.col(mise.ash.s.1, mise.BMSM.s.1, mise.hf.ti.r.s.1, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1),
+mgp = c(3, 1.5, 0))
+vioplot.col(mise.ash.s.1, mise.BMSM.s.1, mise.hf.ti.r.s.1, horizontal = TRUE,
+  names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
 title(xlab = "MISE", line = 4)
@@
 
-par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
-vioplot.col(mise.ash.s.8, mise.BMSM.s.8, mise.hf.ti.r.s.8, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1),
+mgp = c(3, 1.5, 0))
+vioplot.col(mise.ash.s.8, mise.BMSM.s.8, mise.hf.ti.r.s.8,
+horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col =
+c("magenta", "red", "red"))
 title(xlab = "MISE", line = 4)
 
-par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1), mgp = c(3, 1.5, 0))
-vioplot.col(mise.ash.s.128, mise.BMSM.s.128, mise.hf.ti.r.s.128, horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+par(cex.axis = 2, cex.lab = 2, cex.sub = 2, mar = c(6.1, 12.1, 4.1, 2.1),
+ mgp = c(3, 1.5, 0))
+vioplot.col(mise.ash.s.128, mise.BMSM.s.128, mise.hf.ti.r.s.128,
+horizontal = TRUE, names = c("SMASH", "BMSM", "Haar-Fisz"),
+col = c("magenta", "red", "red"))
  title(xlab = "MISE", line = 4)

### 2018-12-20 analysis/poisson.Rmd
Misc. revisions to READMEs and documentation.

@@
 									 mise.hf.ti.r.7.s.128))
-p <- ggplot(pdat1,aes(x = method,y = mise,fill = method.type)) +
+n     <- length(mise.ash.s.1)
+pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
+ 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
+p1    <- 
+vioplot.col(mise.ash.s.1, mise.BMSM.s.1, mise.hf.ti.r.s.1, horizontal = TRUE,
+  names = c("SMASH", "BMSM", "Haar-Fisz"), col = c("magenta", "red", "red"))
+title(xlab = "MISE", line = 4)
+abline(v = median(mise.ash.s.1), lty = 3, col = 3)
+
+p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
       geom_violin(fill = "skyblue",color = "skyblue") +
       geom_boxplot(width = 0.15,outlier.shape = NA) +
-     scale_y_continuous(breaks = seq(6,16,2)) +
-     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
-                       guide = FALSE) +
-     coord_flip() +
+      coord_flip()
       labs(x = "",y = "MISE") +

### 2018-12-20 analysis/index.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))
I have an initial setup of the Shiny server document.
wflow_publish("index.Rmd")

@@
 
-3. [Interactive (Shiny) plot for browsing results of Gaussian mean estimation experiments.](gauss_shiny.html)
+3. [Interactive ("Shiny") plot for exploring results of Gaussian mean estimation experiments.](gauss_shiny_setup.html)
 
@@
 
-3. Poisson-distributed data.
+5. [Summary of results from Poisson simulations.](poisson.html)
 
@@
 
-See here for the source repository. This is what you will find in the
-repository:
+## What's included in the git repository
 
-*Fill out this section.*
+See [here][gtexresults] for the source repository. This is what
+you will find in the repository:
+
+```
+├── analysis
+├── code
+├── data
+├── docs
+├── output
+└── workflows
+```
+
++ The **analysis** contains R Markdown source files for the workflowr
+  website, including R code used in the final step of the analysis to
+  generate figures and tables for the manuscript.
+
++ The **code** directory contains additional supporting code for the
+  analyses.
+
++ The **data** directory contains original and processed data files
+  used in the mash analysis of the GTEx data, example data sets used
+  to illustrate the data processing and analysis pipelines, and
+  additional data used to generate the tables and figures for the
+  manuscript.
+
++ The **docs** directory contains webpages generated from the R
+  Markdown files in the analysis directory.
+
++ The **output** stores outputs from data processing and analysis
+  pipelines ("workflows").
+
++ The **workflows** directory contains source code ("SoS workflows")
+  and Docker configuration files ("Dockerfiles") implementing a data
+  processing pipeline for mash and an end-to-end analysis of the GTEx
+  data using the multivariate statistical methods ("mash").
 
@@
 
-All source code and software in this repository are made available
-under the terms of the [MIT license][mit-license]. See the
-[LICENSE](LICENSE) file for the full text of the license.
+Our numerical comparisons make use of some of the functions from
+[WaveLab][wavelab], so we have included the WaveLab source code in
+this repository. See the `COPYING.m` Wavelab850 subdirectory for more
+information about distributing WaveLab.
+
+Our numerical comparisons also use of some functions from
+[waveden][waveden], so we have included the GaussianWaveDen source in
+this repository. For information about distributing GaussianWaveDen,
+see the `copyright.m` in the WavDen subdirectory. Note that we made
+one small improvement to the code in `blockJS.m` to prevent an error
+that occurs when running the code in newer versions of MATLAB.
+
+All other source code and software in this repository are made
+available under the terms of the [MIT license][mit-license]. See the
+`LICENSE` file in the git repository for the full text of the license.
 
@@
 [mit-license]: https://opensource.org/licenses/mit-license.html
+[wavelab]: http://statweb.stanford.edu/~wavelab
+[waveden]: http://www-ljk.imag.fr/SMS/software/GaussianWaveDen/down.html
 [zhengrong]: https://github.com/zrxing

### 2018-12-20 analysis/index.Rmd
wflow_publish("index.Rmd")

@@
 
-## What's included in the git repository
-
-See [here][gtexresults] for the source repository. This is what
-you will find in the repository:
+See [here][smash-github] for the source repository. This is the
+overall structure of the repository:
 
@@
 ├── docs
+├── dsc
 ├── output
-└── workflows
+└── shiny
 ```
 
-+ The **analysis** contains R Markdown source files for the workflowr
-  website, including R code used in the final step of the analysis to
-  generate figures and tables for the manuscript.
++ The `analysis` directory contains R Markdown source files for the
+  workflowr website, including R code implementing the SMASH demos,
+  and R code to generate tables and figures for the manuscript.
 
-+ The **code** directory contains additional supporting code for the
-  analyses.
++ The `code` directory contains additional supporting code for the
+  demos and analyses of the results.
 
-+ The **data** directory contains original and processed data files
-  used in the mash analysis of the GTEx data, example data sets used
-  to illustrate the data processing and analysis pipelines, and
-  additional data used to generate the tables and figures for the
-  manuscript.
++ The `data` directory contains data files used in the ChIP-seq demo.
 
-+ The **docs** directory contains webpages generated from the R
++ The `docs` directory contains webpages generated from the R
   Markdown files in the analysis directory.
 
-+ The **output** stores outputs from data processing and analysis
-  pipelines ("workflows").
++ The `dsc` directory contains R and MATLAB code used to implement the
+  "Gaussian mean estimation" simulations in the manuscript.
 
-+ The **workflows** directory contains source code ("SoS workflows")
-  and Docker configuration files ("Dockerfiles") implementing a data
-  processing pipeline for mash and an end-to-end analysis of the GTEx
-  data using the multivariate statistical methods ("mash").
++ The `output` directory contains results from the Gaussian and
+  Poisson simulations.
+
++ The `shiny` directory contains code to generate the Shiny
+  Web app in R.
 

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

--- 2018-12-20 analysis/poisson.Rmd
@@
 ---
-title: "Title goes here."
+title: "Plots and tables summarizing results of Poisson simulations"
 author: "Zhengrong Xing, Peter Carbonetto and Matthew Stephens"
@@
 
+These are settings used in plotting the test functions:
+
+```{r plot-settings}
+n <- 1024
+t <- 1:n/n
+```
+
 Set up environment
@@
 
+Some of the test functions are defined in `signals.R`:
+
+```{r source-signals}
+source("../code/signals.R")
+```
+
 Load results
@@
 
-## Spikes data
+Spikes data
+-----------
+
+This is the function used to simulate the "Spikes" data sets:
+
+```{r spikes-function, fig.height=5, fig.width=10}
+mu.s <- spike.f(t)
+plot(t,mu.s,xlab = "",ylab = "",type = "l",
+     main = "Spikes intensity function")
+```
 
@@
 									 mise.hf.ti.r.7.s.128))
-p <- ggplot(pdat1,aes(x = method,y = mise,fill = method.type)) +
+n     <- length(mise.ash.s.1)
+pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
+ 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
+p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
       geom_violin(fill = "skyblue",color = "skyblue") +
       geom_boxplot(width = 0.15,outlier.shape = NA) +
-     scale_y_continuous(breaks = seq(6,16,2)) +
-     scale_fill_manual(values = c("darkorange","dodgerblue","gold"),
-                       guide = FALSE) +
-     coord_flip() +
+      coord_flip()
       labs(x = "",y = "MISE") +

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-This is the function used to simulate the "Spikes" data sets:
+This is the function used to simulate the "Spikes" data sets at
+different ranges of intensities:
 
-```{r spikes-function, fig.height=5, fig.width=10}
+```{r plot-spikes-function, fig.height=4, fig.width=8}
 mu.s <- spike.f(t)
@@
 									 mise.hf.ti.r.7.s.128))
-n     <- length(mise.ash.s.1)
-pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
+m     <- length(mise.ash.s.1)
+pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = m),
  				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
@@
 
-### Angles data
+Angles data
+-----------
+
+This is the function used to simulate the "Angles" data sets at
+different ranges of intensities:
+
+```{r plot-angles-function, fig.height=4, fig.width=8}
+mu.ang <- dop.f(t)
+sig <- ((2 * t + 0.5) * (t <= 0.15)) +
+  ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
+  0.2 * (t > 0.2 & t <= 0.5) + 
+  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
+  ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
+  ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
+  ((2 * (t - 0.85) + 0.2) * (t > 0.85))
+mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
+plot(t,mu.ang,xlab = "",ylab = "",type = "l",
+     main = "Angles intensity function")
+```
 
@@
 
-### Heavisine data
+Heavisine data
+--------------
+
+This is the function used to simulate the "Heavisine" data sets at
+different ranges of intensities:
+
+```{r plot-heavisine-function, fig.height=4, fig.width=8}
+heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
+mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
+mu.hs <- mu.hs - min(mu.hs)
+plot(t,mu.hs,xlab = "",ylab = "",type = "l",
+     main = "Heavisine intensity function")
+```
 
@@
 
-### Bursts data
+Bursts data
+-----------
+
+This is the function used to simulate the "Bursts" data sets at
+different ranges of intensities:
+
+```{r plot-bursts-function, fig.height=4, fig.width=8}
+I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
+       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
+I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
+       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
+I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
+       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
+mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
+plot(t,mu.bur,xlab = "",ylab = "",type = "l",
+     main = "Bursts intensity function")
+```
 
@@
 
-### Clipped Blocks data
+Clipped Blocks data
+-------------------
+
+This is the function used to simulate the "Clipped Blocks" data sets at
+different ranges of intensities:
+
+```{r plot-cb-function, fig.height=4, fig.width=8}
+pos   <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
+hgt   <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
+mu.cb <- rep(0,n)
+for (j in 1:length(pos))
+  mu.cb <- mu.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
+mu.cb[mu.cb < 0] <- 0
+plot(t,mu.cb,xlab = "",ylab = "",type = "l",
+     main = "Clipped Blocks intensity function")
+```
 
@@
 
-### Bumps data
+Bumps data
+----------
+
+This is the function used to simulate the "Bumps" data sets at
+different ranges of intensities:
+
+```{r plot-bumps-function, fig.height=4, fig.width=8}
+pos  <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
+hgt  <- 2.97/5 * c(4,5,3,4,5,4.2,2.1,4.3,3.1,5.1,4.2)
+wth  <- c(0.005,0.005,0.006,0.01,0.01,0.03,0.01,0.01,0.005,0.008,0.005)
+mu.b <- rep(0, n)
+for (j in 1:length(pos))
+  mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
+plot(t,mu.b,xlab = "",ylab = "",type = "l",
+     main = "Bumps intensity function")
+```
 

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

--- 2018-12-20 analysis/poisson.Rmd
@@
 ```{r knitr-opts, include=FALSE}
-knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center")
+knitr::opts_chunk$set(comment = "#",collapse = TRUE,fig.align = "center",
+                      results = "hold")
 ```
@@
 table.row.names <- c("SMASH","BMSM","Haar-Fisz")
-table.col.names <- c("intensity (0.01,3)","intensity (1/8,8)",
-                     "intensity (1/128,128)")
+table.col.names <- c("(1/100,3)","(1/8,8)","(1/128,128)")
 ```
@@
 
-This is the function used to simulate the "Spikes" data sets:
+This is the function used to simulate the "Spikes" data sets at
+different ranges of intensities:
 
-```{r spikes-function, fig.height=5, fig.width=10}
+```{r plot-spikes-function, fig.height=4, fig.width=8}
 mu.s <- spike.f(t)
-plot(t,mu.s,xlab = "",ylab = "",type = "l",
-     main = "Spikes intensity function")
+plot(t,mu.s,xlab = "",ylab = "",type = "l")
 ```
 
-Summarize the results from the Spikes simulations in a table.
-
-Comparison of methods for denoising Poisson data for the "Spikes"
-test function for 3 different (min,max) intensities ((0.01,3),
-(1/8,8), (1/128,128)). Performance is measured using MISE over 100
-independent datasets, with smaller values indicating better
-performance. Values colored in red indicates the smallest MISE amongst
-all methods for a given (min, max) intensity.
+This table summarizes the results from the Spikes simulations:
 
@@
 colnames(mise.s.table) <- table.col.names
-print(xtable(mise.s.table),type = "html")
+print(xtable(mise.s.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
 ```
 
-Summarize the results from the Spikes simulations in combined violin
-and boxplots.
+Each column shows results at a different range of intensities.  The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
 
-```{r spikes-violin-plots, fig.height=5, fig.width=7}
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
+m                  <- length(mise.ash.s.1)
+method.labels      <- c("Haar-Fisz","BMSM","SMASH")
 mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
@@
 									 mise.hf.ti.r.7.s.128))
-n     <- length(mise.ash.s.1)
-pdat1 <- data.frame(method = rep(c("SMASH","BMSM","HF"),each = n),
- 				    mise   = c(mise.ash.s.1,mise.BMSM.s.1,mise.hf.ti.r.s.1))
+pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
+                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
+pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
+                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
+pdat128 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
 p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
@@
       geom_boxplot(width = 0.15,outlier.shape = NA) +
-      coord_flip()
-      labs(x = "",y = "MISE") +
-     theme(axis.line = element_blank(),
-           axis.ticks.y = element_blank())
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
+	  theme(axis.line = element_blank())
+p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
+      geom_violin(fill = "skyblue",color = "skyblue") +
+      geom_boxplot(width = 0.15,outlier.shape = NA) +
+	  scale_x_discrete(breaks = NULL) +
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
+	  theme(axis.line = element_blank())
+p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
+      geom_violin(fill = "skyblue",color = "skyblue") +
+      geom_boxplot(width = 0.15,outlier.shape = NA) +
+	  scale_x_discrete(breaks = NULL) +
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
+	  theme(axis.line = element_blank())
+plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
 ```
@@
 
-### Angles data
+Angles data
+-----------
 
-```{r, results="asis"}
-print(xtable(mise.ang.table,caption="Comparison of methods for denoising Poisson data for the ``Angles'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
-Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
-Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_ang",digits=2),type = "html")
+This is the function used to simulate the "Angles" data sets at
+different ranges of intensities:
+
+```{r plot-angles-function, fig.height=4, fig.width=8}
+mu.ang <- dop.f(t)
+sig <- ((2 * t + 0.5) * (t <= 0.15)) +
+  ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
+  0.2 * (t > 0.2 & t <= 0.5) + 
+  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
+  ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
+  ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
+  ((2 * (t - 0.85) + 0.2) * (t > 0.85))
+mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
+plot(t,mu.ang,xlab = "",ylab = "",type = "l")
 ```
 
-### Heavisine data
+This table summarizes the results from the Angles simulations:
+
+```{r angles-table, results="asis"}
+mise.ang.table   <- cbind(mise.ang.1[methods],
+                          mise.ang.8[methods],
+                          mise.ang.128[methods])
+rownames(mise.ang.table) <- table.row.names
+colnames(mise.ang.table) <- table.col.names
+print(xtable(mise.ang.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
+```
+
+Each column shows results at a different range of intensities.  The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
+
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r angles-violin-plots, fig.height=3.5, fig.width=10}
+mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
+                                       mise.hf.ti.r.5.ang.1,
+                                       mise.hf.ti.r.6.ang.1,
+					  				   mise.hf.ti.r.7.ang.1))
+mise.hf.ti.r.ang.8   <- colMeans(rbind(mise.hf.ti.r.4.ang.8,
+ 									   mise.hf.ti.r.5.ang.8,
+                                       mise.hf.ti.r.6.ang.8,
+                                       mise.hf.ti.r.7.ang.8))
+mise.hf.ti.r.ang.128 <- colMeans(rbind(mise.hf.ti.r.4.ang.128,
+                                       mise.hf.ti.r.5.ang.128,
+                                       mise.hf.ti.r.6.ang.128,
+									   mise.hf.ti.r.7.ang.128))
+pdat1 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
+pdat8 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
+pdat128 <-
+  data.frame(method=factor(rep(method.labels,each = m),method.labels),
+             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
+p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
+      geom_violin(fill = "skyblue",color = "skyblue") +
+      geom_boxplot(width = 0.15,outlier.shape = NA) +
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
+	  theme(axis.line = element_blank())
+p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
+      geom_violin(fill = "skyblue",color = "skyblue") +
+      geom_boxplot(width = 0.15,outlier.shape = NA) +
+	  scale_x_discrete(breaks = NULL) +
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
+	  theme(axis.line = element_blank())
+p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
+      geom_violin(fill = "skyblue",color = "skyblue") +
+      geom_boxplot(width = 0.15,outlier.shape = NA) +
+	  scale_x_discrete(breaks = NULL) +
+      coord_flip() +
+      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
+	  theme(axis.line = element_blank())
+plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
+```
+
+Heavisine data
+--------------
+
+This is the function used to simulate the "Heavisine" data sets at
+different ranges of intensities:
+
+```{r plot-heavisine-function, fig.height=4, fig.width=8}
+heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
+mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
+mu.hs <- mu.hs - min(mu.hs)
+plot(t,mu.hs,xlab = "",ylab = "",type = "l")
+```
 
@@
 
-### Bursts data
+Bursts data
+-----------
+
+This is the function used to simulate the "Bursts" data sets at
+different ranges of intensities:
+
+```{r plot-bursts-function, fig.height=4, fig.width=8}
+I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
+       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
+I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
+       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
+I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
+       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
+mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
+plot(t,mu.bur,xlab = "",ylab = "",type = "l")
+```
 
@@
 
-### Clipped Blocks data
+Clipped Blocks data
+-------------------
+
+This is the function used to simulate the "Clipped Blocks" data sets at
+different ranges of intensities:
+
+```{r plot-cb-function, fig.height=4, fig.width=8}
+pos   <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
+hgt   <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
+mu.cb <- rep(0,n)
+for (j in 1:length(pos))
+  mu.cb <- mu.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
+mu.cb[mu.cb < 0] <- 0
+plot(t,mu.cb,xlab = "",ylab = "",type = "l")
+```
 
@@
 
-### Bumps data
+Bumps data
+----------
+
+This is the function used to simulate the "Bumps" data sets at
+different ranges of intensities:
+
+```{r plot-bumps-function, fig.height=4, fig.width=8}
+pos  <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
+hgt  <- 2.97/5 * c(4,5,3,4,5,4.2,2.1,4.3,3.1,5.1,4.2)
+wth  <- c(0.005,0.005,0.006,0.01,0.01,0.03,0.01,0.01,0.005,0.008,0.005)
+mu.b <- rep(0, n)
+for (j in 1:length(pos))
+  mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
+plot(t,mu.b,xlab = "",ylab = "",type = "l")
+```
 

### 2018-12-20 analysis/poisson.Rmd

@@
              mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
+create.violin.plots <- function (pdat1, pdat8, pdat128) {
   p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
@@
 	    theme(axis.line = element_blank())
-plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
+  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
+}
+create.violin.plots(pdat1,pdat8,pdat128)
 ```
@@
              mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
-p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
-      geom_violin(fill = "skyblue",color = "skyblue") +
-      geom_boxplot(width = 0.15,outlier.shape = NA) +
-      coord_flip() +
-      labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
-	  theme(axis.line = element_blank())
-p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
-      geom_violin(fill = "skyblue",color = "skyblue") +
-      geom_boxplot(width = 0.15,outlier.shape = NA) +
-	  scale_x_discrete(breaks = NULL) +
-      coord_flip() +
-      labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
-	  theme(axis.line = element_blank())
-p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
-      geom_violin(fill = "skyblue",color = "skyblue") +
-      geom_boxplot(width = 0.15,outlier.shape = NA) +
-	  scale_x_discrete(breaks = NULL) +
-      coord_flip() +
-      labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
-	  theme(axis.line = element_blank())
-plot_grid(p1,p8,p128,nrow = 1,ncol = 3)
+create.violin.plots(pdat1,pdat8,pdat128)
 ```
@@
 ```
+
+This table summarizes the results from the Angles simulations:
+
+```{r heavisine-table, results="asis"}
+mise.ang.table   <- cbind(mise.hs.1[methods],
+                          mise.hs.8[methods],
+                          mise.hs.128[methods])
+rownames(mise.hs.table) <- table.row.names
+colnames(mise.hs.table) <- table.col.names
+print(xtable(mise.hs.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
+```
+
+Each column shows results at a different range of intensities.  The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
 

### 2018-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 ```{r get-spikes-results}
-mise.ang.table <- cbind(mise.ang.1[methods],
-                        mise.ang.8[methods],
-                        mise.ang.128[methods])
 mise.bur.table <- cbind(mise.bur.1[methods],
@@
                         mise.b.128[methods])
-mise.hs.table  <- cbind(mise.hs.1[methods],
-                        mise.hs.8[methods],
-                        mise.hs.128[methods])
-rownames(mise.ang.table) <- table.row.names
 rownames(mise.b.table)   <- table.row.names
 rownames(mise.cb.table)  <- table.row.names
-rownames(mise.hs.table)  <- table.row.names
 rownames(mise.bur.table) <- table.row.names
-colnames(mise.ang.table) <- table.col.names
 colnames(mise.b.table)   <- table.col.names
 colnames(mise.cb.table)  <- table.col.names
-colnames(mise.hs.table)  <- table.col.names
 colnames(mise.bur.table) <- table.col.names
@@
 
-This table summarizes the results from the Angles simulations:
+This table summarizes the results from the Heavisine simulations:
 
 ```{r heavisine-table, results="asis"}
-mise.ang.table   <- cbind(mise.hs.1[methods],
+mise.hs.table <- cbind(mise.hs.1[methods],
                        mise.hs.8[methods],
@@
 
-```{r, results="asis"}
-print(xtable(mise.hs.table,caption="Comparison of methods for denoising Poisson data for the ``Heavisine'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
-Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
-Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_hs",digits=2),type = "html")
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r heavisine-violin-plots, fig.height=3.5, fig.width=10}
+mise.hf.ti.r.hs.1   <- colMeans(rbind(mise.hf.ti.r.4.hs.1,
+                                      mise.hf.ti.r.5.hs.1,
+                                      mise.hf.ti.r.6.hs.1,
+						  			  mise.hf.ti.r.7.hs.1))
+mise.hf.ti.r.hs.8   <- colMeans(rbind(mise.hf.ti.r.4.hs.8,
+                                      mise.hf.ti.r.5.hs.8,
+                                      mise.hf.ti.r.6.hs.8,
+							  		  mise.hf.ti.r.7.hs.8))
+mise.hf.ti.r.hs.128 <- colMeans(rbind(mise.hf.ti.r.4.hs.128,
+                                      mise.hf.ti.r.5.hs.128,
+                                      mise.hf.ti.r.6.hs.128,
+									  mise.hf.ti.r.7.hs.128))
+pdat1 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.hs.1,mise.BMSM.hs.1,mise.ash.hs.1))
+pdat8 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.hs.8,mise.BMSM.hs.8,mise.ash.hs.8))
+pdat128 <-
+  data.frame(method=factor(rep(method.labels,each = m),method.labels),
+             mise  =c(mise.hf.ti.r.hs.128,mise.BMSM.hs.128,mise.ash.hs.128))
+create.violin.plots(pdat1,pdat8,pdat128)
 ```

### 2018-12-20 analysis/index.Rmd
wflow_publish("index.Rmd")

@@
 + The `output` directory contains results from the Gaussian and
-  Poisson simulations.
+  Poisson simulations. File `pois_hf.RData` contains results from
+  experimenting with different Gaussian denoising techniques for the
+  Haar-Fisz algorithm in the Poisson simulations.
 
@@
 Our numerical comparisons also use of some functions from
-[waveden][waveden], so we have included the GaussianWaveDen source in
-this repository. For information about distributing GaussianWaveDen,
-see the `copyright.m` in the WavDen subdirectory. Note that we made
-one small improvement to the code in `blockJS.m` to prevent an error
-that occurs when running the code in newer versions of MATLAB.
+[GaussianWaveDen][waveden], so we have included the GaussianWaveDen
+source in this repository. For information about distributing
+GaussianWaveDen, see the `copyright.m` in the WavDen
+subdirectory. Note that we made one small improvement to the code in
+`blockJS.m` to prevent an error that occurs when running the code in
+newer versions of MATLAB.
 

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-This script produces supplementary tables for Poisson simulations.
+Here we create plots and tables to compare SMASH and against other
+methods for reconstructing a spatially structured signal from
+Poisson-distributed data. Similar to the Gaussian simulations, we
+generated data sets using a variety of test functions and intensity
+ranges. Specifically, we considered 6 test functions, rescaling the
+test function so that the smallest intensity was x and the largest
+intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
+(1/128, 128). For each combination of test function and intensity
+range, we simulated 100 data sets. In the plots and tables below, We
+summarize the error (MISE) in the estimates from the 100 data sets in
+each setting.
 
-*Explain which set of results correspond to the plots given in the main
-text.*
+The plots below summarizing the results from the "Bursts" simulations
+were included in the manuscript.
 

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-Here we create plots and tables to compare SMASH and against other
-methods for reconstructing a spatially structured signal from
+Here we create plots and tables to compare various methods, including
+SMASH, for reconstructing a spatially structured signal from
 Poisson-distributed data. Similar to the Gaussian simulations, we
@@
 (1/128, 128). For each combination of test function and intensity
-range, we simulated 100 data sets. In the plots and tables below, We
-summarize the error (MISE) in the estimates from the 100 data sets in
-each setting.
+range, we simulated 100 data sets. In the plots and tables below, we
+summarize the error (MISE) in the estimates computed in the 100 data
+sets from each simulation setting.
 
-The plots below summarizing the results from the "Bursts" simulations
-were included in the manuscript.
+The plots for the "Bursts" simulations were included in the
+manuscript.
 
@@
 
-Specify the row and column names for the tables:
+These variables specify the row and column names for the tables:
 
@@
 
-*Add text here.*
+Load the ggplot2 cowplot and xtable packages.
 
@@
 
-Some of the test functions are defined in `signals.R`:
+Some of the test functions are defined in `signals.R`, so we load them
+here:
 
@@
 
-Each column shows results at a different range of intensities.  The
-individual table entries give the average error (MISE) in the
+Each column shows the results at a different range of intensities.
+The individual table entries give the average error (MISE) in the
 estimates, in which the average is taken over the 100 data sets
@@
 
-Combine the results of the simulation experiments into several larger
-tables.
-
-```{r get-spikes-results}
+```{r get-spikes-results, echo=FALSE, eval=TRUE}
 mise.bur.table <- cbind(mise.bur.1[methods],

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 ```{r get-spikes-results, echo=FALSE, eval=TRUE}
-mise.bur.table <- cbind(mise.bur.1[methods],
-                        mise.bur.8[methods],
-                        mise.bur.128[methods])
 mise.cb.table  <- cbind(mise.cb.1[methods],
@@
 rownames(mise.cb.table)  <- table.row.names
-rownames(mise.bur.table) <- table.row.names
 colnames(mise.b.table)   <- table.col.names
 colnames(mise.cb.table)  <- table.col.names
-colnames(mise.bur.table) <- table.col.names
 ```
@@
 
-```{r, results="asis"}
-print(xtable(mise.bur.table,caption="Comparison of methods for denoising Poisson data for the ``Bursts'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
-Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
-Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_bur",digits=2),type = "html")
+This table summarizes the results from the Bursts simulations:
+
+```{r bursts-table, results="asis"}
+mise.bur.table <- cbind(mise.bur.1[methods],
+                        mise.bur.8[methods],
+                        mise.bur.128[methods])
+rownames(mise.bur.table) <- table.row.names
+colnames(mise.bur.table) <- table.col.names
+print(xtable(mise.bur.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
+```
+
+Each column shows results at a different range of intensities. The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
+
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r bursts-violin-plots, fig.height=3.5, fig.width=10}
+mise.hf.ti.r.bur.1   <- colMeans(rbind(mise.hf.ti.r.4.bur.1,
+                                       mise.hf.ti.r.5.bur.1,
+                                       mise.hf.ti.r.6.bur.1,
+						  			   mise.hf.ti.r.7.bur.1))
+mise.hf.ti.r.bur.8   <- colMeans(rbind(mise.hf.ti.r.4.bur.8,
+                                       mise.hf.ti.r.5.bur.8,
+                                       mise.hf.ti.r.6.bur.8,
+									   mise.hf.ti.r.7.bur.8))
+mise.hf.ti.r.bur.128 <- colMeans(rbind(mise.hf.ti.r.4.bur.128,
+                                       mise.hf.ti.r.5.bur.128,
+                                       mise.hf.ti.r.6.bur.128,
+									   mise.hf.ti.r.7.bur.128))
+pdat1 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.bur.1,mise.BMSM.bur.1,mise.ash.bur.1))
+pdat8 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.bur.8,mise.BMSM.bur.8,mise.ash.bur.8))
+pdat128 <-
+  data.frame(method=factor(rep(method.labels,each = m),method.labels),
+             mise  =c(mise.hf.ti.r.bur.128,mise.BMSM.bur.128,mise.ash.bur.128))
+create.violin.plots(pdat1,pdat8,pdat128)
 ```

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 create.violin.plots(pdat1,pdat8,pdat128)
-```
-
-```{r get-spikes-results, echo=FALSE, eval=TRUE}
-mise.cb.table  <- cbind(mise.cb.1[methods],
-                        mise.cb.8[methods],
-                        mise.cb.128[methods])
-mise.b.table   <- cbind(mise.b.1[methods],
-                        mise.b.8[methods],
-                        mise.b.128[methods])
-rownames(mise.b.table)   <- table.row.names
-rownames(mise.cb.table)  <- table.row.names
-colnames(mise.b.table)   <- table.col.names
-colnames(mise.cb.table)  <- table.col.names
 ```
@@
 
-```{r, results="asis"}
-print(xtable(mise.cb.table,caption="Comparison of methods for denoising Poisson data for the ``Clipped Blocks'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
-Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
-Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_cb",digits=2),type = "html")
+This table summarizes the results from the Clipped Blocks simulations:
+
+```{r cb-table, results="asis"}
+mise.cb.table <- cbind(mise.cb.1[methods],
+                       mise.cb.8[methods],
+                       mise.cb.128[methods])
+rownames(mise.cb.table) <- table.row.names
+colnames(mise.cb.table) <- table.col.names
+print(xtable(mise.cb.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
+```
+
+Each column shows results at a different range of intensities. The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
+
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r cb-violin-plots, fig.height=3.5, fig.width=10}
+mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
+                                      mise.hf.ti.r.5.cb.1,
+                                      mise.hf.ti.r.6.cb.1,
+			  						  mise.hf.ti.r.7.cb.1))
+mise.hf.ti.r.cb.8   <- colMeans(rbind(mise.hf.ti.r.4.cb.8,
+                                      mise.hf.ti.r.5.cb.8,
+                                      mise.hf.ti.r.6.cb.8,
+									  mise.hf.ti.r.7.cb.8))
+mise.hf.ti.r.cb.128 <- colMeans(rbind(mise.hf.ti.r.4.cb.128,
+                                      mise.hf.ti.r.5.cb.128,
+                                      mise.hf.ti.r.6.cb.128,
+									  mise.hf.ti.r.7.cb.128))
+pdat1 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
+pdat8 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
+pdat128 <-
+  data.frame(method=factor(rep(method.labels,each = m),method.labels),
+             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
+create.violin.plots(pdat1,pdat8,pdat128)
 ```
@@
 
-```{r, results="asis"}
-print(xtable(mise.b.table,caption="Comparison of methods for denoising Poisson data for the ``Bumps'' test function for 3 different (min,max) intensities ((0.01,3), (1/8,8), (1/128,128)).
-Performance is measured using MISE over 100 independent datasets, with smaller values indicating better performance.
-Values colored in red indicates the smallest MISE amongst all methods for a given (min, max) intensity.",label="table:pois_b",digits=2),type = "html")
+This table summarizes the results from the Bumps simulations:
+
+```{r bumps-table, results="asis"}
+mise.b.table <- cbind(mise.b.1[methods],
+                      mise.b.8[methods],
+                      mise.b.128[methods])
+rownames(mise.b.table) <- table.row.names
+colnames(mise.b.table) <- table.col.names
+print(xtable(mise.b.table,caption = " "),type = "html",
+      html.table.attributes = "border=0")
 ```
+
+Each column shows results at a different range of intensities. The
+individual table entries give the average error (MISE) in the
+estimates, in which the average is taken over the 100 data sets
+simulated at the given range of intensities.
+
+The combined violin-boxplots provide a visualization of the same
+results:
+
+```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
+mise.hf.ti.r.b.1 = colMeans(matrix(c(mise.hf.ti.r.4.b.1, mise.hf.ti.r.5.b.1, mise.hf.ti.r.6.b.1, mise.hf.ti.r.7.b.1), byrow = TRUE, nr = 4))
+mise.hf.ti.r.b.8 = colMeans(matrix(c(mise.hf.ti.r.4.b.8, mise.hf.ti.r.5.b.8, mise.hf.ti.r.6.b.8, mise.hf.ti.r.7.b.8), byrow = TRUE, nr = 4))
+mise.hf.ti.r.b.128 = colMeans(matrix(c(mise.hf.ti.r.4.b.128, mise.hf.ti.r.5.b.128, mise.hf.ti.r.6.b.128, mise.hf.ti.r.7.b.128), byrow = TRUE, nr = 4))
+pdat1 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
+pdat8 <-
+  data.frame(method = factor(rep(method.labels,each = m),method.labels),
+             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
+pdat128 <-
+  data.frame(method=factor(rep(method.labels,each = m),method.labels),
+             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
+create.violin.plots(pdat1,pdat8,pdat128)
+```

### 2018-12-21 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 ```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
-mise.hf.ti.r.b.1 = colMeans(matrix(c(mise.hf.ti.r.4.b.1, mise.hf.ti.r.5.b.1, mise.hf.ti.r.6.b.1, mise.hf.ti.r.7.b.1), byrow = TRUE, nr = 4))
-mise.hf.ti.r.b.8 = colMeans(matrix(c(mise.hf.ti.r.4.b.8, mise.hf.ti.r.5.b.8, mise.hf.ti.r.6.b.8, mise.hf.ti.r.7.b.8), byrow = TRUE, nr = 4))
-mise.hf.ti.r.b.128 = colMeans(matrix(c(mise.hf.ti.r.4.b.128, mise.hf.ti.r.5.b.128, mise.hf.ti.r.6.b.128, mise.hf.ti.r.7.b.128), byrow = TRUE, nr = 4))
+mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,
+                                     mise.hf.ti.r.5.b.1,
+                                     mise.hf.ti.r.6.b.1,
+                                     mise.hf.ti.r.7.b.1))
+mise.hf.ti.r.b.8   <- colMeans(rbind(mise.hf.ti.r.4.b.8,
+                                     mise.hf.ti.r.5.b.8,
+                                     mise.hf.ti.r.6.b.8,
+									 mise.hf.ti.r.7.b.8))
+mise.hf.ti.r.b.128 <- colMeans(rbind(mise.hf.ti.r.4.b.128,
+									 mise.hf.ti.r.5.b.128,
+									 mise.hf.ti.r.6.b.128,
+									 mise.hf.ti.r.7.b.128))
 pdat1 <-

### 2018-12-21 analysis/index.Rmd
wflow_publish(c("index.Rmd", "poisson.Rmd"))

@@
 + The `output` directory contains results from the Gaussian and
-  Poisson simulations. File `pois_hf.RData` contains results from
-  experimenting with different Gaussian denoising techniques for the
-  Haar-Fisz algorithm in the Poisson simulations.
+  Poisson simulations. The `pois_hf.RData` file in this directory
+  contains results from experimenting with different Gaussian
+  denoising techniques for the Haar-Fisz algorithm in the Poisson
+  simulations.
 

### 2019-03-14 analysis/index.Rmd
Updated LICENSE; updated main workflowr page.

@@
 
-> Zhengrong Xing and Matthew Stephens (2016). *Smoothing via Adaptive
-Shrinkage (smash): denoising Poisson and heteroskedastic Gaussian
-signals.* [arXiv:1709.10066][smash-preprint].
+> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2019).
+> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
+> [arXiv:1605.07787][smash-preprint].
 
@@
 The following analyses generate some of the empirical results
-presented in [Xing & Stephens (2016)][smash-preprint]. If you
-encounter a problem running any of the R code in these examples,
+presented in [Xing, Carbonetto & Stephens (2019)][smash-preprint]. If
+you encounter a problem running any of the R code in these examples,
 please post an [issue][issues].
@@
 
-Copyright (c) 2016-2018, Zhengrong Xing, Peter Carbonetto & Matthew
+Copyright (c) 2016-2019, Zhengrong Xing, Peter Carbonetto & Matthew
 Stephens.
@@
 [smashr]: https://github.com/stephenslab/smashr
-[smash-preprint]: http://arxiv.org/abs/1605.07787
+[smash-preprint]: https://arxiv.org/abs/1605.07787
 [issues]: https://github.com/stephenslab/smash-paper/issues

### 2019-11-08 analysis/gausdemo.Rmd
Added data points to gausdemo plots.

This demo plots SMASH against TI-thresholding (using RMAD to estimate variance) for a variety of mean-variance-snr combinations.

```{r demo, fig.height=4, fig.width=6}
library(AlgDesign)
library(smashr)
source("../code/signals.R")

# today's date
set.seed(191027)

meanfn = c(spikes.fn, bumps.fn, blocks.fn, angles.fn, doppler.fn, blip.fn, cor.fn)
meanfn.short = c("sp", "bump", "blk", "ang", "dop", "blip", "cor")
rsnr = sqrt(c(1, 3))
varfn = c(cons.fn, texp.fn, doppler.fn, cblocks.fn)
varfn.short = c("cons", "texp", "dop", "cblk")

design = gen.factorial(c(length(varfn), length(rsnr), length(meanfn)), center = FALSE)

for (i in 1:dim(design)[1]) {
  name = paste(meanfn.short[design[i, 3]], rsnr[design[i, 2]]^2, varfn.short[design[i, 1]], sep = ".")
  args = list(n = 1024, rsnr = rsnr[design[i, 2]], meanfn = meanfn[[design[i, 3]]], varfn = varfn[[design[i, 1]]])

  t = (1:1024)/1024

  mu = args$meanfn(t, "mean")
  sigma = sqrt(args$varfn(t, "var"))
  sd = sigma/mean(sigma) * sd(mu)/rsnr^2
  x.sim = rnorm(args$n, mu, sd)

  mu.smash = smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
  mu.ti = ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
                        filter.number = 8)
  title = paste("mean: ", meanfn.short[design[i, 3]], ", var: ", varfn.short[design[i, 1]], ", snr: ", rsnr[design[i, 2]]^2, sep = "")
  par(cex.axis = 1)
  plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
       ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4), main = title)
  points(x.sim,cex = 0.7,pch = 1,col = "skyblue")
  lines(mu.ti,col = "dodgerblue",lwd = 3)
  lines(mu.smash,col = "orangered",lwd = 3)
  legend(650, 1.05, c("ground-truth signal", "TI-thresholding (RMAD)", "SMASH"), col = c("black", "dodgerblue", "orangered"), bty = "n", lwd = 1, pt.cex = 1, cex = 0.75)
}
```

### 2019-11-11 analysis/gausfullres.Rmd
update demo and results
only include 7 selected methods shown in paper

This demo plots SMASH against TI-thresholding (using RMAD to estimate variance) for a variety of mean-variance-snr combinations.

```{r demo, fig.height=4, fig.width=6}
load("../output/dscr.RData")
res_agg = aggregate(mise ~ scenario + method, data = res, FUN = mean)
selected_methods = c("smash.true.s8", "smash.s8", "smash.homo.s8", "tithresh.true.s8", "tithresh.smash.s8", "tithresh.rmad.s8", "ebayesthresh")
res_agg = res_agg[res_agg$method %in% selected_methods, ]
scenarios = unique(res_agg$scenario)

for (scenario in scenarios) {

  mise_order = order(res_agg$mise[res_agg$scenario == scenario])
  mise_ordered = sort(res_agg$mise[res_agg$scenario == scenario])
  names_ordered = res_agg$method[res_agg$scenario == scenario][mise_order]
  mise_ordered_rounded = round(mise_ordered, digits = 0)

  par(mar=c(9,4,4,2))
  ylim = c(0, 1.2 * max(mise_ordered))
  bp = barplot(mise_ordered, names.arg = names_ordered, ylim = ylim, las = 2)
  text(x = bp, y = mise_ordered, label = mise_ordered_rounded, pos = 3, cex = 0.8, col = "red") 
  title(scenario)
}

```

### 2019-11-12 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
         labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
+		theme_cowplot() +
 	    theme(axis.line = element_blank())
@@
         labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
+		theme_cowplot() +
 	    theme(axis.line = element_blank())
@@
         labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
+		theme_cowplot() +
 	    theme(axis.line = element_blank())
@@
   data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
+             mise   = c(mise.hf.ti.r.b.1,mise.BMSM.b.1,mise.ash.b.1))
 pdat8 <-
   data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
+             mise   = c(mise.hf.ti.r.b.8,mise.BMSM.b.8,mise.ash.b.8))
 pdat128 <-
   data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
+             mise  =c(mise.hf.ti.r.b.128,mise.BMSM.b.128,mise.ash.b.128))
 create.violin.plots(pdat1,pdat8,pdat128)

### 2019-11-12 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
         labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
-		theme_cowplot() +
-	    theme(axis.line = element_blank())
+		theme_cowplot()
   p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
@@
         labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
-		theme_cowplot() +
-	    theme(axis.line = element_blank())
+		theme_cowplot()
   p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
@@
         labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
-		theme_cowplot() +
-	    theme(axis.line = element_blank())
+		theme_cowplot()
   return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))

### 2019-11-12 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-The plots for the "Bursts" simulations were included in the
-manuscript.
+The plots shown below for the "Bursts" simulations were included in
+the manuscript.
 
@@
 mu.s <- spike.f(t)
-plot(t,mu.s,xlab = "",ylab = "",type = "l")
+plot(t,mu.s,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
         labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
-		theme_cowplot()
+		theme_cowplot() +
+		theme(axis.line = element_blank())
   p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
@@
         geom_boxplot(width = 0.15,outlier.shape = NA) +
-  	    scale_x_discrete(breaks = NULL) +
         coord_flip() +
         labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
-		theme_cowplot()
+		theme_cowplot() +
+		theme(axis.line = element_blank())
   p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
@@
         geom_boxplot(width = 0.15,outlier.shape = NA) +
- 	    scale_x_discrete(breaks = NULL) +
         coord_flip() +
         labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
-		theme_cowplot()
+		theme_cowplot() +
+		theme(axis.line = element_blank())
   return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
@@
 mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
-plot(t,mu.ang,xlab = "",ylab = "",type = "l")
+plot(t,mu.ang,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
 
-```{r angles-violin-plots, fig.height=3.5, fig.width=10}
+```{r angles-violin-plots, fig.height=3.25, fig.width=10}
 mise.hf.ti.r.ang.1   <- colMeans(rbind(mise.hf.ti.r.4.ang.1,
@@
 mu.hs <- mu.hs - min(mu.hs)
-plot(t,mu.hs,xlab = "",ylab = "",type = "l")
+plot(t,mu.hs,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
 
-```{r heavisine-violin-plots, fig.height=3.5, fig.width=10}
+```{r heavisine-violin-plots, fig.height=3.25, fig.width=10}
 mise.hf.ti.r.hs.1   <- colMeans(rbind(mise.hf.ti.r.4.hs.1,
@@
 mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
-plot(t,mu.bur,xlab = "",ylab = "",type = "l")
+plot(t,mu.bur,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
 
-```{r bursts-violin-plots, fig.height=3.5, fig.width=10}
+```{r bursts-violin-plots, fig.height=3.25, fig.width=10}
 mise.hf.ti.r.bur.1   <- colMeans(rbind(mise.hf.ti.r.4.bur.1,
@@
 mu.cb[mu.cb < 0] <- 0
-plot(t,mu.cb,xlab = "",ylab = "",type = "l")
+plot(t,mu.cb,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
 
-```{r cb-violin-plots, fig.height=3.5, fig.width=10}
+```{r cb-violin-plots, fig.height=3.25, fig.width=10}
 mise.hf.ti.r.cb.1   <- colMeans(rbind(mise.hf.ti.r.4.cb.1,
@@
   mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
-plot(t,mu.b,xlab = "",ylab = "",type = "l")
+plot(t,mu.b,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
 ```
@@
 
-```{r bumps-violin-plots, fig.height=3.5, fig.width=10}
+```{r bumps-violin-plots, fig.height=3.25, fig.width=10}
 mise.hf.ti.r.b.1   <- colMeans(rbind(mise.hf.ti.r.4.b.1,

### 2019-11-12 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 ranges. Specifically, we considered 6 test functions, rescaling the
-test function so that the smallest intensity was x and the largest
-intensity was y, with (x,y) set to either (1/100, 3), (1/8, 8) or
-(1/128, 128). For each combination of test function and intensity
-range, we simulated 100 data sets. In the plots and tables below, we
-summarize the error (MISE) in the estimates computed in the 100 data
-sets from each simulation setting.
+test function so that the smallest intensity was $x$ and the largest
+intensity was $y$, with $(x,y)$ set to either $(1/100, 3)$, $(1/8, 8)$
+or $(1/128, 128)$.
+
+For each combination of test function and intensity range, we
+simulated 100 data sets. In the plots and tables below, we summarize
+the error (MISE) in the estimates computed in the 100 data sets from
+each simulation setting.
 
@@
 
-Load the ggplot2 cowplot and xtable packages.
+Load the knitr, kableExtra, ggplot2 and cowplot packages.
 
 ```{r load-pkgs, message=FALSE, warning=FALSE}
+library(knitr)
+library(kableExtra)
 library(ggplot2)
@@
 colnames(mise.s.table) <- table.col.names
-print(xtable(mise.s.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+kable(mise.s.table,format = "html",
+  table.attr = paste("class=\"table\";","style=\"font-family: sans-serif;",
+                     "width: auto; margin-left: auto; margin-right: auto\""))
 ```
@@
 
-The combined violin-boxplots provide a visualization of the same
-results:
+The combined violin-boxplots provide a more detailed summary of
+the same results:
 
@@
 		theme_cowplot() +
-		theme(axis.line = element_blank())
+		theme(plot.title = element_text(size = 14,face = "plain"),
+		      axis.line = element_blank())
   p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
@@
 		theme_cowplot() +
-		theme(axis.line = element_blank())
+		theme(plot.title = element_text(size = 14,face = "plain"),
+		      axis.line = element_blank())
   p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
@@
 		theme_cowplot() +
-		theme(axis.line = element_blank())
+		theme(plot.title = element_text(size = 14,face = "plain"),
+		      axis.line = element_blank())
   return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))

### 2019-11-12 analysis/motorcycle.Rmd
Simplifying some of the code in poisson.Rmd.

@@
 packages. The MASS package is loaded only for the Motorcycle Accident
-data. Some additional functions are defined in
-`functions.motorcycle.R`.
+data. Some additional functions are defined in file
+`motorcycle.functions.R`.
 
@@
 
+Finally, we compare the SMASH estimates (the orange
+line) against the the mean estimates obtained by TI thresholding (dark
+blue line) using RMAD.
+
+```{r plot-ti-thresh-estimates, fig.height=5, fig.width=7}
+res.ti.rmad.mc <- tithresh.rmad.wrapper(x.ini.mc,y.ini.mc)
+
+plot(res.mc$x,res.mc$mu.est,type = "l",
+     ylim = c(min(res.mc$y - 2 * sqrt(res.mc$var.est)),
+              max(res.mc$y + 2 * sqrt(res.mc$var.est))),
+	 xlab = "time (ms)",ylab = "acceleration (g)",lwd = 2,
+	 col = "darkorange",xlim = c(0,60),xaxp = c(0,60,6))
+lines(res.ti.rmad.mc$x,res.ti.rmad.mc$mu.est,lwd = 2,lty = "solid",
+      col = "darkblue")
+points(res.mc$x,res.mc$y,pch = 1,cex = 0.8,col = "black")
+lines(res.mc$x, res.mc$mu.est + 2*sqrt(res.mc$var.est),lty = 5,
+	 lwd = 2,col = "dodgerblue")
+lines(res.mc$x,res.mc$mu.est - 2*sqrt(res.mc$var.est),
+      lty = 5,lwd = 2,col = "dodgerblue")
+legend(30, -100, c("TI-thresholding mean estimate", "SMASH mean estimate", "SMASH variance estimate"), col = c("darkblue", "darkorange", "dodgerblue"), bty = "n", lwd = 1, lty = c(1, 1, 5), pt.cex = 1, cex = 0.75)
+```
+
 [smash-github]: https://github.com/stephenslab/smash-paper

### 2019-11-12 analysis/poisson.Rmd
Simplifying some of the code in poisson.Rmd.

@@
 
-The plots shown below for the "Bursts" simulations were included in
-the manuscript.
+The plots for the "Bursts" simulations shown below were also included
+in the manuscript.
 
@@
 ```{r table-row-and-col-names}
-table.row.names <- c("SMASH","BMSM","Haar-Fisz")
-table.col.names <- c("(1/100,3)","(1/8,8)","(1/128,128)")
 ```
@@
 library(cowplot)
-library(xtable)
 ```
@@
 Some of the test functions are defined in `signals.R`, so we load them
-here:
+here. Some additional functions are defined in file
+`poisson.functions.R`.
 
-```{r source-signals}
+```{r load-functions}
+source("../code/poisson.functions.R")
 source("../code/signals.R")
@@
                       mise.s.128[methods])
-rownames(mise.s.table) <- table.row.names
-colnames(mise.s.table) <- table.col.names
-kable(mise.s.table,format = "html",
-  table.attr = paste("class=\"table\";","style=\"font-family: sans-serif;",
-                     "width: auto; margin-left: auto; margin-right: auto\""))
+create.results.table(mise.s.table)
 ```
@@
              mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
-create.violin.plots <- function (pdat1, pdat8, pdat128) {
-  p1 <- ggplot(pdat1,aes(x = method,y = mise)) +
-        geom_violin(fill = "skyblue",color = "skyblue") +
-        geom_boxplot(width = 0.15,outlier.shape = NA) +
-        coord_flip() +
-        labs(x = "",y = "MISE",title = "intensities (1/100,3)") +
-		theme_cowplot() +
-		theme(plot.title = element_text(size = 14,face = "plain"),
-		      axis.line = element_blank())
-  p8 <- ggplot(pdat8,aes(x = method,y = mise)) +
-        geom_violin(fill = "skyblue",color = "skyblue") +
-        geom_boxplot(width = 0.15,outlier.shape = NA) +
-        coord_flip() +
-        labs(x = "",y = "MISE",title = "intensities (1/8,8)") +
-		theme_cowplot() +
-		theme(plot.title = element_text(size = 14,face = "plain"),
-		      axis.line = element_blank())
-  p128 <- ggplot(pdat128,aes(x = method,y = mise)) +
-        geom_violin(fill = "skyblue",color = "skyblue") +
-        geom_boxplot(width = 0.15,outlier.shape = NA) +
-        coord_flip() +
-        labs(x = "",y = "MISE",title = "intensities (1/128,128)") +
-		theme_cowplot() +
-		theme(plot.title = element_text(size = 14,face = "plain"),
-		      axis.line = element_blank())
-  return(plot_grid(p1,p8,p128,nrow = 1,ncol = 3))
-}
 create.violin.plots(pdat1,pdat8,pdat128)
@@
                         mise.ang.128[methods])
-rownames(mise.ang.table) <- table.row.names
-colnames(mise.ang.table) <- table.col.names
-print(xtable(mise.ang.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+create.results.table(mise.ang.table)
 ```
@@
                        mise.hs.128[methods])
-rownames(mise.hs.table) <- table.row.names
-colnames(mise.hs.table) <- table.col.names
-print(xtable(mise.hs.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+create.results.table(mise.hs.table)
 ```
@@
                         mise.bur.128[methods])
-rownames(mise.bur.table) <- table.row.names
-colnames(mise.bur.table) <- table.col.names
-print(xtable(mise.bur.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+create.results.table(mise.bur.table)
 ```
@@
                        mise.cb.128[methods])
-rownames(mise.cb.table) <- table.row.names
-colnames(mise.cb.table) <- table.col.names
-print(xtable(mise.cb.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+create.results.table(mise.cb.table)
 ```
@@
                       mise.b.128[methods])
-rownames(mise.b.table) <- table.row.names
-colnames(mise.b.table) <- table.col.names
-print(xtable(mise.b.table,caption = " "),type = "html",
-      html.table.attributes = "border=0")
+create.results.table(mise.b.table)
 ```

### 2019-11-12 code/spikesdemo.functions.R

@@ -1,4 +1,4 @@
-# This file defines a few functions used in some of the analyses.
+# This file defines a few functions used in the "spikes" demo.
 
 # Interleave two vectors
 # @param x,y: two vectors of the same length

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish(c("index.Rmd", "gaussian_signals.Rmd", "gaussmeanest.Rmd", "gauss_shiny_setup.Rmd"))
wflow_publish("gaussian_signals.Rmd")

--- 2018-12-04 analysis/gaussian_signals.Rmd
@@
 
-## Generate the ground-truth signals
+Generate the ground-truth signals
+---------------------------------
 
@@
 
-## Plot the signal means
+Plot the signal means
+---------------------
 
@@
 ```{r plot-mean-functions, fig.height=10, fig.width=6}
+theme_set(theme_cowplot())
 plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
@@
 
-## Plot the signal variances
+Plot the signal variances
+-------------------------
 

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 
-Define the Blip mean function.
+Define the "Blip" mean function.
 
 ```{r define-blip}
-mu.blip = (0.32 + 0.6 * t +
-           0.3 * exp(-100 * (t - 0.3)^2)) * (t >= 0 & t <= 0.8) +
-  (-0.28 + 0.6 * t + 0.3 * exp(-100 * (t - 1.3)^2)) * (t > 0.8 & t <= 1)
+mu.blip = blip.fn(t,"mean")
 ```
 
-Define the Corner mean function.
+Define the "Corner" mean function.
 
 ```{r define-corner}
-mu.cor = 623.87 * t^3 * (1 - 2 * t) * (t >= 0 & t <= 0.5) +
-         187.161 * (0.125 - t^3) * t^4 * (t > 0.5 & t <= 0.8) +
-         3708.470441 * (t - 1)^3 * (t > 0.8 & t <= 1)
-mu.cor = (0.6/(max(mu.cor) - min(mu.cor))) * mu.cor
-mu.cor = mu.cor - min(mu.cor) + 0.2
+mu.cor = cor.fn(t,"mean")
 ```
 
-Define the rest of the mean functions.
+Define the remainder of the mean functions.
 
@@
 var3 = (1e-02 + 2 * mu.dop.var)
-var4 = 1e-02 + mu.b
-var5 = 1e-02 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
+var4 = 0.01 + mu.b
+var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
 var1 = var1/2
@@
 theme_set(theme_cowplot())
-plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
-          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
-          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
-          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
-          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
-          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
-          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
+plot.signal <- function (t, y, label)
+  quickplot(t,y,geom = "line",color = I("darkorange"),
+            xlab = "",ylab = "",main = label)
+plot_grid(plot.signal(t,mu.sp,"Spikes (sp)"),
+          plot.signal(t,mu.bump,"Bumps (bump)"),
+          plot.signal(t,mu.blk,"Blocks (blk)"),
+          plot.signal(t,mu.ang,"Angles (ang)"),
+          plot.signal(t,mu.dop,"Doppler (dop)"),
+          plot.signal(t,mu.blip,"Blip (blip)"),
+          plot.signal(t,mu.cor,"Corner (cor)"),
 		  nrow = 4,ncol = 2)
@@
 ```{r plot-variance-functions, fig.height=7.5, fig.width=6}
-plot_grid(
-  qplot(t,var1,geom="line",xlab="",ylab="",main="Constant variance (v1)"),
-  qplot(t,var2,geom="line",xlab="",ylab="",main="Triple exponential (v2)"),
-  qplot(t,var3,geom="line",xlab="",ylab="",main="Doppler (v3)"),
-  qplot(t,var4,geom="line",xlab="",ylab="",main="Bumps (v4)"),
-  qplot(t,var5,geom="line",xlab="",ylab="",main="Clipped (v5)"),
+plot_grid(plot.signal(t,var1,"Constant variance (v1)"),
+          plot.signal(t,var2,"Triple exponential (v2)"),
+          plot.signal(t,var3,"Doppler (v3)"),
+		  plot.signal(t,var4,"Bumps (v4)"),
+		  plot.signal(t,var5,"Clipped (v5)"),
 		  nrow = 3,ncol = 2)

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 ```{r specify-n}
-n = 1024
-t = 1:n/n
-```
-
-Define the Spikes mean function.
-
-```{r define-spikes}
-mu.s = spike.f(t)
-```
-
-Define the Bumps variance function.
-
-```{r define-bumps}
-pos = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
-hgt = 2.97/5 * c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
-wth = c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005, 0.008, 0.005)
-mu.b = rep(0, n)
-for (j in 1:length(pos))
-  mu.b = mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
-```
-
-Define the Doppler mean function.
-
-```{r define-doppler}
-mu.dop     = dop.f(t)
-mu.dop     = 3/(max(mu.dop) - min(mu.dop)) * (mu.dop - min(mu.dop))
-mu.dop.var = 10 * dop.f(t)
-mu.dop.var = mu.dop.var - min(mu.dop.var)
+n <- 1024
+t <- 1:n/n
 ```
@@
 
-Define the "Blip" mean function.
+Define the mean functions.
 
-```{r define-blip}
-mu.blip = blip.fn(t,"mean")
-```
-
-Define the "Corner" mean function.
-
-```{r define-corner}
-mu.cor = cor.fn(t,"mean")
+```{r define-mean}
+mu.sp   <- spike.fn(t,"mean")
+mu.bump <- bumps.fn(t,"mean")
+mu.dop  <- doppler.fn(t,"mean")
+mu.blip <- blip.fn(t,"mean")
+mu.cor  <- cor.fn(t,"mean")
 ```
@@
 
-```{r define-mean}
-mu.sp   = (1 + mu.s)/5
-mu.bump = (1 + mu.b)/5
+```{r define-mean-2}
 mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
 mu.ang  = (1 + mu.ang)/5
-mu.dop  = (1 + mu.dop)/5
 ```
@@
 var1 = rep(1, n)
-var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
+var2 = (0.01 + 4 * (exp(-550 * (t - 0.2)^2) +
                      exp(-200 * (t - 0.5)^2) +
                      exp(-950 * (t - 0.8)^2)))
-var3 = (1e-02 + 2 * mu.dop.var)
-var4 = 0.01 + mu.b
+var3 <- doppler.fn(t,"var")
+var4 <- bumps.fn(t,"var")
 var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
@@
 var2 = var2/max(var2)
-var3 = var3/max(var3)
-var4 = var4/max(var4)
 var5 = var5/max(var5)
@@
 
+This function will be used to draw the mean and variance functions.
+
+```{r define-plot-signal}
+plot.signal <- function (t, y, label)
+  quickplot(t,y,geom = "line",color = I("darkorange"),
+            xlab = "",ylab = "",main = label)
+```
+
 These plots show each of the mean functions used in generating the
@@
 theme_set(theme_cowplot())
-plot.signal <- function (t, y, label)
-  quickplot(t,y,geom = "line",color = I("darkorange"),
-            xlab = "",ylab = "",main = label)
 plot_grid(plot.signal(t,mu.sp,"Spikes (sp)"),

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

@@
 
-Define the Angle mean function.
-
-```{r define-angle} 
-sig = ((2 * t + 0.5) * (t <= 0.15)) +
-      ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
-      0.2 * (t > 0.2 & t <= 0.5) + 
-      ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
-      ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
-      ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
-      ((2 * (t - 0.85) + 0.2) * (t > 0.85))
-mu.ang = 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
-```
-Define the Block mean and variance functions.
-
-```{r define-block}
-pos    = c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
-hgt    = 2.88/5 * c(4, (-5), 3, (-4), 5, (-4.2), 2.1, 4.3, (-3.1), 2.1, (-4.2))
-mu.blk = rep(0, n)
-for (j in 1:length(pos))
-  mu.blk = mu.blk + (1 + sign(t - pos[j])) * (hgt[j]/2)
-mu.cblk = mu.blk
-mu.cblk[mu.cblk < 0] = 0
-```
-
 Define the mean functions.
@@
 mu.bump <- bumps.fn(t,"mean")
+mu.blk  <- blocks.fn(t,"mean")
+mu.ang  <- angles.fn(t,"mean")
 mu.dop  <- doppler.fn(t,"mean")
@@
 
-Define the remainder of the mean functions.
-
-```{r define-mean-2}
-mu.blk  = 0.2 + 0.6 * (mu.blk - min(mu.blk))/max(mu.blk - min(mu.blk))
-mu.ang  = (1 + mu.ang)/5
-```
-
 Define the variance functions.
@@
 ```{r define-variance}
-var1 = rep(1, n)
-var2 = (0.01 + 4 * (exp(-550 * (t - 0.2)^2) +
-                     exp(-200 * (t - 0.5)^2) +
-                     exp(-950 * (t - 0.8)^2)))
+var1 <- cons.fn(t,"var")
+var2 <- texp.fn(t,"var")
 var3 <- doppler.fn(t,"var")
 var4 <- bumps.fn(t,"var")
-var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
-var1 = var1/2
-var2 = var2/max(var2)
-var5 = var5/max(var5)
+var5 <- cblocks.fn(t,"var")
 ```
@@
 
-This function will be used to draw the mean and variance functions.
+This function is used to draw the mean and variance functions.
 

### 2019-11-12 analysis/poisson.Rmd
Restructured some of the code in signals.R.

@@
 
-We will extract the results from these methods:
+We will view the results from these methods:
 
@@
 ```{r plot-angles-function, fig.height=4, fig.width=8}
-mu.ang <- dop.f(t)
-sig <- ((2 * t + 0.5) * (t <= 0.15)) +
-  ((-12 * (t - 0.15) + 0.8) * (t > 0.15 & t <= 0.2)) +
-  0.2 * (t > 0.2 & t <= 0.5) + 
-  ((6 * (t - 0.5) + 0.2) * (t > 0.5 & t <= 0.6)) +
-  ((-10 * (t - 0.6) + 0.8) * (t > 0.6 & t <= 0.65)) +
-  ((-0.5 * (t - 0.65) + 0.3) * (t > 0.65 & t <= 0.85)) +
-  ((2 * (t - 0.85) + 0.2) * (t > 0.85))
-mu.ang <- 3/5 * ((5/(max(sig) - min(sig))) * sig - 1.6) - 0.0419569
+mu.ang <- angles.f(t)
 plot(t,mu.ang,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
@@
 ```{r plot-cb-function, fig.height=4, fig.width=8}
-pos   <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
-hgt   <- 2.88/5 * c(4,-5,3,-4,5,-4.2,2.1,4.3,-3.1,2.1,-4.2)
-mu.cb <- rep(0,n)
-for (j in 1:length(pos))
-  mu.cb <- mu.cb + (1 + sign(t - pos[j])) * (hgt[j]/2)
-mu.cb[mu.cb < 0] <- 0
+mu.cb <- cblocks.f(t)
 plot(t,mu.cb,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
@@
 ```{r plot-bumps-function, fig.height=4, fig.width=8}
-pos  <- c(0.1,0.13,0.15,0.23,0.25,0.4,0.44,0.65,0.76,0.78,0.81)
-hgt  <- 2.97/5 * c(4,5,3,4,5,4.2,2.1,4.3,3.1,5.1,4.2)
-wth  <- c(0.005,0.005,0.006,0.01,0.01,0.03,0.01,0.01,0.005,0.008,0.005)
-mu.b <- rep(0, n)
-for (j in 1:length(pos))
-  mu.b <- mu.b + hgt[j]/((1 + (abs(t - pos[j])/wth[j]))^4)
+mu.b <- bumps.f(t)
 plot(t,mu.b,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")

### 2019-11-12 code/signals.R

@@ -23,6 +23,15 @@ spike.f <- function (x)
 # This defines the "Bumps" mean and variance functions.
 bumps.fn <- function (t, type = c("mean","var")) {
   type <- match.arg(type)
+  if (type == "mean")
+    return((1 + f)/5)
+  else if (type == "var")
+    return(1e-05 + f)
+}
+
+# This is used by bumps.fn to define the "Bumps" mean and variance
+# functions.
+bumps.f <- function (t) {
   pos  <- c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
   hgt  <- 2.97/5*c(4, 5, 3, 4, 5, 4.2, 2.1, 4.3, 3.1, 5.1, 4.2)
   wth  <- c(0.005, 0.005, 0.006, 0.01, 0.01, 0.03, 0.01, 0.01, 0.005,
@@ -30,10 +39,7 @@ bumps.fn <- function (t, type = c("mean","var")) {
   f = rep(0,length(t))
   for (i in 1:length(pos))
     f <- f + hgt[i]/((1 + (abs(t - pos[i])/wth[i]))^4)
-  if (type == "mean")
-    return((1 + f)/5)
-  else if (type == "var")
-    return(1e-05 + f)
+  return(f)
 }
 
 # This defines the "Blocks" mean and variance functions.
@@ -42,8 +48,8 @@ blocks.fn <- function (t, type = c("mean","var")) {
   pos  <- c(0.1, 0.13, 0.15, 0.23, 0.25, 0.4, 0.44, 0.65, 0.76, 0.78, 0.81)
   hgt  <- 2.88/5 * c(4, -5, 3, -4, 5, -4.2, 2.1, 4.3, -3.1, 2.1, -4.2)
   f    <- rep(0,length(t))
-  for (j in 1:length(pos))
-    f <- f + (1 + sign(t - pos[j])) * hgt[j]/2
+  for (i in 1:length(pos))
+    f <- f + (1 + sign(t - pos[i])) * hgt[i]/2
   if (type == "mean")
     return(0.2 + 0.6 * (f - min(f))/max(f - min(f)))
   else if (type == "var")
@@ -52,6 +58,15 @@ blocks.fn <- function (t, type = c("mean","var")) {
 
 # This defines the "Angles" mean function.
 angles.fn <- function (t, type = c("mean","var")) {
+  f <- angles.f(t)
[…]

### 2019-11-13 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 ```{r plot-heavisine-function, fig.height=4, fig.width=8}
-heavi <- 4 * sin(4 * pi * t) - sign(t - 0.3) - sign(0.72 - t)
-mu.hs <- heavi/sqrt(var(heavi)) * 1 * 2.99/3.366185
-mu.hs <- mu.hs - min(mu.hs)
+mu.hs <- heavi.f(t)
 plot(t,mu.hs,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
@@
 ```{r plot-bursts-function, fig.height=4, fig.width=8}
-I_1 <- exp(-(abs(t - 0.2)/0.01)^1.2) * (t <= 0.2) +
-       exp(-(abs(t - 0.2)/0.03)^1.2) * (t > 0.2)
-I_2 <- exp(-(abs(t - 0.3)/0.01)^1.2) * (t <= 0.3) +
-       exp(-(abs(t - 0.3)/0.03)^1.2) * (t > 0.3)
-I_3 <- exp(-(abs(t - 0.4)/0.01)^1.2) * (t <= 0.4) +
-       exp(-(abs(t - 0.4)/0.03)^1.2) * (t > 0.4)
-mu.bur <- 2.99/4.51804 * (4 * I_1 + 3 * I_2 + 4.5 * I_3)
+mu.bur <- bursts.f(t)
 plot(t,mu.bur,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")

### 2019-11-13 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 Some of the test functions are defined in `signals.R`, so we load them
-here. Some additional functions are defined in file
-`poisson.functions.R`.
+here. Some additional functions are defined in file `poisson.functions.R`.
 
 ```{r load-functions}
+source("../code/signals.R")
 source("../code/poisson.functions.R")
-source("../code/signals.R")
 ```
@@
 									 mise.hf.ti.r.7.b.128))
-pdat1 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.b.1,mise.BMSM.b.1,mise.ash.b.1))
-pdat8 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.b.8,mise.BMSM.b.8,mise.ash.b.8))
-pdat128 <-
-  data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.b.128,mise.BMSM.b.128,mise.ash.b.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.hf.1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
+                                         BMSM        = mise.BMSM.b.1,
+		  						         SMASH       = mise.ash.b.1))
+pdat.hf.8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
+                                         BMSM        = mise.BMSM.b.8,
+				   				         SMASH       = mise.ash.b.8))
+pdat.hf.128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
+                                         BMSM        = mise.BMSM.b.128,
+									     SMASH       = mise.ash.b.128))
+create.violin.plots(pdat.hf.1,pdat.hf.8,pdat.hf.128)
 ```
+
+Combined results
+----------------
+
+*Create plot showing combined results here.*

### 2019-11-13 analysis/poisson.Rmd
Some small adjustments to the plotting code in poisson.Rmd.

@@
 									 mise.hf.ti.r.7.b.128))
-pdat.hf.1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
-                                         BMSM        = mise.BMSM.b.1,
-		  						         SMASH       = mise.ash.b.1))
-pdat.hf.8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
-                                         BMSM        = mise.BMSM.b.8,
-				   				         SMASH       = mise.ash.b.8))
-pdat.hf.128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
-                                         BMSM        = mise.BMSM.b.128,
-									     SMASH       = mise.ash.b.128))
-create.violin.plots(pdat.hf.1,pdat.hf.8,pdat.hf.128)
+pdat.hf1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
+                                        "BMSM"      = mise.BMSM.b.1,
+	  						            "SMASH"     = mise.ash.b.1))
+pdat.hf8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
+                                        "BMSM"      = mise.BMSM.b.8,
+				   				        "SMASH"     = mise.ash.b.8))
+pdat.hf128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
+                                        "BMSM"      = mise.BMSM.b.128,
+									    "SMASH"     = mise.ash.b.128))
+create.violin.plots(pdat.hf1,pdat.hf8,pdat.hf128)
 ```

### 2019-11-14 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

--- 2019-11-13 analysis/poisson.Rmd
@@
 the error (MISE) in the estimates computed in the 100 data sets from
-each simulation setting.
+each simulation setting. A final summary of all the simulations is
+shown at the end.
 
-The plots for the "Bursts" simulations shown below were also included
-in the manuscript.
+The plots shown below for the "Bursts" simulations, as well as the bar
+plots summarizing all the Poisson simulations, were included in the
+manuscript.
 
@@
 ```{r spikes-violin-plots, fig.height=3.5, fig.width=10}
-m                  <- length(mise.ash.s.1)
-method.labels      <- c("Haar-Fisz","BMSM","SMASH")
 mise.hf.ti.r.s.1   <- colMeans(rbind(mise.hf.ti.r.4.s.1,
@@
 									 mise.hf.ti.r.7.s.128))
-pdat1 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
-                    mise   = c(mise.hf.ti.r.s.1,mise.BMSM.s.1,mise.ash.s.1))
-pdat8 <- data.frame(method = factor(rep(method.labels,each = m),method.labels),
-                    mise   = c(mise.hf.ti.r.s.8,mise.BMSM.s.8,mise.ash.s.8))
-pdat128 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.s.128,mise.BMSM.s.128,mise.ash.s.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.s1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.1,
+                                       "BMSM"      = mise.BMSM.s.1,
+	  						           "SMASH"     = mise.ash.s.1))
+pdat.s8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.8,
+                                       "BMSM"      = mise.BMSM.s.8,
+	  						           "SMASH"     = mise.ash.s.8))
+pdat.s128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.s.128,
+                                       "BMSM"      = mise.BMSM.s.128,
+	  						           "SMASH"     = mise.ash.s.128))
+create.violin.plots(pdat.s1,pdat.s8,pdat.s128)
 ```
@@
 									   mise.hf.ti.r.7.ang.128))
-pdat1 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.ang.1,mise.BMSM.ang.1,mise.ash.ang.1))
-pdat8 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.ang.8,mise.BMSM.ang.8,mise.ash.ang.8))
-pdat128 <-
-  data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.ang.128,mise.BMSM.ang.128,mise.ash.ang.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.ang1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.1,
+                                         "BMSM"      = mise.BMSM.ang.1,
+	  						             "SMASH"     = mise.ash.ang.1))
+pdat.ang8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.8,
+                                         "BMSM"      = mise.BMSM.ang.8,
+	  						             "SMASH"     = mise.ash.ang.8))
+pdat.ang128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.ang.128,
+                                         "BMSM"      = mise.BMSM.ang.128,
+	  						             "SMASH"     = mise.ash.ang.128))
+create.violin.plots(pdat.ang1,pdat.ang8,pdat.ang128)
 ```
@@
 									  mise.hf.ti.r.7.hs.128))
-pdat1 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.hs.1,mise.BMSM.hs.1,mise.ash.hs.1))
-pdat8 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.hs.8,mise.BMSM.hs.8,mise.ash.hs.8))
-pdat128 <-
-  data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.hs.128,mise.BMSM.hs.128,mise.ash.hs.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.hs1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.1,
+                                        "BMSM"      = mise.BMSM.hs.1,
+	  						            "SMASH"     = mise.ash.hs.1))
+pdat.hs8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.8,
+                                        "BMSM"      = mise.BMSM.hs.8,
+	  						            "SMASH"     = mise.ash.hs.8))
+pdat.hs128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.hs.128,
+                                        "BMSM"      = mise.BMSM.hs.128,
+	  						            "SMASH"     = mise.ash.hs.128))
+create.violin.plots(pdat.hs1,pdat.hs8,pdat.hs128)
 ```
@@
 									   mise.hf.ti.r.7.bur.128))
-pdat1 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.bur.1,mise.BMSM.bur.1,mise.ash.bur.1))
-pdat8 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.bur.8,mise.BMSM.bur.8,mise.ash.bur.8))
-pdat128 <-
-  data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.bur.128,mise.BMSM.bur.128,mise.ash.bur.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.bur1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.1,
+                                         "BMSM"      = mise.BMSM.bur.1,
+	  						             "SMASH"     = mise.ash.bur.1))
+pdat.bur8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.8,
+                                         "BMSM"      = mise.BMSM.bur.8,
+	  						             "SMASH"     = mise.ash.bur.8))
+pdat.bur128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.bur.128,
+                                         "BMSM"      = mise.BMSM.bur.128,
+	  						             "SMASH"     = mise.ash.bur.128))
+create.violin.plots(pdat.bur1,pdat.bur8,pdat.bur128)
 ```
@@
 									  mise.hf.ti.r.7.cb.128))
-pdat1 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.cb.1,mise.BMSM.cb.1,mise.ash.cb.1))
-pdat8 <-
-  data.frame(method = factor(rep(method.labels,each = m),method.labels),
-             mise   = c(mise.hf.ti.r.cb.8,mise.BMSM.cb.8,mise.ash.cb.8))
-pdat128 <-
-  data.frame(method=factor(rep(method.labels,each = m),method.labels),
-             mise  =c(mise.hf.ti.r.cb.128,mise.BMSM.cb.128,mise.ash.cb.128))
-create.violin.plots(pdat1,pdat8,pdat128)
+pdat.cb1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.1,
+                                        "BMSM"      = mise.BMSM.cb.1,
+	  						            "SMASH"     = mise.ash.cb.1))
+pdat.cb8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.8,
+                                        "BMSM"      = mise.BMSM.cb.8,
+	  						            "SMASH"     = mise.ash.cb.8))
+pdat.cb128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.cb.128,
+                                        "BMSM"      = mise.BMSM.cb.128,
+	  						            "SMASH"     = mise.ash.cb.128))
+create.violin.plots(pdat.cb1,pdat.cb8,pdat.cb128)
 ```
@@
 									 mise.hf.ti.r.7.b.128))
-pdat.hf.1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
-                                         BMSM        = mise.BMSM.b.1,
-		  						         SMASH       = mise.ash.b.1))
-pdat.hf.8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
-                                         BMSM        = mise.BMSM.b.8,
-				   				         SMASH       = mise.ash.b.8))
-pdat.hf.128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
-                                         BMSM        = mise.BMSM.b.128,
-									     SMASH       = mise.ash.b.128))
-create.violin.plots(pdat.hf.1,pdat.hf.8,pdat.hf.128)
+pdat.b1   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.1,
+                                       "BMSM"      = mise.BMSM.b.1,
+	  						           "SMASH"     = mise.ash.b.1))
+pdat.b8   <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.8,
+                                       "BMSM"      = mise.BMSM.b.8,
+				   				       "SMASH"     = mise.ash.b.8))
+pdat.b128 <- get.violin.plot.data(list("Haar-Fisz" = mise.hf.ti.r.b.128,
+                                       "BMSM"      = mise.BMSM.b.128,
+									   "SMASH"     = mise.ash.b.128))
+create.violin.plots(pdat.b1,pdat.b8,pdat.b128)
 ```

### 2019-11-14 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-Load the knitr, kableExtra, ggplot2 and cowplot packages.
+Load the plyr, knitr, kableExtra, ggplot2 and cowplot packages.
 
 ```{r load-pkgs, message=FALSE, warning=FALSE}
+library(plyr)
 library(knitr)
@@
 
-*Create plot showing combined results here.*
+These plots summarize the results for all 6 simulation scenarios.
+
+```{r summarize-all-results, fig.height=6, fig.width=10}
+pdat.s1$simulation   <- "Spikes"
+pdat.s8$simulation   <- "Spikes"
+pdat.s128$simulation <- "Spikes"
+pdat.s1$intensity    <- "(1/100, 3)"
+pdat.s8$intensity    <- "(1/8, 8)"
+pdat.s128$intensity  <- "(1/128, 128)"
+
+pdat.ang1$simulation   <- "Angles"
+pdat.ang8$simulation   <- "Angles"
+pdat.ang128$simulation <- "Angles"
+pdat.ang1$intensity    <- "(1/100, 3)"
+pdat.ang8$intensity    <- "(1/8, 8)"
+pdat.ang128$intensity  <- "(1/128, 128)"
+
+pdat.hs1$simulation   <- "Heavisine"
+pdat.hs8$simulation   <- "Heavisine"
+pdat.hs128$simulation <- "Heavisine"
+pdat.hs1$intensity    <- "(1/100, 3)"
+pdat.hs8$intensity    <- "(1/8, 8)"
+pdat.hs128$intensity  <- "(1/128, 128)"
+
+pdat.bur1$simulation   <- "Bursts"
+pdat.bur8$simulation   <- "Bursts"
+pdat.bur128$simulation <- "Bursts"
+pdat.bur1$intensity    <- "(1/100, 3)"
+pdat.bur8$intensity    <- "(1/8, 8)"
+pdat.bur128$intensity  <- "(1/128, 128)"
+
+pdat.cb1$simulation   <- "Clipped"
+pdat.cb8$simulation   <- "Clipped"
+pdat.cb128$simulation <- "Clipped"
+pdat.cb1$intensity    <- "(1/100, 3)"
+pdat.cb8$intensity    <- "(1/8, 8)"
+pdat.cb128$intensity  <- "(1/128, 128)"
+
+pdat.b1$simulation   <- "Bumps"
+pdat.b8$simulation   <- "Bumps"
+pdat.b128$simulation <- "Bumps"
+pdat.b1$intensity    <- "(1/100, 3)"
+pdat.b8$intensity    <- "(1/8, 8)"
+pdat.b128$intensity  <- "(1/128, 128)"
+
+pdat <- rbind(pdat.s1,pdat.s8,pdat.s128,
+              pdat.ang1,pdat.ang8,pdat.ang128,
+              pdat.hs1,pdat.hs8,pdat.hs128,
+              pdat.bur1,pdat.bur8,pdat.bur128,
+              pdat.cb1,pdat.cb8,pdat.cb128)
+p1   <- create.bar.plots(pdat,show.legend = FALSE)
+pdat <- rbind(pdat.b1,pdat.b8,pdat.b128)
+p2   <- create.bar.plots(pdat)
+plot_grid(p1,p2,nrow = 1,rel_widths =  c(7,4))
+```

### 2019-12-16 analysis/poisson.Rmd
Small edit to code in poisson.Rmd.
Implemented function create.signal.plot in poisson.functions.R.

@@
 
+Initialize the sequence of pseudorandom numbers.
+
 Load results
@@
 
-This is the function used to simulate the "Spikes" data sets at
-different ranges of intensities:
+This plot shows the function used to simulate the "Spikes" data sets
+at the $(1/100, 3)$ intensity range, along with an example data set
+(black circles):
 
-```{r plot-spikes-function, fig.height=4, fig.width=8}
-mu.s <- spike.f(t)
-plot(t,mu.s,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+```{r plot-spikes-function, fig.height=2.5, fig.width=8}
+mu.s <- 0.01 + spike.f(t)
+x    <- rpois(n,mu.s)
+create.signal.plot(mu.s,x)
 ```
@@
 
-```{r plot-angles-function, fig.height=4, fig.width=8}
-mu.ang <- angles.f(t)
-plot(t,mu.ang,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+```{r plot-angles-function, fig.height=2.5, fig.width=8}
+mu.ang <- 0.01 + angles.f(t)
+x      <- rpois(n,mu.ang)
+create.signal.plot(mu.ang,x)
 ```
@@
 
-```{r plot-heavisine-function, fig.height=4, fig.width=8}
-mu.hs <- heavi.f(t)
-plot(t,mu.hs,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+```{r plot-heavisine-function, fig.height=2.5, fig.width=8}
+mu.hs <- 0.01 + heavi.f(t)
+x     <- rpois(n,mu.hs)
+create.signal.plot(mu.hs,x)
 ```

### 2019-12-16 code/poisson.functions.R

@@ -1,5 +1,13 @@
 # This file defines some functions used by the "poisson" analysis.
 
+# Create a plot showing the test function (mu) and an example data set
+# simulated using that test function (x).
+create.signal.plot <- function (mu, x)
+  ggplot(data.frame(x = t,y = x),aes_string(x = "x",y = "y")) +
+    geom_point(color = "black",shape = 1) +
+    geom_line(dat = data.frame(x = t,y = mu),color = "darkorange",size = 1) +
+    labs(x = "",y = "")
+
 # This function is used to create the tables in the "poisson"
 # analysis.
 create.results.table <- function (dat) {

### 2019-12-16 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-```{r plot-bursts-function, fig.height=4, fig.width=8}
-mu.bur <- bursts.f(t)
-plot(t,mu.bur,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+```{r plot-bursts-function, fig.height=2.5, fig.width=8}
+mu.bur <- 0.01 + bursts.f(t)
+x      <- rpois(n,mu.bur)
+create.signal.plot(mu.bur,x)
 ```
@@
 ```{r plot-cb-function, fig.height=4, fig.width=8}
-mu.cb <- cblocks.f(t)
-plot(t,mu.cb,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+mu.cb <- 0.01 + cblocks.f(t)
+x     <- rpois(n,mu.cb)
+create.signal.plot(mu.cb,x)
 ```
@@
 ```{r plot-bumps-function, fig.height=4, fig.width=8}
-mu.b <- bumps.f(t)
-plot(t,mu.b,xlab = "",ylab = "",type = "l",lwd = 2,col = "darkorange")
+mu.b <- 0.01 + bumps.f(t)
+x    <- rpois(n,mu.b)
+create.signal.plot(mu.b,x)
 ```

### 2019-12-16 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
+```{r set-seed}
+set.seed(1)
+```
+
 Load results
@@
 x    <- rpois(n,mu.s)
-create.signal.plot(mu.s,x)
+create.signal.plot(t,x,mu.s)
 ```
@@
 x      <- rpois(n,mu.ang)
-create.signal.plot(mu.ang,x)
+create.signal.plot(t,x,mu.ang)
 ```
@@
 x     <- rpois(n,mu.hs)
-create.signal.plot(mu.hs,x)
+create.signal.plot(t,x,mu.hs)
 ```
@@
 x      <- rpois(n,mu.bur)
-create.signal.plot(mu.bur,x)
+create.signal.plot(t,x,mu.bur)
 ```
@@
 x     <- rpois(n,mu.cb)
-create.signal.plot(mu.cb,x)
+create.signal.plot(t,x,mu.cb)
 ```
@@
 x    <- rpois(n,mu.b)
-create.signal.plot(mu.b,x)
+create.signal.plot(t,x,mu.b)
 ```

### 2019-12-18 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

--- 2018-11-07 analysis/motorcycle.Rmd
@@
 
-Apply SMASH again, this time assuming equal variances
------------------------------------------------------
+SMASH, homoskedastic vs. heteroskedastic
+----------------------------------------
 
-Apply SMASH (assuming equal variances) to the Motorcycle Accident data
-set.
+Apply SMASH, this time assuming equal variances, to the Motorcycle
+Accident data set:
 
@@
 ```
-
-Apply TI thresholding to the Motorcycle Accident data
------------------------------------------------------
-
-Apply TI thresholding to the Motorcycle Accident data set.
-
-```{r run-tithresh}
-res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
-```
-
-Apply TI thresholding to the Motorcycle Accident data, this time using
-the variances estimated by SMASH.
-
-```{r run-tithresh-with-smash-var}
-res.ti.mc <- tithresh.wrapper(x.ini.mc,y.ini.mc)
-```
-
-Compare results from all methods
---------------------------------
 
@@
 
-And in this next plot, we compare the SMASH estimates (the orange
-line) against the the mean estimates obtained by TI thresholding (dark
-blue line), and TI thresholding when the variances have been estimated
-by SMASH (dotted green line).
+While the estimates are similar, heteroskedastic SMASH yields a
+noticeably smoother curve.
+
+Apply TI thresholding to the Motorcycle Accident data
+-----------------------------------------------------
+
+Apply TI thresholding to the Motorcycle Accident data set. In this
+first run, the variance is assumed to be constant.
+
+```{r run-tithresh}
+res.ti.cons.mc <- tithresh.cons.wrapper(x.ini.mc,y.ini.mc)
+```
+
+Apply TI thresholding to the Motorcycle Accident data, this time using
+the variances estimated using the "median absolute deviation", or
+RMAD, method.
+
+```{r run-tithresh-rmad}
+res.ti.rmad.mc <- tithresh.rmad.wrapper(x.ini.mc,y.ini.mc)
+```
+
+Apply TI thresholding to the Motorcycle Accident data, this time using
+the variances estimated by SMASH.
+
+```{r run-tithresh-with-smash-var}
+res.ti.mc <- tithresh.wrapper(x.ini.mc,y.ini.mc)
+```
+
+Compare SMASH vs. TI thresholding
+---------------------------------
+
+In this next plot, we compare the SMASH estimates with heteroskedastic
+variances (the same orange line as above) against the the mean estimates
+obtained by TI thresholding with constant variance (solid dark blue
+line), TI thresholding with RMAD variance estimates (solid light blue
+line), and TI thresholding when the variances have been estimated by
+SMASH (dotted green line).
 
@@
 	 col = "darkblue")
+lines(res.ti.rmad.mc$x,res.ti.rmad.mc$mu.est,lwd = 2,lty = "solid",
+      col = "dodgerblue")
 lines(res.ti.mc$x,res.ti.mc$mu.est,lwd = 2,col = "limegreen",lty = "dotted")
@@
 
-The TI thresholding estimate and the SMASH estimate with homoskedastic
-variances both show notable artifacts. When the TI thresholding method
-is provided with the SMASH variance estimate, the mean signal is
-substantially smoother.
+The TI thresholding estimate, like the SMASH estimate with
+homoskedastic variances, shows notable artifacts. When TI thresholding
+estimates the variance using RMAD, or when it is provided with the
+SMASH variance estimate, the mean signal is substantially smoother.
 

### 2019-12-18 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 
-The TI thresholding estimate, like the SMASH estimate with
-homoskedastic variances, shows notable artifacts. When TI thresholding
-estimates the variance using RMAD, or when it is provided with the
-SMASH variance estimate, the mean signal is substantially smoother.
+The TI thresholding estimate with constant variance, like the SMASH
+estimate with homoskedastic variances (in the plot above), shows
+notable artifacts. By contrast, when TI thresholding is provided with
+either the RMAD or SMASH variance estimates, the mean signal is
+substantially smoother.
 

### 2019-12-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")
Adjusted setup steps in a few of the R Markdown files.
Working on code to run HF method in chipseq example.

@@
 library(cowplot)
+library(haarfisz)
 ```
@@
 
-Run SMASH
----------
+Run SMASH and Haar-Fisz methods
+-------------------------------
+
+The Haar-Fisz method transforms the Poisson counts, then applies
+Gaussian wavelet methods to the transformed data.
+
+```{r run-haar-fisz}
+res.hf <- denoise.poisson(counts,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+```
 
@@
 retrieve the peaks identified in the same ChIP-seq data using the MACS
-software.
+software. Again, these data should have been included with the git
+repository you downloaded.
 
@@
 Based on this plot, it is clear that the the strongest SMASH intensity
-estimates align very closely with the peaks found by MACS.
+estimates align very closely with the peaks found by MACS. Intriguingly,
+the SMASH estimates also suggest the presence of several additional
+weaker peaks that were not identified by MACS.
 
-Intriguingly, the SMASH estimates also suggest the presence of several
-additional weaker peaks that were not identified by MACS.
+We compare the results against those produced by Haar-Fisz
+```{r plot-smash-estimates-2, fig.height=3, fig.width=9}
+create.chipseq.plot(bppos/1e6,counts,res.hf,(peaks$start + peaks$end)/2e6,
+                    nbreaks = 80) +
+  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
+  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
+```
 

### 2019-12-18 code/chipseq.functions.R

@@ -16,6 +16,19 @@ read.macs.peaks <- function (file, min.pos, max.pos) {
               end    = peaks[i,3]))
 }
 
+# This is the Gaussian denoising routine used in the Haar-Fisz method;
+# this specifies the "meth.1" argument in the call to "denoise.poisson"
+# from the haarfisz package.
+hf.la10.ti4 <- function (x) {
+  TT      <- length(x)
+  thresh  <- sqrt(2*log(TT))
+  x.w     <- wd(x,10,"DaubLeAsymm",type = "station")
+  x.w.t   <- threshold(x.w,levels = 4:(x.w$nlevels-1),policy = "manual",
+                       value = thresh,type = "hard")
+  x.w.t.r <- AvBasis(convert(x.w.t))
+  return(x.w.t.r)
+}
+
 # Create a plot showing. This is a very *ad hoc* implementation that
 # will only work for the specific data set that was analyzed in the
 # "chipseq.Rmd" example.

### 2019-12-18 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

@@
 The Haar-Fisz method transforms the Poisson counts, then applies
-Gaussian wavelet methods to the transformed data.
+Gaussian wavelet methods to the transformed data. Note that this call
+can take several minutes to run on a modern desktop computer.
 
@@
 Next, we apply SMASH to the read counts to estimate the mean and
-variance of the underlying signal. It may take several minutes to
+variance of the underlying signal. It could also take several minutes to
 complete this step.
@@
 
-Plot the SMASH estimates
-------------------------
+Plot the SMASH and Haar-Fisz estimates
+--------------------------------------
 
@@
 
-This next plot shows the intensity function estimated by SMASH (orange
-line). The read count data are depicted as light blue circles, in
-which the area of each circle is scaled by the number of data points
-that fall within each 1.6-kb "bin". (We show counts summarized within
-bins because there are too many data points to plot them
-individually.)
+This next plot shows the intensity functions estimated by SMASH
+(orange line) and the Haar-Fisz method (dark blue line). The read
+count data are depicted as light blue circles, in which the area of
+each circle is scaled by the number of data points that fall within
+each 1.6-kb "bin". (We show counts summarized within bins because
+there are too many data points to plot them individually.)
 
@@
 ```{r plot-smash-estimates, fig.height=3, fig.width=9}
-create.chipseq.plot(bppos/1e6,counts,res$est,(peaks$start + peaks$end)/2e6,
-                    nbreaks = 80) +
+create.chipseq.plot(bppos/1e6,counts,res$est,res.hf,
+                    (peaks$start + peaks$end)/2e6,nbreaks = 80) +
   scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
@@
 
-Based on this plot, it is clear that the the strongest SMASH intensity
-estimates align very closely with the peaks found by MACS. Intriguingly,
-the SMASH estimates also suggest the presence of several additional
-weaker peaks that were not identified by MACS.
-
-We compare the results against those produced by Haar-Fisz
-```{r plot-smash-estimates-2, fig.height=3, fig.width=9}
-create.chipseq.plot(bppos/1e6,counts,res.hf,(peaks$start + peaks$end)/2e6,
-                    nbreaks = 80) +
-  scale_x_continuous(limits = c(0.88,1.02),breaks = seq(0.88,1.02,0.02)) +
-  scale_y_continuous(limits = c(-1,9),breaks = seq(0,8,2))
-```
+Based on this plot, it is clear that the strongest Haar-Fisz and SMASH
+intensity estimates align very closely with the peaks found by
+MACS. Intriguingly, the SMASH estimates also suggest the presence of
+several additional weaker peaks that were not identified by MACS.
 

### 2019-12-18 analysis/chipseq.Rmd
Made a few small revisions to the text in the chipseq analysis.

@@
 
-```{r run-smash}
+```{r run-smash, warning=FALSE}
 res <- smash.poiss(counts,post.var = TRUE)
@@
 software. Again, these data should have been included with the git
-repository you downloaded.
+repository you downloaded by following the instructions above.
 
@@
 each 1.6-kb "bin". (We show counts summarized within bins because
-there are too many data points to plot them individually.)
-
-The peaks identified by the MACS software are shown as red
-triangles. (Specifically, these are the *mean positions* of the
-identified peak intervals; the peak intervals are short enough that it
-is not useful to show both the start and end positions of these
-intervals.)
+there are too many data points to plot them individually.) The peaks
+identified by the MACS software are shown as red triangles.
+(Specifically, these are the *mean positions* of the identified peak
+intervals; the peak intervals are short enough that it is not useful
+to show both the start and end positions of these intervals.)
 
@@
 Based on this plot, it is clear that the strongest Haar-Fisz and SMASH
-intensity estimates align very closely with the peaks found by
-MACS. Intriguingly, the SMASH estimates also suggest the presence of
-several additional weaker peaks that were not identified by MACS.
+intensity estimates align very closely with the peaks found by MACS,
+although the Haar-Fisz method failed to replicate at least two of
+the MACS peaks. Intriguingly, the SMASH estimates also suggest the
+presence of several additional weaker peaks that were not identified
+by MACS.
 

### 2019-12-18 code/chipseq.functions.R

@@ -1,3 +1,16 @@
+# This is the Gaussian denoising routine used in the Haar-Fisz method;
+# this specifies the "meth.1" argument in the call to "denoise.poisson"
+# from the haarfisz package.
+hf.la10.ti4 <- function (x) {
+  TT      <- length(x)
+  thresh  <- sqrt(2*log(TT))
+  x.w     <- wd(x,10,"DaubLeAsymm",type = "station")
+  x.w.t   <- threshold(x.w,levels = 4:(x.w$nlevels-1),policy = "manual",
+                       value = thresh,type = "hard")
+  x.w.t.r <- AvBasis(convert(x.w.t))
+  return(x.w.t.r)
+}
+
 # Load the MACS peaks data from a text file, returning all peaks
 # within the selected range of base-pair positions.
 read.macs.peaks <- function (file, min.pos, max.pos) {
@@ -16,23 +29,11 @@ read.macs.peaks <- function (file, min.pos, max.pos) {
               end    = peaks[i,3]))
 }
 
-# This is the Gaussian denoising routine used in the Haar-Fisz method;
-# this specifies the "meth.1" argument in the call to "denoise.poisson"
-# from the haarfisz package.
-hf.la10.ti4 <- function (x) {
-  TT      <- length(x)
-  thresh  <- sqrt(2*log(TT))
-  x.w     <- wd(x,10,"DaubLeAsymm",type = "station")
-  x.w.t   <- threshold(x.w,levels = 4:(x.w$nlevels-1),policy = "manual",
-                       value = thresh,type = "hard")
-  x.w.t.r <- AvBasis(convert(x.w.t))
-  return(x.w.t.r)
-}
-
 # Create a plot showing. This is a very *ad hoc* implementation that
 # will only work for the specific data set that was analyzed in the
 # "chipseq.Rmd" example.
-create.chipseq.plot <- function (pos, counts, smash.est, peaks, nbreaks) {
+create.chipseq.plot <- function (pos, counts, smash.est, hf.est, peaks,
+                                 nbreaks) {
 
   # Sum the read counts in equally sized "bins" (small chromosome
   # intervals).
@@ -54,7 +55,10 @@ create.chipseq.plot <- function (pos, counts, smash.est, peaks, nbreaks) {
          scale_size(range = c(0.5,3.5)) +
          geom_line(data = data.frame(position = pos,y = 4*smash.est),
                    mapping = aes_string(x = "position",y = "y"),
-                   color = "darkorange",inherit.aes = FALSE) +
[…]

### 2019-12-20 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 
-```{r plot-cb-function, fig.height=4, fig.width=8}
+```{r plot-cb-function, fig.height=2.5, fig.width=8}
 mu.cb <- 0.01 + cblocks.f(t)
@@
 
-```{r plot-bumps-function, fig.height=4, fig.width=8}
+```{r plot-bumps-function, fig.height=2.5, fig.width=8}
 mu.b <- 0.01 + bumps.f(t)

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 ```{r load-pkgs, message=FALSE, warning=FALSE}
+library(smashr)
 library(ggplot2)
@@
 
-```{r load-results}
+```{r load-results, warning=FALSE}
 load("../output/dscr.RData")
@@
 
-This plot shows the mean function as a block line, and the +/- 2
+This plot shows the mean function as a black line, and the +/- 2
 standard deviations as orange lines:
@@
 t         <- (1:1024)/1024
-mu        <- spikes.fn(t,"mean")
+mu        <- spike.fn(t,"mean")
 sigma.ini <- sqrt(cblocks.fn(t,"var"))
@@
 lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+```
+Now, we plot the ground-truth signal (the mean function, drawn as
+a black line) and the signals recovered by TI thresholding (light blue
+line) and SMASH (the red line) for one simulated dataset as an illustration
+
+```{r spikes-signal-with-estimates, fig.height=4, fig.width=6}
+t         <- (1:1024)/1024
+mu        <- spike.fn(t,"mean")
+sigma.ini <- sqrt(cblocks.fn(t,"var"))
+sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
+x.sim  <- rnorm(1024,mu,sd.fn)
+mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
+mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
+                      filter.number = 8)
+par(cex.axis = 1)
+plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
+     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
+lines(mu.ti,col = "dodgerblue",lwd = 3)
+lines(mu.smash,col = "orangered",lwd = 3)
 ```
@@
 lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+```
+
+Now, we plot the ground-truth signal (the mean function, drawn as
+a black line) and the signals recovered by TI thresholding (light blue
+line) and SMASH (the red line) for one simulated dataset as an illustration
+
+```{r corner-signal-with-estimates, fig.height=4, fig.width=6}
+t         <- (1:1024)/1024
+mu        <- cor.fn(t,"mean") 
+sigma.ini <- sqrt(doppler.fn(t,"var"))
+sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
+x.sim  <- rnorm(1024,mu,sd.fn)
+mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)
+mu.ti    <- ti.thresh(x.sim,method = "rmad",family = "DaubLeAsymm",
+                      filter.number = 8)
+par(cex.axis = 1)
+plot(mu,type = "l",col = "black",lwd = 3,xlab = "position",ylab = "",
+     ylim = c(-0.05,1),xaxp = c(0,1024,4),yaxp = c(0,1,4))
+lines(mu.ti,col = "dodgerblue",lwd = 3)
+lines(mu.smash,col = "orangered",lwd = 3)
 ```

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 
-Since the simulation experiments are computationally intensive, they
-were implemented separately. (For instructions on re-running these
-simulation experiments, see the README in the "dsc" directory of the
-git repository). Here we create plots to summarize the results of
-these experiments.
+Since the simulation experiments are computationally intensive, here
+we only illustrate the application of the signal denoising methods,
+and create plots summarizing the results of the full experiments; the
+full experiments were implemented separately. (For instructions on
+re-running these simulation experiments, see the README in the "dsc"
+directory of the git repository).
 
@@
 source("../code/signals.R")
+source("../code/gaussmeanest.functions.R")
 ```
@@
 accuracy of the mean curves estimated from the data sets that were
-simulated using the "Spikes" mean function with constant variance.
+simulated using the "Spikes" mean function with constant variance and
+a signal-to-noise ratio of 3.
 
-First, extract the results used to generate this plot.
+First, extract the results used to generate this plot, and transform
+them into a data frame suitable for plotting using ggplot2.
 
 ```{r plot-1-extract-data}
-homo.data.smash <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "smash.s8",]
-homo.data.smash.homo <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "smash.homo.s8",]
-homo.data.tithresh <-
-  res[res$.id == "sp.3.v1" &
-      res$method == "tithresh.homo.s8",]
-homo.data.ebayes <-
-  res[res$.id    == "sp.3.v1" &
-      res$method == "ebayesthresh",]
-homo.data.smash.true <-
-  res[res$.id == "sp.3.v1" &
-  res$method  == "smash.true.s8",]
-homo.data <-
-  res[res$.id == "sp.3.v1" &
-  (res$method == "smash.s8" |
-   res$method == "ebayesthresh" |
-   res$method == "tithresh.homo.s8"),]
+pdat <- get.results.homosked(res,"sp.3.v1")
 ```
 
-Transform these results into a data frame suitable for ggplot2.
+Create the combined boxplot and violin plot using ggplot2.
 
-```{r plot-1-transform-data}
-pdat <-
-  rbind(data.frame(method      = "smash",
-                   method.type = "est",
-                   mise        = homo.data.smash$mise),
-        data.frame(method      = "smash.homo",
-                   method.type = "homo",
-                   mise        = homo.data.smash.homo$mise),
-        data.frame(method      = "tithresh",
-                   method.type = "homo",
-                   mise        = homo.data.tithresh$mise),
-        data.frame(method      = "ebayesthresh",
-                   method.type = "homo",
-                   mise        = homo.data.ebayes$mise),
-        data.frame(method      = "smash.true",
-                   method.type = "true",
-                   mise        = homo.data.smash.true$mise))
+```{r plot-1-create, fig.height=4, fig.width=5}
 pdat <-
@@
                                        decreasing = TRUE))))
-```
-
-Create the combined boxplot and violin plot using ggplot2.
-
-```{r plot-1-create, fig.height=4, fig.width=5}
 p <- ggplot(pdat,aes(x = method,y = mise,fill = method.type)) +
@@
 outperformed EbayesThresh and TI thresholding in this setting.
+
+*TO DO: Add bar plots summarizing results from all 7 scenarios and 2
+signal-to-noise ratios.*
 

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 ```{r load-pkgs, message=FALSE, warning=FALSE}
+library(plyr)
 library(smashr)
@@
 
-```{r plot-1-extract-data}
+```{r homo-extract-data}
 pdat <- get.results.homosked(res,"sp.3.v1")
@@
 
-```{r plot-1-create, fig.height=4, fig.width=5}
+```{r create-violin-plot-homo, fig.height=4, fig.width=5}
 pdat <-
@@
 
-From this plot, we see that the three variations of SMASH all
+From this plot, we see that the three variants of SMASH all
 outperformed EbayesThresh and TI thresholding in this setting.
 
-*TO DO: Add bar plots summarizing results from all 7 scenarios and 2
-signal-to-noise ratios.*
+These plots summarize the results for all 7 simulation scenarios and
+the two signal-to-noise ratios (1 and 3), including the "Spikes"
+scenario shown in greater detail in the violin plot above.
+
+```{r extract-data-for-barplots-homo, fig.height=5, fig.width=8}
+create.bar.plots(rbind(
+  data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
+  data.frame(sim = "bump",snr = 1,get.results.homosked(res,"bump.1.v1")),
+  data.frame(sim = "blkp",snr = 1,get.results.homosked(res,"blk.1.v1")),
+  data.frame(sim = "ang", snr = 1,get.results.homosked(res,"ang.1.v1")),
+  data.frame(sim = "dop", snr = 1,get.results.homosked(res,"dop.1.v1")),
+  data.frame(sim = "blip",snr = 1,get.results.homosked(res,"blip.1.v1")),
+  data.frame(sim = "cor", snr = 1,get.results.homosked(res,"cor.1.v1")),
+  data.frame(sim = "sp",  snr = 3,get.results.homosked(res,"sp.3.v1")),
+  data.frame(sim = "bump",snr = 3,get.results.homosked(res,"bump.3.v1")),
+  data.frame(sim = "blkp",snr = 3,get.results.homosked(res,"blk.3.v1")),
+  data.frame(sim = "ang", snr = 3,get.results.homosked(res,"ang.3.v1")),
+  data.frame(sim = "dop", snr = 3,get.results.homosked(res,"dop.3.v1")),
+  data.frame(sim = "blip",snr = 3,get.results.homosked(res,"blip.3.v1")),
+  data.frame(sim = "cor", snr = 3,get.results.homosked(res,"cor.3.v1"))))
+```
 

### 2019-12-20 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 
-```{r extract-data-for-barplots-homo, fig.height=5, fig.width=8}
+```{r summarize-results-homo, fig.height=4, fig.width=8}
 create.bar.plots(rbind(

### 2019-12-20 analysis/gausfullres.Rmd
Implemented function create.bar.plots in gaussmeanest.functions.R.

@@
 scenarios = unique(res_agg$scenario)
-
 for (scenario in scenarios) {
-
   mise_order = order(res_agg$mise[res_agg$scenario == scenario])
@@
   mise_ordered_rounded = round(mise_ordered, digits = 0)
-
   par(mar=c(9,4,4,2))
@@
 }
-
 ```

### 2019-12-31 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 ```{r summarize-results-homo, fig.height=4, fig.width=8}
-create.bar.plots(rbind(
+create.bar.plots.homosked(rbind(
   data.frame(sim = "sp",  snr = 1,get.results.homosked(res,"sp.1.v1")),
@@
 thresholding and EbayesThresh approaches.
+
+Combined results from simulated data sets with heteroskedastic errors
+---------------------------------------------------------------------
+
+These plots summarize the results from all combinations of test
+functions and a signal-to-noise ratio of 1.
+
+```{r summarize-results-heterosked-snr-1, fig.height=4.5, fig.width=9}
+create.bar.plots.heterosked(rbind(
+  data.frame(mean="sp",  var="v2",snr=1,get.results.heterosked(res,"sp.1.v2")),
+  data.frame(mean="sp",  var="v3",snr=1,get.results.heterosked(res,"sp.1.v3")),
+  data.frame(mean="sp",  var="v4",snr=1,get.results.heterosked(res,"sp.1.v4")),
+  data.frame(mean="sp",  var="v5",snr=1,get.results.heterosked(res,"sp.1.v5")),
+  data.frame(mean="bump",var="v2",snr=1,get.results.heterosked(res,"bump.1.v2")),
+  data.frame(mean="bump",var="v3",snr=1,get.results.heterosked(res,"bump.1.v3")),
+  data.frame(mean="bump",var="v4",snr=1,get.results.heterosked(res,"bump.1.v4")),
+  data.frame(mean="bump",var="v5",snr=1,get.results.heterosked(res,"bump.1.v5")),
+  data.frame(mean="blk", var="v2",snr=1,get.results.heterosked(res,"blk.1.v2")),
+  data.frame(mean="blk", var="v3",snr=1,get.results.heterosked(res,"blk.1.v3")),
+  data.frame(mean="blk", var="v4",snr=1,get.results.heterosked(res,"blk.1.v4")),
+  data.frame(mean="blk", var="v5",snr=1,get.results.heterosked(res,"blk.1.v5")),
+  data.frame(mean="ang", var="v2",snr=1,get.results.heterosked(res,"ang.1.v2")),
+  data.frame(mean="ang", var="v3",snr=1,get.results.heterosked(res,"ang.1.v3")),
+  data.frame(mean="ang", var="v4",snr=1,get.results.heterosked(res,"ang.1.v4")),
+  data.frame(mean="ang", var="v5",snr=1,get.results.heterosked(res,"ang.1.v5")),
+  data.frame(mean="dop", var="v2",snr=1,get.results.heterosked(res,"dop.1.v2")),
+  data.frame(mean="dop", var="v3",snr=1,get.results.heterosked(res,"dop.1.v3")),
+  data.frame(mean="dop", var="v4",snr=1,get.results.heterosked(res,"dop.1.v4")),
+  data.frame(mean="dop", var="v5",snr=1,get.results.heterosked(res,"dop.1.v5")),
+  data.frame(mean="blip",var="v2",snr=1,get.results.heterosked(res,"blip.1.v2")),
+  data.frame(mean="blip",var="v3",snr=1,get.results.heterosked(res,"blip.1.v3")),
+  data.frame(mean="blip",var="v4",snr=1,get.results.heterosked(res,"blip.1.v4")),
+  data.frame(mean="blip",var="v5",snr=1,get.results.heterosked(res,"blip.1.v5")),
+  data.frame(mean="cor", var="v2",snr=1,get.results.heterosked(res,"cor.1.v2")),
+  data.frame(mean="cor", var="v3",snr=1,get.results.heterosked(res,"cor.1.v3")),
+  data.frame(mean="cor", var="v4",snr=1,get.results.heterosked(res,"cor.1.v4")),
+  data.frame(mean="cor", var="v5",snr=1,get.results.heterosked(res,"cor.1.v5"))))
+```
+
+These plots summarize the results from data sets simulated using a
+signal-to-noise ratio of 3.
+
+```{r summarize-results-heterosked-snr-3, fig.height=4.5, fig.width=9}
+create.bar.plots.heterosked(rbind(
+  data.frame(mean="sp",  var="v2",snr=1,get.results.heterosked(res,"sp.3.v2")),
+  data.frame(mean="sp",  var="v3",snr=1,get.results.heterosked(res,"sp.3.v3")),
+  data.frame(mean="sp",  var="v4",snr=1,get.results.heterosked(res,"sp.3.v4")),
+  data.frame(mean="sp",  var="v5",snr=1,get.results.heterosked(res,"sp.3.v5")),
+  data.frame(mean="bump",var="v2",snr=1,get.results.heterosked(res,"bump.3.v2")),
+  data.frame(mean="bump",var="v3",snr=1,get.results.heterosked(res,"bump.3.v3")),
+  data.frame(mean="bump",var="v4",snr=1,get.results.heterosked(res,"bump.3.v4")),
+  data.frame(mean="bump",var="v5",snr=1,get.results.heterosked(res,"bump.3.v5")),
+  data.frame(mean="blk", var="v2",snr=1,get.results.heterosked(res,"blk.3.v2")),
+  data.frame(mean="blk", var="v3",snr=1,get.results.heterosked(res,"blk.3.v3")),
+  data.frame(mean="blk", var="v4",snr=1,get.results.heterosked(res,"blk.3.v4")),
+  data.frame(mean="blk", var="v5",snr=1,get.results.heterosked(res,"blk.3.v5")),
+  data.frame(mean="ang", var="v2",snr=1,get.results.heterosked(res,"ang.3.v2")),
+  data.frame(mean="ang", var="v3",snr=1,get.results.heterosked(res,"ang.3.v3")),
+  data.frame(mean="ang", var="v4",snr=1,get.results.heterosked(res,"ang.3.v4")),
+  data.frame(mean="ang", var="v5",snr=1,get.results.heterosked(res,"ang.3.v5")),
+  data.frame(mean="dop", var="v2",snr=1,get.results.heterosked(res,"dop.3.v2")),
+  data.frame(mean="dop", var="v3",snr=1,get.results.heterosked(res,"dop.3.v3")),
+  data.frame(mean="dop", var="v4",snr=1,get.results.heterosked(res,"dop.3.v4")),
+  data.frame(mean="dop", var="v5",snr=1,get.results.heterosked(res,"dop.3.v5")),
+  data.frame(mean="blip",var="v2",snr=1,get.results.heterosked(res,"blip.3.v2")),
+  data.frame(mean="blip",var="v3",snr=1,get.results.heterosked(res,"blip.3.v3")),
+  data.frame(mean="blip",var="v4",snr=1,get.results.heterosked(res,"blip.3.v4")),
+  data.frame(mean="blip",var="v5",snr=1,get.results.heterosked(res,"blip.3.v5")),
+  data.frame(mean="cor", var="v2",snr=1,get.results.heterosked(res,"cor.3.v2")),
+  data.frame(mean="cor", var="v3",snr=1,get.results.heterosked(res,"cor.3.v3")),
+  data.frame(mean="cor", var="v4",snr=1,get.results.heterosked(res,"cor.3.v4")),
+  data.frame(mean="cor", var="v5",snr=1,get.results.heterosked(res,"cor.3.v5"))))
+```

### 2019-12-31 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

--- 2019-12-20 analysis/gaussmeanest.Rmd
@@
 thresholding and EbayesThresh approaches.
+
+Combined results from simulated data sets with heteroskedastic errors
+---------------------------------------------------------------------
+
+These plots summarize the results from all combinations of test
+functions and a signal-to-noise ratio of 1.
+
+```{r summarize-results-heterosked-snr-1, fig.height=4.5, fig.width=9}
+create.bar.plots.heterosked(rbind(
+  data.frame(mean="sp",  var="v2",get.results.heterosked(res,"sp.1.v2")),
+  data.frame(mean="sp",  var="v3",get.results.heterosked(res,"sp.1.v3")),
+  data.frame(mean="sp",  var="v4",get.results.heterosked(res,"sp.1.v4")),
+  data.frame(mean="sp",  var="v5",get.results.heterosked(res,"sp.1.v5")),
+  data.frame(mean="bump",var="v2",get.results.heterosked(res,"bump.1.v2")),
+  data.frame(mean="bump",var="v3",get.results.heterosked(res,"bump.1.v3")),
+  data.frame(mean="bump",var="v4",get.results.heterosked(res,"bump.1.v4")),
+  data.frame(mean="bump",var="v5",get.results.heterosked(res,"bump.1.v5")),
+  data.frame(mean="blk", var="v2",get.results.heterosked(res,"blk.1.v2")),
+  data.frame(mean="blk", var="v3",get.results.heterosked(res,"blk.1.v3")),
+  data.frame(mean="blk", var="v4",get.results.heterosked(res,"blk.1.v4")),
+  data.frame(mean="blk", var="v5",get.results.heterosked(res,"blk.1.v5")),
+  data.frame(mean="ang", var="v2",get.results.heterosked(res,"ang.1.v2")),
+  data.frame(mean="ang", var="v3",get.results.heterosked(res,"ang.1.v3")),
+  data.frame(mean="ang", var="v4",get.results.heterosked(res,"ang.1.v4")),
+  data.frame(mean="ang", var="v5",get.results.heterosked(res,"ang.1.v5")),
+  data.frame(mean="dop", var="v2",get.results.heterosked(res,"dop.1.v2")),
+  data.frame(mean="dop", var="v3",get.results.heterosked(res,"dop.1.v3")),
+  data.frame(mean="dop", var="v4",get.results.heterosked(res,"dop.1.v4")),
+  data.frame(mean="dop", var="v5",get.results.heterosked(res,"dop.1.v5")),
+  data.frame(mean="blip",var="v2",get.results.heterosked(res,"blip.1.v2")),
+  data.frame(mean="blip",var="v3",get.results.heterosked(res,"blip.1.v3")),
+  data.frame(mean="blip",var="v4",get.results.heterosked(res,"blip.1.v4")),
+  data.frame(mean="blip",var="v5",get.results.heterosked(res,"blip.1.v5")),
+  data.frame(mean="cor", var="v2",get.results.heterosked(res,"cor.1.v2")),
+  data.frame(mean="cor", var="v3",get.results.heterosked(res,"cor.1.v3")),
+  data.frame(mean="cor", var="v4",get.results.heterosked(res,"cor.1.v4")),
+  data.frame(mean="cor", var="v5",get.results.heterosked(res,"cor.1.v5"))))
+```
+
+These plots summarize the results from data sets simulated using a
+signal-to-noise ratio of 3.
+
+```{r summarize-results-heterosked-snr-3, fig.height=4.5, fig.width=9}
+create.bar.plots.heterosked(rbind(
+  data.frame(mean="sp",  var="v2",get.results.heterosked(res,"sp.3.v2")),
+  data.frame(mean="sp",  var="v3",get.results.heterosked(res,"sp.3.v3")),
+  data.frame(mean="sp",  var="v4",get.results.heterosked(res,"sp.3.v4")),
+  data.frame(mean="sp",  var="v5",get.results.heterosked(res,"sp.3.v5")),
+  data.frame(mean="bump",var="v2",get.results.heterosked(res,"bump.3.v2")),
+  data.frame(mean="bump",var="v3",get.results.heterosked(res,"bump.3.v3")),
+  data.frame(mean="bump",var="v4",get.results.heterosked(res,"bump.3.v4")),
+  data.frame(mean="bump",var="v5",get.results.heterosked(res,"bump.3.v5")),
+  data.frame(mean="blk", var="v2",get.results.heterosked(res,"blk.3.v2")),
+  data.frame(mean="blk", var="v3",get.results.heterosked(res,"blk.3.v3")),
+  data.frame(mean="blk", var="v4",get.results.heterosked(res,"blk.3.v4")),
+  data.frame(mean="blk", var="v5",get.results.heterosked(res,"blk.3.v5")),
+  data.frame(mean="ang", var="v2",get.results.heterosked(res,"ang.3.v2")),
+  data.frame(mean="ang", var="v3",get.results.heterosked(res,"ang.3.v3")),
+  data.frame(mean="ang", var="v4",get.results.heterosked(res,"ang.3.v4")),
+  data.frame(mean="ang", var="v5",get.results.heterosked(res,"ang.3.v5")),
+  data.frame(mean="dop", var="v2",get.results.heterosked(res,"dop.3.v2")),
+  data.frame(mean="dop", var="v3",get.results.heterosked(res,"dop.3.v3")),
+  data.frame(mean="dop", var="v4",get.results.heterosked(res,"dop.3.v4")),
+  data.frame(mean="dop", var="v5",get.results.heterosked(res,"dop.3.v5")),
+  data.frame(mean="blip",var="v2",get.results.heterosked(res,"blip.3.v2")),
+  data.frame(mean="blip",var="v3",get.results.heterosked(res,"blip.3.v3")),
+  data.frame(mean="blip",var="v4",get.results.heterosked(res,"blip.3.v4")),
+  data.frame(mean="blip",var="v5",get.results.heterosked(res,"blip.3.v5")),
+  data.frame(mean="cor", var="v2",get.results.heterosked(res,"cor.3.v2")),
+  data.frame(mean="cor", var="v3",get.results.heterosked(res,"cor.3.v3")),
+  data.frame(mean="cor", var="v4",get.results.heterosked(res,"cor.3.v4")),
+  data.frame(mean="cor", var="v5",get.results.heterosked(res,"cor.3.v5"))))
+```

### 2020-06-16 analysis/gaussmeanest.Rmd
Working on code to illustrate methods applied to Spikes data.
wflow_publish("gaussmeanest.Rmd")

@@
 
-This plot shows the mean function as a black line, and the +/- 2
-standard deviations as orange lines:
+This plot shows the mean function as an orange line, the +/- 2
+standard deviations as dashed, light blue lines, and an example
+simulated data set (black circles):
 
-```{r spikes-signal, fig.height=4, fig.width=6}
-t         <- (1:1024)/1024
-mu        <- spike.fn(t,"mean")
-sigma.ini <- sqrt(cblocks.fn(t,"var"))
-sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
-par(cex.axis = 1,cex.lab = 1.25)
-plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
-     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
-lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
-lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
-```
-Now, we plot the ground-truth signal (the mean function, drawn as
-a black line) and the signals recovered by TI thresholding (light blue
-line) and SMASH (the red line) for one simulated dataset as an illustration
-
-```{r spikes-signal-with-estimates, fig.height=4, fig.width=6}
+```{r spikes-signal-with-data, fig.height=4, fig.width=6}
 t         <- (1:1024)/1024
@@
 x.sim     <- rnorm(1024,mu,sd.fn)
+par(cex.axis = 1,cex.lab = 1.25)
+plot(mu,type = "l", ylim = c(-0.05,1),col = "darkorange",
+     xlab = "position",ylab = "",lwd = 1.75,xaxp = c(0,1024,4),
+     yaxp = c(0,1,4))
+lines(mu + 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
+lines(mu - 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
+points(x.sim,cex = 0.7,pch = 1,col = "black")
+```
+
+Next, we plot the ground-truth signal (the mean function, drawn as a
+black line), and the signals recovered by TI thresholding (light blue
+line) and SMASH (the red line) for the example simulated data set.
+
+```{r spikes-signal-with-estimates, fig.height=4, fig.width=6}
 mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)

### 2020-06-16 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 mean function and the "Doppler" variance function. These plots were
-also used in Fig. 3 of the manuscript.
+also used in Figure 3 of the manuscript.
 
-This plot shows the mean function as a black line, and the +/- 2
-standard deviations as orange lines:
+This plot shows the mean function as an orange line, the +/- 2
+standard deviations as dashed, light blue lines, and an example
+simulated data set (black circles):
 
 ```{r corner-signal, fig.height=4, fig.width=6}
+t         <- (1:1024)/1024
 mu        <- cor.fn(t,"mean") 
@@
 sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
-plot(mu,type = "l", ylim = c(-0.05,1),xlab = "position",ylab = "",
-     lwd = 1.75,xaxp = c(0,1024,4),yaxp = c(0,1,4))
-lines(mu + 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
-lines(mu - 2*sd.fn,col = "darkorange",lty = 5,lwd = 1.75)
+x.sim     <- rnorm(1024,mu,sd.fn)
+plot(mu,type = "l",col = "darkorange",ylim = c(-0.05,1),
+     xlab = "position",ylab = "",lwd = 1.75,xaxp = c(0,1024,4),
+     yaxp = c(0,1,4))
+lines(mu + 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
+lines(mu - 2*sd.fn,col = "dodgerblue",lty = "dashed",lwd = 1.75)
+points(x.sim,cex = 0.7,pch = 1,col = "black")
 ```
@@
 ```{r corner-signal-with-estimates, fig.height=4, fig.width=6}
-t         <- (1:1024)/1024
-mu        <- cor.fn(t,"mean") 
-sigma.ini <- sqrt(doppler.fn(t,"var"))
-sd.fn     <- sigma.ini/mean(sigma.ini) * sd(mu)/3
-x.sim  <- rnorm(1024,mu,sd.fn)
 mu.smash <- smash(x.sim,family = "DaubLeAsymm",filter.number = 8)

### 2020-06-16 analysis/gaussmeanest.Rmd
wflow_publish("gaussmeanest.Rmd")

@@
 source("../code/gaussmeanest.functions.R")
+theme_set(theme_cowplot())
 ```

### 2020-06-23 analysis/gaussmeanest.Rmd
A few small revisions to the workflowr analyses.

@@
 
-Now, we plot the ground-truth signal (the mean function, drawn as
-a black line) and the signals recovered by TI thresholding (light blue
-line) and SMASH (the red line) for one simulated dataset as an illustration
+Now, we plot the ground-truth signal (the mean function, drawn as a
+black line) and the signals recovered by TI thresholding (light blue
+line) and SMASH (the red line) for one simulated dataset as an
+illustration.
 

### 2020-06-23 analysis/poisson.Rmd
A few small revisions to the workflowr analyses.

--- 2019-12-16 analysis/poisson.Rmd
@@
 library(cowplot)
+theme_set(theme_cowplot())
 ```
@@
 x <- rpois(n,mu.s)
-create.signal.plot(t,x,mu.s)
+p1 <- create.signal.plot(t,x,mu.s)
+print(p1)
 ```
@@
 x <- rpois(n,mu.ang)
-create.signal.plot(t,x,mu.ang)
+p2 <- create.signal.plot(t,x,mu.ang)
+print(p2)
 ```
@@
 x <- rpois(n,mu.hs)
-create.signal.plot(t,x,mu.hs)
+p3 <- create.signal.plot(t,x,mu.hs)
+print(p3)
 ```
@@
 x <- rpois(n,mu.bur)
-create.signal.plot(t,x,mu.bur)
+p4 <- create.signal.plot(t,x,mu.bur)
+print(p4)
 ```
@@
 
-```{r plot-cb-function, fig.height=4, fig.width=8}
+```{r plot-cb-function, fig.height=2.5, fig.width=8}
 mu.cb <- 0.01 + cblocks.f(t)
 x <- rpois(n,mu.cb)
-create.signal.plot(t,x,mu.cb)
+p5 <- create.signal.plot(t,x,mu.cb)
+print(p5)
 ```
@@
 
-```{r plot-bumps-function, fig.height=4, fig.width=8}
+```{r plot-bumps-function, fig.height=2.5, fig.width=8}
 mu.b <- 0.01 + bumps.f(t)
 x <- rpois(n,mu.b)
-create.signal.plot(t,x,mu.b)
+p6 <- create.signal.plot(t,x,mu.b)
+print(p6)
 ```
@@
               pdat.cb1,pdat.cb8,pdat.cb128)
-p1   <- create.bar.plots(pdat,show.legend = FALSE)
+pA   <- create.bar.plots(pdat,show.legend = FALSE)
 pdat <- rbind(pdat.b1,pdat.b8,pdat.b128)
-p2   <- create.bar.plots(pdat)
-plot_grid(p1,p2,nrow = 1,rel_widths = c(7,4))
+pB   <- create.bar.plots(pdat)
+plot_grid(pA,pB,nrow = 1,rel_widths = c(7,4))
 ```

### 2020-06-24 analysis/motorcycle.Rmd
wflow_publish("motorcycle.Rmd")

@@
 This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
-applied to the Motorcycle Accident data. This implements the
+applied to the Motorcycle Acceleration data. This implements the
 "illustrative application" presented in Sec. 5.1 of the manuscript.
@@
 Load the MASS, lattice wavethresh, EbayesThresh and smashr
-packages. The MASS package is loaded only for the Motorcycle Accident
+packages. The MASS package is loaded only for the Motorcycle Acceleration
 data. Some additional functions are defined in file
@@
 
-Apply SMASH to the Motorcycle Accident data set.
+Apply SMASH to the Motorcycle Acceleration data set.
 
@@
 
-Create a plot showing the Motorcycle Accident data and the smash
+Create a plot showing the Motorcycle Acceleration data and the smash
 estimates (with the dashed red lines showing the confidence
@@
 Apply SMASH, this time assuming equal variances, to the Motorcycle
-Accident data set:
+Acceleration data set:
 
@@
 
-Apply TI thresholding to the Motorcycle Accident data
+Apply TI thresholding to the Motorcycle Acceleration data
 -----------------------------------------------------
 
-Apply TI thresholding to the Motorcycle Accident data set. In this
+Apply TI thresholding to the Motorcycle Acceleration data set. In this
 first run, the variance is assumed to be constant.
@@
 
-Apply TI thresholding to the Motorcycle Accident data, this time using
+Apply TI thresholding to the Motorcycle Acceleration data, this time using
 the variances estimated using the "median absolute deviation", or
@@
 
-Apply TI thresholding to the Motorcycle Accident data, this time using
+Apply TI thresholding to the Motorcycle Acceleration data, this time using
 the variances estimated by SMASH.

### 2020-06-26 analysis/poisson.Rmd
Added example run of smash and HF methods to poisson demo.

@@
 ```{r load-pkgs, message=FALSE, warning=FALSE}
+library(smashr)
+library(haarfisz)
 library(plyr)
@@
 at the $(1/100, 3)$ intensity range, along with an example data set
-(black circles):
+(black circles), and example fitted curves produced by the SMASH and
+Haar-Fisz methods:
 
@@
 x         <- rpois(n,mu.s)
-p1 <- create.signal.plot(t,x,mu.s)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p1 <- create.signal.plot(t,x,mu.s) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p1)

### 2020-06-26 code/poisson.functions.R

@@ -1,11 +1,24 @@
 # This file defines some functions used by the "poisson" analysis.
 
+# This is the Gaussian denoising routine used in the Haar-Fisz method;
+# this specifies the "meth.1" argument in the call to "denoise.poisson"
+# from the haarfisz package.
+hf.la10.ti4 <- function (x) {
+  TT      <- length(x)
+  thresh  <- sqrt(2*log(TT))
+  x.w     <- wd(x,10,"DaubLeAsymm",type = "station")
+  x.w.t   <- threshold(x.w,levels = 4:(x.w$nlevels-1),policy = "manual",
+                       value = thresh,type = "hard")
+  x.w.t.r <- AvBasis(convert(x.w.t))
+  return(x.w.t.r)
+}
+
 # Create a plot showing the test function (mu) and an example data set
 # simulated using that test function (x).
 create.signal.plot <- function (t, x, mu)
   ggplot(data.frame(x = t,y = x),aes_string(x = "x",y = "y")) +
-    geom_point(color = "black",shape = 1) +
-    geom_line(dat = data.frame(x = t,y = mu),color = "darkorange",size = 1) +
+    geom_point(color = "gray",shape = 1) +
+    geom_line(dat = data.frame(x = t,y = mu),color = "black",size = 1) +
     labs(x = "",y = "")
 
 # This function is used to create the tables in the "poisson"

### 2020-06-26 analysis/poisson.Rmd
wflow_publish("poisson.Rmd")

@@
 This plot shows the function used to simulate the "Spikes" data sets
-at the $(1/100, 3)$ intensity range, along with an example data set
-(black circles), and example fitted curves produced by the SMASH and
-Haar-Fisz methods:
+at the $(1/100, 3)$ intensity range. We also show an example data set
+simulated from the Spikes intensity function (black circles), and the
+fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
+method (light blue) to these data:
 
@@
 This is the function used to simulate the "Angles" data sets at
-different ranges of intensities:
+different ranges of intensities. We also show an example data set
+simulated from the Angles intensity function (black circles), and the
+fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
+method (light blue) to these data:
 
@@
 x         <- rpois(n,mu.ang)
-p2 <- create.signal.plot(t,x,mu.ang)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p2 <- create.signal.plot(t,x,mu.ang) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p2)
@@
 This is the function used to simulate the "Heavisine" data sets at
-different ranges of intensities:
+different ranges of intensities. We also show an example data set
+simulated from the Heavisine intensity function (black circles), and
+the fitted curves obtained by applying SMASH (orange) and the
+Haar-Fisz method (light blue) to these data:
 
@@
 x         <- rpois(n,mu.hs)
-p3 <- create.signal.plot(t,x,mu.hs)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p3 <- create.signal.plot(t,x,mu.hs) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p3)
@@
 This is the function used to simulate the "Bursts" data sets at
-different ranges of intensities:
+different ranges of intensities. We also show an example data set
+simulated from the Bursts intensity function (black circles), and the
+fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
+method (light blue) to these data:
 
@@
 x         <- rpois(n,mu.bur)
-p4 <- create.signal.plot(t,x,mu.bur)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p4 <- create.signal.plot(t,x,mu.bur) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p4)
@@
 
-This is the function used to simulate the "Clipped Blocks" data sets at
-different ranges of intensities:
+This is the function used to simulate the "Clipped Blocks" data sets
+at different ranges of intensities. We also show an example data set
+simulated from the Clipped Blocks intensity function (black circles),
+and the fitted curves obtained by applying SMASH (orange) and the
+Haar-Fisz method (light blue) to these data:
 
@@
 x         <- rpois(n,mu.cb)
-p5 <- create.signal.plot(t,x,mu.cb)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p5 <- create.signal.plot(t,x,mu.cb) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p5)
@@
 This is the function used to simulate the "Bumps" data sets at
-different ranges of intensities:
+different ranges of intensities. We also show an example data set
+simulated from the Bumps intensity function (black circles), and the
+fitted curves obtained by applying SMASH (orange) and the Haar-Fisz
+method (light blue) to these data:
 
@@
 x         <- rpois(n,mu.b)
-p6 <- create.signal.plot(t,x,mu.b)
+out.hf    <- denoise.poisson(x,meth.1 = hf.la10.ti4,cs.1 = 50,hybrid = FALSE)
+out.smash <- smash.poiss(x,post.var = TRUE)
+p6 <- create.signal.plot(t,x,mu.b) +
+  geom_line(dat = data.frame(x = t,y = out.smash$est),col = "darkorange") +
+  geom_line(dat = data.frame(x = t,y = out.hf),col = "dodgerblue")
 print(p6)

### 2021-06-02 analysis/index.Rmd
wflow_publish("analysis/index.Rmd")
workflowr::wflow_publish("index.Rmd")

@@
 
-> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2019).
+> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2020).
 > *Flexible signal denoising via flexible empirical Bayes shrinkage.*
@@
 The following analyses generate some of the empirical results
-presented in [Xing, Carbonetto & Stephens (2019)][smash-preprint]. If
+presented in [Xing, Carbonetto & Stephens (2020)][smash-preprint]. If
 you encounter a problem running any of the R code in these examples,
@@
 
-Copyright (c) 2016-2019, Zhengrong Xing, Peter Carbonetto & Matthew
+Copyright (c) 2016-2021, Zhengrong Xing, Peter Carbonetto & Matthew
 Stephens.

### 2021-06-07 analysis/index.Rmd
workflowr::wflow_publish("index.Rmd")

@@
 
-> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2020).
-> *Flexible signal denoising via flexible empirical Bayes shrinkage.*
-> [arXiv:1605.07787][smash-preprint].
+> Zhengrong Xing, Peter Carbonetto and Matthew Stephens (2021).
+> [Flexible signal denoising via flexible empirical Bayes shrinkage.][smash-jmlr]
+> *Journal of Machine Learning Research* 22(93), 1-28.
 
@@
 [smashr]: https://github.com/stephenslab/smashr
-[smash-preprint]: https://arxiv.org/abs/1605.07787
+[smash-jmlr]: https://jmlr.org/papers/v22/19-042.html
 [issues]: https://github.com/stephenslab/smash-paper/issues

### 2021-06-25 analysis/index.Rmd
workflowr::wflow_publish("index.Rmd")
workflowr::wflow_publish("analysis/index.Rmd")

@@
 > [Flexible signal denoising via flexible empirical Bayes shrinkage.][smash-jmlr]
-> *Journal of Machine Learning Research* 22(93), 1-28.
+> *Journal of Machine Learning Research* 22(93), 1--28.
 
@@
 The following analyses generate some of the empirical results
-presented in [Xing, Carbonetto & Stephens (2020)][smash-preprint]. If
+presented in [Xing, Carbonetto & Stephens (2020)][smash-jmlr]. If
 you encounter a problem running any of the R code in these examples,
